### 2019-10-01 paper.tex
bib

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2020}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\begin{document}

%% Title information
\title{Blame and Coercion: Together Again for the First Time}

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{Kuang-Chen Lu}

\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}                    %% \country is recommended
}
\email{first1.last1@inst1.edu}          %% \email is recommended

\author{Jeremy Siek}

\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{Gradual Typing, Blame, Coercion}
%% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}

Text of paper \ldots

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

%% Bibliography
%\bibliography{bibfile}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

\end{document}

### 2019-10-03 paper.tex
ignore refs
intro and hc rules

@@
                         %% http://ctan.org/pkg/subcaption
+\usepackage{stmaryrd}
+
+\newtheorem{theorem}{Theorem}[section]
+\newcommand{\figref}[1]{Fig.~\ref{#1}}
+\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
+\newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
+\newcommand{\comprule}[4]{#1 & \fatsemi^l & #2 & = & #3 & #4 \\}
+\newcommand{\plus}[0]{+}
 
@@
 %% Title information
-\title{Blame and Coercion: Together Again for the First Time}
+\title{Blame and Coercion: Together Again for the Second Time}
 
@@
 
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
 \affiliation{
-  \position{Position1}
-  \department{Department1}              %% \department is recommended
-  \institution{Institution1}            %% \institution is required
-  \streetaddress{Street1 Address1}
-  \city{City1}
-  \state{State1}
-  \postcode{Post-Code1}
-  \country{Country1}                    %% \country is recommended
+  \department{School of Informatics, Computing, and Engineering}              
+  %% \department is recommended
+  \institution{Indiana University}
+  %% \institution is required
+  \country{United States}
+  %% \country is recommended
 }
-\email{first1.last1@inst1.edu}          %% \email is recommended
+\email{kl13@iu.edu}          %% \email is recommended
 
@@
 \begin{abstract}
-Text of abstract \ldots.
+	Gradual Typing is great. Implementing gradually typed with blame tracking 
+	and space efficiency is tricky. There exist two technique to do this: 
+	coercion and threesome. Coercion is easy to understand, and easy enough to 
+	implement, but difficult to reason about formally. Threesome is hard to 
+	understand, easy to implement, and easy to reason about formally. We 
+	propose hyper-coercion, which is easy to understand, as easy to implement 
+	as coercion, and easy to reason about.
 \end{abstract}
@@
 
-Text of paper \ldots
+\citet{siek2006gradual} introduces gradual typing.
+
+\citet{wadler2009well} introduces blame calculus, an intermediate language for 
+gradually typed languages. Blame calculus includes blame labels, which tells 
+the position of the cast that fails at run time (blame tracking).
+
+Implementing gradually typed languages on top of blame calculus suffices sever 
+space leak. Translation to blame calculus might wrap a tail call with a 
+cast. Thus, at runtime, mutually tail-recursive functions can accumulate casts 
+at tail position.
+
+In 2007, \citet{herman2010space} proposes a solution to this problem by 
+translating Blame Calculus to a variant of \citet{henglein1994dynamic}'s 
+Coercions Calculus. The key idea is to represent casts with coercions. 
+Coercions can be composed and normalized. Their solution, however, doesn't 
+include blame tracking.
+
+After that, many efforts have been made to combine blame tracking and 
+space efficiency.
+
+\citet{siek2009exploring} incorporate blame tracking into Coercion Calculus by 
+decorating coercions with labels. They also propose that there are four blame 
+strategies for their Coercion Calculi:
+$ \{Lazy, Eager\} \times \{D, UD\} $. 
+Lazy strategies blame fewer programs than eager ones,
+but also detect less potential type errors.
+$ D $ and $ UD $ assign blame labels differently.
+They prove that $ Lazy UD $ simulates the Blame Calculus in 
+\cite{wadler2009well}. But the counterparts of other strategies in Blame 
+Calculus is unknown.
+
+\citet{siek2010threesomes} proposes another approach to combine blame 
+tracking and space efficiency. Their solution is based on Threesome Calculus, 
+an novel alternative to Coercion Calculus. The key idea is to represent casts 
+with threesomes. Threesomes, like coercions, can be composed. There is no 
+separate normalization for threesome because every threesome is normalized. 
+They prove that their Threesome Calculus bisimulate 
+\citeauthor{siek2009exploring}'s Coercion Calculus and
+\citeauthor{wadler2009well}'s Blame Calculus.
+
+\citet{siek2012interpretations} introduces a $ lazy D $  Blame Calculus. The 
+relation between this new Blame Calculus with the $ lazy D $ 
+Coercion Calculi, however, is not proved.
+
+Following \citet{siek2010threesomes}, \citet{garcia2013calculating} 
+implement all other blame strategies with Threesome Calculus. 
+He claims that 
+coercion with labels is easy to understand but hard to implement, 
+and that 
+threesome with labels, however, is easy to implement but hard to understand.
+His claim is later affirmed by the group of people who develop threesome 
+\citet{siek2015blame}. 
+The connection 
+between his Threesome Calculi and \citeauthor{siek2009exploring}'s Coercion 
+Calculi are established by the fact that the former are derived from the latter.
+The connection between these calculi and Blame Calculus, however, 
+is still unclear.
+
+\citet{siek2015blame} revisit the coercion-based approach. They simplify the 
+Coercion Calculi by only working with coercions in canonical forms.
+Fortunately, coercions are canonical when initially constructed, and 
+their empowered compose function produces canonical coercions as well. Again 
+(\citet{siek2010threesomes}), they delegate all strategies other than 
+$ Lazy UD $.
+
+Last year, \citet{kuhlenschmidt2018efficient} present Grift, a space-efficient 
+and blame-tracking compiler for a gradually typed language of the same name. 
+This implementation is based on the $ Lazy D $ Coercion Calculus.
+Their result suggests that implementing coercion is practical.
+
+Recently, \citet{new2019gradual} show that $ Eager $ strategies are 
+incompatible with $\eta$-equivalence of functions, which suggest that these 
+strategies are not very ideal. Their research kills questions about $ Eager $ 
+strategies, but some questions about $ Lazy $ strategies remain open:
+
+\begin{itemize}
+	\item Is the $ Lazy D $ coercion an ideal cast representation?
+	\item Does the $ Lazy D $ Calculi bi-simulate each other?
+\end{itemize}
+
+The $ Lazy D $ coercion is claimed easy to understand 
+(\cite{garcia2013calculating}, \cite{siek2015blame}) and is shown 
+easy enough to implement in a compiler (\cite{kuhlenschmidt2018efficient}).
+It is still undesirable, however, in a 
+few aspects. Firstly, its compose function is not structurally recursive. Many 
+developers of Grift report that it is tricky to convince their 
+proof assistants that composition terminates. Secondly, canonical coercion
+obscures the nature of a ``normalized cast'' because its definition lies on 
+top of coercion.
+
+Perhaps unsurprisingly, threesome has a straightforward recursive 
+implementation. And its definition is self-standing. Together with the research 
+by \citet{garcia2013calculating}, they suggest that there can be a cast 
+representation whose definition is self-standing, and whose composition is 
+structurally recursive. Super-coercion introduced in 
+\citet{garcia2013calculating} could 
+be a promising candidate. However, its definition is a bit complicated. It uses 
+10 constructors to deal with an elementary type system with only base types and 
+function types. And four constructors are directly related to 
+function types. Thus, super-coercion might not scale very well to more 
+sophisticated type systems.
+
+We present yet another cast representation, hyper-coercion. Its 
+composition is structurally recursive. And its definition is self-standing. 
+Besides, there is a clear connection between it and the canonical coercion, 
+so we are optimistic that implementing hyper-coercion should be as easy (or 
+as hard) as coercion.
+
+Our hyper-coercion considers sum types and product types, which are not 
+accounted in all proofs above. Adding each of them requires us to add only one 
+new constructor to a component of hyper-coercion. This suggests that 
+hyper-coercion might scale better than super-coercion.
+
+We prove formally that $ Lazy D $ (resp. $ Lazy UD $) hyper-coercion calculi 
+bi-simulate the $ Lazy D $ (resp. $ Lazy UD $) Blame Calculi. This is possibly 
+the first bi-simulation proof for the $ Lazy D $ Blame Calculus.
+
+\section{Blame Calculus}
+
+syntax, consistency, shallow consistency ...
+
+\subsection{$Lazy D$ Blame Calculus}
+
+subtyping, reduction ...
+
+\subsection{$Lazy UD$ Blame Calculus}
+
+subtyping, reduction ...
+
+\section{Coercion Calculus}
+
+\subsection{$Lazy D$ Coercion Calculus}
+
+\subsection{$Lazy UD$ Coercion Calculus}
+
+\section{Hyper-coercion}
+
+\begin{figure}
+	\[ 
+	\begin{array}{lclr}
+	\stxrule{c}{hyper-coercions}{
+		id* \mid{}
+		( h , ( b , t ) )
+	}
+	\stxrule{h}{heads}{
+		\epsilon \mid{}
+		?^l
+	}
+	\stxrule{b}{bodies}{
+		U \mid{}
+		c_1 \rightarrow c_2 \mid{}
+		c_1 \times c_2 \mid{}
+		c_1 \plus c_2
+	}
+	\stxrule{t}{tails}{
+		\epsilon \mid{}
+		! \mid{}
+		\bot^l
+	}
+	\end{array}
+	\]
+
+	\fbox{$ c \fatsemi^l c = c $}
+	\[ 
+	\begin{array}{rclclr}
+	\comprule{id*}{id*}{
+		id*
+	}{}
+	\comprule{id*}{( ?^{l'} , ( b , t ) )}{
+		( ?^{l'} , ( b , t ) )
+	}{}
+	\comprule{id*}{( ! , ( b , t ) )}{
+		(?^{l} , ( b , t))
+	}{}
+	\comprule{(h , (b ,\bot^{l'}))}{c}{
+		(h , (b ,\bot^{l'}))
+	}{}
+	\comprule{(h , (b_1 , t_1))}{id*}{
+		(h , (b_1 , !))
+	}{t_1 \neq \bot^{l'}}
+	\comprule{(h , (b_1 , t_1))}{(\epsilon , (b_2 , t_2))}{
+		(h , b_1 \fatsemi^{l} (b_2 , t_2))
+	}{t_1 \neq \bot^{l'}}
+	\comprule{(h , (b_1 , t_1))}{(?^{l'} , (b_2 , t_2))}{
+		(h , b_1 \fatsemi^{l'} (b_2 , t_2))
+	}{t_1 \neq \bot^{l'}}
+	\end{array}
+	\]
+
+	\fbox{$ b \fatsemi^l (b,t) = (b,t) $}
+	\[ 
+	\begin{array}{rclclr}
+	\comprule{U}{(U,t)}{
+		(U,t)
+	}{}
+	\comprule{c_1 \rightarrow c_2}{(c_3 \rightarrow c_4,t)}{
+		(c_3 \fatsemi^{l} c_1 \rightarrow c_2 \fatsemi^l c_4, t)
+	}{}
+	\comprule{c_1 \times c_2}{(c_3 \times c_4,t)}{
+		(c_3 \fatsemi^{l} c_1 \times c_2 \fatsemi^l c_4, t)
+	}{}
+	\comprule{c_1 \plus c_2}{(c_3 \plus c_4,t)}{
+		(c_3 \fatsemi^{l} c_1 \plus c_2 \fatsemi^l c_4, t)
+	}{}
+	\comprule{b_1}{(b_2,t_2)}{
+		(b_1,\bot^l)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ seq(c,c) = c $}
+	\[
+	\begin{array}{rclr}
+	\funrule{seq(c_1,c_2)}{
+		c_1 \fatsemi^l c_2
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ id( T ) = c $}
+	\[
+	\begin{array}{rclr}
+	\funrule{id(*)}{
+		id*
+	}{}
+	\funrule{id(P)}{
+		(\epsilon,(id(P),\epsilon))
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ id( P ) = b $}
+	\[
+	\begin{array}{rclr}
+	\funrule{id(U)}{U}{}
+	\funrule{id(T_1 \rightarrow T_2)}{
+		id(T_1) \rightarrow id(T_2)
+	}{}
+	\funrule{id(T_1 \times T_2)}{
+		id(T_1) \times id(T_2)
+	}{}
+	\funrule{id(T_1 \plus T_2)}{
+		id(T_1) \plus id(T_2)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ cast(T,l,T) = c$}
+	\[
+	\begin{array}{rclr}
+	\funrule{cast(T_1,l,T_2)}{
+		id(T_1) \fatsemi^l id(T_2)
+	}{}
+	\end{array}
+	\]
+
+	\caption{Hyper-coercion}
+	\label{fig:HC-syntax}
+\end{figure}
+
+The syntax of Hyper-coercion is shown in \figref{fig:HC-syntax}.
+
+\subsection{$Lazy D$ Hyper-coercion}
+
+\subsection{$Lazy UD$ Hyper-coercion}
+
+\subsection{Hyper-coercion is Correct}
+
+\begin{theorem}[Hyper-coercion bi-simulates cast]	
+	$ e \Downarrow_B o $ if and only if $ e \Downarrow_H o $
+\end{theorem}
+
+\subsection{Hyper-coercion is Space-efficient}
+
+\section{Related Work}
+
+\section{Conclusion}
 
@@
 %% Bibliography
-%\bibliography{bibfile}
+\bibliography{bibfile}
 

### 2019-10-03 paper.tex
update

@@
 \usepackage{stmaryrd}
+\usepackage{todonotes}
 
@@
 
-\citet{siek2006gradual} introduces gradual typing.
+\todo[inline]{KC: I want to add more citations here}
 
@@
 
-\section{Blame Calculus}
+The structure of this paper is as follows. Section \ref{sec:blame-calculus} 
+reviews the state-of-art of $Lazy$ Coercion Calculi. In section 
+\ref{sec:hyper-coercion} we present Hyper-coercion. Section \ref{sec:conclude} 
+concludes.
+
+\section{Blame Calculus} \label{sec:blame-calculus}
 
@@
 
-\section{Hyper-coercion}
+\section{Hyper-coercion} \label{sec:hyper-coercion}
 
@@
 
-	\caption{Hyper-coercion}
-	\label{fig:HC-syntax}
+	\caption{$Lazy D$ Hyper-coercion}
+	\label{fig:HC-D}
 \end{figure}
 
-The syntax of Hyper-coercion is shown in \figref{fig:HC-syntax}.
+\subsection{$Lazy D$ Hyper-coercion}
 
-\subsection{$Lazy D$ Hyper-coercion}
+The syntax of $ Lazy D $ Hyper-coercion is shown in \figref{fig:HC-D}.
 
@@
 
-\section{Related Work}
-
-\section{Conclusion}
+\section{Conclusion} \label{sec:conclude}
 

### 2019-10-03 paper.tex
head of section 2

@@
 \usepackage{todonotes}
+\usepackage{amsthm}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{stmaryrd}
+\usepackage{semantic}
+\usepackage{hyperref}
 
@@
 \newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
+\newcommand{\stxrulecont}[1]{& | & #1 & \\}
 \newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
@@
 \newcommand{\plus}[0]{+}
+\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
 
@@
 They prove that their Threesome Calculus bisimulate 
-\citeauthor{siek2009exploring}'s Coercion Calculus and
-\citeauthor{wadler2009well}'s Blame Calculus.
+\citet{siek2009exploring}'s Coercion Calculus and
+\citet{wadler2009well}'s Blame Calculus.
 
-\citet{siek2012interpretations} introduces a $ lazy D $  Blame Calculus. The 
-relation between this new Blame Calculus with the $ lazy D $ 
-Coercion Calculi, however, is not proved.
+\citet{siek2012interpretations} introduces a $ lazy D $  Blame Calculus. They 
+conjecture that this calculus bi-simulate the $ lazy D $ Coercion Calculi.
 
@@
 The connection 
-between his Threesome Calculi and \citeauthor{siek2009exploring}'s Coercion 
+between his Threesome Calculi and \citet{siek2009exploring}'s Coercion 
 Calculi are established by the fact that the former are derived from the latter.
@@
 This implementation is based on the $ Lazy D $ Coercion Calculus.
-Their result suggests that implementing coercion is practical.
+Their result suggests that implementing coercion is practical. And this is the 
+first time product types is considered. Their treatment to products in 
+coercions, however, is shown incorrect. **
+
+\todo[inline]{kc: ** I want to cite the GitHub issue page here.}
 
@@
 	\item Is the $ Lazy D $ coercion an ideal cast representation?
-	\item Does the $ Lazy D $ Calculi bi-simulate each other?
+	\item Does the $ Lazy D $ Coercion Calculus bi-simulate the Blame Calculus?
 \end{itemize}
@@
 
-syntax, consistency, shallow consistency ...
+\begin{figure}
+	\[
+	\begin{array}{lclr}
+	\stxrule{S,T}{types}{
+		\star \mid{}
+		P
+	}
+	\stxrule{P,Q}{pre-types}{
+		\iota \mid{}
+		T_1 \rightarrow T_2 \mid{}
+		T_1 \times T_2 \mid{}
+		T_1 \plus T_2 \mid{}
+	}
+%	\stxrule{x,y,z}{variables}{\dots}
+%	\stxrule{l}{labels}{\dots}
+%	\stxrule{k}{constants}{sole}
+	\stxrule{e}{terms}{
+		x \mid{}
+		k \mid{}
+		\lambda^{S\rightarrow{}T}x.t \mid{}
+		e_1 \; e_2 \mid{}
+		\langle T \Leftarrow^l S \rangle t \mid{}
+		\mathtt{blame} \; l
+	}
+	\stxrulecont{
+		\mathtt{cons}\; e_1 \; e_2 \mid{}
+		\mathtt{car}\; e \mid{}
+		\mathtt{cdr}\; t
+	}
+	\stxrulecont{
+		\mathtt{inl} \; e \mid{}
+		\mathtt{inr} \; e \mid{}
+		\mathtt{case}\; e_1 \; e_2 \; e_3
+	}
+	\stxrule{o}{observations}{
+		k \mid{}
+		\mathtt{fun}\mid{}
+		\mathtt{cons}\mid{}
+		\mathtt{inl}\mid{}
+		\mathtt{inr}\mid{}
+		\mathtt{blame}\; l
+	}
+	\end{array}
+	\]
+
+	\fbox{$ S \sim T $}
+	\begin{gather*}
+	\inference{}{
+		\star \sim \star
+	} \quad
+	\inference{}{
+		\star \sim P
+	} \quad
+	\inference{}{
+		P \sim \star
+	} \\
+	\inference{}{
+		\iota \sim \iota
+	} \quad
+	\inference{
+		S_1 \sim S_2 &
+		T_1 \sim T_2
+	}{
+		S_1 \rightarrow T_1 \sim S_2 \rightarrow T_2
+	} \quad
+	\inference{
+		S_1 \sim S_2 &
+		T_1 \sim T_2
+	}{
+		S_1 \times T_1 \sim S_2 \times T_2
+	} \quad
+	\inference{
+		S_1 \sim S_2 &
+		T_1 \sim T_2
+	}{
+		S_1 \plus T_1 \sim S_2 \plus T_2
+	}
+	\end{gather*}
+
+	\fbox{$ S \smile T $}
+	\begin{gather*}
+	\inference{}{
+		\star \smile \star
+	} \quad
+	\inference{}{
+		\star \smile P
+	} \quad
+	\inference{}{
+		P \smile \star
+	} \\
+	\inference{}{
+		\iota \smile \iota
+	} \quad
+	\inference{}{
+		S_1 \rightarrow T_1 \smile S_2 \rightarrow T_2
+	}
+	\inference{}{
+	S_1 \times T_1 \smile S_2 \times T_2
+	}
+	\inference{}{
+	S_1 \plus T_1 \smile S_2 \plus T_2
+	}
+	\end{gather*}
+
+	\fbox{$ \Gamma \vdash e \vdash T $}
+	\begin{gather*}
+		\inference{
+			S \sim T & \Gamma \vdash e : S 
+		}{
+			\judgetype{\Gamma}{\langle T \Leftarrow^l S \rangle t}{T}
+		} \quad
+		\inference{
+		}{
+			\judgetype{\Gamma}{\mathtt{blame} l}{T}
+		}
+	\end{gather*}
+
+	\caption{Blame Calculus and its static semantics}
+	\label{fig:blame-static}
+\end{figure}
+
+\figref{fig:blame-static} defines the form of blame calculus and its static 
+semantics. It is little changed from previous definitions. 
+The dynamic semantics of Blame Calculi depend on blame strategies, so we defer 
+them to sub-sections.
+
+Blame Calculus is based on Simply Typed Lambda Calculus with sum types and 
+product types ($ \mathtt{STLC+} $). 
+Let $ S,T $ range over types. A type is either the dynamic type $ \star $
+(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
+or a pre-type. 
+Let $ P,Q $ range over pre-types. Every pre-type is a type with a 
+traditional type constructor at the top.
+
+$ S \sim T $ reads $ S $ and $ T $ are consistent. Two types are consistent if 
+one of them is $ \star $, or they have the same top-most type constructor and 
+the corresponding sub-parts are consistent. Consistency is reflexive and 
+symmetric, but not transitive.
+
+$ S \smile T $ reads $ S $ and $ T $ are shallowly-consistent. Two types are 
+shallowly-consistent if one of them is $ \star $, or they have the same 
+top-most type constructor. 
+Shallow-consistency is also reflexive, symmetric, and not transitive.
+
+Let $ e $ ranges over terms. Unlike $ \mathtt{STLC+} $, we annotate the 
+co-domain of lambda abstractions explicitly and add casts and blames.
 
@@
 \begin{theorem}[Hyper-coercion bi-simulates cast]	
-	$ e \Downarrow_B o $ if and only if $ e \Downarrow_H o $
+	$ t \Downarrow_B o $ if and only if $ t \Downarrow_H o $
 \end{theorem}

### 2019-10-03 paper.tex
static semantics of blame calculus

@@
 		x \mid{}
-		k \mid{}
+		\mathtt{tt} \mid{}
 		\lambda^{S\rightarrow{}T}x.t \mid{}
@@
 	\stxrule{o}{observations}{
-		k \mid{}
+		\mathtt{tt} \mid{}
 		\mathtt{fun}\mid{}
@@
 Let $ e $ ranges over terms. Unlike $ \mathtt{STLC+} $, we annotate the 
-co-domain of lambda abstractions explicitly and add casts and blames.
+co-domain of lambda abstractions explicitly. Besides, we add casts and blames.
+
+Let $ o $ ranges over observations.
+
+Now let's move to the dynamic semantics.
 
@@
 
-subtyping, reduction ...
+We describe the dynamic semantics of Blame Calculus with the CEK machine 
+(\citet{felleisen1986control}).
 

### 2019-10-03 paper.tex
cite GitHub issue on TBC vs COE
hyper coercion theorems

@@
 
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[]
+\newtheorem{proposition}{Proposition}[]
+\newtheorem{corollary}{Corollary}[]
 \newcommand{\figref}[1]{Fig.~\ref{#1}}
@@
 first time product types is considered. Their treatment to products in 
-coercions, however, is shown incorrect. **
-
-\todo[inline]{kc: ** I want to cite the GitHub issue page here.}
+coercions, however, is shown incorrect (\citet{Gradual-TypingType-based-casts}).
 
@@
 
-\subsection{$Lazy UD$ Hyper-coercion}
-
-\subsection{Hyper-coercion is Correct}
-
-\begin{theorem}[Hyper-coercion bi-simulates cast]	
-	$ t \Downarrow_B o $ if and only if $ t \Downarrow_H o $
+\begin{theorem}[$ Lazy D $ Hyper-coercion is a proper cast representation]
+	\  \\
+\begin{enumerate}
+	\item If $ v : T $, then $ id(T) \; v = \mathtt{succ} \; v $
+	\item If $ v : T_1 $,
+	$ c_1 $ is a hyper-coercion from $ T_1 $ to $ T_2 $, and 
+	$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
+	then $ seq(c_1,c_2) \; v = (c_1 \; v) >>= c_2 $
+	\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+	then $ cast(T_1, l, T_2) \; v = \mathtt{fail} \; l $
+	\item If $ v : \star $, 
+	then $ cast(\star,l,\star) \; v = \mathtt{succ} \; v $
+	\item If $ v : P $,
+	then $ cast(\star,l,Q) \; (inj \; P \; v) = cast(P,l,Q) \; v $
+	\item If $ v : P $,
+	then $ cast(P,l,\star) \; v = \mathtt{succ} \; (inj \; P \; v) $
+	\item If $ v : \iota $,
+	then $ cast(\iota,l,\iota) \; v = \mathtt{succ} \; v $
+	\item $ cast(S_1 \rightarrow T_1,l,S_2 \rightarrow T_2) \; (fun \; c_1 \; 
+	E \; b \; c_2) $ \\
+	$ = \mathtt{succ} \; fun \; seq(cast(S_2,l,S_1),c_1) \; E \; b 
+	\; seq(c_2,cast(T_1,l,T_2)) $ 
+	\item $ cast(S_1 \times T_1,l,S_2 \times T_2) \; (cons \; v_1 \; c_1 \; 
+	v_2 \; c_2) $ \\
+	$ = \mathtt{succ} \; (cons \; v_1 \; seq(c_1,cast(S_1,l,S_2)) \; v_2 \; 
+	seq(c_2,cast(T_1,l,T_2))) $ 
+	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inl \; v \; c) = 
+	\mathtt{succ} \; (inl \; v \; seq(c,cast(S_1,l,T_1)) ) $ 
+	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inr \; v \; c) = 
+	\mathtt{succ} \; (inr \; v \; seq(c,cast(S_2,l,T_2)) ) $ 
+\end{enumerate}
 \end{theorem}
 
-\subsection{Hyper-coercion is Space-efficient}
+\begin{proposition}[Every proper cast represenation is correct]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $
+	\[
+	e \Downarrow_{B}^{D} o \; \text{if and only if} \; 
+	e \Downarrow_{C}^{D} o
+ 	\]
+\end{proposition}
+
+\begin{corollary}[$ Lazy D $ hyper-coercion is correct]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $
+	\[
+	e \Downarrow^{D}_{B} o \; \text{if and only if} \; 
+	e \Downarrow^{D}_{H} o
+	\]
+\end{corollary}
+
+\subsection{$Lazy UD$ Hyper-coercion}
 

### 2019-10-04 paper.tex
intro

@@
 \newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
+\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
+\newcommand{\lazyD}{$\mathtt{Lazy D}$}
+\newcommand{\eager}{$\mathtt{Eager}$}
 
@@
 	propose hyper-coercion, which is easy to understand, as easy to implement 
-	as coercion, and easy to reason about.
+	as coercion, and easy to reason about formally.
 \end{abstract}
@@
 
-\todo[inline]{KC: I want to add more citations here}
+Around 2006, many work on integrating dynamic typing and static typing emerge, 
+notably gradual types \cite{siek2006gradual} and hybrid types 
+\cite{flanagan2006hybrid}. 
+Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
+language for gradual types and hybrid types. 
+Blame Calculus throws a blame label when a runtime type-check fails.
+Blame labels can include useful information on the failed cast, for example, 
+its location in the source code.
 
-\citet{wadler2009well} introduces blame calculus, an intermediate language for 
-gradually typed languages. Blame calculus includes blame labels, which tells 
-the position of the cast that fails at run time (blame tracking).
-
-Implementing gradually typed languages on top of blame calculus suffices sever 
-space leak. Translation to blame calculus might wrap a tail call with a 
-cast. Thus, at runtime, mutually tail-recursive functions can accumulate casts 
-at tail position.
+Implementing gradually typed languages naively on top of blame calculus 
+suffices sever space leak.
+Translation to Blame Calculus can wrap some expressions with a cast, including 
+those at tail position. Thus, at runtime, mutually tail-recursive functions in 
+source language can accumulate casts at tail position.
 
@@
 translating Blame Calculus to a variant of \citet{henglein1994dynamic}'s 
-Coercions Calculus. The key idea is to represent casts with coercions. 
-Coercions can be composed and normalized. Their solution, however, doesn't 
-include blame tracking.
+Coercion Calculus. Their key idea is to represent casts with coercions, 
+which can be composed and normalized. Every coercion looks like a list of 
+trees. For normalized coercion, the length of the list is bounded by a small 
+constant. And the depths of trees do not growth in composition and 
+normalization. These two facts implies that by representing casts with 
+coercions, we can restore the space-efficiency of tail-recursive programs. This 
+Coercion Calculus, however, doesn't include blame tracking.
 
@@
 $ \{Lazy, Eager\} \times \{D, UD\} $. 
-Lazy strategies blame fewer programs than eager ones,
-but also detect less potential type errors.
+Eager strategies detect more potential type errors, 
+but also blame more programs.
 $ D $ and $ UD $ assign blame labels differently.
-They prove that $ Lazy UD $ simulates the Blame Calculus in 
-\cite{wadler2009well}. But the counterparts of other strategies in Blame 
-Calculus is unknown.
+Blame strategy is essentially the semantics of casts.
+They prove that the \lazyUD{} Coercion Calculus simulates the Blame Calculus 
+in \cite{wadler2009well}. But we don't know whether the simulation also works 
+the other way, and what are the Blame counterparts of other Coercion Calculi.
 
 \citet{siek2010threesomes} proposes another approach to combine blame 
-tracking and space efficiency. Their solution is based on Threesome Calculus, 
-an novel alternative to Coercion Calculus. The key idea is to represent casts 
-with threesomes. Threesomes, like coercions, can be composed. There is no 
-separate normalization for threesome because every threesome is normalized. 
-They prove that their Threesome Calculus bisimulate 
-\citet{siek2009exploring}'s Coercion Calculus and
-\citet{wadler2009well}'s Blame Calculus.
+tracking and space efficiency. Their solution is based on Threesome Calculus. 
+Their key idea is to represent casts with threesomes, a novel cast 
+representation. Threesomes, like coercions, can be composed. There is no 
+separate normalization because every threesome is in normal form. 
+They prove that their Threesome Calculus bi-simulates
+the \lazyUD{} Coercion Calculus and the Blame Calculus.
 
-\citet{siek2012interpretations} introduces a $ lazy D $  Blame Calculus. They 
-conjecture that this calculus bi-simulate the $ lazy D $ Coercion Calculi.
+\citet{siek2012interpretations} introduces a \lazyD{} Blame Calculus. They 
+conjecture that it bi-simulates the \lazyD{} Coercion Calculus.
 
@@
 His claim is later affirmed by the group of people who develop threesome 
-\citet{siek2015blame}. 
+(\citet{siek2015blame}).
 The connection 
@@
 Calculi are established by the fact that the former are derived from the latter.
-The connection between these calculi and Blame Calculus, however, 
+The connection between eager calculi and Blame Calculus, however, 
 is still unclear.
@@
 \citet{siek2015blame} revisit the coercion-based approach. They simplify the 
-Coercion Calculi by only working with coercions in canonical forms.
-Fortunately, coercions are canonical when initially constructed, and 
-their empowered compose function produces canonical coercions as well. Again 
-(\citet{siek2010threesomes}), they delegate all strategies other than 
-$ Lazy UD $.
+\lazyUD{} Coercion Calculus by only working with normalized coercions.
+Fortunately, coercions are trivially normalized when initially constructed, and 
+their empowered compose function produces normalized coercions as well. Again 
+\cite{siek2010threesomes}, they delegate all other blame strategies.
 
@@
 and blame-tracking compiler for a gradually typed language of the same name. 
-This implementation is based on the $ Lazy D $ Coercion Calculus.
-Their result suggests that implementing coercion is practical. And this is the 
-first time product types is considered. Their treatment to products in 
-coercions, however, is shown incorrect (\citet{Gradual-TypingType-based-casts}).
+This implementation is based on the \lazyD{} Coercion Calculus.
+Their result suggests that implementing coercion is practical. They implement 
+tuples, which is the first time gradual product types is considered. Their 
+treatment on tuples, however, is shown incorrect 
+\cite{Gradual-TypingType-based-casts}.
 
-Recently, \citet{new2019gradual} show that $ Eager $ strategies are 
+Recently, \citet{new2019gradual} show that \eager{} strategies are 
 incompatible with $\eta$-equivalence of functions, which suggest that these 
-strategies are not very ideal. Their research kills questions about $ Eager $ 
-strategies, but some questions about $ Lazy $ strategies remain open:
+strategies are not very ideal.
 
-\begin{itemize}
-	\item Is the $ Lazy D $ coercion an ideal cast representation?
-	\item Does the $ Lazy D $ Coercion Calculus bi-simulate the Blame Calculus?
-\end{itemize}
-
-The $ Lazy D $ coercion is claimed easy to understand 
-(\cite{garcia2013calculating}, \cite{siek2015blame}) and is shown 
-easy enough to implement in a compiler (\cite{kuhlenschmidt2018efficient}).
-It is still undesirable, however, in a 
-few aspects. Firstly, its compose function is not structurally recursive. Many 
-developers of Grift report that it is tricky to convince their 
-proof assistants that composition terminates. Secondly, canonical coercion
-obscures the nature of a ``normalized cast'' because its definition lies on 
-top of coercion.
+So far, it seems that the coercion-based approach is the best way to combine 
+space-efficiency and blame-tracking: coercion is claimed easy to 
+understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
+easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
+Coercion is not satisfactory, however, in at least two aspects.
+Firstly, its compose function is not structurally recursive, which makes 
+it difficult to study coercion formally.
+Many developers of Grift report that it is tricky to convince their 
+proof assistants that composition terminates. 
+Secondly, it is desirable to understand the nature of ``normalized cast'', but 
+the coercion-based approach capture this concept indirectly because normalized 
+coercion is defined taking a subset of coercion.
 
 Perhaps unsurprisingly, threesome has a straightforward recursive 
-implementation. And its definition is self-standing. Together with the research 
-by \citet{garcia2013calculating}, they suggest that there can be a cast 
+implementation. And its definition is self-standing. Together with 
+\citet{garcia2013calculating}'s work, they suggest that there can be a cast 
 representation whose definition is self-standing, and whose composition is 
@@
 
-We present yet another cast representation, hyper-coercion. Its 
-composition is structurally recursive. And its definition is self-standing. 
-Besides, there is a clear connection between it and the canonical coercion, 
-so we are optimistic that implementing hyper-coercion should be as easy (or 
-as hard) as coercion.
+Now we present one such cast representation: hyper-coercion. As we will show in 
+Section \ref{sec:hyper-coercion}, there is a clear connection between it and 
+the normalized coercion, so we are optimistic that understanding and 
+implementing hyper-coercion should be as easy (or as hard).
 
@@
 
-We prove formally that $ Lazy D $ (resp. $ Lazy UD $) hyper-coercion calculi 
-bi-simulate the $ Lazy D $ (resp. $ Lazy UD $) Blame Calculi. This is possibly 
-the first bi-simulation proof for the $ Lazy D $ Blame Calculus.
+We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
+bi-simulate the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is possibly 
+the first bi-simulation proof for the \lazyD{} Blame Calculus.
 
-The structure of this paper is as follows. Section \ref{sec:blame-calculus} 
-reviews the state-of-art of $Lazy$ Coercion Calculi. In section 
-\ref{sec:hyper-coercion} we present Hyper-coercion. Section \ref{sec:conclude} 
-concludes.
+The structure of this paper is as follows. 
+Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
+Calculi. 
+In section \ref{sec:hyper-coercion} we present Hyper-coercion.
+Section \ref{sec:conclude} concludes.
 
@@
 
-$ S \sim T $ reads $ S $ and $ T $ are consistent. Two types are consistent if 
-one of them is $ \star $, or they have the same top-most type constructor and 
-the corresponding sub-parts are consistent. Consistency is reflexive and 
-symmetric, but not transitive.
+$ S \sim T $ reads ``$ S $ and $ T $ are consistent''.
+Two types are consistent if one of them is $ \star $, or they have the same 
+top-most type constructor and the corresponding sub-parts are consistent. 
+The intuition of $ S \sim T $ is that $ S $ and $ T $ have no conflict type 
+information. Consistency is reflexive and symmetric, but not transitive.
 
-$ S \smile T $ reads $ S $ and $ T $ are shallowly-consistent. Two types are 
-shallowly-consistent if one of them is $ \star $, or they have the same 
-top-most type constructor. 
-Shallow-consistency is also reflexive, symmetric, and not transitive.
+One might be tempted to conclude that inconsistency is the root of all runtime 
+type errors. In the setting of gradual typing, however, runtime type-checking 
+is usually gradual as well. 
+$ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
+are shallowly consistent if one of them is $ \star $, or they have the same 
+top-most type constructor. Shallow-inconsistency is the root of all runtime 
+type error -- Casting a value to a shallowly inconsistent type would 
+lead to an runtime type error immediately. Shallow-consistency is also 
+reflexive, symmetric, and not transitive.
 
@@
 
-The syntax of $ Lazy D $ Hyper-coercion is shown in \figref{fig:HC-D}.
+The syntax of \lazyD{} Hyper-coercion is shown in \figref{fig:HC-D}.
 
-\begin{theorem}[$ Lazy D $ Hyper-coercion is a proper cast representation]
+\begin{theorem}[\lazyD{} Hyper-coercion is a proper cast representation]
 	\  \\
@@
 
-\begin{corollary}[$ Lazy D $ hyper-coercion is correct]
+\begin{corollary}[\lazyD{} hyper-coercion is correct]
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $

### 2019-10-04 paper.tex
blame calculus

@@
 		T_1 \times T_2 \mid{}
-		T_1 \plus T_2 \mid{}
+		T_1 \plus T_2
 	}
@@
 		\lambda^{S\rightarrow{}T}x.t \mid{}
-		e_1 \; e_2 \mid{}
-		\langle T \Leftarrow^l S \rangle t \mid{}
-		\mathtt{blame} \; l
+		e_1 \; e_2
 	}
@@
 		\mathtt{case}\; e_1 \; e_2 \; e_3
+	}
+	\stxrulecont{
+		\langle T \Leftarrow^l S \rangle t \mid{}
+		\mathtt{blame} \; l
 	}
@@
 
-\figref{fig:blame-static} defines the form of blame calculus and its static 
+\figref{fig:blame-static} defines the syntax of blame calculus and its static 
 semantics. It is little changed from previous definitions. 
@@
 or a pre-type. 
-Let $ P,Q $ range over pre-types. Every pre-type is a type with a 
-traditional type constructor at the top.
+Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
+constructor at the top. For simplicity, we only have one base type $ \iota $, 
+the unit type. Other pre-types are functions, products, and sums.
 
@@
 One might be tempted to conclude that inconsistency is the root of all runtime 
-type errors. In the setting of gradual typing, however, runtime type-checking 
-is usually gradual as well. 
+type errors (blames). In the setting of gradual typing, however, runtime 
+type-checking is usually gradual as well. 
 $ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
 are shallowly consistent if one of them is $ \star $, or they have the same 
-top-most type constructor. Shallow-inconsistency is the root of all runtime 
-type error -- Casting a value to a shallowly inconsistent type would 
-lead to an runtime type error immediately. Shallow-consistency is also 
-reflexive, symmetric, and not transitive.
+top-most type constructor. Shallow-inconsistency is the root of all blames -- 
+casting a value to a shallowly inconsistent type leads to a blame immediately. 
+Shallow-consistency is also reflexive, symmetric, and not transitive.
 
-Let $ e $ ranges over terms. Unlike $ \mathtt{STLC+} $, we annotate the 
-co-domain of lambda abstractions explicitly. Besides, we add casts and blames.
+Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $, 
+casts, and blames. Unlike $ \mathtt{STLC+} $, we annotate the 
+co-domain of lambda abstractions explicitly. 
+The end of the figure shows the extra typing rules.
 
-Let $ o $ ranges over observations.
+Let $ o $ ranges over observations. They are what would be observed if a 
+program terminates. Observations include all constructors and blames.
 
@@
 
-We describe the dynamic semantics of Blame Calculus with the CEK machine 
-(\citet{felleisen1986control}).
+We describe the dynamic semantics of \lazyD{} Blame Calculus with the CEK 
+machine (\citet{felleisen1986control}).
 

### 2019-10-04 paper.tex
update ;

@@
 suffices sever space leak.
-Translation to Blame Calculus can wrap some expressions with a cast, including 
-those at tail position. Thus, at runtime, mutually tail-recursive functions in 
-source language can accumulate casts at tail position.
+For example, translation to Blame Calculus can wrap some expressions with a 
+cast, including those at tail position. Thus, at runtime, mutually 
+tail-recursive functions in source language can accumulate casts at tail 
+position. There are more examples in \citet{herman2010space}.
 
@@
 the coercion-based approach capture this concept indirectly because normalized 
-coercion is defined taking a subset of coercion.
+coercion is defined ny taking a subset of coercion.
 
-Perhaps unsurprisingly, threesome has a straightforward recursive 
-implementation. And its definition is self-standing. Together with 
-\citet{garcia2013calculating}'s work, they suggest that there can be a cast 
-representation whose definition is self-standing, and whose composition is 
-structurally recursive. Super-coercion introduced in 
-\citet{garcia2013calculating} could 
-be a promising candidate. However, its definition is a bit complicated. It uses 
-10 constructors to deal with an elementary type system with only base types and 
-function types. And four constructors are directly related to 
-function types. Thus, super-coercion might not scale very well to more 
-sophisticated type systems.
+Perhaps unsurprisingly, threesome has a structurally recursive compose. And its 
+definition is self-standing. Together with \citet{garcia2013calculating}'s 
+work, they suggest that there can be a cast representation whose definition is 
+self-standing, and whose composition is structurally recursive. 
+Super-coercion introduced in \citet{garcia2013calculating} could be a promising 
+candidate. However, its definition is a bit complicated. It uses 10 
+constructors to deal with an elementary type system with only base types and 
+function types. And four constructors are directly related to function types. 
+Thus, super-coercion might not scale very well to more sophisticated type 
+systems.
 
@@
 		}{
-			\judgetype{\Gamma}{\mathtt{blame} l}{T}
+			\judgetype{\Gamma}{\mathtt{blame} \; l}{T}
 		}
@@
 We describe the dynamic semantics of \lazyD{} Blame Calculus with the CEK 
-machine (\citet{felleisen1986control}).
+machine (\citet{felleisen1986control}). We choose CEK machine because to 
+achieve space efficiency, we need to change continuations. 
+Thus, abstract machines that include continuation in states is quite convenient 
+for us. And CEK is one of the simplest machine of this kind.
 
@@
 	}
-	\stxrule{b}{bodies}{
+	\stxrule{m}{middles}{
 		U \mid{}
@@
 	\comprule{c_1 \times c_2}{(c_3 \times c_4,t)}{
-		(c_3 \fatsemi^{l} c_1 \times c_2 \fatsemi^l c_4, t)
+		(c_1 \fatsemi^{l} c_3 \times c_2 \fatsemi^l c_4, t)
 	}{}
 	\comprule{c_1 \plus c_2}{(c_3 \plus c_4,t)}{
-		(c_3 \fatsemi^{l} c_1 \plus c_2 \fatsemi^l c_4, t)
+		(c_1 \fatsemi^{l} c_3 \plus c_2 \fatsemi^l c_4, t)
 	}{}
-	\comprule{b_1}{(b_2,t_2)}{
+	\comprule{b_1}{(b_2,t)}{
 		(b_1,\bot^l)
-	}{}
+	}{b_1 }
 	\end{array}

### 2019-10-08 paper.tex

@@
 \newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
-\newcommand{\comprule}[4]{#1 & \fatsemi^l & #2 & = & #3 & #4 \\}
+\newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
 \newcommand{\plus}[0]{+}
@@
 \newcommand{\eager}{$\mathtt{Eager}$}
+\newcommand{\hyperCoercionI}[0]{id\star}
+\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
 
@@
 
-\section{Blame Calculus} \label{sec:blame-calculus}
+\section{Background: Blame Calculus} \label{sec:blame-calculus}
 
@@
 are shallowly consistent if one of them is $ \star $, or they have the same 
-top-most type constructor. Shallow-inconsistency is the root of all blames -- 
-casting a value to a shallowly inconsistent type leads to a blame immediately. 
-Shallow-consistency is also reflexive, symmetric, and not transitive.
+top-most type constructor. Shallow-inconsistency is the root of all blames in 
+all lazy strategies -- casting a value to a shallowly inconsistent type leads 
+to a blame immediately. Shallow-consistency is also reflexive, symmetric, and 
+not transitive.
 
@@
 
-We describe the dynamic semantics of \lazyD{} Blame Calculus with the CEK 
-machine (\citet{felleisen1986control}). We choose CEK machine because to 
-achieve space efficiency, we need to change continuations. 
-Thus, abstract machines that include continuation in states is quite convenient 
-for us. And CEK is one of the simplest machine of this kind.
+All existing proofs describe the semantics of \lazyD{} Blame Calculus in the 
+style of reduction semantics. 
+We instead do it with the CEK machine (\citet{felleisen1986control}). 
+We choose CEK machine because to achieve space efficiency, we need to change 
+continuations. Thus, abstract machines that include continuation in states is 
+quite convenient for us. And CEK is one of the simplest machine of this kind.
 
@@
 
-\section{Coercion Calculus}
+\section{Background: Coercion Calculus}
 
@@
 	\stxrule{c}{hyper-coercions}{
-		id* \mid{}
-		( h , ( b , t ) )
+		\hyperCoercionI \mid{}
+		\hyperCoercionC{h}{m}{t}
 	}
@@
 	}
+	\stxrule{\ell}{$ \mathtt{Maybe} \; l $}{
+		\epsilon \mid{}
+		l
+	}
 	\end{array}
@@
 
-	\fbox{$ c \fatsemi^l c = c $}
+	\fbox{$ c \fatsemi^\ell c = c $}
 	\[ 
 	\begin{array}{rclclr}
-	\comprule{id*}{id*}{
-		id*
+
+	\comprule{
+		\hyperCoercionI
+	}{
+		\hyperCoercionI
+	}{
+		\hyperCoercionI
 	}{}
-	\comprule{id*}{( ?^{l'} , ( b , t ) )}{
-		( ?^{l'} , ( b , t ) )
+
+	\comprule{
+		\hyperCoercionI
+	}{
+		\hyperCoercionC{?^{l'}}{b}{t}
+	}{
+		\hyperCoercionC{?^{l'}}{b}{t}
 	}{}
-	\comprule{id*}{( ! , ( b , t ) )}{
-		(?^{l} , ( b , t))
+
+	\comprule{
+		\hyperCoercionI
+	}{
+		\hyperCoercionC{!}{b}{t}
+	}{
+		\hyperCoercionC{?^{l}}{b}{t}
+	}{\ell = l}
+
+	\comprule{
+		\hyperCoercionC{h}{b}{\bot^{l'}}
+	}{
+		c
+	}{
+		\hyperCoercionC{h}{b}{\bot^{l'}}
 	}{}
-	\comprule{(h , (b ,\bot^{l'}))}{c}{
-		(h , (b ,\bot^{l'}))
-	}{}
-	\comprule{(h , (b_1 , t_1))}{id*}{
-		(h , (b_1 , !))
-	}{t_1 \neq \bot^{l'}}
-	\comprule{(h , (b_1 , t_1))}{(\epsilon , (b_2 , t_2))}{
-		(h , b_1 \fatsemi^{l} (b_2 , t_2))
-	}{t_1 \neq \bot^{l'}}
-	\comprule{(h , (b_1 , t_1))}{(?^{l'} , (b_2 , t_2))}{
-		(h , b_1 \fatsemi^{l'} (b_2 , t_2))
-	}{t_1 \neq \bot^{l'}}
+
+	\comprule{
+		\hyperCoercionC{h}{b_1}{t_1}
+	}{
+		\hyperCoercionI
+	}{
+		\hyperCoercionC{h}{b_1}{!}
+	}{
+		t_1 \neq \bot^{\centerdot}
+	}
+
+	\comprule{
+		\hyperCoercionC{h}{b_1}{t_1}
+	}{
+		\hyperCoercionC{\epsilon}{b_2}{t_2}
+	}{
+		\hyperCoercionC{h}{b'}{t'}
+	}{
+		t_1 \neq \bot^{\centerdot} \; \text{and} \;
+		b_1 \fatsemi^{\ell} (b_2, t) = (b', t')
+	}
+
+	\comprule{
+		\hyperCoercionC{h}{b_1}{t_1}
+	}{
+		\hyperCoercionC{?^{l'}}{b_2}{t_2}
+	}{
+		\hyperCoercionC{h}{b'}{t'}
+	}{
+		t_1 \neq \bot^{\centerdot} \; \text{and} \;
+		b_1 \fatsemi^{l'} (b_2, t) = (b', t')
+	}
 	\end{array}
@@
 
-	\fbox{$ b \fatsemi^l (b,t) = (b,t) $}
+	\fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
 	\[ 
@@
 	\comprule{c_1 \rightarrow c_2}{(c_3 \rightarrow c_4,t)}{
-		(c_3 \fatsemi^{l} c_1 \rightarrow c_2 \fatsemi^l c_4, t)
+		(c_3 \fatsemi^{l} c_1 \rightarrow c_2 \fatsemi^\ell c_4, t)
 	}{}
 	\comprule{c_1 \times c_2}{(c_3 \times c_4,t)}{
-		(c_1 \fatsemi^{l} c_3 \times c_2 \fatsemi^l c_4, t)
+		(c_1 \fatsemi^{l} c_3 \times c_2 \fatsemi^\ell c_4, t)
 	}{}
 	\comprule{c_1 \plus c_2}{(c_3 \plus c_4,t)}{
-		(c_1 \fatsemi^{l} c_3 \plus c_2 \fatsemi^l c_4, t)
+		(c_1 \fatsemi^{l} c_3 \plus c_2 \fatsemi^\ell c_4, t)
 	}{}
@@
 		(b_1,\bot^l)
-	}{b_1 }
+	}{
+		\ell = l \; \text{and} \;
+		\neg b_1 \smile b_2 
+	}
 	\end{array}
@@
 	\funrule{seq(c_1,c_2)}{
-		c_1 \fatsemi^l c_2
-	}{}
+		c_1 \fatsemi^\epsilon c_2
+	}{cod(c_1) = dom(c_2)}
 	\end{array}
@@
 
-	\fbox{$ id( T ) = c $}
-	\[
-	\begin{array}{rclr}
-	\funrule{id(*)}{
-		id*
-	}{}
-	\funrule{id(P)}{
-		(\epsilon,(id(P),\epsilon))
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$ id( P ) = b $}
+	\fbox{$ id( P ) = m $}
 	\[
@@
 		id(T_1) \plus id(T_2)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ id( T ) = c $}
+	\[
+	\begin{array}{rclr}
+	\funrule{id(\star)}{
+		\hyperCoercionI
+	}{}
+	\funrule{id(P)}{
+		\hyperCoercionC{\epsilon}{id(P)}{\epsilon}
 	}{}

### 2019-10-08 paper.tex
LazyD Blame Calculus CEK

@@
 \newcommand{\stxrulecont}[1]{& | & #1 & \\}
-\newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
+\newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
+\newcommand{\redrule}[3]{#1 & \longrightarrow_B & #2 & #3\\}
 \newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
@@
 \newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
+\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
+\newcommand{\sOOreturn}[2]{\mathtt{Apply} \; #2 \; #1}
+\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
+\newcommand{\TOOdyn}[0]{\star}
+\newcommand{\TOOpre}[1]{#1}
+\newcommand{\POOunit}[0]{\iota}
+\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
+\newcommand{\POOprod}[2]{#1 \times #2}
+\newcommand{\POOsum}[2]{#1 \plus #2}
+\newcommand{\eOOvar}[1]{#1}
+\newcommand{\eOOsole}[0]{\mathtt{tt}}
+\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
+\newcommand{\eOOapp}[2]{#1 \; #2}
+\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
+\newcommand{\eOOcar}[1]{\mathtt{car} \; #1}
+\newcommand{\eOOcdr}[1]{\mathtt{cdr} \; #1}
+\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
+\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
+\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
+\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
+\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
+\newcommand{\oOOinj}{\mathtt{dyn}}
+\newcommand{\oOOsole}{\mathtt{tt}}
+\newcommand{\oOOfun}{\mathtt{fun}}
+\newcommand{\oOOcons}{\mathtt{cons}}
+\newcommand{\oOOinl}{\mathtt{inl}}
+\newcommand{\oOOinr}{\mathtt{inr}}
+\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
+\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
+\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
+\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
+\newcommand{\vOOtt}[0]{\mathtt{tt}}
+\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
+\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
+\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
+\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
+\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
 
@@
 Blame Calculus throws a blame label when a runtime type-check fails.
-Blame labels can include useful information on the failed cast, for example, 
+These labels can include useful information on the failed cast, for example, 
 its location in the source code.
@@
 trees. For normalized coercion, the length of the list is bounded by a small 
-constant. And the depths of trees do not growth in composition and 
+constant. And the depths of trees do not grow in composition and 
 normalization. These two facts implies that by representing casts with 
-coercions, we can restore the space-efficiency of tail-recursive programs. This 
-Coercion Calculus, however, doesn't include blame tracking.
+coercions, we can restore the space-efficiency. This 
+Coercion Calculus, however, does not support blame tracking.
 
@@
 They prove that the \lazyUD{} Coercion Calculus simulates the Blame Calculus 
-in \cite{wadler2009well}. But we don't know whether the simulation also works 
-the other way, and what are the Blame counterparts of other Coercion Calculi.
+in \cite{wadler2009well}. But it is unknown whether the simulation also works 
+the other way, and what the Blame counterparts of other Coercion Calculi are.
 
@@
 They prove that their Threesome Calculus bi-simulates
-the \lazyUD{} Coercion Calculus and the Blame Calculus.
+the \lazyUD{} Coercion Calculus and the Blame Calculus, and that threesomes are 
+space-efficient.
 
-\citet{siek2012interpretations} introduces a \lazyD{} Blame Calculus. They 
-conjecture that it bi-simulates the \lazyD{} Coercion Calculus.
+\citet{siek2012interpretations} present a \lazyD{} Blame Calculus and revised 
+lazy Coercion Calculi. They simplify the Coercion Calculi by only working with 
+normal coercions (i.e. coercions in normal form). 
+Fortunately, coercions are trivially normal when initially constructed, and 
+their empowered compose function is conjectured to produces normal coercions as 
+well. Also, they conjecture that their Coercion Calculi bi-simulate the 
+corresponding Blame Calculi.
 
@@
 Calculi are established by the fact that the former are derived from the latter.
-The connection between eager calculi and Blame Calculus, however, 
-is still unclear.
 
-\citet{siek2015blame} revisit the coercion-based approach. They simplify the 
-\lazyUD{} Coercion Calculus by only working with normalized coercions.
-Fortunately, coercions are trivially normalized when initially constructed, and 
-their empowered compose function produces normalized coercions as well. Again 
-\cite{siek2010threesomes}, they delegate all other blame strategies.
+\citet{siek2015blame} revisit the coercion-based approach. They revise the 
+\lazyUD{} Coercion Calculus by \citet{siek2012interpretations}, prove its 
+space-efficiency and that it bi-simulate the \lazyUD{} Blame Calculus.
 
@@
 and blame-tracking compiler for a gradually typed language of the same name. 
-This implementation is based on the \lazyD{} Coercion Calculus.
-Their result suggests that implementing coercion is practical. They implement 
-tuples, which is the first time gradual product types is considered. Their 
-treatment on tuples, however, is shown incorrect 
-\cite{Gradual-TypingType-based-casts}.
+This implementation is based on the \lazyD{} Coercion Calculus by 
+\citet{siek2012interpretations}.
+Their result suggests that implementing coercion is practical. 
+%They implement 
+%tuples, which is the first time gradual product types is considered. Their 
+%treatment on tuples, however, is shown incorrect 
+%\cite{Gradual-TypingType-based-casts}.
 
@@
 easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
-Coercion is not satisfactory, however, in at least two aspects.
+Coercion is not satisfactory, however, in at least three aspects.
 Firstly, its compose function is not structurally recursive, which makes 
 it difficult to study coercion formally.
-Many developers of Grift report that it is tricky to convince their 
-proof assistants that composition terminates. 
+For instance, many developers of Grift report that it is tricky to convince 
+their proof assistants that composition terminates. 
 Secondly, it is desirable to understand the nature of ``normalized cast'', but 
 the coercion-based approach capture this concept indirectly because normalized 
-coercion is defined ny taking a subset of coercion.
+coercion is defined by taking a subset of coercion.
+Last by not least, the memory representation of normal coercions is not very 
+compact.
 
@@
 Our hyper-coercion considers sum types and product types, which are not 
-accounted in all proofs above. Adding each of them requires us to add only one 
+considered in all proofs above. Adding each of them requires us to add only one 
 new constructor to a component of hyper-coercion. This suggests that 
@@
 We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
-bi-simulate the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is possibly 
+bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is possibly 
 the first bi-simulation proof for the \lazyD{} Blame Calculus.
@@
 \begin{figure}
+	Syntax
 	\[
-	\begin{array}{lclr}
-	\stxrule{S,T}{types}{
+	\begin{array}{rclr}
+	\stxrule{T}{types}{
 		\star \mid{}
@@
 	}
-	\stxrule{P,Q}{pre-types}{
-		\iota \mid{}
-		T_1 \rightarrow T_2 \mid{}
-		T_1 \times T_2 \mid{}
-		T_1 \plus T_2
+	\stxrule{P}{pre-types}{
+		\POOunit \mid
+		\POOfun{T_1}{T_2} \mid
+		\POOprod{T_1}{T_2} \mid
+		\POOsum{T_1}{T_2}
 	}
-%	\stxrule{x,y,z}{variables}{\dots}
-%	\stxrule{l}{labels}{\dots}
-%	\stxrule{k}{constants}{sole}
 	\stxrule{e}{terms}{
-		x \mid{}
-		\mathtt{tt} \mid{}
-		\lambda^{S\rightarrow{}T}x.t \mid{}
-		e_1 \; e_2
+		\eOOvar{x} \mid{}
+		\eOOsole{} \mid{}
+		\eOOlam{T_1}{T_2}{x}{e} \mid
+		\eOOapp{e_1}{e_2}
 	}
 	\stxrulecont{
-		\mathtt{cons}\; e_1 \; e_2 \mid{}
-		\mathtt{car}\; e \mid{}
-		\mathtt{cdr}\; t
+		\eOOcons{e_1}{e_2} \mid
+		\eOOcar{e} \mid
+		\eOOcdr{e}
 	}
 	\stxrulecont{
-		\mathtt{inl} \; e \mid{}
-		\mathtt{inr} \; e \mid{}
-		\mathtt{case}\; e_1 \; e_2 \; e_3
+		\eOOinl{e} \mid
+		\eOOinr{e} \mid
+		\eOOcase{e_1}{e_2}{e_3}
 	}
 	\stxrulecont{
-		\langle T \Leftarrow^l S \rangle t \mid{}
-		\mathtt{blame} \; l
+		\eOOcast{e}{T_1}{l}{T_2} \mid
+		\eOOblame{l}
 	}
 	\stxrule{o}{observations}{
-		\mathtt{tt} \mid{}
-		\mathtt{fun}\mid{}
-		\mathtt{cons}\mid{}
-		\mathtt{inl}\mid{}
-		\mathtt{inr}\mid{}
-		\mathtt{blame}\; l
+		\oOOinj \mid
+		\oOOsole \mid
+		\oOOfun \mid
+		\oOOcons \mid
+		\oOOinl \mid
+		\oOOinr \mid
+		\oOOblame{l}
 	}
@@
 
-	\fbox{$ S \sim T $}
+	Consistency
+	\fbox{$ T_1 \sim T_2 $}
 	\begin{gather*}
@@
 
-	\fbox{$ S \smile T $}
+	Shallow-consistency
+	\fbox{$ T_1 \smile T_2 $}
 	\begin{gather*}
@@
 	\inference{}{
-		S_1 \rightarrow T_1 \smile S_2 \rightarrow T_2
-	}
+		T_{11} \rightarrow T_{12} \smile T_{21} \rightarrow T_{22}
+	} \quad
 	\inference{}{
-	S_1 \times T_1 \smile S_2 \times T_2
-	}
+		T_{11} \times T_{12} \smile T_{21} \times T_{22}
+	} \quad
 	\inference{}{
-	S_1 \plus T_1 \smile S_2 \plus T_2
+	T_{11} \plus T_1 \smile S_2 \plus T_2
 	}
@@
 
+	Term typing
 	\fbox{$ \Gamma \vdash e \vdash T $}
@@
 		}{
-			\judgetype{\Gamma}{\langle T \Leftarrow^l S \rangle t}{T}
+			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
 		} \quad
@@
 		}{
-			\judgetype{\Gamma}{\mathtt{blame} \; l}{T}
+			\judgetype{\Gamma}{\eOOblame{l}}{T}
 		}
@@
 
-$ S \sim T $ reads ``$ S $ and $ T $ are consistent''.
-Two types are consistent if one of them is $ \star $, or they have the same 
-top-most type constructor and the corresponding sub-parts are consistent. 
-The intuition of $ S \sim T $ is that $ S $ and $ T $ have no conflict type 
-information. Consistency is reflexive and symmetric, but not transitive.
+%$ S \sim T $ reads ``$ S $ and $ T $ are consistent''.
+%Two types are consistent if one of them is $ \star $, or they have the same 
+%top-most type constructor and the corresponding sub-parts are consistent. 
+%The intuition of $ S \sim T $ is that $ S $ and $ T $ have no conflict type 
+%information. Consistency is reflexive and symmetric, but not transitive.
 
-One might be tempted to conclude that inconsistency is the root of all runtime 
-type errors (blames). In the setting of gradual typing, however, runtime 
-type-checking is usually gradual as well. 
+%One might be tempted to conclude that inconsistency is the root of all runtime 
+%type errors (blames). In the setting of gradual typing, however, runtime 
+%type-checking is usually gradual as well. 
 $ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
@@
 
-All existing proofs describe the semantics of \lazyD{} Blame Calculus in the 
-style of reduction semantics. 
-We instead do it with the CEK machine (\citet{felleisen1986control}). 
+\begin{figure}
+	Syntax
+	\[
+	\begin{array}{rclr}
+
+	\stxrule{v}{values}{
+		\vOOfun{\rho}{x}{b} \mid
+		\vOOtt{} \mid
+		\vOOcons{v_1}{v_2} \mid
+		\vOOinl{v} \mid
+		\vOOinr{v} \mid		
+		\vOOcast{v}{c}
+	}
+	\stxrule{c}{casts}{
+		\cOOcast{T_1}{l}{T_2}
+	}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+
+	\stxrule{\kappa}{continuations}{
+		\mathtt{mt} \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{car} \; \kappa \mid{}
+		\mathtt{cdr} \; \kappa \mid
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
+	}
+	\stxrulecont{	
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
+		\langle c \rangle \kappa
+	}
+	\end{array}
+	\]
+
+	Value typing \fbox{$ v : T $}
+	\begin{gather*}
+	\dots \quad
+	\inference{
+		v : P &
+		c : P \Longrightarrow T &
+		P \smile T
+	}{
+		\vOOcast{v}{\cOOcast{P}{l}{T}} : T
+	}
+	\end{gather*}
+
+	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
+	\begin{gather*}
+	\dots \quad
+	\inference{
+		c : T_1 \Longrightarrow T_2 &
+		\kappa : T_2 \Longrightarrow T_3
+	}{
+		\langle c \rangle \kappa : T_1 \Longrightarrow T_3
+	}
+	\end{gather*}
+
+	Reduction \fbox{$ s_1 \longrightarrow_B s_2 $}
+	\[
+	\begin{array}{rclr}
+
+	& \vdots \\
+	\redrule{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
+	}{}
+	\redrule{
+		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
+				\cOOcast{\POOfun{T_{11}}{T_{12}}}{l}{\POOfun{T_{21}}{T_{22}}}
+			} \; \kappa)}
+	}{
+		\sOOreturn{v_1}{
+		\langle\cOOcast{T_{21}}{l}{T_{11}}\rangle
+		(\mathtt{app_2} \; v_2 \; 
+		\langle\cOOcast{T_{12}}{l}{T_{22}}\rangle \kappa)}
+	}{}
+
+%	\redrule{
+%		\sOOreturn{v}{(
+%			\mathtt{app_2} \;
+%			(\vOOfun{\rho}{x}{e}) \;
+%			\kappa
+%		)}
+%	}{\sOOinspect{e}{\rho{}[x := v]}{\kappa}}{}
+
+	\redrule{
+		\sOOreturn{
+			\vOOcast{v}{\cOOcast{\POOprod{T_{11}}{T_{12}}}{l}{
+					\POOprod{T_{21}}{T_{22}}}}
+			}{(\mathtt{car} \; \kappa)}
+	}{
+		\sOOreturn{v}{(
+			\mathtt{car} \;
+			\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa
+			)}
+	}{}
+
+	\redrule{
+		\sOOreturn{
+			\vOOcast{v}{\cOOcast{\POOprod{T_{11}}{T_{12}}}{l}{
+					\POOprod{T_{21}}{T_{22}}}}
+		}{(\mathtt{cdr} \; \kappa)}
+	}{
+		\sOOreturn{v}{(
+			\mathtt{cdr} \;
+			\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa
+			)}
+	}{}
+
+	\redrule{
+		\sOOreturn{v_3}{(
+			\mathtt{case_3} \;
+			v_1 \; v_2 \;
+			\kappa
+		)}
+	}{case(v_1,
+	\mathtt{app_2} \; v_2 \; \kappa,
+	\mathtt{app_2} \; v_3 \; \kappa
+	)}{}
+
+	\redrule{
+		\sOOreturn{v}{(
+			\mathtt{cast} \; c \; \kappa
+		)}
+	}{
+		\sOOreturn{u}{\kappa}
+		\\ &
+	}{
+		\text{where} \; applyCast(c,v) = \rOOsucc{u}
+	}
+
+	\redrule{
+		\sOOreturn{v}{(
+			\mathtt{cast} \; c \; \kappa
+			)}
+	}{
+		\sOOhalt{(\oOOblame{l})}
+		\\ &
+	}{
+		\text{where} \; applyCast(c,v) = \rOOfail{l}
+	}
+	\end{array}
+	\]
+
+	Case
+	\[
+	\begin{array}{rclr}
+	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
+		\sOOreturn{v}{\kappa_1}
+	}{}
+	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
+		\sOOreturn{v}{\kappa_2}
+	}{}
+	\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
+		case(v,
+		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
+		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
+	}{}
+	\end{array}
+	\]
+
+	Apply cast
+	\[
+	\begin{array}{rclr}
+	\funrule{
+		applyCast(\cOOcast{\star}{l}{\star},v)
+	}{
+		\rOOsucc{v}
+	}{}
+	\funrule{
+		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
+	}{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{}
+	\funrule{
+		applyCast(\cOOcast{P}{l}{\star},v)
+	}{
+		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
+	}{}
+	\funrule{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{
+		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
+	}{P_1 \smile P_2}
+	\funrule{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{
+		\rOOfail{l}
+	}{\neg P_1 \smile P_2}
+
+	\end{array}
+	\]
+
+	\caption{Dynamic semantics of the \lazyD{} Blame Calculus}
+	\label{ld-blame-cek}
+\end{figure}
+
+Fig.~\ref{ld-blame-cek} defines the dynamic semantcis of the \lazyD{} Blame 
+Calculus in the style of CEK machines (\citet{felleisen1986control}). 
 We choose CEK machine because to achieve space efficiency, we need to change 
@@
 quite convenient for us. And CEK is one of the simplest machine of this kind.
+
+Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
+
+Let $ v $ ranges over values. A value is either a function, the 
+element of unit, a pair, a left injection, a right injection, or a casted value.
+The cast around a casted value is not arbitrary, as shown by value typing: the 
+source type must be a pre-type, and the source and the target must be 
+shallow-consistent.
+
+Let $ r $ ranges over cast results. A cast result is either a success, which 
+brings a value, or a failure, which brings a blame label.
+
+Let $ s $ ranges over machine states. A state is either looking at an 
+expression to decide what to do next, returning a value to a continuation, or 
+halting with an observation.
+
+Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
+continuation. The following continuations correspond to expressions. For 
+example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
+we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
+the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
+returning to $ \kappa $.
+
+In the reduction rules, to evaluate a cast expression, the machine move the 
+cast to the continuation and evaluate the inner expression. To apply a casted 
+function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
+operand to $ v_2 $, the un-casted function, and finally cast the result of the 
+function application. To take out the first (resp. second) part of a casted 
+pair, the machine firstly take out the first (resp. second) part of $ v $, the 
+un-casted pair, and cast the result. To case-split a sum, the machine looks 
+deep inside the value to find out whether it is a left injection or a right 
+one. Along the way, the machine accumulate the pending casts onto the 
+continuations. To cast a value, the machine try to apply the cast to the value. 
+If the cast succeeds, the machine returns the result to the next continuation. 
+If the cast fails, the machine halts with the blame label.
 
@@
 	\comprule{c_1 \rightarrow c_2}{(c_3 \rightarrow c_4,t)}{
-		(c_3 \fatsemi^{l} c_1 \rightarrow c_2 \fatsemi^\ell c_4, t)
+		(c_3 \fatsemi^{\ell} c_1 \rightarrow c_2 \fatsemi^\ell c_4, t)
 	}{}
 	\comprule{c_1 \times c_2}{(c_3 \times c_4,t)}{
-		(c_1 \fatsemi^{l} c_3 \times c_2 \fatsemi^\ell c_4, t)
+		(c_1 \fatsemi^{\ell} c_3 \times c_2 \fatsemi^\ell c_4, t)
 	}{}
 	\comprule{c_1 \plus c_2}{(c_3 \plus c_4,t)}{
-		(c_1 \fatsemi^{l} c_3 \plus c_2 \fatsemi^\ell c_4, t)
+		(c_1 \fatsemi^{\ell} c_3 \plus c_2 \fatsemi^\ell c_4, t)
 	}{}
@@
 	\begin{array}{rclr}
-	\funrule{id(U)}{U}{}
-	\funrule{id(T_1 \rightarrow T_2)}{
-		id(T_1) \rightarrow id(T_2)
+	\funrule{id(\POOunit)}{\POOunit}{}
+	\funrule{id(\POOfun{T_1}{T_2})}{
+		\POOfun{id(T_1)}{id(T_2)}
 	}{}
-	\funrule{id(T_1 \times T_2)}{
-		id(T_1) \times id(T_2)
+	\funrule{id(\POOprod{T_1}{T_2})}{
+		\POOprod{id(T_1)}{id(T_2)}
 	}{}
-	\funrule{id(T_1 \plus T_2)}{
-		id(T_1) \plus id(T_2)
+	\funrule{id(\POOsum{T_1}{T_2})}{
+		\POOsum{id(T_1)}{id(T_2)}
 	}{}

### 2019-10-09 paper.tex
hyper-coercion version of applyCast

@@
 \newcommand{\eager}{$\mathtt{Eager}$}
-\newcommand{\hyperCoercionI}[0]{id\star}
+\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
 \newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
@@
 \newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
+\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
+\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #1 \; #2}
+\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
+\newcommand{\hcvOOtt}[0]{\mathtt{tt}}
+\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
+\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
+\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
 
@@
 
-subtyping, reduction ...
+\dots
 
@@
 	\stxrule{m}{middles}{
-		U \mid{}
-		c_1 \rightarrow c_2 \mid{}
-		c_1 \times c_2 \mid{}
-		c_1 \plus c_2
+		\POOunit \mid
+		\POOfun{c_1}{c_2} \mid
+		\POOprod{c_1}{c_2} \mid
+		\POOsum{c_1}{c_2}
 	}
@@
 
+	Coercion typing \fbox{$ c : T \Longrightarrow T $}
+	\begin{gather*}
+	\inference{}{\typingHC{\hyperCoercionI}{\TOOdyn}{\TOOdyn}}
+	\quad
+	\inference{
+		\typingHC{h}{T_1}{P_1} &
+		\typingHC{m}{P_1}{P_2} &
+		\typingHC{t}{P_2}{T_2}
+	}{
+		\typingHC{\hyperCoercionC{h}{m}{t}}{T_1}{T_2}
+	}
+	\end{gather*}
+
+	Head typing \fbox{$ \typingHC{h}{T}{P} $}
+	\begin{gather*}
+	\inference{}{\typingHC{\epsilon}{P}{P}}
+	\quad
+	\inference{}{\typingHC{?^l}{\TOOdyn}{P}}
+	\end{gather*}
+
+	Middle typing \fbox{$ \typingHC{m}{P}{P} $}
+	\begin{gather*}
+	\inference{}{\typingHC{\POOunit}{\POOunit}{\POOunit}}
+	\\
+	\inference{
+		\typingHC{c_1}{T_3}{T_1} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOfun{c_1}{c_2}}{\POOfun{T_1}{T_2}}{\POOfun{T_3}{T_4}}
+	}
+	\\
+	\inference{
+		\typingHC{c_1}{T_1}{T_3} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
+	}
+	\\
+	\inference{
+		\typingHC{c_1}{T_1}{T_3} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOsum{c_1}{c_2}}{\POOsum{T_1}{T_2}}{\POOsum{T_3}{T_4}}
+	}
+	\end{gather*}
+
+	Tail typing \fbox{$ \typingHC{t}{P}{T} $}
+	\begin{gather*}
+	\inference{}{\typingHC{\epsilon}{P}{P}} \quad
+	\inference{}{\typingHC{!}{P}{\TOOdyn}} \quad
+	\inference{}{\typingHC{\bot^l}{P}{T}} \quad
+	\end{gather*}
+
+	\caption{Syntax of hyper-coercion}
+	\label{fig:hyper-coercion}
+\end{figure}
+
+\figref{fig:hyper-coercion} defines the syntax of hyper-coercions. All 
+definitions and results in this section are new.
+
+Terms, types, pre-types, blame labels, and observations are as before. Let $ c 
+$ ranges over hyper-coercions. A hyper-coercion is either an identity 
+cast between the dynamic types, or a complex including a head, a middle, and a 
+tail. Let $ h $ ranges over heads. A head is either a no-op, or a projection 
+decorated with a label, to which blame is allocated if the projection fails. 
+Let $ m $ ranges over middles. There is a one-to-one 
+correspondence between middles and type constructors. Let $ t $ ranges over 
+tails. A tail is either a no-op, an injection, or a failure. Let $ \ell $ 
+ranges over no-op and labels. It is useful when we introduce composition of 
+hyper-coercions. Typing rules for hyper-coercions, heads, middles, and tails 
+are straightforward.
+
+\subsection{\lazyD{} Hyper-coercion}
+
+\begin{figure}
 	\fbox{$ c \fatsemi^\ell c = c $}
@@
 		c_1 \fatsemi^\epsilon c_2
-	}{cod(c_1) = dom(c_2)}
+	}{
+		c_1 : T_1 \Longrightarrow T_2
+		\; \text{and} \;
+		c_2 : T_2 \Longrightarrow T_3
+	}
 	\end{array}
@@
 	\]
-
 	\caption{$Lazy D$ Hyper-coercion}
@@
 
-\subsection{$Lazy D$ Hyper-coercion}
-
-The syntax of \lazyD{} Hyper-coercion is shown in \figref{fig:HC-D}.
+Functions that construct \lazyD{} Hyper-coercion are shown in \figref{fig:HC-D}.
+When a language implementation want to construct a coercion, it should use 
+these functions: $ cast(T_1,l,T_2) $, $ id(T) $, and $ seq(c_1,c_2) $. $ 
+cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
+target type. $ id(T) $ constructs an identity cast of $ T $. $ seq(c_1,c_2) $ 
+composes two coercions where the target type of $ c_1 $ is equal to the source 
+type of $ T_2 $.
+
+\begin{figure}
+	\fbox{$ applyCast(c,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
+	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
+		applyTail(t',applyMiddle(m',v))
+	}{id(P)\fatsemi^l(m,t) = (m',t')}
+	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
+		applyTail(t,applyMiddle(m,v))}
+	{}
+	\end{array}
+	\]
+
+	\fbox{$ applyMiddle(m,v) = v $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyMiddle(\POOunit,\hcvOOtt)}{\hcvOOtt}{}
+	\funrule{applyMiddle(\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
+		\hcvOOfun{seq(c_3,c_1)}{\rho}{x}{e}{seq(c_2,c_4)}
+	}{}
+	\funrule{applyMiddle(\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
+		\hcvOOcons{v_1}{seq(c_1,c_3)}{v_2}{seq(c_2,c_4)}
+	}{}
+	\funrule{applyMiddle(\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
+		\hcvOOinl{v}{seq(c_1,c_3)}
+	}{}
+	\funrule{applyMiddle(\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
+		\hcvOOinr{v}{seq(c_2,c_4)}
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ applyTail(t,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
+	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
+	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
+	\end{array}
+	\]
+	\caption{Applying hyper-coercions to values}
+\end{figure}
+
+\begin{theorem}[$ id $ constructs neutrals] For all $ c : T_1 \Longrightarrow 
+T_2 $
+	\begin{enumerate}
+		\item $ seq(id(T_1),c) = c $
+		\item $ seq(c,id(T_2)) = c $
+	\end{enumerate}
+\end{theorem}
 

### 2019-10-10 paper.tex
standardize type notations and side conditions

@@
 \newtheorem{corollary}{Corollary}[]
+\newtheorem{definition}{Definition}
+
+\newcommand{\GTLC}{\texttt{GTLC+}}
 \newcommand{\figref}[1]{Fig.~\ref{#1}}
@@
 \newcommand{\TOOpre}[1]{#1}
-\newcommand{\POOunit}[0]{\iota}
+\newcommand{\POOunit}[0]{\mathtt{Unit}}
 \newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
@@
 \newcommand{\eOOvar}[1]{#1}
-\newcommand{\eOOsole}[0]{\mathtt{tt}}
+\newcommand{\eOOsole}[0]{\mathtt{unit}}
 \newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
@@
 \newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
-\newcommand{\eOOcar}[1]{\mathtt{car} \; #1}
-\newcommand{\eOOcdr}[1]{\mathtt{cdr} \; #1}
+\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
+\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
 \newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
@@
 \newcommand{\oOOinj}{\mathtt{dyn}}
-\newcommand{\oOOsole}{\mathtt{tt}}
+\newcommand{\oOOsole}{\mathtt{unit}}
 \newcommand{\oOOfun}{\mathtt{fun}}
@@
 \newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
-\newcommand{\vOOtt}[0]{\mathtt{tt}}
+\newcommand{\vOOtt}[0]{\mathtt{unit}}
 \newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
@@
 \newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
-\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #1 \; #2}
+\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
 \newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
-\newcommand{\hcvOOtt}[0]{\mathtt{tt}}
+\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
 \newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
@@
 \newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
+\newcommand{\hckOOmt}[0]{\mathtt{mt}}
+\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
+\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
+\newcommand{\sidecond}[1]{\text{if}\;#1}
 
@@
 	Term typing
-	\fbox{$ \Gamma \vdash e \vdash T $}
+	\fbox{$ \judgetype{\Gamma}{e}{T} $}
 	\begin{gather*}
@@
 all lazy strategies -- casting a value to a shallowly inconsistent type leads 
-to a blame immediately. Shallow-consistency is also reflexive, symmetric, and 
+to a blame immediately. Shallow-consistency is reflexive, symmetric, but 
 not transitive.
 
-Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $, 
-casts, and blames. Unlike $ \mathtt{STLC+} $, we annotate the 
+Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
+in addition, casts and blames. Unlike $ \mathtt{STLC+} $, we annotate the 
 co-domain of lambda abstractions explicitly. 
-The end of the figure shows the extra typing rules.
+The end of the figure shows the typing rules for the additional terms.
 
@@
 
-	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
-	\begin{gather*}
-	\dots \quad
-	\inference{
-		c : T_1 \Longrightarrow T_2 &
-		\kappa : T_2 \Longrightarrow T_3
-	}{
-		\langle c \rangle \kappa : T_1 \Longrightarrow T_3
-	}
-	\end{gather*}
-
-	Reduction \fbox{$ s_1 \longrightarrow_B s_2 $}
+%	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
+%	\begin{gather*}
+%	\dots \quad
+%	\inference{
+%		c : T_1 \Longrightarrow T_2 &
+%		\kappa : T_2 \Longrightarrow T_3
+%	}{
+%		\langle c \rangle \kappa : T_1 \Longrightarrow T_3
+%	}
+%	\end{gather*}
+
+	Reduction \fbox{$ s_1 \longrightarrow_{D,B} s_2 $}
 	\[
@@
 
-	& \vdots \\
+	& \dots \\
 	\redrule{
@@
 		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
-	}{P_1 \smile P_2}
+	}{\sidecond{P_1 \smile P_2}}
 	\funrule{
@@
 		\rOOfail{l}
-	}{\neg P_1 \smile P_2}
-
-	\end{array}
+	}{\sidecond{\neg P_1 \smile P_2}}
+
+	\end{array}
+	\]
+
+	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s $}\\
+
+	Evaluation \fbox{$ e \Downarrow_{D,B} o $}
+	\[
+	\inference{
+		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{B}^{*} 
+		\sOOhalt{o}
+	}{
+		e \Downarrow_{D,B} o
+	}
 	\]
@@
 	\caption{Dynamic semantics of the \lazyD{} Blame Calculus}
-	\label{ld-blame-cek}
+	\label{machine-cekc}
 \end{figure}
 
-Fig.~\ref{ld-blame-cek} defines the dynamic semantcis of the \lazyD{} Blame 
+Fig.~\ref{machine-cekc} defines the dynamic semantcis of the \lazyD{} Blame 
 Calculus in the style of CEK machines (\citet{felleisen1986control}). 
@@
 Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
-
 Let $ v $ ranges over values. A value is either a function, the 
@@
 shallow-consistent.
-
 Let $ r $ ranges over cast results. A cast result is either a success, which 
 brings a value, or a failure, which brings a blame label.
-
 Let $ s $ ranges over machine states. A state is either looking at an 
@@
 halting with an observation.
-
 Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
-continuation. The following continuations correspond to expressions. For 
+continuation. The remaining continuations correspond to expressions. For 
 example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
@@
 
+Transitive closure of reduction and evaluation are standard.
+
 \subsection{$Lazy UD$ Blame Calculus}
@@
 
-	Coercion typing \fbox{$ c : T \Longrightarrow T $}
-	\begin{gather*}
-	\inference{}{\typingHC{\hyperCoercionI}{\TOOdyn}{\TOOdyn}}
-	\quad
-	\inference{
-		\typingHC{h}{T_1}{P_1} &
-		\typingHC{m}{P_1}{P_2} &
-		\typingHC{t}{P_2}{T_2}
-	}{
-		\typingHC{\hyperCoercionC{h}{m}{t}}{T_1}{T_2}
-	}
-	\end{gather*}
-
-	Head typing \fbox{$ \typingHC{h}{T}{P} $}
-	\begin{gather*}
-	\inference{}{\typingHC{\epsilon}{P}{P}}
-	\quad
-	\inference{}{\typingHC{?^l}{\TOOdyn}{P}}
-	\end{gather*}
-
-	Middle typing \fbox{$ \typingHC{m}{P}{P} $}
-	\begin{gather*}
-	\inference{}{\typingHC{\POOunit}{\POOunit}{\POOunit}}
-	\\
-	\inference{
-		\typingHC{c_1}{T_3}{T_1} &
-		\typingHC{c_2}{T_2}{T_4}
-	}{
-		\typingHC{\POOfun{c_1}{c_2}}{\POOfun{T_1}{T_2}}{\POOfun{T_3}{T_4}}
-	}
-	\\
-	\inference{
-		\typingHC{c_1}{T_1}{T_3} &
-		\typingHC{c_2}{T_2}{T_4}
-	}{
-		\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
-	}
-	\\
-	\inference{
-		\typingHC{c_1}{T_1}{T_3} &
-		\typingHC{c_2}{T_2}{T_4}
-	}{
-		\typingHC{\POOsum{c_1}{c_2}}{\POOsum{T_1}{T_2}}{\POOsum{T_3}{T_4}}
-	}
-	\end{gather*}
-
-	Tail typing \fbox{$ \typingHC{t}{P}{T} $}
-	\begin{gather*}
-	\inference{}{\typingHC{\epsilon}{P}{P}} \quad
-	\inference{}{\typingHC{!}{P}{\TOOdyn}} \quad
-	\inference{}{\typingHC{\bot^l}{P}{T}} \quad
-	\end{gather*}
+	Shallow-consistency between middles
+	\fbox{$ m \smile m $}
+
+%	Coercion typing \fbox{$ c : T \Longrightarrow T $}
+%	\begin{gather*}
+%	\inference{}{\typingHC{\hyperCoercionI}{\TOOdyn}{\TOOdyn}}
+%	\quad
+%	\inference{
+%		\typingHC{h}{T_1}{P_1} &
+%		\typingHC{m}{P_1}{P_2} &
+%		\typingHC{t}{P_2}{T_2}
+%	}{
+%		\typingHC{\hyperCoercionC{h}{m}{t}}{T_1}{T_2}
+%	}
+%	\end{gather*}
+%	
+%	Head typing \fbox{$ \typingHC{h}{T}{P} $}
+%	\begin{gather*}
+%	\inference{}{\typingHC{\epsilon}{P}{P}}
+%	\quad
+%	\inference{}{\typingHC{?^l}{\TOOdyn}{P}}
+%	\end{gather*}
+%	
+%	Middle typing \fbox{$ \typingHC{m}{P}{P} $}
+%	\begin{gather*}
+%	\inference{}{\typingHC{\POOunit}{\POOunit}{\POOunit}}
+%	\\
+%	\inference{
+%		\typingHC{c_1}{T_3}{T_1} &
+%		\typingHC{c_2}{T_2}{T_4}
+%	}{
+%		\typingHC{\POOfun{c_1}{c_2}}{\POOfun{T_1}{T_2}}{\POOfun{T_3}{T_4}}
+%	}
+%	\\
+%	\inference{
+%		\typingHC{c_1}{T_1}{T_3} &
+%		\typingHC{c_2}{T_2}{T_4}
+%	}{
+%		\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
+%	}
+%	\\
+%	\inference{
+%		\typingHC{c_1}{T_1}{T_3} &
+%		\typingHC{c_2}{T_2}{T_4}
+%	}{
+%		\typingHC{\POOsum{c_1}{c_2}}{\POOsum{T_1}{T_2}}{\POOsum{T_3}{T_4}}
+%	}
+%	\end{gather*}
+%	
+%	Tail typing \fbox{$ \typingHC{t}{P}{T} $}
+%	\begin{gather*}
+%	\inference{}{\typingHC{\epsilon}{P}{P}} \quad
+%	\inference{}{\typingHC{!}{P}{\TOOdyn}} \quad
+%	\inference{}{\typingHC{\bot^l}{P}{T}} \quad
+%	\end{gather*}
 
@@
 
-\figref{fig:hyper-coercion} defines the syntax of hyper-coercions. All 
-definitions and results in this section are new.
-
-Terms, types, pre-types, blame labels, and observations are as before. Let $ c 
-$ ranges over hyper-coercions. A hyper-coercion is either an identity 
-cast between the dynamic types, or a complex including a head, a middle, and a 
-tail. Let $ h $ ranges over heads. A head is either a no-op, or a projection 
+All definitions and results in this section are new.
+\figref{fig:hyper-coercion} defines the syntax of hyper-coercions.
+Terms, types, pre-types, blame labels, and observations are as before.
+
+Let $ c $ ranges over hyper-coercions. We re-use the meta-variable $ c $ to 
+stress that hyper-coercion is a cast representation. A hyper-coercion is either 
+an identity cast between the dynamic types, or a complex including a head, a 
+middle, and a tail. 
+Let $ h $ ranges over heads. A head is either a no-op, or a projection 
 decorated with a label, to which blame is allocated if the projection fails. 
 Let $ m $ ranges over middles. There is a one-to-one 
-correspondence between middles and type constructors. Let $ t $ ranges over 
-tails. A tail is either a no-op, an injection, or a failure. Let $ \ell $ 
-ranges over no-op and labels. It is useful when we introduce composition of 
-hyper-coercions. Typing rules for hyper-coercions, heads, middles, and tails 
-are straightforward.
+correspondence between middles and type constructors. 
+We generalize shallow-consistency to include middles in the natural way.
+Let $ t $ ranges over tails. A tail is either a no-op, an injection, or a 
+failure. 
+Let $ \ell $ ranges over no-op and labels. It is useful when we introduce 
+composition of hyper-coercions.
 
@@
 	}{
-		\hyperCoercionC{!}{b}{t}
+		\hyperCoercionC{\epsilon}{b}{t}
 	}{
 		\hyperCoercionC{?^{l}}{b}{t}
-	}{\ell = l}
+	}{\sidecond{\ell = l}}
 
@@
 	}{
-		t_1 \neq \bot^{\centerdot}
+		\sidecond{\forall l. t_1 \neq \bot^{l}}
 	}
@@
 	}{
+		\sidecond{
 			t_1 \neq \bot^{\centerdot} \; \text{and} \;
@@
 		}
+	}
 
@@
 	}{
+		\sidecond{
 		t_1 \neq \bot^{\centerdot} \; \text{and} \;
@@
 		}
+	}
 	\end{array}
@@
 	\begin{array}{rclclr}
-	\comprule{U}{(U,t)}{
-		(U,t)
-	}{}
-	\comprule{c_1 \rightarrow c_2}{(c_3 \rightarrow c_4,t)}{
-		(c_3 \fatsemi^{\ell} c_1 \rightarrow c_2 \fatsemi^\ell c_4, t)
-	}{}
-	\comprule{c_1 \times c_2}{(c_3 \times c_4,t)}{
-		(c_1 \fatsemi^{\ell} c_3 \times c_2 \fatsemi^\ell c_4, t)
-	}{}
-	\comprule{c_1 \plus c_2}{(c_3 \plus c_4,t)}{
-		(c_1 \fatsemi^{\ell} c_3 \plus c_2 \fatsemi^\ell c_4, t)
-	}{}
-	\comprule{b_1}{(b_2,t)}{
-		(b_1,\bot^l)
-	}{
+	\comprule{\POOunit}{(\POOunit,t)}{
+		(\POOunit,t)
+	}{}
+	\comprule{\POOfun{c_1}{c_2}}{(\POOfun{c_3}{c_4},t)}{
+		(\POOfun{c_3 \fatsemi^{\ell} c_1}{c_2 \fatsemi^\ell c_4},t)
+	}{}
+	\comprule{\POOprod{c_1}{c_2}}{(\POOprod{c_3}{c_4},t)}{
+		(\POOprod{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
+	}{}
+	\comprule{\POOsum{c_1}{c_2}}{(\POOsum{c_3}{c_4},t)}{
+		(\POOsum{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
+	}{}
+	\comprule{m_1}{(m_2,t)}{
+		(m_1,\bot^l)
+	}{
+		\sidecond{
 		\ell = l \; \text{and} \;
-		\neg b_1 \smile b_2 
+		\neg m_1 \smile m_2 
+		}
 	}
@@
 		c_1 \fatsemi^\epsilon c_2
-	}{
-		c_1 : T_1 \Longrightarrow T_2
-		\; \text{and} \;
-		c_2 : T_2 \Longrightarrow T_3
-	}
+	}{}
 	\end{array}
@@
 		\POOsum{id(T_1)}{id(T_2)}
-	}{}
+	}{}s
 	\end{array}
@@
 
-Functions that construct \lazyD{} Hyper-coercion are shown in \figref{fig:HC-D}.
-When a language implementation want to construct a coercion, it should use 
-these functions: $ cast(T_1,l,T_2) $, $ id(T) $, and $ seq(c_1,c_2) $. $ 
-cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
-target type. $ id(T) $ constructs an identity cast of $ T $. $ seq(c_1,c_2) $ 
-composes two coercions where the target type of $ c_1 $ is equal to the source 
-type of $ T_2 $.
-
-\begin{figure}
-	\fbox{$ applyCast(c,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
-	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
-		applyTail(t',applyMiddle(m',v))
-	}{id(P)\fatsemi^l(m,t) = (m',t')}
-	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
-		applyTail(t,applyMiddle(m,v))}
-	{}
-	\end{array}
-	\]
-
-	\fbox{$ applyMiddle(m,v) = v $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyMiddle(\POOunit,\hcvOOtt)}{\hcvOOtt}{}
-	\funrule{applyMiddle(\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
-		\hcvOOfun{seq(c_3,c_1)}{\rho}{x}{e}{seq(c_2,c_4)}
-	}{}
-	\funrule{applyMiddle(\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
-		\hcvOOcons{v_1}{seq(c_1,c_3)}{v_2}{seq(c_2,c_4)}
-	}{}
-	\funrule{applyMiddle(\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
-		\hcvOOinl{v}{seq(c_1,c_3)}
-	}{}
-	\funrule{applyMiddle(\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
-		\hcvOOinr{v}{seq(c_2,c_4)}
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$ applyTail(t,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
-	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
-	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
-	\end{array}
-	\]
-	\caption{Applying hyper-coercions to values}
-\end{figure}
+Functions that construct \lazyD{} hyper-coercions are shown in 
+\figref{fig:HC-D}.
+
+$ c_1 \fatsemi^\ell c_2 = c' $ composes two hyper-coercions. The target of $ 
+c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
+be a label.
+
+$ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 
+pair of a middle and a tail. Similarly, the target of $ m_1 $ and the source of 
+$ m_2 $ might be different, in which case $ \ell $ must be a label.
+
+$ seq(c_1,c_2) $ composes two coercions where the target type of $ c_1 $ is 
+equal to the source type of $ T_2 $.
+
+$ id(T) $ constructs an identity coercion of $ T $.
+
+$ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
+target type.
 
@@
 
+\subsubsection{an abstract machine that composes casts} 
+To show that hyper-coercion is a correct cast representation, we introduce an 
+hyper-coercion-based machine for the \lazyD\ blame calculus, and show that it 
+bi-simulates the previous machine. 
+\figref{machine-cekcc} defines the new machine.
+
+\begin{figure}
+	Syntax
+	\[
+	\begin{array}{rclr}
+
+	\stxrule{v}{values}{
+		\hcvOOtt \mid
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
+		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+	}
+	\stxrulecont{
+		\hcvOOinl{v}{c} \mid
+		\hcvOOinr{v}{c} \mid
+		\hcvOOinj{P}{v}
+	}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+	\stxrule{\kappa}{continuation}{
+		(c,k)
+	}
+	\stxrule{k}{pre-continuations}{
+		\mathtt{mt} \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{car} \; \kappa \mid{}
+		\mathtt{cdr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
+	}
+	\end{array}
+	\]
+
+	Build continuation \fbox{$ cont(k) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{cont(k)}{(id(T_1),k)}{\\&&\text{where} \; k : T_1 \Longrightarrow 
+	T_2}
+	\end{array}
+	\]
+
+	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
+	\end{array}
+	\]
+
+	Reduction \fbox{$ s_1 \longrightarrow_{D,P(C)} s_2 $}
+	\[
+	\begin{array}{rclr}
+	& \vdots \\
+	\redrule{
+		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
+	}{
+		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
+	}{}
+	\redrule{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+	}{}
+	\redrule{
+		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+	}{}
+	\redrule{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
+	}
+	\redrule{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOhalt{(\oOOblame{l})}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
+	}
+	\end{array}
+	\]
+
+	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,P(C)}^{*} s $}
+	\[\dots\]
+
+	Evaluation \fbox{$ e \Downarrow_{D,P(C)} o $}
+	\[
+	\inference{
+		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{P(C)}^{*} 
+		\sOOhalt{o}
+	}{
+		e \Downarrow_{D,P(C)} o
+	}
+	\]
+
+	\caption{An abstract machine that composes casts.}
+	\label{machine-cekcc}
+\end{figure}
+
+Let $ v $ ranges over value. We push casts into values. For instance, function 
+values now include two more components: a cast for argument and a cast for the 
+output. The last kind of values is injection to $ \TOOdyn $. 
+Cast results ($ r $) and machine states ($ s $) are as before. 
+Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
+pre-continuations. 
+A continuation is now a pair whose first part is a cast, and whose second part 
+is a pre-continuation. 
+Pre-continuation are like the continuations before.
+
+We list a fraction of reduction rules due to space limitation.
+When values are constructed, their hyper-coercion parts are filled with outputs 
+of $ id $. For instance, when a function value is constructed, its first part 
+and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
+When evaluating a cast expression, the current continuation is extended with a 
+hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
+with the hyper-coercion on the top of the continuation.
+When evaluating a compound expression, the machine firstly construct the new 
+pre-continuation, then turn it to a continuation by adding an identity 
+hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
+expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
+the new pre-continuation, then call $ cont $ which adds an identity cast to 
+construct a continuation. 
+When a function call happens, the machine firstly cast the operand. If the 
+casting succeeds, the machine then evaluate the body in the extended 
+environment and the extended continuation. If the casting fails, the machine 
+then halts with the blame label.
+
+Transitive closure of reduction and evaluation are standard.
+
+The machine depends on four functions that consumes and/or construct 
+hyper-coercions: $ id(T) $, $ seq(c,c) $, $ cast(T,l,T) $, and $ applyCast(T,v) 
+$. The first three are described above. We will show $ applyCast $ shortly.
+
+Some reader might have noticed that the machine is representation-independent 
+w.r.t cast. That being said, if some people want to use normal coercion instead 
+of hyper-coercion, they can implement the normal coercion version of the four 
+functions mentioned aboved and get another abstract machine. We capture the 
+idea of ``abstract cast'' by the following definition.
+
+\begin{definition}[Cast Representation]
+	A cast representation has four interface functions:
+	\begin{description}
+		\item[$ id(T) $] constructs an identity cast
+		\item[$ seq(c_1,c_2) $] composes two casts
+		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$ applyCast(c,v) $] applies a cast onto a value
+	\end{description}
+\end{definition}
+
+One of our major contributions is for all cast presentation, if it is proper, 
+then it is correct.
+
+\begin{definition}[Proper Cast Representation]
+	A cast representation is proper if
+	\begin{enumerate}
+		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ v : T_1 $,
+		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
+		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
+		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
+		v.applyCast(c_2,v) $
+		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		\item If $ v : \star $, 
+		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		\item If $ v : P $,
+		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
+		= applyCast(cast(P,l,Q),v) $
+		\item If $ v : P $,
+		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item If $ v : \iota $,
+		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		\item $ 
+		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		= 
+		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+
+		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
+		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		$ = 
+		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
+		 $ 
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
+	\end{enumerate}
+\end{definition}
+
+\begin{proposition}[proper cast represenations are correct]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a proper cast 
+	representation
+	\[
+	e \Downarrow_{D,B} o \; \text{if and only if} \; 
+	e \Downarrow_{D,P(C)} o
+	\]
+\end{proposition}
+
+Perhaps unsurprisingly, hyper-coercion is correct.
+
 \begin{theorem}[\lazyD{} Hyper-coercion is a proper cast representation]
-	\  \\
-\begin{enumerate}
-	\item If $ v : T $, then $ id(T) \; v = \mathtt{succ} \; v $
-	\item If $ v : T_1 $,
-	$ c_1 $ is a hyper-coercion from $ T_1 $ to $ T_2 $, and 
-	$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
-	then $ seq(c_1,c_2) \; v = (c_1 \; v) >>= c_2 $
-	\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-	then $ cast(T_1, l, T_2) \; v = \mathtt{fail} \; l $
-	\item If $ v : \star $, 
-	then $ cast(\star,l,\star) \; v = \mathtt{succ} \; v $
-	\item If $ v : P $,
-	then $ cast(\star,l,Q) \; (inj \; P \; v) = cast(P,l,Q) \; v $
-	\item If $ v : P $,
-	then $ cast(P,l,\star) \; v = \mathtt{succ} \; (inj \; P \; v) $
-	\item If $ v : \iota $,
-	then $ cast(\iota,l,\iota) \; v = \mathtt{succ} \; v $
-	\item $ cast(S_1 \rightarrow T_1,l,S_2 \rightarrow T_2) \; (fun \; c_1 \; 
-	E \; b \; c_2) $ \\
-	$ = \mathtt{succ} \; fun \; seq(cast(S_2,l,S_1),c_1) \; E \; b 
-	\; seq(c_2,cast(T_1,l,T_2)) $ 
-	\item $ cast(S_1 \times T_1,l,S_2 \times T_2) \; (cons \; v_1 \; c_1 \; 
-	v_2 \; c_2) $ \\
-	$ = \mathtt{succ} \; (cons \; v_1 \; seq(c_1,cast(S_1,l,S_2)) \; v_2 \; 
-	seq(c_2,cast(T_1,l,T_2))) $ 
-	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inl \; v \; c) = 
-	\mathtt{succ} \; (inl \; v \; seq(c,cast(S_1,l,T_1)) ) $ 
-	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inr \; v \; c) = 
-	\mathtt{succ} \; (inr \; v \; seq(c,cast(S_2,l,T_2)) ) $ 
-\end{enumerate}
+	See appendix.
 \end{theorem}
-
-\begin{proposition}[Every proper cast represenation is correct]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $
-	\[
-	e \Downarrow_{B}^{D} o \; \text{if and only if} \; 
-	e \Downarrow_{C}^{D} o
- 	\]
-\end{proposition}
 
@@
 	\[
-	e \Downarrow^{D}_{B} o \; \text{if and only if} \; 
-	e \Downarrow^{D}_{H} o
+	e \Downarrow_{D,B} o \; \text{if and only if} \; 
+	e \Downarrow_{D,P(H)} o
 	\]
 \end{corollary}
+
+\figref{hc-applyCast} defines $ applyCast $. Applying the identity cast for the 
+dynamic type succeeds immediately. When applying a compound cast, we firstly 
+apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
+that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
+is the failure.
+$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
+
+\begin{figure}
+	\fbox{$ applyCast(c,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
+	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
+		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
+		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ applyMiddle(\ell,m,v) = v $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
+	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
+		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
+		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
+		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
+		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,m,v)}{
+		\rOOfail{l}
+	}{
+		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
+	}
+	\end{array}
+	\]
+
+	\fbox{$ applyTail(t,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
+	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
+	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
+	\end{array}
+	\]
+	\caption{Applying hyper-coercions to values}
+	\label{hc-applyCast}
+\end{figure}
 

### 2019-10-10 paper.tex
standardize state names

@@
 \newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
-\newcommand{\sOOreturn}[2]{\mathtt{Apply} \; #2 \; #1}
+\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
 \newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
@@
 \newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
-\newcommand{\hckOOmt}[0]{\mathtt{mt}}
+\newcommand{\hckOOmt}[0]{\mathtt{stop}}
 \newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
@@
 	\stxrule{\kappa}{continuations}{
-		\mathtt{mt} \mid{}
+		\mathtt{stop} \mid{}
 		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
@@
 		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
-				\cOOcast{\POOfun{T_{11}}{T_{12}}}{l}{\POOfun{T_{21}}{T_{22}}}
+				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
 			} \; \kappa)}
@@
 		\sOOreturn{v_1}{
-		\langle\cOOcast{T_{21}}{l}{T_{11}}\rangle
+		\langle\cOOcast{T_3}{l}{T_1}\rangle
 		(\mathtt{app_2} \; v_2 \; 
-		\langle\cOOcast{T_{12}}{l}{T_{22}}\rangle \kappa)}
+		\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
 	}{}
@@
 		\sOOreturn{
-			\vOOcast{v}{\cOOcast{\POOprod{T_{11}}{T_{12}}}{l}{
-					\POOprod{T_{21}}{T_{22}}}}
+			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
+					\POOprod{T_3}{T_4}}}
 			}{(\mathtt{car} \; \kappa)}
@@
 			\mathtt{car} \;
-			\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa
+			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
 			)}
@@
 		\sOOreturn{
-			\vOOcast{v}{\cOOcast{\POOprod{T_{11}}{T_{12}}}{l}{
-					\POOprod{T_{21}}{T_{22}}}}
+			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
+					\POOprod{T_3}{T_4}}}
 		}{(\mathtt{cdr} \; \kappa)}
@@
 			\mathtt{cdr} \;
-			\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa
+			\langle \cOOcast{T_2}{l}{T_4} \rangle \kappa
 			)}
@@
 	}{
-		\text{where} \; applyCast(c,v) = \rOOsucc{u}
+		\sidecond{applyCast(c,v) = \rOOsucc{u}}
 	}
@@
 	}{
-		\text{where} \; applyCast(c,v) = \rOOfail{l}
+		\sidecond{applyCast(c,v) = \rOOfail{l}}
 	}
@@
 
-\subsubsection{an abstract machine that composes casts} 
 To show that hyper-coercion is a correct cast representation, we introduce an 
@@
 	\stxrule{k}{pre-continuations}{
-		\mathtt{mt} \mid{}
+		\hckOOmt \mid{}
 		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
@@
 	\begin{array}{rclc}
-	\funrule{cont(k)}{(id(T_1),k)}{\\&&\text{where} \; k : T_1 \Longrightarrow 
-	T_2}
+	\funrule{cont(k)}{(id(T_1),k)}{
+		\sidecond{k : T_1 \Longrightarrow T_2}}
 	\end{array}

### 2019-10-10 paper.tex
minor fixes

@@
 \begin{figure}
-	\fbox{$ c \fatsemi^\ell c = c $}
+	Composition of hyper-coercions \fbox{$ c \fatsemi^\ell c = c $}
 	\[ 
@@
 
-	\fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
+	Composition of middles \fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
 	\[ 
@@
 expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
-the new pre-continuation, then call $ cont $ which adds an identity cast to 
-construct a continuation. 
+the new pre-continuation, then call $ cont $, which adds an identity cast to 
+form a continuation. 
 When a function call happens, the machine firstly cast the operand. If the 

### 2019-10-10 paper.tex
revise intro

@@
 which can be composed and normalized. Every coercion looks like a list of 
-trees. For normalized coercion, the length of the list is bounded by a small 
+trees. For normal coercion, the length of the list is bounded by a small 
 constant. And the depths of trees do not grow in composition and 
-normalization. These two facts implies that by representing casts with 
-coercions, we can restore the space-efficiency. This 
-Coercion Calculus, however, does not support blame tracking.
+normalization. These two facts implies that coercion is a space-efficient cast 
+representation. This Coercion Calculus, however, does not support blame 
+tracking.
 
@@
 $ D $ and $ UD $ assign blame labels differently.
-Blame strategy is essentially the semantics of casts.
-They prove that the \lazyUD{} Coercion Calculus simulates the Blame Calculus 
-in \cite{wadler2009well}. But it is unknown whether the simulation also works 
-the other way, and what the Blame counterparts of other Coercion Calculi are.
+They prove partially that the \lazyUD{} Coercion Calculus is correct by showing 
+that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
+however, whether the simulation also works the other direction.
 
@@
 Their key idea is to represent casts with threesomes, a novel cast 
-representation. Threesomes, like coercions, can be composed. There is no 
-separate normalization because every threesome is in normal form. 
-They prove that their Threesome Calculus bi-simulates
-the \lazyUD{} Coercion Calculus and the Blame Calculus, and that threesomes are 
-space-efficient.
-
-\citet{siek2012interpretations} present a \lazyD{} Blame Calculus and revised 
-lazy Coercion Calculi. They simplify the Coercion Calculi by only working with 
-normal coercions (i.e. coercions in normal form). 
-Fortunately, coercions are trivially normal when initially constructed, and 
-their empowered compose function is conjectured to produces normal coercions as 
-well. Also, they conjecture that their Coercion Calculi bi-simulate the 
-corresponding Blame Calculi.
-
-Following \citet{siek2010threesomes}, \citet{garcia2013calculating} 
-implement all other blame strategies with Threesome Calculus. 
-He claims that 
-coercion with labels is easy to understand but hard to implement, 
-and that 
-threesome with labels, however, is easy to implement but hard to understand.
+representation.
+%Threesomes can also be composed. Unlike coercions, there is no 
+%separate normalization because every threesome is in normal form. 
+They prove that their Threesome Calculus is correct by showing it bi-simulates
+the \lazyUD{} Coercion Calculus in \citet{siek2009exploring} and the Blame 
+Calculus in \citet{wadler2009well}.
+They also prove that threesome is space-efficient as well.
+
+\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
+revised lazy Coercion Calculi.
+They simplify the Coercion Calculi by only 
+working with normal coercions (i.e. coercions in normal form). 
+%Fortunately, coercions are trivially normal when initially constructed, and 
+%their empowered compose function is conjectured to produces normal coercions 
+%as well. 
+They conjecture that their Coercion Calculi bi-simulate the corresponding Blame 
+Calculi.
+
+Following \citet{siek2010threesomes}, \citet{garcia2013calculating} discovers
+Threesome Calculi for other blame strategies. After studying the relation 
+between coercion and threesome,
+he claims that normal coercion with labels is easy to understand but hard to 
+implement and hard to reason about, and that 
+threesome with labels, however, is easy to implement and easy to reason about 
+but hard to understand. 
 His claim is later affirmed by the group of people who develop threesome 
 (\citet{siek2015blame}).
-The connection 
-between his Threesome Calculi and \citet{siek2009exploring}'s Coercion 
-Calculi are established by the fact that the former are derived from the latter.
+His threesome calculi are equivalent to the Coercion Calculi in 
+\citet{siek2009exploring} because the former ones are derived from the latter 
+ones.
 
 \citet{siek2015blame} revisit the coercion-based approach. They revise the 
-\lazyUD{} Coercion Calculus by \citet{siek2012interpretations}, prove its 
-space-efficiency and that it bi-simulate the \lazyUD{} Blame Calculus.
-
-Last year, \citet{kuhlenschmidt2018efficient} present Grift, a space-efficient 
-and blame-tracking compiler for a gradually typed language of the same name. 
-This implementation is based on the \lazyD{} Coercion Calculus by 
+\lazyUD{} Coercion Calculus in \citet{siek2012interpretations}.
+They prove that their calculus agrees with the \lazyUD{} Blame Calculus.
+
+Last year, \citet{kuhlenschmidt2018efficient} present Grift, a compiler for a 
+gradually typed language of the same name. 
+This implementation is based on the \lazyD{} Coercion Calculus in 
 \citet{siek2012interpretations}.
-Their result suggests that implementing coercion is practical. 
-%They implement 
-%tuples, which is the first time gradual product types is considered. Their 
-%treatment on tuples, however, is shown incorrect 
-%\cite{Gradual-TypingType-based-casts}.
+Their result suggests that normal coercion is easy enough to implement in a 
+compiler.
 
@@
 So far, it seems that the coercion-based approach is the best way to combine 
-space-efficiency and blame-tracking: coercion is claimed easy to 
+space-efficiency and blame-tracking: normal coercion is claimed easy to 
 understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
 easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
-Coercion is not satisfactory, however, in at least three aspects.
-Firstly, its compose function is not structurally recursive, which makes 
-it difficult to study coercion formally.
-For instance, many developers of Grift report that it is tricky to convince 
-their proof assistants that composition terminates. 
-Secondly, it is desirable to understand the nature of ``normalized cast'', but 
-the coercion-based approach capture this concept indirectly because normalized 
-coercion is defined by taking a subset of coercion.
-Last by not least, the memory representation of normal coercions is not very 
-compact.
-
-Perhaps unsurprisingly, threesome has a structurally recursive compose. And its 
-definition is self-standing. Together with \citet{garcia2013calculating}'s 
-work, they suggest that there can be a cast representation whose definition is 
-self-standing, and whose composition is structurally recursive. 
+Normal coercion is still not satisfactory, however, in at least three aspects.
+Firstly, as we mentioned above, it is hard to reason about. The major 
+difficulty is from its non-structurally recursive composition.
+For instance, many developers of Grift report convincing
+their proof assistants that the composition terminates is tricky. 
+Secondly, the definition of normal coercion lies unnecessarily on top 
+of coercion: all coercions are normal when they are initially constructed, and 
+\citet{siek2012interpretations} have shown that there exist functions that 
+compose and produce normal coercions.
+
+Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
+self-standing definition. Together with \citet{garcia2013calculating}'s 
+work, they suggest that there might be a cast representation whose definition 
+is self-standing, and whose composition is structurally recursive. 
 Super-coercion introduced in \citet{garcia2013calculating} could be a promising 
@@
 
-Now we present one such cast representation: hyper-coercion. As we will show in 
-Section \ref{sec:hyper-coercion}, there is a clear connection between it and 
-the normalized coercion, so we are optimistic that understanding and 
-implementing hyper-coercion should be as easy (or as hard).
+We present hyper-coercion, a cast representation whose composition is 
+structurally recursive, and whose definition is self-standing. What's more, it 
+should be at 
+least as easy to implement and understand as normal coercions, because there is 
+a clear connection between them, as we will show in Section 
+\ref{sec:hyper-coercion}.
+
+By comparing hyper-coercion with normal coercion, we notice another problem of 
+the latter in memory representation. \dots
 
@@
 We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
-bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is possibly 
-the first bi-simulation proof for the \lazyD{} Blame Calculus.
+bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
+the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.
 
@@
 Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
+Calculi. 
+Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
 Calculi. 
@@
 Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
-constructor at the top. For simplicity, we only have one base type $ \iota $, 
-the unit type. Other pre-types are functions, products, and sums.
+constructor at the top. For simplicity, we only have one base type, $ \POOunit 
+$. 
+Other pre-types are functions, products, and sums.
 
@@
 all lazy strategies -- casting a value to a shallowly inconsistent type leads 
-to a blame immediately. Shallow-consistency is reflexive, symmetric, but 
+to a blame. Shallow-consistency is reflexive, symmetric, but 
 not transitive.
@@
 
-\subsection{$Lazy D$ Blame Calculus}
+\subsection{\lazyD{} Blame Calculus}
 
@@
 
-\section{Background: Coercion Calculus}
+\section{Background: Coercion Calculus} \label{sec:coercion-calculus}
+
+\todo[inline]{Which version of normal coercion should this section review?}
 

### 2019-10-11 paper.tex
monoid

@@
 
-	Reduction \fbox{$ s_1 \longrightarrow_{D,B} s_2 $}
+	Reduction \fbox{$ s \longrightarrow_{D,B} s $}
 	\[
@@
 
-	Case
+	\fbox{$case(v, \kappa, \kappa) = s$}
 	\[
@@
 
-	Apply cast
+	\fbox{$applyCast(c,v) = r$}
 	\[
@@
 
-	\caption{Dynamic semantics of the \lazyD{} Blame Calculus}
+	\caption{CEK abstract machine for the \lazyD{} Blame Calculus}
 	\label{machine-cekc}
@@
 
-\subsection{$Lazy UD$ Blame Calculus}
-
-\dots
+\subsection{$Lazy UD$ Blame Calculus [Jeremy]}
+
+UNDER CONSTRUCTION
 
@@
 
-\begin{theorem}[$ id $ constructs neutrals] For all $ c : T_1 \Longrightarrow 
-	T_2 $
+\begin{proposition}[Hyper-coercions form a Monoid]
+  For all $c : T_1 \Longrightarrow T_2$,
+  $c_1 : T_1 \Longrightarrow T_2$,
+  $c_2 : T_2 \Longrightarrow T_3$, and
+  $c_3 : T_3 \Longrightarrow T_4$,
   \begin{enumerate}
-		\item $ seq(id(T_1),c) = c $
-		\item $ seq(c,id(T_2)) = c $
+  \item $seq(id(T_1),c) = c$,
+  \item $seq(c,id(T_2)) = c$, and
+  \item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
   \end{enumerate}
-\end{theorem}
+\end{proposition}
 
@@
 
-	Reduction \fbox{$ s_1 \longrightarrow_{D,P(C)} s_2 $}
+	Reduction \fbox{$ s \longrightarrow_{D,P(C)} s $}
 	\[
@@
 
-\subsection{$Lazy UD$ Hyper-coercion}
+\subsection{$Lazy UD$ Hyper-coercion [Jeremy]}
+
+UNDER CONSTRUCTION
 

### 2019-10-11 paper.tex
new sections

@@
 
+\section{Space-efficient CEK Abstract Machine}
+
+[move the definition of the generic machine here -Jeremy]
+
 \section{Hyper-coercion} \label{sec:hyper-coercion}
@@
 
+\subsection{Correctness of \lazyD{} Hyper-coercions}
+
 One of our major contributions is for all cast presentation, if it is proper, 
@@
 
-\begin{theorem}[\lazyD{} Hyper-coercion is a proper cast representation]
+\begin{lemma}[\lazyD{} Hyper-coercion is a proper cast representation]
 	See appendix.
-\end{theorem}
-
-\begin{corollary}[\lazyD{} hyper-coercion is correct]
+\end{lemma}
+
+\begin{theorem}[\lazyD{} hyper-coercion is correct]
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
@@
 	\]
-\end{corollary}
+\end{theorem}
 

### 2019-10-14 paper.tex
fix typos in figs
part of the machine section

@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
+%% For double-blind review submission, w/o CCS and ACM Reference (max 
+%%submission space)
 \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
@@
 %\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
+%% For single-blind review submission, w/o CCS and ACM Reference (max 
+%%submission space)
 %\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
@@
 \newcommand{\redrule}[3]{#1 & \longrightarrow_B & #2 & #3\\}
+\newcommand{\redruleS}[3]{#1 & \longrightarrow_{S(C)} & #2 & #3\\}
 \newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
@@
 <concept_id>10011007.10011006.10011008</concept_id>
-<concept_desc>Software and its engineering~General programming languages</concept_desc>
+<concept_desc>Software and its engineering~General programming 
+languages</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept_id>10003456.10003457.10003521.10003525</concept_id>
-<concept_desc>Social and professional topics~History of programming languages</concept_desc>
+<concept_desc>Social and professional topics~History of programming 
+languages</concept_desc>
 <concept_significance>300</concept_significance>
@@
 cast, including those at tail position. Thus, at runtime, mutually 
-tail-recursive functions in source language can accumulate casts at tail 
-position. There are more examples in \citet{herman2010space}.
+tail-recursive functions in source language can accumulate unbounded space. 
+There are more examples in \citet{herman2010space}.
 
@@
 
-\citet{siek2009exploring} incorporate blame tracking into Coercion Calculus by 
+%\subsection{coercion-based approach and blame strategies}
+
+\citet{siek2009exploring} incorporate blame tracking into 
+\citet{herman2010space}'s Coercion Calculus by 
 decorating coercions with labels. They also propose that there are four blame 
@@
 that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
-however, whether the simulation also works the other direction.
+however, whether the simulation also works in the other direction.
 
@@
 %separate normalization because every threesome is in normal form. 
-They prove that their Threesome Calculus is correct by showing it bi-simulates
-the \lazyUD{} Coercion Calculus in \citet{siek2009exploring} and the Blame 
-Calculus in \citet{wadler2009well}.
-They also prove that threesome is space-efficient as well.
+They show that their threesome calculus bi-simulates the \lazyUD{} Coercion 
+Calculus in \citet{siek2009exploring} and the Blame Calculus in 
+\citet{wadler2009well}. They also prove that threesome is space-efficient as 
+well.
 
@@
 but hard to understand. 
-His claim is later affirmed by the group of people who develop threesome 
+His claim is partially affirmed by the group of people who develop threesome 
 (\citet{siek2015blame}).
@@
 \citet{siek2015blame} revisit the coercion-based approach. They revise the 
-\lazyUD{} Coercion Calculus in \citet{siek2012interpretations}.
-They prove that their calculus agrees with the \lazyUD{} Blame Calculus.
+\lazyUD{} Coercion Calculus in \citet{siek2012interpretations} and prove that 
+their revised coercion calculus bi-simulates the \lazyUD{} Blame Calculus.
 
@@
 Normal coercion is still not satisfactory, however, in at least three aspects.
-Firstly, as we mentioned above, it is hard to reason about. The major 
-difficulty is from its non-structurally recursive composition.
-For instance, many developers of Grift report convincing
-their proof assistants that the composition terminates is tricky. 
+Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
+major difficulty is from its non-structurally recursive composition.
+For instance, many developers of Grift report it is tricky to convince
+their proof assistants that the composition terminates. 
 Secondly, the definition of normal coercion lies unnecessarily on top 
@@
 \ref{sec:hyper-coercion}.
-
-By comparing hyper-coercion with normal coercion, we notice another problem of 
-the latter in memory representation. \dots
 
@@
 
-\subsection{$Lazy UD$ Blame Calculus [Jeremy]}
+\subsection{\lazyUD{} Blame Calculus [Jeremy]}
 
@@
 
-\subsection{$Lazy D$ Coercion Calculus}
-
-\subsection{$Lazy UD$ Coercion Calculus}
+\subsection{\lazyD{} Coercion Calculus}
+
+\subsection{\lazyUD{} Coercion Calculus}
 
@@
 [move the definition of the generic machine here -Jeremy]
+
+All definitions and results in this section are new.
+
+We present a space-efficient CEK machine for blame calculi. This machine is
+parameterized over cast representation.
+
+\begin{definition}[Cast Representation]
+	A cast representation has four interface functions:
+	\begin{description}
+		\item[$ id(T) $] constructs an identity cast
+		\item[$ seq(c_1,c_2) $] composes two casts
+		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$ applyCast(c,v) $] applies a cast onto a value
+	\end{description}
+\end{definition}
+
+\begin{figure}
+	Syntax
+	\[
+	\begin{array}{rclr}
+
+	\stxrule{v}{values}{
+		\hcvOOtt \mid
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
+		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+	}
+	\stxrulecont{
+		\hcvOOinl{v}{c} \mid
+		\hcvOOinr{v}{c} \mid
+		\hcvOOinj{P}{v}
+	}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+	\stxrule{\kappa}{continuation}{
+		(c,k)
+	}
+	\stxrule{k}{pre-continuations}{
+		\hckOOmt \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{car} \; \kappa \mid{}
+		\mathtt{cdr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
+	}
+	\end{array}
+	\]
+
+	Build continuation \fbox{$ cont(k) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{cont(k)}{(id(T_1),k)}{
+		\sidecond{k : T_1 \Longrightarrow T_2}}
+	\end{array}
+	\]
+
+	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
+	\end{array}
+	\]
+
+	Reduction \fbox{$ s \longrightarrow_{S(C)} s $}
+	\[
+	\begin{array}{rclr}
+	& \vdots \\
+	\redruleS{
+		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
+	}{
+		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
+	}{}
+	\redruleS{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+	}{}
+	\redruleS{
+		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+	}{}
+	\redruleS{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
+	}
+	\redruleS{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOhalt{(\oOOblame{l})}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
+	}
+	\end{array}
+	\]
+
+%	Transitive closure of reduction \fbox{$ s \longrightarrow_{S(C)}^{*} s $}
+%	\[\dots\]
+
+	Evaluation \fbox{$ e \Downarrow_{S(C)} o $}
+	\[
+	\inference{
+		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{S(C)}^{*} 
+		\sOOhalt{o}
+	}{
+		e \Downarrow_{S(C)} o
+	}
+	\]
+
+	\caption{A space-efficient CKE machine for Blame Calculus.}
+	\label{machine-cekcc}
+\end{figure}
+
+\figref{machine-cekcc} defines the machine. 
+Let $ v $ ranges over value. We push casts into values. For instance, function 
+values now include two more components: a cast for argument and a cast for the 
+output. The last kind of values is injection to $ \TOOdyn $. 
+Cast results ($ r $) and machine states ($ s $) are as before. 
+Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
+pre-continuations. 
+A continuation is now a pair whose first part is a cast, and whose second part 
+is a pre-continuation. 
+Pre-continuation are like the continuations before.
+
+We list a fraction of reduction rules due to space limitation.
+When values are constructed, their hyper-coercion parts are filled with outputs 
+of $ id $. For instance, when a function value is constructed, its first part 
+and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
+When evaluating a cast expression, the current continuation is extended with a 
+hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
+with the hyper-coercion on the top of the continuation.
+When evaluating a compound expression, the machine firstly construct the new 
+pre-continuation, then turn it to a continuation by adding an identity 
+hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
+expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
+the new pre-continuation, then call $ cont $, which adds an identity cast to 
+form a continuation. 
+When a function call happens, the machine firstly cast the operand. If the 
+casting succeeds, the machine then evaluate the body in the extended 
+environment and the extended continuation. If the casting fails, the machine 
+then halts with the blame label.
+
+Transitive closure of reduction and evaluation are standard.
+
+\subsection{\lazyD\ Cast Representations}
+
+We show that all \textit{proper} cast representations are 
+equivalent.
+
+\begin{definition}[Proper Cast Representation]
+	A cast representation is proper if
+	\begin{enumerate}
+		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ v : T_1 $,
+		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
+		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
+		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
+		v.applyCast(c_2,v) $
+		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		\item If $ v : \star $, 
+		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		\item If $ v : P $,
+		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
+		= applyCast(cast(P,l,Q),v) $
+		\item If $ v : P $,
+		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item If $ v : \iota $,
+		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		\item $ 
+		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		= 
+		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+
+		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
+		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		$ = 
+		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
+		$ 
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
+	\end{enumerate}
+\end{definition}
+
+With the properties of proper cast representation, it is straightforward to 
+proof that all machines instantiated with a proper cast representation are 
+strongly bi-simulated.
+
+\begin{theorem}[Strong Bi-simulation of Proper Cast Representations]
+	If $ C_1 $ and $ C_2 $ are proper cast representations,
+	$ s_1 $ and $ s_2 $ are states of $ S(C_1) $,
+	$ s_3 $ is an state of $ S(C_2) $,
+	$ s_1 \longrightarrow_{S(C_1)} s_2 $,
+	and $ s_1 \approx s_3 $, \\
+	then there exists an $ s_4 $ such that $ s_3 \approx s_4 $ and
+	$ s_3 \longrightarrow_{S(C_2)} s_4 $
+\end{theorem}
+
+As a corollary, machines instantiated with proper cast representations are 
+equivalent when used as interpreters.
+
+\begin{theorem}[proper cast represenations are equivalent]
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and that $ C_1 $ and $ C_2 $ 
+	are 
+	proper cast representations
+	\[
+	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+	e \Downarrow_{S(C_2)} o
+	\]
+\end{theorem}
 
@@
 	}{
-		\hyperCoercionC{?^{l'}}{b}{t}
-	}{
-		\hyperCoercionC{?^{l'}}{b}{t}
+		\hyperCoercionC{?^{l'}}{m}{t}
+	}{
+		\hyperCoercionC{?^{l'}}{m}{t}
 	}{}
@@
 	}{
-		\hyperCoercionC{\epsilon}{b}{t}
-	}{
-		\hyperCoercionC{?^{l}}{b}{t}
+		\hyperCoercionC{\epsilon}{m}{t}
+	}{
+		\hyperCoercionC{?^{l}}{m}{t}
 	}{\sidecond{\ell = l}}
@@
 	\comprule{
-		\hyperCoercionC{h}{b}{\bot^{l'}}
+		\hyperCoercionC{h}{m}{\bot^{l'}}
 	}{
@@
 	}{
-		\hyperCoercionC{h}{b}{\bot^{l'}}
+		\hyperCoercionC{h}{m}{\bot^{l'}}
 	}{}
@@
 	\comprule{
-		\hyperCoercionC{h}{b_1}{t_1}
+		\hyperCoercionC{h}{m}{t}
 	}{
@@
 	}{
-		\hyperCoercionC{h}{b_1}{!}
-	}{
-		\sidecond{\forall l. t_1 \neq \bot^{l}}
+		\hyperCoercionC{h}{m}{!}
+	}{
+		\sidecond{\forall l. t \neq \bot^{l}}
 	}
@@
 	\comprule{
-		\hyperCoercionC{h}{b_1}{t_1}
-	}{
-		\hyperCoercionC{\epsilon}{b_2}{t_2}
-	}{
-		\hyperCoercionC{h}{b'}{t'}
+		\hyperCoercionC{h}{m_1}{t_1}
+	}{
+		\hyperCoercionC{\epsilon}{m_2}{t_2}
+	}{
+		\hyperCoercionC{h}{m'}{t'}
 	}{
@@
 			t_1 \neq \bot^{\centerdot} \; \text{and} \;
-			b_1 \fatsemi^{\ell} (b_2, t) = (b', t')
+			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
 		}
@@
 	\comprule{
-		\hyperCoercionC{h}{b_1}{t_1}
-	}{
-		\hyperCoercionC{?^{l'}}{b_2}{t_2}
-	}{
-		\hyperCoercionC{h}{b'}{t'}
+		\hyperCoercionC{h}{m_1}{t_1}
+	}{
+		\hyperCoercionC{?^{l'}}{m_2}{t_2}
+	}{
+		\hyperCoercionC{h}{m'}{t'}
 	}{
@@
 		t_1 \neq \bot^{\centerdot} \; \text{and} \;
-		b_1 \fatsemi^{l'} (b_2, t) = (b', t')
+		m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
 		}
@@
 	\]
-	\caption{$Lazy D$ Hyper-coercion}
+	\caption{\lazyD{} Hyper-coercion}
 	\label{fig:HC-D}
@@
 bi-simulates the previous machine.
-\figref{machine-cekcc} defines the new machine.
-
-\begin{figure}
-	Syntax
-	\[
-	\begin{array}{rclr}
-
-	\stxrule{v}{values}{
-		\hcvOOtt \mid
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
-		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
-	}
-	\stxrulecont{
-		\hcvOOinl{v}{c} \mid
-		\hcvOOinr{v}{c} \mid
-		\hcvOOinj{P}{v}
-	}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
-	\stxrule{\kappa}{continuation}{
-		(c,k)
-	}
-	\stxrule{k}{pre-continuations}{
-		\hckOOmt \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
-	}
-	\stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{car} \; \kappa \mid{}
-		\mathtt{cdr} \; \kappa
-	}
-	\stxrulecont{
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
-		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
-	}
-	\end{array}
-	\]
-
-	Build continuation \fbox{$ cont(k) = \kappa $}
-	\[
-	\begin{array}{rclc}
-	\funrule{cont(k)}{(id(T_1),k)}{
-		\sidecond{k : T_1 \Longrightarrow T_2}}
-	\end{array}
-	\]
-
-	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
-	\[
-	\begin{array}{rclc}
-	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
-	\end{array}
-	\]
-
-	Reduction \fbox{$ s \longrightarrow_{D,P(C)} s $}
-	\[
-	\begin{array}{rclr}
-	& \vdots \\
-	\redrule{
-		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
-	}{
-		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
-	}{}
-	\redrule{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-	}{
-		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
-	}{}
-	\redrule{
-		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
-	}{
-		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
-	}{}
-	\redrule{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
-		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
-	}
-	\redrule{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
-		\sOOhalt{(\oOOblame{l})}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
-	}
-	\end{array}
-	\]
-
-	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,P(C)}^{*} s $}
-	\[\dots\]
-
-	Evaluation \fbox{$ e \Downarrow_{D,P(C)} o $}
-	\[
-	\inference{
-		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{P(C)}^{*} 
-		\sOOhalt{o}
-	}{
-		e \Downarrow_{D,P(C)} o
-	}
-	\]
-
-	\caption{An abstract machine that composes casts.}
-	\label{machine-cekcc}
-\end{figure}
-
-Let $ v $ ranges over value. We push casts into values. For instance, function 
-values now include two more components: a cast for argument and a cast for the 
-output. The last kind of values is injection to $ \TOOdyn $. 
-Cast results ($ r $) and machine states ($ s $) are as before. 
-Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
-pre-continuations. 
-A continuation is now a pair whose first part is a cast, and whose second part 
-is a pre-continuation. 
-Pre-continuation are like the continuations before.
-
-We list a fraction of reduction rules due to space limitation.
-When values are constructed, their hyper-coercion parts are filled with outputs 
-of $ id $. For instance, when a function value is constructed, its first part 
-and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
-When evaluating a cast expression, the current continuation is extended with a 
-hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
-with the hyper-coercion on the top of the continuation.
-When evaluating a compound expression, the machine firstly construct the new 
-pre-continuation, then turn it to a continuation by adding an identity 
-hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
-expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
-the new pre-continuation, then call $ cont $, which adds an identity cast to 
-form a continuation. 
-When a function call happens, the machine firstly cast the operand. If the 
-casting succeeds, the machine then evaluate the body in the extended 
-environment and the extended continuation. If the casting fails, the machine 
-then halts with the blame label.
-
-Transitive closure of reduction and evaluation are standard.
 
@@
 
-\begin{definition}[Cast Representation]
-	A cast representation has four interface functions:
-	\begin{description}
-		\item[$ id(T) $] constructs an identity cast
-		\item[$ seq(c_1,c_2) $] composes two casts
-		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
-		\item[$ applyCast(c,v) $] applies a cast onto a value
-	\end{description}
-\end{definition}
-
 \subsection{Correctness of \lazyD{} Hyper-coercions}
@@
 then it is correct.
-
-\begin{definition}[Proper Cast Representation]
-	A cast representation is proper if
-	\begin{enumerate}
-		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
-		\item If $ v : T_1 $,
-		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
-		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
-		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
-		v.applyCast(c_2,v) $
-		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
-		\item If $ v : \star $, 
-		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
-		\item If $ v : P $,
-		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
-		= applyCast(cast(P,l,Q),v) $
-		\item If $ v : P $,
-		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \iota $,
-		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
-		\item $ 
-		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
-		= 
-		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-
-		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
-		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
-		$ = 
-		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
-		 $ 
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
-		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
-		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
-	\end{enumerate}
-\end{definition}
 
@@
 
-\subsection{$Lazy UD$ Hyper-coercion [Jeremy]}
+\subsection{\lazyUD{} Hyper-coercion [Jeremy]}
 

### 2019-10-15 paper.tex
normal coercion

@@
 \newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
-\newcommand{\redrule}[3]{#1 & \longrightarrow_B & #2 & #3\\}
 \newcommand{\redruleS}[3]{#1 & \longrightarrow_{S(C)} & #2 & #3\\}
@@
 \newcommand{\eager}{$\mathtt{Eager}$}
-\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
-\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
 \newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
@@
 \newcommand{\sidecond}[1]{\text{if}\;#1}
+% Lazy D blame calculus
+\newcommand{\judgeDBreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
+\newcommand{\judgeDBreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
+\newcommand{\judgeDBeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
+\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
+% Normal Coercion
+\newcommand{\ncProj}[2]{#1?^{#2}}
+\newcommand{\ncInj}[1]{#1!}
+\newcommand{\ncId}[0]{\iota}
+\newcommand{\ncSeq}[2]{#1;#2}
+\newcommand{\ncFail}[1]{\bot^{#1}}
+\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
+\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
+\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
+% Hyper-coercion
+\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
+\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
 
@@
 
-	Reduction \fbox{$ s \longrightarrow_{D,B} s $}
+	Reduction \fbox{$ \judgeDBreduce{s}{s} $}
 	\[
@@
 
-	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s $}\\
-
-	Evaluation \fbox{$ e \Downarrow_{D,B} o $}
+%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s $}\\
+
+	Evaluation \fbox{$\judgeDBeval{e}{o}$}
 	\[
@@
 	}{
-		e \Downarrow_{D,B} o
+		\judgeDBeval{e}{o}
 	}
@@
 
-Fig.~\ref{machine-cekc} defines the dynamic semantcis of the \lazyD{} Blame 
+Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
 Calculus in the style of CEK machines (\citet{felleisen1986control}). 
-We choose CEK machine because to achieve space efficiency, we need to change 
-continuations. Thus, abstract machines that include continuation in states is 
-quite convenient for us. And CEK is one of the simplest machine of this kind.
+We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
+\citet{siek2012interpretations}.
+We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
+equivalent to an abstract machine that represents casts with hyper-coercions.
 
@@
 
-Transitive closure of reduction and evaluation are standard.
+Transitive closure of reduction ($ \judgeDBreduceTrans{s}{s} $) and evaluation 
+are 
+standard.
 
@@
 
-\section{Background: Coercion Calculus} \label{sec:coercion-calculus}
-
-\todo[inline]{Which version of normal coercion should this section review?}
-
-\subsection{\lazyD{} Coercion Calculus}
-
-\subsection{\lazyUD{} Coercion Calculus}
-
-\section{Space-efficient CEK Abstract Machine}
-
-[move the definition of the generic machine here -Jeremy]
-
-All definitions and results in this section are new.
-
-We present a space-efficient CEK machine for blame calculi. This machine is
-parameterized over cast representation.
-
-\begin{definition}[Cast Representation]
-	A cast representation has four interface functions:
-	\begin{description}
-		\item[$ id(T) $] constructs an identity cast
-		\item[$ seq(c_1,c_2) $] composes two casts
-		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
-		\item[$ applyCast(c,v) $] applies a cast onto a value
-	\end{description}
-\end{definition}
+\section{Background: Normal Coercion} \label{sec:coercion-calculus}
+
+In this section we review the normal coercion (NC) in 
+\citet{siek2012interpretations}. We ignore sum types and product types in this 
+section, because they were not presented in the paper. We assume a basic 
+familiarity with coercion, and direct readers who do not know it to 
+\citet{siek2012interpretations}.
+
+As the name suggests, 
+hyper-coercion is largely inspired by coercion, especially its subst NC. We 
+will highlight the similarity of normal coercion and hyper-coercion, and hope 
+this would convince you that hyper-coercion should be as difficult to implement 
+as NC.
 
 \begin{figure}
-	Syntax
 	\[
 	\begin{array}{rclr}
-
-	\stxrule{v}{values}{
-		\hcvOOtt \mid
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
-		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+	\stxrule{I}{injectable types (\lazyD)}{
+		\POOfun{T}{T}}
+	\stxrule{I}{injectable types (\lazyUD)}{
+		\POOfun{\TOOdyn}{\TOOdyn}
+	}
+	\stxrule{c}{coercions}{
+		\ncInj{I} \mid
+		\ncProj{I}{l} \mid
+		\ncId \mid
+		\ncFail{l} \mid
+		\ncSeq{c}{c} \mid
+		\ncFun{c}{c}
+	}
+	\stxrule{\bar{c}}{wrapper coercions}{	
+		\ncInj{I} \mid
+		\ncFun{\hat{c}}{\hat{c}} \mid
+		\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
+	}
+%	\stxrulecont{
+%		\ncProd{\hat{c}}{\hat{c}} \mid
+%		\ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
+%		\ncSum{\hat{c}}{\hat{c}} \mid
+%		\ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid	
+%	}
+	\stxrule{\hat{c}}{normal coercions}{
+		\bar{c} \mid
+		\ncId \mid
+		\ncFail{l} \mid
+		\ncProj{I}{l} \mid
+		\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
+		\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
 	}
 	\stxrulecont{
-		\hcvOOinl{v}{c} \mid
-		\hcvOOinr{v}{c} \mid
-		\hcvOOinj{P}{v}
-	}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
-	\stxrule{\kappa}{continuation}{
-		(c,k)
-	}
-	\stxrule{k}{pre-continuations}{
-		\hckOOmt \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
+		\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
+		\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
+	}
+	\end{array}
+	\]
+	\caption{Syntax of Normal Coercion (NC)}
+	\label{fig:normal-coercion}
+\end{figure}
+
+\figref{fig:normal-coercion} defines the normal coercion. 
+Let $ I $ ranges over injectable types. An injectable type is a type that can 
+be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
+definition of injectable type depends on blame strategy. With \lazyD, all 
+pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
+is injectable. 
+Let $ c $ ranges over coercions, a coercion is either injection, projection, 
+identity, failure, sequencing, or function coercion.
+Let $ \bar{c} $ ranges over wrapper coercions, which represent casts in $ 
+\vOOcast{v}{c} $.
+Let $ \hat{c} $ ranges over normal coercions. If we inline $ \bar{c} $ and 
+re-arrange cases a little bit, the definition becomes:
+\[
+\begin{array}{rclr}
+\stxrule{\hat{c}}{normal coercions}{
+	\ncFun{\hat{c}}{\hat{c}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
+	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
 }
 \stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{car} \; \kappa \mid{}
-		\mathtt{cdr} \; \kappa
-	}
-	\stxrulecont{
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
-		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
-	}
-	\end{array}
-	\]
-
-	Build continuation \fbox{$ cont(k) = \kappa $}
-	\[
-	\begin{array}{rclc}
-	\funrule{cont(k)}{(id(T_1),k)}{
-		\sidecond{k : T_1 \Longrightarrow T_2}}
-	\end{array}
-	\]
-
-	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
-	\[
-	\begin{array}{rclc}
-	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
-	\end{array}
-	\]
-
-	Reduction \fbox{$ s \longrightarrow_{S(C)} s $}
-	\[
-	\begin{array}{rclr}
-	& \vdots \\
-	\redruleS{
-		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
-	}{
-		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
-	}{}
-	\redruleS{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-	}{
-		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
-	}{}
-	\redruleS{
-		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
-	}{
-		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
-	}{}
-	\redruleS{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
-		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
-	}
-	\redruleS{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
-		\sOOhalt{(\oOOblame{l})}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
-	}
-	\end{array}
-	\]
-
-%	Transitive closure of reduction \fbox{$ s \longrightarrow_{S(C)}^{*} s $}
-%	\[\dots\]
-
-	Evaluation \fbox{$ e \Downarrow_{S(C)} o $}
-	\[
-	\inference{
-		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{S(C)}^{*} 
-		\sOOhalt{o}
-	}{
-		e \Downarrow_{S(C)} o
-	}
-	\]
-
-	\caption{A space-efficient CKE machine for Blame Calculus.}
-	\label{machine-cekcc}
-\end{figure}
-
-\figref{machine-cekcc} defines the machine. 
-Let $ v $ ranges over value. We push casts into values. For instance, function 
-values now include two more components: a cast for argument and a cast for the 
-output. The last kind of values is injection to $ \TOOdyn $. 
-Cast results ($ r $) and machine states ($ s $) are as before. 
-Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
-pre-continuations. 
-A continuation is now a pair whose first part is a cast, and whose second part 
-is a pre-continuation. 
-Pre-continuation are like the continuations before.
-
-We list a fraction of reduction rules due to space limitation.
-When values are constructed, their hyper-coercion parts are filled with outputs 
-of $ id $. For instance, when a function value is constructed, its first part 
-and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
-When evaluating a cast expression, the current continuation is extended with a 
-hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
-with the hyper-coercion on the top of the continuation.
-When evaluating a compound expression, the machine firstly construct the new 
-pre-continuation, then turn it to a continuation by adding an identity 
-hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
-expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
-the new pre-continuation, then call $ cont $, which adds an identity cast to 
-form a continuation. 
-When a function call happens, the machine firstly cast the operand. If the 
-casting succeeds, the machine then evaluate the body in the extended 
-environment and the extended continuation. If the casting fails, the machine 
-then halts with the blame label.
-
-Transitive closure of reduction and evaluation are standard.
-
-\subsection{\lazyD\ Cast Representations}
-
-We show that all \textit{proper} cast representations are 
-equivalent.
-
-\begin{definition}[Proper Cast Representation]
-	A cast representation is proper if
+	\ncId \mid
+	\ncProj{I}{l} \mid
+	\ncInj{I} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
+	\ncFail{l} \mid
+}
+\end{array}
+\]
+
+Three observations on the definition leads to hyper-coercion: 
 \begin{enumerate}
-		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
-		\item If $ v : T_1 $,
-		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
-		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
-		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
-		v.applyCast(c_2,v) $
-		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
-		\item If $ v : \star $, 
-		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
-		\item If $ v : P $,
-		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
-		= applyCast(cast(P,l,Q),v) $
-		\item If $ v : P $,
-		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \iota $,
-		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
-		\item $ 
-		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
-		= 
-		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-
-		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
-		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
-		$ = 
-		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
-		$ 
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
-		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
-		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
+	\item The length of normal coercion is at most three.
+	\item Projections are always at the beginning when presented.
+	\item Injections and failures are always at the end when presented.
 \end{enumerate}
-\end{definition}
-
-With the properties of proper cast representation, it is straightforward to 
-proof that all machines instantiated with a proper cast representation are 
-strongly bi-simulated.
-
-\begin{theorem}[Strong Bi-simulation of Proper Cast Representations]
-	If $ C_1 $ and $ C_2 $ are proper cast representations,
-	$ s_1 $ and $ s_2 $ are states of $ S(C_1) $,
-	$ s_3 $ is an state of $ S(C_2) $,
-	$ s_1 \longrightarrow_{S(C_1)} s_2 $,
-	and $ s_1 \approx s_3 $, \\
-	then there exists an $ s_4 $ such that $ s_3 \approx s_4 $ and
-	$ s_3 \longrightarrow_{S(C_2)} s_4 $
-\end{theorem}
-
-As a corollary, machines instantiated with proper cast representations are 
-equivalent when used as interpreters.
-
-\begin{theorem}[proper cast represenations are equivalent]
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and that $ C_1 $ and $ C_2 $ 
-	are 
-	proper cast representations
-	\[
-	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-	e \Downarrow_{S(C_2)} o
-	\]
-\end{theorem}
 
@@
 	%	}{
-%		\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
+	%		
+	%\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
 	%	}
@@
 
+\section{Space-efficient CEK Abstract Machine}
+
+[move the definition of the generic machine here -Jeremy]
+
+All definitions and results in this section are new.
+
+We present a space-efficient CEK machine for blame calculi. This machine is
+parameterized over cast representation.
+
+\begin{definition}[Cast Representation]
+	A cast representation has four interface functions:
+	\begin{description}
+		\item[$ id(T) $] constructs an identity cast
+		\item[$ seq(c_1,c_2) $] composes two casts
+		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$ applyCast(c,v) $] applies a cast onto a value
+	\end{description}
+\end{definition}
+
+\begin{figure}
+	Syntax
+	\[
+	\begin{array}{rclr}
+
+	\stxrule{v}{values}{
+		\hcvOOtt \mid
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
+		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+	}
+	\stxrulecont{
+		\hcvOOinl{v}{c} \mid
+		\hcvOOinr{v}{c} \mid
+		\hcvOOinj{P}{v}
+	}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+	\stxrule{\kappa}{continuation}{
+		(c,k)
+	}
+	\stxrule{k}{pre-continuations}{
+		\hckOOmt \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{car} \; \kappa \mid{}
+		\mathtt{cdr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
+	}
+	\end{array}
+	\]
+
+	Build continuation \fbox{$ cont(k) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{cont(k)}{(id(T_1),k)}{
+		\sidecond{k : T_1 \Longrightarrow T_2}}
+	\end{array}
+	\]
+
+	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
+	\[
+	\begin{array}{rclc}
+	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
+	\end{array}
+	\]
+
+	Reduction \fbox{$ s \longrightarrow_{S(C)} s $}
+	\[
+	\begin{array}{rclr}
+	& \vdots \\
+	\redruleS{
+		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
+	}{
+		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
+	}{}
+	\redruleS{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+	}{}
+	\redruleS{
+		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+	}{}
+	\redruleS{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
+	}
+	\redruleS{
+		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+	}{
+		\sOOhalt{(\oOOblame{l})}
+	}{
+		\\ & &
+		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
+	}
+	\end{array}
+	\]
+
+%	Transitive closure of reduction \fbox{$ s \longrightarrow_{S(C)}^{*} s $}
+%	\[\dots\]
+
+	Evaluation \fbox{$ e \Downarrow_{S(C)} o $}
+	\[
+	\inference{
+		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{S(C)}^{*} 
+		\sOOhalt{o}
+	}{
+		e \Downarrow_{S(C)} o
+	}
+	\]
+
+	\caption{A space-efficient CKE machine for Blame Calculus.}
+	\label{machine-cekcc}
+\end{figure}
+
+\figref{machine-cekcc} defines the machine. 
+Let $ v $ ranges over value. We push casts into values. For instance, function 
+values now include two more components: a cast for argument and a cast for the 
+output. The last kind of values is injection to $ \TOOdyn $. 
+Cast results ($ r $) and machine states ($ s $) are as before. 
+Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
+pre-continuations. 
+A continuation is now a pair whose first part is a cast, and whose second part 
+is a pre-continuation. 
+Pre-continuation are like the continuations before.
+
+We list a fraction of reduction rules due to space limitation.
+When values are constructed, their hyper-coercion parts are filled with outputs 
+of $ id $. For instance, when a function value is constructed, its first part 
+and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
+When evaluating a cast expression, the current continuation is extended with a 
+hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
+with the hyper-coercion on the top of the continuation.
+When evaluating a compound expression, the machine firstly construct the new 
+pre-continuation, then turn it to a continuation by adding an identity 
+hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
+expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
+the new pre-continuation, then call $ cont $, which adds an identity cast to 
+form a continuation. 
+When a function call happens, the machine firstly cast the operand. If the 
+casting succeeds, the machine then evaluate the body in the extended 
+environment and the extended continuation. If the casting fails, the machine 
+then halts with the blame label.
+
+Transitive closure of reduction and evaluation are standard.
+
+\subsection{\lazyD\ Cast Representations}
+
+We show that all \textit{proper} cast representations are 
+equivalent.
+
+\begin{definition}[Proper Cast Representation]
+	A cast representation is proper if
+	\begin{enumerate}
+		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ v : T_1 $,
+		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
+		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
+		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
+		v.applyCast(c_2,v) $
+		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		\item If $ v : \star $, 
+		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		\item If $ v : P $,
+		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
+		= applyCast(cast(P,l,Q),v) $
+		\item If $ v : P $,
+		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item If $ v : \iota $,
+		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		\item $ 
+		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		= 
+		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+
+		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
+		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		$ = 
+		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
+		$ 
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
+	\end{enumerate}
+\end{definition}
+
+With the properties of proper cast representation, it is straightforward to 
+proof that all machines instantiated with a proper cast representation are 
+strongly bi-simulated.
+
+\begin{theorem}[Strong Bi-simulation of Proper Cast Representations]
+	If $ C_1 $ and $ C_2 $ are proper cast representations,
+	$ s_1 $ and $ s_2 $ are states of $ S(C_1) $,
+	$ s_3 $ is an state of $ S(C_2) $,
+	$ s_1 \longrightarrow_{S(C_1)} s_2 $,
+	and $ s_1 \approx s_3 $, \\
+	then there exists an $ s_4 $ such that $ s_3 \approx s_4 $ and
+	$ s_3 \longrightarrow_{S(C_2)} s_4 $
+\end{theorem}
+
+As a corollary, machines instantiated with proper cast representations are 
+equivalent when used as interpreters.
+
+\begin{theorem}[proper cast represenations are equivalent]
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and that $ C_1 $ and $ C_2 $ 
+	are 
+	proper cast representations
+	\[
+	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+	e \Downarrow_{S(C_2)} o
+	\]
+\end{theorem}
+
 \section{Conclusion} \label{sec:conclude}

### 2019-10-15 paper.tex
missing conclusion; LCast

@@
 \newcommand{\figref}[1]{Fig.~\ref{#1}}
+\newcommand{\secref}[1]{Section~\ref{#1}}
 \newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
@@
 \newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
-\newcommand{\redruleS}[3]{#1 & \longrightarrow_{S(C)} & #2 & #3\\}
 \newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
@@
 \newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
+\newcommand{\judgeType}[2]{#1 : #2}
+\newcommand{\judgeTypeFT}[3]{#1 : #2 \Longrightarrow #3} % FT = From To
 \newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
@@
 \newcommand{\sidecond}[1]{\text{if}\;#1}
-% Lazy D blame calculus
+% Lazy D blame calculus on space-inefficient CEK
 \newcommand{\judgeDBreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
@@
 \newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
+% blame calculus on space-efficient CEK
+\newcommand{\judgeSreduce}[3]{#2 \longrightarrow_{\mathcal{S}(#1)} #3}
+\newcommand{\judgeSreduceTrans}[3]{#2 \longrightarrow_{\mathcal{S}(#1)}^{*} #3}
+\newcommand{\judgeSeval}[3]{#2 \Downarrow_{\mathcal{S}(#1)} #3}
+\newcommand{\redruleS}[3]{#1 & \longrightarrow_{\mathcal{S}(C)} & #2 & #3\\}
 % Normal Coercion
@@
 
-	\caption{CEK abstract machine for the \lazyD{} Blame Calculus}
+	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} Blame 
+	Calculus}
 	\label{machine-cekc}
@@
 \figref{fig:normal-coercion} defines the normal coercion. 
+Types, pre-types, and blame labels are as before.
 Let $ I $ ranges over injectable types. An injectable type is a type that can 
@@
 
-Three observations on the definition leads to hyper-coercion: 
+Three observations on this definition leads to hyper-coercion: 
 \begin{enumerate}
@@
 \begin{figure}
+	Syntax
 	\[
 	\begin{array}{lclr}
+	\stxrule{I}{injectable types (\lazyD)}{P}
+	\stxrule{I}{injectable types (\lazyUD)}{
+		\POOunit \mid
+		\POOfun{\TOOdyn}{\TOOdyn} \mid
+		\POOprod{\TOOdyn}{\TOOdyn} \mid
+		\POOsum{\TOOdyn}{\TOOdyn}
+	}
 	\stxrule{c}{hyper-coercions}{
@@
 	}
-	\stxrule{\ell}{$ \mathtt{Maybe} \; l $}{
-		\epsilon \mid{}
-		l
-	}
-	\end{array}
-	\]
-
-	Shallow-consistency between middles
-	\fbox{$ m \smile m $}
-
-	%	Coercion typing \fbox{$ c : T \Longrightarrow T $}
-	%	\begin{gather*}
-	%	\inference{}{\typingHC{\hyperCoercionI}{\TOOdyn}{\TOOdyn}}
-	%	\quad
-	%	\inference{
-	%		\typingHC{h}{T_1}{P_1} &
-	%		\typingHC{m}{P_1}{P_2} &
-	%		\typingHC{t}{P_2}{T_2}
-	%	}{
-	%		\typingHC{\hyperCoercionC{h}{m}{t}}{T_1}{T_2}
-	%	}
-	%	\end{gather*}
-	%	
-	%	Head typing \fbox{$ \typingHC{h}{T}{P} $}
-	%	\begin{gather*}
-	%	\inference{}{\typingHC{\epsilon}{P}{P}}
-	%	\quad
-	%	\inference{}{\typingHC{?^l}{\TOOdyn}{P}}
-	%	\end{gather*}
-	%	
-	%	Middle typing \fbox{$ \typingHC{m}{P}{P} $}
-	%	\begin{gather*}
-	%	\inference{}{\typingHC{\POOunit}{\POOunit}{\POOunit}}
-	%	\\
-	%	\inference{
-	%		\typingHC{c_1}{T_3}{T_1} &
-	%		\typingHC{c_2}{T_2}{T_4}
-	%	}{
-	%		\typingHC{\POOfun{c_1}{c_2}}{\POOfun{T_1}{T_2}}{\POOfun{T_3}{T_4}}
-	%	}
-	%	\\
-	%	\inference{
-	%		\typingHC{c_1}{T_1}{T_3} &
-	%		\typingHC{c_2}{T_2}{T_4}
-	%	}{
-	%		
-	%\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
-	%	}
-	%	\\
-	%	\inference{
-	%		\typingHC{c_1}{T_1}{T_3} &
-	%		\typingHC{c_2}{T_2}{T_4}
-	%	}{
-	%		\typingHC{\POOsum{c_1}{c_2}}{\POOsum{T_1}{T_2}}{\POOsum{T_3}{T_4}}
-	%	}
-	%	\end{gather*}
-	%	
-	%	Tail typing \fbox{$ \typingHC{t}{P}{T} $}
-	%	\begin{gather*}
-	%	\inference{}{\typingHC{\epsilon}{P}{P}} \quad
-	%	\inference{}{\typingHC{!}{P}{\TOOdyn}} \quad
-	%	\inference{}{\typingHC{\bot^l}{P}{T}} \quad
-	%	\end{gather*}
-
-	\caption{Syntax of hyper-coercion}
+	\end{array}
+	\]
+
+	Hyper-coercion typing \fbox{$ c : T \Longrightarrow T $}
+	\begin{gather*}
+	\inference{}{\typingHC{\hyperCoercionI}{\TOOdyn}{\TOOdyn}}
+	\quad
+	\inference{
+		\typingHC{h}{T_1}{P_1} &
+		\typingHC{m}{P_1}{P_2} &
+		\typingHC{t}{P_2}{T_2}
+	}{
+		\typingHC{\hyperCoercionC{h}{m}{t}}{T_1}{T_2}
+	}
+	\end{gather*}
+
+	Head typing \fbox{$ \typingHC{h}{T}{P} $}
+	\begin{gather*}
+	\inference{}{\typingHC{\epsilon}{P}{P}}
+	\quad
+	\inference{}{\typingHC{?^l}{\TOOdyn}{I}}
+	\end{gather*}
+
+	Middle typing \fbox{$ \typingHC{m}{T}{T} $}
+	\begin{gather*}
+	\inference{}{\typingHC{\POOunit}{\POOunit}{\POOunit}}
+	\quad
+	\inference{
+		\typingHC{c_1}{T_3}{T_1} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOfun{c_1}{c_2}}{\POOfun{T_1}{T_2}}{\POOfun{T_3}{T_4}}
+	}
+	\\
+	\inference{
+		\typingHC{c_1}{T_1}{T_3} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOprod{c_1}{c_2}}{\POOprod{T_1}{T_2}}{\POOprod{T_3}{T_4}}
+	}
+	\quad
+	\inference{
+		\typingHC{c_1}{T_1}{T_3} &
+		\typingHC{c_2}{T_2}{T_4}
+	}{
+		\typingHC{\POOsum{c_1}{c_2}}{\POOsum{T_1}{T_2}}{\POOsum{T_3}{T_4}}
+	}
+		\end{gather*}
+
+		Tail typing \fbox{$ \typingHC{t}{P}{T} $}
+		\begin{gather*}
+		\inference{}{\typingHC{\epsilon}{P}{P}} \quad
+		\inference{}{\typingHC{!}{I}{\TOOdyn}} \quad
+		\inference{}{\typingHC{\bot^l}{P}{T}} \quad
+		\end{gather*}
+
+	\caption{Definition of Hyper-coercion (HC)}
 	\label{fig:hyper-coercion}
@@
 
-All definitions and results in this section are new.
-\figref{fig:hyper-coercion} defines the syntax of hyper-coercions.
-Terms, types, pre-types, blame labels, and observations are as before.
-
-Let $ c $ ranges over hyper-coercions. We re-use the meta-variable $ c $ to 
-stress that hyper-coercion is a cast representation. A hyper-coercion is either 
+This section presents our first contribution, hyper-coercion (HC). 
+\figref{fig:hyper-coercion} defines the syntax of HC.
+Types, pre-types, and blame labels are as before.
+
+Let $ c $ ranges over hyper-coercions. A hyper-coercion is either 
 an identity cast between the dynamic types, or a complex including a head, a 
 middle, and a tail. 
-Let $ h $ ranges over heads. A head is either a no-op, or a projection 
-decorated with a label, to which blame is allocated if the projection fails. 
+Let $ h $ ranges over heads. A head is either a no-op, or a projection.
 Let $ m $ ranges over middles. There is a one-to-one 
 correspondence between middles and type constructors. 
-We generalize shallow-consistency to include middles in the natural way.
+We generalize shallow-consistency to middles $ m \smile m $ in the natural way.
 Let $ t $ ranges over tails. A tail is either a no-op, an injection, or a 
@@
 \begin{figure}
+	\[
+	\begin{array}{rclr}
+	\stxrule{\ell}{Maybe $ l $}{\epsilon \mid l}
+	\end{array}
+	\]
+
 	Composition of hyper-coercions \fbox{$ c \fatsemi^\ell c = c $}
@@
 
-Functions that construct \lazyD{} hyper-coercions are shown in 
-\figref{fig:HC-D}.
+\lazyD{} HC constructors are in \figref{fig:HC-D}.
 
@@
 be a label.
-
 $ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 
@@
 $ m_2 $ might be different, in which case $ \ell $ must be a label.
-
 $ seq(c_1,c_2) $ composes two coercions where the target type of $ c_1 $ is 
 equal to the source type of $ T_2 $.
-
-$ id(T) $ constructs an identity coercion of $ T $.
-
+$ id(T) $ constructs an identity coercion of $ T $ with the help of $ id(P) $.
 $ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
@@
 
-\begin{proposition}[Hyper-coercions form a Monoid]
+\begin{proposition}[\lazyD\ Hyper-coercions is a Monoid]
 	For all $c : T_1 \Longrightarrow T_2$,
@@
 
-To show that hyper-coercion is a correct cast representation, we introduce an 
-hyper-coercion-based machine for the \lazyD\ blame calculus, and show that it 
-bi-simulates the previous machine.
-
-The machine depends on four functions that consumes and/or construct 
-hyper-coercions: $ id(T) $, $ seq(c,c) $, $ cast(T,l,T) $, and $ applyCast(T,v) 
-$. The first three are described above. We will show $ applyCast $ shortly.
-
-Some reader might have noticed that the machine is representation-independent 
-w.r.t cast. That being said, if some people want to use normal coercion instead 
-of hyper-coercion, they can implement the normal coercion version of the four 
-functions mentioned aboved and get another abstract machine. We capture the 
-idea of ``abstract cast'' by the following definition.
-
-\subsection{Correctness of \lazyD{} Hyper-coercions}
-
-One of our major contributions is for all cast presentation, if it is proper, 
-then it is correct.
-
-\begin{proposition}[proper cast represenations are correct]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a proper cast 
-	representation
-	\[
-	e \Downarrow_{D,B} o \; \text{if and only if} \; 
-	e \Downarrow_{D,P(C)} o
-	\]
-\end{proposition}
-
-Perhaps unsurprisingly, hyper-coercion is correct.
-
-\begin{lemma}[\lazyD{} Hyper-coercion is a proper cast representation]
-	See appendix.
-\end{lemma}
-
-\begin{theorem}[\lazyD{} hyper-coercion is correct]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
-	\[
-	e \Downarrow_{D,B} o \; \text{if and only if} \; 
-	e \Downarrow_{D,P(H)} o
-	\]
-\end{theorem}
-
-\figref{hc-applyCast} defines $ applyCast $. Applying the identity cast for the 
-dynamic type succeeds immediately. When applying a compound cast, we firstly 
-apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
-that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
-is the failure.
-$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
-
-\begin{figure}
-	\fbox{$ applyCast(c,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
-	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
-		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
-		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$ applyMiddle(\ell,m,v) = v $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
-	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
-		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
-		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
-		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
-		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,m,v)}{
-		\rOOfail{l}
-	}{
-		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
-	}
-	\end{array}
-	\]
-
-	\fbox{$ applyTail(t,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
-	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
-	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
-	\end{array}
-	\]
-	\caption{Applying hyper-coercions to values}
-	\label{hc-applyCast}
-\end{figure}
+The correctness proof of \lazyD\ HC is deferred to \secref{sec:LDHC-correct} 
+because it relies on the space-efficient CEK abstract machine in 
+\secref{sec:CEKS}.
 
@@
 \section{Space-efficient CEK Abstract Machine}
-
-[move the definition of the generic machine here -Jeremy]
-
-All definitions and results in this section are new.
-
-We present a space-efficient CEK machine for blame calculi. This machine is
-parameterized over cast representation.
+\label{sec:CEKS}
+
+This section presents our second contribution, a space-efficient CEK abstract 
+machine. This machine is parameterized over \emph{cast representation} (CR).
 
@@
 
-	Reduction \fbox{$ s \longrightarrow_{S(C)} s $}
+	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
 	\[
@@
 
-	Evaluation \fbox{$ e \Downarrow_{S(C)} o $}
-	\[
-	\inference{
-		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{S(C)}^{*} 
+	Evaluation \fbox{$ \judgeSeval{C}{e}{o} $}
+	\[
+	\inference{
+		\judgeSreduceTrans{C}{
+			\sOOinspect{e}{\emptyset}{cont(\hckOOmt)}
+		}{
 			\sOOhalt{o}
-	}{
-		e \Downarrow_{S(C)} o
-	}
-	\]
-
-	\caption{A space-efficient CKE machine for Blame Calculus.}
+		}		
+	}{
+		\judgeSeval{C}{e}{o}
+	}
+	\]
+
+	\caption{Space-efficient CEK machine $ \mathcal{S}(C) $}
 	\label{machine-cekcc}
@@
 \figref{machine-cekcc} defines the machine. 
-Let $ v $ ranges over value. We push casts into values. For instance, function 
-values now include two more components: a cast for argument and a cast for the 
-output. The last kind of values is injection to $ \TOOdyn $. 
+Let $ v $ ranges over value. A value is either the unit value, function, pair, 
+left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
 Cast results ($ r $) and machine states ($ s $) are as before. 
@@
 pre-continuations. 
-A continuation is now a pair whose first part is a cast, and whose second part 
-is a pre-continuation. 
+A continuation is now a pair where the first part is a cast and the second 
+part is a pre-continuation. 
 Pre-continuation are like the continuations before.
@@
 
-Transitive closure of reduction and evaluation are standard.
-
-\subsection{\lazyD\ Cast Representations}
-
-We show that all \textit{proper} cast representations are 
-equivalent.
-
-\begin{definition}[Proper Cast Representation]
-	A cast representation is proper if
+Transitive closure of reduction ($ \judgeSreduceTrans{C}{s}{s} $) and 
+evaluation are standard. Value typing ($ \judgeType{v}{T} $) is straightforward.
+
+\section{\lazyD\ Cast Representations}
+
+In this section we describe a subset of SR, where all 
+elements implement the \lazyD{} blame strategy. We will show in 
+\secref{sec:LDHC-correct} that the \lazyD\ HC is a member of this set.
+
+\begin{definition}[Surely \lazyD]
+	A cast representation is surely \lazyD\ if
 	\begin{enumerate}
 		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
-		\item If $ v : T_1 $,
-		$ c_1 $ is from $ T_1 $ to $ T_2 $, and 
-		$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
-		then $ applyCast(seq(c_1,c_2),v) = applyCast(c_1,v) >>= \lambda 
-		v.applyCast(c_2,v) $
+		\item If $ \judgeType{v}{T_1} $,
+				 $ \judgeTypeFT{c_1}{T_1}{T_2} $, and
+				 $ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
+		then $ applyCast(seq(c_1,c_2),v) = 
+			   applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
+		where 
+		\[
+		\begin{array}{rcl}
+			\rOOsucc{v} >>= f & = & f(v) \\
+			\rOOfail{l} >>= f & = & \rOOfail{l}
+		\end{array}
+		\]
 		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
@@
 		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \iota $,
+		\item If $ v : \POOunit $,
 		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
-		\item $ 
+		\item
+		$ 
 		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
@@
 
-With the properties of proper cast representation, it is straightforward to 
-proof that all machines instantiated with a proper cast representation are 
-strongly bi-simulated.
-
-\begin{theorem}[Strong Bi-simulation of Proper Cast Representations]
-	If $ C_1 $ and $ C_2 $ are proper cast representations,
-	$ s_1 $ and $ s_2 $ are states of $ S(C_1) $,
-	$ s_3 $ is an state of $ S(C_2) $,
-	$ s_1 \longrightarrow_{S(C_1)} s_2 $,
-	and $ s_1 \approx s_3 $, \\
-	then there exists an $ s_4 $ such that $ s_3 \approx s_4 $ and
-	$ s_3 \longrightarrow_{S(C_2)} s_4 $
-\end{theorem}
+\subsection{All surely \lazyD{} cast representations are equivalents}
+
+With the properties of surely \lazyD{} CR, it is straightforward to proof that 
+all machines instantiated with these CRs bi-simulate each other. 
+The relation connecting states of these machines ($ s \approx s $) is derived 
+from the definition of states. \begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2 &
+	v_1 \approx v_2
+}{
+	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+}
+\quad
+\inference{
+}{
+	\sOOhalt{o} \approx \sOOhalt{o}
+}
+\end{gather*}
+
+The relations between continuations, pre-continuations, enviroments, values, 
+cast results are also derived from their definitions. But the relation for 
+casts is special. \begin{gather*}
+\inference{
+}{
+	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
+}
+\quad
+\inference{
+}{
+	id_1(T) \approx id_2(T)
+}
+\quad
+\inference{
+	c_1 \approx c_2 &
+	c_3 \approx c_4
+}{
+	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
+}
+\end{gather*}
+
+\begin{proposition}[Strong Bi-simulation of surely \lazyD{} Cast 
+Representations]
+	If 
+	\begin{itemize}
+		\item $ C_1 $ and $ C_2 $ are surely \lazyD,
+		\item $ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $
+		\item $ s_1 \approx s_3 $
+		\item $ \judgeSreduce{C_1}{s_1}{s_2} $
+	\end{itemize}
+	then there exists an $ s_4 $ such that
+	\begin{itemize}
+	\item $ s_3 \approx s_4 $ and
+	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
+	\end{itemize}
+\end{proposition}
+
+The key idea of this proof is using the property (2) of surely 
+\lazyD{} CR to undo sequencing. Property (3)-(11) cover all possibly uses of $ 
+cast(T,l,T) $.
 
@@
 
-\begin{theorem}[proper cast represenations are equivalent]
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and that $ C_1 $ and $ C_2 $ 
-	are 
-	proper cast representations
+\begin{proposition}[Equivalence of surely \lazyD{} Cast Representations]
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+	are surely \lazyD,
 	\[
@@
 	e \Downarrow_{S(C_2)} o
+	\]
+\end{proposition}
+
+\subsection{Relating Surely \lazyD\ Cast Representations to $ \mathcal{D} $}
+
+Now we proof that all $ 
+\mathcal{S}(\cdot) $ instantiated with a surely \lazyD{} CR weakly bi-simulate 
+the machine $ \mathcal{D} $.
+
+\todo[inline]{list of cast}
+
+\begin{proposition}[proper cast represenations are correct]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a surely 
+	\lazyD{} cast 
+	representation
+	\[
+	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeSeval{C}{e}{o}
+	\]
+\end{proposition}
+
+\section{Correctness Proof of \lazyD{} Hyper-coercions}
+\label{sec:LDHC-correct}
+
+To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
+uses the theorems in \secref{sec:CEKS} to prove our goals.
+
+\figref{hc-applyCast} defines $ applyCast $, the last interface function.
+We generalize shallow-consistency to middles and values $ m \smile v $ in the 
+natural way.
+Applying the identity cast for the 
+dynamic type succeeds immediately. When applying a compound cast, we firstly 
+apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
+that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
+is the failure.
+$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
+
+\begin{figure}
+	\fbox{$ applyCast(c,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
+	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
+		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
+		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ applyMiddle(\ell,m,v) = v $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
+	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
+		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
+		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
+		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
+		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,m,v)}{
+		\rOOfail{l}
+	}{
+		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
+	}
+	\end{array}
+	\]
+
+	\fbox{$ applyTail(t,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
+	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
+	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
+	\end{array}
+	\]
+	\caption{\lazyD\ Hyper-coercion's $ applyCast $}
+	\label{hc-applyCast}
+\end{figure}
+
+\begin{lemma}[\lazyD{} Hyper-coercion is surely \lazyD]
+	See appendix.
+\end{lemma}
+
+\begin{theorem}[\lazyD{} hyper-coercion is correct]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
+	\[
+	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeSeval{H}{e}{o}
 	\]

### 2019-10-15 paper.tex
revise intro

@@
 Blame Calculus throws a blame label when a runtime type-check fails.
-These labels can include useful information on the failed cast, for example, 
-its location in the source code.
-
-Implementing gradually typed languages naively on top of blame calculus 
-suffices sever space leak.
-For example, translation to Blame Calculus can wrap some expressions with a 
-cast, including those at tail position. Thus, at runtime, mutually 
-tail-recursive functions in source language can accumulate unbounded space. 
-There are more examples in \citet{herman2010space}.
+Labels provide useful debugging information, therefore are necessary for 
+practical use of gradually typed languages.
+
+Implementing gradually typed languages naively on top of blame calculus, 
+however, suffices sever space leak.
+For example, translation to Blame Calculus can wrap some expressions with code 
+that performs runtime type-checking (casts), including those expressions at 
+tail position. Thus, mutually tail-recursive functions in source language can 
+consume unbounded space at runtime. There are more examples of space leaking in 
+\citet{herman2010space}.
 
 In 2007, \citet{herman2010space} proposes a solution to this problem by 
-translating Blame Calculus to a variant of \citet{henglein1994dynamic}'s 
-Coercion Calculus. Their key idea is to represent casts with coercions, 
+representing casts with coercion \cite{henglein1994dynamic}, 
 which can be composed and normalized. Every coercion looks like a list of 
 trees. For normal coercion, the length of the list is bounded by a small 
-constant. And the depths of trees do not grow in composition and 
+constant. And the depths of trees do not grow during composition and
 normalization. These two facts implies that coercion is a space-efficient cast 
-representation. This Coercion Calculus, however, does not support blame 
+representation. This coercion, however, does not support blame 
 tracking.
@@
 
-\citet{siek2009exploring} incorporate blame tracking into 
-\citet{herman2010space}'s Coercion Calculus by 
-decorating coercions with labels. They also propose that there are four blame 
-strategies for their Coercion Calculi:
+\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions with 
+labels to restore 
+blame-tracking. They also propose that there are four blame 
+strategies for their coercion:
 $ \{Lazy, Eager\} \times \{D, UD\} $. 
 Eager strategies detect more potential type errors, 
-but also blame more programs.
+but blame more programs.
 $ D $ and $ UD $ assign blame labels differently.
-They prove partially that the \lazyUD{} Coercion Calculus is correct by showing 
+They prove partially that their \lazyUD{} coercion is correct by showing 
 that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
@@
 \citet{siek2010threesomes} proposes another approach to combine blame 
-tracking and space efficiency. Their solution is based on Threesome Calculus. 
-Their key idea is to represent casts with threesomes, a novel cast 
-representation.
-%Threesomes can also be composed. Unlike coercions, there is no 
-%separate normalization because every threesome is in normal form. 
-They show that their threesome calculus bi-simulates the \lazyUD{} Coercion 
-Calculus in \citet{siek2009exploring} and the Blame Calculus in 
+tracking and space efficiency. Their solution represents casts with threesomes, 
+a novel cast representation.
+They show that their calculus bi-simulates the \lazyUD{} coercion 
+calculus in \citet{siek2009exploring} and the Blame Calculus in 
 \citet{wadler2009well}. They also prove that threesome is space-efficient as 
@@
 \citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
-revised lazy Coercion Calculi.
-They simplify the Coercion Calculi by only 
+revised coercion calculi.
+They simplify the coercion calculi by only 
 working with normal coercions (i.e. coercions in normal form). 
-%Fortunately, coercions are trivially normal when initially constructed, and 
-%their empowered compose function is conjectured to produces normal coercions 
-%as well. 
-They conjecture that their Coercion Calculi bi-simulate the corresponding Blame 
-Calculi.
-
-Following \citet{siek2010threesomes}, \citet{garcia2013calculating} discovers
-Threesome Calculi for other blame strategies. After studying the relation 
+They conjecture that their revised coercion calculi bi-simulate the 
+corresponding Blame Calculi.
+
+Following \citet{siek2010threesomes}, \citet{garcia2013calculating} develops
+threesome for other blame strategies. After studying in depth the relation 
 between coercion and threesome,
@@
 but hard to understand. 
-His claim is partially affirmed by the group of people who develop threesome 
+His claim is mostly affirmed by the group of people who develop threesome 
 (\citet{siek2015blame}).
-His threesome calculi are equivalent to the Coercion Calculi in 
+His threesome calculi are equivalent to the coercion calculi in 
 \citet{siek2009exploring} because the former ones are derived from the latter 
@@
 \citet{siek2015blame} revisit the coercion-based approach. They revise the 
-\lazyUD{} Coercion Calculus in \citet{siek2012interpretations} and prove that 
+\lazyUD{} coercion in \citet{siek2012interpretations} and prove that 
 their revised coercion calculus bi-simulates the \lazyUD{} Blame Calculus.
@@
 gradually typed language of the same name. 
-This implementation is based on the \lazyD{} Coercion Calculus in 
+This implementation is based on the \lazyD{} coercion in 
 \citet{siek2012interpretations}.
@@
 
-So far, it seems that the coercion-based approach is the best way to combine 
+So far, it seems that normal coercion is the best way to combine 
 space-efficiency and blame-tracking: normal coercion is claimed easy to 
@@
 easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
-Normal coercion is still not satisfactory, however, in at least three aspects.
+Normal coercion is still not satisfactory, however, in at least two aspects.
 Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
@@
 of coercion: all coercions are normal when they are initially constructed, and 
-\citet{siek2012interpretations} have shown that there exist functions that 
-compose and produce normal coercions.
+\citet{siek2012interpretations} have shown an function that 
+composes and produces normal coercions.
 
@@
 Super-coercion introduced in \citet{garcia2013calculating} could be a promising 
-candidate. However, its definition is a bit complicated. It uses 10 
-constructors to deal with an elementary type system with only base types and 
+candidate. It is believed even more complicated than threesome 
+\cite{siek2015blame}. In fact, it uses 10 constructors to deal with an 
+elementary type system with only base types and 
 function types. And four constructors are directly related to function types. 
@@
 \ref{sec:hyper-coercion}.
-
 Our hyper-coercion considers sum types and product types, which are not 

### 2019-10-15 paper.tex
progress

@@
 a novel cast representation.
-They show that their calculus bi-simulates the \lazyUD{} coercion 
+They show that their calculus bisimulates the \lazyUD{} coercion 
 calculus in \citet{siek2009exploring} and the Blame Calculus in 
@@
 		\POOsum{id(T_1)}{id(T_2)}
-	}{}s
+	}{}
 	\end{array}
@@
 
-UNDER CONSTRUCTION
+Figure~\ref{fig:HC-UD}
+
+\begin{figure}
+  Composition of hypercoercions \fbox{$ c \fatsemi c = c $}
+  \[
+  \begin{array}{rclclr}
+  c &\fatsemi& \hyperCoercionI{} &=& c\\
+  \hyperCoercionI{} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
+       \hyperCoercionC{p_2}{m_2}{i_2} \\
+  \hyperCoercionC{p_1}{m_1}{\epsilon} &\fatsemi& \hyperCoercionC{\epsilon}{m_2}{i_2} &=&
+       \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} \\
+  \hyperCoercionC{p_1}{m_1}{!} &\fatsemi& \hyperCoercionC{?^l}{m_2}{i_2} &=&
+  \begin{cases}
+    \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} & \text{if } m_1 \smile m_2 \\
+    \hyperCoercionC{p_1}{m_1}{\bot^l} & \text{otherwise}
+  \end{cases} \\
+  \hyperCoercionC{p_1}{m_1}{\bot^l} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
+     \hyperCoercionC{p_1}{m_1}{\bot^l}
+  \end{array}
+  \]
+  Composition of middles \fbox{$m \fatsemi m = m$}
+  \[
+  \begin{array}{rclclr}  
+  \POOunit &\fatsemi& \POOunit &=& \POOunit \\
+  c \to d &\fatsemi& c' \to d' &=& (c' \fatsemi c) \to (d \fatsemi d') \\
+  c \times d &\fatsemi& c' \times d' &=& (c \fatsemi c') \times (d \fatsemi d') \\
+  c + d &\fatsemi& c' + d' &=& (c \fatsemi c') + (d \fatsemi d')
+  \end{array}
+  \]
+  Shallow consistency of middles \fbox{$m \smile m$}
+  \[
+  \POOunit \smile \POOunit \quad
+  (c \to d) \smile (c' \to d') \quad
+  (c \times d) \smile (c' \times d') \quad
+  (c + d) \smile (c' + d')
+  \]
+
+  \fbox{$seq(c,c) = c$}
+  \[
+  \begin{array}{rclr}
+    \funrule{seq(c_1,c_2)}{
+      c_1 \fatsemi c_2
+    }{}
+  \end{array}
+  \]
+
+  \fbox{$ id( P ) = m $}
+  \[
+  \begin{array}{rclr}
+    \funrule{id(\POOunit)}{\POOunit}{}
+    \funrule{id(\POOfun{T_1}{T_2})}{
+		\POOfun{id(T_1)}{id(T_2)}
+    }{}
+    \funrule{id(\POOprod{T_1}{T_2})}{
+		\POOprod{id(T_1)}{id(T_2)}
+    }{}
+    \funrule{id(\POOsum{T_1}{T_2})}{
+		\POOsum{id(T_1)}{id(T_2)}
+    }{}
+  \end{array}
+  \]
+
+  \fbox{$ id( T ) = c $}
+  \[
+  \begin{array}{rclr}
+    \funrule{id(\star)}{
+		\hyperCoercionI
+    }{}
+    \funrule{id(P)}{
+		\hyperCoercionC{\epsilon}{id(P)}{\epsilon}
+    }{}
+  \end{array}
+  \]
+
+  \caption{Lazy UD Hypercoercions}
+  \label{fig:HC-UD}
+\end{figure}
+
+\begin{figure}
+  \fbox{$ \mathit{castToDyn}(P,l) = c$}
+  \[
+  \begin{array}{rclr}
+    \funrule{\mathit{castToDyn}(\star,l,\star)}{ \hyperCoercionI{} }{} 
+    \funrule{\mathit{castToDyn}(I,l,\star)}{
+      \hyperCoercionC{\epsilon}{\mathit{castToInj}(I,l,I) }{!}
+    }{}
+    \funrule{\mathit{castToDyn}(P,l,\star)}{
+      \hyperCoercionC{\epsilon}{\mathit{castToInj}(P,l,I) }{!}
+    }{}
+  \end{array}
+  \]
+
+  \fbox{$ \mathit{castFromDyn}(P,l) = c$}
+
+  \fbox{$ \mathit{castToInj}(P,l,I) = m$}
+
+  \fbox{$ \mathit{castFromInj}(I,l,P) = m$}
+
+  \fbox{$ cast(T,l,T) = c$}
+  \[
+  \begin{array}{rclr}
+    \funrule{cast(\star,l,T_2)}{ castFromDyn(T_2, l) }{} 
+    \funrule{cast(T_1,l,\star)}{ castToDyn(T_2, l) }{} 
+    \funrule{cast(\POOunit,l,\POOunit)}{
+        \hyperCoercionC{\epsilon}{\POOunit}{\epsilon} }{} 
+    cast(T_1 \to T_2,l, T_3 \to T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        \to
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_3, l, T_1) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
+    cast(T_1 \times T_2,l, T_3 \times T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        \times
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
+    cast(T_1 + T_2,l, T_3 + T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        +
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)
+  \end{array}
+  \]
+
+  \caption{\textit{cast} and auxilliary functions for Lazy UD.}
+  \label{fig:HC-UD-cast}
+\end{figure}
 

### 2019-10-16 paper.tex
a bit more progress
acm stuff
KC almost finishes his part

--- 2019-10-15 paper.tex
@@
 \newtheorem{theorem}{Theorem}[]
+\newtheorem{lemma}{Lemma}[section]
 \newtheorem{proposition}{Proposition}[]
-\newtheorem{corollary}{Corollary}[]
 \newtheorem{definition}{Definition}
@@
 \newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
+% machine state simulations
+\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
+\newcommand{\eqvDS}[3]{#2 \approx_{\mathcal{DS}} #3}
 
@@
 \begin{definition}[Cast Representation]
-	A cast representation has four interface functions:
+	A cast representation is a set indexed by two types and has four interface 
+	functions:
 	\begin{description}
@@
 	\end{description}
+\end{definition}
+
+\begin{definition}[Monoidic Cast Representation]
+	A cast representation is monoidic if 
+	for all $c : T_1 \Longrightarrow T_2$,
+	$c_1 : T_1 \Longrightarrow T_2$,
+	$c_2 : T_2 \Longrightarrow T_3$, and
+	$c_3 : T_3 \Longrightarrow T_4$,
+	\begin{enumerate}
+		\item $seq(id(T_1),c) = c$,
+		\item $seq(c,id(T_2)) = c$, and
+		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
+	\end{enumerate}
 \end{definition}
@@
 
-\section{\lazyD\ Cast Representations}
+\section{Correctness Proof of \lazyD{} Hyper-coercions}
+
+\subsection{\lazyD\ Cast Representations}
 
@@
 elements implement the \lazyD{} blame strategy. We will show in 
-\secref{sec:LDHC-correct} that the \lazyD\ HC is a member of this set.
-
-\begin{definition}[Surely \lazyD]
+Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.
+
+\begin{definition}[Surely \lazyD\ Cast Representation]
 	A cast representation is surely \lazyD\ if
@@
 
-\subsection{All surely \lazyD{} cast representations are equivalents}
+\subsection{Relating All Surely \lazyD{} Cast Representations}
 
@@
 all machines instantiated with these CRs bi-simulate each other. 
-The relation connecting states of these machines ($ s \approx s $) is derived 
-from the definition of states. \begin{gather*}
+The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+derived from the definition of states. We omit subscripts when there is no 
+ambiguity. \begin{gather*}
 \inference{
@@
 cast results are also derived from their definitions. But the relation for 
-casts is special. \begin{gather*}
+casts is special: \begin{gather*}
 \inference{
@@
 
-\begin{proposition}[Strong Bi-simulation of surely \lazyD{} Cast 
-Representations]
+\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
+	\label{thm:CEKS-bisim}
 	If 
-	\begin{itemize}
-		\item $ C_1 $ and $ C_2 $ are surely \lazyD,
-		\item $ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $
-		\item $ s_1 \approx s_3 $
-		\item $ \judgeSreduce{C_1}{s_1}{s_2} $
-	\end{itemize}
+	$ C_1 $ and $ C_2 $ are surely \lazyD,
+	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
+	$ s_1 \approx s_3 $,
+	$ \judgeSreduce{C_1}{s_1}{s_2} $,
 	then there exists an $ s_4 $ such that
 	\begin{itemize}
-	\item $ s_3 \approx s_4 $ and
+	\item $ s_2 \approx s_4 $ and
 	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
@@
 \end{proposition}
-
-The key idea of this proof is using the property (2) of surely 
-\lazyD{} CR to undo sequencing. Property (3)-(11) cover all possibly uses of $ 
-cast(T,l,T) $.
-
-As a corollary, machines instantiated with proper cast representations are 
-equivalent when used as interpreters.
-
-\begin{proposition}[Equivalence of surely \lazyD{} Cast Representations]
+\begin{proof}
+	The key ideas of this proof are undoing sequencing with the property (2) of 
+	surely \lazyD{} CR, and handling all possibly uses of $ 
+	cast(T,l,T) $ with property (3)-(11).
+\end{proof}
+
+\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+	\label{thm:surely-lazyD-eqv}
 	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-	are surely \lazyD,
+	are surely \lazyD cast representations,
 	\[
@@
 \end{proposition}
-
-\subsection{Relating Surely \lazyD\ Cast Representations to $ \mathcal{D} $}
-
-Now we proof that all $ 
-\mathcal{S}(\cdot) $ instantiated with a surely \lazyD{} CR weakly bi-simulate 
-the machine $ \mathcal{D} $.
-
-\todo[inline]{list of cast}
-
-\begin{proposition}[proper cast represenations are correct]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a surely 
-	\lazyD{} cast 
-	representation
+\begin{proof}
+	Immediately from Proposition~\ref{thm:CEKS-bisim}.
+\end{proof}
+
+\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
+
+So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
+each other. But this does not mean they respect the semantics of the \lazyD{} 
+Blame Calculus. We solve prove this part in this subsection.
+
+The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
+definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
+between continuations, between values, and from continuations to 
+pre-continuations.
+
+\todo[inline]{bisimilarity}
+
+\begin{lemma}[Weak Bi-simulation between $ \mathcal{S}(\cdot) $ and $ 
+\mathcal{D} $]
+\label{thm:surely-monoidic-reduce}
+For all cast representations $ C $, 
+if $ C $ is surely \lazyD{} and monoidic,
+$ s_1 \in \mathcal{D} $,
+$ s_2 \in \mathcal{S}(C) $, and
+$ s_1 \approx s_2 $, 
+\begin{enumerate}
+	\item If $ \judgeDBreduce{s_1}{s_3} $,
+	then
+	there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
+	such that \begin{itemize}
+		\item $ s_5 \approx s_4 $, and
+		\item $ \judgeSreduce{C}{s_2}{s_4} $,
+		\item $ \judgeDBreduceTrans{s_3}{s_5} $
+	\end{itemize}
+	\item If $ \judgeSreduce{C}{s_2}{s_4} $,
+	then
+	there exist $ s_3 \in \mathcal{D} $,
+	such that \begin{itemize}
+		\item $ s_3 \approx s_4 $
+		\item $ \judgeDBreduceTrans{s_1}{s_3} $
+	\end{itemize}
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+	See the supplementary material.
+\end{proof}
+
+\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
+$ \mathcal{D} $]
+	\label{thm:surely-monoidic-eval}
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
+	\lazyD{} and monoidic,
 	\[
@@
 	\]
-\end{proposition}
-
-\section{Correctness Proof of \lazyD{} Hyper-coercions}
+\end{lemma}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
+\end{proof}
+
+\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
+	$ \mathcal{D} $]
+	\label{thm:surely-lazyD-correct}
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
+	\lazyD{}
+\[
+\judgeDBeval{e}{o} \; \text{if and only if} \; 
+\judgeSeval{C}{e}{o}
+\]
+\end{theorem}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
+	Proposition~\ref{thm:surely-lazyD-eqv}.
+\end{proof}
+
+\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
 \label{sec:LDHC-correct}
@@
 To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
-uses the theorems in \secref{sec:CEKS} to prove our goals.
+uses the Theorem~\ref{thm:surely-lazyD-correct} to prove its correctness.
 
 \figref{hc-applyCast} defines $ applyCast $, the last interface function.
-We generalize shallow-consistency to middles and values $ m \smile v $ in the 
+We generalize shallow-consistency to middles and values ($ m \smile v $) in the 
 natural way.
@@
 
-\begin{lemma}[\lazyD{} Hyper-coercion is surely \lazyD]
-	See appendix.
+\begin{lemma}[\lazyD{} Hyper-coercion is Surely \lazyD]
+	\label{thm:hc-surely-lazyD}
 \end{lemma}
-
-\begin{theorem}[\lazyD{} hyper-coercion is correct]
+\begin{proof}
+	See the supplementary material.
+\end{proof}
+
+\begin{theorem}[\lazyD{} Hyper-coercion Respect $ \mathcal{D} $]
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
@@
 \end{theorem}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:hc-surely-lazyD} and 
+	Theorem~\ref{thm:surely-lazyD-correct}.
+\end{proof}
 

### 2019-10-16 paper.tex

@@
 
-\newtheorem{theorem}{Theorem}[]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{proposition}{Proposition}[]
-\newtheorem{definition}{Definition}
+%\newtheorem{theorem}{Theorem}[]
+%\newtheorem{lemma}{Lemma}[section]
+%\newtheorem{proposition}{Proposition}[]
+%\newtheorem{definition}{Definition}
 
@@
 
+\begin{figure}
+
+  \fbox{$\mathit{applyCast}(v,c) = r$}
+  \[
+  \begin{array}{rclr}
+    \mathit{applyCast}(v,c) = r
+  \end{array}
+  \]
+
+\end{figure}
+
 \section{Background: Normal Coercion} \label{sec:coercion-calculus}
@@
 
-UNDER CONSTRUCTION
+Figure~\ref{fig:HC-UD}
+
+\begin{figure}
+  Composition of hypercoercions \fbox{$ c \fatsemi c = c $}
+  \[
+  \begin{array}{rclclr}
+  c &\fatsemi& \hyperCoercionI{} &=& c\\
+  \hyperCoercionI{} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
+       \hyperCoercionC{p_2}{m_2}{i_2} \\
+  \hyperCoercionC{p_1}{m_1}{\epsilon} &\fatsemi& \hyperCoercionC{\epsilon}{m_2}{i_2} &=&
+       \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} \\
+  \hyperCoercionC{p_1}{m_1}{!} &\fatsemi& \hyperCoercionC{?^l}{m_2}{i_2} &=&
+  \begin{cases}
+    \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} & \text{if } m_1 \smile m_2 \\
+    \hyperCoercionC{p_1}{m_1}{\bot^l} & \text{otherwise}
+  \end{cases} \\
+  \hyperCoercionC{p_1}{m_1}{\bot^l} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
+     \hyperCoercionC{p_1}{m_1}{\bot^l}
+  \end{array}
+  \]
+  Composition of middles \fbox{$m \fatsemi m = m$}
+  \[
+  \begin{array}{rclclr}  
+  \POOunit &\fatsemi& \POOunit &=& \POOunit \\
+  c \to d &\fatsemi& c' \to d' &=& (c' \fatsemi c) \to (d \fatsemi d') \\
+  c \times d &\fatsemi& c' \times d' &=& (c \fatsemi c') \times (d \fatsemi d') \\
+  c + d &\fatsemi& c' + d' &=& (c \fatsemi c') + (d \fatsemi d')
+  \end{array}
+  \]
+  Shallow consistency of middles \fbox{$m \smile m$}
+  \[
+  \POOunit \smile \POOunit \quad
+  (c \to d) \smile (c' \to d') \quad
+  (c \times d) \smile (c' \times d') \quad
+  (c + d) \smile (c' + d')
+  \]
+
+  \fbox{$seq(c,c) = c$}
+  \[
+  \begin{array}{rclr}
+    \funrule{seq(c_1,c_2)}{
+      c_1 \fatsemi c_2
+    }{}
+  \end{array}
+  \]
+
+  \fbox{$ id( P ) = m $}
+  \[
+  \begin{array}{rclr}
+    \funrule{id(\POOunit)}{\POOunit}{}
+    \funrule{id(\POOfun{T_1}{T_2})}{
+		\POOfun{id(T_1)}{id(T_2)}
+    }{}
+    \funrule{id(\POOprod{T_1}{T_2})}{
+		\POOprod{id(T_1)}{id(T_2)}
+    }{}
+    \funrule{id(\POOsum{T_1}{T_2})}{
+		\POOsum{id(T_1)}{id(T_2)}
+    }{}
+  \end{array}
+  \]
+
+  \fbox{$ id( T ) = c $}
+  \[
+  \begin{array}{rclr}
+    \funrule{id(\star)}{
+		\hyperCoercionI
+    }{}
+    \funrule{id(P)}{
+		\hyperCoercionC{\epsilon}{id(P)}{\epsilon}
+    }{}
+  \end{array}
+  \]
+
+  \caption{Lazy UD Hypercoercions}
+  \label{fig:HC-UD}
+\end{figure}
+
+Figure~\ref{fig:HC-UD-cast}
+
+\begin{figure}
+  \fbox{$ \mathit{castToDyn}(P,l) = c$}
+  \[
+  \begin{array}{rclr}
+    \mathit{castToDyn}(\star,l) &=& \hyperCoercionI{} \\
+    \mathit{castToDyn}(P,l) &=&
+      \hyperCoercionC{\epsilon}{m}{!} \\
+    && \text{where } m = \mathit{castToInj}(P,l,\mathit{ground}(P)) 
+  \end{array}
+  \]
+  \fbox{$ \mathit{castFromDyn}(P,l) = c$}
+  \[
+  \begin{array}{rclr}
+    \mathit{castFromDyn}(\star,l) &=& \hyperCoercionI{} \\
+    \mathit{castFromDyn}(P,l) &=& \hyperCoercionC{?^l}{m}{\epsilon} \\
+    && \text{where } m = \mathit{castFromInj}(\mathit{ground}(P),l,P) 
+  \end{array}
+  \]
+  \fbox{$ \mathit{castToInj}(P,l,I) = m$}
+  \[
+  \begin{array}{rclr}
+    \mathit{castToInj}(\POOunit,l,\POOunit) &=& \POOunit \\
+    \mathit{castToInj}(T_1 \to T_2,l, \star \to \star) &=&
+        \mathit{castFromDyn}(T_1,l) \to \mathit{castToDyn}(T_2,l) \\
+    \mathit{castToInj}(T_1 \times T_2,l, \star \times \star) &=&
+        \mathit{castToDyn}(T_1,l) \times \mathit{castToDyn}(T_2,l) \\
+    \mathit{castToInj}(T_1 + T_2,l, \star + \star) &=&
+        \mathit{castToDyn}(T_1,l) + \mathit{castToDyn}(T_2,l) \\
+  \end{array}
+  \]
+
+  \fbox{$ \mathit{castFromInj}(I,l,P) = m$}
+  \[
+  \begin{array}{rclr}
+    \mathit{castFromInj}(\POOunit,l,\POOunit) &=& \POOunit \\
+    \mathit{castFromInj}(\star \to \star,l, T_1 \to T_2) &=&
+        \mathit{castToDyn}(T_1,l) \to \mathit{castFromDyn}(T_2,l) \\
+    \mathit{castFromInj}(\star \times \star,l, T_1 \times T_2) &=&
+        \mathit{castFromDyn}(T_1,l) \times \mathit{castFromDyn}(T_2,l) \\
+    \mathit{castFromInj}(\star + \star,l, T_1 + T_2) &=&
+        \mathit{castFromDyn}(T_1,l) + \mathit{castFromDyn}(T_2,l) \\
+  \end{array}
+  \]
+
+  \fbox{$ cast(T,l,T) = c$}
+  \[
+  \begin{array}{rclr}
+    \funrule{cast(\star,l,T_2)}{ castFromDyn(T_2, l) }{} 
+    \funrule{cast(T_1,l,\star)}{ castToDyn(T_1, l) }{} 
+    \funrule{cast(\POOunit,l,\POOunit)}{
+        \hyperCoercionC{\epsilon}{\POOunit}{\epsilon} }{} 
+    cast(T_1 \to T_2,l, T_3 \to T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        \to
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_3, l, T_1) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
+    cast(T_1 \times T_2,l, T_3 \times T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        \times
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
+    cast(T_1 + T_2,l, T_3 + T_4) &=&
+      \hyperCoercionC{\epsilon}{
+         c_1
+        +
+         c_2
+      }{\epsilon}
+      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
+      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)
+  \end{array}
+  \]
+
+  \caption{\textit{cast} and its auxilliary functions for Lazy UD.}
+  \label{fig:HC-UD-cast}
+\end{figure}
 

### 2019-10-16 paper.tex
applyCast for lazy UD blame calculus

@@
 \affiliation{
-  \department{School of Informatics, Computing, and Engineering}              
+  \department{Computer Science Department}              
   %% \department is recommended
@@
 
-\author{Jeremy Siek}
-
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
+\author{Jeremy G. Siek}
+\email{jsiek@indiana.edu}         %% \email is recommended
+
+%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
 \affiliation{
-  \position{Position2a}
-  \department{Department2a}             %% \department is recommended
-  \institution{Institution2a}           %% \institution is required
+%  \position{Position2a}
+  \department{Computer Science Department}             %% \department is recommended
+  \institution{Indiana University}           %% \institution is required
   \streetaddress{Street2a Address2a}
-  \city{City2a}
-  \state{State2a}
-  \postcode{Post-Code2a}
-  \country{Country2a}                   %% \country is recommended
-}
+  %% \city{City2a}
+  %% \state{State2a}
+  %% \postcode{Post-Code2a}
+  \country{United States}                   %% \country is recommended
+}
+
+\author{Andre Kuhlenschmidt}
 \email{first2.last2@inst2a.com}         %% \email is recommended
@@
 \begin{abstract}
-	Gradual Typing is great. Implementing gradually typed with blame tracking 
-	and space efficiency is tricky. There exist two technique to do this: 
-	coercion and threesome. Coercion is easy to understand, and easy enough to 
-	implement, but difficult to reason about formally. Threesome is hard to 
-	understand, easy to implement, and easy to reason about formally. We 
-	propose hyper-coercion, which is easy to understand, as easy to implement 
-	as coercion, and easy to reason about formally.
+  \todo[inline]{Rewrite this abstract based on the comparision table. -Jeremy}
+  Gradual Typing is great. Implementing gradually typed with blame
+  tracking and space efficiency is tricky. There exist two technique
+  to do this: coercion and threesome. Coercion is easy to understand,
+  and easy enough to implement, but difficult to reason about
+  formally. Threesome is hard to understand, easy to implement, and
+  easy to reason about formally. We propose hyper-coercion, which is
+  easy to understand, as easy to implement as coercion, and easy to
+  reason about formally.
+  \todo[inline]{Spell it ``hypercoercion'' without the hyphen. -Jeremy}
 \end{abstract}
@@
 \maketitle
+
+\listoftodos{}
 
@@
 semantics. It is little changed from previous definitions.
+\todo[inline]{Which previous definitions are you refering to?
+  What are the little changes? -Jeremy}
+\todo[inline]{The term typing rule for casts is broken. -Jeremy}
 The dynamic semantics of Blame Calculi depend on blame strategies, so we defer 
@@
 Calculus in the style of CEK machines (\citet{felleisen1986control}).
+\todo[inline]{The figure is too tall. You may need to pull some things
+  out of the figure, such as the value typing. -Jeremy}
+\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
+\todo[inline]{Explain why you are using a CEK machine instead of
+  reduction semantics. -Jeremy}
+\todo[inline]{Change the order of parameters for applyCast to take
+  the value first and the cast second. -Jeremy}
+\todo[inline]{The definition of values is too loose for a cast.
+  You need to restrict the casts to just the inert ones. -Jeremy }
 We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
@@
 
+Fig.~\ref{fig:apply-Cast-UD}
+
 \begin{figure}
 
+  Syntax
+  \[
+  \begin{array}{rclr}
+    \stxrule{v}{values}{
+      \cdots \mid 
+      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
+      \vOOcast{v}{ \cOOcast{P}{l}{P} }
+    }
+  \end{array}
+  \]
+
   \fbox{$\mathit{applyCast}(v,c) = r$}
@@
   \begin{array}{rclr}
-    \mathit{applyCast}(v,c) = r
-  \end{array}
-  \]
-
+    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& v \\
+    \mathit{applyCast}(v, \cOOcast{P}{l}{\star}) &=&
+        v \langle \cOOcast{P}{l}{I} \rangle
+          \langle \cOOcast{I}{l}{\star} \rangle
+        & \text{if } I \sim P, I \neq P \\  
+    \mathit{applyCast}(v, \cOOcast{\star}{l}{P}) &=&          
+        v \langle \cOOcast{\star}{l}{I} \rangle
+          \langle \cOOcast{I}{l}{P} \rangle
+        & \text{if } I \sim P, I \neq P \\  
+  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& v \\
+  \mathit{applyCast}(v \langle \cOOcast{I_1}{l}{\star} \rangle , \cOOcast{\star}{l}{I_2}) &=& \rOOfail{l} & \text{if } I_1 \neq I_2 \\
+  \mathit{applyCast}(v, \cOOcast{P_1}{l}{P_2}) &=&
+     v \langle \cOOcast{P_1}{l}{P_2} \rangle & \text{if } P_1 \smile P_2
+  \end{array}
+  \]
+
+  \caption{Definition of \textit{applyCast} for \lazyUD{}.}
+  \label{fig:apply-Cast-UD}
 \end{figure}
+
+% the following are temporary -Jeremy
+\clearpage
+\pagebreak
 

### 2019-10-16 paper.tex
hyper-coercion => hypercoercion

@@
 \newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
-% Hyper-coercion
+% Hypercoercion
 \newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
@@
   formally. Threesome is hard to understand, easy to implement, and
-  easy to reason about formally. We propose hyper-coercion, which is
+  easy to reason about formally. We propose hypercoercion, which is
   easy to understand, as easy to implement as coercion, and easy to
@@
 working with normal coercions (i.e. coercions in normal form). 
-They conjecture that their revised coercion calculi bi-simulate the 
+They conjecture that their revised coercion calculi bisimulate the 
 corresponding Blame Calculi.
@@
 \lazyUD{} coercion in \citet{siek2012interpretations} and prove that 
-their revised coercion calculus bi-simulates the \lazyUD{} Blame Calculus.
+their revised coercion calculus bisimulates the \lazyUD{} Blame Calculus.
 
@@
 
-We present hyper-coercion, a cast representation whose composition is 
+We present hypercoercion, a cast representation whose composition is 
 structurally recursive, and whose definition is self-standing. What's more, it 
@@
 a clear connection between them, as we will show in Section 
-\ref{sec:hyper-coercion}.
-Our hyper-coercion considers sum types and product types, which are not 
+\ref{sec:hypercoercion}.
+Our hypercoercion considers sum types and product types, which are not 
 considered in all proofs above. Adding each of them requires us to add only one 
-new constructor to a component of hyper-coercion. This suggests that 
-hyper-coercion might scale better than super-coercion.
-
-We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
-bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
+new constructor to a component of hypercoercion. This suggests that 
+hypercoercion might scale better than super-coercion.
+
+We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
+bisimulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
 the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.
@@
 Calculi. 
-In section \ref{sec:hyper-coercion} we present Hyper-coercion.
+In section \ref{sec:hypercoercion} we present hypercoercion.
 Section \ref{sec:conclude} concludes.
@@
 \citet{siek2012interpretations}.
-We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
-equivalent to an abstract machine that represents casts with hyper-coercions.
+We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
+equivalent to an abstract machine that represents casts with hypercoercions.
 
@@
 As the name suggests, 
-hyper-coercion is largely inspired by coercion, especially its subst NC. We 
-will highlight the similarity of normal coercion and hyper-coercion, and hope 
-this would convince you that hyper-coercion should be as difficult to implement 
+hypercoercion is largely inspired by coercion, especially its subst NC. We 
+will highlight the similarity of normal coercion and hypercoercion, and hope 
+this would convince you that hypercoercion should be as difficult to implement 
 as NC.
@@
 
-Three observations on this definition leads to hyper-coercion: 
+Three observations on this definition leads to hypercoercion: 
 \begin{enumerate}
@@
 
-\section{Hyper-coercion} \label{sec:hyper-coercion}
+\section{hypercoercion} \label{sec:hypercoercion}
 
@@
 	}
-	\stxrule{c}{hyper-coercions}{
+	\stxrule{c}{hypercoercions}{
 		\hyperCoercionI \mid{}
@@
 
-	Hyper-coercion typing \fbox{$ c : T \Longrightarrow T $}
+	hypercoercion typing \fbox{$ c : T \Longrightarrow T $}
 	\begin{gather*}
@@
 
-	\caption{Definition of Hyper-coercion (HC)}
-	\label{fig:hyper-coercion}
+	\caption{Definition of hypercoercion (HC)}
+	\label{fig:hypercoercion}
 \end{figure}
 
-This section presents our first contribution, hyper-coercion (HC). 
-\figref{fig:hyper-coercion} defines the syntax of HC.
+This section presents our first contribution, hypercoercion (HC). 
+\figref{fig:hypercoercion} defines the syntax of HC.
 Types, pre-types, and blame labels are as before.
 
-Let $ c $ ranges over hyper-coercions. A hyper-coercion is either 
+Let $ c $ ranges over hypercoercions. A hypercoercion is either 
 an identity cast between the dynamic types, or a complex including a head, a 
@@
 Let $ \ell $ ranges over no-op and labels. It is useful when we introduce 
-composition of hyper-coercions.
-
-\subsection{\lazyD{} Hyper-coercion}
+composition of hypercoercions.
+
+\subsection{\lazyD{} hypercoercion}
 
@@
 
-	Composition of hyper-coercions \fbox{$ c \fatsemi^\ell c = c $}
+	Composition of hypercoercions \fbox{$ c \fatsemi^\ell c = c $}
 	\[ 
@@
 	\]
-	\caption{\lazyD{} Hyper-coercion}
+	\caption{\lazyD{} hypercoercion}
 	\label{fig:HC-D}
@@
 
-$ c_1 \fatsemi^\ell c_2 = c' $ composes two hyper-coercions. The target of $ 
+$ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
 c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
@@
 
-\begin{proposition}[\lazyD\ Hyper-coercions is a Monoid]
+\begin{proposition}[\lazyD\ hypercoercions is a Monoid]
 	For all $c : T_1 \Longrightarrow T_2$,
@@
 
-\subsection{\lazyUD{} Hyper-coercion [Jeremy]}
+\subsection{\lazyUD{} hypercoercion [Jeremy]}
 
@@
 We list a fraction of reduction rules due to space limitation.
-When values are constructed, their hyper-coercion parts are filled with outputs 
+When values are constructed, their hypercoercion parts are filled with outputs 
 of $ id $. For instance, when a function value is constructed, its first part 
@@
 When evaluating a cast expression, the current continuation is extended with a 
-hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
-with the hyper-coercion on the top of the continuation.
+hypercoercion constructed by $ cast $. $ ext $ composes the new hypercoercion 
+with the hypercoercion on the top of the continuation.
 When evaluating a compound expression, the machine firstly construct the new 
 pre-continuation, then turn it to a continuation by adding an identity 
-hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
+hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
 expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
@@
 
-\section{Correctness Proof of \lazyD{} Hyper-coercions}
+\section{Correctness Proof of \lazyD{} hypercoercions}
 
@@
 With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-all machines instantiated with these CRs bi-simulate each other. 
+all machines instantiated with these CRs bisimulate each other. 
 The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
-derived from the definition of states. We omit subscripts when there is no 
-ambiguity. \begin{gather*}
+derived from the definition of states.
+\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
+  ``bisimulation relation''. I don't think you are using it properly
+  in the above sentence. -Jeremy}
+We omit subscripts when there is no 
+ambiguity.
+\begin{gather*}
 \inference{
@@
 
-\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
+\subsection{\lazyD\ hypercoercion Respect $ \mathcal{D} $}
 \label{sec:LDHC-correct}
@@
 	\]
-	\caption{\lazyD\ Hyper-coercion's $ applyCast $}
+	\caption{\lazyD\ hypercoercion's $ applyCast $}
 	\label{hc-applyCast}
@@
 
-\begin{lemma}[\lazyD{} Hyper-coercion is Surely \lazyD]
+\begin{lemma}[\lazyD{} hypercoercion is Surely \lazyD]
 	\label{thm:hc-surely-lazyD}
@@
 
-\begin{theorem}[\lazyD{} Hyper-coercion Respect $ \mathcal{D} $]
+\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{D} $]
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 

### 2019-10-16 paper.tex
plurals
list todos

--- 2019-10-16 paper.tex
@@
 \newcommand{\eqvDS}[3]{#2 \approx_{\mathcal{DS}} #3}
+% to-dos
+\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
 
@@
 \begin{abstract}
+	\todoKC{rewrite abstract}
 	Gradual Typing is great. Implementing gradually typed with blame tracking 
@@
 For example, translation to Blame Calculus can wrap some expressions with code 
-that performs runtime type-checking (casts), including those expressions at 
-tail position. Thus, mutually tail-recursive functions in source language can 
+that performs runtime type-checking (casts), including expressions at 
+tail positions. Thus, mutually tail-recursive functions in source language can 
 consume unbounded space at runtime. There are more examples of space leaking in 
@@
 $ D $ and $ UD $ assign blame labels differently.
-They prove partially that their \lazyUD{} coercion is correct by showing 
-that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
-however, whether the simulation also works in the other direction.
+They prove their \lazyUD{} coercion simulates the Blame Calculus in 
+\cite{wadler2009well}. It is unknown, however, whether the simulation in the 
+other direction also works.
 
@@
 tracking and space efficiency. Their solution represents casts with threesomes, 
-a novel cast representation.
-They show that their calculus bisimulates the \lazyUD{} coercion 
+a novel cast representation. Threesome is proved space-efficient as well.
+They prove that their calculus bisimulates the \lazyUD{} coercion 
 calculus in \citet{siek2009exploring} and the Blame Calculus in 
-\citet{wadler2009well}. They also prove that threesome is space-efficient as 
-well.
+\citet{wadler2009well}.
 
@@
 working with normal coercions (i.e. coercions in normal form). 
-They conjecture that their revised coercion calculi bi-simulate the 
+They conjecture that their revised coercion calculi bisimulate the 
 corresponding Blame Calculi.
 
-Following \citet{siek2010threesomes}, \citet{garcia2013calculating} develops
-threesome for other blame strategies. After studying in depth the relation 
+\citet{garcia2013calculating} develops
+threesome for other blame strategies. After studying in depth the connection 
 between coercion and threesome,
@@
 We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
-bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
+bisimulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
 the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.
@@
 are shallowly consistent if one of them is $ \star $, or they have the same 
-top-most type constructor. Shallow-inconsistency is the root of all blames in 
+type constructor at the top. Shallow-inconsistency is the root of all blames in 
 all lazy strategies -- casting a value to a shallowly inconsistent type leads 
@@
 Let $ o $ ranges over observations. They are what would be observed if a 
-program terminates. Observations include all constructors and blames.
+program terminates. Observations include all value constructors and blames.
 
@@
 		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{car} \; \kappa \mid{}
-		\mathtt{cdr} \; \kappa \mid
+		\mathtt{fst} \; \kappa \mid{}
+		\mathtt{snd} \; \kappa \mid
 		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
@@
 					\POOprod{T_3}{T_4}}}
-			}{(\mathtt{car} \; \kappa)}
+			}{(\mathtt{fst} \; \kappa)}
 	}{
 		\sOOreturn{v}{(
-			\mathtt{car} \;
+			\mathtt{fst} \;
 			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
@@
 					\POOprod{T_3}{T_4}}}
-		}{(\mathtt{cdr} \; \kappa)}
+		}{(\mathtt{snd} \; \kappa)}
 	}{
 		\sOOreturn{v}{(
-			\mathtt{cdr} \;
+			\mathtt{snd} \;
 			\langle \cOOcast{T_2}{l}{T_4} \rangle \kappa
@@
 Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
-Calculus in the style of CEK machines (\citet{felleisen1986control}). 
-We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
+Calculus in the style of CEK machine (\citet{felleisen1986control}). 
+We conjecture that this CEK machine agree with the \lazyD{} blame calculus in 
 \citet{siek2012interpretations}.
-We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
+We will show in Section~\ref{sec:hyper-coercion} that this abstract machine is 
 equivalent to an abstract machine that represents casts with hyper-coercions.
+
+\todoKC{change the reduction rules of case}
 
@@
 		\sidecond{
-			t_1 \neq \bot^{\centerdot} \; \text{and} \;
 			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
+			 \; \text{and} \;
+			 \forall l. t \neq \bot^{l}
 		}
@@
 		\sidecond{
-			t_1 \neq \bot^{\centerdot} \; \text{and} \;
 			m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
+			\; \text{and} \;
+			\forall l. t \neq \bot^{l} 
 		}
@@
 
-\lazyD{} HC constructors are in \figref{fig:HC-D}.
-
-$ c_1 \fatsemi^\ell c_2 = c' $ composes two hyper-coercions. The target of $ 
+\figref{fig:HC-D} defines the constructors of \lazyD{} HC.
+
+\todoKC{check consistency before using middle composition.}
+
+$ c_1 \fatsemi^\ell c_2 = c' $ composes two HCs. The target of $ 
 c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
@@
 \begin{proposition}[\lazyD\ Hyper-coercions is a Monoid]
+	\label{thm:hc-monoid}
 	For all $c : T_1 \Longrightarrow T_2$,
@@
 		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{car} \; \kappa \mid{}
-		\mathtt{cdr} \; \kappa
+		\mathtt{fst} \; \kappa \mid{}
+		\mathtt{snd} \; \kappa
 	}
@@
 
-In this section we describe a subset of SR, where all 
+In this section we describe a subset of cast representations, where all 
 elements implement the \lazyD{} blame strategy. We will show in 
@@
 
-\subsection{Relating All Surely \lazyD{} Cast Representations}
-
-With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-all machines instantiated with these CRs bi-simulate each other. 
-The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
-derived from the definition of states. We omit subscripts when there is no 
-ambiguity. \begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2 &
-	v_1 \approx v_2
-}{
-	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-}
-\quad
-\inference{
-}{
-	\sOOhalt{o} \approx \sOOhalt{o}
-}
-\end{gather*}
-
-The relations between continuations, pre-continuations, enviroments, values, 
-cast results are also derived from their definitions. But the relation for 
-casts is special: \begin{gather*}
-\inference{
-}{
-	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
-}
-\quad
-\inference{
-}{
-	id_1(T) \approx id_2(T)
-}
-\quad
-\inference{
-	c_1 \approx c_2 &
-	c_3 \approx c_4
-}{
-	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
-}
-\end{gather*}
-
-\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
-	\label{thm:CEKS-bisim}
-	If 
-	$ C_1 $ and $ C_2 $ are surely \lazyD,
-	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
-	$ s_1 \approx s_3 $,
-	$ \judgeSreduce{C_1}{s_1}{s_2} $,
-	then there exists an $ s_4 $ such that
-	\begin{itemize}
-	\item $ s_2 \approx s_4 $ and
-	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
-	\end{itemize}
-\end{proposition}
-\begin{proof}
-	The key ideas of this proof are undoing sequencing with the property (2) of 
-	surely \lazyD{} CR, and handling all possibly uses of $ 
-	cast(T,l,T) $ with property (3)-(11).
-\end{proof}
-
-\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
-	\label{thm:surely-lazyD-eqv}
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-	are surely \lazyD cast representations,
-	\[
-	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-	e \Downarrow_{S(C_2)} o
-	\]
-\end{proposition}
-\begin{proof}
-	Immediately from Proposition~\ref{thm:CEKS-bisim}.
-\end{proof}
-
-\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
-
-So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
-each other. But this does not mean they respect the semantics of the \lazyD{} 
-Blame Calculus. We solve prove this part in this subsection.
-
-The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
+\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
+$\mathcal{D}$}
+
+We use bisimulation to proof equivalence between the two machines.
+The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
 definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
 between continuations, between values, and from continuations to 
-pre-continuations.
-
-\todo[inline]{bisimilarity}
+pre-continuations. We omit subscripts when there is no ambiguity.
+
+\todoKC{write down the exceptional bisimilarity relations}
 
@@
 
-\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
-	$ \mathcal{D} $]
-	\label{thm:surely-lazyD-correct}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
-	\lazyD{}
-\[
-\judgeDBeval{e}{o} \; \text{if and only if} \; 
-\judgeSeval{C}{e}{o}
-\]
-\end{theorem}
-\begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
-	Proposition~\ref{thm:surely-lazyD-eqv}.
-\end{proof}
-
 \subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
 \label{sec:LDHC-correct}
-
-To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
-uses the Theorem~\ref{thm:surely-lazyD-correct} to prove its correctness.
 
@@
 \begin{proof}
-	Immediately from Lemma~\ref{thm:hc-surely-lazyD} and 
-	Theorem~\ref{thm:surely-lazyD-correct}.
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
+	Lemma~\ref{thm:hc-surely-lazyD}, and 
+	Proposition~\ref{thm:hc-monoid}.
+\end{proof}
+
+\subsection{Extra Theorems}
+
+In these section we show some extra theorems that might be useful in proving 
+the correctness of other cast representations.
+
+With the properties of surely \lazyD{} CR, it is straightforward to proof that 
+all machines instantiated with these CRs bisimulate each other. 
+The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+derived from the definition of states. We omit subscripts when there is no 
+ambiguity. \begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2 &
+	v_1 \approx v_2
+}{
+	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+}
+\quad
+\inference{
+}{
+	\sOOhalt{o} \approx \sOOhalt{o}
+}
+\end{gather*}
+
+The relations between continuations, pre-continuations, enviroments, values, 
+cast results are also derived from their definitions. But the relation for 
+casts is special: \begin{gather*}
+\inference{
+}{
+	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
+}
+\quad
+\inference{
+}{
+	id_1(T) \approx id_2(T)
+}
+\quad
+\inference{
+	c_1 \approx c_2 &
+	c_3 \approx c_4
+}{
+	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
+}
+\end{gather*}
+
+\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
+	\label{thm:CEKS-bisim}
+	If 
+	$ C_1 $ and $ C_2 $ are surely \lazyD,
+	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
+	$ s_1 \approx s_3 $,
+	$ \judgeSreduce{C_1}{s_1}{s_2} $,
+	then there exists an $ s_4 $ such that
+	\begin{itemize}
+	\item $ s_2 \approx s_4 $ and
+	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
+	\end{itemize}
+\end{lemma}
+\begin{proof}
+	The key ideas of this proof are undoing sequencing with the property (2) of 
+	surely \lazyD{} CR, and handling all possibly uses of $ 
+	cast(T,l,T) $ with property (3)-(11).
+\end{proof}
+
+\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+	\label{thm:surely-lazyD-eqv}
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+	are surely \lazyD\ cast representations,
+	\[
+	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+	e \Downarrow_{S(C_2)} o
+	\]
+\end{proposition}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:CEKS-bisim}.
+\end{proof}
+
+\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
+	$ \mathcal{D} $]
+	\label{thm:surely-lazyD-correct}
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
+	\lazyD{}
+	\[
+	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeSeval{C}{e}{o}
+	\]
+\end{theorem}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
+	Proposition~\ref{thm:surely-lazyD-eqv}.
 \end{proof}

### 2019-10-16 paper.tex

--- 2019-10-16 paper.tex
@@
 \begin{abstract}
-  \todo[inline]{Rewrite this abstract based on the comparision table. -Jeremy}
+\todoKC{rewrite this abstract based on the comparision table. -Jeremy}
   Gradual Typing is great. Implementing gradually typed with blame
@@
 
+\todo[inline]{I see lots of mistakes regarding when to make words
+  plural (whether they should have an ``s'' at the end). Please review
+  the rules of English regarding plurals. -Jeremy}
+
 Around 2006, many work on integrating dynamic typing and static typing emerge, 
@@
 
-Following \citet{siek2010threesomes}, \citet{garcia2013calculating} develops
-threesome for other blame strategies. After studying in depth the relation 
+\citet{garcia2013calculating} develops
+threesome for other blame strategies. After studying in depth the connection 
 between coercion and threesome,
@@
 equivalent to an abstract machine that represents casts with hypercoercions.
+
+\todoKC{change the reduction rules of case}
 
@@
 
-\lazyD{} HC constructors are in \figref{fig:HC-D}.
-
+\figref{fig:HC-D} defines the constructors of \lazyD{} HC.
+
+\todoKC{check consistency before using middle composition.}
 $ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
@@
 
-\begin{proposition}[\lazyD\ hypercoercions is a Monoid]
+\begin{proposition}[\lazyD\ hypercoercion is a monoid]
 	For all $c : T_1 \Longrightarrow T_2$,
@@
 
-\subsection{Relating All Surely \lazyD{} Cast Representations}
-
-With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-all machines instantiated with these CRs bisimulate each other. 
-The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
-derived from the definition of states.
-\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
-  ``bisimulation relation''. I don't think you are using it properly
-  in the above sentence. -Jeremy}
-We omit subscripts when there is no 
-ambiguity.
-\begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2 &
-	v_1 \approx v_2
-}{
-	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-}
-\quad
-\inference{
-}{
-	\sOOhalt{o} \approx \sOOhalt{o}
-}
-\end{gather*}
-
-The relations between continuations, pre-continuations, enviroments, values, 
-cast results are also derived from their definitions. But the relation for 
-casts is special: \begin{gather*}
-\inference{
-}{
-	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
-}
-\quad
-\inference{
-}{
-	id_1(T) \approx id_2(T)
-}
-\quad
-\inference{
-	c_1 \approx c_2 &
-	c_3 \approx c_4
-}{
-	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
-}
-\end{gather*}
-
-\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
-	\label{thm:CEKS-bisim}
-	If 
-	$ C_1 $ and $ C_2 $ are surely \lazyD,
-	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
-	$ s_1 \approx s_3 $,
-	$ \judgeSreduce{C_1}{s_1}{s_2} $,
-	then there exists an $ s_4 $ such that
-	\begin{itemize}
-	\item $ s_2 \approx s_4 $ and
-	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
-	\end{itemize}
-\end{proposition}
-\begin{proof}
-	The key ideas of this proof are undoing sequencing with the property (2) of 
-	surely \lazyD{} CR, and handling all possibly uses of $ 
-	cast(T,l,T) $ with property (3)-(11).
-\end{proof}
-
-\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
-	\label{thm:surely-lazyD-eqv}
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-	are surely \lazyD cast representations,
-	\[
-	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-	e \Downarrow_{S(C_2)} o
-	\]
-\end{proposition}
-\begin{proof}
-	Immediately from Proposition~\ref{thm:CEKS-bisim}.
-\end{proof}
-
-\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
-
-So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
-each other. But this does not mean they respect the semantics of the \lazyD{} 
-Blame Calculus. We solve prove this part in this subsection.
-
-The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
+\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
+$\mathcal{D}$}
+
+We use bisimulation to proof equivalence between the two machines.
+The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
 definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
 between continuations, between values, and from continuations to 
-pre-continuations.
-
-\todo[inline]{bisimilarity}
+pre-continuations. We omit subscripts when there is no ambiguity.
+
+\todoKC{write down the exceptional bisimilarity relations}
 
@@
 
-\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
-	$ \mathcal{D} $]
-	\label{thm:surely-lazyD-correct}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
-	\lazyD{}
-\[
-\judgeDBeval{e}{o} \; \text{if and only if} \; 
-\judgeSeval{C}{e}{o}
-\]
-\end{theorem}
-\begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
-	Proposition~\ref{thm:surely-lazyD-eqv}.
-\end{proof}
-
-\subsection{\lazyD\ hypercoercion Respect $ \mathcal{D} $}
+\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
 \label{sec:LDHC-correct}
-
-To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
-uses the Theorem~\ref{thm:surely-lazyD-correct} to prove its correctness.
 
@@
 \begin{proof}
-	Immediately from Lemma~\ref{thm:hc-surely-lazyD} and 
-	Theorem~\ref{thm:surely-lazyD-correct}.
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
+	Lemma~\ref{thm:hc-surely-lazyD}, and 
+	Proposition~\ref{thm:hc-monoid}.
+\end{proof}
+
+\subsection{Extra Theorems}
+
+In these section we show some extra theorems that might be useful in proving 
+the correctness of other cast representations.
+
+With the properties of surely \lazyD{} CR, it is straightforward to proof that 
+all machines instantiated with these CRs bisimulate each other. 
+The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+derived from the definition of states.
+\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
+	``bisimulation relation''. I don't think you are using it properly
+	in the above sentence. -Jeremy}
+We omit subscripts when there is no 
+ambiguity. \begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2 &
+	v_1 \approx v_2
+}{
+	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+}
+\quad
+\inference{
+}{
+	\sOOhalt{o} \approx \sOOhalt{o}
+}
+\end{gather*}
+
+The relations between continuations, pre-continuations, enviroments, values, 
+cast results are also derived from their definitions. But the relation for 
+casts is special: \begin{gather*}
+\inference{
+}{
+	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
+}
+\quad
+\inference{
+}{
+	id_1(T) \approx id_2(T)
+}
+\quad
+\inference{
+	c_1 \approx c_2 &
+	c_3 \approx c_4
+}{
+	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
+}
+\end{gather*}
+
+\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
+	\label{thm:CEKS-bisim}
+	If 
+	$ C_1 $ and $ C_2 $ are surely \lazyD,
+	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
+	$ s_1 \approx s_3 $,
+	$ \judgeSreduce{C_1}{s_1}{s_2} $,
+	then there exists an $ s_4 $ such that
+	\begin{itemize}
+	\item $ s_2 \approx s_4 $ and
+	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
+	\end{itemize}
+\end{lemma}
+\begin{proof}
+	The key ideas of this proof are undoing sequencing with the property (2) of 
+	surely \lazyD{} CR, and handling all possibly uses of $ 
+	cast(T,l,T) $ with property (3)-(11).
+\end{proof}
+
+\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+	\label{thm:surely-lazyD-eqv}
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+	are surely \lazyD\ cast representations,
+	\[
+	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+	e \Downarrow_{S(C_2)} o
+	\]
+\end{proposition}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:CEKS-bisim}.
+\end{proof}
+
+\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
+	$ \mathcal{D} $]
+	\label{thm:surely-lazyD-correct}
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
+	\lazyD{}
+	\[
+	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeSeval{C}{e}{o}
+	\]
+\end{theorem}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
+	Proposition~\ref{thm:surely-lazyD-eqv}.
 \end{proof}

### 2019-10-16 paper.tex
edits

--- 2019-10-16 paper.tex
@@
 
+\todo[inline]{I see lots of mistakes regarding when to make words
+  plural (whether they should have an ``s'' at the end). Please review
+  the rules of English regarding plurals. The rules are tricky...
+  some words don't have a plural form, like ``blame''. -Jeremy}
+
+\todo[inline]{The first paragraph of the introduction should summarize
+  the entire introduction, and in some sense, the entire paper. -Jeremy}
+
+\todo[inline]{BTW, using the Coercion and Blame paper as a model for
+  how to write papers is perhaps not the best idea. That paper intentionally
+  diverged from the normal paper format in several ways. You can
+  do that too after you've become a master at writing papers.
+  For now you are much better off following the advice of
+  Simon Peyton Jones about how to write a paper (google it).}
+
 Around 2006, many work on integrating dynamic typing and static typing emerge, 
@@
 
-\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions with 
-labels to restore 
-blame-tracking. They also propose that there are four blame 
-strategies for their coercion:
-$ \{Lazy, Eager\} \times \{D, UD\} $. 
-Eager strategies detect more potential type errors, 
-but blame more programs.
-$ D $ and $ UD $ assign blame labels differently.
-They prove partially that their \lazyUD{} coercion is correct by showing 
-that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
-however, whether the simulation also works in the other direction.
+\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions
+with labels to restore blame-tracking. They also propose that there
+are four blame strategies for coercions: $ \{Lazy, Eager\} \times \{D,
+UD\} $.  Eager strategies detect more potential type errors, but blame
+more programs.  $ D $ and $ UD $ assign blame labels differently.
+They prove that the \lazyUD{} calculus simulates the Blame Calculus of
+\citet{wadler2009well}.  They do not prove the other direction,
+whether the Blame Calculus simulates the \lazyUD{} calculus.
+\todo[inline]{Is it important to this paper whether there is a
+  simulation in the other direction? -Jeremy}
 
 \citet{siek2010threesomes} proposes another approach to combine blame
-tracking and space efficiency. Their solution represents casts with threesomes, 
-a novel cast representation.
-They show that their calculus bisimulates the \lazyUD{} coercion 
-calculus in \citet{siek2009exploring} and the Blame Calculus in 
-\citet{wadler2009well}. They also prove that threesome is space-efficient as 
-well.
+tracking and space efficiency. Their solution represents casts with
+threesomes, a novel cast representation.  They show that their
+calculus bisimulates the \lazyUD{} coercion calculus in
+\citet{siek2009exploring} and the Blame Calculus in
+\citet{wadler2009well}. They also prove that threesome is
+space-efficient as well.
 
@@
 revised coercion calculi.
+\todo[inline]{Not ``first''... lazy D is in the 2009 paper, right?
+  Or did you mean something else? -Jeremy}
+\todo[inline]{The ``Blame Calculus'' is a \lazyUD{} cast calculus.
+  There is no such thing as a \lazyD{} Blame Calculus. -Jeremy}
 They simplify the coercion calculi by only 
@@
 (\citet{siek2015blame}).
-His threesome calculi are equivalent to the coercion calculi in 
+His threesome calculi are equivalent to the coercion calculi of
 \citet{siek2009exploring} because the former ones are derived from the latter 
@@
 
-\citet{siek2015blame} revisit the coercion-based approach. They revise the 
-\lazyUD{} coercion in \citet{siek2012interpretations} and prove that 
-their revised coercion calculus bisimulates the \lazyUD{} Blame Calculus.
+\citet{siek2015blame} revisit the coercion-based approach. They revise
+the \lazyUD{} coercion in \citet{siek2012interpretations} and prove
+that their revised coercion calculus bisimulates the \lazyUD{} Blame
+Calculus \citet{wadler2009well}.
 
@@
 their proof assistants that the composition terminates.
+%
+\todo[inline]{Don't lie. There are not many developers of Grift.
+  I only know 2 people developing Grift: Andre and Deyaa. -Jeremy}
+%
 Secondly, the definition of normal coercion lies unnecessarily on top 
@@
 composes and produces normal coercions.
+%
+\todo[inline]{Many researchers would view this as a positive thing,
+  not a negative. For example, the notion of normal forms comes up
+  over and over again in mathematics and logic. -Jeremy}
 
@@
 is self-standing, and whose composition is structurally recursive. 
-Super-coercion introduced in \citet{garcia2013calculating} could be a promising 
+supercoercion introduced in \citet{garcia2013calculating} could be a promising 
 candidate. It is believed even more complicated than threesome 
@@
 function types. And four constructors are directly related to function types. 
-Thus, super-coercion might not scale very well to more sophisticated type 
+Thus, supercoercion might not scale very well to more sophisticated type 
 systems.
@@
 new constructor to a component of hypercoercion. This suggests that 
-hypercoercion might scale better than super-coercion.
+hypercoercion might scale better than supercoercion.
 
@@
 bisimulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
-the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.
+the first bisimulation proof for the \lazyD{} Blame Calculus as far as we know.
+
+\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}
 
@@
 Section \ref{sec:conclude} concludes.
-
-\section{Background: Blame Calculus} \label{sec:blame-calculus}
+\todo[inline]{Lots of missing sections. -Jeremy}
+
+\section{Background: Cast Calculi} \label{sec:blame-calculus}
 
@@
 
-	\caption{Blame Calculus and its static semantics}
+	\caption{Syntax and static semantics of the cast calculi.}
 	\label{fig:blame-static}
@@
 
-\figref{fig:blame-static} defines the syntax of blame calculus and its static 
-semantics. It is little changed from previous definitions.
-\todo[inline]{Which previous definitions are you refering to?
-  What are the little changes? -Jeremy}
-\todo[inline]{The term typing rule for casts is broken. -Jeremy}
-The dynamic semantics of Blame Calculi depend on blame strategies, so we defer 
-them to sub-sections.
+\figref{fig:blame-static} defines the syntax of blame calculus and its
+static semantics. It is little changed from previous definitions.
+\todo[inline]{Which previous definitions are you refering to?  What
+  are the little changes? -Jeremy} \todo[inline]{The term typing rule
+  for casts is broken. -Jeremy} The dynamic semantics of Blame Calculi
+depend on blame strategies, so we defer them to sub-sections.
 
@@
 are shallowly consistent if one of them is $ \star $, or they have the same 
-top-most type constructor. Shallow-inconsistency is the root of all blames in 
-all lazy strategies -- casting a value to a shallowly inconsistent type leads 
+top-most type constructor. Shallow-inconsistency is the root of all blame in 
+lazy cast strategies -- casting a value to a shallowly inconsistent type leads 
 to a blame. Shallow-consistency is reflexive, symmetric, but 
@@
 Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
-in addition, casts and blames. Unlike $ \mathtt{STLC+} $, we annotate the 
-co-domain of lambda abstractions explicitly. 
-The end of the figure shows the typing rules for the additional terms.
+in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
+codomain of lambda abstractions explicitly.
+\todo[inline]{Why do you annotate the codomain of lambda abstractions
+  explicitly? -Jeremy}
+The end of \figref{fig:blame-static} shows the typing rules for the
+additional terms.
 
@@
 program terminates. Observations include all constructors and blames.
+\todo[inline]{``blames'' is incorrect. See
+https://www.wordhippo.com/what-is/the-plural-of/blame.html}
 
@@
 
-\subsection{\lazyD{} Blame Calculus}
+\subsection{The Blame Calculus (a \lazyD{} cast calculus)}
 
@@
 Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
-Calculus in the style of CEK machines (\citet{felleisen1986control}).
+Calculus in the style of CEK machines \citep{felleisen1986control}.
+\todo[inline]{Briefly present the main ideas regarding how a CEK
+  machine works. (2-3 sentences) -Jeremy}
+\todo[inline]{Use citep to put a citation in parentheses, as I've
+  done above. -Jeremy }
 \todo[inline]{The figure is too tall. You may need to pull some things
@@
 
-Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
+Let $ c $ ranges over casts.
+\todo[inline]{``ranges'' should be ``range'', not plural. -Jeremy}
+A cast is a triple of a type, a label, and a type.
 Let $ v $ ranges over values. A value is either a function, the 
@@
 deep inside the value to find out whether it is a left injection or a right 
-one. Along the way, the machine accumulate the pending casts onto the 
+one.
+\todo[inline]{Change the rules for case to be small step, i.e.,
+ the case function should not be recursive. -Jeremy}
+Along the way, the machine accumulate the pending casts onto the 
 continuations. To cast a value, the machine try to apply the cast to the value. 
@@
 
-\subsection{\lazyUD{} Blame Calculus [Jeremy]}
-
-UNDER CONSTRUCTION
+\subsection{The \lazyUD{} cast calculus [Jeremy]}
 
@@
 
-\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
+\begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
 	\label{thm:CEKS-bisim}
@@
 
-\begin{lemma}[Weak Bi-simulation between $ \mathcal{S}(\cdot) $ and $ 
+\begin{lemma}[Weak bisimulation between $ \mathcal{S}(\cdot) $ and $ 
 \mathcal{D} $]

### 2019-10-16 paper.tex

--- 2019-10-16 paper.tex
@@
   plural (whether they should have an ``s'' at the end). Please review
-  the rules of English regarding plurals. -Jeremy}
+  the rules of English regarding plurals. The rules are tricky...
+  some words don't have a plural form, like ``blame''. -Jeremy}
+
+\todo[inline]{The first paragraph of the introduction should summarize
+  the entire introduction, and in some sense, the entire paper. -Jeremy}
+
+\todo[inline]{BTW, using the Coercion and Blame paper as a model for
+  how to write papers is perhaps not the best idea. That paper intentionally
+  diverged from the normal paper format in several ways. You can
+  do that too after you've become a master at writing papers.
+  For now you are much better off following the advice of
+  Simon Peyton Jones about how to write a paper (google it).}
 
@@
 other direction also works.
+\todo[inline]{Is it important to this paper whether there is a
+  simulation in the other direction? -Jeremy}
 
@@
 are shallowly consistent if one of them is $ \star $, or they have the same 
-type constructor at the top. Shallow-inconsistency is the root of all blames in 
-all lazy strategies -- casting a value to a shallowly inconsistent type leads 
+type constructor at the top. Shallow-inconsistency is the root of all blame in 
+lazy cast strategies -- casting a value to a shallowly inconsistent type leads 
 to a blame. Shallow-consistency is reflexive, symmetric, but 
@@
 program terminates. Observations include all value constructors and blames.
+\todo[inline]{``blames'' is incorrect. See
+https://www.wordhippo.com/what-is/the-plural-of/blame.html}
 
@@
 Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
+\todo[inline]{``ranges'' should be ``range'', not plural. -Jeremy}
 Let $ v $ ranges over values. A value is either a function, the 
@@
 
+%%<<<<<<< HEAD
+With the properties of surely \lazyD{} CR, it is straightforward to proof that 
+all machines instantiated with these CRs bisimulate each other. 
+The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+derived from the definition of states.
+\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
+  ``bisimulation relation''. I don't think you are using it properly
+  in the above sentence. -Jeremy}
+We omit subscripts when there is no 
+ambiguity.
+\begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2 &
+	v_1 \approx v_2
+}{
+	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+}
+\quad
+\inference{
+}{
+	\sOOhalt{o} \approx \sOOhalt{o}
+}
+\end{gather*}
+
+The relations between continuations, pre-continuations, enviroments, values, 
+cast results are also derived from their definitions. But the relation for 
+casts is special: \begin{gather*}
+\inference{
+}{
+	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
+}
+\quad
+\inference{
+}{
+	id_1(T) \approx id_2(T)
+}
+\quad
+\inference{
+	c_1 \approx c_2 &
+	c_3 \approx c_4
+}{
+	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
+}
+\end{gather*}
+
+\begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
+	\label{thm:CEKS-bisim}
+	If 
+	$ C_1 $ and $ C_2 $ are surely \lazyD,
+	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
+	$ s_1 \approx s_3 $,
+	$ \judgeSreduce{C_1}{s_1}{s_2} $,
+	then there exists an $ s_4 $ such that
+	\begin{itemize}
+	\item $ s_2 \approx s_4 $ and
+	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
+	\end{itemize}
+\end{proposition}
+\begin{proof}
+	The key ideas of this proof are undoing sequencing with the property (2) of 
+	surely \lazyD{} CR, and handling all possibly uses of $ 
+	cast(T,l,T) $ with property (3)-(11).
+\end{proof}
+
+\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+	\label{thm:surely-lazyD-eqv}
+	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+	are surely \lazyD cast representations,
+	\[
+	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+	e \Downarrow_{S(C_2)} o
+	\]
+\end{proposition}
+\begin{proof}
+	Immediately from Proposition~\ref{thm:CEKS-bisim}.
+\end{proof}
+
+\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
+
+So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
+each other. But this does not mean they respect the semantics of the \lazyD{} 
+Blame Calculus. We solve prove this part in this subsection.
+
+The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
+%%=======
 We use bisimulation to proof equivalence between the two machines.
 The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
+%%>>>>>>> 6d40f5173c83f5f7f7b37a4128391ca516854ac9
 definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
@@
 
+%%<<<<<<< HEAD
+\begin{lemma}[Weak bisimulation between $ \mathcal{S}(\cdot) $ and $ 
+\mathcal{D} $]
+\label{thm:surely-monoidic-reduce}
+For all cast representations $ C $, 
+if $ C $ is surely \lazyD{} and monoidic,
+$ s_1 \in \mathcal{D} $,
+$ s_2 \in \mathcal{S}(C) $, and
+$ s_1 \approx s_2 $, 
+\begin{enumerate}
+	\item If $ \judgeDBreduce{s_1}{s_3} $,
+	then
+	there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
+	such that \begin{itemize}
+		\item $ s_5 \approx s_4 $, and
+		\item $ \judgeSreduce{C}{s_2}{s_4} $,
+		\item $ \judgeDBreduceTrans{s_3}{s_5} $
+	\end{itemize}
+	\item If $ \judgeSreduce{C}{s_2}{s_4} $,
+	then
+	there exist $ s_3 \in \mathcal{D} $,
+	such that \begin{itemize}
+		\item $ s_3 \approx s_4 $
+		\item $ \judgeDBreduceTrans{s_1}{s_3} $
+	\end{itemize}
+\end{enumerate}
+%%=======
 \begin{lemma}[Weak Bi-simulation between $ \mathcal{S}(\cdot) $ and $ 
@@
 	\end{enumerate}
+%%>>>>>>> 6d40f5173c83f5f7f7b37a4128391ca516854ac9
 \end{lemma}

### 2019-10-16 paper.tex
resolved merge

@@
 
-%%<<<<<<< HEAD
-With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-all machines instantiated with these CRs bisimulate each other. 
-The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
-derived from the definition of states.
-\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
-  ``bisimulation relation''. I don't think you are using it properly
-  in the above sentence. -Jeremy}
-We omit subscripts when there is no 
-ambiguity.
-\begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2 &
-	v_1 \approx v_2
-}{
-	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-}
-\quad
-\inference{
-}{
-	\sOOhalt{o} \approx \sOOhalt{o}
-}
-\end{gather*}
-
-The relations between continuations, pre-continuations, enviroments, values, 
-cast results are also derived from their definitions. But the relation for 
-casts is special: \begin{gather*}
-\inference{
-}{
-	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
-}
-\quad
-\inference{
-}{
-	id_1(T) \approx id_2(T)
-}
-\quad
-\inference{
-	c_1 \approx c_2 &
-	c_3 \approx c_4
-}{
-	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
-}
-\end{gather*}
-
-\begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
-	\label{thm:CEKS-bisim}
-	If 
-	$ C_1 $ and $ C_2 $ are surely \lazyD,
-	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
-	$ s_1 \approx s_3 $,
-	$ \judgeSreduce{C_1}{s_1}{s_2} $,
-	then there exists an $ s_4 $ such that
-	\begin{itemize}
-	\item $ s_2 \approx s_4 $ and
-	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
-	\end{itemize}
-\end{proposition}
-\begin{proof}
-	The key ideas of this proof are undoing sequencing with the property (2) of 
-	surely \lazyD{} CR, and handling all possibly uses of $ 
-	cast(T,l,T) $ with property (3)-(11).
-\end{proof}
-
-\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
-	\label{thm:surely-lazyD-eqv}
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-	are surely \lazyD cast representations,
-	\[
-	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-	e \Downarrow_{S(C_2)} o
-	\]
-\end{proposition}
-\begin{proof}
-	Immediately from Proposition~\ref{thm:CEKS-bisim}.
-\end{proof}
-
-\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
-
-So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
-each other. But this does not mean they respect the semantics of the \lazyD{} 
-Blame Calculus. We solve prove this part in this subsection.
-
-The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
-%%=======
+% Did you really mean to delete all the following? -Jeremy
+%% With the properties of surely \lazyD{} CR, it is straightforward to proof that 
+%% all machines instantiated with these CRs bisimulate each other. 
+%% The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+%% derived from the definition of states.
+%% \todo[inline]{The term ``bisimilarity'' has a different technical meaning from
+%%   ``bisimulation relation''. I don't think you are using it properly
+%%   in the above sentence. -Jeremy}
+%% We omit subscripts when there is no 
+%% ambiguity.
+%% \begin{gather*}
+%% \inference{
+%% 	\rho_1 \approx \rho_2 &
+%% 	\kappa_1 \approx \kappa_2
+%% }{
+%% 	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+%% }
+%% \quad
+%% \inference{
+%% 	\kappa_1 \approx \kappa_2 &
+%% 	v_1 \approx v_2
+%% }{
+%% 	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+%% }
+%% \quad
+%% \inference{
+%% }{
+%% 	\sOOhalt{o} \approx \sOOhalt{o}
+%% }
+%% \end{gather*}
+
+%% The relations between continuations, pre-continuations, enviroments, values, 
+%% cast results are also derived from their definitions. But the relation for 
+%% casts is special: \begin{gather*}
+%% \inference{
+%% }{
+%% 	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
+%% }
+%% \quad
+%% \inference{
+%% }{
+%% 	id_1(T) \approx id_2(T)
+%% }
+%% \quad
+%% \inference{
+%% 	c_1 \approx c_2 &
+%% 	c_3 \approx c_4
+%% }{
+%% 	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
+%% }
+%% \end{gather*}
+
+%% \begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
+%% 	\label{thm:CEKS-bisim}
+%% 	If 
+%% 	$ C_1 $ and $ C_2 $ are surely \lazyD,
+%% 	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
+%% 	$ s_1 \approx s_3 $,
+%% 	$ \judgeSreduce{C_1}{s_1}{s_2} $,
+%% 	then there exists an $ s_4 $ such that
+%% 	\begin{itemize}
+%% 	\item $ s_2 \approx s_4 $ and
+%% 	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
+%% 	\end{itemize}
+%% \end{proposition}
+%% \begin{proof}
+%% 	The key ideas of this proof are undoing sequencing with the property (2) of 
+%% 	surely \lazyD{} CR, and handling all possibly uses of $ 
+%% 	cast(T,l,T) $ with property (3)-(11).
+%% \end{proof}
+
+%% \begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+%% 	\label{thm:surely-lazyD-eqv}
+%% 	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+%% 	are surely \lazyD cast representations,
+%% 	\[
+%% 	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
+%% 	e \Downarrow_{S(C_2)} o
+%% 	\]
+%% \end{proposition}
+%% \begin{proof}
+%% 	Immediately from Proposition~\ref{thm:CEKS-bisim}.
+%% \end{proof}
+
+%% \subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
+
+%% So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
+%% each other. But this does not mean they respect the semantics of the \lazyD{} 
+%% Blame Calculus. We solve prove this part in this subsection.
+
+%% The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the
+
 We use bisimulation to proof equivalence between the two machines.
 The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
-%%>>>>>>> 6d40f5173c83f5f7f7b37a4128391ca516854ac9
 definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
@@
 
-%%<<<<<<< HEAD
-\begin{lemma}[Weak bisimulation between $ \mathcal{S}(\cdot) $ and $ 
+\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and $ 
 	\mathcal{D} $]
@@
 	\end{enumerate}
-%%=======
-\begin{lemma}[Weak Bi-simulation between $ \mathcal{S}(\cdot) $ and $ 
-	\mathcal{D} $]
-	\label{thm:surely-monoidic-reduce}
-	For all cast representations $ C $, 
-	if $ C $ is surely \lazyD{} and monoidic,
-	$ s_1 \in \mathcal{D} $,
-	$ s_2 \in \mathcal{S}(C) $, and
-	$ s_1 \approx s_2 $, 
-	\begin{enumerate}
-		\item If $ \judgeDBreduce{s_1}{s_3} $,
-		then
-		there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
-		such that \begin{itemize}
-			\item $ s_5 \approx s_4 $, and
-			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-			\item $ \judgeDBreduceTrans{s_3}{s_5} $
-		\end{itemize}
-		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
-		then
-		there exist $ s_3 \in \mathcal{D} $,
-		such that \begin{itemize}
-			\item $ s_3 \approx s_4 $
-			\item $ \judgeDBreduceTrans{s_1}{s_3} $
-		\end{itemize}
-	\end{enumerate}
-%%>>>>>>> 6d40f5173c83f5f7f7b37a4128391ca516854ac9
 \end{lemma}

### 2019-10-16 paper.tex
progress on lazy UD

@@
   There is no such thing as a \lazyD{} Blame Calculus. -Jeremy}
+\todo[inline]{Actually, Wadler might disagree that the blame calculus is
+  a lazy UD calculus... because the blame calculus has polarity in the blame
+  labels, and the lazy UD calculus does not. So perhaps we should just
+  say lazy UD cast calculus, and explain that it is very close to the
+  blame calculus. -Jeremy}
 They simplify the coercion calculi by only 
@@
 
-\subsection{The \lazyUD{} cast calculus [Jeremy]}
-
-Fig.~\ref{fig:apply-Cast-UD}
+\subsection{The Blame Calculus (i.e. \lazyUD{} cast calculus) [Jeremy]}
+
+The dynamic semantics of the Blame Calculus, which we define here as a
+CEK machine, is similar to that of the \lazyD{} cast calculus
+(Fig. \ref{machine-cekc}). The only difference is in the definition of
+the $\mathit{applyCast}$ function, in which a cast whose source or
+target is the unknown type $\star$ is always split into two casts that
+go through an injectiable type, that is, a type in which all
+sub-components are the unknown type, such as $\star \to \star$. The
+definition of $\mathit{applyCast}$ for the Blame Calculus is given in
+Fig.~\ref{fig:apply-Cast-UD}.
 
@@
   \begin{array}{rclr}
+     \stxrule{I}{injectable types}{
+		\POOfun{\star}{\star} \mid \POOunit \mid \star \times \star \mid \star + \star}
     \stxrule{v}{values}{
@@
 
-\section{Background: Normal Coercion} \label{sec:coercion-calculus}
+\subsection{Coercions in Normal Form} \label{sec:coercion-calculus}
 

### 2019-10-16 paper.tex
rm hyphen in hyper-coercion
reply
rebase on cast calculus

@@
 \newcommand{\sidecond}[1]{\text{if}\;#1}
-% Lazy D blame calculus on space-inefficient CEK
-\newcommand{\judgeDBreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
-\newcommand{\judgeDBreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
-\newcommand{\judgeDBeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
+% Lazy D cast calculus on space-inefficient CEK
+\newcommand{\judgeDCreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
+\newcommand{\judgeDCreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
+\newcommand{\judgeDCeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
 \newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
@@
 \newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
+% abbrev
+\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
 
@@
   reason about formally.
-\todo[inline]{Spell it ``hypercoercion'' without the hyphen. -Jeremy}
 \end{abstract}
@@
 
-%\subsection{coercion-based approach and blame strategies}
-
-\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions with 
-labels to restore 
-blame-tracking. They also propose that there are four blame 
-strategies for their coercion:
-$ \{Lazy, Eager\} \times \{D, UD\} $. 
-Eager strategies detect more potential type errors, 
-but blame more programs.
-$ D $ and $ UD $ assign blame labels differently.
-They prove their \lazyUD{} coercion simulates the Blame Calculus in 
-\cite{wadler2009well}. It is unknown, however, whether the simulation in the 
-other direction also works.
+\citet{siek2009exploring} present another intermediate langauge for gradually 
+typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
+and space-efficiency for this language by decorating \citet{herman2010space}'s 
+coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
+with the dynamic type and cast expressions. The labels in \castCalculus\, 
+unlike their counterparts in the Blame Calculus, have no polarity. 
+They also propose that there are four blame strategies for \castCalculus{}:
+$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
+type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
+differently. They claim that their \lazyUD\ cast calculus is the same as the 
+Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
+coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
+however, whether the simulation in the other direction also works.
 \todo[inline]{Is it important to this paper whether there is a
   simulation in the other direction? -Jeremy}
+\todo[inline]{I guessed to say coercion is correct the other direction is 
+necessary. -KC}
 
@@
 
-\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
-revised coercion calculi.
-\todo[inline]{Not ``first''... lazy D is in the 2009 paper, right?
-  Or did you mean something else? -Jeremy}
-\todo[inline]{The ``Blame Calculus'' is a \lazyUD{} cast calculus.
-  There is no such thing as a \lazyD{} Blame Calculus. -Jeremy}
+\citet{siek2012interpretations} present a revised coercion calculi.
 \todo[inline]{Actually, Wadler might disagree that the blame calculus is
@@
   blame calculus. -Jeremy}
+\todo[inline]{I replace most uses of blame calculus to cast calculus.}
 They simplify the coercion calculi by only 
@@
 We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
-bisimulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
-the first bisimulation proof for the \lazyD{} Blame Calculus as far as we know.
+bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
+the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
 
@@
 
-\figref{fig:blame-static} defines the syntax of blame calculus and its
+\figref{fig:blame-static} defines the syntax of cast calculus and its
 static semantics. It is little changed from previous definitions.
@@
 
-Blame Calculus is based on Simply Typed Lambda Calculus with sum types and 
-product types ($ \mathtt{STLC+} $). 
+Our cast calculus extend the one in \citet{siek2009exploring} with sum types 
+and product types ($ \mathtt{STLC+} $). 
 Let $ S,T $ range over types. A type is either the dynamic type $ \star $
@@
 
-\subsection{The Blame Calculus (a \lazyD{} cast calculus)}
+\subsection{The \lazyD{} cast calculus}
 
@@
 
-	Reduction \fbox{$ \judgeDBreduce{s}{s} $}
+	Reduction \fbox{$ \judgeDCreduce{s}{s} $}
 	\[
@@
 
-	Evaluation \fbox{$\judgeDBeval{e}{o}$}
+	Evaluation \fbox{$\judgeDCeval{e}{o}$}
 	\[
@@
 	}{
-		\judgeDBeval{e}{o}
+		\judgeDCeval{e}{o}
 	}
@@
   You need to restrict the casts to just the inert ones. -Jeremy }
-We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
+We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
 \citet{siek2012interpretations}.
@@
 
-Transitive closure of reduction ($ \judgeDBreduceTrans{s}{s} $) and evaluation 
+Transitive closure of reduction ($ \judgeDCreduceTrans{s}{s} $) and evaluation 
 are 
@@
 
-\subsection{The Blame Calculus (i.e. \lazyUD{} cast calculus) [Jeremy]}
-
-The dynamic semantics of the Blame Calculus, which we define here as a
+\subsection{The \lazyUD{} cast calculus [Jeremy]}
+
+The dynamic semantics of the \lazyUD{} cast calculus, which we define here as a
 CEK machine, is similar to that of the \lazyD{} cast calculus
@@
 sub-components are the unknown type, such as $\star \to \star$. The
-definition of $\mathit{applyCast}$ for the Blame Calculus is given in
+definition of $\mathit{applyCast}$ for the \lazyUD{} cast calculus is given in
 Fig.~\ref{fig:apply-Cast-UD}.
@@
 	\begin{enumerate}
-		\item If $ \judgeDBreduce{s_1}{s_3} $,
+		\item If $ \judgeDCreduce{s_1}{s_3} $,
 		then
@@
 			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-			\item $ \judgeDBreduceTrans{s_3}{s_5} $
+			\item $ \judgeDCreduceTrans{s_3}{s_5} $
 		\end{itemize}
@@
 			\item $ s_3 \approx s_4 $
-			\item $ \judgeDBreduceTrans{s_1}{s_3} $
+			\item $ \judgeDCreduceTrans{s_1}{s_3} $
 		\end{itemize}
@@
 	\[
-	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeDCeval{e}{o} \; \text{if and only if} \; 
 	\judgeSeval{C}{e}{o}
@@
 	\[
-	\judgeDBeval{e}{o} \; \text{if and only if} \; 
+	\judgeDCeval{e}{o} \; \text{if and only if} \; 
 	\judgeSeval{H}{e}{o}

### 2019-10-16 paper.tex
check

--- 2019-10-16 paper.tex
@@
 
-In this section we review the normal coercion (NC) in 
-\citet{siek2012interpretations}. We ignore sum types and product types in this 
+In this section we review the normal coercions (NC) of 
+\citet{siek2012interpretations}.
+\todo[inline]{Don't abbreviate to NC. -Jeremy}
+We ignore sum types and product types in this 
 section, because they were not presented in the paper. We assume a basic 
@@
 As the name suggests, 
-hypercoercion is largely inspired by coercion, especially its subst NC. We 
+hypercoercion is largely inspired by coercion, especially its subst NC.
+\todo[inline]{``subst'' is not a word.}
+We 
 will highlight the similarity of normal coercion and hypercoercion, and hope 
@@
 as NC.
+
+\todo[inline]{I don't think we should try to convince the reader that
+  hypercoercions are easier to implement. We don't have real evidence
+  for that.}
 
@@
 \figref{fig:normal-coercion} defines the normal coercion.
+\todo[inline]{Give a summary statement about the shape of the normal form.}
 Types, pre-types, and blame labels are as before.
@@
 re-arrange cases a little bit, the definition becomes:
+\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
 \[
@@
 	\item Projections are always at the beginning when presented.
+          \todo[inline]{change ``presented'' to ``present''. }
 	\item Injections and failures are always at the end when presented.
+          \todo[inline]{change ``presented'' to ``present''. }
 \end{enumerate}
@@
 \end{figure}
+
+\todo[inline]{What is the main idea behind the organization of
+ hypercoercions?}
 

### 2019-10-16 paper.tex
minor fixes to intro

--- 2019-10-16 paper.tex
@@
   blame calculus. -Jeremy}
-\todo[inline]{I replace most uses of blame calculus to cast calculus.}
+\todo[inline]{I replace most uses of blame calculus to cast calculus. -KC}
 They simplify the coercion calculi by only 
@@
 major difficulty is from its non-structurally recursive composition.
-For instance, many developers of Grift report it is tricky to convince
+For instance, the developers of Grift report it is tricky to convince
 their proof assistants that the composition terminates.
-%
-\todo[inline]{Don't lie. There are not many developers of Grift.
-  I only know 2 people developing Grift: Andre and Deyaa. -Jeremy}
-%
+
 Secondly, the definition of normal coercion lies unnecessarily on top 
@@
   over and over again in mathematics and logic. -Jeremy}
+\todo[inline]{I guess having a notion of normal forms is more convenient when a 
+notion of normalization is convenient. But we don't even need a notion of 
+normalization for cast representations. -KC}
 
@@
 \todo[inline]{Lots of missing sections. -Jeremy}
+\todo[inline]{Will fix finally, I am moving stuff. -KC}
 

### 2019-10-16 paper.tex
explain why lazy

@@
 
-Recently, \citet{new2019gradual} show that \eager{} strategies are 
-incompatible with $\eta$-equivalence of functions, which suggest that these 
-strategies are not very ideal.
-
 So far, it seems that normal coercion is the best way to combine 
@@
 the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
-
+We care more about lazy strategies because recently, \citet{new2019gradual} 
+show that \eager{} strategies are incompatible with $\eta$-equivalence of 
+functions, which suggest that these strategies are not very ideal. 
 \todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}
+\todo[inline]{Explained, not sure if it suffice. -KC}
 

### 2019-10-16 paper.tex
fix syntax of cast calculus

@@
 \figref{fig:blame-static} defines the syntax of cast calculus and its
-static semantics. It is little changed from previous definitions.
+static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
+types and product types, and annotates function codomain explicitly. 
+Its semantics depend on blame strategies, so we defer them to sub-sections.
 \todo[inline]{Which previous definitions are you refering to?  What
-  are the little changes? -Jeremy} \todo[inline]{The term typing rule
-  for casts is broken. -Jeremy} The dynamic semantics of Blame Calculi
-depend on blame strategies, so we defer them to sub-sections.
-
-Our cast calculus extend the one in \citet{siek2009exploring} with sum types 
-and product types ($ \mathtt{STLC+} $). 
+  are the little changes? -Jeremy}
+\todo[inline]{Fixed -KC}
+\todo[inline]{The term typing rule for casts is broken. -Jeremy}
+
 Let $ S,T $ range over types. A type is either the dynamic type $ \star $

### 2019-10-16 paper.tex
fix typing of cast cal
minor fixes

@@
 \newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
+\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
 % abbrev
@@
 		\inference{
-			S \sim T & \Gamma \vdash e : S 
+			\Gamma \vdash e : T_1 & T_1 \sim T_2
 		}{
@@
   are the little changes? -Jeremy}
-\todo[inline]{Fixed -KC}
+\todoKCFixed{}
 \todo[inline]{The term typing rule for casts is broken. -Jeremy}
+\todoKCFixed{}
 
@@
   explicitly? -Jeremy}
+\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
 The end of \figref{fig:blame-static} shows the typing rules for the
@@
 Let $ o $ ranges over observations. They are what would be observed if a 
-program terminates. Observations include all value constructors and blames.
-\todo[inline]{``blames'' is incorrect. See
-https://www.wordhippo.com/what-is/the-plural-of/blame.html}
+program terminates. Observations include all value constructors and blame.
 
@@
 
-Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
-\todo[inline]{``ranges'' should be ``range'', not plural. -Jeremy}
-Let $ v $ ranges over values. A value is either a function, the 
+Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
+Let $ v $ range over values. A value is either a function, the 
 element of unit, a pair, a left injection, a right injection, or a casted value.

### 2019-10-16 paper.tex
let ... ranges => let ... range

@@
 
-Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
+Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
 in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
@@
 
-Let $ o $ ranges over observations. They are what would be observed if a 
+Let $ o $ range over observations. They are what would be observed if a 
 program terminates. Observations include all value constructors and blame.
@@
 shallow-consistent.
-Let $ r $ ranges over cast results. A cast result is either a success, which 
+Let $ r $ range over cast results. A cast result is either a success, which 
 brings a value, or a failure, which brings a blame label.
-Let $ s $ ranges over machine states. A state is either looking at an 
+Let $ s $ range over machine states. A state is either looking at an 
 expression to decide what to do next, returning a value to a continuation, or 
 halting with an observation.
-Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
+Let $ \kappa $ range over continuations. $ \mathtt{mt} $ is the top 
 continuation. The remaining continuations correspond to expressions. For 
@@
 Types, pre-types, and blame labels are as before.
-Let $ I $ ranges over injectable types. An injectable type is a type that can 
+Let $ I $ range over injectable types. An injectable type is a type that can 
 be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
@@
 is injectable. 
-Let $ c $ ranges over coercions, a coercion is either injection, projection, 
+Let $ c $ range over coercions, a coercion is either injection, projection, 
 identity, failure, sequencing, or function coercion.
-Let $ \bar{c} $ ranges over wrapper coercions, which represent casts in $ 
+Let $ \bar{c} $ range over wrapper coercions, which represent casts in $ 
 \vOOcast{v}{c} $.
-Let $ \hat{c} $ ranges over normal coercions. If we inline $ \bar{c} $ and 
+Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
 re-arrange cases a little bit, the definition becomes:
@@
 
-Let $ c $ ranges over hypercoercions. A hypercoercion is either 
+Let $ c $ range over hypercoercions. A hypercoercion is either 
 an identity cast between the dynamic types, or a complex including a head, a 
 middle, and a tail. 
-Let $ h $ ranges over heads. A head is either a no-op, or a projection.
-Let $ m $ ranges over middles. There is a one-to-one 
+Let $ h $ range over heads. A head is either a no-op, or a projection.
+Let $ m $ range over middles. There is a one-to-one 
 correspondence between middles and type constructors. 
 We generalize shallow-consistency to middles $ m \smile m $ in the natural way.
-Let $ t $ ranges over tails. A tail is either a no-op, an injection, or a 
+Let $ t $ range over tails. A tail is either a no-op, an injection, or a 
 failure. 
-Let $ \ell $ ranges over no-op and labels. It is useful when we introduce 
+Let $ \ell $ range over no-op and labels. It is useful when we introduce 
 composition of hypercoercions.
@@
 \figref{machine-cekcc} defines the machine. 
-Let $ v $ ranges over value. A value is either the unit value, function, pair, 
+Let $ v $ range over value. A value is either the unit value, function, pair, 
 left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
 Cast results ($ r $) and machine states ($ s $) are as before. 
-Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
+Let $ \kappa $ range over continuations and let $ k $ range over 
 pre-continuations. 

### 2019-10-16 paper.tex
cite => citep

@@
 Around 2006, many work on integrating dynamic typing and static typing emerge, 
-notably gradual types \cite{siek2006gradual} and hybrid types 
-\cite{flanagan2006hybrid}. 
+notably gradual types \citep{siek2006gradual} and hybrid types 
+\citep{flanagan2006hybrid}. 
 Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
@@
 In 2007, \citet{herman2010space} proposes a solution to this problem by 
-representing casts with coercion \cite{henglein1994dynamic}, 
+representing casts with coercion \citep{henglein1994dynamic}, 
 which can be composed and normalized. Every coercion looks like a list of 
@@
 space-efficiency and blame-tracking: normal coercion is claimed easy to 
-understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
-easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
+understand \citep{garcia2013calculating}\citep{siek2015blame} and is shown 
+easy enough to implement in a compiler \citep{kuhlenschmidt2018efficient}.
 Normal coercion is still not satisfactory, however, in at least two aspects.
@@
 candidate. It is believed even more complicated than threesome 
-\cite{siek2015blame}. In fact, it uses 10 constructors to deal with an 
+\citep{siek2015blame}. In fact, it uses 10 constructors to deal with an 
 elementary type system with only base types and 

### 2019-10-17 paper.tex
presented -> present
revise normal coercion

@@
   some words don't have a plural form, like ``blame''. -Jeremy}
-
+\todo[inline]{Will fix grammar after fixing all other problems -KC}
 \todo[inline]{The first paragraph of the introduction should summarize
   the entire introduction, and in some sense, the entire paper. -Jeremy}
-
-\todo[inline]{BTW, using the Coercion and Blame paper as a model for
-  how to write papers is perhaps not the best idea. That paper intentionally
-  diverged from the normal paper format in several ways. You can
-  do that too after you've become a master at writing papers.
-  For now you are much better off following the advice of
-  Simon Peyton Jones about how to write a paper (google it).}
 
@@
 \citet{siek2012interpretations} present a revised coercion calculi.
-\todo[inline]{Actually, Wadler might disagree that the blame calculus is
-  a lazy UD calculus... because the blame calculus has polarity in the blame
-  labels, and the lazy UD calculus does not. So perhaps we should just
-  say lazy UD cast calculus, and explain that it is very close to the
-  blame calculus. -Jeremy}
-\todo[inline]{I replace most uses of blame calculus to cast calculus. -KC}
 They simplify the coercion calculi by only 
@@
 
-	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} Blame 
-	Calculus}
+	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} cast 
+	calculus}
 	\label{machine-cekc}
@@
   the value first and the cast second. -Jeremy}
-\todo[inline]{The definition of values is too loose for a cast.
-  You need to restrict the casts to just the inert ones. -Jeremy }
 We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
@@
 equivalent to an abstract machine that represents casts with hypercoercions.
-
-\todoKC{change the reduction rules of case}
 
@@
 
-In this section we review the normal coercions (NC) of 
-\citet{siek2012interpretations}.
-\todo[inline]{Don't abbreviate to NC. -Jeremy}
+In this section we review the normal coercions \citep{siek2012interpretations} 
+to motivate the design of hypercoercion. 
 We ignore sum types and product types in this 
-section, because they were not presented in the paper. We assume a basic 
+section, because they were not in the paper. We assume a basic 
 familiarity with coercion, and direct readers who do not know it to 
 \citet{siek2012interpretations}.
-
-As the name suggests, 
-hypercoercion is largely inspired by coercion, especially its subst NC.
-\todo[inline]{``subst'' is not a word.}
-We 
-will highlight the similarity of normal coercion and hypercoercion, and hope 
-this would convince you that hypercoercion should be as difficult to implement 
-as NC.
-
-\todo[inline]{I don't think we should try to convince the reader that
-  hypercoercions are easier to implement. We don't have real evidence
-  for that.}
+%We 
+%will highlight the similarity of normal coercion and hypercoercion, and hope 
+%this would convince you that hypercoercion should be as difficult to implement 
+%as normal coercions.
+%\todo[inline]{I don't think we should try to convince the reader that
+%  hypercoercions are easier to implement. We don't have real evidence
+%  for that.}
 
@@
 
+\todo[inline]{Give a summary statement about the shape of the normal form.}
+\todo[inline]{The three-part shape is not obvious before the transformation at 
+the end of the next paragraph. So the summary is given after that. -KC}
+
 \figref{fig:normal-coercion} defines the normal coercion.
-\todo[inline]{Give a summary statement about the shape of the normal form.}
 Types, pre-types, and blame labels are as before.
@@
 Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
-re-arrange cases a little bit, the definition becomes:
-\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
+re-order the cases, the definition of $ \hat{c} $ becomes:
 \[
@@
 	\item The length of normal coercion is at most three.
-	\item Projections are always at the beginning when presented.
-          \todo[inline]{change ``presented'' to ``present''. }
-	\item Injections and failures are always at the end when presented.
-          \todo[inline]{change ``presented'' to ``present''. }
+	\item Projections are always at the beginning when present.
+	\item Injections and failures are always at the end when present.
 \end{enumerate}

### 2019-10-17 paper.tex
reformat replies

@@
 \begin{abstract}
-\todoKC{rewrite this abstract based on the comparision table. -Jeremy}
+\todoKC{rewrite this abstract based on the comparision table.}
   Gradual Typing is great. Implementing gradually typed with blame
@@
   the rules of English regarding plurals. The rules are tricky...
-  some words don't have a plural form, like ``blame''. -Jeremy}
-\todo[inline]{Will fix grammar after fixing all other problems -KC}
+  some words don't have a plural form, like ``blame''. -Jeremy
+  \\---\\
+  Will fix grammar after fixing all other problems -KC}
 \todo[inline]{The first paragraph of the introduction should summarize
@@
 \todo[inline]{Is it important to this paper whether there is a
-  simulation in the other direction? -Jeremy}
-\todo[inline]{I guessed to say coercion is correct the other direction is 
+simulation in the other direction? -Jeremy
+\\ --- \\
+I guessed to say coercion is correct the other direction is 
 necessary. -KC}
@@
   not a negative. For example, the notion of normal forms comes up
-  over and over again in mathematics and logic. -Jeremy}
-\todo[inline]{I guess having a notion of normal forms is more convenient when a 
+  over and over again in mathematics and logic. -Jeremy
+\\ --- \\
+I guess having a notion of normal forms is more convenient when a 
 notion of normalization is convenient. But we don't even need a notion of 
@@
 functions, which suggest that these strategies are not very ideal. 
-\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}
-\todo[inline]{Explained, not sure if it suffice. -KC}
+\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
+	\\ --- \\ Explained, not sure if it suffice. -KC}
 
@@
 \todo[inline]{Lots of missing sections. -Jeremy}
-\todo[inline]{Will fix finally, I am moving stuff. -KC}
 
@@
 \todo[inline]{Which previous definitions are you refering to?  What
-  are the little changes? -Jeremy}
-\todoKCFixed{}
-\todo[inline]{The term typing rule for casts is broken. -Jeremy}
-\todoKCFixed{}
+  are the little changes? -Jeremy
+\\ --- \\ Fixed -KC}
+\todo[inline]{The term typing rule for casts is broken. -Jeremy
+\\ --- \\ Fixed -KC}
 
@@
 \todo[inline]{Why do you annotate the codomain of lambda abstractions
-  explicitly? -Jeremy}
-\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
+  explicitly? -Jeremy
+  \\---\\
+  Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
 The end of \figref{fig:blame-static} shows the typing rules for the
@@
 \todo[inline]{Change the order of parameters for applyCast to take
-  the value first and the cast second. -Jeremy}
+  the value first and the cast second. -Jeremy
+\\---\\
+Could you tell me why taking the value first is better?
+I am always taking the target of induction/match first. -KC}
 We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
@@
 
-\todo[inline]{Give a summary statement about the shape of the normal form.}
-\todo[inline]{The three-part shape is not obvious before the transformation at 
+\todo[inline]{Give a summary statement about the shape of the normal form. 
+-Jeremy
+\\---\\The three-part shape is not obvious before the transformation at 
 the end of the next paragraph. So the summary is given after that. -KC}

### 2019-10-17 paper.tex
split the fig of the first CEK

@@
 
+	\caption{Syntax of CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} 
+	cast calculus}
+\label{machine-cekc-syntax}
+\end{figure}
+
+\begin{figure}
 %	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
@@
 
-	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} cast 
-	calculus}
-	\label{machine-cekc}
+	\caption{Reduction rules of CEK abstract machine ($ \mathcal{D} $) for the 
+	\lazyD{} cast calculus}
+	\label{machine-cekc-reduction}
 \end{figure}
 
-Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
-Calculus in the style of CEK machines \citep{felleisen1986control}.
+Fig.~\ref{machine-cekc-syntax} defines the syntax of a CEK machine 
+\citep{felleisen1986control} evaluating 
+the \lazyD{} cast calculus.
 \todo[inline]{Briefly present the main ideas regarding how a CEK

### 2019-10-17 paper.tex
replace more uses of blame calculus to cast calculus

@@
 They conjecture that their revised coercion calculi bisimulate the 
-corresponding Blame Calculi.
+corresponding cast calculi.
 
@@
 The structure of this paper is as follows. 
-Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
-Calculi. 
+Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ cast 
+calculi. 
 Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 

### 2019-10-17 paper.tex
move cast calc value typing

@@
 \newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
-\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
+\newcommand{\eOOcast}[2]{#1 \langle #2 \rangle}
 \newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
@@
 	}
+	\stxrule{I}{injectable types (\lazyD)}{
+		P
+	}
+	\stxrule{I}{injectable types (\lazyUD)}{
+		\POOunit \mid
+		\POOfun{\star}{\star} \mid
+		\star \times \star \mid
+		\star + \star
+	}
 	\stxrule{e}{terms}{
@@
 	\stxrulecont{
-		\eOOcast{e}{T_1}{l}{T_2} \mid
+		\eOOcast{e}{c} \mid
 		\eOOblame{l}
+	}
+	\stxrule{v}{values}{
+		\vOOfun{\rho}{x}{e} \mid
+		\vOOtt{} \mid
+		\vOOcons{v_1}{v_2} \mid
+		\vOOinl{v} \mid
+		\vOOinr{v} \mid		
+		\vOOcast{v}{c}
+	}
+	\stxrule{c}{casts}{
+		\cOOcast{T_1}{l}{T_2}
 	}
@@
 		}{
-			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
+			\judgetype{\Gamma}{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{T_2}
 		} \quad
@@
 			\judgetype{\Gamma}{\eOOblame{l}}{T}
+		}
+	\end{gather*}
+
+	Value typing \fbox{$ v : T $}
+	\begin{gather*}
+	\dots \quad
+	\inference{
+		v : I
+	}{
+		\vOOcast{v}{\cOOcast{I}{l}{\TOOdyn}} : \TOOdyn
+	}
+	\quad
+	\inference{
+		v : P_1 &
+		P_1 \smile P_2
+	}{
+		\vOOcast{v}{\cOOcast{P_1}{l}{P_2}} : P_2
 	}
@@
 \figref{fig:blame-static} defines the syntax of cast calculus and its
-static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
-types and product types, and annotates function codomain explicitly. 
-Its semantics depend on blame strategies, so we defer them to sub-sections.
+static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
+types and product types. Besides, we annotate function codomain explicitly 
+because we need the codomain when evaluating cast calculus with hypercoercions.
 \todo[inline]{Which previous definitions are you refering to?  What
@@
 \\ --- \\ Fixed -KC}
-
+\todo[inline]{Why do you annotate the codomain of lambda abstractions
+	explicitly? -Jeremy
+	\\---\\
+	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
 Let $ S,T $ range over types. A type is either the dynamic type $ \star $
@@
 codomain of lambda abstractions explicitly.
-\todo[inline]{Why do you annotate the codomain of lambda abstractions
-  explicitly? -Jeremy
-  \\---\\
-  Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
 The end of \figref{fig:blame-static} shows the typing rules for the
@@
 	\begin{array}{rclr}
-
-	\stxrule{v}{values}{
-		\vOOfun{\rho}{x}{b} \mid
-		\vOOtt{} \mid
-		\vOOcons{v_1}{v_2} \mid
-		\vOOinl{v} \mid
-		\vOOinr{v} \mid		
-		\vOOcast{v}{c}
-	}
-	\stxrule{c}{casts}{
-		\cOOcast{T_1}{l}{T_2}
-	}
 	\stxrule{r}{cast results}{
@@
 	\]
-
-	Value typing \fbox{$ v : T $}
-	\begin{gather*}
-	\dots \quad
-	\inference{
-		v : P &
-		c : P \Longrightarrow T &
-		P \smile T
-	}{
-		\vOOcast{v}{\cOOcast{P}{l}{T}} : T
-	}
-	\end{gather*}
 
@@
 	\redrule{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
 	}{
@@
   \begin{array}{rclr}
-     \stxrule{I}{injectable types}{
-		\POOfun{\star}{\star} \mid \POOunit \mid \star \times \star \mid \star + \star}
     \stxrule{v}{values}{
@@
 	\redruleS{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
 	}{

### 2019-10-17 paper.tex
revise bg:cast calc

@@
 	}
+	\stxrule{c}{casts}{
+		\cOOcast{T_1}{l}{T_2}
+	}
+	\stxrule{e}{terms}{
+		\eOOvar{x} \mid{}
+		\eOOsole{} \mid{}
+		\eOOlam{T_1}{T_2}{x}{e} \mid
+		\eOOapp{e_1}{e_2}
+	}
+	\stxrulecont{
+		\eOOcons{e_1}{e_2} \mid
+		\eOOcar{e} \mid
+		\eOOcdr{e}
+	}
+	\stxrulecont{
+		\eOOinl{e} \mid
+		\eOOinr{e} \mid
+		\eOOcase{e_1}{e_2}{e_3}
+	}
+	\stxrulecont{
+		\eOOcast{e}{c} \mid
+		\eOOblame{l}
+	}
 	\stxrule{I}{injectable types (\lazyD)}{
@@
 		\star + \star
-	}
-	\stxrule{e}{terms}{
-		\eOOvar{x} \mid{}
-		\eOOsole{} \mid{}
-		\eOOlam{T_1}{T_2}{x}{e} \mid
-		\eOOapp{e_1}{e_2}
-	}
-	\stxrulecont{
-		\eOOcons{e_1}{e_2} \mid
-		\eOOcar{e} \mid
-		\eOOcdr{e}
-	}
-	\stxrulecont{
-		\eOOinl{e} \mid
-		\eOOinr{e} \mid
-		\eOOcase{e_1}{e_2}{e_3}
-	}
-	\stxrulecont{
-		\eOOcast{e}{c} \mid
-		\eOOblame{l}
 	}
@@
 		\vOOcast{v}{c}
-	}
-	\stxrule{c}{casts}{
-		\cOOcast{T_1}{l}{T_2}
 	}
@@
 	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
-Let $ S,T $ range over types. A type is either the dynamic type $ \star $
+Let $ T $ range over types. A type is either the dynamic type $ \star $
 (a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
 or a pre-type. 
-Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
+Let $ P $ range over pre-types. Every pre-type is a type with a type 
 constructor at the top. For simplicity, we only have one base type, $ \POOunit 
@@
 
-%$ S \sim T $ reads ``$ S $ and $ T $ are consistent''.
-%Two types are consistent if one of them is $ \star $, or they have the same 
-%top-most type constructor and the corresponding sub-parts are consistent. 
-%The intuition of $ S \sim T $ is that $ S $ and $ T $ have no conflict type 
-%information. Consistency is reflexive and symmetric, but not transitive.
-
-%One might be tempted to conclude that inconsistency is the root of all runtime 
-%type errors (blames). In the setting of gradual typing, however, runtime 
-%type-checking is usually gradual as well. 
-$ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
-are shallowly consistent if one of them is $ \star $, or they have the same 
-type constructor at the top. Shallow-inconsistency is the root of all blame in 
-lazy cast strategies -- casting a value to a shallowly inconsistent type leads 
-to a blame. Shallow-consistency is reflexive, symmetric, but 
+$ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
+The intuition of $ T_1 \sim T $ is that $ T_1 $ and $ T_2 $ have no conflict 
+type information. Two types are consistent if one of them is $ \star $, or they 
+have the same top-most type constructor and the corresponding sub-parts are 
+consistent. Consistency is reflexive and symmetric, but not transitive.
+
+$ T_1 \smile T_2 $ reads ``$ T_1 $ and $ T_2 $ are shallowly-consistent''. Two 
+types are shallowly consistent if one of them is $ \star $, or they have the 
+same type constructor at the top. Shallow-inconsistency is the root of all 
+blame in lazy cast strategies -- casting a value to a shallowly inconsistent 
+type leads to a blame. Shallow-consistency is reflexive, symmetric, but 
 not transitive.
 
-Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
-in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
-codomain of lambda abstractions explicitly.
-The end of \figref{fig:blame-static} shows the typing rules for the
-additional terms.
+Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
+of lambda abstractions explicitly because we need it when evaluating cast 
+calculus with hypercoercion. We have two additional terms: cast expressions and 
+blame expressions. Cast expressions insert runtime type checks. And blame 
+expressions raise an error. The end of \figref{fig:blame-static} shows the 
+typing rules for the additional terms.
 

### 2019-10-17 paper.tex
reorder syntax of cast calculus
revise static sem. of cast calc

@@
 		\eOOlam{T_1}{T_2}{x}{e} \mid
-		\eOOapp{e_1}{e_2}
-	}
-	\stxrulecont{
+		\eOOapp{e_1}{e_2} \mid
 		\eOOcons{e_1}{e_2} \mid
@@
 		\eOOinr{e} \mid
-		\eOOcase{e_1}{e_2}{e_3}
-	}
-	\stxrulecont{
+		\eOOcase{e_1}{e_2}{e_3} \mid
 		\eOOcast{e}{c} \mid
 		\eOOblame{l}
+	}
+	\stxrule{v}{values}{
+		\vOOtt{} \mid
+		\vOOfun{\rho}{x}{e} \mid
+		\vOOcons{v_1}{v_2} \mid
+		\vOOinl{v} \mid
+		\vOOinr{v} \mid		
+		\vOOcast{v}{c}
 	}
@@
 		\star + \star
-	}
-	\stxrule{v}{values}{
-		\vOOfun{\rho}{x}{e} \mid
-		\vOOtt{} \mid
-		\vOOcons{v_1}{v_2} \mid
-		\vOOinl{v} \mid
-		\vOOinr{v} \mid		
-		\vOOcast{v}{c}
 	}
@@
 blame expressions. Cast expressions insert runtime type checks. And blame 
-expressions raise an error. The end of \figref{fig:blame-static} shows the 
-typing rules for the additional terms.
+expressions raise an error. The typing rules for the additional terms are
+straightforward.
+
+Let $ v $ range over values. A value is either the unit, a function (a 
+closure), a pair, a left injection, a right injection, or a 
+casted value. As shown 
+by the value typing rules, if the target type of a casted value is the dynamic 
+type, the underlying value must be of an injectable type. The definition of 
+injectable types depends on blame strategies: for the \lazyD\ strategy, every 
+pre-type is injectable; for the \lazyUD\ strategy, a pre-types is injectable if 
+and only if all its sub-parts are the dynamic type. If the target type of a 
+casted value is a pre-type, the type of the underlying value must have the same 
+type constructor.
 

### 2019-10-17 paper.tex
restructure sec. background

@@
 
-\section{Background: Cast Calculi} \label{sec:blame-calculus}
-
+\section{Background} \label{sec:blame-calculus}
+
+In this section, we review lazy cast calculi (\ref{sec:cast-calculi}) and
+normal coercion (\ref{sec:coercion-calculus}).
+
+\subsection{Cast Calculi}
+\label{sec:cast-calculi}
 \begin{figure}
@@
 
-\figref{fig:blame-static} defines the syntax of cast calculus and its
+\figref{fig:blame-static} defines the syntax of cast calculi and its
 static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
@@
 
-Now let's move to the dynamic semantics.
-
-\subsection{The \lazyD{} cast calculus}
-
-\begin{figure}
-	Syntax
-	\[
-	\begin{array}{rclr}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
-
-	\stxrule{\kappa}{continuations}{
-		\mathtt{stop} \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
-	}
-	\stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{fst} \; \kappa \mid{}
-		\mathtt{snd} \; \kappa \mid
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
-	}
-	\stxrulecont{	
-		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
-		\langle c \rangle \kappa
-	}
-	\end{array}
-	\]
-
-	\caption{Syntax of CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} 
-	cast calculus}
-\label{machine-cekc-syntax}
-\end{figure}
-
 \begin{figure}
@@
 
+	Syntax
+	\[
+	\begin{array}{rclr}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+
+	\stxrule{\kappa}{continuations}{
+		\mathtt{stop} \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{fst} \; \kappa \mid{}
+		\mathtt{snd} \; \kappa \mid
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
+	}
+	\stxrulecont{	
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
+		\langle c \rangle \kappa
+	}
+	\end{array}
+	\]
+	Syntax
+	\[
+	\begin{array}{rclr}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+
+	\stxrule{\kappa}{continuations}{
+		\mathtt{stop} \mid{}
+		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{cons_2} \; v \; \kappa \mid{}
+		\mathtt{inl} \; \kappa \mid{}
+		\mathtt{inr} \; \kappa
+	}
+	\stxrulecont{
+		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
+		\mathtt{app_2} \; v \; \kappa \mid{}
+		\mathtt{fst} \; \kappa \mid{}
+		\mathtt{snd} \; \kappa \mid
+		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
+	}
+	\stxrulecont{	
+		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
+		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
+		\langle c \rangle \kappa
+	}
+	\end{array}
+	\]
+
 	Reduction \fbox{$ \judgeDCreduce{s}{s} $}
@@
 
-	\fbox{$applyCast(c,v) = r$}
-	\[
-	\begin{array}{rclr}
-	\funrule{
-		applyCast(\cOOcast{\star}{l}{\star},v)
-	}{
-		\rOOsucc{v}
-	}{}
-	\funrule{
-		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
-	}{
-		applyCast(\cOOcast{P_1}{l}{P_2},v)
-	}{}
-	\funrule{
-		applyCast(\cOOcast{P}{l}{\star},v)
-	}{
-		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
-	}{}
-	\funrule{
-		applyCast(\cOOcast{P_1}{l}{P_2},v)
-	}{
-		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
-	}{\sidecond{P_1 \smile P_2}}
-	\funrule{
-		applyCast(\cOOcast{P_1}{l}{P_2},v)
-	}{
-		\rOOfail{l}
-	}{\sidecond{\neg P_1 \smile P_2}}
-
-	\end{array}
-	\]
-
-%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s $}\\
+	%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s 
+	%$}\\
 
@@
 
-	\caption{Reduction rules of CEK abstract machine ($ \mathcal{D} $) for the 
-	\lazyD{} cast calculus}
-	\label{machine-cekc-reduction}
+	\caption{dynamic semantics of the cast calculi as a CEK machine}
+	\label{machine-cekc}
 \end{figure}
 
-Fig.~\ref{machine-cekc-syntax} defines the syntax of a CEK machine 
-\citep{felleisen1986control} evaluating 
-the \lazyD{} cast calculus.
+Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
+CEK machine \citep{felleisen1986control}.
 \todo[inline]{Briefly present the main ideas regarding how a CEK
 	machine works. (2-3 sentences) -Jeremy}
-\todo[inline]{Use citep to put a citation in parentheses, as I've
-  done above. -Jeremy }
-\todo[inline]{The figure is too tall. You may need to pull some things
-  out of the figure, such as the value typing. -Jeremy}
 \todo[inline]{Please fill in the missing reduction rules. -Jeremy}
@@
 	I am always taking the target of induction/match first. -KC}
-We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
-\citet{siek2012interpretations}.
-We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
-equivalent to an abstract machine that represents casts with hypercoercions.
 
@@
 
+\subsection{The \lazyD{} cast calculus}
+
+\begin{figure}
+
+	\fbox{$applyCast(c,v) = r$}
+	\[
+	\begin{array}{rclr}
+	\funrule{
+		applyCast(\cOOcast{\star}{l}{\star},v)
+	}{
+		\rOOsucc{v}
+	}{}
+	\funrule{
+		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
+	}{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{}
+	\funrule{
+		applyCast(\cOOcast{P}{l}{\star},v)
+	}{
+		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
+	}{}
+	\funrule{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{
+		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
+	}{\sidecond{P_1 \smile P_2}}
+	\funrule{
+		applyCast(\cOOcast{P_1}{l}{P_2},v)
+	}{
+		\rOOfail{l}
+	}{\sidecond{\neg P_1 \smile P_2}}
+
+	\end{array}
+	\]
+	\caption{Definition of $ applyCast $ for \lazyD}
+\end{figure}
+
+We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
+\citet{siek2012interpretations}.
+We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
+equivalent to an abstract machine that represents casts with hypercoercions.
+
 \subsection{The \lazyUD{} cast calculus [Jeremy]}
@@
 \begin{figure}
-
-  Syntax
-  \[
-  \begin{array}{rclr}
-    \stxrule{v}{values}{
-      \cdots \mid 
-      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
-      \vOOcast{v}{ \cOOcast{P}{l}{P} }
-    }
-  \end{array}
-  \]
-
+%
+%  Syntax
+%  \[
+%  \begin{array}{rclr}
+%    \stxrule{v}{values}{
+%      \cdots \mid 
+%      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
+%      \vOOcast{v}{ \cOOcast{P}{l}{P} }
+%    }
+%  \end{array}
+%  \]
+%  
   \fbox{$\mathit{applyCast}(v,c) = r$}
@@
 
-\subsection{Coercions in Normal Form} \label{sec:coercion-calculus}
+\subsection{Coercions in Normal Form} 
+\label{sec:coercion-calculus}
 

### 2019-10-17 paper.tex
explain CEK

@@
 coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
-with the dynamic type and cast expressions. The labels in \castCalculus\, 
+with the dynamic type and cast expressions. The labels in \castCalculus{}, 
 unlike their counterparts in the Blame Calculus, have no polarity. 
@@
 	\]
-	Syntax
-	\[
-	\begin{array}{rclr}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
-
-	\stxrule{\kappa}{continuations}{
-		\mathtt{stop} \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
-	}
-	\stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{fst} \; \kappa \mid{}
-		\mathtt{snd} \; \kappa \mid
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
-	}
-	\stxrulecont{	
-		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
-		\langle c \rangle \kappa
-	}
-	\end{array}
-	\]
 
@@
 Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
-CEK machine \citep{felleisen1986control}.
+CEK machine \citep{felleisen1986control}. CEK machines include continuation as 
+part of their states. They evaluate expressions with two interleaving 
+processes: 
+(1) dive into an expression and extend the continuation;
+(2) return a value to the current continuation.
 \todo[inline]{Briefly present the main ideas regarding how a CEK
-	machine works. (2-3 sentences) -Jeremy}
+	machine works. (2-3 sentences) -Jeremy
+\\---\\Fixed -KC}
+
+Most existing proofs about cast calculi defines the dynamic semantics with 
+reduction semantics. We use a CEK machine instead because one of us is more 
+familiar with CEK machines, and that he believes CEK machines are more 
+convenient because space-efficiency is about compressing continuations.
+\todo[inline]{Explain why you are using a CEK machine instead of
+	reduction semantics. -Jeremy
+\\---\\Fixed -KC}
+
 \todo[inline]{Please fill in the missing reduction rules. -Jeremy}
-\todo[inline]{Explain why you are using a CEK machine instead of
-	reduction semantics. -Jeremy}
 \todo[inline]{Change the order of parameters for applyCast to take
@@
 	Could you tell me why taking the value first is better?
-	I am always taking the target of induction/match first. -KC}
+	I am always taking the target of induction first. -KC}
 

### 2019-10-17 paper.tex
revise ineff CEK

@@
 
+Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
+
 Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
@@
 
-Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
-Let $ v $ range over values. A value is either a function, the 
-element of unit, a pair, a left injection, a right injection, or a casted value.
-The cast around a casted value is not arbitrary, as shown by value typing: the 
-source type must be a pre-type, and the source and the target must be 
-shallow-consistent.
 Let $ r $ range over cast results. A cast result is either a success, which 
-brings a value, or a failure, which brings a blame label.
+brings back a value, or a failure, which brings a blame label.
+
 Let $ s $ range over machine states. A state is either looking at an 
@@
 halting with an observation.
-Let $ \kappa $ range over continuations. $ \mathtt{mt} $ is the top 
+
+Let $ \kappa $ range over continuations. $ \mathtt{stop} $ is the top 
 continuation. The remaining continuations correspond to expressions. For 
@@
 
-In the reduction rules, to evaluate a cast expression, the machine move the 
+In the reduction relation $ \judgeDCreduce{s}{s} $, to evaluate a cast 
+expression, the machine move the 
 cast to the continuation and evaluate the inner expression. To apply a casted 
@@
 
-Transitive closure of reduction ($ \judgeDCreduceTrans{s}{s} $) and evaluation 
-are 
-standard.
+The reflexive transitive closure of reduction ($ \judgeDCreduceTrans{s}{s} $) 
+and evaluation ($ \judgeDCeval{e}{o} $) are standard.
 

### 2019-10-17 paper.tex
minor fix for lazyD cast calc

@@
 
-In the reduction relation $ \judgeDCreduce{s}{s} $, to evaluate a cast 
+The reduction relation $ \judgeDCreduce{s}{s} $ depends on $ applyCast $, a 
+function depending on blame strategies. We will give the definitions of $ 
+applyCast $ shortly.
+To evaluate a cast 
 expression, the machine move the 
@@
 	the case function should not be recursive. -Jeremy}
-Along the way, the machine accumulate the pending casts onto the 
+Along the way, the machine accumulates the pending casts onto the 
 continuations. To cast a value, the machine try to apply the cast to the value. 
@@
 \subsection{The \lazyD{} cast calculus}
+\todo[inline]{I want to merge this and the following subsetion to the 
+subsection above. -KC}
 
@@
 	\caption{Definition of $ applyCast $ for \lazyD}
+	\label{fig:applyCast-D-C}
 \end{figure}
 
-We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
-\citet{siek2012interpretations}.
-We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
-equivalent to an abstract machine that represents casts with hypercoercions.
+\figref{fig:applyCast-D-C} defines the $ applyCast $ for \lazyD. 
+We conjecture that with this $ applyCast $, the CEK machine in 
+\figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
+\citet{siek2009exploring}.
 

### 2019-10-17 paper.tex
minor fixes

@@
 This section presents our second contribution, a space-efficient CEK abstract 
-machine. This machine is parameterized over \emph{cast representation} (CR).
+machine. This machine is parameterized over \emph{cast representation}.
 
@@
 $\mathcal{D}$}
-
-% Did you really mean to delete all the following? -Jeremy
-%% With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-%% all machines instantiated with these CRs bisimulate each other. 
-%% The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
-%% derived from the definition of states.
-%% \todo[inline]{The term ``bisimilarity'' has a different technical meaning from
-%%   ``bisimulation relation''. I don't think you are using it properly
-%%   in the above sentence. -Jeremy}
-%% We omit subscripts when there is no 
-%% ambiguity.
-%% \begin{gather*}
-%% \inference{
-%% 	\rho_1 \approx \rho_2 &
-%% 	\kappa_1 \approx \kappa_2
-%% }{
-%% 	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-%% }
-%% \quad
-%% \inference{
-%% 	\kappa_1 \approx \kappa_2 &
-%% 	v_1 \approx v_2
-%% }{
-%% 	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-%% }
-%% \quad
-%% \inference{
-%% }{
-%% 	\sOOhalt{o} \approx \sOOhalt{o}
-%% }
-%% \end{gather*}
-
-%% The relations between continuations, pre-continuations, enviroments, values, 
-%% cast results are also derived from their definitions. But the relation for 
-%% casts is special: \begin{gather*}
-%% \inference{
-%% }{
-%% 	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
-%% }
-%% \quad
-%% \inference{
-%% }{
-%% 	id_1(T) \approx id_2(T)
-%% }
-%% \quad
-%% \inference{
-%% 	c_1 \approx c_2 &
-%% 	c_3 \approx c_4
-%% }{
-%% 	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
-%% }
-%% \end{gather*}
-
-%% \begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
-%% 	\label{thm:CEKS-bisim}
-%% 	If 
-%% 	$ C_1 $ and $ C_2 $ are surely \lazyD,
-%% 	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
-%% 	$ s_1 \approx s_3 $,
-%% 	$ \judgeSreduce{C_1}{s_1}{s_2} $,
-%% 	then there exists an $ s_4 $ such that
-%% 	\begin{itemize}
-%% 	\item $ s_2 \approx s_4 $ and
-%% 	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
-%% 	\end{itemize}
-%% \end{proposition}
-%% \begin{proof}
-%% 	The key ideas of this proof are undoing sequencing with the property (2) of 
-%% 	surely \lazyD{} CR, and handling all possibly uses of $ 
-%% 	cast(T,l,T) $ with property (3)-(11).
-%% \end{proof}
-
-%% \begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
-%% 	\label{thm:surely-lazyD-eqv}
-%% 	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-%% 	are surely \lazyD cast representations,
-%% 	\[
-%% 	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-%% 	e \Downarrow_{S(C_2)} o
-%% 	\]
-%% \end{proposition}
-%% \begin{proof}
-%% 	Immediately from Proposition~\ref{thm:CEKS-bisim}.
-%% \end{proof}
-
-%% \subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}
-
-%% So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
-%% each other. But this does not mean they respect the semantics of the \lazyD{} 
-%% Blame Calculus. We solve prove this part in this subsection.
-
-%% The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the
 
@@
 
-With the properties of surely \lazyD{} CR, it is straightforward to proof that 
-all machines instantiated with these CRs bisimulate each other. 
+With the properties of surely \lazyD{} cast representation, it is 
+straightforward to proof that 
+all machines instantiated with these cast representations bisimulate each 
+other. 
 The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
@@
 	The key ideas of this proof are undoing sequencing with the property (2) of 
-	surely \lazyD{} CR, and handling all possibly uses of $ 
+	surely \lazyD{} cast representation, and handling all possibly uses of $ 
 	cast(T,l,T) $ with property (3)-(11).

### 2019-10-17 paper.tex
comment
check

@@
 \todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
-	\\ --- \\ Explained, not sure if it suffice. -KC}
+  \\ --- \\ Explained, not sure if it suffice. -KC
+  \\ --- \\
+  That's good that you explained why lazy instead of eager.
+  (Also, you should add that we are interested in lazy because
+  that's what Grift does.)\\
+  But you haven't explained why we are interested in both D and UD. -JS
+}
 
@@
 	\\---\\
-	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
+	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
+        \\---\\
+        The answer you put in the text is to vague. -JS
+        }
 Let $ T $ range over types. A type is either the dynamic type $ \star $
@@
 	Could you tell me why taking the value first is better?
-	I am always taking the target of induction first. -KC}
+	I am always taking the target of induction first. -KC
+	\\---\\
+        It's better because it matches the postfix syntax we are using for
+        casts. Currently line 2 of applyCast for D is difficult to read,
+        compare it with line 4 of applyCast for UD. -JS
+        }
 

### 2019-10-17 paper.tex
comments

@@
   the rules of English regarding plurals. The rules are tricky...
-  some words don't have a plural form, like ``blame''. -Jeremy
+  some words don't have a plural form, like ``blame''. -JS
   \\---\\
@@
 \todo[inline]{The first paragraph of the introduction should summarize
-  the entire introduction, and in some sense, the entire paper. -Jeremy}
+  the entire introduction, and in some sense, the entire paper. -JS}
 
@@
 \todo[inline]{Is it important to this paper whether there is a
-simulation in the other direction? -Jeremy
+simulation in the other direction? -JS
 \\ --- \\
@@
   not a negative. For example, the notion of normal forms comes up
-  over and over again in mathematics and logic. -Jeremy
+  over and over again in mathematics and logic. -JS
 \\ --- \\
@@
 notion of normalization is convenient. But we don't even need a notion of 
-normalization for cast representations. -KC}
+normalization for cast representations. -KC
+\\ --- \\
+FWIW, I agree with you. But the point is that the argument is not
+likely to be convincing to the reader, so we're probably better off
+not wasting space on it. -JS
+}
 
@@
 functions, which suggest that these strategies are not very ideal. 
-\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
+\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -JS
   \\ --- \\ Explained, not sure if it suffice. -KC
@@
 Section \ref{sec:conclude} concludes.
-\todo[inline]{Lots of missing sections. -Jeremy}
+\todo[inline]{Lots of missing sections. -JS}
 
@@
 \todo[inline]{Which previous definitions are you refering to?  What
-  are the little changes? -Jeremy
+  are the little changes? -JS
 \\ --- \\ Fixed -KC}
-\todo[inline]{The term typing rule for casts is broken. -Jeremy
+\todo[inline]{The term typing rule for casts is broken. -JS
 \\ --- \\ Fixed -KC}
 \todo[inline]{Why do you annotate the codomain of lambda abstractions
-	explicitly? -Jeremy
+	explicitly? -JS
 	\\---\\
@@
         \\---\\
-        The answer you put in the text is to vague. -JS
+        The answer you put in the text is too vague. -JS
         }
@@
 \todo[inline]{Briefly present the main ideas regarding how a CEK
-	machine works. (2-3 sentences) -Jeremy
+	machine works. (2-3 sentences) -JS
 \\---\\Fixed -KC}
@@
 \todo[inline]{Explain why you are using a CEK machine instead of
-	reduction semantics. -Jeremy
-\\---\\Fixed -KC}
-
-\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
+	reduction semantics. -JS
+        \\---\\Fixed -KC
+        \\---\\
+        Change ``one of us'' to ``first author''. -JS
+}
+
+\todo[inline]{Please fill in the missing reduction rules. -JS}
 \todo[inline]{Change the order of parameters for applyCast to take
-	the value first and the cast second. -Jeremy
+	the value first and the cast second. -JS
 	\\---\\
@@
 \todo[inline]{Change the rules for case to be small step, i.e.,
-	the case function should not be recursive. -Jeremy}
+	the case function should not be recursive. -JS}
 Along the way, the machine accumulates the pending casts onto the 
@@
 
-% the following are temporary -Jeremy
+% the following are temporary -JS
 \clearpage
@@
 \todo[inline]{Give a summary statement about the shape of the normal form. 
--Jeremy
+-JS
 \\---\\The three-part shape is not obvious before the transformation at 
@@
 	``bisimulation relation''. I don't think you are using it properly
-	in the above sentence. -Jeremy}
+	in the above sentence. -JS}
 We omit subscripts when there is no 

### 2019-10-17 paper.tex
added proposition lazy UD monoid
explain why cod

--- 2019-10-17 paper.tex
@@
 notion of normalization is convenient. But we don't even need a notion of 
-normalization for cast representations. -KC}
+normalization for cast representations. -KC
+\\ --- \\
+FWIW, I agree with you. But the point is that the argument is not
+likely to be convinving to the reader, so we're probably better off
+not wasting space on it. -JS
+}
 
@@
 types and product types. Besides, we annotate function codomain explicitly 
-because we need the codomain when evaluating cast calculus with hypercoercions.
+because we need to compute identity hypercoercion for the codomain when 
+evaluating cast calculus with hypercoercions.
 \todo[inline]{Which previous definitions are you refering to?  What
@@
         \\---\\
-        The answer you put in the text is to vague. -JS
-        }
+        The answer you put in the text is too vague. -JS
+        \\---\\
+        Fixed. -KC}
 Let $ T $ range over types. A type is either the dynamic type $ \star $

### 2019-10-17 paper.tex

--- 2019-10-17 paper.tex
@@
         The answer you put in the text is too vague. -JS
-        }
+        \\---\\
+        Fixed. -KC}
 Let $ T $ range over types. A type is either the dynamic type $ \star $
@@
 \end{figure}
+
+\begin{proposition}[\lazyUD\ hypercoercions form a monoid]
+	For all $c : T_1 \Longrightarrow T_2$,
+	$c_1 : T_1 \Longrightarrow T_2$,
+	$c_2 : T_2 \Longrightarrow T_3$, and
+	$c_3 : T_3 \Longrightarrow T_4$,
+	\begin{enumerate}
+		\item $seq(id(T_1),c) = c$,
+		\item $seq(c,id(T_2)) = c$, and
+		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
+	\end{enumerate}
+\end{proposition}
 

### 2019-10-17 paper.tex
minor fix

@@
 \newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
-\newcommand{\eOOcast}[2]{#1 \langle #2 \rangle}
+\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
 \newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
@@
 	}
-	\stxrule{c}{casts}{
-		\cOOcast{T_1}{l}{T_2}
-	}
 	\stxrule{e}{terms}{
@@
 		\eOOcase{e_1}{e_2}{e_3} \mid
-		\eOOcast{e}{c} \mid
+		\eOOcast{e}{T_1}{l}{T_2} \mid
 		\eOOblame{l}
@@
 		\vOOcast{v}{c}
+	}
+	\stxrule{c}{casts}{
+		\cOOcast{T_1}{l}{T_2}
 	}
@@
 		}{
-			\judgetype{\Gamma}{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{T_2}
+			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
 		} \quad
@@
 
-Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
-
 Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
@@
 type constructor.
+
+Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
 
@@
 	\redrule{
-		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
 	}{
@@
 Most existing proofs about cast calculi defines the dynamic semantics with 
-reduction semantics. We use a CEK machine instead because one of us is more 
-familiar with CEK machines, and that he believes CEK machines are more 
+reduction semantics. We use a CEK machine instead because the first author is 
+more familiar with CEK machines, and that he believes CEK machines are more 
 convenient because space-efficiency is about compressing continuations.
@@
         Change ``one of us'' to ``first author''. -JS
+ 		\\---\\Fixed -KC
 }
@@
 	\redruleS{
-		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
 	}{

### 2019-10-17 paper.tex
recorder casts

@@
 \newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
-\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
+\newcommand{\eOOcast}[4]{\langle \cOOcast{#2}{#3}{#4} \rangle #1}
 \newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
@@
 \newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
-\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
-\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
+%\newcommand{\cOOcast}[3]{#3 \overset{#2}{\Leftarrow} #1}
+\newcommand{\cOOcast}[3]{#3 \Leftarrow^{#2} #1}
+\newcommand{\vOOcast}[2]{\langle#2\rangle#1}
 \newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
@@
     compare it with line 4 of applyCast for UD. -JS
+    \\---\\
+    Does it mean changing the syntax for casts to a prefix syntax would work as 
+    well? 
+    If yes, I prefer this way, because of the reason in my first response 
+    and that function applications (apply) also takes arguments in this order.
+    I have fixed it with my idea so that we can see if it works. This change is 
+    easy to undo.
+    -KC
     }

### 2019-10-17 paper.tex
comment

--- 2019-10-17 paper.tex
@@
 types and product types. Besides, we annotate function codomain explicitly 
-because we need to compute identity hypercoercion for the codomain when 
-evaluating cast calculus with hypercoercions.
+because we need the codomain when evaluating cast calculus with hypercoercions.
 \todo[inline]{Which previous definitions are you refering to?  What
@@
         The answer you put in the text is too vague. -JS
-        \\---\\
-        Fixed. -KC}
+        }
 Let $ T $ range over types. A type is either the dynamic type $ \star $
@@
 
+\todo[inline]{In the definition of values, there is a ``b'' in the fun
+  case. I don't see any definitions of a nonterminal ``b''.
+  Perhaps you meant ``e''. -JS}
+\todo[inline]{In the grammars for values and pre-continuations,
+   remove all the subscripts on c's and v's. -JS}
+\todo[inline]{Change the syntax $(c,k)$ for continuations to
+  $\langle c \rangle$ k. -JS}
+
 \figref{machine-cekcc} defines the machine. 
@@
 
+\todo[inline]{Give a high-level summary of the proof.
+  The summary should be enough so that the reader knows a bit
+  about why you introduce the various definitions below. -JS}
+
 \subsection{\lazyD\ Cast Representations}
@@
 
+\todo[inline]{``monoidic'' is not a word. -JS}
+
 We use bisimulation to proof equivalence between the two machines.
+\todo[inline]{Which two machines? -JS}
 The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
@@
   Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
+  \todo[inline]{I'm guessing that you prove this lemma by induction,
+    using Lemma~\ref{thm:surely-monoidic-reduce}.
+    Proofs by induction are not ``immediate''. -JS}
 \end{proof}

### 2019-10-17 paper.tex
abstracting CEK1 k
fill in missing reduction rules in CEK1
minor fix on grammar

@@
 \newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
+\newcommand{\kOOmt}[0]{\mathtt{stop}}
+\newcommand{\kOOconsI}[3]{\mathtt{cons_1} \; #1 \; #2 \; #3}
+\newcommand{\kOOconsII}[2]{\mathtt{cons_2} \; #1 \; #2}
+\newcommand{\kOOinl}[1]{\mathtt{inl} \; #1}
+\newcommand{\kOOinr}[1]{\mathtt{inr} \; #1}
+\newcommand{\kOOappI}[3]{
+	\mathtt{app_1} \; #1 \; #2 \; #3
+}
+\newcommand{\kOOappII}[2]{
+	\mathtt{app_2} \; #1 \; #2}
+\newcommand{\kOOcar}[1]{
+	\mathtt{fst} \; #1}
+\newcommand{\kOOcdr}[1]{
+	\mathtt{snd} \; #1}
+\newcommand{\kOOcaseI}[4]{
+	\mathtt{case_1} \; #1 \; #2 \; #3 \; #4}
+\newcommand{\kOOcaseII}[4]{
+	\mathtt{case_2} \; #1 \; #2 \; #3 \; #4}
+\newcommand{\kOOcaseIII}[3]{
+	\mathtt{case_3} \; #1 \; #2 \; #3}
+\newcommand{\kOOcast}[2]{
+	\langle #1 \rangle #2}
 \newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
@@
 	\stxrule{\kappa}{continuations}{
-		\mathtt{stop} \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
+		\kOOmt \mid
+		\kOOconsI{e}{\rho}{\kappa} \mid
+		\kOOconsII{v}{\kappa} \mid
+		\kOOinl{\kappa} \mid
+		\kOOinr{\kappa}
 	}
 	\stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{fst} \; \kappa \mid{}
-		\mathtt{snd} \; \kappa \mid
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
+		\kOOappI{e}{\rho}{\kappa} \mid
+		\kOOappII{v}{\kappa} \mid
+		\kOOcar{\kappa} \mid
+		\kOOcdr{\kappa} \mid
+		\kOOcaseI{e_1}{e_2}{\rho}{\kappa}
 	}
 	\stxrulecont{	
-		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
-		\langle c \rangle \kappa
+		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
+		\kOOcaseIII{v_1}{v_2}{\kappa} \mid
+		\kOOcast{c}{\kappa}
 	}
@@
 	\begin{array}{rclr}
-
-	& \dots  \\
+	\redrule{
+		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
+	}{	
+		\sOOreturn{\rho[x]}{\kappa}
+	}{}
+	\redrule{
+		\sOOinspect{\eOOsole}{\rho}{\kappa}
+	}{
+		\sOOreturn{\vOOtt}{\kappa}
+	}{}
+	\redrule{
+		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
+	}{
+		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
+	}{}
+	\redrule{
+		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{E}{}
+	}{}
+	\redrule{
+		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
+	}{}
+	\redrule{
+	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
+	}{
+	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
+	}{}
+	\redrule{
+		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
+	}{
+\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}
+\redrule{
+\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
+\sOOinspect{e}{\rho}{(\kOOcar{\kappa})}}{}
+\redrule{
+	\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
+	\sOOinspect{e}{\rho}{(\kOOcdr{\kappa})}}{}
+\redrule{
+\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
+\sOOinspect{e_1}{\rho}{(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
 	\redrule{
@@
 	}{}
+
+\redrule{
+\sOOreturn{v_1}{(\kOOconsI{\rho}{e_2}{\kappa})}}{
+\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}
+
+\redrule{
+\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
+\sOOreturn{(\vOOcons{v_1}{v_2})}{\kappa}}{}
+
+\redrule{
+\sOOreturn{v}{(\kOOinl{\kappa})}}{
+\sOOreturn{(\vOOinl{v})}{\kappa}}{}
+
+\redrule{
+\sOOreturn{v}{(\kOOinr{\kappa})}}{
+\sOOreturn{(\vOOinr{v})}{\kappa}}{}
+
+\redrule{
+\sOOreturn{v_1}{(\kOOappI{\rho}{e_2}{\kappa})}}{
+\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}
+
+\redrule{
+\sOOreturn{v_2}{(\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa})}}{
+\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
 	\redrule{
@@
 	}{}
-
-	%	\redrule{
-	%		\sOOreturn{v}{(
-	%			\mathtt{app_2} \;
-	%			(\vOOfun{\rho}{x}{e}) \;
-	%			\kappa
-	%		)}
-	%	}{\sOOinspect{e}{\rho{}[x := v]}{\kappa}}{}
-
 	\redrule{
@@
 
+\redrule{
+\sOOreturn{v_1}{(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{
+\sOOinspect{e_2}{\rho}{(\kOOcaseII{E}{v_1}{e_3}{\kappa})}}{}
+
+\redrule{
+\sOOreturn{v_2}{(\kOOcaseII{\rho}{v_1}{e_3}{\kappa})}}{
+\sOOinspect{e_3}{\rho}{
+	(\kOOcaseIII{v_1}{v_2}{\kappa})
+}}{}	
 		\redrule{
@@
 	}
+\redrule{
+\sOOreturn{v}{\kOOmt}}{
+\sOOhalt{observe(v)}}{}
 	\end{array}
@@
 
-\todo[inline]{Please fill in the missing reduction rules. -JS}
+\todo[inline]{Please fill in the missing reduction rules. -JS
+\\---\\ Fixed -KC}
 \todo[inline]{Change the order of parameters for applyCast to take
@@
 		\hcvOOtt \mid
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
-		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
+		\hcvOOcons{v}{c}{v}{c}
 	}
@@
 	\stxrule{\kappa}{continuation}{
-		(c,k)
+		\langle c \rangle k
 	}
@@
 	\stxrulecont{
-		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
+		\mathtt{case_1} \; e \; e \; \rho \; \kappa \mid
 		\mathtt{case_2} \; v \; e \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
+		\mathtt{case_3} \; v \; v \; \rho \; \kappa
 	}
@@
 	\begin{array}{rclc}
-	\funrule{cont(k)}{(id(T_1),k)}{
+	\funrule{cont(k)}{\langle id(T_1) \rangle k}{
 		\sidecond{k : T_1 \Longrightarrow T_2}}
@@
 	\begin{array}{rclc}
-	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
+	\funrule{ext(c_1,\langle c_2 \rangle k)}{\langle seq(c_1,c_2) \rangle k}{}
 	\end{array}
@@
 \end{figure}
-
-\todo[inline]{In the definition of values, there is a ``b'' in the fun
-  case. I don't see any definitions of a nonterminal ``b''.
-  Perhaps you meant ``e''. -JS}
-\todo[inline]{In the grammars for values and pre-continuations,
-   remove all the subscripts on c's and v's. -JS}
-\todo[inline]{Change the syntax $(c,k)$ for continuations to
-  $\langle c \rangle$ k. -JS}
 

### 2019-10-17 paper.tex
define observe(v) = o
remove bisimilarity

@@
 program terminates. Observations include all value constructors and blame.
+The function converting values to observations ($ observe(v) = o $) is defined 
+in the natural way.
 
@@
 \todo[inline]{Which two machines? -JS}
-The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
-definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
+The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
+the definitions of $ \mathcal{D} $. Exceptions include the relations 
 between continuations, between values, and from continuations to 
@@
 other. 
-The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
+The bisimulation relation of states ($\eqvS{C}{C}{s}{s}$) is 
 derived from the definition of states.
@@
 	``bisimulation relation''. I don't think you are using it properly
-	in the above sentence. -JS}
+	in the above sentence. -JS
+\\---\\
+Fixed.
+I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' from 
+wikipedia. (https://en.wikipedia.org/wiki/Bisimulation).
+-KC}
 We omit subscripts when there is no 

### 2019-10-17 paper.tex
minor
give LazyD C a name: C_D

@@
 % Lazy D cast calculus on space-inefficient CEK
-\newcommand{\judgeDCreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
-\newcommand{\judgeDCreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
-\newcommand{\judgeDCeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
-\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
+\newcommand{\judgeCreduce}[2]{#1 \longrightarrow_{\mathcal{C}} #2}
+\newcommand{\judgeCreduceTrans}[2]{#1 \longrightarrow_{\mathcal{C}}^{*} #2}
+\newcommand{\judgeCeval}[2]{#1 \Downarrow_{\mathcal{C}} #2}
+\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{C} & #2 & #3\\}
 % blame calculus on space-efficient CEK
@@
 
-	Reduction \fbox{$ \judgeDCreduce{s}{s} $}
+	Reduction \fbox{$ \judgeCreduce{s}{s} $}
 	\[
@@
 
-	Evaluation \fbox{$\judgeDCeval{e}{o}$}
+	Evaluation \fbox{$\judgeCeval{e}{o}$}
 	\[
@@
 	}{
-		\judgeDCeval{e}{o}
-	}
-	\]
-
-	\caption{dynamic semantics of the cast calculi as a CEK machine}
+		\judgeCeval{e}{o}
+	}
+	\]
+
+	\caption{Dynamic semantics of the cast calculi as a CEK machine ($ 
+	\mathcal{C} $)}
 	\label{machine-cekc}
@@
 
-The reduction relation $ \judgeDCreduce{s}{s} $ depends on $ applyCast $, a 
+The reduction relation $ \judgeCreduce{s}{s} $ depends on $ applyCast $, a 
 function depending on blame strategies. We will give the definitions of $ 
@@
 
-The reflexive transitive closure of reduction ($ \judgeDCreduceTrans{s}{s} $) 
-and evaluation ($ \judgeDCeval{e}{o} $) are standard.
+The reflexive transitive closure of reduction ($ \judgeCreduceTrans{s}{s} $) 
+and evaluation ($ \judgeCeval{e}{o} $) are standard.
 
@@
 \figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
-\citet{siek2009exploring}.
+\citet{siek2009exploring}. We denote this \lazyD{} machine by $ 
+\mathcal{C}_{\mathtt{D}} $.
 
@@
 The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
-the definitions of $ \mathcal{D} $. Exceptions include the relations 
-between continuations, between values, and from continuations to 
-pre-continuations. We omit subscripts when there is no ambiguity.
+the definitions of $ \mathcal{D} $. Exceptions include the relations from 
+continuations to pre-continuations, between continuations, and between values. 
+We omit subscripts when there is no ambiguity.
 
@@
 	\begin{enumerate}
-		\item If $ \judgeDCreduce{s_1}{s_3} $,
+		\item If $ \judgeCreduce{s_1}{s_3} $,
 		then
@@
 			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-			\item $ \judgeDCreduceTrans{s_3}{s_5} $
+			\item $ \judgeCreduceTrans{s_3}{s_5} $
 		\end{itemize}
@@
 			\item $ s_3 \approx s_4 $
-			\item $ \judgeDCreduceTrans{s_1}{s_3} $
+			\item $ \judgeCreduceTrans{s_1}{s_3} $
 		\end{itemize}
@@
 	\[
-	\judgeDCeval{e}{o} \; \text{if and only if} \; 
+	\judgeCeval{e}{o} \; \text{if and only if} \; 
 	\judgeSeval{C}{e}{o}
@@
 	\[
-	\judgeDCeval{e}{o} \; \text{if and only if} \; 
+	\judgeCeval{e}{o} \; \text{if and only if} \; 
 	\judgeSeval{H}{e}{o}

### 2019-10-17 paper.tex
fully remove abbrev NC
name LazyD inefficient CEK as D

@@
 \newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
+% names
+\newcommand{\ineffCEK}{$ \mathcal{C} $}
+\newcommand{\ineffCEKD}{$ \mathcal{D} $}
+\newcommand{\ineffCEKUD}{$ \mathcal{UD} $}
+\newcommand{\judgeDreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
+\newcommand{\judgeDreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
+\newcommand{\judgeDeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
+\newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
 
@@
 
-	\caption{Dynamic semantics of the cast calculi as a CEK machine ($ 
-	\mathcal{C} $)}
+	\caption{Dynamic semantics of the cast calculi as a CEK machine}
 	\label{machine-cekc}
@@
 \figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
-\citet{siek2009exploring}. We denote this \lazyD{} machine by $ 
-\mathcal{C}_{\mathtt{D}} $.
+\citet{siek2009exploring}. We denote this \lazyD{} machine by \ineffCEKD{},
+and the corresponding relations by $ \judgeDreduce{s}{s} $, $ 
+\judgeDreduceTrans{s}{s} $, and $ \judgeDeval{e}{o} $
 
@@
 	\]
-	\caption{Syntax of Normal Coercion (NC)}
+	\caption{Syntax of Normal Coercion}
 	\label{fig:normal-coercion}
@@
 \subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
-$\mathcal{D}$}
+$\mathcal{C}_{\mathtt{D}}$}
 
@@
 The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
-the definitions of $ \mathcal{D} $. Exceptions include the relations from 
+the definitions of $ \mathcal{C} $. Exceptions include the relations from 
 continuations to pre-continuations, between continuations, and between values. 
@@
 \begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and $ 
-	\mathcal{D} $]
+	\mathcal{C} $]
 	\label{thm:surely-monoidic-reduce}
@@
 	if $ C $ is surely \lazyD{} and monoidic,
-	$ s_1 \in \mathcal{D} $,
+	$ s_1 \in \mathcal{C} $,
 	$ s_2 \in \mathcal{S}(C) $, and
@@
 		then
-		there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
+		there exist $ s_5 \in \mathcal{C} $, $ s_4 \in \mathcal{S}(C) $,
 		such that \begin{itemize}
@@
 		then
-		there exist $ s_3 \in \mathcal{D} $,
+		there exist $ s_3 \in \mathcal{C} $,
 		such that \begin{itemize}
@@
 \begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
-	$ \mathcal{D} $]
+	$ \mathcal{C} $]
 	\label{thm:surely-monoidic-eval}
@@
 
-\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
+\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{C}_\mathtt{D} $}
 \label{sec:LDHC-correct}
@@
 
-\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{D} $]
+\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{C}_\mathtt{D} $]
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
@@
 \begin{theorem}[Surely \lazyD\ Cast Representations Respect 
-	$ \mathcal{D} $]
+	$ \mathcal{C}_\mathtt{D} $]
 	\label{thm:surely-lazyD-correct}

### 2019-10-17 paper.tex
rewrite intro

@@
 
-Around 2006, many work on integrating dynamic typing and static typing emerge, 
-notably gradual types \citep{siek2006gradual} and hybrid types 
-\citep{flanagan2006hybrid}. 
-Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
-language for gradual types and hybrid types. 
-Blame Calculus throws a blame label when a runtime type-check fails.
-Labels provide useful debugging information, therefore are necessary for 
-practical use of gradually typed languages.
-
-Implementing gradually typed languages naively on top of blame calculus, 
-however, suffices sever space leak.
-For example, translation to Blame Calculus can wrap some expressions with code 
-that performs runtime type-checking (casts), including expressions at 
-tail positions. Thus, mutually tail-recursive functions in source language can 
-consume unbounded space at runtime. There are more examples of space leaking in 
-\citet{herman2010space}.
-
-In 2007, \citet{herman2010space} proposes a solution to this problem by 
-representing casts with coercion \citep{henglein1994dynamic}, 
-which can be composed and normalized. Every coercion looks like a list of 
-trees. For normal coercion, the length of the list is bounded by a small 
-constant. And the depths of trees do not grow during composition and
-normalization. These two facts implies that coercion is a space-efficient cast 
-representation. This coercion, however, does not support blame 
-tracking.
-
-After that, many efforts have been made to combine blame tracking and 
-space efficiency.
-
-\citet{siek2009exploring} present another intermediate langauge for gradually 
-typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
-and space-efficiency for this language by decorating \citet{herman2010space}'s 
-coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
-with the dynamic type and cast expressions. The labels in \castCalculus{}, 
-unlike their counterparts in the Blame Calculus, have no polarity. 
-They also propose that there are four blame strategies for \castCalculus{}:
-$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
-type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
-differently. They claim that their \lazyUD\ cast calculus is the same as the 
-Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
-coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
-however, whether the simulation in the other direction also works.
-\todo[inline]{Is it important to this paper whether there is a
-simulation in the other direction? -JS
-\\ --- \\
-I guessed to say coercion is correct the other direction is 
-necessary. -KC}
-
-\citet{siek2010threesomes} proposes another approach to combine blame 
-tracking and space efficiency. Their solution represents casts with threesomes, 
-a novel cast representation. Threesome is proved space-efficient as well.
-They prove that their calculus bisimulates the \lazyUD{} coercion 
-calculus in \citet{siek2009exploring} and the Blame Calculus in 
-\citet{wadler2009well}.
-
-\citet{siek2012interpretations} present a revised coercion calculi.
-They simplify the coercion calculi by only 
-working with normal coercions (i.e. coercions in normal form). 
-They conjecture that their revised coercion calculi bisimulate the 
-corresponding cast calculi.
-
-\citet{garcia2013calculating} develops
-threesome for other blame strategies. After studying in depth the connection 
-between coercion and threesome,
-he claims that normal coercion with labels is easy to understand but hard to 
-implement and hard to reason about, and that 
-threesome with labels, however, is easy to implement and easy to reason about 
-but hard to understand. 
-His claim is mostly affirmed by the group of people who develop threesome 
-(\citet{siek2015blame}).
-His threesome calculi are equivalent to the coercion calculi of
-\citet{siek2009exploring} because the former ones are derived from the latter 
-ones.
-
-\citet{siek2015blame} revisit the coercion-based approach. They revise
-the \lazyUD{} coercion in \citet{siek2012interpretations} and prove
-that their revised coercion calculus bisimulates the \lazyUD{} Blame
-Calculus \citet{wadler2009well}.
-
-Last year, \citet{kuhlenschmidt2018efficient} present Grift, a compiler for a 
-gradually typed language of the same name. 
-This implementation is based on the \lazyD{} coercion in 
-\citet{siek2012interpretations}.
-Their result suggests that normal coercion is easy enough to implement in a 
-compiler.
-
-So far, it seems that normal coercion is the best way to combine 
-space-efficiency and blame-tracking: normal coercion is claimed easy to 
-understand \citep{garcia2013calculating}\citep{siek2015blame} and is shown 
-easy enough to implement in a compiler \citep{kuhlenschmidt2018efficient}.
-Normal coercion is still not satisfactory, however, in at least two aspects.
-Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
-major difficulty is from its non-structurally recursive composition.
-For instance, the developers of Grift report it is tricky to convince
-their proof assistants that the composition terminates.
-
-Secondly, the definition of normal coercion lies unnecessarily on top 
-of coercion: all coercions are normal when they are initially constructed, and 
-\citet{siek2012interpretations} have shown an function that 
-composes and produces normal coercions.
+There are two basic ways to represent cast efficiently: coercions 
+\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
+\citep{siek2015blame} and threesomes 
+\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
+strength and 
+weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
+coercion is easy to understand, but hard to implement, while threesome is easy 
+to implement, but hard to understand. \citet{garcia2013calculating} in addition 
+claims that coercion is more difficult to reason about formally, because 
+composition of coercions is not structurally recurisive. The developers of 
+Grift \citep{kuhlenschmidt2018efficient} affirm that it is tricky to convince 
+their proof assistants that composition of coercions terminates.
+
+We present a new cast representation, hypercoercion, which has a structurally 
+recursive composition. We believe hypercoercion is easier to understand than 
+threesome, because its syntax is close to coercion. For instance, the 
+coercion approach represents $ 
+\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
+?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
+\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
+coercion together with cast calculus, the intermediate languages in 
+\citet{kuhlenschmidt2018efficient}. And we present hypercoerion in 
+Section~\ref{sec:hypercoercion-definition}.
+
+Another strength of hypercoercion over coercion is that hypercoercion might 
+have a more compact memory representations ...
+\todo[inline]{Could Jeremy explain here why hypercoercion is more compact in 
+memory? -KC}
+
+Many of the existing research on coercions or threesomes include proof(s) of 
+correctness, that is, the cast calculus reduces to an observation ($ e 
+\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
+e \Downarrow_{*} o $), where an observation is a value constructor or a blame. 
+Despite the striking similarity of these proves, they are all built from ground 
+up. We present a framework for proving correctness of cast reprensentation 
+(Section~\ref{sec:framework}), and use it to prove the correctness of 
+hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
+that this framework is general enough to include coercion and threesome.
+
+Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
+\times \{D, UD\} $. Eager strategies detect more potential type errors, but 
+blame more programs. $ D $ and $ UD $ assign blame labels differently.
+We focus on lazy strategies because recently \citet{new2019gradual} 
+show that \eager{} strategies are incompatible with $\eta$-equivalence of 
+functions, which suggest that they are not very ideal. 
+\todo[inline]{Why do we need to explain why both LD and LUD? -KC}
+
+Here are our major contribution:
+\begin{itemize}
+	\item hypercoercion, a new space-efficient cast representation, which has a 
+	structurally recursive composition and has a more compact memory 
+	representation.
+	\item a framework in Agda for proving correctness of cast represantations. 
+	We conjecture that both coercion and threesome can fit into this framework.
+	\item a formal proof that hypercoercion respect the semantics of cast 
+	calculus
+\end{itemize}
+
+%Around 2006, many work on integrating dynamic typing and static typing emerge, 
+%notably gradual types \citep{siek2006gradual} and hybrid types 
+%\citep{flanagan2006hybrid}. 
+%Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
+%language for gradual types and hybrid types. 
+%Blame Calculus throws a blame label when a runtime type-check fails.
+%Labels provide useful debugging information, therefore are necessary for 
+%practical use of gradually typed languages.
 %
-\todo[inline]{Many researchers would view this as a positive thing,
-  not a negative. For example, the notion of normal forms comes up
-  over and over again in mathematics and logic. -JS
-\\ --- \\
-I guess having a notion of normal forms is more convenient when a 
-notion of normalization is convenient. But we don't even need a notion of 
-normalization for cast representations. -KC
-\\ --- \\
-FWIW, I agree with you. But the point is that the argument is not
-likely to be convincing to the reader, so we're probably better off
-not wasting space on it. -JS
-}
-
-Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
-self-standing definition. Together with \citet{garcia2013calculating}'s 
-work, they suggest that there might be a cast representation whose definition 
-is self-standing, and whose composition is structurally recursive. 
-supercoercion introduced in \citet{garcia2013calculating} could be a promising 
-candidate. It is believed even more complicated than threesome 
-\citep{siek2015blame}. In fact, it uses 10 constructors to deal with an 
-elementary type system with only base types and 
-function types. And four constructors are directly related to function types. 
-Thus, supercoercion might not scale very well to more sophisticated type 
-systems.
-
-We present hypercoercion, a cast representation whose composition is 
-structurally recursive, and whose definition is self-standing. What's more, it 
-should be at 
-least as easy to implement and understand as normal coercions, because there is 
-a clear connection between them, as we will show in Section 
-\ref{sec:hypercoercion}.
-Our hypercoercion considers sum types and product types, which are not 
-considered in all proofs above. Adding each of them requires us to add only one 
-new constructor to a component of hypercoercion. This suggests that 
-hypercoercion might scale better than supercoercion.
-
-We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
-bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
-the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
-We care more about lazy strategies because recently, \citet{new2019gradual} 
-show that \eager{} strategies are incompatible with $\eta$-equivalence of 
-functions, which suggest that these strategies are not very ideal. 
-\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -JS
-  \\ --- \\ Explained, not sure if it suffice. -KC
-  \\ --- \\
-  That's good that you explained why lazy instead of eager.
-  (Also, you should add that we are interested in lazy because
-  that's what Grift does.)\\
-  But you haven't explained why we are interested in both D and UD. -JS
-}
-
-The structure of this paper is as follows. 
-Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ cast 
-calculi. 
-Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
-Calculi. 
-In section \ref{sec:hypercoercion} we present hypercoercion.
-Section \ref{sec:conclude} concludes.
-\todo[inline]{Lots of missing sections. -JS}
-
-\section{Background} \label{sec:blame-calculus}
+%Implementing gradually typed languages naively on top of blame calculus, 
+%however, suffices sever space leak.
+%For example, translation to Blame Calculus can wrap some expressions with code 
+%that performs runtime type-checking (casts), including expressions at 
+%tail positions. Thus, mutually tail-recursive functions in source language can 
+%consume unbounded space at runtime. There are more examples of space leaking 
+%in 
+%\citet{herman2010space}.
+%
+%In 2007, \citet{herman2010space} proposes a solution to this problem by 
+%representing casts with coercion \citep{henglein1994dynamic}, 
+%which can be composed and normalized. Every coercion looks like a list of 
+%trees. For normal coercion, the length of the list is bounded by a small 
+%constant. And the depths of trees do not grow during composition and
+%normalization. These two facts implies that coercion is a space-efficient cast 
+%representation. This coercion, however, does not support blame 
+%tracking. 
+%
+%After that, many efforts have been made to combine blame tracking and 
+%space efficiency. 
+%
+%\citet{siek2009exploring} present another intermediate langauge for gradually 
+%typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
+%and space-efficiency for this language by decorating \citet{herman2010space}'s 
+%coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
+%with the dynamic type and cast expressions. The labels in \castCalculus{}, 
+%unlike their counterparts in the Blame Calculus, have no polarity. 
+%They also propose that there are four blame strategies for \castCalculus{}:
+%$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
+%type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
+%differently. They claim that their \lazyUD\ cast calculus is the same as the 
+%Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
+%coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
+%however, whether the simulation in the other direction also works.
+%\todo[inline]{Is it important to this paper whether there is a
+%simulation in the other direction? -JS
+%\\ --- \\
+%I guessed to say coercion is correct the other direction is 
+%necessary. -KC}
+%
+%\citet{siek2010threesomes} proposes another approach to combine blame 
+%tracking and space efficiency. Their solution represents casts with 
+%threesomes, 
+%a novel cast representation. Threesome is proved space-efficient as well.
+%They prove that their calculus bisimulates the \lazyUD{} coercion 
+%calculus in \citet{siek2009exploring} and the Blame Calculus in 
+%\citet{wadler2009well}.
+%
+%\citet{siek2012interpretations} present a revised coercion calculi.
+%They simplify the coercion calculi by only 
+%working with normal coercions (i.e. coercions in normal form). 
+%They conjecture that their revised coercion calculi bisimulate the 
+%corresponding cast calculi.
+%
+%\citet{garcia2013calculating} develops
+%threesome for other blame strategies. After studying in depth the connection 
+%between coercion and threesome,
+%he claims that normal coercion with labels is easy to understand but hard to 
+%implement and hard to reason about, and that 
+%threesome with labels, however, is easy to implement and easy to reason about 
+%but hard to understand. 
+%His claim is mostly affirmed by the group of people who develop threesome 
+%(\citet{siek2015blame}).
+%His threesome calculi are equivalent to the coercion calculi of
+%\citet{siek2009exploring} because the former ones are derived from the latter 
+%ones.
+%
+%\citet{siek2015blame} revisit the coercion-based approach. They revise
+%the \lazyUD{} coercion in \citet{siek2012interpretations} and prove
+%that their revised coercion calculus bisimulates the \lazyUD{} Blame
+%Calculus \citet{wadler2009well}.
+%
+%Last year, \citet{kuhlenschmidt2018efficient} present Grift, a compiler for a 
+%gradually typed language of the same name. 
+%This implementation is based on the \lazyD{} coercion in 
+%\citet{siek2012interpretations}.
+%Their result suggests that normal coercion is easy enough to implement in a 
+%compiler. 
+%
+%So far, it seems that normal coercion is the best way to combine 
+%space-efficiency and blame-tracking: normal coercion is claimed easy to 
+%understand \citep{garcia2013calculating}\citep{siek2015blame} and is shown 
+%easy enough to implement in a compiler \citep{kuhlenschmidt2018efficient}.
+%Normal coercion is still not satisfactory, however, in at least two aspects.
+%Firstly, as we mentioned above, it is hard to reason about normal coercion. 
+%The 
+%major difficulty is from its non-structurally recursive composition.
+%For instance, the developers of Grift report it is tricky to convince
+%their proof assistants that the composition terminates.
+%
+%Secondly, the definition of normal coercion lies unnecessarily on top 
+%of coercion: all coercions are normal when they are initially constructed, and 
+%\citet{siek2012interpretations} have shown an function that 
+%composes and produces normal coercions.
+%%
+%\todo[inline]{Many researchers would view this as a positive thing,
+%  not a negative. For example, the notion of normal forms comes up
+%  over and over again in mathematics and logic. -JS
+%\\ --- \\
+%I guess having a notion of normal forms is more convenient when a 
+%notion of normalization is convenient. But we don't even need a notion of 
+%normalization for cast representations. -KC
+%\\ --- \\
+%FWIW, I agree with you. But the point is that the argument is not
+%likely to be convincing to the reader, so we're probably better off
+%not wasting space on it. -JS
+%}
+%
+%Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
+%self-standing definition. Together with \citet{garcia2013calculating}'s 
+%work, they suggest that there might be a cast representation whose definition 
+%is self-standing, and whose composition is structurally recursive. 
+%supercoercion introduced in \citet{garcia2013calculating} could be a promising 
+%candidate. It is believed even more complicated than threesome 
+%\citep{siek2015blame}. In fact, it uses 10 constructors to deal with an 
+%elementary type system with only base types and 
+%function types. And four constructors are directly related to function types. 
+%Thus, supercoercion might not scale very well to more sophisticated type 
+%systems. 
+%
+%We present hypercoercion, a cast representation whose composition is 
+%structurally recursive, and whose definition is self-standing. What's more, it 
+%should be at 
+%least as easy to implement and understand as normal coercions, because there 
+%is 
+%a clear connection between them, as we will show in Section 
+%\ref{sec:hypercoercion}.
+%Our hypercoercion considers sum types and product types, which are not 
+%considered in all proofs above. Adding each of them requires us to add only 
+%one 
+%new constructor to a component of hypercoercion. This suggests that 
+%hypercoercion might scale better than supercoercion.
+%
+%We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
+%bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
+%the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
+%We care more about lazy strategies because recently, \citet{new2019gradual} 
+%show that \eager{} strategies are incompatible with $\eta$-equivalence of 
+%functions, which suggest that these strategies are not very ideal. 
+%\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -JS
+%  \\ --- \\ Explained, not sure if it suffice. -KC
+%  \\ --- \\
+%  That's good that you explained why lazy instead of eager.
+%  (Also, you should add that we are interested in lazy because
+%  that's what Grift does.)\\
+%  But you haven't explained why we are interested in both D and UD. -JS
+%}
+%
+%The structure of this paper is as follows. 
+%Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ cast 
+%calculi. 
+%Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ 
+%Coercion 
+%Calculi. 
+%In section \ref{sec:hypercoercion} we present hypercoercion.
+%Section \ref{sec:conclude} concludes.
+%\todo[inline]{Lots of missing sections. -JS}
+
+\section{Background} \label{sec:background}
 
@@
 
-\section{hypercoercion} \label{sec:hypercoercion}
+\section{Definition of Hypercoercion} \label{sec:hypercoercion-definition}
 
@@
 
-\section{Space-efficient CEK Abstract Machine}
-\label{sec:CEKS}
+\section{a framework for proving correctness of cast representations}
+\label{sec:framework}
 
@@
 \section{Correctness Proof of \lazyD{} hypercoercions}
+\label{sec:hypercoercion-correctness}
 
@@
 \subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
-$\mathcal{C}_{\mathtt{D}}$}
+\ineffCEKD}
 
@@
 The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
-the definitions of $ \mathcal{C} $. Exceptions include the relations from 
+the definitions of \ineffCEKD. Exceptions include the relations from 
 continuations to pre-continuations, between continuations, and between values. 
@@
 
-\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and $ 
-	\mathcal{C} $]
+\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and \ineffCEKD]
 	\label{thm:surely-monoidic-reduce}
@@
 	if $ C $ is surely \lazyD{} and monoidic,
-	$ s_1 \in \mathcal{C} $,
+	$ s_1 \in \text{\ineffCEKD} $,
 	$ s_2 \in \mathcal{S}(C) $, and
@@
 	\begin{enumerate}
-		\item If $ \judgeCreduce{s_1}{s_3} $,
+		\item If $ \judgeDreduce{s_1}{s_3} $,
 		then
-		there exist $ s_5 \in \mathcal{C} $, $ s_4 \in \mathcal{S}(C) $,
+		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
 		such that \begin{itemize}
@@
 			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-			\item $ \judgeCreduceTrans{s_3}{s_5} $
+			\item $ \judgeDreduceTrans{s_3}{s_5} $
 		\end{itemize}
@@
 			\item $ s_3 \approx s_4 $
-			\item $ \judgeCreduceTrans{s_1}{s_3} $
+			\item $ \judgeDreduceTrans{s_1}{s_3} $
 		\end{itemize}
@@
 	\[
-	\judgeCeval{e}{o} \; \text{if and only if} \; 
+	\judgeDeval{e}{o} \; \text{if and only if} \; 
 	\judgeSeval{C}{e}{o}
@@
 
-\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{C}_\mathtt{D} $}
+\subsection{\lazyD\ Hyper-coercion Respect \ineffCEKD}
 \label{sec:LDHC-correct}

### 2019-10-17 paper.tex
minor fix in intro

@@
 \Downarrow o $) if and only if their calcului reduce to the same observation ($ 
-e \Downarrow_{*} o $), where an observation is a value constructor or a blame. 
-Despite the striking similarity of these proves, they are all built from ground 
+e \Downarrow_{*} o $), where an observation is either a value constructor or 
+blame. 
+Despite the striking similarity of these proofs, they are all built from ground 
 up. We present a framework for proving correctness of cast reprensentation 

### 2019-10-17 paper.tex
minor fix in intro

@@
 
-There are two basic ways to represent cast efficiently: coercions 
+There are two basic ways to represent cast space-efficiently: coercions 
 \citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
@@
 to implement, but hard to understand. \citet{garcia2013calculating} in addition 
-claims that coercion is more difficult to reason about formally, because 
-composition of coercions is not structurally recurisive. The developers of 
-Grift \citep{kuhlenschmidt2018efficient} affirm that it is tricky to convince 
-their proof assistants that composition of coercions terminates.
+claims that coercion is more difficult to reason about formally because 
+its compose function is not structurally recurisive. For instance, the 
+developers of Grift \citep{kuhlenschmidt2018efficient} report that it is tricky 
+to convince their proof assistants that the compose function terminates.
 
 We present a new cast representation, hypercoercion, which has a structurally 
-recursive composition. We believe hypercoercion is easier to understand than 
-threesome, because its syntax is close to coercion. For instance, the 
+recursive composition. When we prove theorems about hypercoercion in Agda, the 
+definition ``just works''. 
+Besides, We believe hypercoercion is about as easy to understand as coercion 
+because their syntax definitions are similar. For instance, the 
 coercion approach represents $ 
@@
 \hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
-coercion together with cast calculus, the intermediate languages in 
-\citet{kuhlenschmidt2018efficient}. And we present hypercoerion in 
-Section~\ref{sec:hypercoercion-definition}.
+coercion together with cast calculus, an intermediate languages for gradual 
+typing \citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
+present hypercoerion in Section~\ref{sec:hypercoercion-definition}.
 
@@
 Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
-\times \{D, UD\} $. Eager strategies detect more potential type errors, but 
+\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
+potential type errors, but 
 blame more programs. $ D $ and $ UD $ assign blame labels differently.
@@
 $ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
-The intuition of $ T_1 \sim T $ is that $ T_1 $ and $ T_2 $ have no conflict 
+The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $ T_2 $ have no conflict 
 type information. Two types are consistent if one of them is $ \star $, or they 

### 2019-10-17 paper.tex
minor fix
starting para of sec 4

@@
 
-This section presents our first contribution, hypercoercion (HC). 
-\figref{fig:hypercoercion} defines the syntax of HC.
-Types, pre-types, and blame labels are as before.
+This section presents our first contribution, the definition of hypercoercion. 
+The functions that construct hypercoercions are deferred to subsections because 
+they depend on blame strategies.
+And the functions that apply hypercoercions to values are deferred to 
+Section~\ref{sec:hypercoercion-correctness} because 
+they depends on a new definition of values, which is part of the framework in
+Section~\ref{sec:framework}.
+
+\figref{fig:hypercoercion} defines the syntax of hypercoercion. Types, 
+pre-types, and blame labels are as before.
 
@@
 
-This section presents our second contribution, a space-efficient CEK abstract 
+This section presents our second contribution, a framework for proving 
+correctness of cast representations.
+In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
+of semantics (in the style of CEK machines) indexed by cast representations ($ 
+C $). 
+In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
+$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
+\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
+representation respects the \lazyD\ cast calculus. 
+Proving a similar theorem for \lazyUD\ is in progress.
+
+\subsection{A Space-efficient CEK machine}
+\label{ssec:framework:cek}
+
+We define cast representations and \effCEK{C}
+
+space-efficient CEK abstract 
 machine. This machine is parameterized over \emph{cast representation}.
@@
 
+\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
+\label{ssec:framework:correctness}
+
+\todo[inline]{KC needs to move some content in the next section to here. -KC}
+
 \section{Correctness Proof of \lazyD{} hypercoercions}
@@
 		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
-		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
 		\item $ 
 		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
-		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
 	\end{enumerate}

### 2019-10-17 paper.tex
4.1 effCEK

@@
 In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of semantics (in the style of CEK machines) indexed by cast representations ($ 
-C $). 
+of space-efficient semantics (in the style of CEK machines) indexed by cast 
+representations ($ C $). 
 In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
@@
 
-\subsection{A Space-efficient CEK machine}
-\label{ssec:framework:cek}
-
-We define cast representations and \effCEK{C}
-
-space-efficient CEK abstract 
-machine. This machine is parameterized over \emph{cast representation}.
+Our space-efficient CEK machine is parameterized over \emph{cast 
+	representations}.
 
@@
 
-\begin{definition}[Monoidic Cast Representation]
-	A cast representation is monoidic if 
+Some cast representations are monoids as well. They are useful in our 
+correctness proof.
+
+\begin{definition}[Monoid]
+	A cast representation is a monoid if 
 	for all $c : T_1 \Longrightarrow T_2$,
@@
 
+\subsection{A Space-efficient CEK machine}
+\label{ssec:framework:cek}
+
 \begin{figure}
@@
 
-\figref{machine-cekcc} defines the machine. 
+\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
+machine is similar to \ineffCEK{}. 
+The most important differences are in values and continuations.
+In \ineffCEK\, we have one value constructor for all casted value.
+In \effCEK{C}, however, we do not have this generic value constructor, 
+instead we push those casts into the value constructors most of the time and 
+use $ \hcvOOinj{P}{v} $ to construct values injected to $ \TOOdyn $.
+Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
+casts are identity (i.e. constructed by $ id(T) $).
+In \ineffCEK\, a continuation have zero or more casts at the top.
+In \effCEK{C}, however, every continuation has exactly one cast at the top.
+Continuations in \ineffCEK\ that have no casts at the top correspond to 
+continuations in \effCEK{C}\ whose casts are identity.
+And continuations in \ineffCEK\ that have many casts at the top correspond to 
+continuations in \effCEK{C}\ where those casts are composed by $ 
+seq(c,c) $.
+
 Let $ v $ range over value. A value is either the unit value, function, pair, 
@@
 pre-continuations. 
-A continuation is now a pair where the first part is a cast and the second 
-part is a pre-continuation. 
-Pre-continuation are like the continuations before.
-
+A continuation is now a pre-continuation capped with a cast.
+Pre-continuation are like the continuations in \ineffCEK.
+
+\todo[inline]{KC needs to describe added rules. -KC}
 We list a fraction of reduction rules due to space limitation.

### 2019-10-17 paper.tex
move stuff

@@
 representations ($ C $). 
-In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
+In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
 $ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
-\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
+\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
 representation respects the \lazyD\ cast calculus. 
@@
 \subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
-\label{ssec:framework:correctness}
-
-\todo[inline]{KC needs to move some content in the next section to here. -KC}
-
-\section{Correctness Proof of \lazyD{} hypercoercions}
-\label{sec:hypercoercion-correctness}
+\label{secc:framework:correctness}
 
@@
 	about why you introduce the various definitions below. -JS}
-
-\subsection{\lazyD\ Cast Representations}
-
-In this section we describe a subset of cast representations, where all 
-elements implement the \lazyD{} blame strategy. We will show in 
-Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.
+\todo[inline]{KC needs to move some content in the next section to here. -KC}
 
@@
 
-\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
-\ineffCEKD}
-
-\todo[inline]{``monoidic'' is not a word. -JS}
-
-We use bisimulation to proof equivalence between the two machines.
-\todo[inline]{Which two machines? -JS}
 The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
@@
 
+\section{Correctness Proof of \lazyD{} hypercoercions}
+\label{sec:hypercoercion-correctness}
+
+In this section we prove \lazyD\ hypercoercions is correct by showing it, as a 
+cast representation, is surely \lazyD\ and a monoid. To use hypercoercion as a 
+cast representation in our framework, we need to defined four functions: $ 
+cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
+the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
+define the $ applyCast(c,v) $
+
+\todo[inline]{``monoidic'' is not a word. -JS}
+
+We use bisimulation to proof equivalence between the two machines.
+\todo[inline]{Which two machines? -JS}
+
 \subsection{\lazyD\ Hyper-coercion Respect \ineffCEKD}

### 2019-10-17 paper.tex
move framework stuff to the framework section

@@
 
-\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
+\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
 \label{secc:framework:correctness}
@@
 
-\section{Correctness Proof of \lazyD{} hypercoercions}
-\label{sec:hypercoercion-correctness}
-
-In this section we prove \lazyD\ hypercoercions is correct by showing it, as a 
-cast representation, is surely \lazyD\ and a monoid. To use hypercoercion as a 
-cast representation in our framework, we need to defined four functions: $ 
-cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
-the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
-define the $ applyCast(c,v) $
-
-\todo[inline]{``monoidic'' is not a word. -JS}
-
-We use bisimulation to proof equivalence between the two machines.
-\todo[inline]{Which two machines? -JS}
-
-\subsection{\lazyD\ Hyper-coercion Respect \ineffCEKD}
-\label{sec:LDHC-correct}
-
-\figref{hc-applyCast} defines $ applyCast $, the last interface function.
-We generalize shallow-consistency to middles and values ($ m \smile v $) in the 
-natural way.
-Applying the identity cast for the 
-dynamic type succeeds immediately. When applying a compound cast, we firstly 
-apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
-that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
-is the failure.
-$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
-
-\begin{figure}
-	\fbox{$ applyCast(c,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
-	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
-		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
-		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$ applyMiddle(\ell,m,v) = v $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
-	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
-		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
-		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
-		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
-		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,m,v)}{
-		\rOOfail{l}
-	}{
-		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
-	}
-	\end{array}
-	\]
-
-	\fbox{$ applyTail(t,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
-	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
-	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
-	\end{array}
-	\]
-	\caption{\lazyD\ hypercoercion's $ applyCast $}
-	\label{hc-applyCast}
-\end{figure}
-
-\begin{lemma}[\lazyD{} hypercoercion is Surely \lazyD]
-	\label{thm:hc-surely-lazyD}
-\end{lemma}
-\begin{proof}
-	See the supplementary material.
-\end{proof}
-
-\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{C}_\mathtt{D} $]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
-	\[
-	\judgeCeval{e}{o} \; \text{if and only if} \; 
-	\judgeSeval{H}{e}{o}
-	\]
-\end{theorem}
-\begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
-	Lemma~\ref{thm:hc-surely-lazyD}, and 
-	Proposition~\ref{thm:hc-monoid}.
-\end{proof}
-
-\subsection{Extra Theorems}
-
-In these section we show some extra theorems that might be useful in proving 
-the correctness of other cast representations.
-
 With the properties of surely \lazyD{} cast representation, it is 
@@
 	Fixed.
-I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' from 
+	I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' 
+	from 
 	wikipedia. (https://en.wikipedia.org/wiki/Bisimulation).
@@
 
+\section{Correctness Proof of \lazyD{} hypercoercions}
+\label{sec:hypercoercion-correctness}
+
+In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
+correct.
+
+To use hypercoercion as a 
+cast representation in our framework, we need to defined four functions: $ 
+cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
+the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
+define the $ applyCast(c,v) $  in \figref{hc-applyCast}
+
+Applying the identity cast for the 
+dynamic type succeeds immediately. When applying a compound cast, we firstly 
+apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
+that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
+is the failure.
+$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
+In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
+shallow-consistency to compare middles and values ($ m \smile v $) in the 
+natural way.
+
+\begin{figure}
+	\fbox{$ applyCast(c,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
+	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
+		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
+		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ applyMiddle(\ell,m,v) = v $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
+	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
+		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
+		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
+		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
+	}{}
+	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
+		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
+	}{}
+	\funrule{applyMiddle(\ell,m,v)}{
+		\rOOfail{l}
+	}{
+		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
+	}
+	\end{array}
+	\]
+
+	\fbox{$ applyTail(t,v) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
+	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
+	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
+	\end{array}
+	\]
+	\caption{\lazyD\ hypercoercion's $ applyCast $}
+	\label{hc-applyCast}
+\end{figure}
+
+\begin{lemma}[\lazyD{} hypercoercion is Surely \lazyD]
+	\label{thm:hc-surely-lazyD}
+\end{lemma}
+\begin{proof}
+	See the supplementary material.
+\end{proof}
+
+\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
+	\[
+	\judgeCeval{e}{o} \; \text{if and only if} \; 
+	\judgeSeval{H}{e}{o}
+	\]
+\end{theorem}
+\begin{proof}
+	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
+	Lemma~\ref{thm:hc-surely-lazyD}, and 
+	Proposition~\ref{thm:hc-monoid}.
+\end{proof}
+
 \section{Conclusion} \label{sec:conclude}

### 2019-10-17 paper.tex
trivial

@@
 instead we push those casts into the value constructors most of the time and 
-use $ \hcvOOinj{P}{v} $ to construct values injected to $ \TOOdyn $.
+use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
 Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 

### 2019-10-18 paper.tex
revise intro para of sec 4

@@
 \judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
-representation respects the \lazyD\ cast calculus. 
-Proving a similar theorem for \lazyUD\ is in progress.
+representation respects the semantics of \lazyD\ cast calculus. Having this 
+theorem means when people want to prove a \lazyD\ cast reprentation is correct, 
+all they have to do is to prove that their cast representation is $ surely \;
+LazyD $ and apply our framework to this proof, which should be much simpler 
+than proving equivalence of semantics.
+We are working on a similar theorem for \lazyUD{}.
 
@@
 		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
+	\end{enumerate}
+\end{definition}
+
+\begin{definition}[Surely \lazyD\ Cast Representation]
+	A cast representation is surely \lazyD\ if
+	\begin{enumerate}
+		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ \judgeType{v}{T_1} $,
+		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
+		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
+		then $ applyCast(seq(c_1,c_2),v) = 
+		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
+		where 
+		\[
+		\begin{array}{rcl}
+		\rOOsucc{v} >>= f & = & f(v) \\
+		\rOOfail{l} >>= f & = & \rOOfail{l}
+		\end{array}
+		\]
+		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		\item If $ v : \star $, 
+		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		\item If $ v : P $,
+		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
+		= applyCast(cast(P,l,Q),v) $
+		\item If $ v : P $,
+		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item If $ v : \POOunit $,
+		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		\item
+		$ 
+		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		= 
+		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+
+		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
+		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		$ = 
+		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
+		$ 
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
 	\end{enumerate}
@@
 \todo[inline]{KC needs to move some content in the next section to here. -KC}
-
-\begin{definition}[Surely \lazyD\ Cast Representation]
-	A cast representation is surely \lazyD\ if
-	\begin{enumerate}
-		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
-		\item If $ \judgeType{v}{T_1} $,
-		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
-		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
-		then $ applyCast(seq(c_1,c_2),v) = 
-		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
-		where 
-		\[
-		\begin{array}{rcl}
-		\rOOsucc{v} >>= f & = & f(v) \\
-		\rOOfail{l} >>= f & = & \rOOfail{l}
-		\end{array}
-		\]
-		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
-		\item If $ v : \star $, 
-		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
-		\item If $ v : P $,
-		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
-		= applyCast(cast(P,l,Q),v) $
-		\item If $ v : P $,
-		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \POOunit $,
-		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
-		\item
-		$ 
-		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
-		= 
-		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-
-		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
-		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
-		$ = 
-		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
-		$ 
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
-		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
-		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
-	\end{enumerate}
-\end{definition}
 

### 2019-10-18 paper.tex
make intro more friendly

@@
 
-There are two basic ways to represent cast space-efficiently: coercions 
+\todo[inline]{Big background}
+Around 2006, many work on integrating dynamic typing and static typing emerge, 
+notably gradual types \citep{siek2006gradual} and hybrid types 
+\citep{flanagan2006hybrid}. The semantics of gradually typed languages is 
+usuallly defined in terms of intermediate languages, where places for runtime 
+type checking are explicitly stated in the forms of cast expressions. Examples 
+of these intermediate languages include the blame calculus 
+\citep{wadler2009well} 
+and the cast calculus \citep{siek2009exploring}.
+Representing casts naively, however, suffices sever space leak. 
+For example, translation to intermediate languages can wrap some expressions 
+with casts, including expressions at tail positions. Thus, mutually 
+tail-recursive functions in source language can consume unbounded space at 
+runtime. There are more examples of space leaking in \citet{herman2010space}.
+
+\todo[inline]{The problem: space-efficient cast representation}
+There are two best studied ways to represent cast space-efficiently: coercions 
 \citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
@@
 
+\todo[inline]{Our solution: hypercoercion}
 We present a new cast representation, hypercoercion, which has a structurally 
@@
 \hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
-coercion together with cast calculus, an intermediate languages for gradual 
-typing \citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
+coercion together with cast calculus 
+\citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
 present hypercoerion in Section~\ref{sec:hypercoercion-definition}.
@@
 
+\todo[inline]{The problem: proving correctness of cast representations}
 Many of the existing research on coercions or threesomes include proof(s) of 
@@
 Despite the striking similarity of these proofs, they are all built from ground 
-up. We present a framework for proving correctness of cast reprensentation 
+up.
+
+\todo[inline]{Our solution: a framework}
+We present a framework for proving correctness of cast reprensentation 
 (Section~\ref{sec:framework}), and use it to prove the correctness of 
@@
 
-Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
-\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
-potential type errors, but 
-blame more programs. $ D $ and $ UD $ assign blame labels differently.
+%Some readers might know that there are four blame strategies: $ \{Lazy, 
+%Eager\} 
+%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
+%potential type errors, but 
+%blame more programs. $ D $ and $ UD $ assign blame labels differently.
 We focus on lazy strategies because recently \citet{new2019gradual} 

### 2019-10-18 paper.tex
sec framework intro

@@
 This section presents our second contribution, a framework for proving 
-correctness of cast representations.
+correctness of cast representations. The framework is a theorem saying that for 
+all cast representation $ C $, if $ C $ satisfies a collection of properties, 
+that an interpreter using $ C $ as the cast representation is extensionally 
+equivalent to the standard interpreter for \lazyD\ cast calculus. 
+We are working on a similar theorem for \lazyUD{}.
+
+Firstly, let us define what we mean by \emph{cast representations}. The first 
+three operators allow the interpreter to construct casts. We call them cast 
+constructors. 
+And the forth and last operator enable the interpreter to use casts.
+
+\begin{definition}[Cast Representation]
+	A cast representation is a set indexed by two types and has four interface 
+	functions:
+	\begin{description}
+		\item[$ id(T) $] constructs an identity cast
+		\item[$ seq(c_1,c_2) $] composes two casts
+		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$ applyCast(c,v) $] applies a cast onto a value
+	\end{description}
+\end{definition}
+
+To use the framework, users needs to prove that their cast representation is 
+\emph{surely LazyD}. The properties of surely \lazyD\ allow the framework to 
+compute the result of $ applyCast(c,v) $ without referring to its actual 
+definitions. This is because every casts at runtime is constructed by one of 
+the three cast constructors. The first property handles casts constructed by $ 
+id(T) $. And the second property handles $ seq(c,c) $. All remaining properties 
+handles $ cast(T,l,T) $. They are effectively a duplication of the $ 
+applyCast(c,v) $ in \ineffCEKD\ (Fig.~\ref{fig:applyCast-D-C}).
+
+\begin{definition}[Surely \lazyD\ Cast Representation]
+	A cast representation is surely \lazyD\ if
+	\begin{enumerate}
+		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ \judgeType{v}{T_1} $,
+		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
+		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
+		then $ applyCast(seq(c_1,c_2),v) = 
+		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
+		where 
+		\[
+		\begin{array}{rcl}
+		\rOOsucc{v} >>= f & = & f(v) \\
+		\rOOfail{l} >>= f & = & \rOOfail{l}
+		\end{array}
+		\]
+		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
+		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		\item If $ v : \star $, 
+		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		\item If $ v : P_1 $,
+		then $ applyCast(cast(\star,l,P_2),\hcvOOinj{P_1}{v}) 
+		= applyCast(cast(P_1,l,P_2),v) $
+		\item If $ v : P $,
+		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item If $ v : \POOunit $,
+		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		\item
+		$ 
+		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
+		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		= 
+		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+
+		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
+		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		$ = 
+		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
+		$ 
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
+		\item $ 
+		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
+	\end{enumerate}
+\end{definition}
+
 In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
@@
 than proving equivalence of semantics.
-We are working on a similar theorem for \lazyUD{}.
 
@@
 	representations}.
-
-\begin{definition}[Cast Representation]
-	A cast representation is a set indexed by two types and has four interface 
-	functions:
-	\begin{description}
-		\item[$ id(T) $] constructs an identity cast
-		\item[$ seq(c_1,c_2) $] composes two casts
-		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
-		\item[$ applyCast(c,v) $] applies a cast onto a value
-	\end{description}
-\end{definition}
 
@@
 		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
-	\end{enumerate}
-\end{definition}
-
-\begin{definition}[Surely \lazyD\ Cast Representation]
-	A cast representation is surely \lazyD\ if
-	\begin{enumerate}
-		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
-		\item If $ \judgeType{v}{T_1} $,
-		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
-		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
-		then $ applyCast(seq(c_1,c_2),v) = 
-		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
-		where 
-		\[
-		\begin{array}{rcl}
-		\rOOsucc{v} >>= f & = & f(v) \\
-		\rOOfail{l} >>= f & = & \rOOfail{l}
-		\end{array}
-		\]
-		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
-		\item If $ v : \star $, 
-		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
-		\item If $ v : P $,
-		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
-		= applyCast(cast(P,l,Q),v) $
-		\item If $ v : P $,
-		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \POOunit $,
-		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
-		\item
-		$ 
-		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
-		= 
-		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-
-		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
-		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
-		$ = 
-		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
-		$ 
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
-		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
-		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
-		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
 	\end{enumerate}

### 2019-10-18 paper.tex
finish intro of sec4:framework

@@
 
+\todo[inline]{What is the framework? Why can it simply proofs? Soundness?}
+
 This section presents our second contribution, a framework for proving 
@@
 all cast representation $ C $, if $ C $ satisfies a collection of properties, 
-that an interpreter using $ C $ as the cast representation is extensionally 
-equivalent to the standard interpreter for \lazyD\ cast calculus. 
-We are working on a similar theorem for \lazyUD{}.
-
-Firstly, let us define what we mean by \emph{cast representations}. The first 
-three operators allow the interpreter to construct casts. We call them cast 
-constructors. 
+then instantiating our parameterized space-efficient interpreter with $ C $ 
+gives an interpter that is extensionally equal to the standard interpreter for 
+\lazyD\ cast calculus. We are working on a similar theorem for \lazyUD{}.
+
+Firstly, let us define what we mean by \emph{cast representations} 
+(Definition~\ref{def:cast-rep}). The first three operators allow the 
+interpreter to construct casts. We call them \textit{cast constructors}. 
 And the forth and last operator enable the interpreter to use casts.
@@
 \begin{definition}[Cast Representation]
+	\label{def:cast-rep}
 	A cast representation is a set indexed by two types and has four interface 
@@
 To use the framework, users needs to prove that their cast representation is 
-\emph{surely LazyD}. The properties of surely \lazyD\ allow the framework to 
-compute the result of $ applyCast(c,v) $ without referring to its actual 
-definitions. This is because every casts at runtime is constructed by one of 
-the three cast constructors. The first property handles casts constructed by $ 
-id(T) $. And the second property handles $ seq(c,c) $. All remaining properties 
-handles $ cast(T,l,T) $. They are effectively a duplication of the $ 
-applyCast(c,v) $ in \ineffCEKD\ (Fig.~\ref{fig:applyCast-D-C}).
+\emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
+The definition confines the behavior of $ applyCast(c,v) $ so narrowly that it 
+allows the framework to apply casts without referring to the actual definition 
+of $ applyCast(c,v) $. This 
+is because every casts at runtime is constructed by one of 
+the three cast constructors. 
+Property (1) handles casts constructed by $ id(T) $. 
+And property (2) handles $ seq(c,c) $, which says applying the 
+composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
+All remaining properties handles $ cast(T,l,T) $. They are effectively a 
+duplication of the $ applyCast(c,v) $ in \ineffCEKD\ 
+(Fig.~\ref{fig:applyCast-D-C}).
 
 \begin{definition}[Surely \lazyD\ Cast Representation]
+	\label{def:surely-lazyd}
 	A cast representation is surely \lazyD\ if
@@
 
-In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of space-efficient semantics (in the style of CEK machines) indexed by cast 
-representations ($ C $). 
-In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
-$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
-\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
-representation respects the semantics of \lazyD\ cast calculus. Having this 
-theorem means when people want to prove a \lazyD\ cast reprentation is correct, 
-all they have to do is to prove that their cast representation is $ surely \;
-LazyD $ and apply our framework to this proof, which should be much simpler 
-than proving equivalence of semantics.
-
-Our space-efficient CEK machine is parameterized over \emph{cast 
-	representations}.
-
-Some cast representations are monoids as well. They are useful in our 
-correctness proof.
+If a cast representation is surely LazyD, proving this should be easier than 
+proving equivalence to the standard semantics of cast calculus.
+
+Some cast representations are also \textit{monoids}. They are useful in the 
+proof of our framework, and might be interesting elsewhere.
 
@@
 	A cast representation is a monoid if 
-	for all $c : T_1 \Longrightarrow T_2$,
+	for all
 	$c_1 : T_1 \Longrightarrow T_2$,
@@
 	\begin{enumerate}
-		\item $seq(id(T_1),c) = c$,
-		\item $seq(c,id(T_2)) = c$, and
+		\item $seq(id(T_1),c_1) = c_1$,
+		\item $seq(c_1,id(T_2)) = c_1$, and
 		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
@@
 \end{definition}
+
+In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
+of space-efficient semantics indexed by cast representations ($ C $). 
+In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is 
+$ surely \; \text{\lazyD} $ and is a monoid as well, $ \judgeDeval{e}{o} $ if 
+and only if $ \judgeSeval{C}{e}{o} $. In 
+subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
+the requirement that $ C $ must be a monoid, that is, every surely \lazyD\ cast 
+representation is correct.
 
@@
 \end{figure}
-
+ (in the style of CEK machines)
 \figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
@@
 
-\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
-\label{secc:framework:correctness}
+\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD\ if They are 
+Monoids}
+\label{secc:framework:monoid-correct}
 
@@
 
+\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
+\label{secc:framework:all-correct}
+
 With the properties of surely \lazyD{} cast representation, it is 

### 2019-10-18 paper.tex
LOTS OF ENGLISH SENTENCES

@@
 \newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
-\newcommand{\eqvDS}[3]{#2 \approx_{\mathcal{DS}} #3}
+\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
 % to-dos
@@
 	}{
-		\sOOreturn{u}{\kappa}
-		\\ &
-	}{
-		\sidecond{applyCast(c,v) = \rOOsucc{u}}
-	}
-
-	\redrule{
-		\sOOreturn{v}{(
-			\mathtt{cast} \; c \; \kappa
-			)}
-	}{
-		\sOOhalt{(\oOOblame{l})}
-		\\ &
-	}{
-		\sidecond{applyCast(c,v) = \rOOfail{l}}
-	}
+\begin{cases}
+	\sOOreturn{u}{\kappa} & \sidecond{applyCast(c,v) = \rOOsucc{u}}
+	\\
+	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(c,v) = \rOOfail{l}}
+\end{cases}
+	}{}
 \redrule{
@@
 \sOOhalt{observe(v)}}{}
+
+\redrule{
+\sOOhalt{o}}{
+\sOOhalt{o}}{}
 	\end{array}
@@
 \begin{proposition}[\lazyD\ hypercoercion is a monoid]
+	\label{thm:hc-monoid}
 	For all $c : T_1 \Longrightarrow T_2$,
@@
 \end{figure}
- (in the style of CEK machines)
-\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
-machine is similar to \ineffCEK{}. 
+\figref{machine-cekcc} defines, \effCEK{C}, a space-efficient semantics of cast 
+calculus in the style of CEK machines.
+This machine is similar to \ineffCEK{}. 
 The most important differences are in values and continuations.
@@
 pre-continuations. 
-A continuation is now a pre-continuation capped with a cast.
+A continuation is now a pre-continuation prefixed with a cast.
 Pre-continuation are like the continuations in \ineffCEK.
@@
 	The summary should be enough so that the reader knows a bit
-	about why you introduce the various definitions below. -JS}
-\todo[inline]{KC needs to move some content in the next section to here. -KC}
-
-The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
-the definitions of \ineffCEKD. Exceptions include the relations from 
-continuations to pre-continuations, between continuations, and between values. 
-We omit subscripts when there is no ambiguity.
-
-\todoKC{write down the exceptional bisimilarity relations}
-
-\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and \ineffCEKD]
+	about why you introduce the various definitions below. -JS
+\\---\\
+Fixed -KC}
+
+In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD and 
+is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
+$. We proof this theorem with a weak bisimulation between \ineffCEKD\ and 
+\effCEK{C}.
+
+The bisimulation relation between states ($\eqvSD{C}{s}{s}$) is mostly derived 
+from the state definition: \begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2 &
+	v_1 \approx v_2
+}{
+	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
+}
+\quad
+\inference{
+}{
+	\sOOhalt{o} \approx \sOOhalt{o}
+}
+\end{gather*}
+
+The bisimulation relation between environments and cast results are derived 
+from their definitions as well. And the relation from continuations in 
+\ineffCEKD\ and the pre-continuation in \effCEK{C} is in the natural way, for 
+example: \begin{gather*}
+\inference{
+	\rho_1 \approx \rho_2 &
+	\kappa_1 \approx \kappa_2
+}{
+	\kOOconsI{e}{\rho_1}{\kappa_1} \approx \kOOconsI{e}{\rho_2}{\kappa_2}
+}
+\end{gather*}
+
+And the relation between continuations is defined in terms of $ cont(k) $ and $ 
+ext(c,k) $: \begin{gather*}
+\inference{
+	k \approx \kappa
+}{
+	cont(k) \approx \kappa
+}
+\quad
+\inference{
+	\kappa_1 \approx \kappa_2
+}{
+	ext(cast(T_1,l,T_2),\kappa_1)
+	\approx
+	\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2} 
+}
+\end{gather*}
+
+The relation between values is more special. When the \ineffCEKD\ value is 
+non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
+the cast into the value constructors, except injections. For examples: 
+\begin{gather*}
+\inference{
+	v_1, v_2 : P &
+	v_1 \approx v_2
+}{
+	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
+}
+\quad
+\inference{
+	\Gamma , x : T_1 \vdash T_2 &
+	\rho_1 \approx \rho_2
+}{
+	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
+}
+%\quad
+%\inference{
+%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
+%	\approx
+%	v
+%}{
+%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
+%}
+\\
+\inference{
+	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
+	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
+}{
+	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
+	\approx
+	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
+}
+\end{gather*}
+
+Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
+introduce one more definition: $ s_1 \approx^{*} s_2 $ if and only if there 
+exists $ s_2' \in \text{\ineffCEKD} $ 
+such that $ \judgeCreduceTrans{s_2}{s_2'}$ and $ s_1 \approx s_2' $.
+
+\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
 	\label{thm:surely-monoidic-reduce}
 	For all cast representations $ C $, 
-	if $ C $ is surely \lazyD{} and monoidic,
-	$ s_1 \in \text{\ineffCEKD} $,
-	$ s_2 \in \mathcal{S}(C) $, and
-	$ s_1 \approx s_2 $, 
-	\begin{enumerate}
-		\item If $ \judgeDreduce{s_1}{s_3} $,
-		then
-		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
-		such that \begin{itemize}
-			\item $ s_5 \approx s_4 $, and
-			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-			\item $ \judgeDreduceTrans{s_3}{s_5} $
-		\end{itemize}
-		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
-		then
-		there exist $ s_3 \in \mathcal{C} $,
-		such that \begin{itemize}
-			\item $ s_3 \approx s_4 $
-			\item $ \judgeDreduceTrans{s_1}{s_3} $
-		\end{itemize}
-	\end{enumerate}
+	if $ C $ is surely \lazyD{} and is a monoid, 
+	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
+	$ s_{2}, s_{2}' \in \text{\ineffCEKD} $,
+	$ s_{1} \approx s_{2} $,
+	$ \judgeSreduce{C}{s_{1}}{s_{1}'} $, and
+	$ \judgeDreduce{s_{2}}{s_{2}'} $, then
+%	then there exist $ s_2'' \in \text{\ineffCEKD} $ such that
+	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
+	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
+%	\begin{enumerate}
+%		\item If $ \judgeDreduce{s_1}{s_3} $,
+%		then
+%		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
+%		such that \begin{itemize}
+%			\item $ s_5 \approx s_4 $, and
+%			\item $ \judgeSreduce{C}{s_2}{s_4} $,
+%			\item $ \judgeDreduceTrans{s_3}{s_5} $
+%		\end{itemize}
+%		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
+%		then
+%		there exist $ s_3 \in \mathcal{C} $,
+%		such that \begin{itemize}
+%			\item $ s_3 \approx s_4 $
+%			\item $ \judgeDreduceTrans{s_1}{s_3} $
+%		\end{itemize}
+%	\end{enumerate}
+
+Or diagrammatically, 
+\[\begin{array}{clclc}
+s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+\rotatebox[origin=c]{90}{$\approx$} 
+& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+s_{2} & 
+\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+\end{array}\]
+
 \end{lemma}
 \begin{proof}
-	See the supplementary material.
+	By following the transition rule of \ineffCEKD. See the supplementary 
+	materials for details.
 \end{proof}
@@
 	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
-	\lazyD{} and monoidic,
-	\[
-	\judgeDeval{e}{o} \; \text{if and only if} \; 
+	\lazyD{} and is a monoid,
+	\[
 	\judgeSeval{C}{e}{o}
+	 \; \text{if and only if} \; 
+	\judgeDeval{e}{o}
 	\]
 \end{lemma}
-\begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
+\begin{proof}Proving left implies right is trivial.
+To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
+we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
+taking one or more steps in \ineffCEKD. As we just took a positive number of 
+steps, we are closer to the halting state.
 	\todo[inline]{I'm guessing that you prove this lemma by induction,
 		using Lemma~\ref{thm:surely-monoidic-reduce}.
-		Proofs by induction are not ``immediate''. -JS}
+		Proofs by induction are not ``immediate''. -JS
+	\\---\\Fixed. -KC}
 \end{proof}
@@
 
-With the properties of surely \lazyD{} cast representation, it is 
-straightforward to proof that 
-all machines instantiated with these cast representations bisimulate each 
-other. 
-The bisimulation relation of states ($\eqvS{C}{C}{s}{s}$) is 
-derived from the definition of states.
-\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
-	``bisimulation relation''. I don't think you are using it properly
-	in the above sentence. -JS
-	\\---\\
-	Fixed.
-	I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' 
-	from 
-	wikipedia. (https://en.wikipedia.org/wiki/Bisimulation).
-	-KC}
-We omit subscripts when there is no 
-ambiguity. \begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2 &
-	v_1 \approx v_2
-}{
-	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-}
-\quad
-\inference{
-}{
-	\sOOhalt{o} \approx \sOOhalt{o}
-}
-\end{gather*}
-
-The relations between continuations, pre-continuations, enviroments, values, 
-cast results are also derived from their definitions. But the relation for 
-casts is special: \begin{gather*}
+In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD, then 
+$ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first prove 
+that all $ S(C) $ where $ C $ is surely lazyD are equivalent, then connect this 
+theorem to Lemma~\ref{thm:surely-monoidic-eval}.
+
+We prove the equivalence among \effCEK{S(C)} with strong bisimulation. This 
+time almost all the bisimulation relations are all derived from definitions 
+except the relaton for casts, which is by cast constructors:
+\begin{gather*}
 \inference{
@@
 	$ C_1 $ and $ C_2 $ are surely \lazyD,
-	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
-	$ s_1 \approx s_3 $,
-	$ \judgeSreduce{C_1}{s_1}{s_2} $,
-	then there exists an $ s_4 $ such that
-	\begin{itemize}
-		\item $ s_2 \approx s_4 $ and
-		\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
-	\end{itemize}
+	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
+	$ s_1 \approx s_2 $,
+	$ \judgeSreduce{C_1}{s_1}{s_1'} $, and
+	$ \judgeSreduce{C_2}{s_2}{s_2'} $, then 
+	$ s_1' \approx s_2' $
+
+	Or diagrammatically, 
+	\[\begin{array}{clc}
+	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+	\rotatebox[origin=c]{90}{$\approx$} 
+	& & \rotatebox[origin=c]{90}{$\approx$} \\
+	s_{2} & 
+	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
+	\end{array}\]
 \end{lemma}
 \begin{proof} 
+	This proof is effectively a duplication of the transition rule of 
+	\effCEK{S(C)}.
 	The key ideas of this proof are undoing sequencing with the property (2) of 
@@
 \begin{proof}
-	Immediately from Lemma~\ref{thm:CEKS-bisim}.
+	By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
 \end{proof}
 
-\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
-	$ \mathcal{C}_\mathtt{D} $]
+\begin{theorem}[Surely \lazyD\ Cast Representations Respect \ineffCEKD]
 	\label{thm:surely-lazyD-correct}
@@
 \begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
-	Proposition~\ref{thm:surely-lazyD-eqv}.
+	If we have a surely LazyD cast representation and it is a monoid, this 
+	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
+	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
+	represent casts as a list of triples of type, label, and type, where $ 
+	id(T) $ is the empty list and $ seq(c,c,) $ is list append. Another such 
+	representation is the \lazyD\ hypercoercion!
 \end{proof}
@@
 In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
-correct.
-
-To use hypercoercion as a 
-cast representation in our framework, we need to defined four functions: $ 
-cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
-the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
-define the $ applyCast(c,v) $  in \figref{hc-applyCast}
-
+correct. First we define $ applyCast(c,v) $ to make it a cast representation, 
+then prove that it is surely lazyD, and finally apply 
+Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.
+
+%To use hypercoercion as a 
+%cast representation in our framework, we need to defined four functions: $ 
+%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
+%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
+%we 
+%define the $ applyCast(c,v) $  in
+
+\figref{hc-applyCast} defines $ applyCast(c,v) $ for \lazyD\ hypercoercion. 
 Applying the identity cast for the 
@@
 \end{lemma}
-\begin{proof}
-	See the supplementary material.
-\end{proof}
+\begin{proof} See the supplementary material. \end{proof}
 
@@
 \begin{proof}
-	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
+	Immediately from Theorem~\ref{thm:surely-lazyD-correct} and 
+	Lemma~\ref{thm:hc-surely-lazyD}.
+	Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
 	Lemma~\ref{thm:hc-surely-lazyD}, and 

### 2019-10-18 paper.tex
clean up todo list

@@
 
-\todo[inline]{Big background}
 Around 2006, many work on integrating dynamic typing and static typing emerge, 
@@
 
-\todo[inline]{The problem: space-efficient cast representation}
 There are two best studied ways to represent cast space-efficiently: coercions 
@@
 
-\todo[inline]{Our solution: hypercoercion}
 We present a new cast representation, hypercoercion, which has a structurally 
@@
 
-\todo[inline]{The problem: proving correctness of cast representations}
 Many of the existing research on coercions or threesomes include proof(s) of 
@@
 
-\todo[inline]{Our solution: a framework}
 We present a framework for proving correctness of cast reprensentation 
@@
 \subsection{The \lazyD{} cast calculus}
-\todo[inline]{I want to merge this and the following subsetion to the 
-subsection above. -KC}
 
@@
 \todo[inline]{What is the main idea behind the organization of
- hypercoercions?}
+ hypercoercions? -JS
+ \\---\\
+ Are you asking why hc has three parts? Or why these subsections 
+in this section? -KC}
 
@@
 
-\todoKC{check consistency before using middle composition.}
 $ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
@@
 
-\todo[inline]{What is the framework? Why can it simply proofs? Soundness?}
-
 This section presents our second contribution, a framework for proving 
@@
 
-\todo[inline]{KC needs to describe added rules. -KC}
+\todo[inline]{KC needs to add missing rules in and describe them. -KC}
 We list a fraction of reduction rules due to space limitation.

### 2019-10-18 paper.tex
removed some todos, responded to others

@@
 functions, which suggest that they are not very ideal. 
-\todo[inline]{Why do we need to explain why both LD and LUD? -KC}
+\todo[inline]{Why do we need to explain why both LD and LUD? -KC
+  \\---\\
+Because the paper includes both. -JS}
 
@@
 \figref{fig:blame-static} defines the syntax of cast calculi and its
-static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
-types and product types. Besides, we annotate function codomain explicitly 
-because we need to compute identity hypercoercion for the codomain when 
-evaluating cast calculus with hypercoercions.
-\todo[inline]{Which previous definitions are you refering to?  What
-  are the little changes? -JS
-\\ --- \\ Fixed -KC}
-\todo[inline]{The term typing rule for casts is broken. -JS
-\\ --- \\ Fixed -KC}
-\todo[inline]{Why do you annotate the codomain of lambda abstractions
-	explicitly? -JS
-	\\---\\
-	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
-        \\---\\
-        The answer you put in the text is too vague. -JS
-        \\---\\
-        Fixed. -KC}
-Let $ T $ range over types. A type is either the dynamic type $ \star $
-(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
-or a pre-type. 
-Let $ P $ range over pre-types. Every pre-type is a type with a type 
-constructor at the top. For simplicity, we only have one base type, $ \POOunit 
-$. 
-Other pre-types are functions, products, and sums.
-
-$ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
-The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $ T_2 $ have no conflict 
-type information. Two types are consistent if one of them is $ \star $, or they 
-have the same top-most type constructor and the corresponding sub-parts are 
-consistent. Consistency is reflexive and symmetric, but not transitive.
-
-$ T_1 \smile T_2 $ reads ``$ T_1 $ and $ T_2 $ are shallowly-consistent''. Two 
-types are shallowly consistent if one of them is $ \star $, or they have the 
-same type constructor at the top. Shallow-inconsistency is the root of all 
-blame in lazy cast strategies -- casting a value to a shallowly inconsistent 
-type leads to a blame. Shallow-consistency is reflexive, symmetric, but 
-not transitive.
-
-Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
-of lambda abstractions explicitly because we need it when evaluating cast 
-calculus with hypercoercion. We have two additional terms: cast expressions and 
-blame expressions. Cast expressions insert runtime type checks. And blame 
-expressions raise an error. The typing rules for the additional terms are
-straightforward.
+static semantics. We extend the syntax of \citet{siek2009exploring}
+with sum and product types.  Let $ T $ range over types. A type is
+either the dynamic type $ \star $ (a.k.a. $ \mathtt{Dyn} $, $
+\mathbb{?} $, or $ \mathtt{Unknown} $), or a type with a type
+constructor at the top, that is, a pre-type, ranged over by $ P $. We
+include just one base type, $\POOunit$. The other pre-types are
+functions, products, and sums.
+
+As usual we write $ T_1 \sim T_2 $ when $ T_1 $ and $ T_2 $ are
+consistent. The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $
+T_2 $ have no conflicting type information. Two types are consistent
+if one of them is $ \star $, or they have the same top-most type
+constructor and the corresponding sub-parts are
+consistent. Consistency is reflexive and symmetric, but not
+transitive.
+
+We write $ T_1 \smile T_2 $ when $ T_1 $ and $ T_2 $ are
+shallowly-consistent, that is, if one of them is $ \star $, or they
+have the same type constructor at the top. Shallow-inconsistency is
+the root of all blame in lazy cast strategies -- casting a value to a
+shallowly inconsistent type leads to a blame. Shallow-consistency is
+reflexive, symmetric, but not transitive.
+
+Let $ e $ range over terms. Most terms are standard for a simply-typed
+lambda calculus. We annotate the codomain of a lambda abstraction
+explicitly because we refer to it in the dynamic semantics. Becuase
+this is a cast calculus, we have two additional terms: cast
+expressions and blame expressions. Cast expressions perform runtime
+type checks and blame expressions raise an error.
 
 Let $ v $ range over values. A value is either the unit, a function (a
-closure), a pair, a left injection, a right injection, or a 
-casted value. As shown 
-by the value typing rules, if the target type of a casted value is the dynamic 
-type, the underlying value must be of an injectable type. The definition of 
-injectable types depends on blame strategies: for the \lazyD\ strategy, every 
-pre-type is injectable; for the \lazyUD\ strategy, a pre-types is injectable if 
-and only if all its sub-parts are the dynamic type. If the target type of a 
-casted value is a pre-type, the type of the underlying value must have the same 
-type constructor.
+closure), a pair, a left injection, a right injection, or a casted
+value. As shown by the value typing rules, if the target type of a
+casted value is the dynamic type, the underlying value must be of an
+injectable type. The definition of injectable types depends on blame
+strategies: for the \lazyD\ strategy, every pre-type is injectable;
+for the \lazyUD\ strategy, a pre-types is injectable if and only if
+all its sub-parts are the dynamic type. If the target type of a casted
+value is a pre-type, the type of the underlying value must have the
+same type constructor.
 
@@
 
-Let $ o $ range over observations. They are what would be observed if a 
-program terminates. Observations include all value constructors and blame.
-The function converting values to observations ($ observe(v) = o $) is defined 
-in the natural way.
+Let $ o $ range over observations. They are what would be observed if
+a program terminates. Observations include all value constructors and
+blame.  The function converting values to observations ($ observe(v) =
+o $) is defined in the natural way.
 
@@
 (2) return a value to the current continuation.
-\todo[inline]{Briefly present the main ideas regarding how a CEK
-	machine works. (2-3 sentences) -JS
-\\---\\Fixed -KC}
 
@@
 convenient because space-efficiency is about compressing continuations.
-\todo[inline]{Explain why you are using a CEK machine instead of
-	reduction semantics. -JS
-        \\---\\Fixed -KC
-        \\---\\
-        Change ``one of us'' to ``first author''. -JS
- 		\\---\\Fixed -KC
-}
-
-\todo[inline]{Please fill in the missing reduction rules. -JS
-\\---\\ Fixed -KC}
+
 \todo[inline]{Change the order of parameters for applyCast to take
@@
     -KC
+    \\---\\
+    Postfix is better than prefix because then the casts read left to right,
+    which is the normal direction for English readers.
+    Please make it so. -JS
     }
@@
  Are you asking why hc has three parts? Or why these subsections 
-in this section? -KC}
+ in this section? -KC
+ \\---\\
+ three parts -JS
+}
 
@@
 \label{secc:framework:monoid-correct}
-
-\todo[inline]{Give a high-level summary of the proof.
-	The summary should be enough so that the reader knows a bit
-	about why you introduce the various definitions below. -JS
-\\---\\
-Fixed -KC}
 
@@
 steps, we are closer to the halting state.
-	\todo[inline]{I'm guessing that you prove this lemma by induction,
-		using Lemma~\ref{thm:surely-monoidic-reduce}.
-		Proofs by induction are not ``immediate''. -JS
-	\\---\\Fixed. -KC}
 \end{proof}

### 2019-10-18 paper.tex
comment
revert value and cast everywhere

@@
 \newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
-\newcommand{\eOOcast}[4]{\langle \cOOcast{#2}{#3}{#4} \rangle #1}
+\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
 \newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
+\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
 \newcommand{\oOOinj}{\mathtt{dyn}}
@@
 \newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
-%\newcommand{\cOOcast}[3]{#3 \overset{#2}{\Leftarrow} #1}
-\newcommand{\cOOcast}[3]{#3 \Leftarrow^{#2} #1}
-\newcommand{\vOOcast}[2]{\langle#2\rangle#1}
+\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
 \newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
@@
 \begin{cases}
-	\sOOreturn{u}{\kappa} & \sidecond{applyCast(c,v) = \rOOsucc{u}}
+	\sOOreturn{u}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{u}}
 	\\
-	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(c,v) = \rOOfail{l}}
+	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
 \end{cases}
@@
     which is the normal direction for English readers.
-    Please make it so. -JS
+    Please make it so. BTW, the way you keep choosing notation etc.
+    different from what I'm use to is making it more difficult than
+    necessary for me to collaborate with you. If this keeps up,
+    I may decide to stop. It's fine for you to ask why, it's not fine
+    for you to choose to make things difficult for me. -JS
+    \\---\\
+    Sorry, I don't indent to make things difficult for you. I have turned to 
+    postfix notation. -KC
     }
@@
 
-	\fbox{$applyCast(c,v) = r$}
+	\fbox{$applyCast(v,c) = r$}
 	\[
@@
 	\funrule{
-		applyCast(\cOOcast{\star}{l}{\star},v)
+		applyCast(v,\cOOcast{\star}{l}{\star})
 	}{
@@
 	\funrule{
-		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
-	}{
-		applyCast(\cOOcast{P_1}{l}{P_2},v)
+		applyCast(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
+	}{
+		applyCast(v,\cOOcast{P_1}{l_2}{P_2})
 	}{}
 	\funrule{
-		applyCast(\cOOcast{P}{l}{\star},v)
+		applyCast(v,\cOOcast{P}{l}{\star})
 	}{
@@
 	\funrule{
-		applyCast(\cOOcast{P_1}{l}{P_2},v)
+		applyCast(v,\cOOcast{P_1}{l}{P_2})
 	}{
@@
 		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
-		\item[$ applyCast(c,v) $] applies a cast onto a value
+		\item[$ applyCast(v,c) $] applies a cast onto a value
 	\end{description}
@@
 \emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
-The definition confines the behavior of $ applyCast(c,v) $ so narrowly that it 
+The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
 allows the framework to apply casts without referring to the actual definition 
-of $ applyCast(c,v) $. This 
+of $ applyCast(v,c) $. This 
 is because every casts at runtime is constructed by one of 
@@
 All remaining properties handles $ cast(T,l,T) $. They are effectively a 
-duplication of the $ applyCast(c,v) $ in \ineffCEKD\ 
+duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
 (Fig.~\ref{fig:applyCast-D-C}).
@@
 	\begin{enumerate}
-		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
+		\item If $ v : T $, then $ applyCast(v,id(T)) = \mathtt{succ} \; v $
 		\item If $ \judgeType{v}{T_1} $,
@@
 		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
-		then $ applyCast(seq(c_1,c_2),v) = 
-		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
+		then $ applyCast(v,seq(c_1,c_2)) = 
+		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2) $ \\
 		where 
@@
 		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
+		then $ applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
 		\item If $ v : \star $, 
-		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
+		then $ applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
 		\item If $ v : P_1 $,
-		then $ applyCast(cast(\star,l,P_2),\hcvOOinj{P_1}{v}) 
-		= applyCast(cast(P_1,l,P_2),v) $
+		then $ applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
+		= applyCast(v,cast(P_1,l,P_2)) $
 		\item If $ v : P $,
-		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		then $ applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
 		\item If $ v : \POOunit $,
-		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
+		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
 		\item
 		$ 
-		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
-		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
+		applyCast(\hcvOOfun{c_1}{\rho}{x}{b}{c_2}, 
+		cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
 		= 
@@
 
-		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
-		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
+		\item $ 
+		applyCast(\hcvOOcons{v_1}{c_1}{v_2}{c_2},cast(\POOprod{T_1}{T_2},l,T_3 
+		\times 
+		T_4)) $ \\
 		$ = 
@@
 		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
+		applyCast(\hcvOOinl{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
 		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
 		\item $ 
-		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
+		applyCast(\hcvOOinr{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
 		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
@@
 	}{
-		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
-	}
-	\redruleS{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
-		\sOOhalt{(\oOOblame{l})}
-	}{
-		\\ & &
-		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
-	}
+		\begin{cases}
+		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
+		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
+		\\
+		\sOOhalt{(\oOOblame{l})} \\
+		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
+		\end{cases}
+
+	}{}
 	\end{array}
@@
 In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
-correct. First we define $ applyCast(c,v) $ to make it a cast representation, 
+correct. First we define $ applyCast(v,c) $ to make it a cast representation, 
 then prove that it is surely lazyD, and finally apply 
@@
 %we 
-%define the $ applyCast(c,v) $  in
-
-\figref{hc-applyCast} defines $ applyCast(c,v) $ for \lazyD\ hypercoercion. 
+%define the $ applyCast(v,c) $  in
+
+\figref{hc-applyCast} defines $ applyCast(v,c) $ for \lazyD\ hypercoercion. 
 Applying the identity cast for the 
@@
 is the failure.
-$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
-In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
-shallow-consistency to compare middles and values ($ m \smile v $) in the 
+$ applyMiddle(v,\ell,m) $ and $ applyTail(v,t) $ are straightforward.
+In the definition of $ applyMiddle(v,\ell,m) $, we generalize 
+shallow-consistency to compare middles and values ($ v \smile m $) in the 
 natural way.
@@
 \begin{figure}
-	\fbox{$ applyCast(c,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
-	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
-		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
-		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$ applyMiddle(\ell,m,v) = v $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
-	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
-		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
-		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
-		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
-	}{}
-	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
-		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
-	}{}
-	\funrule{applyMiddle(\ell,m,v)}{
+	\fbox{$ applyCast(v,c) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyCast(v,\hyperCoercionI,)}{\rOOsucc{v}}{}
+	\funrule{applyCast(\hcvOOinj{P}{v},\hyperCoercionC{?^l}{m}{t})}{
+		applyMiddle(v,l,m) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\funrule{applyCast(v,\hyperCoercionC{\epsilon}{m}{t})}{
+		applyMiddle(v,\epsilon,m) \; >>= \; \lambda v. applyTail(t,v)
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$ applyMiddle(v,\ell,m) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
+	\funrule{applyMiddle(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
+		\rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 
+		\fatsemi^\ell c_4)})}
+	}{}
+	\funrule{applyMiddle(\hcvOOcons{v_1}{c_1}{v_2}{c_2},\ell,\POOprod{c_3}{c_4})}{
+		\rOOsucc{(\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 
+		\fatsemi^\ell c_4)})}
+	}{}
+	\funrule{applyMiddle(\hcvOOinl{v}{c_1},\ell,\POOsum{c_3}{c_4})}{
+		\rOOsucc{(\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)})}
+	}{}
+	\funrule{applyMiddle(\hcvOOinr{v}{c_2},\ell,\POOsum{c_3}{c_4})}{
+		\rOOsucc{(\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)})}
+	}{}
+	\funrule{applyMiddle(v,l,m)}{
 		\rOOfail{l}
 	}{
-		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
-	}
-	\end{array}
-	\]
-
-	\fbox{$ applyTail(t,v) = r $}
-	\[
-	\begin{array}{rclr}
-	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
-	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
-	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
+		\sidecond{\neg v \smile m}
+	}
+	\end{array}
+	\]
+
+	\fbox{$ applyTail(v,t) = r $}
+	\[
+	\begin{array}{rclr}
+	\funrule{applyTail(v,\bot^l)}{\rOOfail{l}}{}
+	\funrule{applyTail(v,\epsilon)}{\rOOsucc{v}}{}
+	\funrule{applyTail(v,!)}{\rOOsucc{(\hcvOOinj{P}{v})}}{}
 	\end{array}

### 2019-10-18 paper.tex
comments to myself
first para of intro

@@
 \todo[inline]{The first paragraph of the introduction should summarize
-  the entire introduction, and in some sense, the entire paper. -JS}
+  the entire introduction, and in some sense, the entire paper. -JS
+\\---\\
+Fixed -KC}
 
@@
 notably gradual types \citep{siek2006gradual} and hybrid types 
-\citep{flanagan2006hybrid}. The semantics of gradually typed languages is 
-usuallly defined in terms of intermediate languages, where places for runtime 
-type checking are explicitly stated in the forms of cast expressions. Examples 
-of these intermediate languages include the blame calculus 
-\citep{wadler2009well} 
-and the cast calculus \citep{siek2009exploring}.
-Representing casts naively, however, suffices sever space leak. 
-For example, translation to intermediate languages can wrap some expressions 
-with casts, including expressions at tail positions. Thus, mutually 
-tail-recursive functions in source language can consume unbounded space at 
-runtime. There are more examples of space leaking in \citet{herman2010space}.
+\citep{flanagan2006hybrid}. People usually define the semantics of gradually 
+typed languages with intermediate languages that have cast expressions, such as
+the blame calculus \citep{wadler2009well} and
+the cast calculus \citep{siek2009exploring}. Casts are ubiquitous at runtime. 
+For example, they can go in to values and continuations. Thus, representing 
+casts naively with types can change asymptotically the space consumption of 
+programs \citep{herman2010space}. There are several known space-efficient cast 
+representations, but they have different strength and weakness. This paper 
+presents a new solution that combines some of their best parts. Also, a valid 
+cast representation must not change the result of programs. This paper presents 
+the first framework for proving this kind of theorems.
+
+%
+%For example, translation to intermediate languages can wrap some expressions 
+%with casts, including expressions at tail positions. Thus, mutually 
+%tail-recursive functions in source language can consume unbounded space at 
+%runtime. There are more examples of space leaking in \citet{herman2010space}.
 
@@
 	\rho_1 \approx \rho_2
-}{
+}{z
 	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
@@
 \end{gather*}
+\todo[inline]{need a more readable example -KC}
 

### 2019-10-18 paper.tex
intro

@@
 Another strength of hypercoercion over coercion is that hypercoercion might 
-have a more compact memory representations ...
-\todo[inline]{Could Jeremy explain here why hypercoercion is more compact in 
-memory? -KC}
+have a more compact memory representations. In Grift 
+\citep{kuhlenschmidt2018efficient}, the longest coercions are represented with
+two cons boxes. But for hypercoercion, we are optimistic that one cons box 
+suffices. Using less cons boxes saves memory as well as running time.
+\todo[inline]{
+	Could Jeremy help explain explaining why hypercoercion is more compact in 
+	memory?
+	Cons boxes seem to be non-standard, but I don't know a better name.
+ -KC}
 
@@
 correctness, that is, the cast calculus reduces to an observation ($ e 
-\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
-e \Downarrow_{*} o $), where an observation is either a value constructor or 
+\Downarrow o $) if and only if their space-efficient calcului reduce to the 
+same observation ($ e \Downarrow_{*} o $), where an observation is either a 
+value constructor or 
 blame. 
@@
 show that \eager{} strategies are incompatible with $\eta$-equivalence of 
-functions, which suggest that they are not very ideal. 
+functions, which suggest that they are not very ideal. We are unaware of any 
+strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
 \todo[inline]{Why do we need to explain why both LD and LUD? -KC
   \\---\\
-Because the paper includes both. -JS}
+Because the paper includes both. -JS
+\\---\\
+Fixed. -KC}
 
@@
 	\item hypercoercion, a new space-efficient cast representation, which has a 
-	structurally recursive composition and has a more compact memory 
+	structurally recursive composition and a more compact memory 	
 	representation.
@@
 	We conjecture that both coercion and threesome can fit into this framework.
-	\item a formal proof that hypercoercion respect the semantics of cast 
+	\item a formal proof that hypercoercion respects the semantics of cast 
 	calculus

### 2019-10-18 paper.tex
standardize Lazy D and Lazy UD font

@@
 \newcommand{\judgeTypeFT}[3]{#1 : #2 \Longrightarrow #3} % FT = From To
-\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
-\newcommand{\lazyD}{$\mathtt{Lazy D}$}
-\newcommand{\eager}{$\mathtt{Eager}$}
+\newcommand{\lazyUD}{Lazy\;UD}
+\newcommand{\lazyD}{Lazy\;D}
 \newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
@@
 We focus on lazy strategies because recently \citet{new2019gradual} 
-show that \eager{} strategies are incompatible with $\eta$-equivalence of 
+show that eager strategies are incompatible with $\eta$-equivalence of 
 functions, which suggest that they are not very ideal. We are unaware of any 

### 2019-10-18 paper.tex
HC -> hypercoercion

@@
 
-\figref{fig:HC-D} defines the constructors of \lazyD{} HC.
+\figref{fig:HC-D} defines the constructors of \lazyD{} hypercoercion.
 
@@
 
-The correctness proof of \lazyD\ HC is deferred to \secref{sec:LDHC-correct} 
+The correctness proof of \lazyD\ hypercoercion is deferred to 
+\secref{sec:LDHC-correct} 
 because it relies on the space-efficient CEK abstract machine in 

### 2019-10-18 paper.tex
revised first paragraph of intro

--- 2019-10-18 paper.tex
@@
 
-Around 2006, many work on integrating dynamic typing and static typing emerge, 
-notably gradual types \citep{siek2006gradual} and hybrid types 
-\citep{flanagan2006hybrid}. People usually define the semantics of gradually 
-typed languages with intermediate languages that have cast expressions, such as
-the blame calculus \citep{wadler2009well} and
-the cast calculus \citep{siek2009exploring}. Casts are ubiquitous at runtime. 
-For example, they can go in to values and continuations. Thus, representing 
-casts naively with types can change asymptotically the space consumption of 
-programs \citep{herman2010space}. There are several known space-efficient cast 
-representations, but they have different strength and weakness. This paper 
-presents a new solution that combines some of their best parts. Also, a valid 
-cast representation must not change the result of programs. This paper presents 
-the first framework for proving this kind of theorems.
+Around 2006, several groups of researchers proposed ways to integrate
+dynamic typing and static typing, notably gradual typing
+\citep{siek2006gradual}, hybrid typing \citep{flanagan2006hybrid},
+migratory typing \citep{Tobin-Hochstadt:2006fk}, and multi-language
+iteroperability \citep{Gray:2005ij,Matthews:2007zr}. Researchers
+usually define the semantics of gradually typed languages by
+translation to an intermediate language with casts, such as the blame
+calculus \citep{wadler2009well} and other cast calculi
+\citep{siek2009exploring}. Unfortunately, straightforward
+implementations of casts on higher-order values (functions, objects,
+etc.) impose significant runtime overheads that can change the
+asymptotic time and space complexity of a program
+\citep{herman2010space}. There are several known space-efficient cast
+representations, with various strengths and weaknesses. This paper
+presents a new cast representation, named \emph{hypercoercions}, that
+is good for both mechanized metatheory and good for implementation.
+The composition operator for hypercoercions is structurally recursive
+and the hypercoercions are suggestive of a bit-level representation
+that minimizes the need for pointers and fits all first-order casts
+into 64 bits.  Of course, valid cast representation must not change
+the result of programs. This paper presents first steps toward a
+framework for proving the equivalence of cast calculi.
 
@@
 %% Bibliography
-\bibliography{bibfile}
+\bibliography{bibfile,all}
 

### 2019-10-18 paper.tex
intro editing

@@
 \citep{herman2010space}. There are several known space-efficient cast
-representations, with various strengths and weaknesses. This paper
+representations, with various strengths and weaknesses \citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,Garcia-Perez:2014aa}. This paper
 presents a new cast representation, named \emph{hypercoercions}, that

### 2019-10-18 paper.tex
change citation

--- 2019-10-18 paper.tex
@@
 \citep{herman2010space}. There are several known space-efficient cast
-representations, with various strengths and weaknesses. This paper
+representations, with various strengths and weaknesses \citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}. This paper
 presents a new cast representation, named \emph{hypercoercions}, that

### 2019-10-18 paper.tex
changed title
edit to intro

--- 2019-10-18 paper.tex
@@
 %% Title information
-\title{Blame and Coercion: Together Again for the Second Time}
+\title{Hypercoercions and a Framework for Equivalence of Cast Calculi}
 
@@
 \citep{herman2010space}. There are several known space-efficient cast
-representations, with various strengths and weaknesses. This paper
-presents a new cast representation, named \emph{hypercoercions}, that
-is good for both mechanized metatheory and good for implementation.
-The composition operator for hypercoercions is structurally recursive
-and the hypercoercions are suggestive of a bit-level representation
-that minimizes the need for pointers and fits all first-order casts
-into 64 bits.  Of course, valid cast representation must not change
-the result of programs. This paper presents first steps toward a
-framework for proving the equivalence of cast calculi.
+representations, with various strengths and weaknesses
+\citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}. This
+paper presents a new cast representation, named \emph{hypercoercions},
+that is good for both mechanized metatheory and good for
+implementation. Recall that it is the composition operator in these
+systems that enables space-efficiency by compressing casts.  The
+composition operator for hypercoercions is structurally recursive and
+hypercoercions are suggestive of a bit-level representation that
+minimizes the need for pointers and fits all first-order casts into 64
+bits.  Of course, an alternative cast representation must not change
+the result of programs. This paper presents steps toward a framework
+for proving the equivalence of cast calculi and, in particular, proves
+that an abstract machine using hypercoercions is equivalent to an
+abstract machine using standard casts.
 
@@
 
-There are two best studied ways to represent cast space-efficiently: coercions 
-\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
-\citep{siek2015blame} and threesomes 
-\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
-strength and 
-weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
-coercion is easy to understand, but hard to implement, while threesome is easy 
-to implement, but hard to understand. \citet{garcia2013calculating} in addition 
-claims that coercion is more difficult to reason about formally because 
-its compose function is not structurally recurisive. For instance, the 
-developers of Grift \citep{kuhlenschmidt2018efficient} report that it is tricky 
-to convince their proof assistants that the compose function terminates.
+The current state of the art regarding cast representations includes
+\begin{itemize}
+\item threesomes \citep{siek2010threesomes},
+\item supercoercions \citep{garcia2014deriving}, and
+\item coercions in normal form
+  \citep{siek2012interpretations,siek2015blame}.
+\end{itemize}
+Threesomes and supercoercions are good for mechanized metatheory
+because their compose operators are structurally recursive, making
+them easy to define in a proof assistant such as Agda. In contrast,
+the coercions in normal form have compose operators that are not
+structurally recursive, which makes it more difficult to define in
+Agda, requiring what amounts to an explicit proof of termination.
+%
+On the other hand, coercions in normal form are easier to understand
+than threesomes (with a strange labelled bottom type), and
+supercoercions (with 10 different kinds).
+
+%% There are two best studied ways to represent cast space-efficiently:
+%% coercions
+%% \citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations}
+%% \citep{siek2015blame} and threesomes
+%% \citep{siek2010threesomes}\citep{garcia2013calculating}. They have
+%% different strength and weakness. \citet{garcia2013calculating} and
+%% \citet{siek2015blame} claim that coercion is easy to understand, but
+%% hard to implement, while threesome is easy to implement, but hard to
+%% understand. \citet{garcia2013calculating} in addition claims that
+%% coercion is more difficult to reason about formally because its
+%% compose function is not structurally recurisive. For instance, the
+%% developers of Grift \citep{kuhlenschmidt2018efficient} report that it
+%% is tricky to convince their proof assistants that the compose function
+%% terminates.
 

### 2019-10-19 paper.tex
small step
small-step case

@@
 \redrule{
-\sOOreturn{v_1}{(\kOOconsI{\rho}{e_2}{\kappa})}}{
+\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
 \sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}
@@
 \redrule{
-\sOOreturn{v_1}{(\kOOappI{\rho}{e_2}{\kappa})}}{
+\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
 \sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}
@@
 \redrule{
-\sOOreturn{v_1}{(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{
-\sOOinspect{e_2}{\rho}{(\kOOcaseII{E}{v_1}{e_3}{\kappa})}}{}
-
-\redrule{
-\sOOreturn{v_2}{(\kOOcaseII{\rho}{v_1}{e_3}{\kappa})}}{
+\sOOreturn{v_1}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{
+\sOOinspect{e_2}{\rho}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{}
+
+\redrule{
+\sOOreturn{v_2}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{
 \sOOinspect{e_3}{\rho}{
@@
 }}{}
-		\redrule{
-		\sOOreturn{v_3}{(
-			\mathtt{case_3} \;
-			v_1 \; v_2 \;
-			\kappa
-			)}
-	}{case(v_1,
-		\mathtt{app_2} \; v_2 \; \kappa,
-		\mathtt{app_2} \; v_3 \; \kappa
-		)}{}
+
+\redrule{
+\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)}
+}{
+\sOOreturn{v}{(\kOOappII{v_2}{\kappa})}
+}{}
+
+\redrule{
+	\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)}
+}{
+\sOOreturn{v}{(\kOOappII{v_3}{\kappa})}
+}{}
+
+\redrule{
+	\sOOreturn{v_3}{(\mathtt{case_3}\;
+		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
+		\;v_2\;\kappa)}
+}{
+	\sOOreturn{v_3'}{
+		(\mathtt{case_3}\;v
+		\;v_2'\;\kappa)
+	}
+}{\\&&
+\text{where}\;
+v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}
+\\&&
+\text{and}\;
+v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}
+}
 
@@
 	\]	
-
-	\fbox{$case(v, \kappa, \kappa) = s$}
-	\[
-	\begin{array}{rclr}
-	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
-		\sOOreturn{v}{\kappa_1}
-	}{}
-	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
-		\sOOreturn{v}{\kappa_2}
-	}{}
-	\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
-		case(v,
-		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
-		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
-	}{}
-	\end{array}
-	\]
+%	
+%	\fbox{$case(v, \kappa, \kappa) = s$}
+%	\[
+%	\begin{array}{rclr}
+%	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
+%		\sOOreturn{v}{\kappa_1}
+%	}{}
+%	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
+%		\sOOreturn{v}{\kappa_2}
+%	}{}
+%	
+%\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
+%		case(v,
+%		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
+%		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
+%	}{}
+%	\end{array}
+%	\]
 
@@
 pair, the machine firstly take out the first (resp. second) part of $ v $, the 
-un-casted pair, and cast the result. To case-split a sum, the machine looks 
-deep inside the value to find out whether it is a left injection or a right 
-one.
+un-casted pair, and cast the result. In case spliting, if the target value is a 
+left injection, the machine moves to a state that will apply the first 
+continuation function to the value inside the left injection. The case for 
+right injection is similar. When the target value is a casted sum, the machine 
+moves the cast from the target value to continuations functions. 
 \todo[inline]{Change the rules for case to be small step, i.e.,
-	the case function should not be recursive. -JS}
-Along the way, the machine accumulates the pending casts onto the 
-continuations. To cast a value, the machine try to apply the cast to the value. 
+	the case function should not be recursive. -JS
+\\---\\ Fixed. -KC}
+%Along the way, the machine accumulates the pending casts onto the 
+%continuations. 
+To cast a value, the machine try to apply the cast to the value. 
 If the cast succeeds, the machine returns the result to the next continuation. 
 If the cast fails, the machine halts with the blame label.
+When the continuation is $ stop $, the machine enters a halting state. The 
+When the machine is in a halting state, it stays in the same state.
 

### 2019-10-19 paper.tex
edits to the intro

@@
   Will fix grammar after fixing all other problems -KC}
-\todo[inline]{The first paragraph of the introduction should summarize
-  the entire introduction, and in some sense, the entire paper. -JS
-\\---\\
-Fixed -KC}
 
@@
 %blame more programs. $ D $ and $ UD $ assign blame labels differently.
-We focus on lazy strategies because recently \citet{new2019gradual} 
-show that eager strategies are incompatible with $\eta$-equivalence of 
-functions, which suggest that they are not very ideal. We are unaware of any 
-strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
-\todo[inline]{Why do we need to explain why both LD and LUD? -KC
-  \\---\\
-Because the paper includes both. -JS
-\\---\\
-Fixed. -KC}
-
-Here are our major contribution:
+
+We focus on lazy cast strategies because we suspect that they are more
+efficient that eager strategies, which is why lazy was chosen in the
+Grift compiler \citep{Kuhlenschmidt:2019aa}, and because
+\citet{new2019gradual} show that eager strategies are incompatible
+with $\eta$-equivalence of functions. We are interested in the D blame
+tracking strategy because it has a more straightforward notion safe
+cast compared to UD \citep{siek2009exploring}, which is why D was
+chosen Grift compiler. However, we are also intersted in UD because it
+plays a prominent role in the gradual typing literature
+\citep{wadler2009well}.
+
+The primary contributions of this paper are:
 \begin{itemize}
-	\item hypercoercion, a new space-efficient cast representation, which has a 
-	structurally recursive composition and a more compact memory 	
+\item hypercoercions, a new space-efficient cast representation, which
+  has a structurally recursive composition and a more compact memory
   representation.
-	\item a framework in Agda for proving correctness of cast represantations. 
-	We conjecture that both coercion and threesome can fit into this framework.
-	\item a formal proof that hypercoercion respects the semantics of cast 
-	calculus
+\item a framework in Agda for proving correctness of cast
+  represantations.  We conjecture that both coercion and
+  threesome can fit into this framework.
+\item a formal proof that hypercoercion respects the semantics
+  of the \lazyD{} cast calculus.
 \end{itemize}
@@
 
-\todo[inline]{Change the order of parameters for applyCast to take
-	the value first and the cast second. -JS
-	\\---\\
-	Could you tell me why taking the value first is better?
-	I am always taking the target of induction first. -KC
-	\\---\\
-    It's better because it matches the postfix syntax we are using for
-    casts. Currently line 2 of applyCast for D is difficult to read,
-    compare it with line 4 of applyCast for UD. -JS
-    \\---\\
-    Does it mean changing the syntax for casts to a prefix syntax would work as 
-    well? 
-    If yes, I prefer this way, because of the reason in my first response 
-    and that function applications (apply) also takes arguments in this order.
-    I have fixed it with my idea so that we can see if it works. This change is 
-    easy to undo.
-    -KC
-    \\---\\
-    Postfix is better than prefix because then the casts read left to right,
-    which is the normal direction for English readers.
-    Please make it so. BTW, the way you keep choosing notation etc.
-    different from what I'm use to is making it more difficult than
-    necessary for me to collaborate with you. If this keeps up,
-    I may decide to stop. It's fine for you to ask why, it's not fine
-    for you to choose to make things difficult for me. -JS
-    \\---\\
-    Sorry, I don't indent to make things difficult for you. I have turned to 
-    postfix notation. -KC
-    }
-
 Let $ r $ range over cast results. A cast result is either a success, which 

### 2019-10-19 paper.tex
some more comments
describe machine D

--- 2019-10-19 paper.tex
@@
 		\redrule{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
+	}{}
+
+	\redrule{
 		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
@@
 \sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}
+
 \redrule{
@@
 \sOOinspect{e}{\rho}{(\kOOcar{\kappa})}}{}
+
 \redrule{
@@
 	\sOOinspect{e}{\rho}{(\kOOcdr{\kappa})}}{}
+
 \redrule{
@@
 \sOOinspect{e_1}{\rho}{(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
-	\redrule{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-	}{
-		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
-	}{}
 
@@
 
-The reduction relation $ \judgeCreduce{s}{s} $ depends on $ applyCast $, a 
-function depending on blame strategies. We will give the definitions of $ 
-applyCast $ shortly.
-To evaluate a cast 
-expression, the machine move the 
-cast to the continuation and evaluate the inner expression. To apply a casted 
+The reduction relation $ \judgeCreduce{s}{s} $ is parameterized over $ 
+applyCast $. 
+When evaluating a cast expression, the machine moves the cast to the 
+continuation and evaluate the inner expression.
+Other transition rules starting from $ Eval $ states are standard.
+To apply a casted 
 function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
@@
 \inference{
-	\Gamma , x : T_1 \vdash T_2 &
-	\rho_1 \approx \rho_2
-}{z
-	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
-}
+	v_1, v_2 : T &
+	v_1 \approx v_2
+}{
+	\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
+}
+\quad
+\inference{
+	(\hcvOOinl{v}{c}, v_2) : \POOsum{T_1}{T_2}
+}{
+	\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))} \approx 
+	\vOOcast{v_2}{\cOOcast{T_1}{l}{T_3}}
+}
+%\quad
+%\inference{
+%	\Gamma , x : T_1 \vdash T_2 &
+%	\rho_1 \approx \rho_2
+%}{
+%	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
+%}
 %\quad
@@
 %}
-\\
-\inference{
-	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
-	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
-}{
-	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
-	\approx
-	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
-}
+%\\
+%\inference{
+%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
+%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
+%}{
+%	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
+%	\approx
+%	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
+%}
 \end{gather*}
-\todo[inline]{need a more readable example -KC}
 

### 2019-10-19 paper.tex

--- 2019-10-19 paper.tex
@@
 moves the cast from the target value to continuations functions. 
-\todo[inline]{Change the rules for case to be small step, i.e.,
-	the case function should not be recursive. -JS
-\\---\\ Fixed. -KC}
 %Along the way, the machine accumulates the pending casts onto the 
@@
 
+\todo[inline]{Change ``Cast Representation'' to
+  ``Cast Abstract Data Type''. -JS}
+
 \begin{definition}[Cast Representation]
@@
 \end{definition}
+
+\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS}
 

### 2019-10-19 paper.tex
use mapsto instead of rightarr, mimic PLT Redex
rename to ADT

@@
 % Lazy D cast calculus on space-inefficient CEK
-\newcommand{\judgeCreduce}[2]{#1 \longrightarrow_{\mathcal{C}} #2}
-\newcommand{\judgeCreduceTrans}[2]{#1 \longrightarrow_{\mathcal{C}}^{*} #2}
+\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
+\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
 \newcommand{\judgeCeval}[2]{#1 \Downarrow_{\mathcal{C}} #2}
-\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{C} & #2 & #3\\}
+\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
 % blame calculus on space-efficient CEK
-\newcommand{\judgeSreduce}[3]{#2 \longrightarrow_{\mathcal{S}(#1)} #3}
-\newcommand{\judgeSreduceTrans}[3]{#2 \longrightarrow_{\mathcal{S}(#1)}^{*} #3}
+\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
+\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
 \newcommand{\judgeSeval}[3]{#2 \Downarrow_{\mathcal{S}(#1)} #3}
-\newcommand{\redruleS}[3]{#1 & \longrightarrow_{\mathcal{S}(C)} & #2 & #3\\}
+\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
 % Normal Coercion
@@
 \newcommand{\ineffCEKUD}{$ \mathcal{UD} $}
-\newcommand{\judgeDreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
-\newcommand{\judgeDreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
+\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
+\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
 \newcommand{\judgeDeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
@@
 
-Firstly, let us define what we mean by \emph{cast representations} 
-(Definition~\ref{def:cast-rep}). The first three operators allow the 
-interpreter to construct casts. We call them \textit{cast constructors}. 
-And the forth and last operator enable the interpreter to use casts.
+We captures the set of operators that every cast representation must provide 
+with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
+The first three operators allow a language implementation to construct casts. 
+So we call them \textit{cast constructors}. And the forth and last operator 
+enable the implementation to use apply casts.
 
 \todo[inline]{Change ``Cast Representation'' to
-  ``Cast Abstract Data Type''. -JS}
-
-\begin{definition}[Cast Representation]
+  ``Cast Abstract Data Type''. -JS
+\\---\\
+Fixed -KC}
+
+\begin{definition}[Cast Abstract Data Type (Cast ADT)]
 	\label{def:cast-rep}
-	A cast representation is a set indexed by two types and has four interface 
-	functions:
+	A cast abstract data type is a set $ Cast $ indexed by two types with
+	four operators:
 	\begin{description}
-		\item[$ id(T) $] constructs an identity cast
-		\item[$ seq(c_1,c_2) $] composes two casts
-		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
-		\item[$ applyCast(v,c) $] applies a cast onto a value
+		\item[$ id(T) = c $] constructs an identity cast
+		\item[$ seq(c_1,c_2)=c $] composes two casts
+		\item[$ cast(T_1,l,T_2)=c $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$ applyCast(v,c)=r $] applies a cast onto a value
 	\end{description}
@@
 
-\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS}
-
-To use the framework, users needs to prove that their cast representation is 
-\emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
+\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS
+\\---\\
+Fixed -KC}
+
+To use our framework, users needs to prove that their cast representation 
+implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}).
 The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
@@
 
-\begin{definition}[Surely \lazyD\ Cast Representation]
+\begin{definition}[Lazy D Cast ADT]
 	\label{def:surely-lazyd}
-	A cast representation is surely \lazyD\ if
+	A  Cast ADT is a Lazy D Cast ADT if:
 	\begin{enumerate}
@@
 
-If a cast representation is surely LazyD, proving this should be easier than 
-proving equivalence to the standard semantics of cast calculus.
+If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
+and be confident that this cast representation is valid.
 
@@
 \begin{definition}[Monoid]
-	A cast representation is a monoid if 
+	A Cast ADT is a monoid if 
 	for all
@@
 In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of space-efficient semantics indexed by cast representations ($ C $). 
+of space-efficient semantics indexed by Cast ADTs ($ C $). 
 In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
-$ surely \; \text{\lazyD} $ and is a monoid as well, $ \judgeDeval{e}{o} $ if 
+a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
 and only if $ \judgeSeval{C}{e}{o} $. In 
 subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
-the requirement that $ C $ must be a monoid, that is, every surely \lazyD\ cast 
-representation is correct.
+the requirement that $ C $ must be a monoid, that is, every instance of Lazy D 
+Cast ADT is correct.
 
@@
 
-\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD\ if They are 
+\subsection{\lazyD\ Cast ADTs Respect \ineffCEKD\ if They are 
 Monoids}
@@
 
-In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD and 
+In this subsection, we prove that if a instance of Cast ADT $ C $ is Lazy D and 
 is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
@@
 	\label{thm:surely-monoidic-reduce}
-	For all cast representations $ C $, 
-	if $ C $ is surely \lazyD{} and is a monoid, 
+	For all instance of Cast ADT $ C $, 
+	if $ C $ is \lazyD{} and is a monoid, 
 	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
@@
 
-\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
+\begin{lemma}[$ \text{Lazy D Cast ADT} \cap \text{Monoid} $ Respects 
 	$ \mathcal{C} $]
 	\label{thm:surely-monoidic-eval}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
-	\lazyD{} and is a monoid,
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
+	\lazyD{} Cast ADT and a monoid,
 	\[
@@
 
-\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
+\subsection{\lazyD\ Cast ADT Respect \ineffCEKD}
 \label{secc:framework:all-correct}
 
-In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD, then 
-$ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first prove 
-that all $ S(C) $ where $ C $ is surely lazyD are equivalent, then connect this 
-theorem to Lemma~\ref{thm:surely-monoidic-eval}.
+In this subsection, we prove that for all $ C $, if $ C $ is a Lazy D Cast ADT, 
+then $ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first 
+prove that all $ S(C) $ where $ C $ is a Lazy D Cast ADT are equivalent, then 
+connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.
 
@@
 	If 
-	$ C_1 $ and $ C_2 $ are surely \lazyD,
+	$ C_1 $ and $ C_2 $ are instances of Lazy D Cast ADT,
 	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
@@
 	The key ideas of this proof are undoing sequencing with the property (2) of 
-	surely \lazyD{} cast representation, and handling all possibly uses of $ 
+	Lazy D Cast ADT, and handling all possibly uses of $ 
 	cast(T,l,T) $ with property (3)-(11).
@@
 
-\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
+\begin{proposition}[Equivalence of \lazyD{} Cast ADT]
 	\label{thm:surely-lazyD-eqv}
 	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
-	are surely \lazyD\ cast representations,
+	are \lazyD\ Cast ADTs,
 	\[
@@
 
-\begin{theorem}[Surely \lazyD\ Cast Representations Respect \ineffCEKD]
+\begin{theorem}[\lazyD\ Cast ADT Respects \ineffCEKD]
 	\label{thm:surely-lazyD-correct}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
-	\lazyD{}
+	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
+	\lazyD{} Cast ADT.
 	\[
@@
 \begin{proof}
-	If we have a surely LazyD cast representation and it is a monoid, this 
+	If we have a surely LazyD Cast ADT and it is a monoid, this 
 	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
@@
 
-In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
-correct. First we define $ applyCast(v,c) $ to make it a cast representation, 
-then prove that it is surely lazyD, and finally apply 
+In this section we prove \lazyD\ hypercoercion is 
+correct. First we define $ applyCast(v,c) $ to make it an instance of Cast ADT, 
+then prove that it is also Lazy D, and finally apply 
 Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.
-
-%To use hypercoercion as a 
-%cast representation in our framework, we need to defined four functions: $ 
-%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
-%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
-%we 
-%define the $ applyCast(v,c) $  in
 
@@
 
-\begin{lemma}[\lazyD{} hypercoercion is Surely \lazyD]
+\begin{lemma}[\lazyD{} hypercoercion is a \lazyD Cast ADT]
 	\label{thm:hc-surely-lazyD}

### 2019-10-19 paper.tex
sec4 intro

@@
 all cast representation $ C $, if $ C $ satisfies a collection of properties, 
-then instantiating our parameterized space-efficient interpreter with $ C $ 
-gives an interpter that is extensionally equal to the standard interpreter for 
-\lazyD\ cast calculus. We are working on a similar theorem for \lazyUD{}.
+then it would respect the Lazy D semantics of cast calculi. We are working on a 
+similar theorem for \lazyUD{}.
+
+%then instantiating our parameterized space-efficient interpreter with $ C $ 
+%gives an interpter that is extensionally equal to the standard interpreter for 
+%\lazyD\ cast calculus.
 
@@
 To use our framework, users needs to prove that their cast representation 
-implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}).
-The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
-allows the framework to apply casts without referring to the actual definition 
-of $ applyCast(v,c) $. This 
-is because every casts at runtime is constructed by one of 
-the three cast constructors. 
-Property (1) handles casts constructed by $ id(T) $. 
-And property (2) handles $ seq(c,c) $, which says applying the 
-composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
-All remaining properties handles $ cast(T,l,T) $. They are effectively a 
-duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
-(Fig.~\ref{fig:applyCast-D-C}).
+implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}). To be a Lazy D 
+Cast ADT, $ id(T) $ must acts like the identity function. And $ seq(c,c) $ 
+must acts like a sequence of casts. What's more, $ cast(T_1,l,T_2) $ must act 
+like the Lazy D $ applyCast $ (Fig.~\ref{fig:applyCast-D-C}).
 
@@
 
+%Lazy D Cast ADT confines the behavior of operators so narrowly that it 
+%effectively allows us to ``run'' programs without referring to an actual 
+%representation of cast.
+
 If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
@@
 
-Some cast representations are also \textit{monoids}. They are useful in the 
-proof of our framework, and might be interesting elsewhere.
+Some cast representations are also \textit{monoids}. This definition is useful 
+in the proof of our framework, and might be interesting for other people.
 
@@
 In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of space-efficient semantics indexed by Cast ADTs ($ C $). 
+of space-efficient semantics indexed by Cast ADT ($ C $). When $ C $ is a Lazy 
+D Cast ADT, \effCEK{C} repects \ineffCEKD.
 In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
@@
 and only if $ \judgeSeval{C}{e}{o} $. In 
-subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
-the requirement that $ C $ must be a monoid, that is, every instance of Lazy D 
-Cast ADT is correct.
+subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
+a Lazy D Cast ADT, $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
+$.
 

### 2019-10-19 paper.tex
eval everywhere

@@
 \newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
-\newcommand{\judgeCeval}[2]{#1 \Downarrow_{\mathcal{C}} #2}
+\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
 \newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
@@
 \newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
-\newcommand{\judgeSeval}[3]{#2 \Downarrow_{\mathcal{S}(#1)} #3}
+\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
 \newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
@@
 \newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
-\newcommand{\judgeDeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
+\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) #2}
 \newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
+\newcommand{\evalEqv}[2]{$ eval_{\text{#1}} = eval_{\text{#2}} $}
 
@@
 Many of the existing research on coercions or threesomes include proof(s) of 
-correctness, that is, the cast calculus reduces to an observation ($ e 
-\Downarrow o $) if and only if their space-efficient calcului reduce to the 
-same observation ($ e \Downarrow_{*} o $), where an observation is either a 
-value constructor or 
-blame. 
+correctness, that is, the evaluation (partial) function of cast calculus $ eval 
+$ is equal to their space-efficient evaluation ($ eval_{*} $).
 Despite the striking similarity of these proofs, they are all built from ground 
@@
 
-\redrule{
-\sOOhalt{o}}{
-\sOOhalt{o}}{}
+%\redrule{
+%\sOOhalt{o}}{
+%\sOOhalt{o}}{}
 	\end{array}
@@
 The reflexive transitive closure of reduction ($ \judgeCreduceTrans{s}{s} $) 
-and evaluation ($ \judgeCeval{e}{o} $) are standard.
+and evaluation ($ eval_\mathcal{C}(e) $) are standard.
 
@@
 subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
-a Lazy D Cast ADT, $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
-$.
+a Lazy D Cast ADT, \evalEqv{\ineffCEKD}{\effCEK{C}}.
 
@@
 In this subsection, we prove that if a instance of Cast ADT $ C $ is Lazy D and 
-is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
-$. We proof this theorem with a weak bisimulation between \ineffCEKD\ and 
+is a monoid, then $ eval_\mathcal{D} = eval_{\mathcal{S}(C)} $. We proof this 
+theorem with a weak bisimulation between \ineffCEKD\ and 
 \effCEK{C}.
@@
 	\[
-	\judgeSeval{C}{e}{o}
-	 \; \text{if and only if} \; 
-	\judgeDeval{e}{o}
+	\text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
 	\]
@@
 In this subsection, we prove that for all $ C $, if $ C $ is a Lazy D Cast ADT, 
-then $ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first 
+then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
 prove that all $ S(C) $ where $ C $ is a Lazy D Cast ADT are equivalent, then 
@@
 	\[
-	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
-	e \Downarrow_{S(C_2)} o
+	eval_{S(C_1)} = eval_{S(C_2)}
 	\]
@@
 	\[
-	\judgeCeval{e}{o} \; \text{if and only if} \; 
-	\judgeSeval{C}{e}{o}
+	\text{\evalEqv{\ineffCEKD}{\effCEK{C}}}
 	\]
@@
 \begin{proof}
-	If we have a surely LazyD Cast ADT and it is a monoid, this 
+	If we have a Lazy D Cast ADT and it is a monoid, this 
 	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
@@
 	represent casts as a list of triples of type, label, and type, where $ 
-	id(T) $ is the empty list and $ seq(c,c,) $ is list append. Another such 
+	id(T) $ is the empty list and $ seq(c,c) $ is the list append. Another such 
 	representation is the \lazyD\ hypercoercion!
@@
 	\[
-	\judgeCeval{e}{o} \; \text{if and only if} \; 
-	\judgeSeval{H}{e}{o}
+	\text{\evalEqv{\ineffCEKD}{\effCEK{H}}}
 	\]

### 2019-10-19 paper.tex
abstract

@@
 \begin{abstract}
-\todoKC{rewrite this abstract based on the comparision table.}
-  Gradual Typing is great. Implementing gradually typed with blame
-  tracking and space efficiency is tricky. There exist two technique
-  to do this: coercion and threesome. Coercion is easy to understand,
-  and easy enough to implement, but difficult to reason about
-  formally. Threesome is hard to understand, easy to implement, and
-  easy to reason about formally. We propose hypercoercion, which is
-  easy to understand, as easy to implement as coercion, and easy to
-  reason about formally.
+	Designing a space-efficient cast representation that is good for both 
+	mechanized metatheory and implementation is challenging. Existing solution 
+	solutions have various strengths and weaknesses. We presents a new cast 
+	representation, named hypercoercions, that is good for both. On our way to 
+	prove the correctness of hypercoercions, we also step toward a framework 
+	for proving correctness of cast representations.
 \end{abstract}
@@
  three parts -JS
+ \\---\\
+ Fixed -KC
 }
@@
 This section presents our first contribution, the definition of hypercoercion. 
-The functions that construct hypercoercions are deferred to subsections because 
-they depend on blame strategies.
-And the functions that apply hypercoercions to values are deferred to 
-Section~\ref{sec:hypercoercion-correctness} because 
-they depends on a new definition of values, which is part of the framework in
-Section~\ref{sec:framework}.
+The design of hypercoercion is motivated by observations on coercion normal 
+forms: a normal coercion has at most three parts; projections are always at the 
+beginning; injections and failures are always at the end. Hypercoercions have 
+similar shape: a hypercion has either one part or three parts; for three-part 
+hypercoercions, the first part is either a projection or a no-op, while the 
+last part is either an injection, a failure, or a no-op.
 
@@
 failure.
-Let $ \ell $ range over no-op and labels. It is useful when we introduce 
-composition of hypercoercions.
+
+We define hypercoercion constructs in the following subsections.
+But functions that apply hypercoercions to values are deferred to 
+Section~\ref{sec:hypercoercion-correctness} because 
+they depends on a new definition of values, which is part of the framework in
+Section~\ref{sec:framework}.
 
@@
 
+Let $ \ell $ range over $ \epsilon $ and labels.
 $ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
@@
 \end{proposition}
-
-The correctness proof of \lazyD\ hypercoercion is deferred to 
-\secref{sec:LDHC-correct} 
-because it relies on the space-efficient CEK abstract machine in 
-\secref{sec:CEKS}.
 
@@
 \end{figure}
-\figref{machine-cekcc} defines, \effCEK{C}, a space-efficient semantics of cast 
-calculus in the style of CEK machines.
+\figref{machine-cekcc} defines, \effCEK{C}, a space-efficient semantics as a 
+CEK machine.
 This machine is similar to \ineffCEK{}. 
 The most important differences are in values and continuations.
+
+Let $ v $ range over value. 
 In \ineffCEK\, we have one value constructor for all casted value.
@@
 casts are identity (i.e. constructed by $ id(T) $).
+
+Cast results ($ r $) and machine states ($ s $) are as before.
+
+Let $ \kappa $ range over continuations and let $ k $ range over 
+pre-continuations. 
+A continuation is now a pre-continuation prefixed with a cast.
+Pre-continuation are like the continuations in \ineffCEK.
 In \ineffCEK\, a continuation have zero or more casts at the top.
@@
 seq(c,c) $.
-
-Let $ v $ range over value. A value is either the unit value, function, pair, 
-left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
-Cast results ($ r $) and machine states ($ s $) are as before. 
-Let $ \kappa $ range over continuations and let $ k $ range over 
-pre-continuations. 
-A continuation is now a pre-continuation prefixed with a cast.
-Pre-continuation are like the continuations in \ineffCEK.
 
@@
 
+\todo[inline]{Standardize theorem statement -KC}
 \begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
@@
 
+\todo[inline]{Standardize theorem statement -KC}
 \begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]

### 2019-10-19 paper.tex
removed fixed comments

@@
 
-\todo[inline]{What is the main idea behind the organization of
- hypercoercions? -JS
- \\---\\
- Are you asking why hc has three parts? Or why these subsections 
- in this section? -KC
- \\---\\
- three parts -JS
- \\---\\
- Fixed -KC
-}
-
 This section presents our first contribution, the definition of hypercoercion. 
@@
 
-\todo[inline]{Change ``Cast Representation'' to
-  ``Cast Abstract Data Type''. -JS
-\\---\\
-Fixed -KC}
-
 \begin{definition}[Cast Abstract Data Type (Cast ADT)]
@@
 \end{definition}
-
-\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS
-\\---\\
-Fixed -KC}
 

### 2019-10-19 paper.tex
minor fix
sec 4.0

@@
 \newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
-\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) #2}
+\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
 \newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
@@
 So we call them \textit{cast constructors}. And the forth and last operator 
-enable the implementation to use apply casts.
+enable the implementation to apply casts on values.
 
@@
 
+Some instances of Cast ADT (or "some Cast" for short) are also 
+\textit{monoids}. This definition is useful in the proof of 
+our framework, and might be interesting for other people.
+
+\begin{definition}[Monoid]
+	A Cast is a monoid if 
+	for all
+	$c_1 : T_1 \Longrightarrow T_2$,
+	$c_2 : T_2 \Longrightarrow T_3$, and
+	$c_3 : T_3 \Longrightarrow T_4$,
+	\begin{enumerate}
+		\item $seq(id(T_1),c_1) = c_1$,
+		\item $seq(c_1,id(T_2)) = c_1$, and
+		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
+	\end{enumerate}
+\end{definition}
+
 To use our framework, users needs to prove that their cast representation
-implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}). To be a Lazy D 
-Cast ADT, $ id(T) $ must acts like the identity function. And $ seq(c,c) $ 
-must acts like a sequence of casts. What's more, $ cast(T_1,l,T_2) $ must act 
-like the Lazy D $ applyCast $ (Fig.~\ref{fig:applyCast-D-C}).
+implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}). Property (1) 
+states that $ id(T) $ must acts like the identity function. Property (2) states 
+that $ seq(c,c) $ must acts like a sequence of casts. Properties (3) through 
+(11) state that $ cast(T_1,l,T_2) $ must act like the Lazy D $ applyCast $ 
+defined in Fig.~\ref{fig:applyCast-D-C}.
 
@@
 	\label{def:surely-lazyd}
-	A  Cast ADT is a Lazy D Cast ADT if:
+	A  Cast is a Lazy D Cast if:
 	\begin{enumerate}
@@
 		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
-		\item
+		\item If $ (\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2} $,
+		then\\
 		$ 
-		applyCast(\hcvOOfun{c_1}{\rho}{x}{b}{c_2}, 
+		applyCast(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}, 
 		cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
@@
 		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-
-		\item $ 
+		\item If $ (\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2} $,
+		then \\
+		$ 
 		applyCast(\hcvOOcons{v_1}{c_1}{v_2}{c_2},cast(\POOprod{T_1}{T_2},l,T_3 
@@
 		$ 
-		\item $ 
+		\item If $ (\hcvOOinl{v}{c}) : \POOsum{T_1}{T_2} $ ,
+		then \\
+		$ 
 		applyCast(\hcvOOinl{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
 		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
-		\item $ 
+		\item If $ (\hcvOOinr{v}{c}) : \POOsum{T_1}{T_2} $ ,
+		then \\ $ 
 		applyCast(\hcvOOinr{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
@@
 
-If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
-and be confident that this cast representation is valid.
-
-Some cast representations are also \textit{monoids}. This definition is useful 
-in the proof of our framework, and might be interesting for other people.
-
-\begin{definition}[Monoid]
-	A Cast ADT is a monoid if 
-	for all
-	$c_1 : T_1 \Longrightarrow T_2$,
-	$c_2 : T_2 \Longrightarrow T_3$, and
-	$c_3 : T_3 \Longrightarrow T_4$,
-	\begin{enumerate}
-		\item $seq(id(T_1),c_1) = c_1$,
-		\item $seq(c_1,id(T_2)) = c_1$, and
-		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
-	\end{enumerate}
-\end{definition}
-
-In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of space-efficient semantics indexed by Cast ADT ($ C $). When $ C $ is a Lazy 
-D Cast ADT, \effCEK{C} repects \ineffCEKD.
-In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
-a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
-and only if $ \judgeSeval{C}{e}{o} $. In 
-subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
-a Lazy D Cast ADT, \evalEqv{\ineffCEKD}{\effCEK{C}}.
+After showing their cast representation is a Lazy D Cast, users of our 
+frameworks can plug-in this cast representation to our space-efficient abstract 
+machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
+equivalent to \ineffCEKD subsection~\ref{secc:framework:all-correct}, which 
+depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
 

### 2019-10-19 paper.tex
revise text of 4.1

@@
 	}{}
-
 	\redrule{
@@
 machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
-equivalent to \ineffCEKD subsection~\ref{secc:framework:all-correct}, which 
+equivalent to \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which 
 depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
@@
 In \effCEK{C}, however, we do not have this generic value constructor, 
-instead we push those casts into the value constructors most of the time and 
-use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
-Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
-casts are identity (i.e. constructed by $ id(T) $).
+instead we push those casts into the ordinary values. For instance, $ 
+(\vOOcons{v_1}{v_2}) $ corresponds to $ 
+(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)}) $. To construct values of the 
+dynamic type, we use $ (\hcvOOinj{P}{v}) $.
 
@@
 A continuation is now a pre-continuation prefixed with a cast.
-Pre-continuation are like the continuations in \ineffCEK.
-In \ineffCEK\, a continuation have zero or more casts at the top.
+Pre-continuation are like the continuations in \ineffCEK, but there is no 
+constructor for casts.
+Continuations in \ineffCEKD\ have zero or more casts at the top.
 In \effCEK{C}, however, every continuation has exactly one cast at the top.
@@
 Transitive closure of reduction ($ \judgeSreduceTrans{C}{s}{s} $) and 
-evaluation are standard. Value typing ($ \judgeType{v}{T} $) is straightforward.
+evaluation ($ \judgeSeval{C}{e}{o} $) are standard. Value typing ($ 
+\judgeType{v}{T} $) is straightforward.
 

### 2019-10-19 paper.tex
edits to sec 2

--- 2019-10-19 paper.tex
@@
 \newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
-\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
+\newcommand{\cOOcast}[3]{#1 \Rightarrow^{#2} #3}
 \newcommand{\oOOinj}{\mathtt{dyn}}
@@
 \newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
+\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
 % blame calculus on space-efficient CEK
@@
 \newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
-\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) #2}
+\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
 \newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
 \newcommand{\evalEqv}[2]{$ eval_{\text{#1}} = eval_{\text{#2}} $}
+
+\newcommand{\highlight}[1]{{\color{red} #1}}
 
@@
 \begin{abstract}
-	Designing a space-efficient cast representation that is good for both 
-	mechanized metatheory and implementation is challenging. Existing solution 
-	solutions have various strengths and weaknesses. We presents a new cast 
-	representation, named hypercoercions, that is good for both. On our way to 
-	prove the correctness of hypercoercions, we also step toward a framework 
-	for proving correctness of cast representations.
+  Designing a space-efficient cast representation that is good for
+  both mechanized metatheory and implementation is
+  challenging. Existing solutions are good for one or the other. This
+  paper presents a new cast representation, named hypercoercions, that
+  is good for both. On the way to proving the correctness of
+  hypercoercions, this paper also makes progress on a general
+  framework for proving the correctness of cast representations.
 \end{abstract}
@@
 representations, with various strengths and weaknesses
-\citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}. This
-paper presents a new cast representation, named \emph{hypercoercions},
-that is good for both mechanized metatheory and good for
-implementation. Recall that it is the composition operator in these
-systems that enables space-efficiency by compressing casts.  The
-composition operator for hypercoercions is structurally recursive and
-hypercoercions are suggestive of a bit-level representation that
-minimizes the need for pointers and fits all first-order casts into 64
-bits.  Of course, an alternative cast representation must not change
-the result of programs. This paper presents steps toward a framework
-for proving the equivalence of cast calculi and, in particular, proves
-that an abstract machine using hypercoercions is equivalent to an
-abstract machine using standard casts.
-
-%
-%For example, translation to intermediate languages can wrap some expressions 
-%with casts, including expressions at tail positions. Thus, mutually 
-%tail-recursive functions in source language can consume unbounded space at 
-%runtime. There are more examples of space leaking in \citet{herman2010space}.
-
-The current state of the art regarding cast representations includes
+\citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}.
+The current state of the art includes
 \begin{itemize}
@@
 \end{itemize}
-Threesomes and supercoercions are good for mechanized metatheory
-because their compose operators are structurally recursive, making
-them easy to define in a proof assistant such as Agda. In contrast,
-the coercions in normal form have compose operators that are not
-structurally recursive, which makes it more difficult to define in
+Recall that in these systems, casts are compressed using a composition
+operator.  Threesomes and supercoercions are good for mechanized
+metatheory because their compose operators are structurally recursive,
+making them easy to define in a proof assistant such as Agda. In
+contrast, the coercions in normal form have compose operators that are
+not structurally recursive, which makes it more difficult to define in
 Agda, requiring what amounts to an explicit proof of termination.
@@
 than threesomes (with a strange labelled bottom type), and
-supercoercions (with 10 different kinds).
-
-%% There are two best studied ways to represent cast space-efficiently:
-%% coercions
-%% \citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations}
-%% \citep{siek2015blame} and threesomes
-%% \citep{siek2010threesomes}\citep{garcia2013calculating}. They have
-%% different strength and weakness. \citet{garcia2013calculating} and
-%% \citet{siek2015blame} claim that coercion is easy to understand, but
-%% hard to implement, while threesome is easy to implement, but hard to
-%% understand. \citet{garcia2013calculating} in addition claims that
-%% coercion is more difficult to reason about formally because its
-%% compose function is not structurally recurisive. For instance, the
-%% developers of Grift \citep{kuhlenschmidt2018efficient} report that it
-%% is tricky to convince their proof assistants that the compose function
-%% terminates.
-
-We present a new cast representation, hypercoercion, which has a structurally 
-recursive composition. When we prove theorems about hypercoercion in Agda, the 
-definition ``just works''. 
-Besides, We believe hypercoercion is about as easy to understand as coercion 
-because their syntax definitions are similar. For instance, the 
-coercion approach represents $ 
-\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
-?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
-\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
-coercion together with cast calculus 
-\citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
-present hypercoerion in Section~\ref{sec:hypercoercion-definition}.
-
-Another strength of hypercoercion over coercion is that hypercoercion might 
-have a more compact memory representations. In Grift 
-\citep{kuhlenschmidt2018efficient}, the longest coercions are represented with
-two cons boxes. But for hypercoercion, we are optimistic that one cons box 
-suffices. Using less cons boxes saves memory as well as running time.
-\todo[inline]{
-	Could Jeremy help explain explaining why hypercoercion is more compact in 
-	memory?
-	Cons boxes seem to be non-standard, but I don't know a better name.
- -KC}
-
-Many of the existing research on coercions or threesomes include proof(s) of 
-correctness, that is, the evaluation (partial) function of cast calculus $ eval 
-$ is equal to their space-efficient evaluation ($ eval_{*} $).
-Despite the striking similarity of these proofs, they are all built from ground 
-up.
-
-We present a framework for proving correctness of cast reprensentation 
-(Section~\ref{sec:framework}), and use it to prove the correctness of 
-hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
-that this framework is general enough to include coercion and threesome.
-
-%Some readers might know that there are four blame strategies: $ \{Lazy, 
-%Eager\} 
-%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
-%potential type errors, but 
-%blame more programs. $ D $ and $ UD $ assign blame labels differently.
-
-We focus on lazy cast strategies because we suspect that they are more
-efficient that eager strategies, which is why lazy was chosen in the
-Grift compiler \citep{Kuhlenschmidt:2019aa}, and because
-\citet{new2019gradual} show that eager strategies are incompatible
-with $\eta$-equivalence of functions. We are interested in the D blame
-tracking strategy because it has a more straightforward notion safe
-cast compared to UD \citep{siek2009exploring}, which is why D was
-chosen Grift compiler. However, we are also intersted in UD because it
-plays a prominent role in the gradual typing literature
-\citep{wadler2009well}.
-
-The primary contributions of this paper are:
+supercoercions (10 different kinds).
+
+This paper presents a new cast representation, named
+\emph{hypercoercions}, that is good for both mechanized metatheory and
+good for implementation. The composition operator for hypercoercions
+is defined by structural recursion and hypercoercions are suggestive
+of a bit-level representation that minimizes the need for pointers and
+fits all first-order casts into 64 bits. We present two flavors of
+hypercoercions to support the two blame tracking strategies from the
+literature: D and UD~\citep{siek2009exploring}. We are interested in
+the D blame tracking strategy because it comes with a more
+straightforward notion safe cast compared to
+UD~\citep{siek2009exploring}, which is why D was chosen Grift
+compiler. We are also intersted in UD because it plays a prominent
+role in the gradual typing literature \citep{wadler2009well}. The
+semantics of casts can also be lazy or
+eager~\citep{siek2009exploring}. In this paper we focus on lazy cast
+strategies because we suspect that they are more efficient than eager
+strategies and because \citet{new2019gradual} show that eager
+strategies are incompatible with $\eta$-equivalence of functions.
+
+Of course, an alternative cast representation must be proved
+correct. This paper presents steps toward a general framework for
+proving equivalence of cast calculi and, in particular, proves that an
+abstract machine using \lazyD{} hypercoercions is equivalent to an
+abstract machine using standard \lazyD{}
+casts~\citep{siek2009exploring}. We conjecture that the framework can
+be generalized to \lazyUD{} and that it can be applied to coercions in
+normal form and threesomes.
+
+To summarize, the primary contributions of this paper are:
 \begin{itemize}
@@
   representation.
-\item a framework in Agda for proving correctness of cast
-  represantations.  We conjecture that both coercion and
-  threesome can fit into this framework.
+\item a framework in Agda for proving the correctness of cast
+  represantations.
 \item a formal proof that hypercoercion respects the semantics
@@
 
-%Around 2006, many work on integrating dynamic typing and static typing emerge, 
-%notably gradual types \citep{siek2006gradual} and hybrid types 
-%\citep{flanagan2006hybrid}. 
-%Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
-%language for gradual types and hybrid types. 
-%Blame Calculus throws a blame label when a runtime type-check fails.
-%Labels provide useful debugging information, therefore are necessary for 
-%practical use of gradually typed languages.
-%
-%Implementing gradually typed languages naively on top of blame calculus, 
-%however, suffices sever space leak.
-%For example, translation to Blame Calculus can wrap some expressions with code 
-%that performs runtime type-checking (casts), including expressions at 
-%tail positions. Thus, mutually tail-recursive functions in source language can 
-%consume unbounded space at runtime. There are more examples of space leaking 
-%in 
-%\citet{herman2010space}.
-%
-%In 2007, \citet{herman2010space} proposes a solution to this problem by 
-%representing casts with coercion \citep{henglein1994dynamic}, 
-%which can be composed and normalized. Every coercion looks like a list of 
-%trees. For normal coercion, the length of the list is bounded by a small 
-%constant. And the depths of trees do not grow during composition and
-%normalization. These two facts implies that coercion is a space-efficient cast 
-%representation. This coercion, however, does not support blame 
-%tracking. 
-%
-%After that, many efforts have been made to combine blame tracking and 
-%space efficiency. 
-%
-%\citet{siek2009exploring} present another intermediate langauge for gradually 
-%typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
-%and space-efficiency for this language by decorating \citet{herman2010space}'s 
-%coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
-%with the dynamic type and cast expressions. The labels in \castCalculus{}, 
-%unlike their counterparts in the Blame Calculus, have no polarity. 
-%They also propose that there are four blame strategies for \castCalculus{}:
-%$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
-%type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
-%differently. They claim that their \lazyUD\ cast calculus is the same as the 
-%Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
-%coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
-%however, whether the simulation in the other direction also works.
-%\todo[inline]{Is it important to this paper whether there is a
-%simulation in the other direction? -JS
-%\\ --- \\
-%I guessed to say coercion is correct the other direction is 
-%necessary. -KC}
-%
-%\citet{siek2010threesomes} proposes another approach to combine blame 
-%tracking and space efficiency. Their solution represents casts with 
-%threesomes, 
-%a novel cast representation. Threesome is proved space-efficient as well.
-%They prove that their calculus bisimulates the \lazyUD{} coercion 
-%calculus in \citet{siek2009exploring} and the Blame Calculus in 
-%\citet{wadler2009well}.
-%
-%\citet{siek2012interpretations} present a revised coercion calculi.
-%They simplify the coercion calculi by only 
-%working with normal coercions (i.e. coercions in normal form). 
-%They conjecture that their revised coercion calculi bisimulate the 
-%corresponding cast calculi.
-%
-%\citet{garcia2013calculating} develops
-%threesome for other blame strategies. After studying in depth the connection 
-%between coercion and threesome,
-%he claims that normal coercion with labels is easy to understand but hard to 
-%implement and hard to reason about, and that 
-%threesome with labels, however, is easy to implement and easy to reason about 
-%but hard to understand. 
-%His claim is mostly affirmed by the group of people who develop threesome 
-%(\citet{siek2015blame}).
-%His threesome calculi are equivalent to the coercion calculi of
-%\citet{siek2009exploring} because the former ones are derived from the latter 
-%ones.
-%
-%\citet{siek2015blame} revisit the coercion-based approach. They revise
-%the \lazyUD{} coercion in \citet{siek2012interpretations} and prove
-%that their revised coercion calculus bisimulates the \lazyUD{} Blame
-%Calculus \citet{wadler2009well}.
-%
-%Last year, \citet{kuhlenschmidt2018efficient} present Grift, a compiler for a 
-%gradually typed language of the same name. 
-%This implementation is based on the \lazyD{} coercion in 
-%\citet{siek2012interpretations}.
-%Their result suggests that normal coercion is easy enough to implement in a 
-%compiler. 
-%
-%So far, it seems that normal coercion is the best way to combine 
-%space-efficiency and blame-tracking: normal coercion is claimed easy to 
-%understand \citep{garcia2013calculating}\citep{siek2015blame} and is shown 
-%easy enough to implement in a compiler \citep{kuhlenschmidt2018efficient}.
-%Normal coercion is still not satisfactory, however, in at least two aspects.
-%Firstly, as we mentioned above, it is hard to reason about normal coercion. 
-%The 
-%major difficulty is from its non-structurally recursive composition.
-%For instance, the developers of Grift report it is tricky to convince
-%their proof assistants that the composition terminates.
-%
-%Secondly, the definition of normal coercion lies unnecessarily on top 
-%of coercion: all coercions are normal when they are initially constructed, and 
-%\citet{siek2012interpretations} have shown an function that 
-%composes and produces normal coercions.
-%%
-%\todo[inline]{Many researchers would view this as a positive thing,
-%  not a negative. For example, the notion of normal forms comes up
-%  over and over again in mathematics and logic. -JS
-%\\ --- \\
-%I guess having a notion of normal forms is more convenient when a 
-%notion of normalization is convenient. But we don't even need a notion of 
-%normalization for cast representations. -KC
-%\\ --- \\
-%FWIW, I agree with you. But the point is that the argument is not
-%likely to be convincing to the reader, so we're probably better off
-%not wasting space on it. -JS
-%}
-%
-%Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
-%self-standing definition. Together with \citet{garcia2013calculating}'s 
-%work, they suggest that there might be a cast representation whose definition 
-%is self-standing, and whose composition is structurally recursive. 
-%supercoercion introduced in \citet{garcia2013calculating} could be a promising 
-%candidate. It is believed even more complicated than threesome 
-%\citep{siek2015blame}. In fact, it uses 10 constructors to deal with an 
-%elementary type system with only base types and 
-%function types. And four constructors are directly related to function types. 
-%Thus, supercoercion might not scale very well to more sophisticated type 
-%systems. 
-%
-%We present hypercoercion, a cast representation whose composition is 
-%structurally recursive, and whose definition is self-standing. What's more, it 
-%should be at 
-%least as easy to implement and understand as normal coercions, because there 
-%is 
-%a clear connection between them, as we will show in Section 
-%\ref{sec:hypercoercion}.
-%Our hypercoercion considers sum types and product types, which are not 
-%considered in all proofs above. Adding each of them requires us to add only 
-%one 
-%new constructor to a component of hypercoercion. This suggests that 
-%hypercoercion might scale better than supercoercion.
-%
-%We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
-%bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
-%the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
-%We care more about lazy strategies because recently, \citet{new2019gradual} 
-%show that \eager{} strategies are incompatible with $\eta$-equivalence of 
-%functions, which suggest that these strategies are not very ideal. 
-%\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -JS
-%  \\ --- \\ Explained, not sure if it suffice. -KC
-%  \\ --- \\
-%  That's good that you explained why lazy instead of eager.
-%  (Also, you should add that we are interested in lazy because
-%  that's what Grift does.)\\
-%  But you haven't explained why we are interested in both D and UD. -JS
-%}
-%
-%The structure of this paper is as follows. 
-%Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ cast 
-%calculi. 
-%Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ 
-%Coercion 
-%Calculi. 
-%In section \ref{sec:hypercoercion} we present hypercoercion.
-%Section \ref{sec:conclude} concludes.
-%\todo[inline]{Lots of missing sections. -JS}
+In Section~\ref{sec:background} we review cast calculi and coercions.
+We present hypercoercions in
+Section~\ref{sec:hypercoercion-definition}.  We present a framework
+for proving correctness of cast reprensentations in
+Section~\ref{sec:framework} and use it to prove the correctness of
+\lazyD{} hypercoercions in
+Section~\ref{sec:hypercoercion-correctness}.
 
@@
 
-In this section, we review lazy cast calculi (\ref{sec:cast-calculi}) and
-normal coercion (\ref{sec:coercion-calculus}).
+In this section, we review lazy cast calculi
+(Section~\ref{sec:cast-calculi}) and coercion in normal form
+(Section~\ref{sec:coercion-calculus}).
 
@@
 \label{sec:cast-calculi}
+
 \begin{figure}
@@
 		\eOOblame{l}
-	}
-	\stxrule{v}{values}{
-		\vOOtt{} \mid
-		\vOOfun{\rho}{x}{e} \mid
-		\vOOcons{v_1}{v_2} \mid
-		\vOOinl{v} \mid
-		\vOOinr{v} \mid		
-		\vOOcast{v}{c}
-	}
-	\stxrule{c}{casts}{
-		\cOOcast{T_1}{l}{T_2}
-	}
-	\stxrule{I}{injectable types (\lazyD)}{
-		P
-	}
-	\stxrule{I}{injectable types (\lazyUD)}{
-		\POOunit \mid
-		\POOfun{\star}{\star} \mid
-		\star \times \star \mid
-		\star + \star
-	}
-	\stxrule{o}{observations}{
-		\oOOinj \mid
-		\oOOsole \mid
-		\oOOfun \mid
-		\oOOcons \mid
-		\oOOinl \mid
-		\oOOinr \mid
-		\oOOblame{l}
 	}
@@
 		P \sim \star
-	} \\
+	} \\[1ex]
 	\inference{}{
@@
 	\end{gather*}
+
+	Term typing
+	\fbox{$ \judgetype{\Gamma}{e}{T} $}
+	\begin{gather*}
+          \dots \qquad
+		\inference{
+			\Gamma \vdash e : T_1 & T_1 \sim T_2
+		}{
+			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
+		} \quad
+		\inference{
+		}{
+			\judgetype{\Gamma}{\eOOblame{l}}{T}
+		}
+	\end{gather*}
+
+	\caption{Syntax and static semantics of the cast calculi.}
+	\label{fig:blame-static}
+\end{figure}
+
+\paragraph{Syntax and Static Semantics}
+
+The syntax and static semantics is the same for the \lazyD{} and
+\lazyUD{} cast calculi, and is reviewed in \figref{fig:blame-static}.
+As usual, the important features are the cast expressions,
+$\eOOcast{e}{T_1}{l}{T_2}$, which are responsible for runtime type
+checking, and blame expressions, $\eOOblame{l}$, that raise errors.
+The syntax and static semantics is the same that of
+\citet{siek2009exploring} except for a few minor exceptions:
+\begin{itemize}
+\item We add sum, product, and unit types.
+\item We separate types into those with a type constructor at the top,
+  the \emph{pretypes} ($\POOunit$, functions, products, and sums),
+  versus the dynamic type $\star$ (a.k.a. $ \mathtt{Dyn} $ or
+  $\mathbb{?}$).
+\item We annotate the codomain of a lambda abstraction explicitly
+  because we refer to it in the dynamic semantics. 
+\end{itemize}
+As usual, the source $T_1$ and target types $T_2$ of a cast
+$\eOOcast{e}{T_1}{l}{T_2}$ are required to be consistent, written $T_1
+\sim T_2$. The consistency relation is standard and defined in
+\figref{fig:blame-static}.
+
+%% defines the syntax of the cast calculus and
+%% its static semantics. We extend the syntax of
+%%  with sum and product types.  Let $ T $ range
+%% over types. A type is either the dynamic type $ \star $ (a.k.a. $
+%% \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), or a type
+
+%% As usual we write $ T_1 \sim T_2 $ when $ T_1 $ and $ T_2 $ are
+%% consistent. The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $
+%% T_2 $ have no conflicting type information. Two types are consistent
+%% if one of them is $ \star $, or they have the same top-most type
+%% constructor and the corresponding sub-parts are
+%% consistent. Consistency is reflexive and symmetric, but not
+%% transitive.
+
+%% We write $ T_1 \smile T_2 $ when $ T_1 $ and $ T_2 $ are
+%% shallowly-consistent, that is, if one of them is $ \star $, or they
+%% have the same type constructor at the top. Shallow-inconsistency is
+%% the root of all blame in lazy cast strategies -- casting a value to a
+%% shallowly inconsistent type leads to a blame. Shallow-consistency is
+%% reflexive, symmetric, but not transitive.
+
+%% Let $ e $ range over terms. Most terms are standard for a simply-typed
+%% lambda calculus. We annotate the codomain of a lambda abstraction
+%% explicitly because we refer to it in the dynamic semantics. Becuase
+%% this is a cast calculus, we have two additional terms: cast
+%% expressions and blame expressions. Cast expressions perform runtime
+%% type checks and blame expressions raise an error.
+
+\paragraph{Dynamic Semantics}
+
+The dynamic semantics of a cast calculus is typically defined with a
+reduction semantics. Here we use a CEK machine
+\citep{felleisen1986control} instead because the first author is more
+familiar with CEK machines and believes that a CEK machine is more
+convenient to use for the space-efficient semantics in
+Section~\ref{sec:framework:cek} (space-efficiency is about compressing
+continuations). So using an abstract machine for the cast calculi in
+this section makes it easier prove correctness of the space-efficient
+machines. Of course, one should prove that the abstract machine
+presented here is equivalent to the standard reduction semantics for
+cast calculi, but we have not yet done so.
+
+Fig.~\ref{fig:machine-cekc} defines the transition relation of the CEK
+machine and Fig.~\ref{fig:state} gives a grammar for machine states
+$s$, including a definition of values and value typing. The
+transitions involving casts are highlighted in red and described in
+more detail below. The other transitions are standard for a CEK
+machine for an extended simply typed lambda calculus.
+%
+Recall that CEK machine involves two kinds of transitions, (1) those
+that dive further into an expression (looking for a redex) and push an
+entry onto the continuation, and (2) those that return a value to the
+current continuation and possibly perform a computation.
+Corresponding to (1) and (2), the machine state is either in an
+$\mathtt{Eval}$ or $\mathtt{Cont}$ configuration, respectively.
+Additionally, there is the $\mathtt{Halt}$ configuration.
+
+The transition relation $\judgeCreduce{s}{s}$ is parameterized over
+$applyCast$ to allow for the differences between D and UD.
+%
+When evaluating a cast expression, the machine moves the cast to the
+continuation and evaluates the inner expression.
+%% Other
+%% transition rules starting from $ Eval $ states are standard.
+To apply a casted function, the machine first casts $ v_1 $, the
+operand, then applies the casted operand to $ v_2 $, the underlying
+function, and finally cast the result of the function application.
+%
+To take out the first (resp. second) part of a casted pair, the
+machine firstly take out the first (resp. second) part of $ v $, the
+underlying pair, and cast the result.
+%
+In case splitting, if the target value is a left injection, the
+machine moves to a state that will apply the first continuation
+function to the value inside the left injection. The case for right
+injection is similar.
+%
+When the target value is a casted sum, the machine moves the cast from
+the target value to continuations functions.
+%
+To cast a value, the machine invokes $applyCast$ on the value.  If the
+cast succeeds, the machine returns the result to the next
+continuation.  If the cast fails, the machine halts with the blame
+label.
+%
+%% When the continuation is $ stop $, the machine enters a halting
+%% state. The When the machine is in a halting state, it stays in the
+%% same state.
+
+The reflexive transitive closure of reduction ($
+\judgeCreduceTrans{s}{s} $) and evaluation ($ eval_\mathcal{C}(e) $)
+are standard~\citep{felleisen03:_pllc}.
+
+\begin{figure}
+  Machine state and other runtime data structures
+  \[
+  \begin{array}{rclr}
+	\stxrule{v}{values}{
+		\vOOtt{} \mid
+		\vOOfun{\rho}{x}{e} \mid
+		\vOOcons{v_1}{v_2} \mid
+		\vOOinl{v} \mid
+		\vOOinr{v} \mid		
+		\vOOcast{v}{c}
+	}
+	\stxrule{c}{casts}{
+		\cOOcast{T_1}{l}{T_2}
+	}
+	\stxrule{I}{injectable types (\lazyD)}{
+		P
+	}
+	\stxrule{I}{injectable types (\lazyUD)}{
+		\POOunit \mid
+		\POOfun{\star}{\star} \mid
+		\star \times \star \mid
+		\star + \star
+	}
+	\stxrule{o}{observations}{
+		\oOOinj \mid
+		\oOOsole \mid
+		\oOOfun \mid
+		\oOOcons \mid
+		\oOOinl \mid
+		\oOOinr \mid
+		\oOOblame{l}
+	}
+	\stxrule{r}{cast results}{
+		\rOOsucc{v} \mid
+		\rOOfail{l}
+	}
+	\stxrule{s}{states}{
+		\sOOinspect{e}{\rho}{\kappa} \mid{}
+		\sOOreturn{v}{\kappa} \mid{}
+		\sOOhalt{o}
+	}
+	\stxrule{\kappa}{continuations}{
+		\kOOmt \mid
+		\kOOconsI{e}{\rho}{\kappa} \mid
+		\kOOconsII{v}{\kappa} \mid
+		\kOOinl{\kappa} \mid
+		\kOOinr{\kappa}
+	}
+	\stxrulecont{
+		\kOOappI{e}{\rho}{\kappa} \mid
+		\kOOappII{v}{\kappa} \mid
+		\kOOcar{\kappa} \mid
+		\kOOcdr{\kappa} \mid
+		\kOOcaseI{e_1}{e_2}{\rho}{\kappa}
+	}
+	\stxrulecont{	
+		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
+		\kOOcaseIII{v_1}{v_2}{\kappa} \mid
+		\kOOcast{c}{\kappa}
+	}
+  \end{array}
+  \]
 
@@
 
-	Term typing
-	\fbox{$ \judgetype{\Gamma}{e}{T} $}
-	\begin{gather*}
-		\inference{
-			\Gamma \vdash e : T_1 & T_1 \sim T_2
-		}{
-			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
-		} \quad
-		\inference{
-		}{
-			\judgetype{\Gamma}{\eOOblame{l}}{T}
-		}
-	\end{gather*}
-
 	Value typing \fbox{$ v : T $}
 	\begin{gather*}
-	\dots \quad
+	\dots \qquad
 	\inference{
@@
 	\end{gather*}
-
-	\caption{Syntax and static semantics of the cast calculi.}
-	\label{fig:blame-static}
+        \caption{Definition of machine state and auxilliary data
+          structures.}
+        \label{fig:state}
 \end{figure}
-
-\figref{fig:blame-static} defines the syntax of cast calculi and its
-static semantics. We extend the syntax of \citet{siek2009exploring}
-with sum and product types.  Let $ T $ range over types. A type is
-either the dynamic type $ \star $ (a.k.a. $ \mathtt{Dyn} $, $
-\mathbb{?} $, or $ \mathtt{Unknown} $), or a type with a type
-constructor at the top, that is, a pre-type, ranged over by $ P $. We
-include just one base type, $\POOunit$. The other pre-types are
-functions, products, and sums.
-
-As usual we write $ T_1 \sim T_2 $ when $ T_1 $ and $ T_2 $ are
-consistent. The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $
-T_2 $ have no conflicting type information. Two types are consistent
-if one of them is $ \star $, or they have the same top-most type
-constructor and the corresponding sub-parts are
-consistent. Consistency is reflexive and symmetric, but not
-transitive.
-
-We write $ T_1 \smile T_2 $ when $ T_1 $ and $ T_2 $ are
-shallowly-consistent, that is, if one of them is $ \star $, or they
-have the same type constructor at the top. Shallow-inconsistency is
-the root of all blame in lazy cast strategies -- casting a value to a
-shallowly inconsistent type leads to a blame. Shallow-consistency is
-reflexive, symmetric, but not transitive.
-
-Let $ e $ range over terms. Most terms are standard for a simply-typed
-lambda calculus. We annotate the codomain of a lambda abstraction
-explicitly because we refer to it in the dynamic semantics. Becuase
-this is a cast calculus, we have two additional terms: cast
-expressions and blame expressions. Cast expressions perform runtime
-type checks and blame expressions raise an error.
 
@@
 
-	Syntax
-	\[
-	\begin{array}{rclr}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
-
-	\stxrule{\kappa}{continuations}{
-		\kOOmt \mid
-		\kOOconsI{e}{\rho}{\kappa} \mid
-		\kOOconsII{v}{\kappa} \mid
-		\kOOinl{\kappa} \mid
-		\kOOinr{\kappa}
-	}
-	\stxrulecont{
-		\kOOappI{e}{\rho}{\kappa} \mid
-		\kOOappII{v}{\kappa} \mid
-		\kOOcar{\kappa} \mid
-		\kOOcdr{\kappa} \mid
-		\kOOcaseI{e_1}{e_2}{\rho}{\kappa}
-	}
-	\stxrulecont{	
-		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
-		\kOOcaseIII{v_1}{v_2}{\kappa} \mid
-		\kOOcast{c}{\kappa}
-	}
+	\[
+	\begin{array}{rclr}
 	\end{array}
@@
 	\begin{array}{rclr}
-		\redrule{
+		\hiredrule{
 		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
@@
 	}{	
-		\sOOreturn{\rho[x]}{\kappa}
+		\sOOreturn{\rho(x)}{\kappa}
 	}{}
@@
 	}{
-		\sOOinspect{e_1}{E}{}
+		\sOOinspect{e_1}{\rho}{(\kOOconsI{e_2}{\rho}{\kappa})}
 	}{}
@@
 \sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
-	\redrule{
+	\hiredrule{
 		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
@@
 	}{}
-	\redrule{
+	\hiredrule{
 		\sOOreturn{
@@
 
-	\redrule{
+	\hiredrule{
 		\sOOreturn{
@@
 \redrule{
-	\sOOreturn{v_3}{(\mathtt{case_3}\;
+	\highlight{\sOOreturn{v_3}{(\mathtt{case_3}\;
 		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
-		\;v_2\;\kappa)}
-}{
-	\sOOreturn{v_3'}{
+		\;v_2\;\kappa)}}
+}{
+	\highlight{\sOOreturn{v_3'}{
 		(\mathtt{case_3}\;v
 		\;v_2'\;\kappa)
-	}
+	}}
 }{\\&&
-\text{where}\;
-v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}
+\highlight{\text{where}\;
+v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
 \\&&
-\text{and}\;
-v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}
+\highlight{\text{and}\;
+v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
 }
@@
 	\redrule{
-		\sOOreturn{v}{(
+		\highlight{\sOOreturn{v}{(
 			\mathtt{cast} \; c \; \kappa
-			)}
-	}{
+			)}}
+	}{
+\highlight{          
 \begin{cases}
@@
 	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
-\end{cases}
+\end{cases}}
 	}{}
@@
 \sOOhalt{observe(v)}}{}
-
-%\redrule{
-%\sOOhalt{o}}{
-%\sOOhalt{o}}{}
-	\end{array}
-	\]	
-%	
-%	\fbox{$case(v, \kappa, \kappa) = s$}
-%	\[
-%	\begin{array}{rclr}
-%	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
-%		\sOOreturn{v}{\kappa_1}
-%	}{}
-%	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
-%		\sOOreturn{v}{\kappa_2}
-%	}{}
-%	
-%\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
-%		case(v,
-%		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
-%		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
-%	}{}
-%	\end{array}
-%	\]
-
-	%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s 
-	%$}\\
+	\end{array}
+	\]
 
@@
 
-	\caption{Dynamic semantics of the cast calculi as a CEK machine}
-	\label{machine-cekc}
+	\caption{Dynamic semantics of the cast calculi as a CEK
+          machine. The transitions that involve casts are highlighted
+          in red.}
+	\label{fig:machine-cekc}
 \end{figure}
 
-Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
-CEK machine \citep{felleisen1986control}. CEK machines include continuation as 
-part of their states. They evaluate expressions with two interleaving 
-processes: 
-(1) dive into an expression and extend the continuation;
-(2) return a value to the current continuation.
-
-Most existing proofs about cast calculi defines the dynamic semantics with 
-reduction semantics. We use a CEK machine instead because the first author is 
-more familiar with CEK machines, and that he believes CEK machines are more 
-convenient because space-efficiency is about compressing continuations.
+\todo[inline]{There are missing transition rules for fst and snd. -JS}
 
@@
 
-The reduction relation $ \judgeCreduce{s}{s} $ is parameterized over $ 
-applyCast $. 
-When evaluating a cast expression, the machine moves the cast to the 
-continuation and evaluate the inner expression.
-Other transition rules starting from $ Eval $ states are standard.
-To apply a casted 
-function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
-operand to $ v_2 $, the un-casted function, and finally cast the result of the 
-function application. To take out the first (resp. second) part of a casted 
-pair, the machine firstly take out the first (resp. second) part of $ v $, the 
-un-casted pair, and cast the result. In case spliting, if the target value is a 
-left injection, the machine moves to a state that will apply the first 
-continuation function to the value inside the left injection. The case for 
-right injection is similar. When the target value is a casted sum, the machine 
-moves the cast from the target value to continuations functions. 
-%Along the way, the machine accumulates the pending casts onto the 
-%continuations. 
-To cast a value, the machine try to apply the cast to the value. 
-If the cast succeeds, the machine returns the result to the next continuation. 
-If the cast fails, the machine halts with the blame label.
-When the continuation is $ stop $, the machine enters a halting state. The 
-When the machine is in a halting state, it stays in the same state.
-
-The reflexive transitive closure of reduction ($ \judgeCreduceTrans{s}{s} $) 
-and evaluation ($ eval_\mathcal{C}(e) $) are standard.
-
 \subsection{The \lazyD{} cast calculus}
@@
 We conjecture that with this $ applyCast $, the CEK machine in 
-\figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
+\figref{fig:machine-cekc} would agree with the \lazyD{} cast calculus in 
 \citet{siek2009exploring}. We denote this \lazyD{} machine by \ineffCEKD{},
@@
 
+\todo[inline]{I need to update this subsection. -JS}
+
 The dynamic semantics of the \lazyUD{} cast calculus, which we define here as a
 CEK machine, is similar to that of the \lazyD{} cast calculus
-(Fig. \ref{machine-cekc}). The only difference is in the definition of
+(Fig. \ref{fig:machine-cekc}). The only difference is in the definition of
 the $\mathit{applyCast}$ function, in which a cast whose source or
@@
 
-In this section we review the normal coercions \citep{siek2012interpretations} 
-to motivate the design of hypercoercion. 
-We ignore sum types and product types in this 
-section, because they were not in the paper. We assume a basic 
-familiarity with coercion, and direct readers who do not know it to 
-\citet{siek2012interpretations}.
+In this section we review the coercions in normal form of
+\citet{siek2012interpretations} to motivate the design of
+hypercoercions.  We ignore sum types and product types in this
+section, because \citet{siek2012interpretations} did not discuss
+them. We assume a basic familiarity with coercions and direct readers
+who are not familiar with them to \citet{siek2012interpretations}.
 %We 
@@
 \subsection{A Space-efficient CEK machine}
-\label{ssec:framework:cek}
+\label{sec:framework:cek}
 
@@
 	\caption{Space-efficient CEK machine $ \mathcal{S}(C) $}
-	\label{machine-cekcc}
+	\label{fig:machine-cekcc}
 \end{figure}
-\figref{machine-cekcc} defines, \effCEK{C}, a space-efficient semantics as a 
-CEK machine.
-This machine is similar to \ineffCEK{}. 
+\figref{fig:machine-cekcc} defines, \effCEK{C}, a space-efficient
+semantics as a CEK machine.  This machine is similar to \ineffCEK{}.
 The most important differences are in values and continuations.

### 2019-10-19 paper.tex

@@
 
-If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
-and be confident that this cast representation is valid.
-
-Some cast representations are also \textit{monoids}. This definition is useful 
-in the proof of our framework, and might be interesting for other people.
-
-\begin{definition}[Monoid]
-	A Cast ADT is a monoid if 
-	for all
-	$c_1 : T_1 \Longrightarrow T_2$,
-	$c_2 : T_2 \Longrightarrow T_3$, and
-	$c_3 : T_3 \Longrightarrow T_4$,
-	\begin{enumerate}
-		\item $seq(id(T_1),c_1) = c_1$,
-		\item $seq(c_1,id(T_2)) = c_1$, and
-		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
-	\end{enumerate}
-\end{definition}
-
-In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
-of space-efficient semantics indexed by Cast ADT ($ C $). When $ C $ is a Lazy 
-D Cast ADT, \effCEK{C} repects \ineffCEKD.
-In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
-a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
-and only if $ \judgeSeval{C}{e}{o} $. In 
-subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
-a Lazy D Cast ADT, \evalEqv{\ineffCEKD}{\effCEK{C}}.
+After showing their cast representation is a Lazy D Cast, users of our 
+frameworks can plug-in this cast representation to our space-efficient abstract 
+machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
+equivalent to \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which 
+depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
 

### 2019-10-20 paper.tex
reduction rules for S(C)
remove label of succ/fail
filled in missing rules in S(C)
highlight S(C) rules
minor fix
minor change

@@
 \newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
+\newcommand{\hifunrule}[3]{\highlight{#1} &\highlight{=}& \highlight{#2} & 
+\highlight{#3}\\}
 \newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
@@
 \newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
-\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
-\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
+\newcommand{\rOOsucc}[1]{#1}
+\newcommand{\rOOfail}[1]{#1}
+%\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
+%\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
 \newcommand{\kOOmt}[0]{\mathtt{stop}}
@@
 \newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
+\newcommand{\hiredruleS}[3]{\highlight{#1} & 
+\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
 % Normal Coercion
@@
 \newcommand{\evalEqv}[2]{$ eval_{\text{#1}} = eval_{\text{#2}} $}
-
+\newcommand{\continue}[2]{continue(#2,#1)}
 \newcommand{\highlight}[1]{{\color{red} #1}}
@@
 convenient to use for the space-efficient semantics in
-Section~\ref{sec:framework:cek} (space-efficiency is about compressing
-continuations). So using an abstract machine for the cast calculi in
+Section~\ref{sec:framework:cek} (a major point of space-efficiency is about 
+compressing continuations). So using an abstract machine for the cast calculi in
 this section makes it easier prove correctness of the space-efficient
@@
 	}{}
+	\redrule{
+	\sOOreturn{
+		(\vOOcons{v_1}{v_2})
+	}{(\mathtt{fst} \; \kappa)}
+	}{
+	\sOOreturn{v_1}{\kappa}
+	}{}
 	\hiredrule{
@@
 			)}
+	}{}
+	\redrule{
+	\sOOreturn{
+		(\vOOcons{v_1}{v_2})
+	}{(\mathtt{snd} \; \kappa)}
+	}{
+	\sOOreturn{v_2}{\kappa}
 	}{}
@@
 \begin{cases}
-	\sOOreturn{u}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{u}}
+	\sOOreturn{v'}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{v'}}
 	\\
@@
 
-\todo[inline]{There are missing transition rules for fst and snd. -JS}
+\todo[inline]{There are missing transition rules for fst and snd. -JS
+\\---\\
+Fixed. -KC}
 
@@
 	}
-	\stxrule{r}{cast results}{
-		\rOOsucc{v} \mid
-		\rOOfail{l}
-	}
-	\stxrule{s}{states}{
-		\sOOinspect{e}{\rho}{\kappa} \mid{}
-		\sOOreturn{v}{\kappa} \mid{}
-		\sOOhalt{o}
-	}
+%	\stxrule{r}{cast results}{
+%		\rOOsucc{v} \mid
+%		\rOOfail{l}
+%	}
+%	\stxrule{s}{states}{
+%		\sOOinspect{e}{\rho}{\kappa} \mid{}
+%		\sOOreturn{v}{\kappa} \mid{}
+%		\sOOhalt{o}
+%	}
 	\stxrule{\kappa}{continuation}{
@@
 	\begin{array}{rclr}
-	& \vdots \\
+	\hiredruleS{
+		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+	}{}
 	\redruleS{
-		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
+		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
+	}{	
+		\sOOreturn{\rho[x]}{\kappa}
+	}{}
+	\redruleS{
+		\sOOinspect{\eOOsole}{\rho}{\kappa}
+	}{
+		\sOOreturn{\hcvOOtt}{\kappa}
+	}{}
+	\hiredruleS{
+		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
 	}{
 		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
-	}{}
-	\redruleS{
-		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-	}{
-		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
 	}{}
@@
 	}{
-		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+		\sOOinspect{e_1}{E}{}
 	}{}
 	\redruleS{
-		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-	}{
+		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{cont(\kOOinl{\kappa})}
+	}{}
+	\redruleS{
+		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{cont(\kOOinr{\kappa})}
+	}{}
+	\redruleS{
+		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{\rho}{cont(\kOOappI{E}{e_2}{\kappa})}}{}
+
+	\redruleS{
+		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
+		\sOOinspect{e}{\rho}{cont(\kOOcar{\kappa})}}{}
+
+	\redruleS{
+		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
+		\sOOinspect{e}{\rho}{cont(\kOOcdr{\kappa})}}{}
+
+	\redruleS{
+		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
+		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
+	\hiredruleS{
+		\sOOreturn{v}{\langle c \rangle k}
+	}{
+	\begin{cases}
+	continue(k,v') & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
+	\\
+	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
+	\end{cases}
+	}{}
+%\redruleS{
+%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
+%	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
+%
+%\redrule{
+%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
+%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
+%\\&&
+%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
+%
+%\redrule{
+%\sOOreturn{v}{(\kOOinl{\kappa})}}{
+%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
+%\\&&
+%\sidecond{v : T}}
+%
+%\redrule{
+%\sOOreturn{v}{(\kOOinr{\kappa})}}{
+%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
+%\\&&
+%\sidecond{v : T}}
+%
+%\redrule{
+%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
+%\sOOinspect{e_2}{\rho}{cont(\kOOappII{v_1}{\kappa})}}{}
+%
+%	
+%	& \vdots \\
+%	\redruleS{
+%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
+%	}{
+%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
+%	}{}
+%	\redruleS{
+%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
+%	}{
+%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+%	}{}
+%	\redruleS{
+%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+%	}{
+%		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+%	}{}
+%	\redruleS{
+%		
+%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
+%	}{
+%		\begin{cases}
+%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
+%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
+%		\\
+%		\sOOhalt{(\oOOblame{l})} \\
+%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
+%		\end{cases}
+%		
+%	}{}
+	\end{array}
+	\]
+
+	Apply continuation
+	\fbox{$ continue(k,v) = s $}
+	\[
+	\begin{array}{rclr}
+
+\funrule{
+	\continue{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
+	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
+
+\hifunrule{
+	\continue{v_2}{(\kOOconsII{v_1}{\kappa})}}{
+	\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{}
+
+\hifunrule{
+	\continue{v}{(\kOOinl{\kappa})}}{
+	\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{}
+
+\hifunrule{
+	\continue{v}{(\kOOinr{\kappa})}}{
+	\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{}
+
+\funrule{
+	\continue{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
+	\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}
+
+%\funrule{
+%	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
+%applyCast(v_2,c_1) >>= \lambda v. \sOOinspect{e}{\rho[x:=v]}{ext(c,\kappa)}
+%}{}
+
+\hifunrule{
+	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
 \begin{cases}
 	\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
-		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
+\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
 \\
-		\sOOhalt{(\oOOblame{l})} \\
-		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
+\sOOhalt{l} \\
+\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
 \end{cases}
-
-	}{}
-	\end{array}
-	\]
+}{}
+\hifunrule{
+	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
+		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
+		\;\kappa)}
+}{
+	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
+}{}
+
+\hifunrule{
+	\continue{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}
+	{(\mathtt{case_3}\;(\hcvOOinr{v}{c})\;v_2\;\kappa)}
+}{
+	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
+}{}
+
+\funrule{
+	\continue{v}{\kOOmt}}{
+	\sOOhalt{observe(v)}}{}
+
+	\end{array}\]
 
@@
 
-	Evaluation \fbox{$ \judgeSeval{C}{e}{o} $}
-	\[
-	\inference{
-		\judgeSreduceTrans{C}{
-			\sOOinspect{e}{\emptyset}{cont(\hckOOmt)}
-		}{
-			\sOOhalt{o}
-		}		
-	}{
-		\judgeSeval{C}{e}{o}
-	}
-	\]
+%	Evaluation \fbox{$ \judgeSeval{C}{e}{o} $}
+%	\[
+%	\inference{
+%		\judgeSreduceTrans{C}{
+%			\sOOinspect{e}{\emptyset}{cont(\hckOOmt)}
+%		}{
+%			\sOOhalt{o}
+%		}		
+%	}{
+%		\judgeSeval{C}{e}{o}
+%	}
+%	\]
 
@@
 
-\todo[inline]{KC needs to add missing rules in and describe them. -KC}
 We list a fraction of reduction rules due to space limitation.

### 2019-10-20 paper.tex
proved check consistency before compose middles;

@@
 \newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
+\newcommand{\comprulel}[4]{#1 & \fatsemi^l & #2 & = & #3 & #4 \\}
 \newcommand{\plus}[0]{+}
@@
 
-	\comprule{
+	\comprulel{
 		\hyperCoercionI
@@
 		\hyperCoercionC{?^{l}}{m}{t}
-	}{\sidecond{\ell = l}}
+	}{}
 
@@
 	\comprule{
-		\hyperCoercionC{h}{m_1}{t_1}
+		\hyperCoercionC{h_1}{m_1}{t_1}
 	}{
@@
 	}{
-		\hyperCoercionC{h}{m'}{t'}
+		\hyperCoercionC{h_1}{m_1 \fatsemi^{\ell} m_2}{t_2}
 	}{
 		\sidecond{
-			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
+			m_1 \smile m_2
 			\; \text{and} \;
@@
 	}
-
 	\comprule{
-		\hyperCoercionC{h}{m_1}{t_1}
-	}{
-		\hyperCoercionC{?^{l'}}{m_2}{t_2}
-	}{
-		\hyperCoercionC{h}{m'}{t'}
+		\hyperCoercionC{h_1}{m_1}{t_1}
+	}{
+		\hyperCoercionC{?^l}{m_2}{t_2}
+	}{
+		\hyperCoercionC{h_1}{m_1 \fatsemi^{l} m_2}{t_2}
 	}{
 	\sidecond{
-			m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
+		m_1 \smile m_2
 		\; \text{and} \;
@@
 	}
-	\end{array}
-	\]
-
-	Composition of middles \fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
+	\comprulel{
+	\hyperCoercionC{h_1}{m_1}{t_1}
+	}{
+	\hyperCoercionC{h_2}{m_2}{t_2}
+	}{
+	\hyperCoercionC{h_1}{m_1}{\bot^l}
+	}{
+	\sidecond{
+		\neg \; m_1 \smile m_2
+		\; \text{and} \;
+		\forall l. t \neq \bot^{l}
+	}
+	}
+%
+%	\comprule{
+%		\hyperCoercionC{h}{m_1}{t_1}
+%	}{
+%		\hyperCoercionC{\epsilon}{m_2}{t_2}
+%	}{
+%		\hyperCoercionC{h}{m'}{t'}
+%	}{
+%		\sidecond{
+%			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
+%			 \; \text{and} \;
+%			 \forall l. t \neq \bot^{l}
+%		}
+%	}
+%	
+%	\comprule{
+%		\hyperCoercionC{h}{m_1}{t_1}
+%	}{
+%		\hyperCoercionC{?^{l'}}{m_2}{t_2}
+%	}{
+%		\hyperCoercionC{h}{m'}{t'}
+%	}{
+%		\sidecond{
+%			m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
+%			\; \text{and} \;
+%			\forall l. t \neq \bot^{l} 
+%		}
+%	}
+	\end{array}
+	\]
+
+	Composition of middles \fbox{$ m \fatsemi^\ell m = m $}
 	\[ 
 	\begin{array}{rclclr}
-	\comprule{\POOunit}{(\POOunit,t)}{
-		(\POOunit,t)
-	}{}
-	\comprule{\POOfun{c_1}{c_2}}{(\POOfun{c_3}{c_4},t)}{
-		(\POOfun{c_3 \fatsemi^{\ell} c_1}{c_2 \fatsemi^\ell c_4},t)
-	}{}
-	\comprule{\POOprod{c_1}{c_2}}{(\POOprod{c_3}{c_4},t)}{
-		(\POOprod{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
-	}{}
-	\comprule{\POOsum{c_1}{c_2}}{(\POOsum{c_3}{c_4},t)}{
-		(\POOsum{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
-	}{}
-	\comprule{m_1}{(m_2,t)}{
-		(m_1,\bot^l)
-	}{
-		\sidecond{
-			\ell = l \; \text{and} \;
-			\neg m_1 \smile m_2 
-		}
-	}
+	\comprule{\POOunit}{\POOunit}{
+		\POOunit
+	}{}
+	\comprule{\POOfun{c_1}{c_2}}{\POOfun{c_3}{c_4}}{
+		\POOfun{c_3 \fatsemi^{\ell} c_1}{c_2 \fatsemi^\ell c_4}
+	}{}
+	\comprule{\POOprod{c_1}{c_2}}{\POOprod{c_3}{c_4}}{
+		\POOprod{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4}
+	}{}
+	\comprule{\POOsum{c_1}{c_2}}{\POOsum{c_3}{c_4}}{
+		\POOsum{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4}
+	}{}
 	\end{array}
@@
 	\]
-	\caption{\lazyD{} hypercoercion}
+	\caption{\lazyD{} Hypercoercions}
 	\label{fig:HC-D}
@@
 
-\figref{fig:HC-D} defines the constructors of \lazyD{} hypercoercion.
-
-Let $ \ell $ range over $ \epsilon $ and labels.
+\figref{fig:HC-D} defines functions that construct \lazyD{} hypercoercions. We 
+expect language implementations to call $ id(T) $, which constructs an 
+identity, $ seq(c,c) $, which composes two hypercoercions, and $ 
+cast(T_1,l,T_2) $, which translate a cast to a hypercoercion. Other functions 
+in the figure are their helpers.
+
 $ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
 c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
-be a label.
+be a label. The last two lines are the most interesting. When the head of the 
+second hypercoercion is a no-op, we use the same $ \ell $ to compose the 
+middles. Otherwise, the head must be a projection, where we use the label in 
+the projection to compose middles.
+
+Let $ \ell $ range over $ \epsilon $ and labels.
 $ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 

### 2019-10-21 paper.tex
todos
cite ron for the state of art of threesomes
cite the right garcia for supercoercions
sec 3 in much more details

@@
 \newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
-\newcommand{\rOOsucc}[1]{#1}
-\newcommand{\rOOfail}[1]{#1}
-%\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
-%\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
+%\newcommand{\rOOsucc}[1]{#1}
+%\newcommand{\rOOfail}[1]{#1}
+\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
+\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
 \newcommand{\kOOmt}[0]{\mathtt{stop}}
@@
 The current state of the art includes
+
 \begin{itemize}
-\item threesomes \citep{siek2010threesomes},
-\item supercoercions \citep{garcia2014deriving}, and
+\item threesomes \citep{siek2010threesomes,garcia2013calculating},
+\item supercoercions \citep{garcia2013calculating}, and
 \item coercions in normal form
@@
 beginning; injections and failures are always at the end. Hypercoercions have 
-similar shape: a hypercion has either one part or three parts; for three-part 
-hypercoercions, the first part is either a projection or a no-op, while the 
-last part is either an injection, a failure, or a no-op.
-
-\figref{fig:hypercoercion} defines the syntax of hypercoercion. Types, 
+similar shape: a hypercion either is $ \hyperCoercionI $, the identity cast for 
+$ \TOOdyn $, or contains three parts, where the first part is either a 
+projection or a no-op while last part is either an injection, a failure, or a 
+no-op.
+
+\figref{fig:hypercoercion} defines the syntax of hypercoercions. Types, 
 pre-types, and blame labels are as before.
 
-Let $ c $ range over hypercoercions. A hypercoercion is either 
-an identity cast between the dynamic types, or a complex including a head, a 
-middle, and a tail. 
+Let $ c $ range over hypercoercions. A hypercoercion either is the identity 
+cast between the dynamic types, or includes a head, a middle, and a tail. 
 Let $ h $ range over heads. A head is either a no-op, or a projection.
@@
 correspondence between middles and type constructors. 
-We generalize shallow-consistency to middles $ m \smile m $ in the natural way.
+We generalize shallow-consistency to middles $ m \smile m $ in the obvious way.
 Let $ t $ range over tails. A tail is either a no-op, an injection, or a 
@@
 
-We define hypercoercion constructs in the following subsections.
-But functions that apply hypercoercions to values are deferred to 
-Section~\ref{sec:hypercoercion-correctness} because 
-they depends on a new definition of values, which is part of the framework in
+Subsection~\ref{sec:ld-hc} defines functions that construct \lazyD\ 
+hypercoercions. Subsection~\ref{sec:lud-hc} defines the \lazyUD\ counterparts. 
+Functions that apply hypercoercions to values are deferred to 
+Section~\ref{sec:hypercoercion-correctness} because they depends on a new 
+definition of values, which is part of the framework in
 Section~\ref{sec:framework}.
@@
 \subsection{\lazyD{} hypercoercion}
+\label{sec:ld-hc}
 
@@
 	}{
+		\hyperCoercionC{?^l}{m_2}{t_2}
+	}{
+		\hyperCoercionC{h_1}{m_1}{\bot^l}
+	}{
+		\sidecond{
+			\neg \; m_1 \smile m_2
+			\; \text{and} \;
+			\forall l. t \neq \bot^{l}
+		}
+	}
+
+\comprulel{
+\hyperCoercionC{h_1}{m_1}{t_1}
+}{
 \hyperCoercionC{\epsilon}{m_2}{t_2}
 }{
-		\hyperCoercionC{h_1}{m_1 \fatsemi^{\ell} m_2}{t_2}
+\hyperCoercionC{h_1}{m_1}{\bot^l}
+}{
+\sidecond{
+	\neg \; m_1 \smile m_2
+	\; \text{and} \;
+	\forall l. t \neq \bot^{l}
+}
+}
+\comprule{
+\hyperCoercionC{h_1}{m_1}{t_1}
+}{
+\hyperCoercionC{?^l}{m_2}{t_2}
+}{
+\hyperCoercionC{h_1}{m_1 \fatsemi^{l} m_2}{t_2}
 }{
@@
 	}{
-		\hyperCoercionC{?^l}{m_2}{t_2}
-	}{
-		\hyperCoercionC{h_1}{m_1 \fatsemi^{l} m_2}{t_2}
+		\hyperCoercionC{\epsilon}{m_2}{t_2}
+	}{
+		\hyperCoercionC{h_1}{m_1 \fatsemi^{\ell} m_2}{t_2}
 	}{
@@
 			m_1 \smile m_2
-		\; \text{and} \;
-		\forall l. t \neq \bot^{l}
-	}
-	}
-	\comprulel{
-	\hyperCoercionC{h_1}{m_1}{t_1}
-	}{
-	\hyperCoercionC{h_2}{m_2}{t_2}
-	}{
-	\hyperCoercionC{h_1}{m_1}{\bot^l}
-	}{
-	\sidecond{
-		\neg \; m_1 \smile m_2
 			\; \text{and} \;
@@
 
-$ c_1 \fatsemi^\ell c_2 = c' $ composes two hypercoercions. The target of $ 
-c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
-be a label. The last two lines are the most interesting. When the head of the 
-second hypercoercion is a no-op, we use the same $ \ell $ to compose the 
-middles. Otherwise, the head must be a projection, where we use the label in 
-the projection to compose middles.
-
 Let $ \ell $ range over $ \epsilon $ and labels.
-$ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 
-pair of a middle and a tail. Similarly, the target of $ m_1 $ and the source of 
-$ m_2 $ might be different, in which case $ \ell $ must be a label.
-$ seq(c_1,c_2) $ composes two coercions where the target type of $ c_1 $ is 
-equal to the source type of $ T_2 $.
+$ c_1 \fatsemi^\ell c_2 $ composes hypercoercion $ c_1 $ and hypercoercion $ 
+c_2 $.
+When both $ c_1 $ and $ c_2 $ are $ \hyperCoercionI $, their 
+composition is also $ \hyperCoercionI $.
+When $ c_1 $ is $ \hyperCoercionI $ but $ c_2 $ is not, the head of the 
+composition must be a projection. In this 
+case, if the head of $ c_2 $ is a projection, we reuse it. Otherwise, we need a 
+label to build the projection. Since the head of $ c_2 $ is $ \epsilon $, its 
+source type must be a pretype. Thus we know $ \ell $ must be a label and put it 
+in the projection. 
+When $ c_1 $ ends with a failure, the composition is $ c_1 $ itself. In all 
+remaining cases, we shall assume that $ c_1 $ does not end with 
+a failure.
+When $ m_1 $ and $ m_2 $ have different top constructors ($ \neg\;m_1 \smile 
+m_2 $), proceeding to $ m_2 $ can not make sense. So we end the composition 
+with a failure. To do so we need a label. When $ c_2 $ starts with a 
+projection, we shall accuse it of casting a value to a shallowly inconsistent 
+type. When $ c_2 $ starts with a no-op, $ \ell $ must be a label. And we accuse 
+it of composing shallowly inconsistent hypercoercions. The last two cases 
+compose $ m_1 $ and $ m_2 $ with a helper function $ m \fatsemi^\ell m $, which 
+assumes its inputs have the same top constructor. The definition of $ m 
+\fatsemi^\ell m $ is straightforward. Going back to the last two cases of $ c_1 
+\fatsemi^\ell c_2 $. When $ c_2 $ starts with a projection, we have no clue 
+whether the target type of $ m_1 $ is the same as the source of $ m_2 $, 
+although we know they are shallowly consistent. So we give the $ l $ in the 
+projection to $ m \fatsemi^\ell m $. When $ c_2 $ starts with a no-op, we reuse 
+the $ \ell $.
+
+$ seq(c_1,c_2) $ requires that the target type of $ c_1 $ is the same as the 
+source of $ c_2 $. $ c \fatsemi^\ell c $ does the job for it.
 $ id(T) $ constructs an identity coercion of $ T $ with the help of $ id(P) $. 
+Their definitions are straightforward.
 $ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
-target type.
+target type. $ c \fatsemi^\ell c $ does the most job.
 
@@
 \end{proposition}
+\begin{proof}
+	By induction on hypercoercion(s).
+\end{proof}
+
+\begin{proposition}[]
+	For all $ T $ and $ l $, $ cast(T,l,T) = id(T) $
+\end{proposition}
+\begin{proof}
+	By induction on T.
+\end{proof}
 
 \subsection{\lazyUD{} hypercoercion [Jeremy]}
+\label{sec:lud-hc}
 
@@
 
+\todo[inline]{An extra property is required after changing case to small-step 
+-KC}
 \begin{lemma}[$ \text{Lazy D Cast ADT} \cap \text{Monoid} $ Respects 

### 2019-10-21 paper.tex
new macros for continuations

@@
 \newcommand{\lazyD}{Lazy\;D}
-\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
+
+\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #2(#1) \; #3}
 \newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
 \newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
+
+%\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
+%\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
+%\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
+
 \newcommand{\TOOdyn}[0]{\star}
@@
 \newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
-\newcommand{\kOOmt}[0]{\mathtt{stop}}
-\newcommand{\kOOconsI}[3]{\mathtt{cons_1} \; #1 \; #2 \; #3}
-\newcommand{\kOOconsII}[2]{\mathtt{cons_2} \; #1 \; #2}
-\newcommand{\kOOinl}[1]{\mathtt{inl} \; #1}
-\newcommand{\kOOinr}[1]{\mathtt{inr} \; #1}
+
+\newcommand{\kOOmt}[0]{\square}
+\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; #2(#1) ]}
+\newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
+\newcommand{\kOOinl}[1]{#1[\mathtt{inl} \; \square]}
+\newcommand{\kOOinr}[1]{#1[\mathtt{inr} \; \square]}
 \newcommand{\kOOappI}[3]{
-	\mathtt{app_1} \; #1 \; #2 \; #3
+	#3[\square \; #2(#1) ]
 }
 \newcommand{\kOOappII}[2]{
-	\mathtt{app_2} \; #1 \; #2}
-\newcommand{\kOOcar}[1]{
-	\mathtt{fst} \; #1}
-\newcommand{\kOOcdr}[1]{
-	\mathtt{snd} \; #1}
+	#2[#1 \; \square]}
+\newcommand{\kOOcar}[1]{#1[\mathtt{fst} \; \square]}
+\newcommand{\kOOcdr}[1]{#1[\mathtt{snd} \; \square]}
 \newcommand{\kOOcaseI}[4]{
-	\mathtt{case_1} \; #1 \; #2 \; #3 \; #4}
+	#4[\mathtt{case} \; \square \; #3(#1) \; #3(#2) ]}
 \newcommand{\kOOcaseII}[4]{
-	\mathtt{case_2} \; #1 \; #2 \; #3 \; #4}
+	#4[\mathtt{case} \; #1 \; \square \; #3(#2) ]}
 \newcommand{\kOOcaseIII}[3]{
-	\mathtt{case_3} \; #1 \; #2 \; #3}
+	#3[\mathtt{case} \; #1 \; #2 \; \square]}
 \newcommand{\kOOcast}[2]{
-	\langle #1 \rangle #2}
+	#2[\square \langle #1 \rangle]}
+
+%\newcommand{\kOOmt}[0]{\mathtt{stop}}
+%\newcommand{\kOOconsI}[3]{\mathtt{cons_1} \; #1 \; #2 \; #3}
+%\newcommand{\kOOconsII}[2]{\mathtt{cons_2} \; #1 \; #2}
+%\newcommand{\kOOinl}[1]{\mathtt{inl} \; #1}
+%\newcommand{\kOOinr}[1]{\mathtt{inr} \; #1}
+%\newcommand{\kOOappI}[3]{
+%	\mathtt{app_1} \; #1 \; #2 \; #3
+%}
+%\newcommand{\kOOappII}[2]{
+%	\mathtt{app_2} \; #1 \; #2}
+%\newcommand{\kOOcar}[1]{
+%	\mathtt{fst} \; #1}
+%\newcommand{\kOOcdr}[1]{
+%	\mathtt{snd} \; #1}
+%\newcommand{\kOOcaseI}[4]{
+%	\mathtt{case_1} \; #1 \; #2 \; #3 \; #4}
+%\newcommand{\kOOcaseII}[4]{
+%	\mathtt{case_2} \; #1 \; #2 \; #3 \; #4}
+%\newcommand{\kOOcaseIII}[3]{
+%	\mathtt{case_3} \; #1 \; #2 \; #3}
+%\newcommand{\kOOcast}[2]{
+%	\langle #1 \rangle #2}
+
 \newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
@@
 etc.) impose significant runtime overheads that can change the
-asymptotic time and space complexity of a program
+asymptotic space complexity of a program
 \citep{herman2010space}. There are several known space-efficient cast
@@
 		\kOOconsII{v}{\kappa} \mid
-		\kOOinl{\kappa} \mid
-		\kOOinr{\kappa}
+		\kOOinl{\kappa}
 	}
 	\stxrulecont{
+		\kOOinr{\kappa} \mid
 		\kOOappI{e}{\rho}{\kappa} \mid
 		\kOOappII{v}{\kappa} \mid
-		\kOOcar{\kappa} \mid
-		\kOOcdr{\kappa} \mid
-		\kOOcaseI{e_1}{e_2}{\rho}{\kappa}
+		\kOOcar{\kappa}
 	}
 	\stxrulecont{	
-		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
-		\kOOcaseIII{v_1}{v_2}{\kappa} \mid
+		\kOOcdr{\kappa}\mid
+		\kOOcaseI{e}{e}{\rho}{\kappa}\mid
+		\kOOcaseII{v}{e}{\rho}{\kappa}
+	}
+	\stxrulecont{
+		\kOOcaseIII{v}{v}{\kappa} \mid
 		\kOOcast{c}{\kappa}
@@
         Shallow-consistency
-	\fbox{$ T_1 \smile T_2 $}
+	\fbox{$ T \smile T $}
 	\begin{gather*}
@@
 	}{
-		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
+		\sOOinspect{e}{\rho}{
+			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
+%			\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
+		}
 	}{}
@@
 	}{
-\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}
+\sOOinspect{e_1}{\rho}{(\kOOappI{e_2}{\rho}{\kappa})}}{}
 
@@
 \sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
-\sOOinspect{e_1}{\rho}{(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
+\sOOinspect{e_1}{\rho}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
 
@@
 	\hiredrule{
-		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
+		\sOOreturn{v_1}{
+			\kOOappII{\vOOcast{v_2}{
 					\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
-			} \; \kappa)}
+			}}{\kappa}
+%			(\mathtt{app_2} \; \vOOcast{v_2}{
+%				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
+%			} \; \kappa)
+		}
 	}{
 		\sOOreturn{v_1}{
-			\langle\cOOcast{T_3}{l}{T_1}\rangle
-			(\mathtt{app_2} \; v_2 \; 
-			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
+			\kOOcast{\cOOcast{T_3}{l}{T_1}}{
+				\kOOappII{v_2}{
+					\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}
+				}
+			}
+%			\langle\rangle
+%			(\mathtt{app_2} \; v_2 \; 
+%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
+		}
 	}{}
@@
 		(\vOOcons{v_1}{v_2})
-	}{(\mathtt{fst} \; \kappa)}
+	}{(\kOOcar{\kappa})}
 	}{
@@
 	}{
-		\sOOreturn{v}{(
-			\mathtt{fst} \;
-			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
-			)}
+		\sOOreturn{v}{
+			\kOOcar{
+				\kOOcast{\cOOcast{T_1}{l}{T_3}}{\kappa}
+			}}
 	}{}
@@
 		(\vOOcons{v_1}{v_2})
-	}{(\mathtt{snd} \; \kappa)}
+	}{(\kOOcdr{\kappa})}
 	}{
@@
 	}{
-		\sOOreturn{v}{(
-			\mathtt{snd} \;
-			\langle \cOOcast{T_2}{l}{T_4} \rangle \kappa
-			)}
+		\sOOreturn{v}{
+			\kOOcdr{\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}}}
 	}{}
@@
 \redrule{
-\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)}
+\sOOreturn{v_3}{
+	(\kOOcaseIII{(\vOOinl{v})}{v_2}{\kappa})
+%	(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)
+}
 }{
@@
 \redrule{
-	\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)}
+	\sOOreturn{v_3}{
+		(\kOOcaseIII{(\vOOinr{v})}{v_2}{\kappa})
+%		(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)
+	}
 }{
@@
 		\highlight{\sOOreturn{v}{(
-			\mathtt{cast} \; c \; \kappa
+				\kOOcast{c}{\kappa}
 			)}}
@@
 So we call them \textit{cast constructors}. And the forth and last operator 
-enable the implementation to apply casts on values.
+allows the implementation to apply casts onto values.
 
@@
 	\label{def:cast-rep}
-	A cast abstract data type is a set $ Cast $ indexed by two types with
-	four operators:
+	A cast abstract data type is a set $ Cast $, which is indexed by two types, 
+	with four operators:
 	\begin{description}
-		\item[$ id(T) = c $] constructs an identity cast
+		\item[$ id(T) = c $] constructs an cast from a type
+%		, where $ c : T 
+%		\Longrightarrow T $
 		\item[$ seq(c_1,c_2)=c $] composes two casts
+%		, where $ 
+%		\judgeTypeFT{c_1}{T_1}{T_2} $, $ \judgeTypeFT{c_2}{T_2}{T_3} $, and $ 
+%		\judgeTypeFT{c}{T_1}{T_3} $
 		\item[$ cast(T_1,l,T_2)=c $] constructs a cast from $ T_1 $ to $ T_2 $
@@
 	\end{description}
+	We denote by $ c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
+	T_1 \; T_2 $. And we say ``$ c $ is from $ T_1 $ to $ T_2 $''.
 \end{definition}
@@
 \textit{monoids}. This definition is useful in the proof of 
-our framework, and might be interesting for other people.
+our framework.
 
@@
 To use our framework, users needs to prove that their cast representation
-implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}). Property (1) 
-states that $ id(T) $ must acts like the identity function. Property (2) states 
-that $ seq(c,c) $ must acts like a sequence of casts. Properties (3) through 
-(11) state that $ cast(T_1,l,T_2) $ must act like the Lazy D $ applyCast $ 
+implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
+Cast ADT. Property (1) 
+states that $ id(T) $ acts like the identity function. Property (2) states 
+that $ seq(c,c) $ acts like a sequence of casts. Properties (3) through 
+(11) state that $ cast(T_1,l,T_2) $ act like the Lazy D $ applyCast $ 
 defined in Fig.~\ref{fig:applyCast-D-C}.
+
+\todoKC{define values before Lazy D Cast ADT}
 
@@
 \end{figure}
-\figref{fig:machine-cekcc} defines, \effCEK{C}, a space-efficient
-semantics as a CEK machine.  This machine is similar to \ineffCEK{}.
-The most important differences are in values and continuations.
+\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient
+CEK machine.  This machine is similar to \ineffCEK{}.
+The keys differences are in values and continuations.
 
@@
 
+\todoKC{describe transition rules}
 We list a fraction of reduction rules due to space limitation.

### 2019-10-21 paper.tex
edits to section 2, start of adding text to sec 4

@@
 \newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
+\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
+\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
+\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
 \newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
@@
 
-\todo[inline]{There are missing transition rules for fst and snd. -JS
-\\---\\
-Fixed. -KC}
-
 Let $ r $ range over cast results. A cast result is either a success, which 
@@
 
-\subsection{The \lazyD{} cast calculus}
-
 \begin{figure}
@@
 
-\figref{fig:applyCast-D-C} defines the $ applyCast $ for \lazyD. 
-We conjecture that with this $ applyCast $, the CEK machine in 
-\figref{fig:machine-cekc} would agree with the \lazyD{} cast calculus in 
-\citet{siek2009exploring}. We denote this \lazyD{} machine by \ineffCEKD{},
-and the corresponding relations by $ \judgeDreduce{s}{s} $, $ 
-\judgeDreduceTrans{s}{s} $, and $ \judgeDeval{e}{o} $
-
-\subsection{The \lazyUD{} cast calculus [Jeremy]}
-
-\todo[inline]{I need to update this subsection. -JS}
-
-The dynamic semantics of the \lazyUD{} cast calculus, which we define here as a
-CEK machine, is similar to that of the \lazyD{} cast calculus
-(Fig. \ref{fig:machine-cekc}). The only difference is in the definition of
-the $\mathit{applyCast}$ function, in which a cast whose source or
-target is the unknown type $\star$ is always split into two casts that
-go through an injectiable type, that is, a type in which all
-sub-components are the unknown type, such as $\star \to \star$. The
-definition of $\mathit{applyCast}$ for the \lazyUD{} cast calculus is given in
-Fig.~\ref{fig:apply-Cast-UD}.
+\begin{definition}[\lazyD{} CEK Machine]
+  The \lazyD{} CEK machine, written \ineffCEKD{}, is the CEK machine of
+  \figref{fig:machine-cekc} using the $applyCast$ for \lazyD{} defined
+  in \figref{fig:applyCast-D-C}.  We write the transition relations of
+  this machine as $\judgeUDreduce{s}{s}$ and $\judgeUDreduceTrans{s}{s}$
+  and write the evaluation function as $\judgeUDeval{e}{o}$.
+\end{definition}
+
+We conjecture that \ineffCEKD{} agrees with the \lazyD{} cast calculus
+of \citet{siek2009exploring}.
+
+Next we define the CEK Machine for \lazyUD{}. The only difference with
+respect to \lazyD{} is in the definition of the $\mathit{applyCast}$
+function, in which a cast whose source or target is the unknown type
+$\star$ is always split into two casts that go through an injectiable
+type, that is, a type in which all sub-components are the unknown
+type, such as $\star \to \star$.
+
+\begin{definition}[\lazyUD{} CEK Machine]
+  The \lazyUD{} CEK machine, written \ineffCEKUD{}, is the CEK machine of
+  \figref{fig:machine-cekc} using the $applyCast$ for \lazyUD{} defined
+  in \figref{fig:apply-Cast-UD}.  We write the transition relations of
+  this machine as $\judgeDreduce{s}{s}$ and $\judgeDreduceTrans{s}{s}$
+  and write the evaluation function as $\judgeDeval{e}{o}$.
+\end{definition}
 
 \begin{figure}
-%
-%  Syntax
-%  \[
-%  \begin{array}{rclr}
-%    \stxrule{v}{values}{
-%      \cdots \mid 
-%      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
-%      \vOOcast{v}{ \cOOcast{P}{l}{P} }
-%    }
-%  \end{array}
-%  \]
-%  
   \fbox{$\mathit{applyCast}(v,c) = r$}
@@
 \end{figure}
+
+We conjecture that \ineffCEKUD{} agrees with the \lazyUD{} cast
+calculus of \citet{siek2009exploring}.
 
@@
 
-\section{a framework for proving correctness of cast representations}
+\section{A framework for proving correctness of cast representations}
 \label{sec:framework}
@@
 This section presents our second contribution, a framework for proving
-correctness of cast representations. The framework is a theorem saying that for 
-all cast representation $ C $, if $ C $ satisfies a collection of properties, 
-then it would respect the Lazy D semantics of cast calculi. We are working on a 
+correctness of cast representations. The next section will apply this
+framework to prove the correctness of the \lazyD{} hypercoercions.
+
+The framework is a theorem saying that for all cast representation $ C
+$, if $ C $ satisfies a collection of properties, then it would
+respect the Lazy D semantics of cast calculi. We are working on a
 similar theorem for \lazyUD{}.
@@
 We list a fraction of reduction rules due to space limitation.
+\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS}
 When values are constructed, their hypercoercion parts are filled with outputs 
@@
 \todo[inline]{Standardize theorem statement -KC}
-\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
+\begin{lemma}[Strong Bisimulation among $ \mathcal{S}(\cdot) $]
 	\label{thm:CEKS-bisim}

### 2019-10-21 paper.tex
check

@@
 
+We start by defining a CEK machine \effCEK{C} that is parameterized
+over the cast representation $C$. This machine is space efficient
+provided that the cast representation performs compression.  The
+interface between the machine and the cast representation is defined
+by an abstract data type, named Cast ADT, that we define shortly.
+%
+
+\todo[inline]{UNDER CONSTRUCTION. -JS}
+
 The framework is a theorem saying that for all cast representation $ C
@@
 	\label{def:cast-rep}
-	A cast abstract data type is a set $ Cast $, which is indexed by two types, 
+	A cast abstract data type is a set $Cast $, which is indexed by two types, 
 	with four operators:
 	\begin{description}
-		\item[$ id(T) = c $] constructs an cast from a type
-%		, where $ c : T 
+		\item[$id(T) $] constructs an cast from a type
+%		, where $c : T 
 %		\Longrightarrow T $
-		\item[$ seq(c_1,c_2)=c $] composes two casts
+		\item[$seq(c_1,c_2) $] composes two casts
 %		, where $
-%		\judgeTypeFT{c_1}{T_1}{T_2} $, $ \judgeTypeFT{c_2}{T_2}{T_3} $, and $ 
+%		\judgeTypeFT{c_1}{T_1}{T_2} $, $\judgeTypeFT{c_2}{T_2}{T_3} $, and $
 %		\judgeTypeFT{c}{T_1}{T_3} $
-		\item[$ cast(T_1,l,T_2)=c $] constructs a cast from $ T_1 $ to $ T_2 $
+		\item[$cast(T_1,l,T_2) $] constructs a cast from $T_1$ to $T_2$
 		\item[$ applyCast(v,c)=r $] applies a cast onto a value
 	\end{description}
-	We denote by $ c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
+	We denote by $c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
 	T_1 \; T_2 $. And we say ``$ c $ is from $ T_1 $ to $ T_2 $''.
@@
 -KC}
-\begin{lemma}[$ \text{Lazy D Cast ADT} \cap \text{Monoid} $ Respects 
-	$ \mathcal{C} $]
+\begin{proposition}[Correctness of \effCEK{C}]
 	\label{thm:surely-monoidic-eval}
@@
 	\]
-\end{lemma}
+\end{proposition}
 \begin{proof}Proving left implies right is trivial.

### 2019-10-21 paper.tex
remv whitespaces padding $$

@@
 % names
-\newcommand{\ineffCEK}{$ \mathcal{C} $}
-\newcommand{\ineffCEKD}{$ \mathcal{D} $}
-\newcommand{\ineffCEKUD}{$ \mathcal{UD} $}
+\newcommand{\ineffCEK}{$\mathcal{C}$}
+\newcommand{\ineffCEKD}{$\mathcal{D}$}
+\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
 \newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
@@
 \newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
-\newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}
-\newcommand{\evalEqv}[2]{$ eval_{\text{#1}} = eval_{\text{#2}} $}
+\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
+\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
 \newcommand{\continue}[2]{continue(#2,#1)}
@@
 	Consistency
-	\fbox{$ T_1 \sim T_2 $}
+	\fbox{$T_1 \sim T_2$}
 	\begin{gather*}
@@
 	Term typing
-	\fbox{$ \judgetype{\Gamma}{e}{T} $}
+	\fbox{$\judgetype{\Gamma}{e}{T}$}
 	\begin{gather*}
@@
   the \emph{pretypes} ($\POOunit$, functions, products, and sums),
-  versus the dynamic type $\star$ (a.k.a. $ \mathtt{Dyn} $ or
+  versus the dynamic type $\star$ (a.k.a. $\mathtt{Dyn}$ or
   $\mathbb{?}$).
@@
 %% its static semantics. We extend the syntax of
-%%  with sum and product types.  Let $ T $ range
-%% over types. A type is either the dynamic type $ \star $ (a.k.a. $
-%% \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), or a type
-
-%% As usual we write $ T_1 \sim T_2 $ when $ T_1 $ and $ T_2 $ are
-%% consistent. The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $
-%% T_2 $ have no conflicting type information. Two types are consistent
-%% if one of them is $ \star $, or they have the same top-most type
+%%  with sum and product types.  Let $T$ range
+%% over types. A type is either the dynamic type$\star$(a.k.a. $
+%% \mathtt{Dyn}$, $\mathbb{?}$, or$\mathtt{Unknown}$), or a type
+
+%% As usual we write$T_1 \sim T_2$when$T_1$ and $T_2$ are
+%% consistent. The intuition of $T_1 \sim T_2$ is that $T_1$and $
+%% T_2$have no conflicting type information. Two types are consistent
+%% if one of them is $\star$, or they have the same top-most type
 %% constructor and the corresponding sub-parts are
@@
 
-%% We write $ T_1 \smile T_2 $ when $ T_1 $ and $ T_2 $ are
-%% shallowly-consistent, that is, if one of them is $ \star $, or they
+%% We write$T_1 \smile T_2$when$T_1$ and $T_2$ are
+%% shallowly-consistent, that is, if one of them is $\star$, or they
 %% have the same type constructor at the top. Shallow-inconsistency is
@@
 
-%% Let $ e $ range over terms. Most terms are standard for a simply-typed
+%% Let $e$ range over terms. Most terms are standard for a simply-typed
 %% lambda calculus. We annotate the codomain of a lambda abstraction
@@
 %% Other
-%% transition rules starting from $ Eval $ states are standard.
-To apply a casted function, the machine first casts $ v_1 $, the
-operand, then applies the casted operand to $ v_2 $, the underlying
+%% transition rules starting from$Eval$states are standard.
+To apply a casted function, the machine first casts $v_1$, the
+operand, then applies the casted operand to $v_2$, the underlying
 function, and finally cast the result of the function application.
@@
 To take out the first (resp. second) part of a casted pair, the
-machine firstly take out the first (resp. second) part of $ v $, the
+machine firstly take out the first (resp. second) part of $v$, the
 underlying pair, and cast the result.
@@
 %
-%% When the continuation is $ stop $, the machine enters a halting
+%% When the continuation is $stop$, the machine enters a halting
 %% state. The When the machine is in a halting state, it stays in the
@@
 
-The reflexive transitive closure of reduction ($
-\judgeCreduceTrans{s}{s} $) and evaluation ($ eval_\mathcal{C}(e) $)
+The reflexive transitive closure of reduction ($\judgeCreduceTrans{s}{s}$) and 
+evaluation ($eval_\mathcal{C}(e)$)
 are standard~\citep{felleisen03:_pllc}.
@@
         Shallow-consistency
-	\fbox{$ T \smile T $}
+	\fbox{$T \smile T$}
 	\begin{gather*}
@@
 
-	Value typing \fbox{$ v : T $}
+	Value typing \fbox{$v : T$}
 	\begin{gather*}
@@
 
-Let $ v $ range over values. A value is either the unit, a function (a
+Let $v$ range over values. A value is either the unit, a function (a
 closure), a pair, a left injection, a right injection, or a casted
@@
 
-Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
-
-Let $ o $ range over observations. They are what would be observed if
+Let $c$ range over casts. A cast is a triple of a type, a label, and a type.
+
+Let $o$ range over observations. They are what would be observed if
 a program terminates. Observations include all value constructors and
-blame.  The function converting values to observations ($ observe(v) =
-o $) is defined in the natural way.
+blame.  The function converting values to observations ($observe(v) =
+o$) is defined in the natural way.
 
 \begin{figure}
-	%	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
+	%	Continuation typing \fbox{$\kappa : T_1 \Longrightarrow T_2$}
 	%	\begin{gather*}
@@
 
-	Reduction \fbox{$ \judgeCreduce{s}{s} $}
+	Reduction \fbox{$\judgeCreduce{s}{s}$}
 	\[
@@
 
-Let $ r $ range over cast results. A cast result is either a success, which 
+Let $r$ range over cast results. A cast result is either a success, which 
 brings back a value, or a failure, which brings a blame label.
 
-Let $ s $ range over machine states. A state is either looking at an 
+Let $s$ range over machine states. A state is either looking at an 
 expression to decide what to do next, returning a value to a continuation, or 
@@
 
-Let $ \kappa $ range over continuations. $ \mathtt{stop} $ is the top 
+Let $\kappa$ range over continuations. $\mathtt{stop}$ is the top 
 continuation. The remaining continuations correspond to expressions. For 
-example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
-we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
-the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
-returning to $ \kappa $.
+example, $(\mathtt{cons_1} \; e \; \rho \; \kappa)$ is the continuation where 
+we are waiting for the value of the first argument to a $\mathtt{cons}$. And 
+the last continuation, $\langle c \rangle \kappa$ is to cast the value before 
+returning to $\kappa$.
 
@@
 	\]
-	\caption{Definition of $ applyCast $ for \lazyD}
+	\caption{Definition of $applyCast$for \lazyD}
 	\label{fig:applyCast-D-C}
@@
 Types, pre-types, and blame labels are as before.
-Let $ I $ range over injectable types. An injectable type is a type that can 
-be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
+Let $I$ range over injectable types. An injectable type is a type that can 
+be cast directly to (injection) and from (projection) $\TOOdyn$. The 
 definition of injectable type depends on blame strategy. With \lazyD, all 
-pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
+pre-types are injectable. With \lazyUD, only $\POOfun{\TOOdyn}{\TOOdyn}$
 is injectable. 
-Let $ c $ range over coercions, a coercion is either injection, projection, 
+Let $c$ range over coercions, a coercion is either injection, projection, 
 identity, failure, sequencing, or function coercion.
-Let $ \bar{c} $ range over wrapper coercions, which represent casts in $ 
-\vOOcast{v}{c} $.
-Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
-re-order the cases, the definition of $ \hat{c} $ becomes:
+Let $\bar{c}$ range over wrapper coercions, which represent casts in $
+\vOOcast{v}{c}$.
+Let $\hat{c}$ range over normal coercions. If we inline $\bar{c}$ and 
+re-order the cases, the definition of $\hat{c}$ becomes:
 \[
@@
 
-	hypercoercion typing \fbox{$ c : T \Longrightarrow T $}
+	hypercoercion typing \fbox{$c : T \Longrightarrow T$}
 	\begin{gather*}
@@
 
-	Head typing \fbox{$ \typingHC{h}{T}{P} $}
+	Head typing \fbox{$\typingHC{h}{T}{P}$}
 	\begin{gather*}
@@
 
-	Middle typing \fbox{$ \typingHC{m}{T}{T} $}
+	Middle typing \fbox{$\typingHC{m}{T}{T}$}
 	\begin{gather*}
@@
 
-		Tail typing \fbox{$ \typingHC{t}{P}{T} $}
+		Tail typing \fbox{$\typingHC{t}{P}{T}$}
 		\begin{gather*}
@@
 beginning; injections and failures are always at the end. Hypercoercions have 
-similar shape: a hypercion either is $ \hyperCoercionI $, the identity cast for 
-$ \TOOdyn $, or contains three parts, where the first part is either a 
+similar shape: a hypercion either is $\hyperCoercionI$, the identity cast for 
+$\TOOdyn$, or contains three parts, where the first part is either a 
 projection or a no-op while last part is either an injection, a failure, or a 
@@
 
-Let $ c $ range over hypercoercions. A hypercoercion either is the identity 
+Let $c$ range over hypercoercions. A hypercoercion either is the identity 
 cast between the dynamic types, or includes a head, a middle, and a tail. 
-Let $ h $ range over heads. A head is either a no-op, or a projection.
-Let $ m $ range over middles. There is a one-to-one 
+Let $h$ range over heads. A head is either a no-op, or a projection.
+Let $m$ range over middles. There is a one-to-one 
 correspondence between middles and type constructors. 
-We generalize shallow-consistency to middles $ m \smile m $ in the obvious way.
-Let $ t $ range over tails. A tail is either a no-op, an injection, or a 
+We generalize shallow-consistency to middles $m \smile m$ in the obvious way.
+Let $t$ range over tails. A tail is either a no-op, an injection, or a 
 failure.
@@
 	\begin{array}{rclr}
-	\stxrule{\ell}{Maybe $ l $}{\epsilon \mid l}
-	\end{array}
-	\]
-
-	Composition of hypercoercions \fbox{$ c \fatsemi^\ell c = c $}
+	\stxrule{\ell}{Maybe$l$}{\epsilon \mid l}
+	\end{array}
+	\]
+
+	Composition of hypercoercions \fbox{$c \fatsemi^\ell c = c$}
 	\[ 
@@
 
-	Composition of middles \fbox{$ m \fatsemi^\ell m = m $}
+	Composition of middles \fbox{$m \fatsemi^\ell m = m$}
 	\[ 
@@
 
-	\fbox{$ seq(c,c) = c $}
+	\fbox{$seq(c,c) = c$}
 	\[
@@
 
-	\fbox{$ id( P ) = m $}
+	\fbox{$id( P ) = m$}
 	\[
@@
 
-	\fbox{$ id( T ) = c $}
+	\fbox{$id( T ) = c$}
 	\[
@@
 
-	\fbox{$ cast(T,l,T) = c$}
+	\fbox{$cast(T,l,T) = c$}
 	\[
@@
 \figref{fig:HC-D} defines functions that construct \lazyD{} hypercoercions. We 
-expect language implementations to call $ id(T) $, which constructs an 
-identity, $ seq(c,c) $, which composes two hypercoercions, and $ 
-cast(T_1,l,T_2) $, which translate a cast to a hypercoercion. Other functions 
+expect language implementations to call $id(T)$, which constructs an 
+identity, $seq(c,c)$, which composes two hypercoercions, and $
+cast(T_1,l,T_2)$, which translate a cast to a hypercoercion. Other functions 
 in the figure are their helpers.
 
-Let $ \ell $ range over $ \epsilon $ and labels.
-$ c_1 \fatsemi^\ell c_2 $ composes hypercoercion $ c_1 $ and hypercoercion $ 
-c_2 $.
-When both $ c_1 $ and $ c_2 $ are $ \hyperCoercionI $, their 
-composition is also $ \hyperCoercionI $.
-When $ c_1 $ is $ \hyperCoercionI $ but $ c_2 $ is not, the head of the 
+Let $\ell$ range over $\epsilon$ and labels.
+$ c_1 \fatsemi^\ell c_2$ composes hypercoercion $c_1$ and hypercoercion $c_2$.
+When both $c_1$ and $c_2$ are $\hyperCoercionI$, their 
+composition is also $\hyperCoercionI$.
+When $c_1$ is $\hyperCoercionI$ but $c_2$ is not, the head of the 
 composition must be a projection. In this 
-case, if the head of $ c_2 $ is a projection, we reuse it. Otherwise, we need a 
-label to build the projection. Since the head of $ c_2 $ is $ \epsilon $, its 
-source type must be a pretype. Thus we know $ \ell $ must be a label and put it 
+case, if the head of $c_2$ is a projection, we reuse it. Otherwise, we need a 
+label to build the projection. Since the head of $c_2$ is $\epsilon$, its 
+source type must be a pretype. Thus we know $\ell$ must be a label and put it 
 in the projection. 
-When $ c_1 $ ends with a failure, the composition is $ c_1 $ itself. In all 
-remaining cases, we shall assume that $ c_1 $ does not end with 
+When $c_1$ ends with a failure, the composition is $c_1$ itself. In all 
+remaining cases, we shall assume that $c_1$ does not end with 
 a failure.
-When $ m_1 $ and $ m_2 $ have different top constructors ($ \neg\;m_1 \smile 
-m_2 $), proceeding to $ m_2 $ can not make sense. So we end the composition 
-with a failure. To do so we need a label. When $ c_2 $ starts with a 
+When $m_1$ and $m_2$ have different top constructors ($\neg\;m_1 \smile 
+m_2$), proceeding to $m_2$ can not make sense. So we end the composition 
+with a failure. To do so we need a label. When $c_2$ starts with a 
 projection, we shall accuse it of casting a value to a shallowly inconsistent 
-type. When $ c_2 $ starts with a no-op, $ \ell $ must be a label. And we accuse 
+type. When $c_2$ starts with a no-op, $\ell$ must be a label. And we accuse 
 it of composing shallowly inconsistent hypercoercions. The last two cases 
-compose $ m_1 $ and $ m_2 $ with a helper function $ m \fatsemi^\ell m $, which 
-assumes its inputs have the same top constructor. The definition of $ m 
-\fatsemi^\ell m $ is straightforward. Going back to the last two cases of $ c_1 
-\fatsemi^\ell c_2 $. When $ c_2 $ starts with a projection, we have no clue 
-whether the target type of $ m_1 $ is the same as the source of $ m_2 $, 
-although we know they are shallowly consistent. So we give the $ l $ in the 
-projection to $ m \fatsemi^\ell m $. When $ c_2 $ starts with a no-op, we reuse 
-the $ \ell $.
-
-$ seq(c_1,c_2) $ requires that the target type of $ c_1 $ is the same as the 
-source of $ c_2 $. $ c \fatsemi^\ell c $ does the job for it.
-$ id(T) $ constructs an identity coercion of $ T $ with the help of $ id(P) $. 
+compose $m_1$ and $m_2$ with a helper function $m \fatsemi^\ell m$, which 
+assumes its inputs have the same top constructor. The definition of $m 
+\fatsemi^\ell m$ is straightforward. Going back to the last two cases of $c_1 
+\fatsemi^\ell c_2$. When $c_2$ starts with a projection, we have no clue 
+whether the target type of $m_1$ is the same as the source of $m_2$, 
+although we know they are shallowly consistent. So we give the $l$ in the 
+projection to $m \fatsemi^\ell m$. When $c_2$ starts with a no-op, we reuse 
+the $\ell$.
+
+$seq(c_1,c_2)$ requires that the target type of $c_1$ is the same as the 
+source of $c_2$. $c \fatsemi^\ell c$ does the job for it.
+$id(T)$ constructs an identity coercion of $T$ with the help of $id(P)$. 
 Their definitions are straightforward.
-$ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
-target type. $ c \fatsemi^\ell c $ does the most job.
+$cast(T_1,l,T_2)$ constructs a coercion from a source type, a label, and a 
+target type. $c \fatsemi^\ell c$ does the most job.
 
@@
 \begin{proposition}[]
-	For all $ T $ and $ l $, $ cast(T,l,T) = id(T) $
+	For all $T$ and $l$, $cast(T,l,T) = id(T) $
 \end{proposition}
@@
 \begin{figure}
-  Composition of hypercoercions \fbox{$ c \fatsemi c = c $}
+  Composition of hypercoercions \fbox{$c \fatsemi c = c$}
   \[
@@
 
-  \fbox{$ id( P ) = m $}
+  \fbox{$id( P ) = m$}
   \[
@@
 
-  \fbox{$ id( T ) = c $}
+  \fbox{$id( T ) = c$}
   \[
@@
 \begin{figure}
-  \fbox{$ \mathit{castToDyn}(P,l) = c$}
+  \fbox{$\mathit{castToDyn}(P,l) = c$}
   \[
@@
   \]
-  \fbox{$ \mathit{castFromDyn}(P,l) = c$}
+  \fbox{$\mathit{castFromDyn}(P,l) = c$}
   \[
@@
   \]
-  \fbox{$ \mathit{castToInj}(P,l,I) = m$}
+  \fbox{$\mathit{castToInj}(P,l,I) = m$}
   \[
@@
 
-  \fbox{$ \mathit{castFromInj}(I,l,P) = m$}
+  \fbox{$\mathit{castFromInj}(I,l,P) = m$}
   \[
@@
 
-  \fbox{$ cast(T,l,T) = c$}
+  \fbox{$cast(T,l,T) = c$}
   \[
@@
 
-The framework is a theorem saying that for all cast representation $ C
-$, if $ C $ satisfies a collection of properties, then it would
+The framework is a theorem saying that for all cast representation $C
+$, if $C$ satisfies a collection of properties, then it would
 respect the Lazy D semantics of cast calculi. We are working on a
@@
 
-%then instantiating our parameterized space-efficient interpreter with $ C $ 
+%then instantiating our parameterized space-efficient interpreter with$C$
 %gives an interpter that is extensionally equal to the standard interpreter for 
@@
 	\label{def:cast-rep}
-	A cast abstract data type is a set $Cast $, which is indexed by two types, 
+	A cast abstract data type is a set $Cast$, which is indexed by two types, 
 	with four operators:
 	\begin{description}
-		\item[$id(T) $] constructs an cast from a type
+		\item[$id(T)$] constructs an cast from a type
 %		, where $c : T 
 %		\Longrightarrow T $
-		\item[$seq(c_1,c_2) $] composes two casts
+		\item[$seq(c_1,c_2)$] composes two casts
 %		, where $
-%		\judgeTypeFT{c_1}{T_1}{T_2} $, $\judgeTypeFT{c_2}{T_2}{T_3} $, and $
+%		\judgeTypeFT{c_1}{T_1}{T_2}$, $\judgeTypeFT{c_2}{T_2}{T_3}$, and $
 %		\judgeTypeFT{c}{T_1}{T_3} $
-		\item[$cast(T_1,l,T_2) $] constructs a cast from $T_1$ to $T_2$
-		\item[$ applyCast(v,c)=r $] applies a cast onto a value
+		\item[$cast(T_1,l,T_2)$] constructs a cast from $T_1$ to $T_2$
+		\item[$ applyCast(v,c)=r$] applies a cast onto a value
 	\end{description}
-	We denote by $c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
-	T_1 \; T_2 $. And we say ``$ c $ is from $ T_1 $ to $ T_2 $''.
+	We denote by $c : T_1 \Longrightarrow T_2$ to mean $c$ is in $Cast \; 
+	T_1 \; T_2$. And we say ``$c$ is from $T_1$ to $T_2$''.
 \end{definition}
@@
 Cast ADT. Property (1) 
-states that $ id(T) $ acts like the identity function. Property (2) states 
-that $ seq(c,c) $ acts like a sequence of casts. Properties (3) through 
-(11) state that $ cast(T_1,l,T_2) $ act like the Lazy D $ applyCast $ 
+states that $id(T)$acts like the identity function. Property (2) states 
+that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
+(11) state that $cast(T_1,l,T_2)$act like the Lazy D$applyCast$
 defined in Fig.~\ref{fig:applyCast-D-C}.
@@
 	\begin{enumerate}
-		\item If $ v : T $, then $ applyCast(v,id(T)) = \mathtt{succ} \; v $
-		\item If $ \judgeType{v}{T_1} $,
-		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
-		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
-		then $ applyCast(v,seq(c_1,c_2)) = 
-		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2) $ \\
+		\item if $v : T$, then$applyCast(v,id(T)) = \mathtt{succ} \; v $
+		\item if $\judgeType{v}{T_1}$,
+		$ \judgeTypeFT{c_1}{T_1}{T_2}$, and
+		$ \judgeTypeFT{c_2}{T_2}{T_3}$,\\
+		then$applyCast(v,seq(c_1,c_2)) = 
+		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2)$\\
 		where 
@@
 		\]
-		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
-		then $ applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
-		\item If $ v : \star $, 
-		then $ applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
-		\item If $ v : P_1 $,
-		then $ applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
+		\item if $v : T_1$ and $\neg T_1 \smile T_2$,
+		then$applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
+		\item if $v : \star$, 
+		then$applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
+		\item if $v : P_1$,
+		then$applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
 		= applyCast(v,cast(P_1,l,P_2)) $
-		\item If $ v : P $,
-		then $ applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
-		\item If $ v : \POOunit $,
-		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
-		\item If $ (\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2} $,
+		\item if $v : P$,
+		then$applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		\item if $v : \POOunit$,
+		then$applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
+		\item if $(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2}$,
 		then\\
@@
 		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-		\item If $ (\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2} $,
+		\item if $(\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2}$,
 		then \\
@@
 		\times 
-		T_4)) $ \\
+		T_4))$\\
 		$ = 
@@
 		$ 
-		\item If $ (\hcvOOinl{v}{c}) : \POOsum{T_1}{T_2} $ ,
+		\item if $(\hcvOOinl{v}{c}) : \POOsum{T_1}{T_2}$,
 		then \\
@@
 		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
-		\item If $ (\hcvOOinr{v}{c}) : \POOsum{T_1}{T_2} $ ,
-		then \\ $ 
+		\item if $(\hcvOOinr{v}{c}) : \POOsum{T_1}{T_2}$,
+		then \\$
 		applyCast(\hcvOOinr{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
@@
 
-	Build continuation \fbox{$ cont(k) = \kappa $}
+	Build continuation \fbox{$cont(k) = \kappa$}
 	\[
@@
 
-	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
+	Extend continuation \fbox{$ext(c,\kappa) = \kappa$}
 	\[
@@
 
-	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
+	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
 	\[
@@
 	Apply continuation
-	\fbox{$ continue(k,v) = s $}
+	\fbox{$continue(k,v) = s$}
 	\[
@@
 
-%	Transitive closure of reduction \fbox{$ s \longrightarrow_{S(C)}^{*} s $}
+%	Transitive closure of reduction \fbox{$s \longrightarrow_{S(C)}^{*} s$}
 %	\[\dots\]
 
-%	Evaluation \fbox{$ \judgeSeval{C}{e}{o} $}
+%	Evaluation \fbox{$\judgeSeval{C}{e}{o}$}
 %	\[
@@
 
-	\caption{Space-efficient CEK machine $ \mathcal{S}(C) $}
+	\caption{Space-efficient CEK machine$\mathcal{S}(C)$}
 	\label{fig:machine-cekcc}
@@
 
-Let $ v $ range over value. 
+Let $v$ range over value. 
 In \ineffCEK\, we have one value constructor for all casted value.
 In \effCEK{C}, however, we do not have this generic value constructor, 
-instead we push those casts into the ordinary values. For instance, $ 
-(\vOOcons{v_1}{v_2}) $ corresponds to $ 
-(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)}) $. To construct values of the 
-dynamic type, we use $ (\hcvOOinj{P}{v}) $.
-
-Cast results ($ r $) and machine states ($ s $) are as before.
-
-Let $ \kappa $ range over continuations and let $ k $ range over 
+instead we push those casts into the ordinary values. For 
+instance, $(\vOOcons{v_1}{v_2})$ corresponds to 
+$(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$. To construct values of the 
+dynamic type, we use $(\hcvOOinj{P}{v})$.
+
+Cast results ($r$) and machine states ($s$) are as before.
+
+Let $\kappa$ range over continuations and Let $k$ range over 
 pre-continuations. 
@@
 And continuations in \ineffCEK\ that have many casts at the top correspond to 
-continuations in \effCEK{C}\ where those casts are composed by $ 
-seq(c,c) $.
+continuations in \effCEK{C}\ where those casts are composed by $seq(c,c)$.
 
@@
 When values are constructed, their hypercoercion parts are filled with outputs 
-of $ id $. For instance, when a function value is constructed, its first part 
-and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
+of $id$. For instance, when a function value is constructed, its first part 
+and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
 When evaluating a cast expression, the current continuation is extended with a 
-hypercoercion constructed by $ cast $. $ ext $ composes the new hypercoercion 
+hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
 with the hypercoercion on the top of the continuation.
@@
 hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
-expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
-the new pre-continuation, then call $ cont $, which adds an identity cast to 
+expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
+the new pre-continuation, then call $cont$, which adds an identity cast to 
 form a continuation. 
@@
 
-Transitive closure of reduction ($ \judgeSreduceTrans{C}{s}{s} $) and 
-evaluation ($ \judgeSeval{C}{e}{o} $) are standard. Value typing ($ 
-\judgeType{v}{T} $) is straightforward.
+Transitive closure of reduction ($\judgeSreduceTrans{C}{s}{s}$) and 
+evaluation ($\judgeSeval{C}{e}{o}$) are standard. Value typing 
+($\judgeType{v}{T}$) is straightforward.
 
@@
 
-In this subsection, we prove that if a instance of Cast ADT $ C $ is Lazy D and 
-is a monoid, then $ eval_\mathcal{D} = eval_{\mathcal{S}(C)} $. We proof this 
+In this subsection, we prove that if a instance of Cast ADT $C$ is Lazy D and 
+is a monoid, then $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this 
 theorem with a weak bisimulation between \ineffCEKD\ and 
@@
 
-And the relation between continuations is defined in terms of $ cont(k) $ and $ 
-ext(c,k) $: \begin{gather*}
+And the relation between continuations is defined in terms of $cont(k)$ and 
+$ext(c,k) $: \begin{gather*}
 \inference{
@@
 Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-introduce one more definition: $ s_1 \approx^{*} s_2 $ if and only if there 
-exists $ s_2' \in \text{\ineffCEKD} $ 
-such that $ \judgeCreduceTrans{s_2}{s_2'}$ and $ s_1 \approx s_2' $.
+introduce one more definition: $s_1 \approx^{*} s_2$ if and only if there 
+exists $s_2' \in \text{\ineffCEKD}$
+such that $\judgeCreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
 
@@
 	\label{thm:surely-monoidic-reduce}
-	For all instance of Cast ADT $ C $, 
-	if $ C $ is \lazyD{} and is a monoid, 
-	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
-	$ s_{2}, s_{2}' \in \text{\ineffCEKD} $,
-	$ s_{1} \approx s_{2} $,
-	$ \judgeSreduce{C}{s_{1}}{s_{1}'} $, and
-	$ \judgeDreduce{s_{2}}{s_{2}'} $, then
-%	then there exist $ s_2'' \in \text{\ineffCEKD} $ such that
+	For all instance of Cast ADT$C$, 
+	if $C$ is \lazyD{} and is a monoid, 
+	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
+	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
+	$ s_{1} \approx s_{2}$,
+	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
+	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
+%	then there exist$s_2'' \in \text{\ineffCEKD}$such that
 	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
@@
 %	\begin{enumerate}
-%		\item If $ \judgeDreduce{s_1}{s_3} $,
+%		\item if $\judgeDreduce{s_1}{s_3}$,
 %		then
-%		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
+%		there exist$s_5 \in \text{\ineffCEKD}$, $s_4 \in \mathcal{S}(C)$,
 %		such that \begin{itemize}
-%			\item $ s_5 \approx s_4 $, and
-%			\item $ \judgeSreduce{C}{s_2}{s_4} $,
-%			\item $ \judgeDreduceTrans{s_3}{s_5} $
+%			\item$s_5 \approx s_4$, and
+%			\item$\judgeSreduce{C}{s_2}{s_4}$,
+%			\item$\judgeDreduceTrans{s_3}{s_5} $
 %		\end{itemize}
-%		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
+%		\item if $\judgeSreduce{C}{s_2}{s_4}$,
 %		then
-%		there exist $ s_3 \in \mathcal{C} $,
+%		there exist$s_3 \in \mathcal{C}$,
 %		such that \begin{itemize}
-%			\item $ s_3 \approx s_4 $
-%			\item $ \judgeDreduceTrans{s_1}{s_3} $
+%			\item$s_3 \approx s_4 $
+%			\item$\judgeDreduceTrans{s_1}{s_3} $
 %		\end{itemize}
@@
 	\label{thm:surely-monoidic-eval}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
+	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
 	\lazyD{} Cast ADT and a monoid,
@@
 \begin{proof}Proving left implies right is trivial.
-To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
+To prove $\judgeDeval{e}{o}$ implies $\judgeSeval{C}{e}{o}$, 
 we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
@@
 
-In this subsection, we prove that for all $ C $, if $ C $ is a Lazy D Cast ADT, 
+In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast ADT, 
 then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
-prove that all $ S(C) $ where $ C $ is a Lazy D Cast ADT are equivalent, then 
+prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
 connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.
@@
 \todo[inline]{Standardize theorem statement -KC}
-\begin{lemma}[Strong Bisimulation among $ \mathcal{S}(\cdot) $]
+\begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
 	\label{thm:CEKS-bisim}
 	If 
-	$ C_1 $ and $ C_2 $ are instances of Lazy D Cast ADT,
-	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
-	$ s_1 \approx s_2 $,
-	$ \judgeSreduce{C_1}{s_1}{s_1'} $, and
-	$ \judgeSreduce{C_2}{s_2}{s_2'} $, then 
-	$ s_1' \approx s_2' $
+	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
+	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
+	$s_1 \approx s_2$,
+	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
+	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
+	$s_1' \approx s_2'$
 
@@
 	Lazy D Cast ADT, and handling all possibly uses of $
-	cast(T,l,T) $ with property (3)-(11).
+	cast(T,l,T)$ with property (3)-(11).
 \end{proof}
@@
 	\label{thm:surely-lazyD-eqv}
-	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
+	if $\judgetype{\emptyset}{e}{T}$, $o : T$, and $C_1$ and $C_2$
 	are \lazyD\ Cast ADTs,
@@
 	\label{thm:surely-lazyD-correct}
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
+	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
 	\lazyD{} Cast ADT.
@@
 	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
-	represent casts as a list of triples of type, label, and type, where $ 
-	id(T) $ is the empty list and $ seq(c,c) $ is the list append. Another such 
+	represent casts as a list of triples of type, label, and type, where 
+	$id(T)$ is the empty list and $seq(c,c)$ is the list append. Another such 
 	representation is the \lazyD\ hypercoercion!
@@
 In this section we prove \lazyD\ hypercoercion is 
-correct. First we define $ applyCast(v,c) $ to make it an instance of Cast ADT, 
+correct. First we define$applyCast(v,c)$ to make it an instance of Cast ADT, 
 then prove that it is also Lazy D, and finally apply 
@@
 
-\figref{hc-applyCast} defines $ applyCast(v,c) $ for \lazyD\ hypercoercion. 
+\figref{hc-applyCast} defines$applyCast(v,c)$for \lazyD\ hypercoercion. 
 Applying the identity cast for the 
 dynamic type succeeds immediately. When applying a compound cast, we firstly 
-apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
-that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
+apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
+that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise the result 
 is the failure.
-$ applyMiddle(v,\ell,m) $ and $ applyTail(v,t) $ are straightforward.
-In the definition of $ applyMiddle(v,\ell,m) $, we generalize 
-shallow-consistency to compare middles and values ($ v \smile m $) in the 
+$ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
+In the definition of $applyMiddle(v,\ell,m)$, we generalize 
+shallow-consistency to compare middles and values ($v \smile m$) in the 
 natural way.
@@
 \begin{figure}
-	\fbox{$ applyCast(v,c) = r $}
+	\fbox{$applyCast(v,c) = r$}
 	\[
@@
 
-	\fbox{$ applyMiddle(v,\ell,m) = r $}
+	\fbox{$applyMiddle(v,\ell,m) = r$}
 	\[
@@
 
-	\fbox{$ applyTail(v,t) = r $}
+	\fbox{$applyTail(v,t) = r$}
 	\[
@@
 	\]
-	\caption{\lazyD\ hypercoercion's $ applyCast $}
+	\caption{\lazyD\ hypercoercion's $applyCast$}
 	\label{hc-applyCast}
@@
 \begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
-	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
+	if $\judgetype{\emptyset}{e}{T}$ and $o : T$
 	\[

### 2019-10-21 paper.tex
more on notations
use macro
fill in all rules in S(C)

@@
 
-\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #2(#1) \; #3}
-\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
+\newcommand{\sOOinspect}[3]{\langle\langle#1,#2\rangle,#3\rangle}
+\newcommand{\sOOreturn}[2]{\langle#1,#2\rangle}
 \newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
@@
 \newcommand{\kOOmt}[0]{\square}
-\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; #2(#1) ]}
+\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]}
 \newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
@@
 \newcommand{\kOOappI}[3]{
-	#3[\square \; #2(#1) ]
+	#3[\square \; \langle#1,#2\rangle ]
 }
@@
 \newcommand{\kOOcaseI}[4]{
-	#4[\mathtt{case} \; \square \; #3(#1) \; #3(#2) ]}
+	#4[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]}
 \newcommand{\kOOcaseII}[4]{
-	#4[\mathtt{case} \; #1 \; \square \; #3(#2) ]}
+	#4[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]}
 \newcommand{\kOOcaseIII}[3]{
@@
 \newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
-\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
+%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
+\newcommand{\hcvOOfun}[5]{\mathtt{fun}^{\POOfun{#1}{#5}} \; #2 \; #3 \; #4}
 \newcommand{\hcvOOtt}[0]{\mathtt{unit}}
-\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
-\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
-\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
+%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
+\newcommand{\hcvOOcons}[4]{\mathtt{cons}^{\POOprod{#2}{#4}}\;#1\;#3}
+%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
+%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
+\newcommand{\hcvOOinl}[2]{\mathtt{inl}^{#2}\;#1}
+\newcommand{\hcvOOinr}[2]{\mathtt{inr}^{#2}\;#1}
 \newcommand{\hckOOmt}[0]{\mathtt{stop}}
@@
 %
-In case splitting, if the target value is a left injection, the
-machine moves to a state that will apply the first continuation
-function to the value inside the left injection. The case for right
-injection is similar.
+%In case splitting, if the target value is a left injection, the
+%machine moves to a state that will apply the first continuation
+%function to the value inside the left injection. The case for right
+%injection is similar.
 %
@@
 \redrule{
-	\highlight{\sOOreturn{v_3}{(\mathtt{case_3}\;
-		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
-		\;v_2\;\kappa)}}
+	\highlight{\sOOreturn{v_3}{
+		(	\kOOcaseIII{
+				\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+			}{v_2}{\kappa})
+%		
+%			(\mathtt{case_3}\;
+%		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
+%		\;v_2\;\kappa)
+	}}
 }{
 	\highlight{\sOOreturn{v_3'}{
-		(\mathtt{case_3}\;v
-		\;v_2'\;\kappa)
+			(\kOOcaseIII{v}{v_2'}{\kappa})
 	}}
@@
 that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
-(11) state that $cast(T_1,l,T_2)$act like the Lazy D$applyCast$
+(11) state that $cast(T_1,l,T_2)$act like the Lazy D $applyCast$
 defined in Fig.~\ref{fig:applyCast-D-C}.
@@
 }{}
+
+\hifunrule{
+	\continue{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{
+		\kOOcar{\kappa}
+	}
+}{
+	\sOOreturn{v_1}{ext(c_1,k)}
+}{}
+\hifunrule{
+	\continue{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{
+		\kOOcdr{\kappa}
+	}
+}{
+	\sOOreturn{v_2}{ext(c_2,k)}
+}{}
+
+\funrule{
+	\continue{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}
+}{
+	\sOOinspect{e_2}{\rho}{
+		cont(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
+	}
+}{}
+
+\funrule{
+	\continue{v_2}{
+		\kOOcaseII{v_1}{e_3}{\rho}{\kappa}
+	}
+}{
+	\sOOinspect{e_3}{\rho}{
+	\kOOcaseIII{v_1}{v_2}{\kappa}
+	}
+}{}
+
 \hifunrule{
@@
 We list a fraction of reduction rules due to space limitation.
-\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS}
-When values are constructed, their hypercoercion parts are filled with outputs 
-of $id$. For instance, when a function value is constructed, its first part 
-and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
-When evaluating a cast expression, the current continuation is extended with a 
-hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
-with the hypercoercion on the top of the continuation.
-When evaluating a compound expression, the machine firstly construct the new 
-pre-continuation, then turn it to a continuation by adding an identity 
-hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
-expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
-the new pre-continuation, then call $cont$, which adds an identity cast to 
-form a continuation. 
-When a function call happens, the machine firstly cast the operand. If the 
-casting succeeds, the machine then evaluate the body in the extended 
-environment and the extended continuation. If the casting fails, the machine 
-then halts with the blame label.
+\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS
+\\---\\They are all in the figure. I haven't updated this paragraph 
+accordingly. -KC}
+
+%When evaluating a cast expression, the machine moves the cast to the
+%continuation and evaluates the inner expression.
+%To apply a casted function, the machine first casts $v_1$, the
+%operand, then applies the casted operand to $v_2$, the underlying
+%function, and finally cast the result of the function application.
+%%
+%To take out the first (resp. second) part of a casted pair, the
+%machine firstly take out the first (resp. second) part of $v$, the
+%underlying pair, and cast the result.
+%%
+%%In case splitting, if the target value is a left injection, the
+%%machine moves to a state that will apply the first continuation
+%%function to the value inside the left injection. The case for right
+%%injection is similar.
+%%
+%When the target value is a casted sum, the machine moves the cast from
+%the target value to continuations functions.
+%%
+%To cast a value, the machine invokes $applyCast$ on the value.  If the
+%cast succeeds, the machine returns the result to the next
+%continuation.  If the cast fails, the machine halts with the blame
+%label.
+
+The transition relation $\judgeSreduce{C}{s}{s}$ uses functions provides by $C$ 
+to represent cases and to apply casts.
+%
+When evaluating a cast expression, the machine extends the continuation with 
+cast $cast(T_1,l,T_2)$. The function $ext(c,\kappa)$ composes $c$ with the cast 
+at the top of $k$ by calling $seq$.
+%
+To construct a function, the machine fills the casts $id$.
+%
+To return a value to a continuation, the machine first applies the top cast to 
+the value. If the application fails, the machine halts with the blame label 
+from the failure. Otherwise, the machine handles the pre-continuation with 
+$continue$.
+%
+When the machine constructs a pair, a left injection, or a right injection, it 
+fills the casts with $id$ as well, just like how it did for functions. 
+%
+To apply a function, the machine applies the domain cast $c_1$ to the 
+operand $v_2$, extends the continuation with the codomain cast $c_2$, and 
+evaluate the function body.
+%
+To take out the first (resp. second) part of a pair ...
+%
+%%In case splitting, if the target value is a left injection, the
+%%machine moves to a state that will apply the first continuation
+%%function to the value inside the left injection. The case for right
+%%injection is similar.
+%%
+%When the target value is a casted sum, the machine moves the cast from
+%the target value to continuations functions.
+To case spliting a variant, ...
+
+%When values are constructed, their hypercoercion parts are filled with outputs 
+%of $id$. For instance, when a function value is constructed, its first part 
+%and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
+%When evaluating a cast expression, the current continuation is extended with a 
+%hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
+%with the hypercoercion on the top of the continuation.
+%When evaluating a compound expression, the machine firstly construct the new 
+%pre-continuation, then turn it to a continuation by adding an identity 
+%hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
+%expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
+%the new pre-continuation, then call $cont$, which adds an identity cast to 
+%form a continuation. 
+%When a function call happens, the machine firstly cast the operand. If the 
+%casting succeeds, the machine then evaluate the body in the extended 
+%environment and the extended continuation. If the casting fails, the machine 
+%then halts with the blame label.
 

### 2019-10-21 paper.tex
one more para in 4.0

@@
 
+If $C$, an implementation of the Cast ADT inteface, satisifies a collection of 
+properties that we defined as Lazy D Cast ADT. We can instantiate our framework 
+theorem that we define shortly to prove that evaluating an program in 
+\effCEK{C} gives the same result as \ineffCEKD. We are working on a
+similar theorem for \lazyUD{}.
+
+\todo[inline]{UNDER CONSTRUCTION. -KC}
+
 The framework is a theorem saying that for all cast representation $C
@@
 with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
-The first three operators allow a language implementation to construct casts. 
+The first three operators allow \effCEK{C} to construct casts. 
 So we call them \textit{cast constructors}. And the forth and last operator 
-allows the implementation to apply casts onto values.
+allows \effCEK{C} to apply casts onto values.
 

### 2019-10-21 paper.tex
minor changes

@@
 Cast ADT. Property (1) 
-states that $id(T)$acts like the identity function. Property (2) states 
-that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
-(11) state that $cast(T_1,l,T_2)$act like the Lazy D $applyCast$
-defined in Fig.~\ref{fig:applyCast-D-C}.
-
-\todoKC{define values before Lazy D Cast ADT}
+states that $id(T)$ acts like the identity function. Property (2) states 
+that $seq(c,c)$ acts like a sequence of casts. Properties (3) through 
+(11) state that $cast(T_1,l,T_2)$ act like the Lazy D $applyCast$
+(Fig.~\ref{fig:applyCast-D-C}).
+
+\todo[inline]{We might need to values before Lazy D Cast ADT.}
 

### 2019-10-21 paper.tex
mimic CEK syntax in PL&LambdaCalculi
bisim relation for SC and D

@@
 
-\newcommand{\kOOmt}[0]{\square}
-\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]}
-\newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
-\newcommand{\kOOinl}[1]{#1[\mathtt{inl} \; \square]}
-\newcommand{\kOOinr}[1]{#1[\mathtt{inr} \; \square]}
+\newcommand{\kOOmt}[0]{\mathtt{stop}}
+\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
+\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
+\newcommand{\kOOinl}[1]{[\mathtt{inl} \; \square]#1}
+\newcommand{\kOOinr}[1]{[\mathtt{inr} \; \square]#1}
 \newcommand{\kOOappI}[3]{
-	#3[\square \; \langle#1,#2\rangle ]
+	[\square \; \langle#1,#2\rangle ]#3
 }
 \newcommand{\kOOappII}[2]{
-	#2[#1 \; \square]}
-\newcommand{\kOOcar}[1]{#1[\mathtt{fst} \; \square]}
-\newcommand{\kOOcdr}[1]{#1[\mathtt{snd} \; \square]}
+	[#1 \; \square]#2}
+\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
+\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
 \newcommand{\kOOcaseI}[4]{
-	#4[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]}
+	[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
 \newcommand{\kOOcaseII}[4]{
-	#4[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]}
+	[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
 \newcommand{\kOOcaseIII}[3]{
-	#3[\mathtt{case} \; #1 \; #2 \; \square]}
+	[\mathtt{case} \; #1 \; #2 \; \square]#3}
 \newcommand{\kOOcast}[2]{
-	#2[\square \langle #1 \rangle]}
+	[\square \langle #1 \rangle]#2}
 
@@
 %\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
-\newcommand{\hcvOOfun}[5]{\mathtt{fun}^{\POOfun{#1}{#5}} \; #2 \; #3 \; #4}
+\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
 \newcommand{\hcvOOtt}[0]{\mathtt{unit}}
 %\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
-\newcommand{\hcvOOcons}[4]{\mathtt{cons}^{\POOprod{#2}{#4}}\;#1\;#3}
+\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
 %\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
 %\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
-\newcommand{\hcvOOinl}[2]{\mathtt{inl}^{#2}\;#1}
-\newcommand{\hcvOOinr}[2]{\mathtt{inr}^{#2}\;#1}
+\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
+\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
 \newcommand{\hckOOmt}[0]{\mathtt{stop}}
@@
 	\stxrule{\kappa}{continuation}{
-		\langle c \rangle k
+		\kOOcast{c}{k}
 	}
 	\stxrule{k}{pre-continuations}{
-		\hckOOmt \mid{}
-		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{cons_2} \; v \; \kappa \mid{}
-		\mathtt{inl} \; \kappa \mid{}
-		\mathtt{inr} \; \kappa
+		\kOOmt \mid{}
+		\kOOconsI{e}{\rho}{\kappa} \mid
+		\kOOconsII{v}{\kappa} \mid
+		\kOOinl{\kappa} \mid
+		\kOOinr{\kappa}
 	}
 	\stxrulecont{
-		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
-		\mathtt{app_2} \; v \; \kappa \mid{}
-		\mathtt{fst} \; \kappa \mid{}
-		\mathtt{snd} \; \kappa
+		\kOOappI{e}{\rho}{\kappa} \mid
+		\kOOappII{v}{\kappa} \mid
+		\kOOcar{\kappa} \mid
+		\kOOcdr{\kappa}
 	}
 	\stxrulecont{
-		\mathtt{case_1} \; e \; e \; \rho \; \kappa \mid
-		\mathtt{case_2} \; v \; e \; \rho \; \kappa \mid{}
-		\mathtt{case_3} \; v \; v \; \rho \; \kappa
+		\kOOcaseI{e}{e}{\rho}{\kappa} \mid
+		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
+		\kOOcaseIII{v}{v}{\kappa}
 	}
@@
 	\begin{array}{rclc}
-	\funrule{cont(k)}{\langle id(T_1) \rangle k}{
+	\funrule{cont(k)}{\kOOcast{id(T_1)}{k}}{
 		\sidecond{k : T_1 \Longrightarrow T_2}}
@@
 	\begin{array}{rclc}
-	\funrule{ext(c_1,\langle c_2 \rangle k)}{\langle seq(c_1,c_2) \rangle k}{}
+	\funrule{ext(c_1,\kOOcast{c_2}{k})}{
+		\kOOcast{seq(c_1,c_2)}{k}
+	}{}
 	\end{array}
@@
 		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
-		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
+		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
 	\hiredruleS{
-		\sOOreturn{v}{\langle c \rangle k}
+		\sOOreturn{v}{\kOOcast{c}{k}}
 	}{
@@
 
-\subsection{\lazyD\ Cast ADTs Respect \ineffCEKD\ if They are 
-Monoids}
+\subsection{Relating Some \effCEK{C} to \ineffCEKD}
 \label{secc:framework:monoid-correct}
@@
 is a monoid, then $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this 
-theorem with a weak bisimulation between \ineffCEKD\ and 
-\effCEK{C}.
+theorem with a weak bisimulation between \effCEK{C} and \ineffCEKD.
+
+Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
+that make the relation a congruence.
+
+\begin{figure}
+	\fbox{$\text{\effCEK{C}} \approx \text{\ineffCEKD}$}
+	\[\dots\]
+
+	\fbox{$\kappa \approx \kappa$}
+	\begin{gather*}
+	\inference{
+		k \approx \kappa
+	}{
+		cont(k) \approx \kappa
+	}
+	\quad
+	\inference{
+		\kappa_1 \approx \kappa_2
+	}{
+		ext(cast(T_1,l,T_2),\kappa_1) \approx 
+		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
+	}
+	\end{gather*}
+
+	\fbox{$v \approx v$}
+	\begin{gather}
+	\inference{
+		v_1 \approx v_2 &
+		v_2 : P
+	}{
+		\hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
+	}
+	\quad
+	\inference{}{
+		\hcvOOtt \approx \vOOtt
+	}
+	\quad
+	\inference{}{
+		\hcvOOtt \approx \vOOcast{\vOOtt}{\cOOcast{\POOunit}{l}{\POOunit}}
+	}
+	\\
+	\inference{
+		\rho_1 \approx \rho_2 &
+		dom(\rho_1) = dom(\rho_2) = \Gamma \\
+		\Gamma , x : T_1 \vdash e : T_2
+	}{
+		\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)}
+		\approx
+		\vOOfun{\rho_2}{x}{e}
+	}
+	\quad
+	\inference{
+		v_1 \approx v_2 & v_3 \approx v_4 &
+		\judgeType{v_1}{T_1} &
+		\judgeType{v_3}{T_2}
+	}{
+		\hcvOOcons{v_1}{id(T_1)}{v_3}{id(T_2)}
+		\approx
+		\vOOcons{v_2}{v_3}
+	}
+	\\
+	\inference{
+		\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 \\
+%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
+		\judgeType{v_2}{\POOfun{T_1}{T_2}} \\
+		c_1' = seq(cast(T_3,l,T1),c_1) \\
+		c_2' = seq(c_2,cast(T_2,l,T_4))
+	}{
+		\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
+		\approx
+		\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
+	}
+	\quad
+	\inference{
+		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 \\
+		\judgeType{v_2}{\POOprod{T_1}{T_2}} \\
+		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
+		c_2' = seq(c_2,cast(T_2,l,T_4))
+	}{
+		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
+		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
+	}
+	\\
+	\inference{
+		v_1 \approx v_2 & v_1 : T
+	}{
+		\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
+	}
+	\quad
+	\inference{
+		\hcvOOinl{v_1}{c} \approx v_2 &
+		v_2 : \POOsum{T_1}{T_2} &
+		c' = seq(c,cast(T_1,l,T_3))
+	}{
+		\hcvOOinl{v_1}{c'} \approx
+		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+	}
+	\\
+	\inference{
+	v_1 \approx v_2 & v_1 : T
+	}{
+	\hcvOOinr{v_1}{id(T)} \approx \vOOinr{v_2}
+	}
+	\quad
+	\inference{
+	\hcvOOinr{v_1}{c} \approx v_2 &
+	v_2 : \POOsum{T_1}{T_2} &
+	c' = seq(c,cast(T_2,l,T_4))
+	}{
+	\hcvOOinr{v_1}{c'} \approx
+	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+	}
+	\end{gather}
+	\caption{Bisimulation between \effCEK{C} and \ineffCEKD}
+	\label{fig:bisim-SC-D}
+\end{figure}
 
@@
 }
-\quad
+\\
 \inference{
@@
 	\label{thm:surely-monoidic-reduce}
-	For all instance of Cast ADT$C$, 
-	if $C$ is \lazyD{} and is a monoid, 
+	For all instance of Cast ADT $C$, 
+	if $C$ is \lazyD{} and is a monoid and $cast(T,l,T)=id(T)$,
 	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,

### 2019-10-21 paper.tex
one the way to describe S(C) relates to D

@@
 \newcommand{\kOOappI}[3]{
-	[\square \; \langle#1,#2\rangle ]#3
+	[\mathtt{app} \; \square \; \langle#1,#2\rangle ]#3
 }
 \newcommand{\kOOappII}[2]{
-	[#1 \; \square]#2}
+	[\mathtt{app} \; #1 \; \square]#2}
 \newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
@@
 \newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
-\newcommand{\continue}[2]{continue(#2,#1)}
+\newcommand{\continue}[2]{cont(#2,#1)}
 \newcommand{\highlight}[1]{{\color{red} #1}}
@@
 	\inference{
-		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{B}^{*} 
+		\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)} \longrightarrow_{B}^{*} 
 		\sOOhalt{o}
@@
 
-\todo[inline]{We might need to values before Lazy D Cast ADT.}
+\todo[inline]{We might need to values before Lazy D Cast ADT. This will reduce 
+the extreme height of Fig.~\ref{fig:machine-cekcc} as well. -KC}
 
@@
 
-	Build continuation \fbox{$cont(k) = \kappa$}
+	Build continuation \fbox{$wrap(k) = \kappa$}
 	\[
 	\begin{array}{rclc}
-	\funrule{cont(k)}{\kOOcast{id(T_1)}{k}}{
+	\funrule{wrap(k)}{\kOOcast{id(T_1)}{k}}{
 		\sidecond{k : T_1 \Longrightarrow T_2}}
@@
 	}{
-		\sOOinspect{e}{\rho}{cont(\kOOinl{\kappa})}
+		\sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
 	}{}
@@
 	}{
-		\sOOinspect{e}{\rho}{cont(\kOOinr{\kappa})}
+		\sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
 	}{}
@@
 	}{
-		\sOOinspect{e_1}{\rho}{cont(\kOOappI{E}{e_2}{\kappa})}}{}
+		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{E}{e_2}{\kappa})}}{}
 
@@
 		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
-		\sOOinspect{e}{\rho}{cont(\kOOcar{\kappa})}}{}
+		\sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}
 
@@
 		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
-		\sOOinspect{e}{\rho}{cont(\kOOcdr{\kappa})}}{}
+		\sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}
 
@@
 		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
-		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
+		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
 	\hiredruleS{
@@
 	\begin{cases}
-	continue(k,v') & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
+	\continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
 	\\
@@
 %	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
-%	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
+%	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
 %
@@
 %\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
-%\sOOinspect{e_2}{\rho}{cont(\kOOappII{v_1}{\kappa})}}{}
+%\sOOinspect{e_2}{\rho}{wrap(\kOOappII{v_1}{\kappa})}}{}
 %
@@
 %	}{
-%		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
+%		\sOOinspect{e_1}{\rho}{wrap(\hckOOconsI{e_2}{\rho}{\kappa})}
 %	}{}
@@
 	\continue{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
-	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
+	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
 
@@
 	\sOOinspect{e_2}{\rho}{
-		cont(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
+		wrap(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
 	}
@@
 }{
-	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
+	\sOOreturn{v}{wrap(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
 }{}
@@
 %		\judgeSreduceTrans{C}{
-%			\sOOinspect{e}{\emptyset}{cont(\hckOOmt)}
+%			\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)}
 %		}{
@@
 that make the relation a congruence.
+%
+There are two cases where a continuation in \effCEK{C} relates to a 
+continuation in \ineffCEKD. When $k \approx \kappa$, adding an identity cast on 
+top of $k$ gives a related continuation. When $\kappa_1 \approx \kappa_2$, 
+extending $\kappa_1$ and $\kappa_2$ with the same cast gives related results.
+%
+As for $v \approx v$, there is one rule for the dynamic type, and two rules for 
+each ordinary value constructor.
+
+And continuations in \ineffCEK\ that have many casts at the top correspond to 
+continuations in \effCEK{C}\ where those casts are composed by $seq(c,c)$.
 
@@
 	}{
-		cont(k) \approx \kappa
+		wrap(k) \approx \kappa
 	}
@@
 
-And the relation between continuations is defined in terms of $cont(k)$ and 
+And the relation between continuations is defined in terms of $wrap(k)$ and 
 $ext(c,k) $: \begin{gather*}
@@
 }{
-	cont(k) \approx \kappa
+	wrap(k) \approx \kappa
 }

### 2019-10-21 paper.tex
describ bisim

@@
 %
-There are two cases where a continuation in \effCEK{C} relates to a 
-continuation in \ineffCEKD. When $k \approx \kappa$, adding an identity cast on 
-top of $k$ gives a related continuation. When $\kappa_1 \approx \kappa_2$, 
-extending $\kappa_1$ and $\kappa_2$ with the same cast gives related results.
-%
-As for $v \approx v$, there is one rule for the dynamic type, and two rules for 
-each ordinary value constructor.
-
-And continuations in \ineffCEK\ that have many casts at the top correspond to 
-continuations in \effCEK{C}\ where those casts are composed by $seq(c,c)$.
-
+The relation $\kappa \approx \kappa$ relates two continuations. 
+%
+If $k \approx \kappa$, adding an identity cast on top of $k$ gives a related 
+continuation. 
+%
+If $\kappa_1 \approx \kappa_2$, extending $\kappa_1$ and $\kappa_2$ with the 
+same cast gives related results.
+%
+%
+The relation $v \approx v : T$ relates two value and also report their type. We 
+will see shortly why reporting the type. 
+%
+If two values of type $P$ are related, injecting them to $\TOOdyn$ gives 
+related values.
+%
+Unit values are of course related.
+%
+To relate to a non-casted function in \ineffCEKD, the casts in the \effCEK{C} 
+function must be identity.
+%
+If functions are related, we can apply the same cast on both side.
+
+\todo[inline]{In Fig.~\ref{fig:bisim-SC-D}, how to suppress rule numbers like 
+(1), (2), etc.? -KC}
 \begin{figure}
-	\fbox{$\text{\effCEK{C}} \approx \text{\ineffCEKD}$}
+%	\fbox{$\text{\effCEK{C}} \approx \text{\ineffCEKD}$}
 	\[\dots\]
@@
 	}
+\\
 	\end{gather*}
-
-	\fbox{$v \approx v$}
+\\	
+	\fbox{$v \approx v : T$}
 	\begin{gather}
 	\inference{
-		v_1 \approx v_2 &
-		v_2 : P
+		v_1 \approx v_2 : P
 	}{
 		\hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
-	}
-	\quad
+		: \TOOdyn
+	}
+\\ \\
 	\inference{}{
-		\hcvOOtt \approx \vOOtt
+		\hcvOOtt \approx \vOOtt : \POOunit
 	}
@@
 		\hcvOOtt \approx \vOOcast{\vOOtt}{\cOOcast{\POOunit}{l}{\POOunit}}
-	}
-	\\
+		: \POOunit
+	}
+	\\ \\
 	\inference{
@@
 		\vOOfun{\rho_2}{x}{e}
-	}
-	\quad
+		: \POOfun{T_1}{T_2}
+	}
+\\ \\
 \inference{
-		v_1 \approx v_2 & v_3 \approx v_4 &
-		\judgeType{v_1}{T_1} &
-		\judgeType{v_3}{T_2}
+\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
+%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
+c_1' = seq(cast(T_3,l,T_1),c_1) \\
+c_2' = seq(c_2,cast(T_2,l,T_4))
+}{
+\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
+\approx
+\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
+: \POOfun{T_3}{T_4}
+}
+\\ \\
+	\inference{
+		v_1 \approx v_2 : T_1 &
+		v_3 \approx v_4 : T_2 &
 	}{
@@
 		\vOOcons{v_2}{v_3}
+		: \POOprod{T_1}{T_2}
+	}
+\\ \\
+	\inference{
+		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOsum{T_1}{T_2} \\
+		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
+		c_2' = seq(c_2,cast(T_2,l,T_4))
+	}{
+		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
+		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
+		: \POOprod{T_3}{T_4}
+	}
+\\ \\
+	\inference{
+		v_1 \approx v_2 : T
+	}{
+		\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
+		: \POOsum{T}{T'}
+	}
+	\quad
+	\inference{
+		\hcvOOinl{v_1}{c} \approx v_2
+		: \POOsum{T_1}{T_2} &
+		c' = seq(c,cast(T_1,l,T_3))
+	}{
+		\hcvOOinl{v_1}{c'} \approx
+		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+		: \POOsum{T}{T'}	
 	}
@@
 	\inference{
-		\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 \\
-%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
-		\judgeType{v_2}{\POOfun{T_1}{T_2}} \\
-		c_1' = seq(cast(T_3,l,T1),c_1) \\
-		c_2' = seq(c_2,cast(T_2,l,T_4))
-	}{
-		\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
-		\approx
-		\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
+	v_1 \approx v_2 : T
+	}{
+	\hcvOOinr{v_1}{id(T)} \approx \vOOinr{v_2}
+	: \POOsum{T'}{T}
 	}
@@
 	\inference{
-		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 \\
-		\judgeType{v_2}{\POOprod{T_1}{T_2}} \\
-		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
-		c_2' = seq(c_2,cast(T_2,l,T_4))
-	}{
-		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
-		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
-	}
-	\\
-	\inference{
-		v_1 \approx v_2 & v_1 : T
-	}{
-		\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
-	}
-	\quad
-	\inference{
-		\hcvOOinl{v_1}{c} \approx v_2 &
-		v_2 : \POOsum{T_1}{T_2} &
-		c' = seq(c,cast(T_1,l,T_3))
-	}{
-		\hcvOOinl{v_1}{c'} \approx
-		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
-	}
-	\\
-	\inference{
-	v_1 \approx v_2 & v_1 : T
-	}{
-	\hcvOOinr{v_1}{id(T)} \approx \vOOinr{v_2}
-	}
-	\quad
-	\inference{
-	\hcvOOinr{v_1}{c} \approx v_2 &
-	v_2 : \POOsum{T_1}{T_2} &
+	\hcvOOinr{v_1}{c} \approx v_2
+	: \POOsum{T_1}{T_2} &
 	c' = seq(c,cast(T_2,l,T_4))
@@
 	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+	: \POOsum{T'}{T}
 	}
@@
 \end{figure}
-
-The bisimulation relation between states ($\eqvSD{C}{s}{s}$) is mostly derived 
-from the state definition: \begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2 &
-	v_1 \approx v_2
-}{
-	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
-}
-\quad
-\inference{
-}{
-	\sOOhalt{o} \approx \sOOhalt{o}
-}
-\end{gather*}
-
-The bisimulation relation between environments and cast results are derived 
-from their definitions as well. And the relation from continuations in 
-\ineffCEKD\ and the pre-continuation in \effCEK{C} is in the natural way, for 
-example: \begin{gather*}
-\inference{
-	\rho_1 \approx \rho_2 &
-	\kappa_1 \approx \kappa_2
-}{
-	\kOOconsI{e}{\rho_1}{\kappa_1} \approx \kOOconsI{e}{\rho_2}{\kappa_2}
-}
-\end{gather*}
-
-And the relation between continuations is defined in terms of $wrap(k)$ and 
-$ext(c,k) $: \begin{gather*}
-\inference{
-	k \approx \kappa
-}{
-	wrap(k) \approx \kappa
-}
-\quad
-\inference{
-	\kappa_1 \approx \kappa_2
-}{
-	ext(cast(T_1,l,T_2),\kappa_1)
-	\approx
-	\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2} 
-}
-\end{gather*}
-
-The relation between values is more special. When the \ineffCEKD\ value is 
-non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
-the cast into the value constructors, except injections. For examples: 
-\begin{gather*}
-\inference{
-	v_1, v_2 : P &
-	v_1 \approx v_2
-}{
-	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
-}
-\quad
-\inference{
-	v_1, v_2 : T &
-	v_1 \approx v_2
-}{
-	\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
-}
-\\
-\inference{
-	(\hcvOOinl{v}{c}, v_2) : \POOsum{T_1}{T_2}
-}{
-	\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))} \approx 
-	\vOOcast{v_2}{\cOOcast{T_1}{l}{T_3}}
-}
-%\quad
-%\inference{
-%	\Gamma , x : T_1 \vdash T_2 &
-%	\rho_1 \approx \rho_2
-%}{
-%	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
-%}
-%\quad
-%\inference{
-%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
-%	\approx
-%	v
-%}{
-%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
-%}
-%\\
-%\inference{
-%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
-%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
-%}{
-%	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
-%	\approx
-%	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
-%}
-\end{gather*}
 

### 2019-10-21 paper.tex
fix typos in fig11
a little progress

--- 2019-10-21 paper.tex
@@
 This section presents our second contribution, a framework for proving
-correctness of cast representations. The next section will apply this
+correctness of cast representations, especially space efficient
+ones. Section~\ref{sec:hypercoercion-correctness} will apply this
 framework to prove the correctness of the \lazyD{} hypercoercions.
@@
 by an abstract data type, named Cast ADT, that we define shortly.
-%
-
-\todo[inline]{UNDER CONSTRUCTION. -JS}
-
-If $C$, an implementation of the Cast ADT inteface, satisifies a collection of 
-properties that we defined as Lazy D Cast ADT. We can instantiate our framework 
-theorem that we define shortly to prove that evaluating an program in 
-\effCEK{C} gives the same result as \ineffCEKD. We are working on a
-similar theorem for \lazyUD{}.
-
-\todo[inline]{UNDER CONSTRUCTION. -KC}
-
-The framework is a theorem saying that for all cast representation $C
-$, if $C$ satisfies a collection of properties, then it would
-respect the Lazy D semantics of cast calculi. We are working on a
-similar theorem for \lazyUD{}.
-
-%then instantiating our parameterized space-efficient interpreter with$C$
-%gives an interpter that is extensionally equal to the standard interpreter for 
-%\lazyD\ cast calculus.
+
+When then prove that, for any instance $C$ of the Cast ADT, \effCEK{C}
+is equivelent to \ineffCEKD{] provided that $C$ satisfies a collection
+of properties that we call the Lazy D Cast abstract data type.
+In Section~\ref{sec:hypercoercion-correctness} we show that
+the \lazyD{} hypercoercions $H$ are an instance of the Lazy D ADT,
+and therefore \effCEK{H} is equivalent to \ineffCEKD{}.
+
+We are working on a similar theorem for \lazyUD{}.
+
+\todo[inline]{UNDER CONSTRUCTION -JS}
 

### 2019-10-21 paper.tex

--- 2019-10-21 paper.tex
@@
 	}{
-		\sOOinspect{e_1}{E}{}
+		\sOOinspect{e_1}{\rho}{
+			wrap(\kOOconsI{e_2}{\rho}{\kappa})
+		}
 	}{}
@@
 	}{
-		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{E}{e_2}{\kappa})}}{}
+		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}
 
@@
 		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
-		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
+		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
 	\hiredruleS{
@@
 	}{}
-%\redruleS{
-%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
-%	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
-%
-%\redrule{
-%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
-%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
-%\\&&
-%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
-%
-%\redrule{
-%\sOOreturn{v}{(\kOOinl{\kappa})}}{
-%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
-%\\&&
-%\sidecond{v : T}}
-%
-%\redrule{
-%\sOOreturn{v}{(\kOOinr{\kappa})}}{
-%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
-%\\&&
-%\sidecond{v : T}}
-%
-%\redrule{
-%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
-%\sOOinspect{e_2}{\rho}{wrap(\kOOappII{v_1}{\kappa})}}{}
-%
-%	
-%	& \vdots \\
-%	\redruleS{
-%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
-%	}{
-%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
-%	}{}
-%	\redruleS{
-%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-%	}{
-%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
-%	}{}
-%	\redruleS{
-%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
-%	}{
-%		\sOOinspect{e_1}{\rho}{wrap(\hckOOconsI{e_2}{\rho}{\kappa})}
-%	}{}
-%	\redruleS{
-%		
-%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
-%	}{
-%		\begin{cases}
-%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
-%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
-%		\\
-%		\sOOhalt{(\oOOblame{l})} \\
-%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
-%		\end{cases}
-%		
-%	}{}
 	\end{array}
@@
 If functions are related, we can apply the same cast on both side.
+%
+Rules for products and sums are similar.
 

### 2019-10-21 paper.tex
check

@@
 
-When then prove that, for any instance $C$ of the Cast ADT, \effCEK{C}
-is equivelent to \ineffCEKD{] provided that $C$ satisfies a collection
-of properties that we call the Lazy D Cast abstract data type.
-In Section~\ref{sec:hypercoercion-correctness} we show that
-the \lazyD{} hypercoercions $H$ are an instance of the Lazy D ADT,
-and therefore \effCEK{H} is equivalent to \ineffCEKD{}.
+We prove that, for any instance $C$ of the Cast ADT, \effCEK{C} is
+equivelent to \ineffCEKD{] provided that $C$ satisfies a collection of
+properties that we call the Lazy D Cast abstract data type.  In
+Section~\ref{sec:hypercoercion-correctness} we show that the \lazyD{}
+hypercoercions $H$ are an instance of the Lazy D ADT, and therefore
+\effCEK{H} is equivalent to \ineffCEKD{}.
 

### 2019-10-21 paper.tex
fix typos

@@
 This section presents our second contribution, a framework for proving
-correctness of cast representations, especially space efficient
-ones. Section~\ref{sec:hypercoercion-correctness} will apply this
+correctness of cast representations. The next section will apply this
 framework to prove the correctness of the \lazyD{} hypercoercions.
@@
 by an abstract data type, named Cast ADT, that we define shortly.
-
-We prove that, for any instance $C$ of the Cast ADT, \effCEK{C} is
-equivelent to \ineffCEKD{] provided that $C$ satisfies a collection of
-properties that we call the Lazy D Cast abstract data type.  In
-Section~\ref{sec:hypercoercion-correctness} we show that the \lazyD{}
-hypercoercions $H$ are an instance of the Lazy D ADT, and therefore
-\effCEK{H} is equivalent to \ineffCEKD{}.
-
-We are working on a similar theorem for \lazyUD{}.
-
-\todo[inline]{UNDER CONSTRUCTION -JS}
+%
+
+\todo[inline]{UNDER CONSTRUCTION. -JS}
+
+If $C$, an implementation of the Cast ADT inteface, satisifies a collection of 
+properties that we defined as Lazy D Cast ADT. We can instantiate our framework 
+theorem that we define shortly to prove that evaluating an program in 
+\effCEK{C} gives the same result as \ineffCEKD. We are working on a
+similar theorem for \lazyUD{}.
+
+\todo[inline]{UNDER CONSTRUCTION. -KC}
+
+The framework is a theorem saying that for all cast representation $C
+$, if $C$ satisfies a collection of properties, then it would
+respect the Lazy D semantics of cast calculi. We are working on a
+similar theorem for \lazyUD{}.
+
+%then instantiating our parameterized space-efficient interpreter with$C$
+%gives an interpter that is extensionally equal to the standard interpreter for 
+%\lazyD\ cast calculus.
 
@@
 
+\todo[inline]{In Fig.~\ref{fig:bisim-SC-D}, how to suppress rule numbers like 
+	(1), (2), etc.? -KC}
 Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
@@
 %
-To relate to a non-casted function in \ineffCEKD, the casts in the \effCEK{C} 
-function must be identity.
+To relate to a non-casted function in \ineffCEKD, the function in \effCEK{C} 
+must use identities as its casts.
 %
@@
 
-\todo[inline]{In Fig.~\ref{fig:bisim-SC-D}, how to suppress rule numbers like 
-(1), (2), etc.? -KC}
+\begin{lemma}[SoAndSo]
+	Assume $C$ implements Lazy D Cast ADT
+	and $v_1$ is a value in \effCEK{C}
+	and $v_2$ is a value in \ineffCEKD\
+	and $v_1 \approx v_2 : T_1$,
+	\[
+	applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
+	\approx 
+	applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
+	\]
+\end{lemma}
+\begin{proof}
+	Case splitting whether $T_1$ is shallowly consistent with $T_2$.
+	If yes, case splitting how they are shallowly consistent.
+	Then apply properties (3) - (11) of Lazy D Cast when applicable.
+\end{proof}
+
 \begin{figure}
-%	\fbox{$\text{\effCEK{C}} \approx \text{\ineffCEKD}$}
+	$\text{\effCEK{C}} \approx \text{\ineffCEKD}$
 	\[\dots\]
@@
 	\inference{
-		v_1 \approx v_2 : T
-	}{
-		\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
-		: \POOsum{T}{T'}
+		v_1 \approx v_2 : T_1
+	}{
+		\hcvOOinl{v_1}{id(T_1)} \approx \vOOinl{v_2}
+		: \POOsum{T_1}{T_2}
 	}
@@
 		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
-		: \POOsum{T}{T'}	
+		: \POOsum{T_3}{T_4}	
 	}
@@
 	\inference{
-	v_1 \approx v_2 : T
-	}{
-	\hcvOOinr{v_1}{id(T)} \approx \vOOinr{v_2}
-	: \POOsum{T'}{T}
+	v_1 \approx v_2 : T_2
+	}{
+	\hcvOOinr{v_1}{id(T_2)} \approx \vOOinr{v_2}
+	: \POOsum{T_1}{T_2}
 	}
@@
 	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
-	: \POOsum{T'}{T}
+	: \POOsum{T_3}{T_4}
 	}

### 2019-10-22 paper.tex
fix typos
progress on writing

@@
 \newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
-\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
+\newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}
 \newcommand{\continue}[2]{cont(#2,#1)}
@@
   in \figref{fig:applyCast-D-C}.  We write the transition relations of
-  this machine as $\judgeUDreduce{s}{s}$ and $\judgeUDreduceTrans{s}{s}$
-  and write the evaluation function as $\judgeUDeval{e}{o}$.
+  this machine as $\judgeDreduce{s}{s}$ and $\judgeDreduceTrans{s}{s}$
+  and write the evaluation function as $\judgeDeval{e}{o}$.
 \end{definition}
@@
   in \figref{fig:apply-Cast-UD}.  We write the transition relations of
-  this machine as $\judgeDreduce{s}{s}$ and $\judgeDreduceTrans{s}{s}$
-  and write the evaluation function as $\judgeDeval{e}{o}$.
+  this machine as $\judgeUDreduce{s}{s}$ and $\judgeUDreduceTrans{s}{s}$
+  and write the evaluation function as $\judgeUDeval{e}{o}$.
 \end{definition}
@@
 
+% the following are temporary -JS
+\clearpage
+\pagebreak
+
 \section{A framework for proving correctness of cast representations}
@@
 This section presents our second contribution, a framework for proving
-correctness of cast representations, especially space efficient
-ones. Section~\ref{sec:hypercoercion-correctness} will apply this
+the correctness of cast representations, especially space efficient
+ones. Section~\ref{sec:hypercoercion-correctness} applies this
 framework to prove the correctness of the \lazyD{} hypercoercions.
@@
 We start by defining a CEK machine \effCEK{C} that is parameterized
-over the cast representation $C$. This machine is space efficient
+over the cast representation $C$
+(Section~\ref{sec:framework:cek}). This machine is space efficient
 provided that the cast representation performs compression.  The
 interface between the machine and the cast representation is defined
-by an abstract data type, named Cast ADT, that we define shortly.
-
-We prove that, for any instance $C$ of the Cast ADT, \effCEK{C} is
-equivelent to \ineffCEKD{] provided that $C$ satisfies a collection of
-properties that we call the Lazy D Cast abstract data type.  In
-Section~\ref{sec:hypercoercion-correctness} we show that the \lazyD{}
-hypercoercions $H$ are an instance of the Lazy D ADT, and therefore
-\effCEK{H} is equivalent to \ineffCEKD{}.
-
-We are working on a similar theorem for \lazyUD{}.
-
-\todo[inline]{UNDER CONSTRUCTION -JS}
-
-We captures the set of operators that every cast representation must provide 
-with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
-The first three operators allow \effCEK{C} to construct casts. 
-So we call them \textit{cast constructors}. And the forth and last operator 
-allows \effCEK{C} to apply casts onto values.
+by an abstract data type, named Cast ADT, that we define shortly.  We
+conjecture that all cast representations defined in the literature
+are instances of this ADT.
+
+In Section~\ref{secc:framework:monoid-correct} we prove that, for any
+instance $C$ of the Cast ADT, if $C$ satisfies a more refined abstract
+data type for Lazy D casts, then \effCEK{C} is equivelent to
+\ineffCEKD{}, that is,
+\[
+  \evalEqv{\effCEK{C}}{\ineffCEKD}
+\]
+We conjecture that all of the cast representations in the literature
+for \lazyD{} (supercoercions, coercions in normal form, threesomes)
+are instances of the Lazy D Cast ADT.  We are working on a similar
+theorem for \lazyUD{} cast representations.
+
+We then apply this framework to \lazyD{} hypercoercions
+(Section~\ref{sec:hypercoercion-correctness}), where we show that $H$
+is an instance of the Lazy D Cast ADT, and therefore
+\[
+  \evalEqv{\effCEK{H}}{\ineffCEKD}
+\]
+
+Before turning to the definition of the abstract data types, we first
+give the definition of values used by the \effCEK{C}, as they are
+mentioned in the definition of the ADTs.
+
+\begin{definition}[Values for the \effCEK{C} machine] \label{def:values-effCEK}
+  \[
+  \begin{array}{rclr}
+	\stxrule{v}{}{
+		\hcvOOtt \mid
+		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
+		\hcvOOcons{v}{c}{v}{c} \mid
+		\hcvOOinl{v}{c} \mid
+		\hcvOOinr{v}{c} \mid
+		\hcvOOinj{P}{v}
+	}
+  \end{array}
+  \]
+\end{definition}
+
+\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS}
+
+\subsection{The Cast Abstract Data Types}
+
+The \emph{Cast Abstract Data Type}, defined below, captures the set of
+operators that a cast representation $C$ must provide for it to be
+used with the \effCEK{C} machine.  The first three operators enables
+\effCEK{C} to construct casts so we call them \textit{cast
+  constructors}. The forth and last operator enables \effCEK{C} to
+apply casts to values.
 
@@
   \begin{description}
-		\item[$id(T)$] constructs an cast from a type
-%		, where $c : T 
-%		\Longrightarrow T $
+  \item[$id(T)$] constructs an identity cast from a type
   \item[$seq(c_1,c_2)$] composes two casts
-%		, where $
-%		\judgeTypeFT{c_1}{T_1}{T_2}$, $\judgeTypeFT{c_2}{T_2}{T_3}$, and $
-%		\judgeTypeFT{c}{T_1}{T_3} $
   \item[$cast(T_1,l,T_2)$] constructs a cast from $T_1$ to $T_2$
-		\item[$ applyCast(v,c)=r$] applies a cast onto a value
+  \item[$ applyCast(v,c)$] applies a cast to a value, producing a result
   \end{description}
-	We denote by $c : T_1 \Longrightarrow T_2$ to mean $c$ is in $Cast \; 
-	T_1 \; T_2$. And we say ``$c$ is from $T_1$ to $T_2$''.
+  We denote by $c : T_1 \Longrightarrow T_2$ to mean $c$ is in $Cast \; T_1 \; T_2$
+  and we say ``$c$ is from $T_1$ to $T_2$''.
 \end{definition}
 
-Some instances of Cast ADT (or "some Cast" for short) are also 
-\textit{monoids}. This definition is useful in the proof of 
-our framework.
-
-\begin{definition}[Monoid]
-	A Cast is a monoid if 
-	for all
-	$c_1 : T_1 \Longrightarrow T_2$,
-	$c_2 : T_2 \Longrightarrow T_3$, and
-	$c_3 : T_3 \Longrightarrow T_4$,
-	\begin{enumerate}
-		\item $seq(id(T_1),c_1) = c_1$,
-		\item $seq(c_1,id(T_2)) = c_1$, and
-		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
-	\end{enumerate}
-\end{definition}
-
-To use our framework, users needs to prove that their cast representation
-implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
-Cast ADT. Property (1) 
-states that $id(T)$ acts like the identity function. Property (2) states 
-that $seq(c,c)$ acts like a sequence of casts. Properties (3) through 
-(11) state that $cast(T_1,l,T_2)$ act like the Lazy D $applyCast$
+Next we define the \emph{Lazy D Cast ADT}, which capture the further
+requirements that are needed for the theorem that establishes
+equivalence to \ineffCEKD{}. Property (1) below states that $id(T)$
+acts like the identity function. Property (2) states that $seq(c,c)$
+acts like a sequence of casts. Properties (3) through (11) state that
+$cast(T_1,l,T_2)$ act like the Lazy D $applyCast$
 (Fig.~\ref{fig:applyCast-D-C}).
-
-\todo[inline]{We might need to values before Lazy D Cast ADT. This will reduce 
-the extreme height of Fig.~\ref{fig:machine-cekcc} as well. -KC}
 
@@
   \begin{enumerate}
-		\item if $v : T$, then$applyCast(v,id(T)) = \mathtt{succ} \; v $
+  \item if $v : T$, then $applyCast(v,id(T)) = \mathtt{succ} \; v $
   \item if $\judgeType{v}{T_1}$,
@@
     $ \judgeTypeFT{c_2}{T_2}{T_3}$,\\
-		then$applyCast(v,seq(c_1,c_2)) = 
+    then $applyCast(v,seq(c_1,c_2)) = 
     applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2)$\\
@@
   \item if $v : T_1$ and $\neg T_1 \smile T_2$,
-		then$applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
+    then $applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
   \item if $v : \star$, 
-		then$applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
-		\item if $v : P_1$,
-		then$applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
-		= applyCast(v,cast(P_1,l,P_2)) $
+    then $applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
   \item if $v : P$,
-		then$applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
+    then $applyCast(\hcvOOinj{P}{v},cast(\star,l,P')) 
+    = applyCast(v,cast(P,l,P')) $
+  \item if $v : P$,
+    then $applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
   \item if $v : \POOunit$,
-		then$applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
+    then $applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
   \item if $(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2}$,
@@
 
-%Lazy D Cast ADT confines the behavior of operators so narrowly that it 
-%effectively allows us to ``run'' programs without referring to an actual 
-%representation of cast.
-
-After showing their cast representation is a Lazy D Cast, users of our 
-frameworks can plug-in this cast representation to our space-efficient abstract 
-machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
-equivalent to \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which 
-depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
+%% After showing their cast is an instance of Lazy D Cast, users of our
+%% frameworks can plug-in this cast representation to our space-efficient
+%% abstract machine in subsection~\ref{ssec:framework:cek}, and prove
+%% that this machine is equivalent to
+%% \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which
+%% depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
 
@@
 	\begin{array}{rclr}
-
-	\stxrule{v}{values}{
-		\hcvOOtt \mid
-		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
-		\hcvOOcons{v}{c}{v}{c}
-	}
-	\stxrulecont{
-		\hcvOOinl{v}{c} \mid
-		\hcvOOinr{v}{c} \mid
-		\hcvOOinj{P}{v}
-	}
 %	\stxrule{r}{cast results}{
@@
 \end{figure}
-\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient
-CEK machine.  This machine is similar to \ineffCEK{}.
-The keys differences are in values and continuations.
-
-Let $v$ range over value. 
-In \ineffCEK\, we have one value constructor for all casted value.
-In \effCEK{C}, however, we do not have this generic value constructor, 
-instead we push those casts into the ordinary values. For 
-instance, $(\vOOcons{v_1}{v_2})$ corresponds to 
-$(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$. To construct values of the 
-dynamic type, we use $(\hcvOOinj{P}{v})$.
-
-Cast results ($r$) and machine states ($s$) are as before.
-
-Let $\kappa$ range over continuations and Let $k$ range over 
-pre-continuations. 
-A continuation is now a pre-continuation prefixed with a cast.
-Pre-continuation are like the continuations in \ineffCEK, but there is no 
-constructor for casts.
-Continuations in \ineffCEKD\ have zero or more casts at the top.
-In \effCEK{C}, however, every continuation has exactly one cast at the top.
-Continuations in \ineffCEK\ that have no casts at the top correspond to 
-continuations in \effCEK{C}\ whose casts are identity.
-And continuations in \ineffCEK\ that have many casts at the top correspond to 
-continuations in \effCEK{C}\ where those casts are composed by $seq(c,c)$.
+
+\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient CEK
+machine.  This machine is similar to the \ineffCEK{} machine
+(Figure~\ref{fig:machine-cekc}).  The key differences are in values
+and continuations.
+
+Let $v$ range over values. In \ineffCEK{} we have one value
+constructor for all casted value.  In \effCEK{C}, however, we do not
+have this generic value constructor, instead we push those casts into
+the ordinary values. For instance, $(\vOOcons{v_1}{v_2})$ corresponds
+to $(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$. To construct values
+of the dynamic type, we use $(\hcvOOinj{P}{v})$.
+
+Cast results ($r$) and machine states ($s$) are the same as for
+\ineffCEK{}.
+
+Let $\kappa$ range over continuations and let $k$ range over
+pre-continuations.  A continuation is now a pre-continuation prefixed
+with a cast.  Pre-continuation are like the continuations in
+\ineffCEK{}, but there is no constructor for casts.  Continuations in
+\ineffCEKD{} have zero or more casts at the top.  In \effCEK{C},
+however, every continuation has exactly one cast at the top.
+Continuations in \ineffCEK\ that have no casts at the top correspond
+to continuations in \effCEK{C}\ whose casts are identity.
+Continuations in \ineffCEK\ that have many casts at the top correspond
+to continuations in \effCEK{C}\ where those casts are composed by
+$seq(c,c)$.
 
@@
 
-\subsection{Relating Some \effCEK{C} to \ineffCEKD}
+\subsection{\effCEK{C} is equivalent to \ineffCEKD, provided $C$ is an instance of the Lazy D ADT}
 \label{secc:framework:monoid-correct}
 
-In this subsection, we prove that if a instance of Cast ADT $C$ is Lazy D and 
-is a monoid, then $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this 
-theorem with a weak bisimulation between \effCEK{C} and \ineffCEKD.
+In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
+ADT, then
+\[
+  \evalEqv{\effCEK{C}}{\ineffCEKD}
+\]
+
+The meat of the proof is in a lemma that establishes a weak
+bisimulation between \ineffCEKD{} and \effCEK{C}.
+
+\todo[inline]{UNDER CONSTRUCTION -JS}
+
+We prove that if a instance of Cast ADT $C$ is
+Lazy D and is a monoid, then $eval_\mathcal{D} =
+eval_{\mathcal{S}(C)}$. We proof this theorem with a weak bisimulation
+between \effCEK{C} and \ineffCEKD.
+
+Some instances of Cast ADT (or "some Cast" for short) are also 
+\textit{monoids}. This definition is useful in the proof of 
+our framework.
+
+\begin{definition}[Monoid]
+	A Cast is a monoid if 
+	for all
+	$c_1 : T_1 \Longrightarrow T_2$,
+	$c_2 : T_2 \Longrightarrow T_3$, and
+	$c_3 : T_3 \Longrightarrow T_4$,
+	\begin{enumerate}
+		\item $seq(id(T_1),c_1) = c_1$,
+		\item $seq(c_1,id(T_2)) = c_1$, and
+		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
+	\end{enumerate}
+\end{definition}
+
+%Lazy D Cast ADT confines the behavior of operators so narrowly that it 
+%effectively allows us to ``run'' programs without referring to an actual 
+%representation of cast.
 
@@
 
-\subsection{\lazyD\ Cast ADT Respect \ineffCEKD}
-\label{secc:framework:all-correct}
+%% \subsection{\lazyD\ Cast ADT Respect \ineffCEKD}
+%% \label{secc:framework:all-correct}
 

### 2019-10-22 paper.tex
progress on writing

@@
 
-The meat of the proof is in a lemma that establishes a weak
-bisimulation between \ineffCEKD{} and \effCEK{C}.
+The main work of proof is in a lemma that establishes a weak
+bisimulation between \ineffCEKD{} and \effCEK{C}.  The bisimulation
+goes more smoothly if we require two more properties of the cast
+representation: that the casts form a monoid (the $id$ and $seq$
+operators) and that the cast constructor is equivalent to the identity
+operator when applied to an identical source and target type.
 

### 2019-10-22 paper.tex
much in-depth description of S(C) ~~ D

--- 2019-10-21 paper.tex
@@
 	\begin{enumerate}
-		\item if $v : T$, then$applyCast(v,id(T)) = \mathtt{succ} \; v $
+		\item if $v : T$, then $applyCast(v,id(T)) = \mathtt{succ} \; v $
 		\item if $\judgeType{v}{T_1}$,
@@
 		$ \judgeTypeFT{c_2}{T_2}{T_3}$,\\
-		then$applyCast(v,seq(c_1,c_2)) = 
+		then $applyCast(v,seq(c_1,c_2)) = 
 		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2)$\\
@@
 		\item if $v : T_1$ and $\neg T_1 \smile T_2$,
-		then$applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
+		then $applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
 		\item if $v : \star$, 
-		then$applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
-		\item if $v : P_1$,
-		then$applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
-		= applyCast(v,cast(P_1,l,P_2)) $
+		then $applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
 		\item if $v : P$,
-		then$applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
+		then $applyCast(\hcvOOinj{P}{v},cast(\star,l,P')) 
+		= applyCast(v,cast(P,l,P')) $
+		\item if $v : P$,
+		then $applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
 		\item if $v : \POOunit$,
-		then$applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
+		then $applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
 		\item if $(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2}$,
@@
 	Apply continuation
-	\fbox{$continue(k,v) = s$}
+	\fbox{$\continue{k}{v} = s$}
 	\[
@@
 
-\begin{lemma}[SoAndSo]
-	Assume $C$ implements Lazy D Cast ADT
-	and $v_1$ is a value in \effCEK{C}
-	and $v_2$ is a value in \ineffCEKD\
-	and $v_1 \approx v_2 : T_1$,
-	\[
-	applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
-	\approx 
-	applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
-	\]
-\end{lemma}
-\begin{proof}
-	Case splitting whether $T_1$ is shallowly consistent with $T_2$.
-	If yes, case splitting how they are shallowly consistent.
-	Then apply properties (3) - (11) of Lazy D Cast when applicable.
-\end{proof}
-
 \begin{figure}
@@
 
-Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-introduce one more definition: $s_1 \approx^{*} s_2$ if and only if there 
-exists $s_2' \in \text{\ineffCEKD}$
-such that $\judgeCreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
+\begin{lemma}[SoAndSo]
+	Assume $C$ implements Lazy D Cast ADT
+	and $v_1$ is a value in \effCEK{C}
+	and $v_2$ is a value in \ineffCEKD\
+	and $v_1 \approx v_2 : T_1$,
+	\[
+	applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
+	\approx 
+	applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
+	\]
+\end{lemma}
+\begin{proof}
+	Case splitting whether $T_1$ is shallowly consistent with $T_2$.
+	If yes, case splitting how they are shallowly consistent.
+	Then apply properties (3) - (11) of Lazy D Cast when applicable.
+\end{proof}
+
+\begin{definition}[SoAndSo] $s_1 \approx^{*} s_2$ if there exists $s_2'$,
+	\[
+	s_1 \approx s_2'
+	\;\text{and}\;
+	\judgeDreduceTrans{s_2}{s_2'} \]
+
+\end{definition}
 
@@
 	\label{thm:surely-monoidic-reduce}
-	For all instance of Cast ADT $C$, 
-	if $C$ is \lazyD{} and is a monoid and $cast(T,l,T)=id(T)$,
-	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
-	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
+	Assume $C$ implements Lazy D Cast ADT
+	and $C$ is a monoid
+	and $cast(T,l,T)=id(T)$,
+	$ s_{1} \in \text{\effCEK{C}}$,
+	$ s_{2} \in \text{\ineffCEKD}$,
 	$ s_{1} \approx s_{2}$,
-	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
-	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
-%	then there exist$s_2'' \in \text{\ineffCEKD}$such that
-	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
-	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
-%	\begin{enumerate}
-%		\item if $\judgeDreduce{s_1}{s_3}$,
-%		then
-%		there exist$s_5 \in \text{\ineffCEKD}$, $s_4 \in \mathcal{S}(C)$,
-%		such that \begin{itemize}
-%			\item$s_5 \approx s_4$, and
-%			\item$\judgeSreduce{C}{s_2}{s_4}$,
-%			\item$\judgeDreduceTrans{s_3}{s_5} $
-%		\end{itemize}
-%		\item if $\judgeSreduce{C}{s_2}{s_4}$,
-%		then
-%		there exist$s_3 \in \mathcal{C}$,
-%		such that \begin{itemize}
-%			\item$s_3 \approx s_4 $
-%			\item$\judgeDreduceTrans{s_1}{s_3} $
-%		\end{itemize}
-%	\end{enumerate}
-
-Or diagrammatically, 
-\[\begin{array}{clclc}
-s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-\rotatebox[origin=c]{90}{$\approx$} 
-& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-s_{2} & 
-\longrightarrow_{\text{\ineffCEKD}} & s_2' &
-\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-\end{array}\]
+\begin{enumerate}
+	\item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
+	\item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+	\item If $\judgeSreduce{C}{s_1}{s_3}$ 
+		then $\judgeDreduce{s_2}{s_4}$ for some $s_4$
+	\item If $\judgeDreduce{s_2}{s_4}$
+		then $\judgeSreduce{C}{s_1}{s_3}$ for some $s_3$
+	\item If $\judgeSreduce{C}{s_1}{s_3}$ and $\judgeDreduce{s_2}{s_4}$
+		then $s_3 \approx^{*} s_4$
+\end{enumerate}
+%	Or diagrammatically, 
+%	\[\begin{array}{clclc}
+%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%	\rotatebox[origin=c]{90}{$\approx$} 
+%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%	s_{2} & 
+%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%	\end{array}\]
+
+%	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
+%	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
+%	$ s_{1} \approx s_{2}$,	
+%	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
+%	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
+%	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
+%	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
+%	Or diagrammatically, 
+%	\[\begin{array}{clclc}
+%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%	\rotatebox[origin=c]{90}{$\approx$} 
+%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%	s_{2} & 
+%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%	\end{array}\]
 
@@
 \begin{proof}
-	By following the transition rule of \ineffCEKD. See the supplementary 
-	materials for details.
+	Part (1) and (2) follow from the definition of $s \approx s$.
+	Part (3) and (4) are true because we have transition rules for every 
+	non-halting state.
+	Part (5) is more interesting.
+	Consider
+	\[
+	\sOOreturn{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{\kOOcast{c}{\kOOcar{\kappa}}}
+	\approx
+	\]
 \end{proof}
+
+\todo[inline]{UNDER CONSTRUCTION -KC}
 

### 2019-10-22 paper.tex
rm a todo
progress on section 4

--- 2019-10-22 paper.tex
@@
 
+\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
+   and should be explained. -JS}
+
 \begin{definition}[Values for the \effCEK{C} machine] \label{def:values-effCEK}
@@
 
-\subsection{\effCEK{C} is equivalent to \ineffCEKD, provided $C$ is an instance of the Lazy D ADT}
+\subsection{\effCEK{C} is equivalent to \ineffCEKD{}, provided $C$ is an instance of the Lazy D ADT}
 \label{secc:framework:monoid-correct}
@@
 \]
-
-The main work of proof is in a lemma that establishes a weak
-bisimulation between \ineffCEKD{} and \effCEK{C}.  The bisimulation
+The main work of the proof is in a lemma that establishes a weak
+bisimulation between \effCEK{C} and \ineffCEKD{}.  The bisimulation
 goes more smoothly if we require two more properties of the cast
@@
 operator when applied to an identical source and target type.
-
-\todo[inline]{UNDER CONSTRUCTION -JS}
-
-We prove that if a instance of Cast ADT $C$ is
-Lazy D and is a monoid, then $eval_\mathcal{D} =
-eval_{\mathcal{S}(C)}$. We proof this theorem with a weak bisimulation
-between \effCEK{C} and \ineffCEKD.
-
-Some instances of Cast ADT (or "some Cast" for short) are also 
-\textit{monoids}. This definition is useful in the proof of 
-our framework.
+However, the final theorem does not require these two properties
+because we can prove 1) that \effCEK{C_1} and \effCEK{C_2} are
+equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$, and 2) there
+is an instance of the Lazy D Cast ADT, named $L$, that is a monoid and
+satisfies the two extra properties, and is therefore equivalent to
+\ineffCEKD{}. So by transitivity, for any Lazy D Cast ADT $C$ we have
+\evalEqv{\effCEK{C}}{\ineffCEKD}.
+
+\subsubsection{Weak Bisimulation between \effCEK{C} and \ineffCEKD{}}
+
+We shall prove that if a instance of Cast ADT $C$ is Lazy D, is a
+monoid, and if $cast(T,l,T) = id(T)$, then there is
+%% $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this lemma with
+a weak bisimulation between \effCEK{C} and \ineffCEKD{}.
+We define monoid as follows.
 
 \begin{definition}[Monoid]
-	A Cast is a monoid if 
+	A Cast ADT is a monoid if 
 	for all
@@
 
-\todo[inline]{In Fig.~\ref{fig:bisim-SC-D}, how to suppress rule numbers like 
-	(1), (2), etc.? -KC}
-Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
-that make the relation a congruence.
+\todo[inline]{How does the following bisimulation relation
+  compare to the one used in the Blame and Coercion paper?
+  Are there any guiding principles to how this bisimulation
+  relation was constructed? -JS}
+
+Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.  It is
+the smallest congruence relation that also includes the pairs induced
+by the rules in Fig.~\ref{fig:bisim-SC-D}.
 %
-The relation $\kappa \approx \kappa$ relates two continuations. 
+The relation is mutually defined on continuations, written $\kappa
+\approx \kappa$, and values, written $v \approx v : T$, where $T$ is
+their type.
 %
@@
 %
+\todo[inline]{The use of ``wrap'' obscures this explanation.
+  Consider getting rid of wrap by inlining it. -JS}
+%
 If $\kappa_1 \approx \kappa_2$, extending $\kappa_1$ and $\kappa_2$ with the 
 same cast gives related results.
-%
-%
-The relation $v \approx v : T$ relates two value and also report their type. We 
-will see shortly why reporting the type. 
 %
@@
 %
-Unit values are of course related.
+% The following is part of being a congruence. -JS
+%Unit values are of course related. 
 %
@@
 
+\todo[inline]{Give the motivation for the following lemma. Where
+  does it get used? As in, which case of which other lemma or theorem? -JS}
+
 \begin{lemma}[SoAndSo]
@@
 	$\text{\effCEK{C}} \approx \text{\ineffCEKD}$
-	\[\dots\]
+%	\[\dots\]
 
@@
 	\fbox{$v \approx v : T$}
-	\begin{gather}
+	\begin{gather*}
 	\inference{
@@
 \\ \\
-	\inference{}{
-		\hcvOOtt \approx \vOOtt : \POOunit
-	}
-	\quad
+	%% \inference{}{
+	%% 	\hcvOOtt \approx \vOOtt : \POOunit
+	%% }
+	%% \quad
 	\inference{}{
@@
 	}
-	\end{gather}
+	\end{gather*}
 	\caption{Bisimulation between \effCEK{C} and \ineffCEKD}
@@
 Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-introduce one more definition: $s_1 \approx^{*} s_2$ if and only if there 
-exists $s_2' \in \text{\ineffCEKD}$
-such that $\judgeCreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
+introduce one more definition.
+
+\begin{definition}[$s \approx^{*} s$]
+Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
+if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
+that $\judgeDreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
+\end{definition}
 
 \todo[inline]{Standardize theorem statement -KC}
+
 \begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
   \label{thm:surely-monoidic-reduce}
-	For all instance of Cast ADT $C$, 
-	if $C$ is \lazyD{} and is a monoid and $cast(T,l,T)=id(T)$,
-	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
-	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
-	$ s_{1} \approx s_{2}$,
-	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
-	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
-%	then there exist$s_2'' \in \text{\ineffCEKD}$such that
-	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
-	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
-%	\begin{enumerate}
-%		\item if $\judgeDreduce{s_1}{s_3}$,
-%		then
-%		there exist$s_5 \in \text{\ineffCEKD}$, $s_4 \in \mathcal{S}(C)$,
-%		such that \begin{itemize}
-%			\item$s_5 \approx s_4$, and
-%			\item$\judgeSreduce{C}{s_2}{s_4}$,
-%			\item$\judgeDreduceTrans{s_3}{s_5} $
-%		\end{itemize}
-%		\item if $\judgeSreduce{C}{s_2}{s_4}$,
-%		then
-%		there exist$s_3 \in \mathcal{C}$,
-%		such that \begin{itemize}
-%			\item$s_3 \approx s_4 $
-%			\item$\judgeDreduceTrans{s_1}{s_3} $
-%		\end{itemize}
-%	\end{enumerate}
-
+  Suppose $C$ is an instance of the Cast ADT
+  and the \lazyD{} ADT, $C$ is a monoid,
+  and $cast(T,l,T)=id(T)$.
+  If
+  $s_{1}, s_{1}' \in \text{\effCEK{C}}$,
+  $s_{2}, s_{2}' \in \text{\ineffCEKD}$,
+  $s_{1} \approx s_{2}$,
+  $\judgeSreduce{C}{s_{1}}{s_{1}'}$, and
+  $\judgeDreduce{s_{2}}{s_{2}'}$, then
+  \todo[inline]{The premise $\judgeDreduce{s_{2}}{s_{2}'}$ is
+    unusual for a weak bisimulation. Makes me suspicious.
+    That is usually in the conclusion. If this is indeed correct,
+    then you'll need to justify/explain it. -JS}
+  \[
+    \exists s_2'' \in \text{\ineffCEKD}: \;
+    \judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2''
+  \]
   Or diagrammatically, 
-\[\begin{array}{clclc}
+  \[
+  \begin{array}{clclc}
     s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
@@
     \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-\end{array}\]
-
+  \end{array}
+  \]
 \end{lemma}
 \begin{proof}
-	By following the transition rule of \ineffCEKD. See the supplementary 
-	materials for details.
+  By following the transition rule of \ineffCEKD.
+  \todo[inline]{What does ``following the transition rules'' mean?
+    That's not normal proof jargon. Do you mean case analysis
+    on $\judgeSreduce{C}{s_{1}}{s_{1}'}$?
+    -JS}
+  See the supplementary materials for details.
 \end{proof}
@@
   -KC}
-\begin{proposition}[Correctness of \effCEK{C}]
+
+\begin{corollary}[Correctness of \effCEK{C}]
   \label{thm:surely-monoidic-eval}
-	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
-	\lazyD{} Cast ADT and a monoid,
+  Suppose $C$ is an instance of the Cast ADT
+  and the \lazyD{} ADT, $C$ is a monoid,
+  and $cast(T,l,T)=id(T)$.
+  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
   \[
@@
   \]
-\end{proposition}
-\begin{proof}Proving left implies right is trivial.
-To prove $\judgeDeval{e}{o}$ implies $\judgeSeval{C}{e}{o}$, 
-we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
-taking one or more steps in \ineffCEKD. As we just took a positive number of 
-steps, we are closer to the halting state.
+\end{corollary}
+\begin{proof}
+  Proving that the left-hand side implies the right-hand side is
+  trivial.  To prove $\judgeDeval{e}{o}$ implies
+  $\judgeSeval{C}{e}{o}$, we first take one step in \effCEK{C}, and
+  catch it up in \ineffCEKD\ by taking one or more steps in
+  \ineffCEKD. As we just took a positive number of steps, we are
+  closer to the halting state.
 \end{proof}
@@
 
-In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast ADT, 
-then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
-prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
-connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.
-
-We prove the equivalence among \effCEK{S(C)} with strong bisimulation. This 
-time almost all the bisimulation relations are all derived from definitions 
-except the relaton for casts, which is by cast constructors:
+%% In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast ADT, 
+%% then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
+%% prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
+%% connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.
+
+\subsubsection{\effCEK{C_1} and \effCEK{C_2} are equivalence if $C_1$ and $C_2$ are Lazy D}
+
+We prove the equivalence among two \effCEK{C} machines with a strong
+bisimulation. This time almost all the bisimulation relations are all
+derived from definitions except the relaton for casts, which is by
+cast constructors:
+\todo[inline]{By ``derived from the definitions'' do you mean
+ that it is a congruence? -JS}
+
 \begin{gather*}
@@
   \effCEK{S(C)}.
-	The key ideas of this proof are undoing sequencing with the property (2) of 
-	Lazy D Cast ADT, and handling all possibly uses of $
-	cast(T,l,T)$ with property (3)-(11).
+%
+  \todo[inline]{The above sentence is not normal proof jargon.  Are
+    you doing a proof by cases on $s_{1}
+    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS}
+%
+  The key ideas of this proof are undoing sequencing with the property
+  (2) of Lazy D Cast ADT, and handling all possibly uses of
+  $cast(T,l,T)$ with property (3)-(11).
 \end{proof}
 
-\begin{proposition}[Equivalence of \lazyD{} Cast ADT]
+\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
   \label{thm:surely-lazyD-eqv}
-	if $\judgetype{\emptyset}{e}{T}$, $o : T$, and $C_1$ and $C_2$
-	are \lazyD\ Cast ADTs,
-	\[
-	eval_{S(C_1)} = eval_{S(C_2)}
+  Suppose $C_1$ and $C_2$ are \lazyD\ Cast ADTs.
+  If $\judgetype{\emptyset}{e}{T}$, $o : T$, then
+  \[
+  eval_{S(C_1)} = eval_{S(C_2)}.
   \]
@@
   By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
+  \todo[inline]{Induction on what? -JS}
 \end{proof}
@@
   \label{thm:surely-lazyD-correct}
-	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
-	\lazyD{} Cast ADT.
+  Suppose $C$ is a \lazyD{} Cast ADT.  If
+  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
   \[

### 2019-10-22 paper.tex
more progress

@@
 
-\todo[inline]{Give the motivation for the following lemma. Where
-  does it get used? As in, which case of which other lemma or theorem? -JS}
-
-\begin{lemma}[SoAndSo]
-	Assume $C$ implements Lazy D Cast ADT
-	and $v_1$ is a value in \effCEK{C}
-	and $v_2$ is a value in \ineffCEKD\
-	and $v_1 \approx v_2 : T_1$,
-	\[
-	applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
-	\approx 
-	applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
-	\]
-\end{lemma}
-\begin{proof}
-	Case splitting whether $T_1$ is shallowly consistent with $T_2$.
-	If yes, case splitting how they are shallowly consistent.
-	Then apply properties (3) - (11) of Lazy D Cast when applicable.
-\end{proof}
-
 \begin{figure}
@@
 
+\todo[inline]{Give the motivation for the following lemma. Where
+  does it get used? As in, which case of which other lemma or theorem? -JS}
+
+\begin{lemma}[SoAndSo]
+	Assume $C$ implements Lazy D Cast ADT
+	and $v_1$ is a value in \effCEK{C}
+	and $v_2$ is a value in \ineffCEKD\
+	and $v_1 \approx v_2 : T_1$,
+	\[
+	applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
+	\approx 
+	applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
+	\]
+\end{lemma}
+\begin{proof}
+	Case splitting whether $T_1$ is shallowly consistent with $T_2$.
+	If yes, case splitting how they are shallowly consistent.
+	Then apply properties (3) - (11) of Lazy D Cast when applicable.
+\end{proof}
+
 Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
@@
 if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
-that $\judgeDreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
+that
+\[
+s_1 \approx s_2'
+\;\text{and}\;
+\judgeDreduceTrans{s_2}{s_2'}
+\]
 \end{definition}
-
-\todo[inline]{Standardize theorem statement -KC}
 
@@
 	\label{thm:surely-monoidic-reduce}
-  Suppose $C$ is an instance of the Cast ADT
-  and the \lazyD{} ADT, $C$ is a monoid,
-  and $cast(T,l,T)=id(T)$.
-  If
-  $s_{1}, s_{1}' \in \text{\effCEK{C}}$,
-  $s_{2}, s_{2}' \in \text{\ineffCEKD}$,
-  $s_{1} \approx s_{2}$,
-  $\judgeSreduce{C}{s_{1}}{s_{1}'}$, and
-  $\judgeDreduce{s_{2}}{s_{2}'}$, then
-  \todo[inline]{The premise $\judgeDreduce{s_{2}}{s_{2}'}$ is
-    unusual for a weak bisimulation. Makes me suspicious.
-    That is usually in the conclusion. If this is indeed correct,
-    then you'll need to justify/explain it. -JS}
-  \[
-    \exists s_2'' \in \text{\ineffCEKD}: \;
-    \judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2''
-  \]
-  Or diagrammatically, 
-  \[
-  \begin{array}{clclc}
-    s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-    \rotatebox[origin=c]{90}{$\approx$} 
-    & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-    s_{2} & 
-    \longrightarrow_{\text{\ineffCEKD}} & s_2' &
-    \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-  \end{array}
-  \]
+	Assume $C$ implements Lazy D Cast ADT
+	and $C$ is a monoid
+	and $cast(T,l,T)=id(T)$,
+	$ s_{1} \in \text{\effCEK{C}}$,
+	$ s_{2} \in \text{\ineffCEKD}$,
+	$ s_{1} \approx s_{2}$,
+\begin{enumerate}
+	\item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
+	\item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+	\item If $\judgeSreduce{C}{s_1}{s_3}$ 
+		then $\judgeDreduce{s_2}{s_4}$ for some $s_4$
+	\item If $\judgeDreduce{s_2}{s_4}$
+		then $\judgeSreduce{C}{s_1}{s_3}$ for some $s_3$
+	\item If $\judgeSreduce{C}{s_1}{s_3}$ and $\judgeDreduce{s_2}{s_4}$
+		then $s_3 \approx^{*} s_4$
+\end{enumerate}
+%	Or diagrammatically, 
+%	\[\begin{array}{clclc}
+%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%	\rotatebox[origin=c]{90}{$\approx$} 
+%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%	s_{2} & 
+%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%	\end{array}\]
+
+%	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
+%	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
+%	$ s_{1} \approx s_{2}$,	
+%	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
+%	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
+%	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
+%	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
+%	Or diagrammatically, 
+%	\[\begin{array}{clclc}
+%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%	\rotatebox[origin=c]{90}{$\approx$} 
+%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%	s_{2} & 
+%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%	\end{array}\]
+
 \end{lemma}
 \begin{proof}
-  By following the transition rule of \ineffCEKD.
-  \todo[inline]{What does ``following the transition rules'' mean?
-    That's not normal proof jargon. Do you mean case analysis
-    on $\judgeSreduce{C}{s_{1}}{s_{1}'}$?
-    -JS}
-  See the supplementary materials for details.
+	Part (1) and (2) follow from the definition of $s \approx s$.
+	Part (3) and (4) are true because we have transition rules for every 
+	non-halting state.
+	Part (5) is more interesting.
+	Consider
+	\[
+	\sOOreturn{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{\kOOcast{c}{\kOOcar{\kappa}}}
+	\approx
+	\]
 \end{proof}
+
+\todo[inline]{UNDER CONSTRUCTION -KC}
 
@@
 
-\begin{theorem}[\lazyD\ Cast ADT Respects \ineffCEKD]
+\subsubsection{Correctness of \effCEK{C}}
+
+\begin{theorem}[\effCEK{C} is correct wrt. \ineffCEKD{}]
   \label{thm:surely-lazyD-correct}
@@
   \[
-  \text{\evalEqv{\ineffCEKD}{\effCEK{C}}}
+  \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
   \]

### 2019-10-22 paper.tex
update

@@
   Are there any guiding principles to how this bisimulation
-  relation was constructed? -JS}
+  relation was constructed? -JS
+\\---\\
+The guiding principle is to keep the change in D side atomic. \\
+In the blame and coercion paper,
+the bisimulation relation between $ \lambda{}C $ and $ \lambda{}S $ seems to be 
+related, but its (iii) rules in Figure 6 looks wired to me. -KC}
 
@@
 \todo[inline]{Give the motivation for the following lemma. Where
-  does it get used? As in, which case of which other lemma or theorem? -JS}
+  does it get used? As in, which case of which other lemma or theorem? -JS
+\\---\\
+Partially fixed. Will say in which cases after finishing the bisim proof. -KC}
+
+We use the following lemma in our bisimulation proof.
 
@@
 
-\todo[inline]{An extra property is required after changing case to small-step 
-  -KC}
-
 \begin{corollary}[Correctness of \effCEK{C}]
@@
 We prove the equivalence among two \effCEK{C} machines with a strong
-bisimulation. This time almost all the bisimulation relations are all
-derived from definitions except the relaton for casts, which is by
-cast constructors:
+bisimulation. The bisimulation relation is the smallest congruence relation 
+that also includes the pairs induced by the rules below.
 \todo[inline]{By ``derived from the definitions'' do you mean
- that it is a congruence? -JS}
+ that it is a congruence? -JS
+\\---\\
+Exactly, fixed. -KC}
 
@@
 	\label{thm:CEKS-bisim}
-	If 
-	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
-	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
-	$s_1 \approx s_2$,
-	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
-	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
-	$s_1' \approx s_2'$
-
+	Assume $C_1$ and $C_2$ implements Lazy D Cast ADT
+	$s_{1} \in \text{\effCEK{C_1}}$,
+	$s_{2} \in \text{\effCEK{C_2}}$,
+	$s_{1} \approx s_{2}$,
+	\begin{enumerate}
+		\item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
+		\item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+		\item If $\judgeSreduce{C}{s_1}{s_3}$ 
+		then $\judgeDreduce{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
+		\item If $\judgeSreduce{C}{s_2}{s_4}$ 
+		then $\judgeDreduce{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
+	\end{enumerate}
+%	If 
+%	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
+%	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
+%	$s_1 \approx s_2$,
+%	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
+%	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
+%	$s_1' \approx s_2'$
+%	
 	Or diagrammatically, 
@@
 \end{lemma}
-\begin{proof} 
-  This proof is effectively a duplication of the transition rule of
-  \effCEK{S(C)}.
+\begin{proof} By casing on $s_{1} \approx s_{2}$.
 %
@@
     you doing a proof by cases on $s_{1}
-    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS}
+    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS
+\\---\\
+By casing on the bisimulation relation. -KC}
 %
@@
   \label{thm:surely-lazyD-eqv}
-  Suppose $C_1$ and $C_2$ are \lazyD\ Cast ADTs.
-  If $\judgetype{\emptyset}{e}{T}$, $o : T$, then
-  \[
-  eval_{S(C_1)} = eval_{S(C_2)}.
+  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
+  \[
+  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
   \]
@@
 \begin{proof}
-  By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
-  \todo[inline]{Induction on what? -JS}
+	Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
+	$\judgeSreduce{C_2}{e}{o}$.\\
+	By the definition of $eval_{\mathcal{S}(C)}$, we know 
+	\[
+	\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_1)}(e)}{\sOOhalt{o}}
+	\]
+	By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
+	have 
+	\[\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_2)}(e)}{\sOOhalt{o}}\]
+	that is, $\judgeSreduce{C_2}{e}{o}$
+\todo[inline]{Induction on what? -JS
+\\---\\
+Fixed. -KC
+\\---\\
+Need to define load. -KC}
 \end{proof}

### 2019-10-22 paper.tex
added subsection about L

@@
 
+\todo[inline]{Jeremy needs to add text. -JS}
+
 Figure~\ref{fig:HC-UD}
@@
 because we can prove 1) that \effCEK{C_1} and \effCEK{C_2} are
-equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$, and 2) there
-is an instance of the Lazy D Cast ADT, named $L$, that is a monoid and
-satisfies the two extra properties, and is therefore equivalent to
-\ineffCEKD{}. So by transitivity, for any Lazy D Cast ADT $C$ we have
-\evalEqv{\effCEK{C}}{\ineffCEKD}.
+equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$
+(Proposition~\ref{thm:surely-lazyD-eqv}), and 2) there is an instance
+of the Lazy D Cast ADT, named $L$, that is a monoid and satisfies the
+two extra properties, and is therefore equivalent to \ineffCEKD{}
+(Lemma~\ref{lem:L-correct}). So by transitivity, for any Lazy D Cast
+ADT $C$ we have \evalEqv{\effCEK{C}}{\ineffCEKD}.
 
@@
 
+\subsubsection{The $L$ instance of the Lazy D Cast ADT}
+
+\todo[inline]{KC, please add the definition of $L$ -JS}
+
+\begin{proposition}[$L$ properties]\ 
+  \begin{enumerate}
+  \item $L$ is an instance of the Lazy D ADT
+  \item $L$ is a monoid
+  \item $cast(T,l,T) = id(T)$
+  \end{enumerate}
+\end{proposition}
+
+\begin{lemma}[$L$ is correct wrt. \ineffCEKD]
+  \label{lem:L-correct}
+  \[
+  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
+  \]
+\end{lemma}
+
 \subsubsection{Correctness of \effCEK{C}}
@@
 \begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
-	if $\judgetype{\emptyset}{e}{T}$ and $o : T$
-	\[
-	\text{\evalEqv{\ineffCEKD}{\effCEK{H}}}
+  If $\judgetype{\emptyset}{e}{T}$ and $o : T$
+  \[
+  \text{\evalEqv{\effCEK{H}}{\ineffCEKD}}
   \]

### 2019-10-22 paper.tex
tweak S(C) Fig; finish its description

@@
 	\hiredruleS{
-		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
+		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
 	}{
@@
 \funrule{
-	\continue{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
+	\continue{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
 	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
@@
 \hifunrule{
-	\continue{v_2}{(\kOOconsII{v_1}{\kappa})}}{
+	\continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
 	\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{}
@@
 \hifunrule{
-	\continue{v}{(\kOOinl{\kappa})}}{
+	\continue{v}{\kOOinl{\kappa}}}{
 	\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{}
@@
 \hifunrule{
-	\continue{v}{(\kOOinr{\kappa})}}{
+	\continue{v}{\kOOinr{\kappa}}}{
 	\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{}
@@
 \funrule{
-	\continue{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
-	\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}
-
-%\funrule{
-%	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
-%applyCast(v_2,c_1) >>= \lambda v. \sOOinspect{e}{\rho[x:=v]}{ext(c,\kappa)}
-%}{}
-
+	\continue{v_1}{\kOOappI{e_2}{\rho}{\kappa}}}{
+	\sOOinspect{e_2}{\rho}{
+		wrap(\kOOappII{v_1}{\kappa})
+	}}{}
 \hifunrule{
@@
 	\sOOinspect{e_3}{\rho}{
-	\kOOcaseIII{v_1}{v_2}{\kappa}
+	wrap(\kOOcaseIII{v_1}{v_2}{\kappa})
 	}
@@
 \hifunrule{
-	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
-		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
-		\;\kappa)}
+	\continue{v_3}{
+		\kOOcaseIII{(\hcvOOinl{v}{c})}{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa}
+%		(\mathtt{case_3}\;()\;
+%		()
+%		\;)
+	}
 }{
@@
 	\continue{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}
-	{(\mathtt{case_3}\;(\hcvOOinr{v}{c})\;v_2\;\kappa)}
+	{
+		\kOOcaseIII{(\hcvOOinr{v}{c})}{v_2}{\kappa}
+	}
 }{
@@
 
-\todoKC{describe transition rules}
-We list a fraction of reduction rules due to space limitation.
-\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS
-\\---\\They are all in the figure. I haven't updated this paragraph 
-accordingly. -KC}
-
-%When evaluating a cast expression, the machine moves the cast to the
-%continuation and evaluates the inner expression.
-%To apply a casted function, the machine first casts $v_1$, the
-%operand, then applies the casted operand to $v_2$, the underlying
-%function, and finally cast the result of the function application.
-%%
-%To take out the first (resp. second) part of a casted pair, the
-%machine firstly take out the first (resp. second) part of $v$, the
-%underlying pair, and cast the result.
-%%
+The transition relation $\judgeSreduce{C}{s}{s}$ uses functions provides by $C$ 
+to represent cases and to apply casts.
+%
+When evaluating a cast expression, the machine extends the continuation with 
+cast $cast(T_1,l,T_2)$. The function $ext(c,\kappa)$ composes $c$ with the cast 
+at the top of $k$ by calling $seq$.
+%
+To construct a function, the machine fills the casts $id$.
+%
+To return a value to a continuation, the machine first applies the top cast to 
+the value. If the application fails, the machine halts with the blame label 
+from the failure. Otherwise, the machine handles the pre-continuation with 
+$cont$.
+%
+When the machine constructs a pair, a left injection, or a right injection, it 
+fills the casts with $id$ as well, just like how it did for functions. 
+%
+To apply a function, the machine applies the domain cast $c_1$ to the 
+operand $v_2$, extends the continuation with the codomain cast $c_2$, and 
+evaluate the function body.
+%
+To take out the first part of a pair, the machine returns the first value to a 
+continuation extended with the first cast. Taking out the second part of a pair 
+is similar.
+%
 %%In case splitting, if the target value is a left injection, the
@@
 %%
-%When the target value is a casted sum, the machine moves the cast from
-%the target value to continuations functions.
-%%
-%To cast a value, the machine invokes $applyCast$ on the value.  If the
-%cast succeeds, the machine returns the result to the next
-%continuation.  If the cast fails, the machine halts with the blame
-%label.
-
-The transition relation $\judgeSreduce{C}{s}{s}$ uses functions provides by $C$ 
-to represent cases and to apply casts.
-%
-When evaluating a cast expression, the machine extends the continuation with 
-cast $cast(T_1,l,T_2)$. The function $ext(c,\kappa)$ composes $c$ with the cast 
-at the top of $k$ by calling $seq$.
-%
-To construct a function, the machine fills the casts $id$.
-%
-To return a value to a continuation, the machine first applies the top cast to 
-the value. If the application fails, the machine halts with the blame label 
-from the failure. Otherwise, the machine handles the pre-continuation with 
-$continue$.
-%
-When the machine constructs a pair, a left injection, or a right injection, it 
-fills the casts with $id$ as well, just like how it did for functions. 
-%
-To apply a function, the machine applies the domain cast $c_1$ to the 
-operand $v_2$, extends the continuation with the codomain cast $c_2$, and 
-evaluate the function body.
-%
-To take out the first (resp. second) part of a pair ...
-%
-%%In case splitting, if the target value is a left injection, the
-%%machine moves to a state that will apply the first continuation
-%%function to the value inside the left injection. The case for right
-%%injection is similar.
-%%
-%When the target value is a casted sum, the machine moves the cast from
-%the target value to continuations functions.
-To case spliting a variant, ...
-
-%When values are constructed, their hypercoercion parts are filled with outputs 
-%of $id$. For instance, when a function value is constructed, its first part 
-%and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
-%When evaluating a cast expression, the current continuation is extended with a 
-%hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
-%with the hypercoercion on the top of the continuation.
-%When evaluating a compound expression, the machine firstly construct the new 
-%pre-continuation, then turn it to a continuation by adding an identity 
-%hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
-%expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
-%the new pre-continuation, then call $cont$, which adds an identity cast to 
-%form a continuation. 
-%When a function call happens, the machine firstly cast the operand. If the 
-%casting succeeds, the machine then evaluate the body in the extended 
-%environment and the extended continuation. If the casting fails, the machine 
-%then halts with the blame label.
+To case split a variant, the machine first look at the variant value. If the 
+variant is a left injection, the machine composes the cast in the left 
+injection with the domain casts of the first continuation function, then moves 
+to a state that will apply the new function to the value in the left injection.
+The case for right injections is similar.
 

### 2019-10-22 paper.tex
reply to todos

@@
 Before turning to the definition of the abstract data types, we first
-give the definition of values used by the \effCEK{C}, as they are
-mentioned in the definition of the ADTs.
+give the definition of values and cast results used by the \effCEK{C}, as they 
+are mentioned in the definition of the ADTs.
 
 \todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
-   and should be explained. -JS}
-
-\begin{definition}[Values for the \effCEK{C} machine] \label{def:values-effCEK}
+   and should be explained. -JS
+\\---\\
+What is the standard way to display it? -KC}
+
+\begin{definition}[Values and cast results for the \effCEK{C} machine] 
+\label{def:values-effCEK}
   \[
   \begin{array}{rclr}
-	\stxrule{v}{}{
+	\stxrule{v}{values}{
 		\hcvOOtt \mid
@@
 	}
+\stxrule{r}{cast results}{
+	\rOOsucc{v} \mid
+	\rOOfail{l}
+}
   \end{array}
@@
 
-\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS}
+\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS
+\\---\\
+Fixed. -KC}
 

### 2019-10-22 paper.tex
reply
bisim S D

@@
 \todo[inline]{The use of ``wrap'' obscures this explanation.
-  Consider getting rid of wrap by inlining it. -JS}
+  Consider getting rid of wrap by inlining it. -JS
+\\---\\
+I agree that inlining wrap and ext can improve readability of $\kappa \approx 
+\kappa$, but this would make latex different from Agda, is it alright?
+-KC}
 %
@@
 \begin{lemma}[SoAndSo]
+	\label{thm:lem-apply-cast-SD}
 	Assume $C$ implements Lazy D Cast ADT
@@
 		then $\judgeSreduce{C}{s_1}{s_3}$ for some $s_3$
-	\item If $\judgeSreduce{C}{s_1}{s_3}$ and $\judgeDreduce{s_2}{s_4}$
+	\item If $\judgeSreduce{C}{s_1}{s_3}$ 
+		and  $\judgeDreduce{s_2}{s_4}$ 
 		then $s_3 \approx^{*} s_4$
 \end{enumerate}
-%	Or diagrammatically, 
-%	\[\begin{array}{clclc}
-%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-%	\rotatebox[origin=c]{90}{$\approx$} 
-%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-%	s_{2} & 
-%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
-%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-%	\end{array}\]
-
-%	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
-%	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
-%	$ s_{1} \approx s_{2}$,	
-%	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
-%	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
-%	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
-%	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
-%	Or diagrammatically, 
-%	\[\begin{array}{clclc}
-%	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-%	\rotatebox[origin=c]{90}{$\approx$} 
-%	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-%	s_{2} & 
-%	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
-%	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-%	\end{array}\]
-
+	Or diagrammatically, 
+	\[\begin{array}{clclc}
+	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+	\rotatebox[origin=c]{90}{$\approx$} 
+	& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+	s_{2} & 
+	\longrightarrow_{\text{\ineffCEKD}} & s_2' &
+	\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+	\end{array}\]
 \end{lemma}
@@
 	non-halting state.
-	Part (5) is more interesting.
+	Part (5) is more interesting. Our goal is to prove that one reduction step 
+	in 	\effCEK{C} corresponds to one or more steps in \ineffCEKD.	
 	Consider
 	\[
-	\sOOreturn{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{\kOOcast{c}{\kOOcar{\kappa}}}
+	\sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
+		wrap(\kOOcar{\kappa})
+	}
 	\approx
-	\]
+	\sOOreturn{v_2}{\kOOcar{\kappa}}
+	\]
+
+	By looking at the definition of $v \approx v$, we know
+	\[ c_{11} = seq(\dots seq(id(T_1),cast(T_1,l,T_3)) \dots) \]
+	\[ c_{12} = seq(\dots seq(id(T_2),cast(T_2,l,T_4)) \dots) \] 
+	\[ v_2 = \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
+		\cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
+	\]
+	Thus we have the following reduction in \effCEK{C}. The equation 
+	reasoning employs the fact that $C$ is a monoid.
+	\[
+	\begin{array}{ll}
+&
+\sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{wrap(\kOOcar{\kappa})}
+\\
+\longmapsto_\text{\effCEK{C}} &
+\sOOreturn{v_{11}}{ext(c_{11},\kappa)}
+\\
+= &
+\sOOreturn{v_{11}}{ext(seq(\dots seq(id(T_1),cast(T_1,l,T_3))\dots),\kappa)}
+\\
+= &
+\sOOreturn{v_{11}}{ext(cast(T_1,l,T_3),\dots,\kappa)}
+	\end{array}
+	\]
+
+And we have the following reduction in \ineffCEKD, where the last state is 
+related to the last state in the above sequence.
+
+\[
+\begin{array}{ll}
+& \sOOreturn{
+	\vOOcast{(\vOOcons{v_{21}}{v_{22}})}{		
+	\cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
+}{\kOOcar{\kappa}}
+\\
+\longmapsto_{\mathcal{D}}^{*} &
+\sOOreturn{(\vOOcons{v_{21}}{v_{22}})}{
+	\kOOcar{
+	\kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
+}}
+\\
+\longmapsto_{\mathcal{D}} &
+\sOOreturn{v_{21}}{
+	\kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
+}
+\end{array}
+\]
+
+Other cases are similar. Of course we need the lemma about $applyCast$ 
+(\ref{thm:lem-apply-cast-SD}) when cast applications happen in both machines. 
+And in case spliting, we shall use $cast(T,l,T)=id(T)$ to relate the 
+continuation functions.
 \end{proof}
 
-\todo[inline]{UNDER CONSTRUCTION -KC}
+\todo[inline]{Should I invest time on restating the bisimulation lemma in the 
+standard format? -KC}
 

### 2019-10-22 paper.tex
minor changes

@@
   closer to the halting state.
+  \todo[inline]{I might want to revise this proof. -KC}
 \end{proof}
@@
 
-\todo[inline]{Standardize theorem statement -KC}
 \begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
@@
 		\item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
-		\item If $\judgeSreduce{C}{s_1}{s_3}$ 
-		then $\judgeDreduce{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
-		\item If $\judgeSreduce{C}{s_2}{s_4}$ 
-		then $\judgeDreduce{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
+		\item If $\judgeSreduce{C_1}{s_1}{s_3}$ 
+		then $\judgeSreduce{C_2}{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
+		\item If $\judgeSreduce{C_2}{s_2}{s_4}$ 
+		then $\judgeSreduce{C_1}{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
 	\end{enumerate}
-%	If 
-%	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
-%	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
-%	$s_1 \approx s_2$,
-%	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
-%	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
-%	$s_1' \approx s_2'$
 %	
@@
 	\[\begin{array}{clc}
-	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_3\\
 	\rotatebox[origin=c]{90}{$\approx$} 
@@
 	s_{2} & 
-	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
+	\longrightarrow_{\text{\ineffCEKD}} & s_4 \\
 	\end{array}\]
@@
 In this section we prove \lazyD\ hypercoercion is 
-correct. First we define$applyCast(v,c)$ to make it an instance of Cast ADT, 
+correct. First we define $applyCast(v,c)$ to make it an instance of Cast ADT, 
 then prove that it is also Lazy D, and finally apply 
@@
 
-\figref{hc-applyCast} defines$applyCast(v,c)$for \lazyD\ hypercoercion. 
+\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercion. 
 Applying the identity cast for the 

### 2019-10-22 paper.tex
minor changes
progress

@@
 \newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
-\newcommand{\eOOapp}[2]{#1 \; #2}
+\newcommand{\eOOapp}[2]{(#1 \; #2)}
 \newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
@@
 \newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
+%\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
+%\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
 \newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
@@
 \newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
-\newcommand{\kOOinl}[1]{[\mathtt{inl} \; \square]#1}
-\newcommand{\kOOinr}[1]{[\mathtt{inr} \; \square]#1}
+\newcommand{\kOOinl}[1]{[\mathtt{inl}\; \square]#1}
+\newcommand{\kOOinr}[1]{[\mathtt{inr}\; \square]#1}
 \newcommand{\kOOappI}[3]{
-	[\mathtt{app} \; \square \; \langle#1,#2\rangle ]#3
+	[\square \; \langle#1,#2\rangle]#3
 }
 \newcommand{\kOOappII}[2]{
-	[\mathtt{app} \; #1 \; \square]#2}
+	[#1 \; \square]#2}
 \newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
@@
   representation.
-\item a framework in Agda for proving the correctness of cast
+\item a framework in Agda for proving the correctness of \lazyD{} cast
   represantations.
-\item a formal proof that hypercoercion respects the semantics
+\item a formal proof that hypercoercions respect the semantics
   of the \lazyD{} cast calculus.
@@
 
-In this section we review the coercions in normal form of
-\citet{siek2012interpretations} to motivate the design of
+In this section we review the
+coercions~\citep{henglein1994dynamic,herman2010space} and the normal
+form of \citet{siek2012interpretations} to motivate the design of
 hypercoercions.  We ignore sum types and product types in this
@@
 who are not familiar with them to \citet{siek2012interpretations}.
-%We 
-%will highlight the similarity of normal coercion and hypercoercion, and hope 
-%this would convince you that hypercoercion should be as difficult to implement 
-%as normal coercions.
-%\todo[inline]{I don't think we should try to convince the reader that
-%  hypercoercions are easier to implement. We don't have real evidence
-%  for that.}
 
@@
 	\stxrule{I}{injectable types (\lazyD)}{
-		\POOfun{T}{T}}
+		\POOfun{T}{T} \mid \POOunit}
 	\stxrule{I}{injectable types (\lazyUD)}{
-		\POOfun{\TOOdyn}{\TOOdyn}
+		\POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
 	}
@@
 	\]
-	\caption{Syntax of Normal Coercion}
+	\caption{Syntax of coercions and normal forms}
 	\label{fig:normal-coercion}
@@
 
-\todo[inline]{Give a summary statement about the shape of the normal form. 
--JS
-\\---\\The three-part shape is not obvious before the transformation at 
-the end of the next paragraph. So the summary is given after that. -KC}
-
-\figref{fig:normal-coercion} defines the normal coercion.
-Types, pre-types, and blame labels are as before.
-Let $I$ range over injectable types. An injectable type is a type that can 
-be cast directly to (injection) and from (projection) $\TOOdyn$. The 
-definition of injectable type depends on blame strategy. With \lazyD, all 
-pre-types are injectable. With \lazyUD, only $\POOfun{\TOOdyn}{\TOOdyn}$
-is injectable. 
-Let $c$ range over coercions, a coercion is either injection, projection, 
-identity, failure, sequencing, or function coercion.
+\figref{fig:normal-coercion} gives the grammar for coercions, written
+$c$ and also coercions in normal form, written $\hat{c}$.
+%
+To review, an injection $I!$ takes a value from an injectiable type
+$I$ to type $\TOOdyn$. An injectable type is simply a type that can be
+cast directly to (injection) and from (projection) $\TOOdyn$. The
+definition of injectable type depends on blame strategy. With \lazyD,
+all pre-types are injectable. With \lazyUD, only
+$\POOfun{\TOOdyn}{\TOOdyn}$ is injectable.
+%
+A projection $I?^l$ takes a value from type $\TOOdyn$ to type $I$, or
+halts the program and blames $l$ if the value is of a different type.
+The coercion $\iota$ is the identity, $\bot^{l}$ is the coercion that
+always fails and blames $l$, and $\ncSeq{c_1}{c_2}$ applies $c_1$ and
+then $c_2$ in sequence. The function coercion $\ncFun{c_1}{c_2}$
+applies $c_1$ to the argument of a function and $c_2$ to the return
+value.
+
+Coercions come with a reduction relation so it is natural to ask what
+are their normal forms. The most important of the reduction rules are
+the ones that handle when an injection is followed by a projection,
+which for \lazyUD{} are:
+\begin{align*}
+  I! ; I?^l &\longmapsto \iota \\
+  I_1! ; I_2?^l & \longmapsto \bot^l & \text{if } I_1 \neq I_2
+\end{align*}
+and the rule for pushing sequences below function coercions:
+\begin{align*}
+  (c_1 \to c_2) ; (c_3 \to c_4) & \longmapsto
+  (c_3 ; c_1) \to (c_2 ; c_4)
+\end{align*}
+Of course there are also rules that remove identity coercions.
+
+\todo[inline]{UNDER CONSTRUCTION -Jeremy}
+
 Let $\bar{c}$ range over wrapper coercions, which represent casts in $
-\vOOcast{v}{c}$.
-Let $\hat{c}$ range over normal coercions. If we inline $\bar{c}$ and 
-re-order the cases, the definition of $\hat{c}$ becomes:
+\vOOcast{v}{c}$.  Let $\hat{c}$ range over normal coercions. If we
+inline $\bar{c}$ and re-order the cases, the definition of $\hat{c}$
+becomes:
 \[
@@
 
-\section{Definition of Hypercoercion} \label{sec:hypercoercion-definition}
+\section{Definition of Hypercoercions} \label{sec:hypercoercion-definition}
 
@@
 
-	\caption{Definition of hypercoercion (HC)}
+	\caption{Definition of hypercoercions (HC)}
 	\label{fig:hypercoercion}
@@
 
-This section presents our first contribution, the definition of hypercoercion. 
-The design of hypercoercion is motivated by observations on coercion normal 
-forms: a normal coercion has at most three parts; projections are always at the 
-beginning; injections and failures are always at the end. Hypercoercions have 
-similar shape: a hypercion either is $\hyperCoercionI$, the identity cast for 
+This section presents our first contribution, the definition of
+hypercoercions.  The design of hypercoercions is motivated by
+observations on coercion normal forms: a normal coercion has at most
+three parts; projections are always at the beginning; injections and
+failures are always at the end. Hypercoercions have similar shape: a
+hypercion either is $\hyperCoercionI$, the identity cast for
 $\TOOdyn$, or contains three parts, where the first part is either a
-projection or a no-op while last part is either an injection, a failure, or a 
-no-op.
+projection or a no-op while last part is either an injection, a
+failure, or a no-op.
 
@@
 
-\subsection{\lazyD{} hypercoercion}
+\subsection{\lazyD{} hypercoercions}
 \label{sec:ld-hc}
@@
 \end{proposition}
+
+\subsection{Compact Memory Representation for Hypercoercions}
+
+\todo[inline]{UNDER CONSTRUCTION (a couple paragraphs) -Jeremy}
 
@@
 	}}{}
+
 \hifunrule{
@@
 \sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
-\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
+\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
 \\
 \sOOhalt{l} \\
-\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
+\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
 \end{cases}
@@
 \end{definition}
+
+\todo[inline]{Explain that this is an unusual formulation of a weak
+  bisimulation.  We promise it will all be OK regarding how it is used
+  in the correctness proof for S(C). -JS}
 

### 2019-10-22 paper.tex
casted value -> value in cast

@@
 
-\newcommand{\sOOinspect}[3]{\langle\langle#1,#2\rangle,#3\rangle}
+\newcommand{\sOOinspect}[3]{\langle#1,#2,#3\rangle}
 \newcommand{\sOOreturn}[2]{\langle#1,#2\rangle}
@@
 \newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
-\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
+\newcommand{\hcvOOinj}[2]{\mathtt{Dyn}_{#1}(#2)}
 %\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
@@
 %% transition rules starting from$Eval$states are standard.
-To apply a casted function, the machine first casts $v_1$, the
-operand, then applies the casted operand to $v_2$, the underlying
+To apply a function in cast, the machine first casts $v_1$, the
+operand, then applies the operand in cast to $v_2$, the underlying
 function, and finally cast the result of the function application.
 %
-To take out the first (resp. second) part of a casted pair, the
+To take out the first (resp. second) part of a pair in cast, the
 machine firstly take out the first (resp. second) part of $v$, the
@@
 %
-When the target value is a casted sum, the machine moves the cast from
+When the target value is a sum in cast, the machine moves the cast from
 the target value to continuations functions.
@@
 Let $v$ range over values. A value is either the unit, a function (a
-closure), a pair, a left injection, a right injection, or a casted
-value. As shown by the value typing rules, if the target type of a
-casted value is the dynamic type, the underlying value must be of an
+closure), a pair, a left injection, a right injection, or a value in cast. As 
+shown by the value typing rules, if the target type of a
+value in cast is the dynamic type, the underlying value must be of an
 injectable type. The definition of injectable types depends on blame
@@
 for the \lazyUD\ strategy, a pre-types is injectable if and only if
-all its sub-parts are the dynamic type. If the target type of a casted
-value is a pre-type, the type of the underlying value must have the
+all its sub-parts are the dynamic type. If the target type of a value in cast 
+is a pre-type, the type of the underlying value must have the
 same type constructor.
@@
 give the definition of values and cast results used by the \effCEK{C}, as they 
-are mentioned in the definition of the ADTs.
+are mentioned in the definition of the ADTs. The notation \hcvOOinj{P}{v} 
+stands for values that are cast to the dynamic type.
 
@@
 \\---\\
-What is the standard way to display it? -KC}
+I switch to the standard notation because we have an observation $\oOOinj$ -KC}
 
@@
 Let $v$ range over values. In \ineffCEK{} we have one value
-constructor for all casted value.  In \effCEK{C}, however, we do not
+constructor for all values in casts.  In \effCEK{C}, however, we do not
 have this generic value constructor, instead we push those casts into
@@
 to $(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$. To construct values
-of the dynamic type, we use $(\hcvOOinj{P}{v})$.
+of the dynamic type, we use $\hcvOOinj{P}{v}$.
 
@@
 %
-To relate to a non-casted function in \ineffCEKD, the function in \effCEK{C} 
+To relate to a naked function in \ineffCEKD, the function in \effCEK{C} 
 must use identities as its casts.

### 2019-10-22 paper.tex
remv paranthesis

@@
 % Lazy D cast calculus on space-inefficient CEK
-\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
-\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
-\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
-\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
-\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
+\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{x}} #2}
+\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{x}}^{*} #2}
+\newcommand{\judgeCeval}[2]{eval_{\mathcal{x}}(#1) = #2}
+\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{x} & #2 & #3\\}
+\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{x}} 
+& \highlight{#2} & \highlight{#3} \\}
 % blame calculus on space-efficient CEK
@@
 	\redrule{
-		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
-	}{
-		\sOOinspect{e_1}{\rho}{(\kOOconsI{e_2}{\rho}{\kappa})}
+		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
 	}{}
 	\redrule{
-		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
-	}{
-		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
+		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
+	}{
+		\sOOinspect{e}{\rho}{\kOOinl{\kappa}}
 	}{}
 	\redrule{
-	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
-	}{
-	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
+	\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
+	}{
+	\sOOinspect{e}{\rho}{\kOOinr{\kappa}}
 	}{}
 	\redrule{
-		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
-	}{
-\sOOinspect{e_1}{\rho}{(\kOOappI{e_2}{\rho}{\kappa})}}{}
+		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
+	}{
+\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}
 
 \redrule{
-\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
-\sOOinspect{e}{\rho}{(\kOOcar{\kappa})}}{}
+\sOOinspect{\eOOcar{e}}{\rho}{\kappa}}{
+\sOOinspect{e}{\rho}{\kOOcar{\kappa}}}{}
 
 \redrule{
-	\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
-	\sOOinspect{e}{\rho}{(\kOOcdr{\kappa})}}{}
+	\sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
+	\sOOinspect{e}{\rho}{\kOOcdr{\kappa}}}{}
 
 \redrule{
-\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
-\sOOinspect{e_1}{\rho}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
+\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
+\sOOinspect{e_1}{\rho}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
-\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}
+\sOOreturn{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
+\sOOinspect{e_2}{\rho}{\kOOconsII{v_1}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
-\sOOreturn{(\vOOcons{v_1}{v_2})}{\kappa}}{}
+\sOOreturn{v_2}{\kOOconsII{v_1}{\kappa}}}{
+\sOOreturn{\vOOcons{v_1}{v_2}}{\kappa}}{}
 
 \redrule{
-\sOOreturn{v}{(\kOOinl{\kappa})}}{
-\sOOreturn{(\vOOinl{v})}{\kappa}}{}
+\sOOreturn{v}{\kOOinl{\kappa}}}{
+\sOOreturn{\vOOinl{v}}{\kappa}}{}
 
 \redrule{
-\sOOreturn{v}{(\kOOinr{\kappa})}}{
-\sOOreturn{(\vOOinr{v})}{\kappa}}{}
+\sOOreturn{v}{\kOOinr{\kappa}}}{
+\sOOreturn{\vOOinr{v}}{\kappa}}{}
 
 \redrule{
-\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
-\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}
+\sOOreturn{v_1}{\kOOappI{e_2}{\rho}{\kappa}}}{
+\sOOinspect{e_2}{\rho}{\kOOappII{v_1}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_2}{(\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa})}}{
+\sOOreturn{v_2}{\kOOappII{\vOOfun{\rho}{x}{e}}{\kappa}}}{
 \sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
@@
 %			(\mathtt{app_2} \; v_2 \; 
-%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
+%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa}
 		}
@@
 	\sOOreturn{
-		(\vOOcons{v_1}{v_2})
-	}{(\kOOcar{\kappa})}
+		\vOOcons{v_1}{v_2}
+	}{\kOOcar{\kappa}}
 	}{
@@
 					\POOprod{T_3}{T_4}}}
-		}{(\mathtt{fst} \; \kappa)}
+		}{\mathtt{fst} \; \kappa}
 	}{
@@
 	\sOOreturn{
-		(\vOOcons{v_1}{v_2})
-	}{(\kOOcdr{\kappa})}
+	\vOOcons{v_1}{v_2}
+	}{\kOOcdr{\kappa}}
 	}{
@@
 					\POOprod{T_3}{T_4}}}
-		}{(\mathtt{snd} \; \kappa)}
+		}{\mathtt{snd} \; \kappa}
 	}{
@@
 \redrule{
-\sOOreturn{v_1}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{
-\sOOinspect{e_2}{\rho}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{}
+\sOOreturn{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{
+\sOOinspect{e_2}{\rho}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_2}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{
+\sOOreturn{v_2}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{
 \sOOinspect{e_3}{\rho}{
-	(\kOOcaseIII{v_1}{v_2}{\kappa})
+	\kOOcaseIII{v_1}{v_2}{\kappa}
 }}{}
@@
 \sOOreturn{v_3}{
-	(\kOOcaseIII{(\vOOinl{v})}{v_2}{\kappa})
-%	(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)
-}
-}{
-\sOOreturn{v}{(\kOOappII{v_2}{\kappa})}
+	\kOOcaseIII{\vOOinl{v}}{v_2}{\kappa}
+}
+}{
+\sOOreturn{v}{\kOOappII{v_2}{\kappa}}
 }{}
@@
 	\sOOreturn{v_3}{
-		(\kOOcaseIII{(\vOOinr{v})}{v_2}{\kappa})
-%		(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)
-	}
-}{
-\sOOreturn{v}{(\kOOappII{v_3}{\kappa})}
+		\kOOcaseIII{\vOOinr{v}}{v_2}{\kappa}
+	}
+}{
+\sOOreturn{v}{\kOOappII{v_3}{\kappa}}
 }{}
@@
 	\highlight{\sOOreturn{v_3}{
-		(	\kOOcaseIII{
+		\kOOcaseIII{
 				\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
-			}{v_2}{\kappa})
-%		
-%			(\mathtt{case_3}\;
-%		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
-%		\;v_2\;\kappa)
+			}{v_2}{\kappa}
 	}}
@@
 	\highlight{\sOOreturn{v_3'}{
-			(\kOOcaseIII{v}{v_2'}{\kappa})
+			\kOOcaseIII{v}{v_2'}{\kappa}
 	}}
@@
 	\redrule{
-		\highlight{\sOOreturn{v}{(
+		\highlight{\sOOreturn{v}{
 				\kOOcast{c}{\kappa}
-			)}}
+			}}
 	}{
@@
 	\\
-	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
+	\sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
 \end{cases}}
@@
 \sOOreturn{v}{\kOOmt}}{
-\sOOhalt{observe(v)}}{}
+\sOOhalt{observe(v}}{}
 	\end{array}
@@
 	\inference{
-		\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)} \longrightarrow_{B}^{*} 
-		\sOOhalt{o}
+		\judgeCreduceTrans{
+			\sOOinspect{e}{\emptyset}{\hckOOmt}
+		}{\sOOhalt{o}}		
 	}{
@@
 give the definition of values and cast results used by the \effCEK{C}, as they 
-are mentioned in the definition of the ADTs. The notation \hcvOOinj{P}{v} 
-stands for values that are cast to the dynamic type.
+are mentioned in the definition of the ADTs. The notation $\hcvOOinj{P}{v}$ 
+stands for values that are cast to the dynamic type, as in ...
 
@@
 \\---\\
-I switch to the standard notation because we have an observation $\oOOinj$ -KC}
+I switch to the standard notation because we have an observation $\oOOinj$
+But I forget the origin of this notation, can Jeremy cite it?
+ -KC}
 

### 2019-10-22 paper.tex
remv paranthesis
ld hc assoc proof
minor fix
type in L
a little progress

@@
 	}{
-		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
+		\sOOreturn{\vOOfun{\rho}{x}{e}}{\kappa}
 	}{}
@@
 \redrule{
-\sOOreturn{v_2}{\kOOappII{\vOOfun{\rho}{x}{e}}{\kappa}}}{
+\sOOreturn{v_2}{\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa}}}{
 \sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
@@
 	}
-	\stxrule{\bar{c}}{wrapper coercions}{	
-		\ncInj{I} \mid
-		\ncFun{\hat{c}}{\hat{c}} \mid
-		\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
-	}
+	%% \stxrule{\bar{c}}{wrapper coercions}{	
+	%% 	\ncInj{I} \mid
+	%% 	\ncFun{\hat{c}}{\hat{c}} \mid
+	%% 	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
+	%% }
 %	\stxrulecont{
@@
 \stxrule{\hat{c}}{normal coercions}{
-		\bar{c} \mid
+	\ncFun{\hat{c}}{\hat{c}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
+	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
+}
+\stxrulecont{
 	\ncId \mid
-		\ncFail{l} \mid
 	\ncProj{I}{l} \mid
-		\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
-		\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
-	}
-	\stxrulecont{
-		\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
-		\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
-	}
+	\ncInj{I} \mid
+	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
+	\ncFail{l} 
+}
+	%% \stxrule{\hat{c}}{normal coercions}{
+	%% 	\bar{c} \mid
+	%% 	\ncId \mid
+	%% 	\ncFail{l} \mid
+	%% 	\ncProj{I}{l} \mid
+	%% 	\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
+	%% 	\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
+	%% }
+	%% \stxrulecont{
+	%% 	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
+	%% 	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
+	%% }
 	\end{array}
@@
 
-\figref{fig:normal-coercion} gives the grammar for coercions, written
-$c$ and also coercions in normal form, written $\hat{c}$.
+\figref{fig:normal-coercion} reviews the grammar for coercions,
+written $c$.
 %
@@
 applies $c_1$ to the argument of a function and $c_2$ to the return
-value.
+pvalue.
 
 Coercions come with a reduction relation so it is natural to ask what
-are their normal forms. The most important of the reduction rules are
-the ones that handle when an injection is followed by a projection,
-which for \lazyUD{} are:
-\begin{align*}
-  I! ; I?^l &\longmapsto \iota \\
-  I_1! ; I_2?^l & \longmapsto \bot^l & \text{if } I_1 \neq I_2
-\end{align*}
-and the rule for pushing sequences below function coercions:
-\begin{align*}
-  (c_1 \to c_2) ; (c_3 \to c_4) & \longmapsto
-  (c_3 ; c_1) \to (c_2 ; c_4)
-\end{align*}
-Of course there are also rules that remove identity coercions.
-
-\todo[inline]{UNDER CONSTRUCTION -Jeremy}
-
-Let $\bar{c}$ range over wrapper coercions, which represent casts in $
-\vOOcast{v}{c}$.  Let $\hat{c}$ range over normal coercions. If we
-inline $\bar{c}$ and re-order the cases, the definition of $\hat{c}$
-becomes:
-\[
-\begin{array}{rclr}
-\stxrule{\hat{c}}{normal coercions}{
-	\ncFun{\hat{c}}{\hat{c}} \mid
-	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
-	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
-	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
-	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
-}
-\stxrulecont{
-	\ncId \mid
-	\ncProj{I}{l} \mid
-	\ncInj{I} \mid
-	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
-	\ncFail{l} \mid
-}
-\end{array}
-\]
-
-Three observations on this definition leads to hypercoercion: 
-\begin{enumerate}
-	\item The length of normal coercion is at most three.
-	\item Projections are always at the beginning when present.
-	\item Injections and failures are always at the end when present.
-\end{enumerate}
+are their normal forms. \figref{fig:normal-coercion} defines the
+syntax of coercion in normal form, written $\hat{c}$. Conceptually, a
+coercion in normal form has three parts, all of which are optional.
+It may start with a projection $I?^l$, then it may be followed by a
+function coercion, and then it may be concluded with an injection $I!$
+or a failure $\bot^l$. While this is a simple idea, there are 10
+clauses in the definition for $\hat{c}$!
+
+%% Let $\bar{c}$ range over wrapper coercions, which represent casts in $
+%% \vOOcast{v}{c}$.  Let $\hat{c}$ range over normal coercions. If we
+%% inline $\bar{c}$ and re-order the cases, the definition of $\hat{c}$
+%% becomes:
+%% \[
+%% \begin{array}{rclr}
+%% \end{array}
+%% \]
+
+%% Three observations on this definition leads to hypercoercion: 
+%% \begin{enumerate}
+%% 	\item The length of normal coercion is at most three.
+%% 	\item Projections are always at the beginning when present.
+%% 	\item Injections and failures are always at the end when present.
+%% \end{enumerate}
 
@@
 This section presents our first contribution, the definition of
-hypercoercions.  The design of hypercoercions is motivated by
-observations on coercion normal forms: a normal coercion has at most
-three parts; projections are always at the beginning; injections and
-failures are always at the end. Hypercoercions have similar shape: a
+hypercoercions.  The design of hypercoercions is motivated by the
+observation that a normal coercion has at most three parts;
+projections are always at the beginning; injections and failures are
+always at the end. Hypercoercions make this structure explicit: a
 hypercion either is $\hyperCoercionI$, the identity cast for
 $\TOOdyn$, or contains three parts, where the first part is either a
-projection or a no-op while last part is either an injection, a
-failure, or a no-op.
+projection or the identity and the last part is either an injection, a
+failure, or the identity.
+
+\todo[inline]{What about the middlepart? -JS}
 
@@
 \end{proposition}
-\begin{proof}
-	By induction on hypercoercion(s).
+\begin{proof} Part (1) and (2) are by induction on $c$. Part (3) is by 
+induction on $c_2$ and case analysis on $c_1$ and $c_3$.
 \end{proof}
@@
 	\hiredruleS{
-		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
-	}{
-		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
+		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
+	}{
+		\sOOreturn{\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)}}{\kappa}
 	}{}
 	\redruleS{
-		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
+		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
 	}{
@@
 	\redruleS{
-		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
+		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
 	}{
@@
 	\redruleS{
-		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
+		\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
 	}{
@@
 	\redruleS{
-		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
+		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
 	}{
@@
 	\redruleS{
-		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
+		\sOOinspect{\eOOcar{e})}{\rho}{\kappa}}{
 		\sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}
@@
 	\redruleS{
-		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
+		\sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
 		\sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}
@@
 	\redruleS{
-		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
+		\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
 		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
@@
 	\\
-	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
+	\sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
 	\end{cases}
@@
 	\continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
-	\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{}
+	\sOOreturn{\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)}}{\kappa}}{}
 
@@
 	\continue{v}{\kOOinl{\kappa}}}{
-	\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{}
+	\sOOreturn{\hcvOOinl{v}{id(T)}}{\kappa}}{}
 
@@
 	\continue{v}{\kOOinr{\kappa}}}{
-	\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{}
+	\sOOreturn{\hcvOOinr{v}{id(T)}}{\kappa}}{}
 
@@
 \hifunrule{
-	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
+	\continue{v_2}{\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa}}}{
 \begin{cases}
@@
 \[
-	\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_1)}(e)}{\sOOhalt{o}}
+\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
 \]
@@
 	have 
-	\[\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_2)}(e)}{\sOOhalt{o}}\]
+\[
+\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
+\]
 	that is, $\judgeSreduce{C_2}{e}{o}$
@@
 \\---\\
-Fixed. -KC
-\\---\\
-Need to define load. -KC}
+Fixed. -KC}
 \end{proof}

### 2019-10-22 paper.tex
rm todo
reply

@@
 
+% LCast
+\newcommand{\lsOOcast}[3]{\cOOcast{#1}{#2}{#3}}
+\newcommand{\lcOOnull}[0]{[]}
+\newcommand{\lcOOcons}[2]{#1 \; :: \; #2}
+
 \begin{document}
@@
 $\TOOdyn$, or contains three parts, where the first part is either a
-projection or the identity and the last part is either an injection, a
-failure, or the identity.
-
-\todo[inline]{What about the middlepart? -JS}
+projection or the identity, the last part is either an injection, a
+failure, or the identity, and each kind of middle part corresponds to a type 
+constructor and include hypercoercion(s) for subpart(s) of corresponding values.
+\todo[inline]{What about the middlepart? -JS
+\\---\\
+Fixed. -KC}
 
@@
 
-\todo[inline]{KC, please add the definition of $L$ -JS}
+\begin{figure}
+Syntax
+\[
+\begin{array}{rclr}
+\stxrule{c}{casts}{\lcOOnull{} \mid \lcOOcons{s}{c}}
+\stxrule{s}{steps}{\lsOOcast{T}{l}{T}}
+\end{array}
+\]
+
+Steps Typing
+\fbox{$\judgeTypeFT{s}{T}{T}$}
+\begin{gather*}
+\inference{
+	T_1 \neq T_2
+}{
+	\judgeTypeFT{\lsOOcast{T_1}{l}{T_2}}{T_1}{T_2}
+}
+\end{gather*}
+
+Casts typing
+\fbox{$\judgeTypeFT{c}{T}{T}$}
+\begin{gather*}
+\inference{
+}{
+	\judgeTypeFT{\lcOOnull}{T}{T}
+}
+\quad
+\inference{
+	\judgeTypeFT{s}{T_1}{T_2} &
+	\judgeTypeFT{c}{T_2}{T_3}
+}{
+	\judgeTypeFT{\lcOOcons{s}{c}}{T_1}{T_3}
+}
+\end{gather*}
+
+\fbox{$seq(c,c)=c$}
+\[
+\begin{array}{rclr}
+\funrule{seq(\lcOOnull,c)}{c}{}
+\funrule{seq(\lcOOcons{s}{c'},c)}{\lcOOcons{s}{seq(c',c)}}{}
+\end{array}
+\]
+
+\fbox{$id(T)=c$}
+\[
+\begin{array}{rclr}
+\funrule{id(T)}{\lcOOnull}{}
+\end{array}
+\]
+
+\fbox{$cast(T,l,T)$}
+\[
+\begin{array}{rclc}
+\funrule{cast(T_1,l,T_2)}{
+	\lcOOnull
+}{
+	\sidecond{T_1 = T_2}
+}
+\funrule{cast(T_1,l,T_2)}{
+	\lcOOcons{\lsOOcast{T_1}{l}{T_2}}{\lcOOnull}
+}{
+	\sidecond{T_1 \neq T_2}
+}
+\end{array}
+\]
+
+\fbox{$appS(v,s) = r$}
+\[
+\begin{array}{rclr}
+\funrule{
+	appS(v,\cOOcast{\star}{l}{\star})
+}{
+	\rOOsucc{v}
+}{}
+\funrule{
+	appS(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
+}{
+	\rOOsucc{v}
+}{\sidecond{P_1 = P_2}}
+\funrule{
+appS(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
+}{
+appS(v,\cOOcast{P_1}{l_2}{P_2})
+}{\sidecond{P_1 \neq P_2}}
+\funrule{
+	appS(v,\cOOcast{P}{l}{\star})
+}{
+	\rOOsucc{\hcvOOinj{P}{v}}
+}{}
+\funrule{
+	appS(v,\lsOOcast{\POOunit}{l}{\POOunit})
+}{
+	\rOOsucc{v}
+}{}
+\funrule{
+	appS(
+		\hcvOOfun{c_1}{\rho}{x}{e}{c_2},
+		\lsOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}})
+}{
+	\rOOsucc{(\hcvOOfun{c_1'}{\rho}{x}{b}{c_2'})}
+}{
+	\\ &&
+	\text{where} \;
+	c_1' = seq(cast(T_3,l,T_1),c_1)
+	\\ &&
+	\text{and} \;
+	c_2' = seq(c_2,cast(T_2,l,T_4))
+}
+
+\funrule{
+	appS(
+		\hcvOOcons{v_1}{c_1}{v_2}{c_2},
+		\lsOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}
+}{
+	\rOOsucc{(\hcvOOcons{v_1}{c_1'}{v_2}{c_2'})}
+}{
+\\ &&
+\text{where} \;
+c_1' = seq(c_1,cast(T_1,l,T_3))
+\\ &&
+\text{and} \;
+c_2' = seq(c_2,cast(T_2,l,T_4))
+}
+\funrule{
+	appS(\hcvOOinl{v}{c},\lsOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}})
+}{
+	\rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})}
+}{}
+\funrule{
+	appS(\hcvOOinr{v}{c},\lsOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}})
+}{
+	\rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})}
+}{}
+\funrule{
+	appS(v,\cOOcast{P_1}{l}{P_2})
+}{
+	\rOOfail{l}
+}{\sidecond{\neg P_1 \smile P_2}}
+
+\end{array}
+\]
+
+\fbox{$applyCast(v,c) = r$}
+\[
+\begin{array}{rclr}
+\funrule{
+	applyCast(v,\lcOOnull)
+}{
+	\rOOsucc{v}
+}{}
+\funrule{
+	applyCast(v,\lcOOcons{s}{c})
+}{
+	applyStep(v,s) >>= \lambda v. applyCast(v,c)
+}{}
+\end{array}
+\]
+
+	\caption{The $L$ Lazy D Cast ADT}
+\end{figure}
 

### 2019-10-22 paper.tex
minor edit

@@
 hypercion either is $\hyperCoercionI$, the identity cast for
-$\TOOdyn$, or contains three parts, where the first part is either a
-projection or the identity, the last part is either an injection, a
-failure, or the identity, and each kind of middle part corresponds to a type 
-constructor and include hypercoercion(s) for subpart(s) of corresponding values.
-\todo[inline]{What about the middlepart? -JS
-\\---\\
-Fixed. -KC}
-
-\figref{fig:hypercoercion} defines the syntax of hypercoercions. Types, 
-pre-types, and blame labels are as before.
-
-Let $c$ range over hypercoercions. A hypercoercion either is the identity 
-cast between the dynamic types, or includes a head, a middle, and a tail. 
-Let $h$ range over heads. A head is either a no-op, or a projection.
-Let $m$ range over middles. There is a one-to-one 
-correspondence between middles and type constructors. 
-We generalize shallow-consistency to middles $m \smile m$ in the obvious way.
-Let $t$ range over tails. A tail is either a no-op, an injection, or a 
+$\TOOdyn$, or contains three parts: the head is either a projection or
+the identity, the tail is either an injection, a failure, or the
+identity, and the middle involves coercions underneath a type
+constructor, i.e., coercions between function, pair, and sum types.
+
+\figref{fig:hypercoercion} defines the syntax of
+hypercoercions. Types, pre-types, and blame labels are as before.  Let
+$c$ range over hypercoercions. A hypercoercion either is the identity
+cast between the dynamic types, or includes a head, a middle, and a
+tail.  Let $h$ range over heads. A head is either a no-op, or a
+projection.  Let $m$ range over middles. There is a one-to-one
+correspondence between middles and type constructors.  We generalize
+shallow-consistency to middles $m \smile m$ in the obvious way.  Let
+$t$ range over tails. A tail is either a no-op, an injection, or a
 failure.

### 2019-10-23 paper.tex
cite well

@@
 give the definition of values and cast results used by the \effCEK{C}, as they 
-are mentioned in the definition of the ADTs. The notation $\hcvOOinj{P}{v}$ 
-stands for values that are cast to the dynamic type, as in ...
+are mentioned in the definition of the ADTs. The $\hcvOOinj{P}{v}$ stands for 
+values that are cast to the dynamic type, as in \citet{wadler2009well}.
 
@@
 \\---\\
-I switch to the standard notation because we have an observation $\oOOinj$
-But I forget the origin of this notation, can Jeremy cite it?
- -KC}
+Fixed. -KC}
 

### 2019-10-23 paper.tex
a little proof, a few revision

@@
 
-\begin{proposition}[$L$ properties]\ 
+\begin{proposition}[$L$ properties]\label{thm:L-LazyD-monoid}\ 
   \begin{enumerate}
@@
 \end{proposition}
+\begin{proof}
+	Part (1) is straightforward because property (1) and (2) are trivial and 
+	that $appS$ basically repeats property (3) - (11).
+	Part (2) is true because in $L$ casts are list, $seq(c,c)$ is list 
+	appending, and $id(T)$ is the empty list. Lists is know to be a monoid 
+	where the binary operation is appending and the identity element is the 
+	empty list.
+	Part (3) follows immediately from the definition of $cast(T,l,T)$
+\end{proof}
 
@@
 \end{lemma}
+\begin{proof}
+	Immedialy from Correctness of \effCEK{C} \ref{thm:surely-monoidic-eval} and 
+	L properties \ref{thm:L-LazyD-monoid}.
+\end{proof}
 
@@
 
-\begin{lemma}[\lazyD{} hypercoercion is a \lazyD Cast ADT]
+\begin{lemma}[\lazyD{} hypercoercion is a \lazyD{} Cast ADT]
 	\label{thm:hc-surely-lazyD}

### 2019-10-23 paper.tex
todo
untabify

@@
 
-\subsection{Coercions in Normal Form} 
+\subsection{Coercions and Normal Forms} 
 \label{sec:coercion-calculus}
@@
 form of \citet{siek2012interpretations} to motivate the design of
-hypercoercions.  We ignore sum types and product types in this
-section, because \citet{siek2012interpretations} did not discuss
-them. We assume a basic familiarity with coercions and direct readers
-who are not familiar with them to \citet{siek2012interpretations}.
+hypercoercions.  We omit sum types and product types in this section,
+because \citet{siek2012interpretations} did not discuss them. We
+assume a basic familiarity with coercions and direct readers who are
+not familiar with them to \citet{siek2012interpretations} and
+\citet{siek2015blame}.
 
@@
 The coercion $\iota$ is the identity, $\bot^{l}$ is the coercion that
-always fails and blames $l$, and $\ncSeq{c_1}{c_2}$ applies $c_1$ and
+always fails and blames $l$, and $(\ncSeq{c_1}{c_2})$ applies $c_1$ and
 then $c_2$ in sequence. The function coercion $\ncFun{c_1}{c_2}$
@@
 
-Coercions come with a reduction relation so it is natural to ask what
-are their normal forms. \figref{fig:normal-coercion} defines the
-syntax of coercion in normal form, written $\hat{c}$. Conceptually, a
-coercion in normal form has three parts, all of which are optional.
-It may start with a projection $I?^l$, then it may be followed by a
-function coercion, and then it may be concluded with an injection $I!$
-or a failure $\bot^l$. While this is a simple idea, there are 10
-clauses in the definition for $\hat{c}$!
+Coercions come with a reduction relation so it is natural to ask about
+their normal forms. \figref{fig:normal-coercion} defines the syntax of
+coercion in normal form, written $\hat{c}$. Conceptually, a coercion
+in normal form has three parts, all of which are optional.  It may
+start with a projection $I?^l$, followed by a function coercion, and
+then concluded with an injection $I!$ or a failure $\bot^l$. While
+this is a simple idea, there are 10 clauses in the definition for
+$\hat{c}$!
 
@@
 
-	hypercoercion typing \fbox{$c : T \Longrightarrow T$}
+  Hypercoercion typing \fbox{$c : T \Longrightarrow T$}
   \begin{gather*}
@@
 hypercoercions.  The design of hypercoercions is motivated by the
-observation that a normal coercion has at most three parts;
-projections are always at the beginning; injections and failures are
-always at the end. Hypercoercions make this structure explicit: a
-hypercion either is $\hyperCoercionI$, the identity cast for
-$\TOOdyn$, or contains three parts: the head is either a projection or
-the identity, the tail is either an injection, a failure, or the
-identity, and the middle involves coercions underneath a type
-constructor, i.e., coercions between function, pair, and sum types.
-
-\figref{fig:hypercoercion} defines the syntax of
-hypercoercions. Types, pre-types, and blame labels are as before.  Let
-$c$ range over hypercoercions. A hypercoercion either is the identity
-cast between the dynamic types, or includes a head, a middle, and a
-tail.  Let $h$ range over heads. A head is either a no-op, or a
-projection.  Let $m$ range over middles. There is a one-to-one
-correspondence between middles and type constructors.  We generalize
-shallow-consistency to middles $m \smile m$ in the obvious way.  Let
-$t$ range over tails. A tail is either a no-op, an injection, or a
-failure.
-
-Subsection~\ref{sec:ld-hc} defines functions that construct \lazyD\ 
-hypercoercions. Subsection~\ref{sec:lud-hc} defines the \lazyUD\ counterparts. 
-Functions that apply hypercoercions to values are deferred to 
-Section~\ref{sec:hypercoercion-correctness} because they depends on a new 
-definition of values, which is part of the framework in
+observation that a normal coercion has at most three
+parts. Hypercoercions make this structure explicit: a hypercion $c$ is
+either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or contains
+three parts: a head, middle, and tail, as defined in
+\figref{fig:hypercoercion}.
+\begin{itemize}
+\item The head $h$ is either a projection or the identity,
+\item the middle $m$ involves coercions that preserve a type
+  constructor, i.e., coercions between function, pair, sum types, and
+  unit types, and
+\item the tail $t$ is either an injection, a failure, or the identity.
+\end{itemize}
+There is a one-to-one correspondence between middle coercions and type
+constructors.  We generalize shallow-consistency to middles $m \smile
+m$ in the obvious way.
+
+Subsection~\ref{sec:ld-hc} defines functions that construct
+\lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines the
+\lazyUD\ counterparts.  The functions that apply hypercoercions to
+values are defined later in
+Section~\ref{sec:hypercoercion-correctness}, after we introduce the
+space-efficient machine and its definition of values in
 Section~\ref{sec:framework}.
@@
 
+\todoKC{write conclusion. -KC}
+
 %% Acknowledgments

### 2019-10-23 paper.tex
edits in section 3

@@
   \end{gather*}
-        \caption{Definition of machine state and auxilliary data
+        \caption{Definition of machine state and auxiliary data
           structures.}
@@
     \rOOfail{l}
-  }{\sidecond{\neg P_1 \smile P_2}}
+  }{\sidecond{P_1 \not\smile P_2}}
 
@@
     \sidecond{
-      \neg \; m_1 \smile m_2
+       m_1 \not\smile m_2
       \; \text{and} \;
@@
 \sidecond{
-  \neg \; m_1 \smile m_2
+  m_1 \not\smile m_2
   \; \text{and} \;
@@
   }
-%
-% \comprule{
-%   \hyperCoercionC{h}{m_1}{t_1}
-% }{
-%   \hyperCoercionC{\epsilon}{m_2}{t_2}
-% }{
-%   \hyperCoercionC{h}{m'}{t'}
-% }{
-%   \sidecond{
-%     m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
-%      \; \text{and} \;
-%      \forall l. t \neq \bot^{l}
-%   }
-% }
-% 
-% \comprule{
-%   \hyperCoercionC{h}{m_1}{t_1}
-% }{
-%   \hyperCoercionC{?^{l'}}{m_2}{t_2}
-% }{
-%   \hyperCoercionC{h}{m'}{t'}
-% }{
-%   \sidecond{
-%     m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
-%     \; \text{and} \;
-%     \forall l. t \neq \bot^{l} 
-%   }
-% }
   \end{array}
@@
 
-\figref{fig:HC-D} defines functions that construct \lazyD{} hypercoercions. We 
-expect language implementations to call $id(T)$, which constructs an 
-identity, $seq(c,c)$, which composes two hypercoercions, and $
-cast(T_1,l,T_2)$, which translate a cast to a hypercoercion. Other functions 
-in the figure are their helpers.
-
-Let $\ell$ range over $\epsilon$ and labels.
-$ c_1 \fatsemi^\ell c_2$ composes hypercoercion $c_1$ and hypercoercion $c_2$.
-When both $c_1$ and $c_2$ are $\hyperCoercionI$, their 
-composition is also $\hyperCoercionI$.
-When $c_1$ is $\hyperCoercionI$ but $c_2$ is not, the head of the 
-composition must be a projection. In this 
-case, if the head of $c_2$ is a projection, we reuse it. Otherwise, we need a 
-label to build the projection. Since the head of $c_2$ is $\epsilon$, its 
-source type must be a pretype. Thus we know $\ell$ must be a label and put it 
-in the projection. 
-When $c_1$ ends with a failure, the composition is $c_1$ itself. In all 
-remaining cases, we shall assume that $c_1$ does not end with 
-a failure.
-When $m_1$ and $m_2$ have different top constructors ($\neg\;m_1 \smile 
-m_2$), proceeding to $m_2$ can not make sense. So we end the composition 
-with a failure. To do so we need a label. When $c_2$ starts with a 
-projection, we shall accuse it of casting a value to a shallowly inconsistent 
-type. When $c_2$ starts with a no-op, $\ell$ must be a label. And we accuse 
-it of composing shallowly inconsistent hypercoercions. The last two cases 
-compose $m_1$ and $m_2$ with a helper function $m \fatsemi^\ell m$, which 
-assumes its inputs have the same top constructor. The definition of $m 
-\fatsemi^\ell m$ is straightforward. Going back to the last two cases of $c_1 
-\fatsemi^\ell c_2$. When $c_2$ starts with a projection, we have no clue 
-whether the target type of $m_1$ is the same as the source of $m_2$, 
-although we know they are shallowly consistent. So we give the $l$ in the 
-projection to $m \fatsemi^\ell m$. When $c_2$ starts with a no-op, we reuse 
-the $\ell$.
-
-$seq(c_1,c_2)$ requires that the target type of $c_1$ is the same as the 
-source of $c_2$. $c \fatsemi^\ell c$ does the job for it.
-$id(T)$ constructs an identity coercion of $T$ with the help of $id(P)$. 
-Their definitions are straightforward.
-$cast(T_1,l,T_2)$ constructs a coercion from a source type, a label, and a 
-target type. $c \fatsemi^\ell c$ does the most job.
-
-\begin{proposition}[\lazyD\ hypercoercion is a monoid]
+\figref{fig:HC-D} defines the functions $id$, $seq$, and $cast$ that
+construct \lazyD{} hypercoercions, towards satisifying the Cast ADT.
+\figref{fig:HC-D} also defines some auxiliary functions.
+
+The $seq$ operator is defined in terms of coercion composition, which
+is the key to compressing coercions and maintaining space efficiency.
+A composition operator for coercions typically requires the target
+type of the first coercion to match the source type of the second.
+However, it is useful to relax this restriction for the D blame
+tracking strategy.
+%
+We shall need optional blame labels, written $\ell$ , that range over
+$\epsilon$ or $l$. Then we write composition of hypercoercions as $c_1
+\fatsemi^\ell c_2$.  When both $c_1$ and $c_2$ are $\hyperCoercionI$,
+their composition is also $\hyperCoercionI$.  If the head of $c_2$ is
+a projection, the result is $c_2$.  Otherwise, we need a label to
+build the projection. Since the head of $c_2$ is $\epsilon$, its
+source type must be a pretype. Thus we know $\ell$ must be a label and
+we put it in the projection. When $c_1$ ends with a failure, the
+composition is $c_1$ itself. In all the remaining cases, $c_1$ does
+not end with a failure.  When $m_1$ and $m_2$ have different top
+constructors ($m_1 \not\smile m_2$), the result is a failure coercion,
+which needs a label. When $c_2$ starts with a projection, it is to
+blame for casting a value to a shallowly inconsistent type. When $c_2$
+starts with a no-op, $\ell$ must be a label. And we blame it for
+composing shallowly inconsistent hypercoercions. The last two cases
+compose $m_1$ and $m_2$ with the auxilliary function $m \fatsemi^\ell
+m$, which assumes its inputs have the same top constructor. The
+definition of $m \fatsemi^\ell m$ is a straightforward structural
+recursion. Going back to the last two cases of $c_1 \fatsemi^\ell
+c_2$. When $c_2$ starts with a projection, we do not know whether the
+target type of $m_1$ matches the source of $m_2$, although we know
+they are shallowly consistent. So we use the $l$ in the projection to
+compose the middles $m_1 \fatsemi^l m_2$. When $c_2$ starts with a
+no-op, we compose the middles using $\ell$.
+
+The definitions of $id(T)$ and $cast(T_1,l,T_2)$ are straightforward,
+although $cast(T_1,l,T_2)$ is unusual in its use of $id$ and
+composition.
+
+The proof of correctness for hypercoercions (in
+Section~\ref{secc:framework:monoid-correct}) relies on the following
+two basic properties of hypercoercions.
+
+\begin{proposition}[\lazyD\ hypercoercions form a monoid]
   \label{thm:hc-monoid}
@@
 \end{proposition}
-\begin{proof} Part (1) and (2) are by induction on $c$. Part (3) is by 
-induction on $c_2$ and case analysis on $c_1$ and $c_3$.
+\begin{proof}
+  Part (1) and (2) are by induction on $c$. Part (3) is by induction
+  on $c_2$ and case analysis on $c_1$ then $c_3$.
 \end{proof}
 
-\begin{proposition}[]
+\begin{proposition}[Identity Casts]
   For all $T$ and $l$, $cast(T,l,T) = id(T) $
@@
   \item[$cast(T_1,l,T_2)$] constructs a cast from $T_1$ to $T_2$
-  \item[$ applyCast(v,c)$] applies a cast to a value, producing a result
+  \item[$applyCast(v,c)$] applies a cast to a value, producing a result
   \end{description}
@@
     \]
-  \item if $v : T_1$ and $\neg T_1 \smile T_2$,
+  \item if $v : T_1$ and $T_1 \not\smile T_2$,
     then $applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
@@
   \rOOfail{l}
-}{\sidecond{\neg P_1 \smile P_2}}
+}{\sidecond{P_1 \not\smile P_2}}
 
@@
   }{
-    \sidecond{\neg v \smile m}
+    \sidecond{v \not\smile m}
   }

### 2019-10-23 paper.tex
check

@@
 
-\todo[inline]{Jeremy needs to add text. -JS}
-
-Figure~\ref{fig:HC-UD}
+Hypercoercions for the UD blame tracking strategy have the same syntax
+as for D (\figref{fig:hypercoercion}), but the definitions of $id$,
+$cast$, and $seq$, given Figure~\ref{fig:HC-UD}, differ from D.
+Again, the $seq$ operator is defined in terms of composition, but here
+composition $c_1 \fatsemi c_2$ makes the usual assumption that the
+target type of $c_1$ matches the source type of $c_2$.  The definition
+of composition for UD is particularly straightfoward. The first two
+lines say that $\hyperCoercionI$ acts as the identity on both the left
+and right. The third line handles the case when both the tail of $c_1$
+and the head of $c_2$ are no-ops, in which case the middles types
+$m_1$ and $m_2$ are composed via an auxiliary composition
+operator. This compose operator for middle coercions assumes that its
+inputs are shallowly consistent.  The fourth line handles the
+important case when the tail of $c_1$ is an injection and the head of
+$c_2$ is a projection. If the two middle coercions are shallowly
+consistent, then they can be composed. If not, the tail of the result
+is a failure coercion with the projection's label.  The last line
+handles the case when the tail of $c_1$ is a failure, in which case
+the result of composition is $c_1$.
 
@@
 \end{proposition}
+
+\todo[inline]{talk about $cast(T,l,T)$. -JS}
+
+\todo[inline]{I need to add $cast(T,l,T) = id(T)$. -JS}
 

### 2019-10-23 paper.tex
cast for UD

@@
 as for D (\figref{fig:hypercoercion}), but the definitions of $id$,
-$cast$, and $seq$, given Figure~\ref{fig:HC-UD}, differ from D.
-Again, the $seq$ operator is defined in terms of composition, but here
+$cast$, and $seq$, differ from D.  Again, the $seq$ operator
+(Figure~\ref{fig:HC-UD}) is defined in terms of composition, but here
 composition $c_1 \fatsemi c_2$ makes the usual assumption that the
@@
 
+The definition of $id$ is straightforward (Figure~\ref{fig:HC-UD}) .
+
 \begin{figure}
@@
   \]
-
   \caption{Lazy UD Hypercoercions}
@@
 \end{figure}
-
-Figure~\ref{fig:HC-UD-cast}
 
@@
 
-\todo[inline]{talk about $cast(T,l,T)$. -JS}
+The $cast$ function is defined in Figure~\ref{fig:HC-UD-cast}.  Prior
+presentations of this function do not use auxiliary functions, as we
+do here. The reason that we introduction the auxiliary functions
+$\mathit{castToDyn}$, $\mathit{castFromDyn}$, $\mathit{castToInj}$,
+and $\mathit{castFromInj}$, is to ensure that all of the are
+structurally recursive, which makes them straightforward to define in
+Agda.
 

### 2019-10-23 paper.tex
minor edits

@@
 parts. Hypercoercions make this structure explicit: a hypercion $c$ is
-either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or contains
+either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or it contains
 three parts: a head, middle, and tail, as defined in
@@
 \end{itemize}
-There is a one-to-one correspondence between middle coercions and type
+There is a close correspondence between middle coercions and type
 constructors.  We generalize shallow-consistency to middles $m \smile
@@
 
-Subsection~\ref{sec:ld-hc} defines functions that construct
+Subsection~\ref{sec:ld-hc} defines the $id$, $seq$, and $cast$
+functions that construct
 \lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines the

### 2019-10-23 paper.tex
finished compact representation paragraph

@@
 of a bit-level representation that minimizes the need for pointers and
-fits all first-order casts into 64 bits. We present two flavors of
-hypercoercions to support the two blame tracking strategies from the
-literature: D and UD~\citep{siek2009exploring}. We are interested in
-the D blame tracking strategy because it comes with a more
-straightforward notion safe cast compared to
-UD~\citep{siek2009exploring}, which is why D was chosen Grift
-compiler. We are also intersted in UD because it plays a prominent
-role in the gradual typing literature \citep{wadler2009well}. The
-semantics of casts can also be lazy or
+fits all first-order casts into 64 bits.
+%
+We present two flavors of hypercoercions to support the two blame
+tracking strategies from the literature: D and
+UD~\citep{siek2009exploring}. We are interested in the D blame
+tracking strategy because it comes with a more straightforward notion
+safe cast compared to UD~\citep{siek2009exploring}, which is why D was
+chosen Grift compiler. We are also intersted in UD because it plays a
+prominent role in the gradual typing literature
+\citep{wadler2009well}.  The UD hypercoercions were inspired by the
+supercoercions of \citet{garcia2013calculating} (hence the name) and
+the D hypercoercions were inspired by the normal forms of
+\citet{siek2012interpretations}.
+%
+The semantics of casts can be lazy or
 eager~\citep{siek2009exploring}. In this paper we focus on lazy cast
@@
 
-% the following are temporary -JS
-\clearpage
-\pagebreak
-
 \subsection{Coercions and Normal Forms} 
@@
 \begin{figure}
-  Syntax
+  Syntax of Hypercoercions
   \[
@@
 
-\begin{proposition}[\lazyD\ hypercoercions form a monoid]
+\begin{proposition}[\lazyD{} hypercoercions form a monoid]
   \label{thm:hc-monoid}
@@
 
-\begin{proposition}[Identity Casts]
+\begin{proposition}[\lazyD{} Identity Casts]
   For all $T$ and $l$, $cast(T,l,T) = id(T) $
@@
 
-\subsection{\lazyUD{} hypercoercion [Jeremy]}
+\subsection{\lazyUD{} hypercoercions}
 \label{sec:lud-hc}
@@
 
-\begin{proposition}[\lazyUD\ hypercoercions form a monoid]
+\begin{proposition}[\lazyUD{} hypercoercions form a monoid]
   For all $c : T_1 \Longrightarrow T_2$,
@@
 \end{proposition}
+\begin{proof}
+  See the Agda proof at the following URL:
+
+  \url{https://github.com/jsiek/gradual-typing-in-agda/blob/master/HyperCoercions.agda}
+
+\end{proof}
 
@@
 
-\todo[inline]{I need to add $cast(T,l,T) = id(T)$. -JS}
-
-\subsection{Compact Memory Representation for Hypercoercions}
-
-\todo[inline]{UNDER CONSTRUCTION (a couple paragraphs) -Jeremy}
-
-% the following are temporary -JS
-\clearpage
-\pagebreak
+\begin{proposition}[\lazyUD{} Identity Casts]
+  For all $T$ and $l$, $cast(T,l,T) = id(T) $
+\end{proposition}
+\begin{proof}
+  By induction on T.
+\end{proof}
+
+\subsection{Compact Representation of Hypercoercions}
+
+Hypercoercions enable a bit-level representation that is particularly
+compact for the most common-case coercions. The most frequent
+coercions are injections and projections to base types (here
+$\POOunit$ is the only base type, but in a real language the base
+types would include integers, Booleans, etc.) and identity coercions.
+Values of base types are often stored in CPU registers, so it would be
+nice for coercions on base types to also fit in registers, that is, in
+64 bits, so that applying a coercion to a value would not require
+access to main memory, which is an order of magnitude slower than
+accessing registers on a modern CPU.
+%
+Coercions involving non-base types, such as functions types,
+may be arbitrarily large, so in those cases the hypercoercion
+representation can be a pointer to a heap-allocated structure.  Here
+is a sketch for the bit-level representation for hypercoercions.
+
+\begin{itemize}
+\item 1 bit to differentiate between $\hyperCoercionI$
+  and three-part coercions.
+
+\item 1 bit to differentiate between middle coercions of base type
+  versus non-base type.
+
+\item If the middle is of non-base type, then 61 bits represent a
+  pointer to a heap-allocated structure. Heap allocated structures are
+  usually 8-byte aligned, so there are 3 unused bits in a pointer.
+
+\item If the middle is of base type, then the remaining 62 bits are
+  used to represent the head (21 bits), middle (22 bits), and tail (19
+  bits).
+  \begin{itemize}
+  \item The head requires 1 bit to differentiate between $\epsilon$
+    and $?^l$ and then 24 bits could be used for the label $l$.
+  \item The middle would use 11 bits to differentiate all the base types.
+  \item The tail requires 2 bits to differentiate between $\epsilon$,
+    $!$, and $\bot^l$, and could use 24 bits for the label $l$.
+  \end{itemize}
+  In the event that a program requires too many blame labels, then one
+  can fallback to using the heap-allocated structure for more
+  coercions.
+\end{itemize}
 

### 2019-10-23 paper.tex
removed some fixed comments

@@
 
-\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
-   and should be explained. -JS
-\\---\\
-Fixed. -KC}
-
 \begin{definition}[Values and cast results for the \effCEK{C} machine] 
@@
     \hcvOOinr{v}{c} \mid
-    \hcvOOinj{P}{v}
+    \hcvOOinj{I}{v}
   }
@@
 \end{definition}
-
-\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS
-\\---\\
-Fixed. -KC}
 
@@
 that also includes the pairs induced by the rules below.
-\todo[inline]{By ``derived from the definitions'' do you mean
- that it is a congruence? -JS
-\\---\\
-Exactly, fixed. -KC}
 
@@
 \end{lemma}
-\begin{proof} By casing on $s_{1} \approx s_{2}$.
-%
-  \todo[inline]{The above sentence is not normal proof jargon.  Are
-    you doing a proof by cases on $s_{1}
-    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS
-\\---\\
-By casing on the bisimulation relation. -KC}
+\begin{proof} By cases on $s_{1} \approx s_{2}$.
 %
@@
   that is, $\judgeSreduce{C_2}{e}{o}$
-\todo[inline]{Induction on what? -JS
-\\---\\
-Fixed. -KC}
 \end{proof}
@@
 \caption{The $L$ Lazy D Cast ADT}
+\label{fig:L-instance-LazyD}
 \end{figure}
+
+The $L$ cast representation is defined in
+\figref{fig:L-instance-LazyD}.
+
+\todo[inline]{KC, please write a 2-3 sentence overview of
+  the $L$ cast representation. -JS}
 

### 2019-10-24 paper.tex
responded to a question of KC
revise intro

@@
 \end{itemize}
-Recall that in these systems, casts are compressed using a composition
-operator.  Threesomes and supercoercions are good for mechanized
+%Recall that in these systems, casts are compressed using a composition
+%operator.
+These systems compress casts using a compose operator.
+Threesomes and supercoercions are good for mechanized
 metatheory because their compose operators are structurally recursive,
@@
 not structurally recursive, which makes it more difficult to define in
-Agda, requiring what amounts to an explicit proof of termination.
+proof assistants, requiring what amounts to an explicit proof of termination.
 %
@@
 UD~\citep{siek2009exploring}. We are interested in the D blame
-tracking strategy because it comes with a more straightforward notion
+tracking strategy because it comes with a more straightforward notion of
 safe cast compared to UD~\citep{siek2009exploring}, which is why D was
-chosen Grift compiler. We are also intersted in UD because it plays a
+chosen in Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
+interested in UD because it plays a
 prominent role in the gradual typing literature
@@
 be generalized to \lazyUD{} and that it can be applied to coercions in
-normal form and threesomes.
+normal form, threesomes, and supercoercions.
 
@@
   represantations.
-\item a formal proof that hypercoercions respect the semantics
+\item a formal proof that \lazyD\ hypercoercions respect the semantics
   of the \lazyD{} cast calculus.
@@
 
-In Section~\ref{sec:background} we review cast calculi and coercions.
+In Section~\ref{sec:background} we review cast calculi and coercions in normal 
+form. 
 We present hypercoercions in
 Section~\ref{sec:hypercoercion-definition}.  We present a framework
-for proving correctness of cast reprensentations in
+for proving correctness of \lazyD\ cast reprensentations in
 Section~\ref{sec:framework} and use it to prove the correctness of
@@
 \kappa$, but this would make latex different from Agda, is it alright?
--KC}
+-KC
+\\---\\
+Yes, that is alright. Inlining is really a trivial change.
+-JS
+}
 %

### 2019-10-24 paper.tex
blame expressions were forgotten
typos in fig
partially revise sec2

@@
 \newcommand{\eOOapp}[2]{(#1 \; #2)}
-\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
+\newcommand{\eOOcons}[4]{\mathtt{cons}^{\POOprod{#1}{#2}} \; #3 \; #4}
 \newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
 \newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
-%\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
-%\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
-\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
-\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
+\newcommand{\eOOinl}[3]{\mathtt{inl}^{\POOsum{#1}{#2}} \; #3}
+\newcommand{\eOOinr}[3]{\mathtt{inr}^{\POOsum{#1}{#2}} \; #3}
 \newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
@@
 \newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
-%\newcommand{\rOOsucc}[1]{#1}
-%\newcommand{\rOOfail}[1]{#1}
 \newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
@@
 \newcommand{\kOOmt}[0]{\mathtt{stop}}
-\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
-\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
-\newcommand{\kOOinl}[1]{[\mathtt{inl}\; \square]#1}
-\newcommand{\kOOinr}[1]{[\mathtt{inr}\; \square]#1}
+\newcommand{\kOOconsI}[5]{
+	[\mathtt{cons}^{\POOprod{#1}{#2}} \; \square \; \langle#3,#4\rangle ]#5}
+\newcommand{\kOOconsII}[4]{
+	[\mathtt{cons}^{\POOprod{#1}{#2}} \; #3 \; \square]#4}
+\newcommand{\kOOinl}[3]{[\mathtt{inl}^{\POOsum{#1}{#2}}\; \square]#3}
+\newcommand{\kOOinr}[3]{[\mathtt{inr}^{\POOsum{#1}{#2}}\; \square]#3}
 \newcommand{\kOOappI}[3]{
@@
     \POOunit \mid
-    \POOfun{T_1}{T_2} \mid
-    \POOprod{T_1}{T_2} \mid
-    \POOsum{T_1}{T_2}
+    \POOfun{T}{T} \mid
+    \POOprod{T}{T} \mid
+    \POOsum{T}{T}
   }
@@
     \eOOsole{} \mid{}
-    \eOOlam{T_1}{T_2}{x}{e} \mid
-    \eOOapp{e_1}{e_2} \mid
-    \eOOcons{e_1}{e_2} \mid
+    \eOOlam{T}{T}{x}{e} \mid
+    \eOOapp{e}{e} \mid
+    \eOOcons{T}{T}{e}{e} \mid
     \eOOcar{e} \mid
@@
   \stxrulecont{
-    \eOOinl{e} \mid
-    \eOOinr{e} \mid
-    \eOOcase{e_1}{e_2}{e_3} \mid
-    \eOOcast{e}{T_1}{l}{T_2} \mid
+    \eOOinl{T}{T}{e} \mid
+    \eOOinl{T}{T}{e} \mid
+    \eOOcase{e}{e}{e} \mid
+    \eOOcast{e}{T}{l}{T} \mid
     \eOOblame{l}
@@
   $\mathbb{?}$).
-\item We annotate the codomain of a lambda abstraction explicitly
-  because we refer to it in the dynamic semantics. 
+\item We annotate the type of many expressions explicitly because we 
+refer to them in the dynamic semantics. These expressions include cons 
+expressions, left injections, right injections, and lambda abstractions.
 \end{itemize}
@@
     \kOOmt \mid
-    \kOOconsI{e}{\rho}{\kappa} \mid
-    \kOOconsII{v}{\kappa} \mid
-    \kOOinl{\kappa}
+    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
+    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
+    \kOOinl{T_1}{T_2}{\kappa}
   }
   \stxrulecont{
-    \kOOinr{\kappa} \mid
+    \kOOinr{T_1}{T_2}{\kappa} \mid
     \kOOappI{e}{\rho}{\kappa} \mid
@@
   \redrule{
-    \sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
+    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
+  }{
+    \sOOinspect{e_1}{\rho}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}
   }{}
   \redrule{
-    \sOOinspect{\eOOinl{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{\kOOinl{\kappa}}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
+  }{
+    \sOOinspect{e}{\rho}{\kOOinl{T_1}{T_2}{\kappa}}
   }{}
   \redrule{
-  \sOOinspect{\eOOinr{e}}{\rho}{\kappa}
-  }{
-  \sOOinspect{e}{\rho}{\kOOinr{\kappa}}
+  \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
+  }{
+  \sOOinspect{e}{\rho}{\kOOinr{T_1}{T_2}{\kappa}}
   }{}
@@
 \redrule{
-\sOOreturn{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
-\sOOinspect{e_2}{\rho}{\kOOconsII{v_1}{\kappa}}}{}
+\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
+\sOOhalt{(\oOOblame{l})}}{}
 
 \redrule{
-\sOOreturn{v_2}{\kOOconsII{v_1}{\kappa}}}{
+\sOOreturn{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
+\sOOinspect{e_2}{\rho}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{}
+
+\redrule{
+\sOOreturn{v_2}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{
 \sOOreturn{\vOOcons{v_1}{v_2}}{\kappa}}{}
@@
 \redrule{
-\sOOreturn{v}{\kOOinl{\kappa}}}{
+\sOOreturn{v}{\kOOinl{T_1}{T_2}{\kappa}}}{
 \sOOreturn{\vOOinl{v}}{\kappa}}{}
@@
 \redrule{
-\sOOreturn{v}{\kOOinr{\kappa}}}{
+\sOOreturn{v}{\kOOinr{T_1}{T_2}{\kappa}}}{
 \sOOreturn{\vOOinr{v}}{\kappa}}{}
@@
     \kOOmt \mid{}
-    \kOOconsI{e}{\rho}{\kappa} \mid
-    \kOOconsII{v}{\kappa} \mid
-    \kOOinl{\kappa} \mid
-    \kOOinr{\kappa}
+    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
+    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
+    \kOOinl{T_1}{T_2}{\kappa}
   }
   \stxrulecont{
+  	\kOOinr{T_1}{T_2}{\kappa} \mid
     \kOOappI{e}{\rho}{\kappa} \mid
@@
   \redruleS{
-    \sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
+    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
   }{
     \sOOinspect{e_1}{\rho}{
-      wrap(\kOOconsI{e_2}{\rho}{\kappa})
+      wrap(\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa})
     }
@@
   \redruleS{
-    \sOOinspect{\eOOinl{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
+  }{
+    \sOOinspect{e}{\rho}{wrap(\kOOinl{T_1}{T_2}{\kappa})}
   }{}
   \redruleS{
-    \sOOinspect{\eOOinr{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
+  }{
+    \sOOinspect{e}{\rho}{wrap(\kOOinr{T_1}{T_2}{\kappa})}
   }{}
@@
     \sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
+
+\redruleS{
+	\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
+	\sOOhalt{(\oOOblame{l})}}{}
+
   \hiredruleS{
@@
 \funrule{
-  \continue{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
-  \sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
+  \continue{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
+  \sOOinspect{e_2}{\rho}{wrap(\kOOconsII{T_1}{T_2}{v_1}{\kappa})}}{}
 
 \hifunrule{
-  \continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
+  \continue{v_2}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{
   \sOOreturn{\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)}}{\kappa}}{}
@@
 \hifunrule{
-  \continue{v}{\kOOinl{\kappa}}}{
-  \sOOreturn{\hcvOOinl{v}{id(T)}}{\kappa}}{}
+  \continue{v}{\kOOinl{T_1}{T_2}{\kappa}}}{
+  \sOOreturn{\hcvOOinl{v}{id(T_1)}}{\kappa}}{}
 
 \hifunrule{
-  \continue{v}{\kOOinr{\kappa}}}{
-  \sOOreturn{\hcvOOinr{v}{id(T)}}{\kappa}}{}
+  \continue{v}{\kOOinr{T_1}{T_2}{\kappa}}}{
+  \sOOreturn{\hcvOOinr{v}{id(T_2)}}{\kappa}}{}
 
@@
 \\ \\
-  %% \inference{}{
-  %%  \hcvOOtt \approx \vOOtt : \POOunit
-  %% }
-  %% \quad
+   \inference{}{
+    \hcvOOtt \approx \vOOtt : \POOunit
+   }
+   \quad
   \inference{}{
@@
 \hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
-%   \judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
 c_1' = seq(cast(T_3,l,T_1),c_1) \\
@@
 \approx
-\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
+\vOOcast{v_2}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
 : \POOfun{T_3}{T_4}
@@
     \approx
-    \vOOcons{v_2}{v_3}
+    \vOOcons{v_2}{v_4}
     : \POOprod{T_1}{T_2}
@@
   \inference{
-    \hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOsum{T_1}{T_2} \\
+    \hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOprod{T_1}{T_2} \\
     c_1' = seq(c_1,cast(T_1,l,T_3)) \\
@@
     \hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
-    \vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
+    \vOOcast{v_2}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
     : \POOprod{T_3}{T_4}
@@
     \hcvOOinl{v_1}{c'} \approx
-    \vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+    \vOOcast{v_2}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
     : \POOsum{T_3}{T_4} 
@@
   \hcvOOinr{v_1}{c'} \approx
-  \vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
+  \vOOcast{v_2}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
   : \POOsum{T_3}{T_4}

### 2019-10-24 paper.tex
remove subscripts in all syntax definitions
move syntax nonterm names to left side
revise sec2

@@
 \newcommand{\secref}[1]{Section~\ref{#1}}
-\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
-\newcommand{\stxrulecont}[1]{& | & #1 & \\}
+\newcommand{\stxrule}[3]{\text{#2} & #1 & ::= & #3\\}
+\newcommand{\stxrulecont}[1]{& & | & #1 \\}
 \newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
@@
 
-In Section~\ref{sec:background} we review cast calculi and coercions in normal 
-form. 
+In Section~\ref{sec:background} we review cast calculi and coercions. 
 We present hypercoercions in
@@
 In this section, we review lazy cast calculi
-(Section~\ref{sec:cast-calculi}) and coercion in normal form
+(Section~\ref{sec:cast-calculi}) and coercions 
 (Section~\ref{sec:coercion-calculus}).
@@
   \[
-  \begin{array}{rclr}
-  \stxrule{T}{types}{
+  \begin{array}{lrcl}
+  \stxrule{T}{Types}{
     \star \mid{}
@@
   }
-  \stxrule{P}{pre-types}{
+  \stxrule{P}{Pre-types}{
     \POOunit \mid
@@
   }
-  \stxrule{e}{terms}{
+  \stxrule{e}{Terms}{
     \eOOvar{x} \mid{}
@@
 
-%% defines the syntax of the cast calculus and
-%% its static semantics. We extend the syntax of
-%%  with sum and product types.  Let $T$ range
-%% over types. A type is either the dynamic type$\star$(a.k.a. $
-%% \mathtt{Dyn}$, $\mathbb{?}$, or$\mathtt{Unknown}$), or a type
-
-%% As usual we write$T_1 \sim T_2$when$T_1$ and $T_2$ are
-%% consistent. The intuition of $T_1 \sim T_2$ is that $T_1$and $
-%% T_2$have no conflicting type information. Two types are consistent
-%% if one of them is $\star$, or they have the same top-most type
-%% constructor and the corresponding sub-parts are
-%% consistent. Consistency is reflexive and symmetric, but not
-%% transitive.
-
-%% We write$T_1 \smile T_2$when$T_1$ and $T_2$ are
-%% shallowly-consistent, that is, if one of them is $\star$, or they
-%% have the same type constructor at the top. Shallow-inconsistency is
-%% the root of all blame in lazy cast strategies -- casting a value to a
-%% shallowly inconsistent type leads to a blame. Shallow-consistency is
-%% reflexive, symmetric, but not transitive.
-
-%% Let $e$ range over terms. Most terms are standard for a simply-typed
-%% lambda calculus. We annotate the codomain of a lambda abstraction
-%% explicitly because we refer to it in the dynamic semantics. Becuase
-%% this is a cast calculus, we have two additional terms: cast
-%% expressions and blame expressions. Cast expressions perform runtime
-%% type checks and blame expressions raise an error.
-
 \paragraph{Dynamic Semantics}
@@
 machine and Fig.~\ref{fig:state} gives a grammar for machine states
-$s$, including a definition of values and value typing. The
-transitions involving casts are highlighted in red and described in
+$s$, including a definition of values and value typing. 
+%Fig.~\ref{fig:state} gives a grammar for machine states
+%$s$, including a definition of values and value typing and
+%Fig.~\ref{fig:machine-cekc} defines the transition relation of the CEK
+%machine.
+The transitions involving casts are highlighted in red and described in
 more detail below. The other transitions are standard for a CEK
@@
 Corresponding to (1) and (2), the machine state is either in an
-$\mathtt{Eval}$ or $\mathtt{Cont}$ configuration, respectively.
-Additionally, there is the $\mathtt{Halt}$ configuration.
+$\sOOinspect{e}{\rho}{\kappa}$ or $\sOOreturn{v}{\kappa}$ configuration, 
+respectively. Additionally, there is the $\sOOhalt{o}$ configuration.
 
@@
 To apply a function in cast, the machine first casts $v_1$, the
-operand, then applies the operand in cast to $v_2$, the underlying
-function, and finally cast the result of the function application.
+operand, then applies the cast operand to $v_2$, the underlying
+function, and finally cast the return value.
 %
@@
 %
-When the target value is a sum in cast, the machine moves the cast from
-the target value to continuations functions.
+To case split an injection in cast, the machine moves the cast from
+the injection to continuations functions.
 %
@@
   \[
-  \begin{array}{rclr}
-  \stxrule{v}{values}{
+  \begin{array}{lrcl}
+  \stxrule{v}{Values}{
     \vOOtt{} \mid
     \vOOfun{\rho}{x}{e} \mid
-    \vOOcons{v_1}{v_2} \mid
+    \vOOcons{v}{v} \mid
     \vOOinl{v} \mid
@@
   }
-  \stxrule{c}{casts}{
-    \cOOcast{T_1}{l}{T_2}
-  }
-  \stxrule{I}{injectable types (\lazyD)}{
+  \stxrule{c}{Casts}{
+    \cOOcast{T}{l}{T}
+  }
+  \stxrule{I}{Injectable types (\lazyD)}{
     P
   }
-  \stxrule{I}{injectable types (\lazyUD)}{
+  \stxrule{I}{Injectable types (\lazyUD)}{
     \POOunit \mid
@@
   }
-  \stxrule{o}{observations}{
+  \stxrule{o}{Observations}{
     \oOOinj \mid
@@
   }
-  \stxrule{r}{cast results}{
+  \stxrule{r}{Cast results}{
     \rOOsucc{v} \mid
@@
   }
-  \stxrule{s}{states}{
+  \stxrule{s}{States}{
     \sOOinspect{e}{\rho}{\kappa} \mid{}
@@
   }
-  \stxrule{\kappa}{continuations}{
+  \stxrule{\kappa}{Continuations}{
     \kOOmt \mid
-    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
-    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
-    \kOOinl{T_1}{T_2}{\kappa}
+    \kOOconsI{T}{T}{e}{\rho}{\kappa} \mid
+    \kOOconsII{T}{T}{v}{\kappa} \mid
+    \kOOinl{T}{T}{\kappa}
   }
   \stxrulecont{
-    \kOOinr{T_1}{T_2}{\kappa} \mid
+    \kOOinr{T}{T}{\kappa} \mid
     \kOOappI{e}{\rho}{\kappa} \mid
@@
 
-Let $v$ range over values. A value is either the unit, a function (a
-closure), a pair, a left injection, a right injection, or a value in cast. As 
-shown by the value typing rules, if the target type of a
-value in cast is the dynamic type, the underlying value must be of an
-injectable type. The definition of injectable types depends on blame
+Let $v$ range over values. A value is either the unit, a function, a pair, a 
+left injection, a right injection, or a value in cast. 
+As shown by the value typing rules, for values in casts, 
+if the cast is between pre-types, source and target types must have the 
+same type constructor at the top. 
+If the cast is from a pre-type to the dynamic type, the pre-type must be 
+injectable. The definition of injectable types depends on blame
 strategies: for the \lazyD\ strategy, every pre-type is injectable;
-for the \lazyUD\ strategy, a pre-types is injectable if and only if
-all its sub-parts are the dynamic type. If the target type of a value in cast 
-is a pre-type, the type of the underlying value must have the
-same type constructor.
+for the \lazyUD\ strategy, a pre-types is injectable if all its sub-parts are 
+the dynamic type.
+%As shown by the value typing rules, if the target type of a
+%value in cast is the dynamic type, the underlying value must be of an
+%injectable type. The definition of injectable types depends on blame
+%strategies: for the \lazyD\ strategy, every pre-type is injectable;
+%for the \lazyUD\ strategy, a pre-types is injectable if and only if
+%all its sub-parts are the dynamic type. If the target type of a value in cast 
+%is a pre-type, the type of the underlying value must have the
+%same type constructor.
 
@@
 
-Let $o$ range over observations. They are what would be observed if
+Let $o$ range over observations. They are what we would observe if 
 a program terminates. Observations include all value constructors and
@@
 Let $r$ range over cast results. A cast result is either a success, which 
-brings back a value, or a failure, which brings a blame label.
+brings back a value, or a failure, which brings back a blame label.
 
@@
 continuation. The remaining continuations correspond to expressions. For 
-example, $(\mathtt{cons_1} \; e \; \rho \; \kappa)$ is the continuation where 
-we are waiting for the value of the first argument to a $\mathtt{cons}$. And 
-the last continuation, $\langle c \rangle \kappa$ is to cast the value before 
-returning to $\kappa$.
+example, $\kOOconsI{T_1}{T_2}{e}{\rho}{\kappa}$ is the continuation waiting for 
+the first part of the pair. And the last continuation, $\kOOcast{c}{\kappa}$ is 
+to cast the value before returning to $\kappa$.
 
@@
   \[
-  \begin{array}{rclr}
-  \stxrule{I}{injectable types (\lazyD)}{
+  \begin{array}{lrcl}
+  \stxrule{I}{Injectable types (\lazyD)}{
     \POOfun{T}{T} \mid \POOunit}
-  \stxrule{I}{injectable types (\lazyUD)}{
+  \stxrule{I}{Injectable types (\lazyUD)}{
     \POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
   }
-  \stxrule{c}{coercions}{
+  \stxrule{c}{Coercions}{
     \ncInj{I} \mid
@@
 applies $c_1$ to the argument of a function and $c_2$ to the return
-pvalue.
+value.
 
@@
 their normal forms. \figref{fig:normal-coercion} defines the syntax of
-coercion in normal form, written $\hat{c}$. Conceptually, a coercion
+coercions in normal form, written $\hat{c}$. Conceptually, a coercion
 in normal form has three parts, all of which are optional.  It may
@@
   \[
-  \begin{array}{lclr}
-  \stxrule{I}{injectable types (\lazyD)}{P}
-  \stxrule{I}{injectable types (\lazyUD)}{
+  \begin{array}{lrcl}
+  \stxrule{I}{Injectable types (\lazyD)}{P}
+  \stxrule{I}{Injectable types (\lazyUD)}{
     \POOunit \mid
@@
   }
-  \stxrule{c}{hypercoercions}{
+  \stxrule{c}{Hypercoercions}{
     \hyperCoercionI \mid{}
@@
   }
-  \stxrule{h}{heads}{
+  \stxrule{h}{Heads}{
     \epsilon \mid{}
@@
   }
-  \stxrule{m}{middles}{
+  \stxrule{m}{Middles}{
     \POOunit \mid
-    \POOfun{c_1}{c_2} \mid
-    \POOprod{c_1}{c_2} \mid
-    \POOsum{c_1}{c_2}
-  }
-  \stxrule{t}{tails}{
+    \POOfun{c}{c} \mid
+    \POOprod{c}{c} \mid
+    \POOsum{c}{c}
+  }
+  \stxrule{t}{Tails}{
     \epsilon \mid{}
@@
   \[
-  \begin{array}{rclr}
-  \stxrule{\ell}{Maybe$l$}{\epsilon \mid l}
+  \begin{array}{lrcl}
+  \stxrule{\ell}{Maybe $l$}{\epsilon \mid l}
   \end{array}
@@
   \[
-  \begin{array}{rclr}
+  \begin{array}{lrcl}
 % \stxrule{r}{cast results}{
@@
 % }
-  \stxrule{\kappa}{continuation}{
+  \stxrule{\kappa}{Continuation}{
     \kOOcast{c}{k}
   }
-  \stxrule{k}{pre-continuations}{
+  \stxrule{k}{Pre-continuations}{
     \kOOmt \mid{}
-    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
-    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
-    \kOOinl{T_1}{T_2}{\kappa}
+    \kOOconsI{T}{T}{e}{\rho}{\kappa} \mid
+    \kOOconsII{T}{T}{v}{\kappa} \mid
+    \kOOinl{T}{T}{\kappa}
   }
   \stxrulecont{
-  	\kOOinr{T_1}{T_2}{\kappa} \mid
+  	\kOOinr{T}{T}{\kappa} \mid
     \kOOappI{e}{\rho}{\kappa} \mid
@@
 \[
-\begin{array}{rclr}
-\stxrule{c}{casts}{\lcOOnull{} \mid \lcOOcons{s}{c}}
-\stxrule{s}{steps}{\lsOOcast{T}{l}{T}}
+\begin{array}{lrcl}
+\stxrule{c}{Casts}{\lcOOnull{} \mid \lcOOcons{s}{c}}
+\stxrule{s}{Steps}{\lsOOcast{T}{l}{T}}
 \end{array}

### 2019-10-24 paper.tex
minor fixes

@@
   \]
-  \caption{Definition of $applyCast$for \lazyD}
+  \caption{Definition of $applyCast$ for \lazyD}
   \label{fig:applyCast-D-C}
@@
   }
-  %% \stxrule{\bar{c}}{wrapper coercions}{  
-  %%  \ncInj{I} \mid
-  %%  \ncFun{\hat{c}}{\hat{c}} \mid
-  %%  \ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
-  %% }
-% \stxrulecont{
-%   \ncProd{\hat{c}}{\hat{c}} \mid
-%   \ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
-%   \ncSum{\hat{c}}{\hat{c}} \mid
-%   \ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid  
-% }
 \stxrule{\hat{c}}{normal coercions}{
@@
 }
-  %% \stxrule{\hat{c}}{normal coercions}{
-  %%  \bar{c} \mid
-  %%  \ncId \mid
-  %%  \ncFail{l} \mid
-  %%  \ncProj{I}{l} \mid
-  %%  \ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
-  %%  \ncSeq{\ncProj{I}{l}}{\ncInj{I}}
-  %% }
-  %% \stxrulecont{
-  %%  \ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
-  %%  \ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
-  %% }
   \end{array}
@@
 their normal forms. \figref{fig:normal-coercion} defines the syntax of
-coercions in normal form, written $\hat{c}$. Conceptually, a coercion
+coercion in normal form, written $\hat{c}$. Conceptually, a coercion
 in normal form has three parts, all of which are optional.  It may
@@
 \section{Definition of Hypercoercions} \label{sec:hypercoercion-definition}
+\todo[inline]{
+The figures of applyCast for hypercoercions is before coercions, even before 
+the syntax definition of hypercoercions! -KC
+}
 

### 2019-10-24 paper.tex
read sec3 the first time, lots of things to fix
camalize thm names

@@
   \begin{array}{lrcl}
-  \stxrule{\ell}{Maybe $l$}{\epsilon \mid l}
+  \stxrule{\ell}{Optional labels}{\epsilon \mid l}
   \end{array}
@@
 \figref{fig:HC-D} defines the functions $id$, $seq$, and $cast$ that
-construct \lazyD{} hypercoercions, towards satisifying the Cast ADT.
+construct \lazyD{} hypercoercions, towards satisifying the Cast abstract data 
+type defined in Section~\ref{sec:framework}.
 \figref{fig:HC-D} also defines some auxiliary functions.
@@
 We shall need optional blame labels, written $\ell$ , that range over
-$\epsilon$ or $l$. Then we write composition of hypercoercions as $c_1
+$\epsilon$ or $l$. The label is mandatory when the target
+type of the first coercion does not match the source type of the second. 
+Then we write composition of hypercoercions as $c_1
 \fatsemi^\ell c_2$.  When both $c_1$ and $c_2$ are $\hyperCoercionI$,
@@
 constructors ($m_1 \not\smile m_2$), the result is a failure coercion,
-which needs a label. When $c_2$ starts with a projection, it is to
-blame for casting a value to a shallowly inconsistent type. When $c_2$
-starts with a no-op, $\ell$ must be a label. And we blame it for
+which needs a label. When $c_2$ starts with a projection, we blame the 
+projection for casting a value to a shallowly inconsistent type. When $c_2$
+starts with a $\epsilon$, we know $\ell$ must be a label, which is blamed for
 composing shallowly inconsistent hypercoercions. The last two cases
@@
 c_2$. When $c_2$ starts with a projection, we do not know whether the
-target type of $m_1$ matches the source of $m_2$, although we know
-they are shallowly consistent. So we use the $l$ in the projection to
-compose the middles $m_1 \fatsemi^l m_2$. When $c_2$ starts with a
-no-op, we compose the middles using $\ell$.
+target type of $m_1$ matches the source of $m_2$. So we use the $l$ in the 
+projection to  compose the middles $m_1 \fatsemi^l m_2$. When $c_2$ starts with 
+a $\epsilon$, we compose the middles using $\ell$.
 
@@
 
-The proof of correctness for hypercoercions (in
+A proof of correctness for hypercoercions (in 
 Section~\ref{secc:framework:monoid-correct}) relies on the following
@@
 
-\begin{proposition}[\lazyD{} hypercoercions form a monoid]
+\begin{proposition}[\lazyD{} Hypercoercions Form a Monoid]
   \label{thm:hc-monoid}
@@
 \begin{proof}
-  By induction on T.
+  By induction on $T$.
 \end{proof}
@@
 
-\begin{proposition}[\lazyUD{} hypercoercions form a monoid]
+\begin{proposition}[\lazyUD{} Hypercoercions Form a Monoid]
   For all $c : T_1 \Longrightarrow T_2$,
@@
 
-\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
+\begin{proposition}[Equivalence of Two \lazyD{} Cast ADTs]
   \label{thm:surely-lazyD-eqv}
@@
 
-\begin{proposition}[$L$ properties]\label{thm:L-LazyD-monoid}\ 
+\begin{proposition}[$L$ Properties]\label{thm:L-LazyD-monoid}\ 
   \begin{enumerate}
@@
 
-\begin{lemma}[$L$ is correct wrt. \ineffCEKD]
+\begin{lemma}[$L$ is Correct wrt. \ineffCEKD]
   \label{lem:L-correct}
@@
 
-\begin{theorem}[\effCEK{C} is correct wrt. \ineffCEKD{}]
+\begin{theorem}[\effCEK{C} is Correct wrt. \ineffCEKD{}]
   \label{thm:surely-lazyD-correct}
@@
 
-\begin{lemma}[\lazyD{} hypercoercion is a \lazyD{} Cast ADT]
+\begin{lemma}[\lazyD{} Hypercoercion is a \lazyD{} Cast ADT]
   \label{thm:hc-surely-lazyD}
@@
 
-\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
+\begin{theorem}[\lazyD{} Hypercoercion Respect \ineffCEKD]
   If $\judgetype{\emptyset}{e}{T}$ and $o : T$

### 2019-10-24 paper.tex
finish revising sec3

@@
 not structurally recursive, which makes it more difficult to define in
-proof assistants, requiring what amounts to an explicit proof of termination.
+Agda, requiring what amounts to an explicit proof of termination.
 %
@@
 \begin{itemize}
-\item The head $h$ is either a projection or the identity,
+\item The head $h$ is either a projection or the no-op,
 \item the middle $m$ involves coercions that preserve a type
@@
   unit types, and
-\item the tail $t$ is either an injection, a failure, or the identity.
+\item the tail $t$ is either an injection, a failure, or the no-op.
 \end{itemize}
@@
 a projection, the result is $c_2$.  Otherwise, we need a label to
-build the projection. Since the head of $c_2$ is $\epsilon$, its
+build the projection. Since the head of $c_2$ is the no-op, its
 source type must be a pretype. Thus we know $\ell$ must be a label and
@@
 projection for casting a value to a shallowly inconsistent type. When $c_2$
-starts with a $\epsilon$, we know $\ell$ must be a label, which is blamed for
+starts with the no-op, we know $\ell$ must be a label, which is blamed for
 composing shallowly inconsistent hypercoercions. The last two cases
@@
 projection to  compose the middles $m_1 \fatsemi^l m_2$. When $c_2$ starts with 
-a $\epsilon$, we compose the middles using $\ell$.
+the no-op, we compose the middles using $\ell$.
 
@@
 \item If the middle is of base type, then the remaining 62 bits are
-  used to represent the head (21 bits), middle (22 bits), and tail (19
+  used to represent the head (25 bits), middle (11 bits), and tail (26
   bits).

### 2019-10-24 paper.tex
minor fixes

@@
 interface between the machine and the cast representation is defined
-by an abstract data type, named Cast ADT, that we define shortly.  We
+by an abstract data type, named Cast ADT, that we define shortly 
+(Section~\ref{sec:framework:adt}).  We
 conjecture that all cast representations defined in the literature
@@
   \[
-  \begin{array}{rclr}
-  \stxrule{v}{values}{
+  \begin{array}{lrcl}
+  \stxrule{v}{Values}{
     \hcvOOtt \mid
@@
   }
-\stxrule{r}{cast results}{
+\stxrule{r}{Cast results}{
   \rOOsucc{v} \mid
@@
 \subsection{The Cast Abstract Data Types}
+\label{sec:framework:adt}
 

### 2019-10-24 paper.tex
revise sec5

@@
   [\square \langle #1 \rangle]#2}
-
-%\newcommand{\kOOmt}[0]{\mathtt{stop}}
-%\newcommand{\kOOconsI}[3]{\mathtt{cons_1} \; #1 \; #2 \; #3}
-%\newcommand{\kOOconsII}[2]{\mathtt{cons_2} \; #1 \; #2}
-%\newcommand{\kOOinl}[1]{\mathtt{inl} \; #1}
-%\newcommand{\kOOinr}[1]{\mathtt{inr} \; #1}
-%\newcommand{\kOOappI}[3]{
-% \mathtt{app_1} \; #1 \; #2 \; #3
-%}
-%\newcommand{\kOOappII}[2]{
-% \mathtt{app_2} \; #1 \; #2}
-%\newcommand{\kOOcar}[1]{
-% \mathtt{fst} \; #1}
-%\newcommand{\kOOcdr}[1]{
-% \mathtt{snd} \; #1}
-%\newcommand{\kOOcaseI}[4]{
-% \mathtt{case_1} \; #1 \; #2 \; #3 \; #4}
-%\newcommand{\kOOcaseII}[4]{
-% \mathtt{case_2} \; #1 \; #2 \; #3 \; #4}
-%\newcommand{\kOOcaseIII}[3]{
-% \mathtt{case_3} \; #1 \; #2 \; #3}
-%\newcommand{\kOOcast}[2]{
-% \langle #1 \rangle #2}
-
 \newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
@@
 
+% URLs
+\newcommand{\urlLazyDProof}{
+	\url{https://github.com/LuKC1024/Blame-and-Coercion-Together-Again-for-the-Second-Time/tree/master/Proof}
+}
+
 \begin{document}
@@
 \section{Definition of Hypercoercions} \label{sec:hypercoercion-definition}
-\todo[inline]{
-The figures of applyCast for hypercoercions is before coercions, even before 
-the syntax definition of hypercoercions! -KC
-}
 
@@
 \begin{proposition}[\lazyD{} Hypercoercions Form a Monoid]
-  \label{thm:hc-monoid}
+  \label{thm:LazyD-HC-monoid}
   For all $c : T_1 \Longrightarrow T_2$,
@@
 \begin{proposition}[\lazyD{} Identity Casts]
+	\label{thm:LazyD-HC-identity-casts}
   For all $T$ and $l$, $cast(T,l,T) = id(T) $
@@
 give the definition of values and cast results used by the \effCEK{C}, as they 
-are mentioned in the definition of the ADTs. The $\hcvOOinj{P}{v}$ stands for 
+are mentioned in the definition of the ADTs. The $\hcvOOinj{I}{v}$ stands for 
 values that are cast to the dynamic type, as in \citet{wadler2009well}.
@@
 operators that a cast representation $C$ must provide for it to be
-used with the \effCEK{C} machine.  The first three operators enables
+used with the \effCEK{C} machine.  The first three operators enable
 \effCEK{C} to construct casts so we call them \textit{cast
@@
   \item[$cast(T_1,l,T_2)$] constructs a cast from $T_1$ to $T_2$
-  \item[$applyCast(v,c)$] applies a cast to a value, producing a result
+  \item[$applyCast(v,c)$] applies a cast to a value, producing a cast result
   \end{description}
@@
 
-\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercion. 
+\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions. 
 Applying the identity cast for the 
-dynamic type succeeds immediately. When applying a compound cast, we firstly 
+dynamic type succeeds immediately. Otherwise, we firstly 
 apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
@@
 \end{lemma}
-\begin{proof} See the supplementary material. \end{proof}
+\begin{proof}
+	See the Agda proof at the following URL:\\
+	\urlLazyDProof
+\end{proof}
 
@@
 \begin{proof}
-  Immediately from Theorem~\ref{thm:surely-lazyD-correct} and 
-  Lemma~\ref{thm:hc-surely-lazyD}.
+  Immediately from that every Lazy D Cast ADT is correct ( 
+  Theorem~\ref{thm:surely-lazyD-correct}) and that Lazy D hypercoercion is a 
+  Lazy D Cast ADT (Lemma~\ref{thm:hc-surely-lazyD}). 
+  %
   Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
-  Lemma~\ref{thm:hc-surely-lazyD}, and 
-  Proposition~\ref{thm:hc-monoid}.
+  Lemma~\ref{thm:hc-surely-lazyD}, Proposition~\ref{thm:LazyD-HC-monoid}, and 
+  Proposition~\ref{thm:LazyD-HC-identity-casts}
 \end{proof}
@@
 \todoKC{write conclusion. -KC}
+
+\todo[inline]{
+Back out and be like remember all our contribution. Bring them back to the 
+beginning. Repeat but not repeat literally.
+I can assume that people have eaten meat.
+}
 

### 2019-10-24 paper.tex
typo

@@
 \newcommand{\urlLazyDProof}{
-	\url{https://github.com/LuKC1024/Blame-and-Coercion-Together-Again-for-the-Second-Time/tree/master/Proof}
+	\url{https://github.com/LuKC1024/hypercoercion-and-framework-wgt2020/tree/master/Proof}
 }
@@
 The reflexive transitive closure of reduction ($\judgeCreduceTrans{s}{s}$) and 
-evaluation ($eval_\mathcal{C}(e)$)
+evaluation ($eval_\mathcal{x}(e)$)
 are standard~\citep{felleisen03:_pllc}.

### 2019-10-24 paper.tex
sec 2

@@
 $\sOOinspect{e}{\rho}{\kappa}$ or $\sOOreturn{v}{\kappa}$ configuration, 
-respectively. Additionally, there is the $\sOOhalt{o}$ configuration.
+respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
+machine halts with an observation.
+%Let $s$ range over machine states. A state is either looking at an 
+%expression to decide what to do next, returning a value to a continuation, or 
+%halting with an observation.
+
+Let $v$ range over values. A value is either the unit, a function, a pair, a 
+left injection, a right injection, or a casted value. Value typing rules 
+restrict the casts in casted values. If the cast is between pre-types, source 
+and target types must have the same type constructor at the top ($P_1 \approx 
+P_2$). If the cast is from a pre-type to the dynamic type, the pre-type must be 
+injectable. The definition of injectable types depends on blame
+strategies: for the \lazyD\ strategy, every pre-type is injectable;
+for the \lazyUD\ strategy, a pre-types is injectable if all its sub-parts are 
+the dynamic type.
 
@@
 %
-To cast a value, the machine invokes $applyCast$ on the value.  If the
-cast succeeds, the machine returns the result to the next
-continuation.  If the cast fails, the machine halts with the blame
-label.
+To cast a value, the machine invokes $applyCast$ on the value. If the cast 
+succeeds ($\rOOsucc{v'}$), the machine returns the result to the next
+continuation.  If the cast fails ($\rOOfail{l}$), the machine halts with the 
+blame label.
+%Let $r$ range over cast results. A cast result is either a success, which 
+%brings back a value, or a failure, which brings back a blame label.
+
 %
@@
 The reflexive transitive closure of reduction ($\judgeCreduceTrans{s}{s}$) and 
-evaluation ($eval_\mathcal{x}(e)$)
-are standard~\citep{felleisen03:_pllc}.
+evaluation ($eval_\mathcal{x}(e)$) are standard~\citep{felleisen03:_pllc}.
+Let $o$ range over observations. They are what we would observe if 
+a program terminates. Observations include all value constructors and
+blame.  The function converting values to observations ($observe(v) =
+o$) is defined in the natural way.
 
@@
 
-Let $v$ range over values. A value is either the unit, a function, a pair, a 
-left injection, a right injection, or a value in cast. 
-As shown by the value typing rules, for values in casts, 
-if the cast is between pre-types, source and target types must have the 
-same type constructor at the top. 
-If the cast is from a pre-type to the dynamic type, the pre-type must be 
-injectable. The definition of injectable types depends on blame
-strategies: for the \lazyD\ strategy, every pre-type is injectable;
-for the \lazyUD\ strategy, a pre-types is injectable if all its sub-parts are 
-the dynamic type.
 %As shown by the value typing rules, if the target type of a
@@
 %same type constructor.
-
-Let $c$ range over casts. A cast is a triple of a type, a label, and a type.
-
-Let $o$ range over observations. They are what we would observe if 
-a program terminates. Observations include all value constructors and
-blame.  The function converting values to observations ($observe(v) =
-o$) is defined in the natural way.
 
@@
 
-Let $r$ range over cast results. A cast result is either a success, which 
-brings back a value, or a failure, which brings back a blame label.
-
-Let $s$ range over machine states. A state is either looking at an 
-expression to decide what to do next, returning a value to a continuation, or 
-halting with an observation.
-
-Let $\kappa$ range over continuations. $\mathtt{stop}$ is the top 
-continuation. The remaining continuations correspond to expressions. For 
-example, $\kOOconsI{T_1}{T_2}{e}{\rho}{\kappa}$ is the continuation waiting for 
-the first part of the pair. And the last continuation, $\kOOcast{c}{\kappa}$ is 
-to cast the value before returning to $\kappa$.
+%Let $\kappa$ range over continuations. $\mathtt{stop}$ is the top 
+%continuation. The remaining continuations correspond to expressions. For 
+%example, $\kOOconsI{T_1}{T_2}{e}{\rho}{\kappa}$ is the continuation waiting 
+%for 
+%the first part of the pair. And the last continuation, $\kOOcast{c}{\kappa}$ 
+%is 
+%to cast the value before returning to $\kappa$.
 
@@
 Let $v$ range over values. In \ineffCEK{} we have one value
-constructor for all values in casts.  In \effCEK{C}, however, we do not
+constructor for all castes values.  In \effCEK{C}, however, we do not
 have this generic value constructor, instead we push those casts into
@@
 
-\todoKC{write conclusion. -KC}
-
 \todo[inline]{
@@
 }
+
+In this
 

### 2019-10-24 paper.tex
revise sec2

@@
 compressing continuations). So using an abstract machine for the cast calculi in
-this section makes it easier prove correctness of the space-efficient
+this section makes it easier to prove correctness of the space-efficient
 machines. Of course, one should prove that the abstract machine
@@
 machine and Fig.~\ref{fig:state} gives a grammar for machine states
-$s$, including a definition of values and value typing. 
+$s$, including a definition of values $v$ and value typing. 
 %Fig.~\ref{fig:state} gives a grammar for machine states
@@
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
-machine halts with an observation.
+machine halts with an observation ($o$). Observations include all value 
+constructors and blame. The function converting values to 
+observations ($observe(v) = o$) is defined in the natural way.
 %Let $s$ range over machine states. A state is either looking at an 
@@
 %% transition rules starting from$Eval$states are standard.
-To apply a function in cast, the machine first casts $v_1$, the
+To apply a casted function, the machine first casts $v_1$, the
 operand, then applies the cast operand to $v_2$, the underlying
@@
 %
-To take out the first (resp. second) part of a pair in cast, the
+To take out the first (resp. second) part of a casted pair, the
 machine firstly take out the first (resp. second) part of $v$, the
@@
 %
-To case split an injection in cast, the machine moves the cast from
+To case split a casted injection, the machine moves the cast from
 the injection to continuations functions.
@@
 evaluation ($eval_\mathcal{x}(e)$) are standard~\citep{felleisen03:_pllc}.
-Let $o$ range over observations. They are what we would observe if 
-a program terminates. Observations include all value constructors and
-blame.  The function converting values to observations ($observe(v) =
-o$) is defined in the natural way.
 

### 2019-10-24 paper.tex
almost conclude

@@
 \begin{itemize}
-\item hypercoercions, a new space-efficient cast representation, which
+\item hypercoercions, a new cast representation, which
   has a structurally recursive composition and a more compact memory
@@
 The $seq$ operator is defined in terms of coercion composition, which
-is the key to compressing coercions and maintaining space efficiency.
+is the key to compressing coercions and maintaining space-efficiency.
 A composition operator for coercions typically requires the target
@@
 This section presents our second contribution, a framework for proving
-the correctness of cast representations, especially space efficient
+the correctness of cast representations, especially space-efficient
 ones. Section~\ref{sec:hypercoercion-correctness} applies this
@@
 over the cast representation $C$
-(Section~\ref{sec:framework:cek}). This machine is space efficient
+(Section~\ref{sec:framework:cek}). This machine is space-efficient
 provided that the cast representation performs compression.  The
@@
 
-%% After showing their cast is an instance of Lazy D Cast, users of our
-%% frameworks can plug-in this cast representation to our space-efficient
-%% abstract machine in subsection~\ref{ssec:framework:cek}, and prove
-%% that this machine is equivalent to
-%% \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which
-%% depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
-
 \subsection{A Space-efficient CEK machine}
@@
 
-In this
+In this paper we presented a new cast representation, hypercoercions, in two 
+flavors, Lazy D and Lazy UD. Hypercoercions have a structurally recursive 
+composition, which is a win over coercions in normal form for mechanized 
+metatheory. What is more, hypercoercions have a more compact memory 
+representation. We prove that $S(H)$, an abstract machine that uses Lazy D 
+hypercoercions, is equivalent to $D$, a semantics of Lazy D Cast Calculus.
+
+We also present a framework for proving the correctness of Lazy D Cast ADT. 
+If $C$ implements the Lazy D Cast ADT, $S(C)$ would be equivalent to $D$.
+
+\todo[inline]{related works. -KC}
 

### 2019-10-25 paper.tex
revise

@@
 % Lazy D cast calculus on space-inefficient CEK
-\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{x}} #2}
-\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{x}}^{*} #2}
-\newcommand{\judgeCeval}[2]{eval_{\mathcal{x}}(#1) = #2}
-\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{x} & #2 & #3\\}
-\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{x}} 
+\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{X}} #2}
+\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{X}}^{*} #2}
+\newcommand{\judgeCeval}[2]{eval_{\mathcal{X}}(#1) = #2}
+\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{X} & #2 & #3\\}
+\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{X}} 
 & \highlight{#2} & \highlight{#3} \\}
@@
 % names
-\newcommand{\ineffCEK}{$\mathcal{C}$}
+\newcommand{\ineffCEK}{$\mathcal{X}$}
 \newcommand{\ineffCEKD}{$\mathcal{D}$}
@@
 
-We start by defining a CEK machine \effCEK{C} that is parameterized
-over the cast representation $C$
-(Section~\ref{sec:framework:cek}). This machine is space-efficient
-provided that the cast representation performs compression.  The
-interface between the machine and the cast representation is defined
-by an abstract data type, named Cast ADT, that we define shortly 
-(Section~\ref{sec:framework:adt}).  We
-conjecture that all cast representations defined in the literature
+The framework includes an abstract data type named Cast ADT 
+(Section~\ref{sec:framework:adt}), and a CEK machine \effCEK{C} that is 
+parameterized over Cast ADTs (Section~\ref{sec:framework:cek}). This machine is 
+space-efficient provided that the Cast ADT implementation performs compression. 
+We conjecture that all cast representations defined in the literature
 are instances of this ADT.
+
+%We start by defining a CEK machine \effCEK{C} that is parameterized
+%over the cast representation $C$
+%(Section~\ref{sec:framework:cek}). This machine is space-efficient
+%provided that the cast representation performs compression.  The
+%interface between the machine and the cast representation is defined
+%by an abstract data type, named Cast ADT, that we define shortly 
+%(Section~\ref{sec:framework:adt}).  We
+%conjecture that all cast representations defined in the literature
+%are instances of this ADT.
 
@@
 
+Let $v$ range over values. In \ineffCEK{} we have one value
+constructor for all casted values.  In \effCEK{C}, however, we do not
+have this generic value constructor, instead we push casts into the ordinary 
+values. Thus non-casted values in \ineffCEK\ corresponds to values in 
+\effCEK{C} where casts are identities. For instance, $(\vOOcons{v_1}{v_2})$ 
+corresponds to $(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$.
+
+%\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOprod{T_1}{T_2} \\
+%c_1' = seq(c_1,cast(T_1,l,T_3)) \\
+%c_2' = seq(c_2,cast(T_2,l,T_4))
+%}{
+%\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
+%\vOOcast{v_2}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
+%: \POOprod{T_3}{T_4}
+%}
+
+Cast results ($r$) are the same as for \ineffCEK.
+
 \subsection{The Cast Abstract Data Types}
@@
   \begin{description}
-  \item[$id(T)$] constructs an identity cast from a type
-  \item[$seq(c_1,c_2)$] composes two casts
-  \item[$cast(T_1,l,T_2)$] constructs a cast from $T_1$ to $T_2$
-  \item[$applyCast(v,c)$] applies a cast to a value, producing a cast result
+  \item[$id(T)=c$] constructs an identity cast from a type
+  \item[$seq(c,c)=c$] composes two casts
+  \item[$cast(T,l,T)=c$] constructs a cast from a source type, a label, and a 
+  target type
+  \item[$applyCast(v,c)=r$] applies a cast to a value, producing a cast result
   \end{description}
@@
 
-Let $v$ range over values. In \ineffCEK{} we have one value
-constructor for all castes values.  In \effCEK{C}, however, we do not
-have this generic value constructor, instead we push those casts into
-the ordinary values. For instance, $(\vOOcons{v_1}{v_2})$ corresponds
-to $(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)})$. To construct values
-of the dynamic type, we use $\hcvOOinj{P}{v}$.
-
-Cast results ($r$) and machine states ($s$) are the same as for
-\ineffCEK{}.
-
 Let $\kappa$ range over continuations and let $k$ range over
@@
 metatheory. What is more, hypercoercions have a more compact memory 
-representation. We prove that $S(H)$, an abstract machine that uses Lazy D 
-hypercoercions, is equivalent to $D$, a semantics of Lazy D Cast Calculus.
-
-We also present a framework for proving the correctness of Lazy D Cast ADT. 
-If $C$ implements the Lazy D Cast ADT, $S(C)$ would be equivalent to $D$.
-
-\todo[inline]{related works. -KC}
+representation.
+
+We also present steps toward the first framework for proving the correctness of 
+cast representations.
+%
+The framework includes abstract data types for cast representations (Cast ADT 
+and Lazy D Cast ADT), an parameterized abstract machine \effCEK{C}, and a 
+theorem states that \effCEK{C} is equivalent to $D$ if $C$ is a Lazy D Cast 
+ADT.
+Cast ADT is the interface between cast representations and \effCEK{C}. Its
+implementation should provide four functions: $cast(T,l,T) = c$, $id(T)=c$, and 
+$seq(c,c)=c$ for cast construction, and $applyCast(v,c)=r$ for cast application.
+%
+Lazy D Cast ADT refines Cast ADT. We conjecture that Lazy D threesomes, and 
+Lazy D coercions in normal form are also Lazy D Cast ADT.
+
+Finally, we proved that Lazy D hypercoercions ($H$) is a Lazy D Cast ADT. By 
+using our framework, we shown that it is a correct cast representation because 
+$S(H)$ is equivalent to $D$.
 

### 2019-10-25 paper.tex
use E for environment

@@
 Corresponding to (1) and (2), the machine state is either in an
-$\sOOinspect{e}{\rho}{\kappa}$ or $\sOOreturn{v}{\kappa}$ configuration, 
+$\sOOinspect{e}{\mathcal{E}}{\kappa}$ or $\sOOreturn{v}{\kappa}$ configuration, 
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
@@
     \vOOtt{} \mid
-    \vOOfun{\rho}{x}{e} \mid
+    \vOOfun{\mathcal{E}}{x}{e} \mid
     \vOOcons{v}{v} \mid
@@
   \stxrule{s}{States}{
-    \sOOinspect{e}{\rho}{\kappa} \mid{}
+    \sOOinspect{e}{\mathcal{E}}{\kappa} \mid{}
     \sOOreturn{v}{\kappa} \mid{}
@@
     \kOOmt \mid
-    \kOOconsI{T}{T}{e}{\rho}{\kappa} \mid
+    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
     \kOOconsII{T}{T}{v}{\kappa} \mid
@@
     \kOOinr{T}{T}{\kappa} \mid
-    \kOOappI{e}{\rho}{\kappa} \mid
+    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
     \kOOappII{v}{\kappa} \mid
@@
     \kOOcdr{\kappa}\mid
-    \kOOcaseI{e}{e}{\rho}{\kappa}\mid
-    \kOOcaseII{v}{e}{\rho}{\kappa}
+    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa}\mid
+    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa}
   }
@@
     \hiredrule{
-    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{
+    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e}{\mathcal{E}}{
       \kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
@@
   \redrule{
-    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
-  }{  
-    \sOOreturn{\rho(x)}{\kappa}
+    \sOOinspect{\eOOvar{x}}{\mathcal{E}}{\kappa}
+  }{  
+    \sOOreturn{\mathcal{E}(x)}{\kappa}
   }{}
   \redrule{
-    \sOOinspect{\eOOsole}{\rho}{\kappa}
+    \sOOinspect{\eOOsole}{\mathcal{E}}{\kappa}
   }{
@@
   \redrule{
-    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
-  }{
-    \sOOreturn{\vOOfun{\rho}{x}{e}}{\kappa}
+    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOreturn{\vOOfun{\mathcal{E}}{x}{e}}{\kappa}
   }{}
   \redrule{
-    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e_1}{\rho}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}
+    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e_1}{\mathcal{E}}{\kOOconsI{T_1}{T_2}{e_2}{\mathcal{E}}{\kappa}}
   }{}
   \redrule{
-    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{\kOOinl{T_1}{T_2}{\kappa}}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e}{\mathcal{E}}{\kOOinl{T_1}{T_2}{\kappa}}
   }{}
   \redrule{
-  \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
-  }{
-  \sOOinspect{e}{\rho}{\kOOinr{T_1}{T_2}{\kappa}}
+  \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
+  }{
+  \sOOinspect{e}{\mathcal{E}}{\kOOinr{T_1}{T_2}{\kappa}}
   }{}
   \redrule{
-    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
-  }{
-\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}
+    \sOOinspect{\eOOapp{e_1}{e_2}}{\mathcal{E}}{\kappa}
+  }{
+\sOOinspect{e_1}{\mathcal{E}}{\kOOappI{e_2}{\mathcal{E}}{\kappa}}}{}
 
 \redrule{
-\sOOinspect{\eOOcar{e}}{\rho}{\kappa}}{
-\sOOinspect{e}{\rho}{\kOOcar{\kappa}}}{}
+\sOOinspect{\eOOcar{e}}{\mathcal{E}}{\kappa}}{
+\sOOinspect{e}{\mathcal{E}}{\kOOcar{\kappa}}}{}
 
 \redrule{
-  \sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
-  \sOOinspect{e}{\rho}{\kOOcdr{\kappa}}}{}
+  \sOOinspect{\eOOcdr{e}}{\mathcal{E}}{\kappa}}{
+  \sOOinspect{e}{\mathcal{E}}{\kOOcdr{\kappa}}}{}
 
 \redrule{
-\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
-\sOOinspect{e_1}{\rho}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{}
+\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\mathcal{E}}{\kappa}}{
+\sOOinspect{e_1}{\mathcal{E}}{\kOOcaseI{e_2}{e_3}{\mathcal{E}}{\kappa}}}{}
 
 \redrule{
-\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
+\sOOinspect{\eOOblame{l}}{\mathcal{E}}{\kappa}}{
 \sOOhalt{(\oOOblame{l})}}{}
@@
 \redrule{
-\sOOreturn{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
-\sOOinspect{e_2}{\rho}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{}
+\sOOreturn{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\mathcal{E}}{\kappa}}}{
+\sOOinspect{e_2}{\mathcal{E}}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{}
 
@@
 \redrule{
-\sOOreturn{v_1}{\kOOappI{e_2}{\rho}{\kappa}}}{
-\sOOinspect{e_2}{\rho}{\kOOappII{v_1}{\kappa}}}{}
+\sOOreturn{v_1}{\kOOappI{e_2}{\mathcal{E}}{\kappa}}}{
+\sOOinspect{e_2}{\mathcal{E}}{\kOOappII{v_1}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_2}{\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa}}}{
-\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
+\sOOreturn{v_2}{\kOOappII{(\vOOfun{\mathcal{E}}{x}{e})}{\kappa}}}{
+\sOOinspect{e}{\mathcal{E}[x:=v_2]}{\kappa}}{}
   \hiredrule{
@@
 \redrule{
-\sOOreturn{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{
-\sOOinspect{e_2}{\rho}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{}
+\sOOreturn{v_1}{\kOOcaseI{e_2}{e_3}{\mathcal{E}}{\kappa}}}{
+\sOOinspect{e_2}{\mathcal{E}}{\kOOcaseII{v_1}{e_3}{\mathcal{E}}{\kappa}}}{}
 
 \redrule{
-\sOOreturn{v_2}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{
-\sOOinspect{e_3}{\rho}{
+\sOOreturn{v_2}{\kOOcaseII{v_1}{e_3}{\mathcal{E}}{\kappa}}}{
+\sOOinspect{e_3}{\mathcal{E}}{
   \kOOcaseIII{v_1}{v_2}{\kappa}
@@
 %continuation. The remaining continuations correspond to expressions. For 
-%example, $\kOOconsI{T_1}{T_2}{e}{\rho}{\kappa}$ is the continuation waiting 
+%example, $\kOOconsI{T_1}{T_2}{e}{\mathcal{E}}{\kappa}$ is the continuation 
+%waiting 
 %for 
@@
     \hcvOOtt \mid
-    \hcvOOfun{c}{\rho}{x}{e}{c} \mid
+    \hcvOOfun{c}{\mathcal{E}}{x}{e}{c} \mid
     \hcvOOcons{v}{c}{v}{c} \mid
@@
 acts like a sequence of casts. Properties (3) through (11) state that
-$cast(T_1,l,T_2)$ act like the Lazy D $applyCast$
+$cast(T_1,l,T_2)$ act like the Lazy D $applyCast$ for \ineffCEK\
 (Fig.~\ref{fig:applyCast-D-C}).
@@
   \begin{enumerate}
-  \item if $v : T$, then $applyCast(v,id(T)) = \mathtt{succ} \; v $
-  \item if $\judgeType{v}{T_1}$,
-    $ \judgeTypeFT{c_1}{T_1}{T_2}$, and
-    $ \judgeTypeFT{c_2}{T_2}{T_3}$,\\
+  \item If $v : T$ then $applyCast(v,id(T)) = \mathtt{succ} \; v $
+  \item If $\judgeType{v}{T_1}$ and
+    $ \judgeTypeFT{c_1}{T_1}{T_2}$ and
+    $ \judgeTypeFT{c_2}{T_2}{T_3}$\\
     then $applyCast(v,seq(c_1,c_2)) = 
-    applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2)$\\
+    applyCast(v,c_1) >>= \lambda v'.applyCast(v',c_2)$\\
     where 
@@
     \]
-  \item if $v : T_1$ and $T_1 \not\smile T_2$,
+  \item If $v : T_1$ and $T_1 \not\smile T_2$,
     then $applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
-  \item if $v : \star$, 
+  \item If $v : \star$,
     then $applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
-  \item if $v : P$,
+  \item If $v : P$,
     then $applyCast(\hcvOOinj{P}{v},cast(\star,l,P')) 
     = applyCast(v,cast(P,l,P')) $
-  \item if $v : P$,
+  \item If $v : P$,
     then $applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
-  \item if $v : \POOunit$,
+  \item If $v : \POOunit$,
     then $applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
-  \item if $(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}) : \POOfun{T_1}{T_2}$,
+  \item If $(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}) : \POOfun{T_1}{T_2}$,
     then\\
     $ 
-    applyCast(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}, 
+    applyCast(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}, 
     cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
     = 
-    \rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
-  \item if $(\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2}$,
+    \rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\mathcal{E}}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+  \item If $(\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2}$,
     then \\
@@
     $ 
-  \item if $(\hcvOOinl{v}{c}) : \POOsum{T_1}{T_2}$,
+  \item If $(\hcvOOinl{v}{c}) : \POOsum{T_1}{T_2}$,
     then \\
@@
     = \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
-  \item if $(\hcvOOinr{v}{c}) : \POOsum{T_1}{T_2}$,
+  \item If $(\hcvOOinr{v}{c}) : \POOsum{T_1}{T_2}$,
     then \\$
@@
 % \stxrule{s}{states}{
-%   \sOOinspect{e}{\rho}{\kappa} \mid{}
+%   \sOOinspect{e}{\mathcal{E}}{\kappa} \mid{}
 %   \sOOreturn{v}{\kappa} \mid{}
@@
     \kOOmt \mid{}
-    \kOOconsI{T}{T}{e}{\rho}{\kappa} \mid
+    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
     \kOOconsII{T}{T}{v}{\kappa} \mid
@@
   	\kOOinr{T}{T}{\kappa} \mid
-    \kOOappI{e}{\rho}{\kappa} \mid
+    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
     \kOOappII{v}{\kappa} \mid
@@
   \stxrulecont{
-    \kOOcaseI{e}{e}{\rho}{\kappa} \mid
-    \kOOcaseII{v}{e}{\rho}{\kappa} \mid
+    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa} \mid
+    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa} \mid
     \kOOcaseIII{v}{v}{\kappa}
@@
   \hiredruleS{
-    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
+    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e}{\mathcal{E}}{ext(cast(T_1,l,T_2),\kappa)}
   }{}
   \redruleS{
-    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
-  }{  
-    \sOOreturn{\rho(x)}{\kappa}
+    \sOOinspect{\eOOvar{x}}{\mathcal{E}}{\kappa}
+  }{  
+    \sOOreturn{\mathcal{E}(x)}{\kappa}
   }{}
   \redruleS{
-    \sOOinspect{\eOOsole}{\rho}{\kappa}
+    \sOOinspect{\eOOsole}{\mathcal{E}}{\kappa}
   }{
@@
   \hiredruleS{
-    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
-  }{
-    \sOOreturn{\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)}}{\kappa}
+    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOreturn{\hcvOOfun{id(T_1)}{\mathcal{E}}{x}{e}{id(T_2)}}{\kappa}
   }{}
   \redruleS{
-    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e_1}{\rho}{
-      wrap(\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa})
+    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e_1}{\mathcal{E}}{
+      wrap(\kOOconsI{T_1}{T_2}{e_2}{\mathcal{E}}{\kappa})
     }
@@
   \redruleS{
-    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{wrap(\kOOinl{T_1}{T_2}{\kappa})}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e}{\mathcal{E}}{wrap(\kOOinl{T_1}{T_2}{\kappa})}
   }{}
   \redruleS{
-    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e}{\rho}{wrap(\kOOinr{T_1}{T_2}{\kappa})}
+    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e}{\mathcal{E}}{wrap(\kOOinr{T_1}{T_2}{\kappa})}
   }{}
   \redruleS{
-    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
-  }{
-    \sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}
+    \sOOinspect{\eOOapp{e_1}{e_2}}{\mathcal{E}}{\kappa}
+  }{
+    \sOOinspect{e_1}{\mathcal{E}}{wrap(\kOOappI{e_2}{\mathcal{E}}{\kappa})}}{}
 
   \redruleS{
-    \sOOinspect{\eOOcar{e})}{\rho}{\kappa}}{
-    \sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}
+    \sOOinspect{\eOOcar{e})}{\mathcal{E}}{\kappa}}{
+    \sOOinspect{e}{\mathcal{E}}{wrap(\kOOcar{\kappa})}}{}
 
   \redruleS{
-    \sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
-    \sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}
+    \sOOinspect{\eOOcdr{e}}{\mathcal{E}}{\kappa}}{
+    \sOOinspect{e}{\mathcal{E}}{wrap(\kOOcdr{\kappa})}}{}
 
   \redruleS{
-    \sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
-    \sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
+    \sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\mathcal{E}}{\kappa}}{
+    \sOOinspect{e_1}{\mathcal{E}}{wrap(\kOOcaseI{e_2}{e_3}{\mathcal{E}}{\kappa})}}{}
 
 \redruleS{
-	\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
+	\sOOinspect{\eOOblame{l}}{\mathcal{E}}{\kappa}}{
 	\sOOhalt{(\oOOblame{l})}}{}
@@
 \funrule{
-  \continue{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
-  \sOOinspect{e_2}{\rho}{wrap(\kOOconsII{T_1}{T_2}{v_1}{\kappa})}}{}
+  \continue{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\mathcal{E}}{\kappa}}}{
+  \sOOinspect{e_2}{\mathcal{E}}{wrap(\kOOconsII{T_1}{T_2}{v_1}{\kappa})}}{}
 
@@
 \funrule{
-  \continue{v_1}{\kOOappI{e_2}{\rho}{\kappa}}}{
-  \sOOinspect{e_2}{\rho}{
+  \continue{v_1}{\kOOappI{e_2}{\mathcal{E}}{\kappa}}}{
+  \sOOinspect{e_2}{\mathcal{E}}{
     wrap(\kOOappII{v_1}{\kappa})
@@
 \hifunrule{
-  \continue{v_2}{\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa}}}{
+  \continue{v_2}{\kOOappII{(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2})}{\kappa}}}{
 \begin{cases}
-\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
+\sOOinspect{e}{\mathcal{E}[x:=v']}{ext(c_2,\kappa)} \\
 \sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
@@
 \funrule{
-  \continue{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}
-}{
-  \sOOinspect{e_2}{\rho}{
-    wrap(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
+  \continue{v_1}{\kOOcaseI{e_2}{e_3}{\mathcal{E}}{\kappa}}
+}{
+  \sOOinspect{e_2}{\mathcal{E}}{
+    wrap(\kOOcaseII{v_1}{e_3}{\mathcal{E}}{\kappa})
   }
@@
   \continue{v_2}{
-    \kOOcaseII{v_1}{e_3}{\rho}{\kappa}
-  }
-}{
-  \sOOinspect{e_3}{\rho}{
+    \kOOcaseII{v_1}{e_3}{\mathcal{E}}{\kappa}
+  }
+}{
+  \sOOinspect{e_3}{\mathcal{E}}{
   wrap(\kOOcaseIII{v_1}{v_2}{\kappa})
@@
   \continue{v_3}{
-    \kOOcaseIII{(\hcvOOinl{v}{c})}{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa}
+    \kOOcaseIII{(\hcvOOinl{v}{c})}{(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2})}{\kappa}
 %   (\mathtt{case_3}\;()\;
@@
 }{
-  \sOOreturn{v}{wrap(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
+  \sOOreturn{v}{wrap(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\mathcal{E}}{x}{e}{c_2})}{\kappa})}
 }{}
@@
 \hifunrule{
-  \continue{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}
+  \continue{(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2})}
   {
@@
 \figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient CEK
-machine.  This machine is similar to the \ineffCEK{} machine
-(Figure~\ref{fig:machine-cekc}).  The key differences are in values
-and continuations.
+machine parameterized over Cast ADT ($C$).  The key differences between 
+\effCEK{C} and \ineffCEK\ are the places where casts can accumulate at runtime, 
+that is, values and continuations. We discuss above the difference in values
+(Definition~\ref{def:values-effCEK}).
 
 Let $\kappa$ range over continuations and let $k$ range over
-pre-continuations.  A continuation is now a pre-continuation prefixed
-with a cast.  Pre-continuation are like the continuations in
-\ineffCEK{}, but there is no constructor for casts.  Continuations in
-\ineffCEKD{} have zero or more casts at the top.  In \effCEK{C},
-however, every continuation has exactly one cast at the top.
+pre-continuations.
+%
+Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
+constructor for casts.
+%
+A continuation is now a pre-continuation prefixed with a cast.
+%
+Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
+\effCEK{C}, however, every continuation has exactly one cast at the top.
 Continuations in \ineffCEK\ that have no casts at the top correspond
-to continuations in \effCEK{C}\ whose casts are identity.
+to continuations in \effCEK{C}\ whose casts are identities.
 Continuations in \ineffCEK\ that have many casts at the top correspond
@@
 
-The transition relation $\judgeSreduce{C}{s}{s}$ uses functions provides by $C$ 
-to represent cases and to apply casts.
+The transition relation $\judgeSreduce{C}{s}{s}$ relies on functions provided 
+by $C$ to work with casts.
 %
@@
   \inference{
-    \rho_1 \approx \rho_2 &
-    dom(\rho_1) = dom(\rho_2) = \Gamma \\
+    \mathcal{E}_1 \approx \mathcal{E}_2 &
+    dom(\mathcal{E}_1) = dom(\mathcal{E}_2) = \Gamma \\
     \Gamma , x : T_1 \vdash e : T_2
   }{
-    \hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)}
+    \hcvOOfun{id(T_1)}{\mathcal{E}_1}{x}{e}{id(T_2)}
     \approx
-    \vOOfun{\rho_2}{x}{e}
+    \vOOfun{\mathcal{E}_2}{x}{e}
     : \POOfun{T_1}{T_2}
@@
 \inference{
-\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
+\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
 c_1' = seq(cast(T_3,l,T_1),c_1) \\
@@
 }{
-\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
+\hcvOOfun{c_1'}{\mathcal{E}}{x}{e}{c_2'}
 \approx
@@
   appS(
-    \hcvOOfun{c_1}{\rho}{x}{e}{c_2},
+    \hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2},
     \lsOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}})
 }{
-  \rOOsucc{(\hcvOOfun{c_1'}{\rho}{x}{b}{c_2'})}
+  \rOOsucc{(\hcvOOfun{c_1'}{\mathcal{E}}{x}{b}{c_2'})}
 }{
@@
   \funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
-  \funrule{applyMiddle(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
-    \rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 
+  \funrule{applyMiddle(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
+    \rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\mathcal{E}}{x}{e}{(c_2 
     \fatsemi^\ell c_4)})}

### 2019-10-25 paper.tex
minor edit
reformulation of statement of lemma 4.7
improve S~~D

@@
   both mechanized metatheory and implementation is
-  challenging. Existing solutions are good for one or the other. This
+  challenging. Existing solutions (i.e. coercions, threesomes, and 
+  supercoercions) are good for one or the other. This
   paper presents a new cast representation, named hypercoercions, that
@@
 
-\listoftodos{}
-
 \section{Introduction}
 
-\todo[inline]{I see lots of mistakes regarding when to make words
-  plural (whether they should have an ``s'' at the end). Please review
-  the rules of English regarding plurals. The rules are tricky...
-  some words don't have a plural form, like ``blame''. -JS
-  \\---\\
-  Will fix grammar after fixing all other problems -KC}
+\todo[inline]{
+	Check grammar;
+	Improve the proof of \ref{thm:SD-bisim}.
+	And the proof of \ref{thm:SD-equiv}
+}
 
@@
 values are defined later in
-Section~\ref{sec:hypercoercion-correctness}, after we introduce the
-space-efficient machine and its definition of values in
-Section~\ref{sec:framework}.
+Section~\ref{sec:hypercoercion-correctness}, after we introduce the framework 
+and its new space-efficient definition of values in Section~\ref{sec:framework}.
 
@@
 Cast results ($r$) are the same as for \ineffCEK. 
+Value typing ($\judgeType{v}{T}$) is defined in the obvious way.
 
@@
 %
-To construct a function, the machine fills the casts $id$.
+To construct a function, the machine fills the casts with $id$s.
 %
@@
 To take out the first part of a pair, the machine returns the first value to a 
-continuation extended with the first cast. Taking out the second part of a pair 
-is similar.
+continuation extended with the first cast. Taking out the second 
+part of a pair is similar.
 %
@@
 variant is a left injection, the machine composes the cast in the left 
-injection with the domain casts of the first continuation function, then moves 
+injection with the domain cast of the first continuation function, then move 
 to a state that will apply the new function to the value in the left injection.
@@
 
-Transitive closure of reduction ($\judgeSreduceTrans{C}{s}{s}$) and 
-evaluation ($\judgeSeval{C}{e}{o}$) are standard. Value typing 
-($\judgeType{v}{T}$) is straightforward.
+Reflexive transitive closure of reduction ($\judgeSreduceTrans{C}{s}{s}$) and
+evaluation ($\judgeSeval{C}{e}{o}$) are the same as for \ineffCEK.
 
@@
 
-In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
+In this section, we prove that for all $C$, if $C$ is a Lazy D Cast
 ADT, then
@@
 
-We shall prove that if a instance of Cast ADT $C$ is Lazy D, is a
+We shall prove that if an instance of Cast ADT $C$ is Lazy D, is a
 monoid, and if $cast(T,l,T) = id(T)$, then there is
@@
 
-\todo[inline]{How does the following bisimulation relation
-  compare to the one used in the Blame and Coercion paper?
-  Are there any guiding principles to how this bisimulation
-  relation was constructed? -JS
-\\---\\
-The guiding principle is to keep the change in D side atomic. \\
-In the blame and coercion paper,
-the bisimulation relation between $ \lambda{}C $ and $ \lambda{}S $ seems to be 
-related, but its (iii) rules in Figure 6 looks wired to me. -KC}
+%\todo[inline]{How does the following bisimulation relation
+%  compare to the one used in the Blame and Coercion paper?
+%  Are there any guiding principles to how this bisimulation
+%  relation was constructed? -JS
+%\\---\\
+%The guiding principle is to keep the change in D side atomic. \\
+%In the blame and coercion paper,
+%the bisimulation relation between $ \lambda{}C $ and $ \lambda{}S $ seems to 
+%be 
+%related, but its (iii) rules in Figure 6 looks wired to me. -KC}
 
@@
 The relation is mutually defined on continuations, written $\kappa
-\approx \kappa$, and values, written $v \approx v : T$, where $T$ is
-their type.
-%
-If $k \approx \kappa$, adding an identity cast on top of $k$ gives a related 
-continuation.
-%
-\todo[inline]{The use of ``wrap'' obscures this explanation.
-  Consider getting rid of wrap by inlining it. -JS
-\\---\\
-I agree that inlining wrap and ext can improve readability of $\kappa \approx 
-\kappa$, but this would make latex different from Agda, is it alright?
--KC
-\\---\\
-Yes, that is alright. Inlining is really a trivial change.
--JS
-}
-%
-If $\kappa_1 \approx \kappa_2$, extending $\kappa_1$ and $\kappa_2$ with the 
-same cast gives related results.
+\approx \kappa : T$, where $T$ is their source type, and values, written $v 
+\approx v : T$, where $T$ is their type.
+%
+If $k \approx \kappa : T$, adding an identity cast on top of $k$ gives a 
+related continuation.
+%
+%\todo[inline]{The use of ``wrap'' obscures this explanation.
+%  Consider getting rid of wrap by inlining it. -JS
+%\\---\\
+%I agree that inlining wrap and ext can improve readability of $\kappa \approx 
+%\kappa$, but this would make latex different from Agda, is it alright?
+%-KC
+%\\---\\
+%Yes, that is alright. Inlining is really a trivial change.
+%-JS
+%}
+%
+If $\kOOcast{c}{k_1} \approx \kappa_2 : T$, extending them with 
+the same cast gives related continuations.
 %
@@
 
-  \fbox{$\kappa \approx \kappa$}
+  \fbox{$\kappa \approx \kappa : T$}
   \begin{gather*}
   \inference{
-    k \approx \kappa
-  }{
-    wrap(k) \approx \kappa
+    k \approx \kappa : T
+  }{
+    \kOOcast{id(T)}{k} \approx \kappa
   }
@@
   \inference{
-    \kappa_1 \approx \kappa_2
-  }{
-    ext(cast(T_1,l,T_2),\kappa_1) \approx 
+    \kOOcast{c}{k_1} \approx \kappa_2 : T_2
+  }{
+    \kOOcast{seq(cast(T_1,l,T_2),c)}{k_1} \approx 
     \kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
@@
 
-\todo[inline]{Give the motivation for the following lemma. Where
-  does it get used? As in, which case of which other lemma or theorem? -JS
-\\---\\
-Partially fixed. Will say in which cases after finishing the bisim proof. -KC}
-
-We use the following lemma in our bisimulation proof.
-
-\begin{lemma}[SoAndSo]
+%\todo[inline]{Give the motivation for the following lemma. Where
+%  does it get used? As in, which case of which other lemma or theorem? -JS
+%\\---\\
+%Partially fixed. Will say in which cases after finishing the bisim proof. -KC}
+
+We use the following lemma in our bisimulation proof when cast applications 
+happen.
+
+\begin{lemma}[$applyCast$ Preserves Bisimulation]
   \label{thm:lem-apply-cast-SD}
-  Assume $C$ implements Lazy D Cast ADT
-  and $v_1$ is a value in \effCEK{C}
-  and $v_2$ is a value in \ineffCEKD\
+  Assume $C$ implements Lazy D Cast ADT,
+  $v_1$ is a value in \effCEK{C},
+  $v_2$ is a value in \ineffCEKD,
   and $v_1 \approx v_2 : T_1$,
   \[
-  applyCast_{\text{\effCEK{C}}}(v,cast(T_1,l,T_2)) 
+  applyCast_{\text{\effCEK{C}}}(v_1,cast(T_1,l,T_2)) 
   \approx 
-  applyCast_{\text{\ineffCEKD}}(v,\cOOcast{T_1}{l}{T_2})
+  applyCast_{\text{\ineffCEKD}}(v_2,\cOOcast{T_1}{l}{T_2})
   \]
@@
 Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-introduce one more definition.
+introduce one more definition. $s_1 \approx^{*} s_2$ means we will get $s_1 
+\approx s_2$ after more transition steps in \ineffCEKD.
 
@@
 
-\todo[inline]{Explain that this is an unusual formulation of a weak
-  bisimulation.  We promise it will all be OK regarding how it is used
-  in the correctness proof for S(C). -JS}
+%\todo[inline]{Explain that this is an unusual formulation of a weak
+%  bisimulation.  We promise it will all be OK regarding how it is used
+%  in the correctness proof for S(C). -JS}
+
+The lemma below formulate the weak bisimulation between \effCEK{C} and 
+\ineffCEKD. It is unusual because we use $s \approx s$ in premise while $s 
+\approx^{*} s$ in conclusion. As we will show in the correctness proof for 
+\effCEK{C}, however, this formulation is fine for our purpose.
 
 \begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
-  \label{thm:surely-monoidic-reduce}
+  \label{thm:SD-bisim}
   Assume $C$ implements Lazy D Cast ADT
@@
   and $cast(T,l,T)=id(T)$,
-  $ s_{1} \in \text{\effCEK{C}}$,
-  $ s_{2} \in \text{\ineffCEKD}$,
-  $ s_{1} \approx s_{2}$,
+  $s_{1} \in \text{\effCEK{C}}$,
+  $s_{2} \in \text{\ineffCEKD}$,
+  $s_{1} \approx s_{2}$,
 \begin{enumerate}
@@
   \item If $\judgeSreduce{C}{s_1}{s_3}$ 
-    then $\judgeDreduce{s_2}{s_4}$ for some $s_4$
+    then $\judgeDreduce{s_2}{s_4}$ 
+    and  $s_3 \approx^{*} s_4$
+    for some $s_4$
   \item If $\judgeDreduce{s_2}{s_4}$
-    then $\judgeSreduce{C}{s_1}{s_3}$ for some $s_3$
-  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
-    and  $\judgeDreduce{s_2}{s_4}$ 
-    then $s_3 \approx^{*} s_4$
+    then $\judgeSreduce{C}{s_1}{s_3}$ 
+    and  $s_3 \approx^{*} s_4$
+    for some $s_3$
 \end{enumerate}
@@
   Part (1) and (2) follow from the definition of $s \approx s$.
-  Part (3) and (4) are true because we have transition rules for every 
-  non-halting state.
-  Part (5) is more interesting. Our goal is to prove that one reduction step 
-  in  \effCEK{C} corresponds to one or more steps in \ineffCEKD.  
+  Part (3) and (4) are more interesting. 
+  By the definition of $s \approx s$, it is straightforward to prove 
+  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
+  So we can prove two parts together by showing that 
+  \[
+  \text{if}\; s_{1} \approx s_{2}
+  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
+  \;\text{and}\;\judgeDreduce{s_2}{s_4}
+  \;\text{then}\; s_3 \approx^{*} s_4.
+  \]
+  To put it another way, our goal is to proving 
+  one reduction step in \effCEK{C} corresponds to
+  one or more steps in \ineffCEKD.  
+  Although there are many cases, the general idea is the same.
   Consider
@@
   By looking at the definition of $v \approx v$, we know
-  \[ c_{11} = seq(\dots seq(id(T_1),cast(T_1,l,T_3)) \dots) \]
-  \[ c_{12} = seq(\dots seq(id(T_2),cast(T_2,l,T_4)) \dots) \] 
+  \[ c_{11} = seq(seq(id(T_1),cast(T_1,l,T_3)) \dots) \]
+  \[ c_{12} = seq(seq(id(T_2),cast(T_2,l,T_4)) \dots) \] 
   \[ v_2 = \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
@@
   Thus we have the following reduction in \effCEK{C}. The equation 
-  reasoning employs the fact that $C$ is a monoid.
+  reasoning employs the premise that $C$ is a monoid.
   \[
@@
 = &
-\sOOreturn{v_{11}}{ext(seq(\dots seq(id(T_1),cast(T_1,l,T_3))\dots),\kappa)}
+\sOOreturn{v_{11}}{ext(seq(seq(id(T_1),cast(T_1,l,T_3))\dots),\kappa)}
 \\
 = &
-\sOOreturn{v_{11}}{ext(cast(T_1,l,T_3),\dots,\kappa)}
+\sOOreturn{v_{11}}{
+	ext(id(T_1),ext(cast(T_1,l,T_3),ext(\dots,\kappa)))
+}
+\\
+= &
+\sOOreturn{v_{11}}{ext(cast(T_1,l,T_3),ext(\dots,\kappa)}
   \end{array}
@@
 And we have the following reduction in \ineffCEKD, where the last state is 
-related to the last state in the above sequence.
+related to the above \effCEK{C} state.
 
@@
 (\ref{thm:lem-apply-cast-SD}) when cast applications happen in both machines. 
-And in case spliting, we shall use $cast(T,l,T)=id(T)$ to relate the 
-continuation functions.
+And in case spliting, we employ $cast(T,l,T)=id(T)$ to relate the continuation 
+functions.
 \end{proof}
 
-\todo[inline]{Should I invest time on restating the bisimulation lemma in the 
-standard format? -KC}
-
 \begin{corollary}[Correctness of \effCEK{C}]
-  \label{thm:surely-monoidic-eval}
+  \label{thm:SD-equiv}
   Suppose $C$ is an instance of the Cast ADT
@@
   closer to the halting state.
-  \todo[inline]{I might want to revise this proof. -KC}
 \end{proof}
@@
 %% prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
-%% connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.
+%% connect this theorem to Lemma~\ref{thm:SD-equiv}.
 
@@
 bisimulation. The bisimulation relation is the smallest congruence relation 
-that also includes the pairs induced by the rules below.
-
+that also includes the rules below.
 \begin{gather*}
@@
 \end{lemma}
-\begin{proof} By cases on $s_{1} \approx s_{2}$.
-%
-  The key ideas of this proof are undoing sequencing with the property
-  (2) of Lazy D Cast ADT, and handling all possibly uses of
-  $cast(T,l,T)$ with property (3)-(11).
+\begin{proof} This proof is straightforward. The key ideas are undoing 
+sequencing with the property (2) of Lazy D Cast ADT, and handling all possibly 
+uses of $cast(T,l,T)$ with property (3)-(11).
 \end{proof}
@@
 
-The $L$ cast representation is defined in
-\figref{fig:L-instance-LazyD}.
-
-\todo[inline]{KC, please write a 2-3 sentence overview of
-  the $L$ cast representation. -JS}
+The $L$ cast representation is defined in \figref{fig:L-instance-LazyD}.
+Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
+\ineffCEKD. The operators $id$ and $seq$ are the empty list and list appending 
+respectively. And $applyCast$ applies steps from left to right. Steps are 
+confined by its type rule such that its source and target are different. This 
+restriction is necessary to show $cast(T,l,T) = id(T)$.
 
@@
 \begin{proof}
-  Part (1) is straightforward because property (1) and (2) are trivial and 
-  that $appS$ basically repeats property (3) - (11).
-  Part (2) is true because in $L$ casts are list, $seq(c,c)$ is list 
-  appending, and $id(T)$ is the empty list. Lists is know to be a monoid 
-  where the binary operation is appending and the identity element is the 
-  empty list.
+  Part (1) is straightforward because property (1) and (2) are 
+  trivially true and because $appS$ effectively repeats property (3) - 
+  (11).
+  Part (2) is true because list is known to be a monoid.
   Part (3) follows immediately from the definition of $cast(T,l,T)$
@@
 \begin{proof}
-  Immedialy from Correctness of \effCEK{C} \ref{thm:surely-monoidic-eval} and 
-  L properties \ref{thm:L-LazyD-monoid}.
+  Immedialy from 
+  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
+  Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).
 \end{proof}
@@
 \begin{proof}
-  If we have a Lazy D Cast ADT and it is a monoid, this 
-  proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
-  Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
-  represent casts as a list of triples of type, label, and type, where 
-  $id(T)$ is the empty list and $seq(c,c)$ is the list append. Another such 
-  representation is the \lazyD\ hypercoercion!
+	Immediately from 
+	\evalEqv{\effCEK{C}}{\effCEK{L}} (Lemma~\ref{thm:surely-lazyD-eqv})
+	and
+	\evalEqv{\effCEK{L}}{\ineffCEKD} (Lemma~\ref{lem:L-correct})
 \end{proof}
@@
   %
-  Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
+  Alternatively, from Lemma~\ref{thm:SD-equiv},
   Lemma~\ref{thm:hc-surely-lazyD}, Proposition~\ref{thm:LazyD-HC-monoid}, and 
@@
 
-\todo[inline]{
-Back out and be like remember all our contribution. Bring them back to the 
-beginning. Repeat but not repeat literally.
-I can assume that people have eaten meat.
-}
-
 In this paper we presented a new cast representation, hypercoercions, in two 
 flavors, Lazy D and Lazy UD. Hypercoercions have a structurally recursive 
-composition, which is a win over coercions in normal form for mechanized 
-metatheory. What is more, hypercoercions have a more compact memory 
-representation.
+composition and have a more compact memory representation in comparison to 
+coercions in normal form.
 
@@
 ADT.
-Cast ADT is the interface between cast representations and \effCEK{C}. Its
-implementation should provide four functions: $cast(T,l,T) = c$, $id(T)=c$, and 
-$seq(c,c)=c$ for cast construction, and $applyCast(v,c)=r$ for cast application.
 %

### 2019-10-25 paper.tex
fixed typo in 2
improve weak bisim statement

@@
 \newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
+\newcommand{\judgeDreducePlus}[2]{#1 \longmapsto_{\mathcal{D}}^{+} #2}
 \newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
@@
 \[
+\judgeDreduceTrans{s_2}{s_2'}
+\;\text{and}\;
 s_1 \approx s_2'
-\;\text{and}\;
-\judgeDreduceTrans{s_2}{s_2'}
 \]
@@
 \begin{enumerate}
-  \item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
-  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
   \item If $\judgeSreduce{C}{s_1}{s_3}$ 
@@
 \end{enumerate}
+{\color{red}
+  Jeremy's attempt to reformulate in a more standard way that
+  remains equivalent:
+\begin{enumerate}
+\item If $\judgeSreduce{C}{s_1}{s_3}$ then
+  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
+\item If $\judgeDreduce{s_2}{s_4}$ then
+  $\judgeSreduce{C}{s_1}{s_3}$,
+  $\judgeDreduceTrans{s_2}{s_5}$, and
+   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
+\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+\end{enumerate}
+}
 Or diagrammatically, 
@@
 \begin{proof}
-  Part (1) and (2) follow from the definition of $s \approx s$.
-  Part (3) and (4) are more interesting. 
+  Part (1) follow from the definition of $s \approx s$.
+  Part (2) and (3) are more interesting. 
   By the definition of $s \approx s$, it is straightforward to prove 

### 2019-10-25 paper.tex
minor edits to the conclusion

@@
 \begin{enumerate}
-  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
-%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+  \item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
+  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
   \item If $\judgeSreduce{C}{s_1}{s_3}$ 
@@
   $\judgeSreduce{C}{s_1}{s_3}$,
-  $\judgeDreduceTrans{s_2}{s_5}$, and
+  $\judgeDreduceTrans{s_4}{s_5}$, and
    $s_3 \approx s_5$ for some $s_3$ and $s_5$.
@@
 \begin{proof}
-  Part (1) follow from the definition of $s \approx s$.
-  Part (2) and (3) are more interesting. 
+  Part (1) and (2) follow from the definition of $s \approx s$.
+  Part (3) and (4) are more interesting. 
   By the definition of $s \approx s$, it is straightforward to prove 
@@
 \begin{proof} This proof is straightforward. The key ideas are undoing 
-sequencing with the property (2) of Lazy D Cast ADT, and handling all possibly 
-uses of $cast(T,l,T)$ with property (3)-(11).
+  uses of $seq$ with the property (2) of Lazy D Cast ADT, and handling all
+  uses of $cast$ with properties (3)-(11).
 \end{proof}
@@
 
-In this paper we presented a new cast representation, hypercoercions, in two 
-flavors, Lazy D and Lazy UD. Hypercoercions have a structurally recursive 
-composition and have a more compact memory representation in comparison to 
-coercions in normal form.
-
-We also present steps toward the first framework for proving the correctness of 
-cast representations.
-%
-The framework includes abstract data types for cast representations (Cast ADT 
-and Lazy D Cast ADT), an parameterized abstract machine \effCEK{C}, and a 
-theorem states that \effCEK{C} is equivalent to $D$ if $C$ is a Lazy D Cast 
-ADT.
-%
-Lazy D Cast ADT refines Cast ADT. We conjecture that Lazy D threesomes, and 
-Lazy D coercions in normal form are also Lazy D Cast ADT.
-
-Finally, we proved that Lazy D hypercoercions ($H$) is a Lazy D Cast ADT. By 
-using our framework, we shown that it is a correct cast representation because 
-$S(H)$ is equivalent to $D$.
+In this paper we presented a new cast representation, hypercoercions,
+in two flavors, Lazy D and Lazy UD. Hypercoercions have a structurally
+recursive composition operator and have a more compact memory
+representation in comparison to coercions in normal form.
+
+We also present steps toward the first framework for proving the
+correctness of cast representations.
+%
+The framework includes abstract data types for cast representations
+(Cast ADT and Lazy D Cast ADT), a parameterized abstract machine
+\effCEK{C}, and a theorem which states that \effCEK{C} is equivalent
+to $D$ when $C$ is a Lazy D Cast ADT.
+%
+The Lazy D Cast ADT refines the Cast ADT. We conjecture that Lazy D
+threesomes, and Lazy D coercions in normal form are instances of the
+Lazy D Cast ADT.
+
+Finally, we proved that Lazy D hypercoercions ($H$) is a Lazy D Cast
+ADT. By using our framework, we showed that it is a correct cast
+representation because $S(H)$ is equivalent to $D$.
 

### 2019-10-25 paper.tex
corol 4.8

--- 2019-10-25 paper.tex
@@
 \begin{proof}
-  Proving that the left-hand side implies the right-hand side is
-  trivial.  To prove $\judgeDeval{e}{o}$ implies
-  $\judgeSeval{C}{e}{o}$, we first take one step in \effCEK{C}, and
-  catch it up in \ineffCEKD\ by taking one or more steps in
-  \ineffCEKD. As we just took a positive number of steps, we are
-  closer to the halting state.
+	By the definitions of $eval$, we need to show 
+	\[
+	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{
+		\sOOhalt{o}
+	}
+	\;\text{if and only if}\;
+	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{\kOOmt}}{
+		\sOOhalt{o}
+	}
+	\]
+	Obviously, the initial states are related in the bisimulation relation.
+	\[
+	\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}
+	\approx
+	\sOOinspect{e}{\emptyset}{\kOOmt}
+	\]
+	So we can generalize our goal, and prove that if $s_1 \approx s_2$
+	\[
+	\judgeSreduceTrans{C}{s_1}{\sOOhalt{o}}
+	\;\text{if and only if}\;
+	\judgeSreduceTrans{C}{s_2}{\sOOhalt{o}}
+	\]
+	Let us prove left to right first by induction on 
+	$\judgeSreduceTrans{C}{s_1}{\sOOhalt{o}}$.
+
+	\begin{itemize}
+		\item 
+		If $s_1$ takes zero step to the halting state, it must be halting.
+		By Lemma~\ref{thm:SD-bisim}, $s_2$ is halting as well, so we are done.
+		\item 
+		If $\judgeSreduce{C}{s_1}{s_3}$ and 
+		$\judgeSreduceTrans{C}{s_3}{\sOOhalt{o}}$,
+		by Lemma~\ref{thm:SD-bisim}, there exists a $s_4$ such that 
+		$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$. So we can apply 
+		our induction hypothesis.
+	\end{itemize}
+
+	The other direction is similar.
+%  Proving that the left-hand side implies the right-hand side is
+%  trivial.  To prove $\judgeDeval{e}{o}$ implies
+%  $\judgeSeval{C}{e}{o}$, we first take one step in \effCEK{C}, and
+%  catch it up in \ineffCEKD\ by taking one or more steps in
+%  \ineffCEKD. As we just took a positive number of steps, we are
+%  closer to the halting state.
 \end{proof}

### 2019-10-25 paper.tex
tweak
grammar check

@@
 
-\todo[inline]{
-	Check grammar;
-	Improve the proof of \ref{thm:SD-bisim}.
-	And the proof of \ref{thm:SD-equiv}
-}
-
 Around 2006, several groups of researchers proposed ways to integrate
@@
 migratory typing \citep{Tobin-Hochstadt:2006fk}, and multi-language
-iteroperability \citep{Gray:2005ij,Matthews:2007zr}. Researchers
+interoperability \citep{Gray:2005ij,Matthews:2007zr}. Researchers
 usually define the semantics of gradually typed languages by
@@
 On the other hand, coercions in normal form are easier to understand
-than threesomes (with a strange labelled bottom type), and
+than threesomes (with a strange labeled bottom type), and
 supercoercions (10 different kinds).
@@
 The semantics of casts can be lazy or
-eager~\citep{siek2009exploring}. In this paper we focus on lazy cast
+eager~\citep{siek2009exploring}. In this paper, we focus on lazy cast
 strategies because we suspect that they are more efficient than eager
-strategies and because \citet{new2019gradual} show that eager
+strategies and because \citet{new2019gradual} show that the eager
 strategies are incompatible with $\eta$-equivalence of functions.
@@
 \item a framework in Agda for proving the correctness of \lazyD{} cast
-  represantations.
+  representations.
 \item a formal proof that \lazyD\ hypercoercions respect the semantics
@@
 Section~\ref{sec:hypercoercion-definition}.  We present a framework
-for proving correctness of \lazyD\ cast reprensentations in
+for proving the correctness of \lazyD\ cast representations in
 Section~\ref{sec:framework} and use it to prove the correctness of
@@
 The syntax and static semantics is the same for the \lazyD{} and
-\lazyUD{} cast calculi, and is reviewed in \figref{fig:blame-static}.
+\lazyUD{} cast calculi and is reviewed in \figref{fig:blame-static}.
 As usual, the important features are the cast expressions,
@@
 compressing continuations). So using an abstract machine for the cast calculi in
-this section makes it easier to prove correctness of the space-efficient
+this section makes it easier to prove the correctness of the space-efficient
 machines. Of course, one should prove that the abstract machine
@@
 %
-Recall that CEK machine involves two kinds of transitions, (1) those
+Recall that CEK machines involve two kinds of transitions, (1) those
 that dive further into an expression (looking for a redex) and push an
@@
 current continuation and possibly perform a computation.
-Corresponding to (1) and (2), the machine state is either in an
-$\sOOinspect{e}{\mathcal{E}}{\kappa}$ or $\sOOreturn{v}{\kappa}$ configuration, 
+Corresponding to (1) and (2), the machine state is either in an evaluating
+$\sOOinspect{e}{\mathcal{E}}{\kappa}$ or continuing $\sOOreturn{v}{\kappa}$ configuration, 
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
@@
 To take out the first (resp. second) part of a casted pair, the
-machine firstly take out the first (resp. second) part of $v$, the
+machine firstly takes out the first (resp. second) part of $v$, the
 underlying pair, and cast the result.
@@
 
-Next we define the CEK Machine for \lazyUD{}. The only difference with
+Next, we define the CEK Machine for \lazyUD{}. The only difference with
 respect to \lazyD{} is in the definition of the $\mathit{applyCast}$
 function, in which a cast whose source or target is the unknown type
-$\star$ is always split into two casts that go through an injectiable
+$\star$ is always split into two casts that go through an injectable
 type, that is, a type in which all sub-components are the unknown
@@
 
-In this section we review the
+In this section, we review the
 coercions~\citep{henglein1994dynamic,herman2010space} and the normal
 form of \citet{siek2012interpretations} to motivate the design of
-hypercoercions.  We omit sum types and product types in this section,
+hypercoercions.  We omit sum types and product types in this section
 because \citet{siek2012interpretations} did not discuss them. We
@@
 %
-To review, an injection $I!$ takes a value from an injectiable type
+To review, an injection $I!$ takes a value from an injectable type
 $I$ to type $\TOOdyn$. An injectable type is simply a type that can be
 cast directly to (injection) and from (projection) $\TOOdyn$. The
-definition of injectable type depends on blame strategy. With \lazyD,
+definition of injectable types depends on the blame strategy. With \lazyD,
 all pre-types are injectable. With \lazyUD, only
@@
 observation that a normal coercion has at most three
-parts. Hypercoercions make this structure explicit: a hypercion $c$ is
+parts. Hypercoercions make this structure explicit: a hypercoercion $c$ is
 either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or it contains
@@
 functions that construct
-\lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines the
+\lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines
 \lazyUD\ counterparts.  The functions that apply hypercoercions to
@@
 
-\begin{figure}
-  Syntax
+\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient CEK
+machine parameterized over Cast ADT ($C$).  The key differences between 
+\effCEK{C} and \ineffCEK\ are the places where casts can accumulate at runtime, 
+that is, values and continuations. We discuss above the difference in values
+(Definition~\ref{def:values-effCEK}).
+
+\begin{definition}[Continuations for the \effCEK{C} machine] 
+\label{def:values-effCEK}
   \[
@@
   \]
-
+\end{definition}
+
+Let $\kappa$ range over continuations and let $k$ range over
+pre-continuations.
+%
+Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
+constructor for casts.
+%
+A continuation is now a pre-continuation prefixed with a cast.
+%
+Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
+\effCEK{C}, however, every continuation has exactly one cast at the top.
+Continuations in \ineffCEK\ that have no casts at the top correspond
+to continuations in \effCEK{C}\ whose casts are identities.
+Continuations in \ineffCEK\ that have many casts at the top correspond
+to continuations in \effCEK{C}\ where those casts are composed by
+$seq(c,c)$.
+
+\begin{figure} 
   Build continuation \fbox{$wrap(k) = \kappa$}
@@
 \end{figure}
-
-\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient CEK
-machine parameterized over Cast ADT ($C$).  The key differences between 
-\effCEK{C} and \ineffCEK\ are the places where casts can accumulate at runtime, 
-that is, values and continuations. We discuss above the difference in values
-(Definition~\ref{def:values-effCEK}).
-
-Let $\kappa$ range over continuations and let $k$ range over
-pre-continuations.
-%
-Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
-constructor for casts.
-%
-A continuation is now a pre-continuation prefixed with a cast.
-%
-Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
-\effCEK{C}, however, every continuation has exactly one cast at the top.
-Continuations in \ineffCEK\ that have no casts at the top correspond
-to continuations in \effCEK{C}\ whose casts are identities.
-Continuations in \ineffCEK\ that have many casts at the top correspond
-to continuations in \effCEK{C}\ where those casts are composed by
-$seq(c,c)$.
 
@@
 
-Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-introduce one more definition. $s_1 \approx^{*} s_2$ means we will get $s_1 
-\approx s_2$ after more transition steps in \ineffCEKD.
-
-\begin{definition}[$s \approx^{*} s$]
-Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
-if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
-that
-\[
-\judgeDreduceTrans{s_2}{s_2'}
-\;\text{and}\;
-s_1 \approx s_2'
-\]
-\end{definition}
-
-%\todo[inline]{Explain that this is an unusual formulation of a weak
-%  bisimulation.  We promise it will all be OK regarding how it is used
-%  in the correctness proof for S(C). -JS}
-
-The lemma below formulate the weak bisimulation between \effCEK{C} and 
-\ineffCEKD. It is unusual because we use $s \approx s$ in premise while $s 
-\approx^{*} s$ in conclusion. As we will show in the correctness proof for 
-\effCEK{C}, however, this formulation is fine for our purpose.
+%Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
+%introduce one more definition. $s_1 \approx^{*} s_2$ means we will get $s_1 
+%\approx s_2$ after more transition steps in \ineffCEKD.
+%
+%\begin{definition}[$s \approx^{*} s$]
+%Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
+%if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
+%that
+%\[
+%\judgeDreduceTrans{s_2}{s_2'}
+%\;\text{and}\;
+%s_1 \approx s_2'
+%\]
+%\end{definition}
+%
+%%\todo[inline]{Explain that this is an unusual formulation of a weak
+%%  bisimulation.  We promise it will all be OK regarding how it is used
+%%  in the correctness proof for S(C). -JS}
+%
+%The lemma below formulate the weak bisimulation between \effCEK{C} and 
+%\ineffCEKD. It is unusual because we use $s \approx s$ in premise while $s 
+%\approx^{*} s$ in conclusion. As we will show in the correctness proof for 
+%\effCEK{C}, however, this formulation is fine for our purpose.
 
@@
 \begin{enumerate}
-  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
-%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
-  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
-    then $\judgeDreduce{s_2}{s_4}$ 
-    and  $s_3 \approx^{*} s_4$
-    for some $s_4$
-  \item If $\judgeDreduce{s_2}{s_4}$
-    then $\judgeSreduce{C}{s_1}{s_3}$ 
-    and  $s_3 \approx^{*} s_4$
-    for some $s_3$
-\end{enumerate}
-{\color{red}
-  Jeremy's attempt to reformulate in a more standard way that
-  remains equivalent:
-\begin{enumerate}
 	\item If $\judgeSreduce{C}{s_1}{s_3}$ then
-  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
+	$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
 	\item If $\judgeDreduce{s_2}{s_4}$ then
-  $\judgeSreduce{C}{s_1}{s_3}$,
+	$\judgeSreduceTrans{C}{s_1}{s_3}$,
 	$\judgeDreduceTrans{s_4}{s_5}$, and
@@
 \end{enumerate}
-}
-Or diagrammatically, 
-  \[\begin{array}{clclc}
-  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-  \rotatebox[origin=c]{90}{$\approx$} 
-  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-  s_{2} & 
-  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
-  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-  \end{array}\]
+%\begin{enumerate}
+%  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+%  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
+%    then $\judgeDreduce{s_2}{s_4}$ 
+%    and  $s_3 \approx^{*} s_4$
+%    for some $s_4$
+%  \item If $\judgeDreduce{s_2}{s_4}$
+%    then $\judgeSreduce{C}{s_1}{s_3}$ 
+%    and  $s_3 \approx^{*} s_4$
+%    for some $s_3$
+%\end{enumerate}
+%{\color{red}
+%  Jeremy's attempt to reformulate in a more standard way that
+%  remains equivalent:
+%\begin{enumerate}
+%\item If $\judgeSreduce{C}{s_1}{s_3}$ then
+%  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
+%\item If $\judgeDreduce{s_2}{s_4}$ then
+%  $\judgeSreduce{C}{s_1}{s_3}$,
+%  $\judgeDreduceTrans{s_4}{s_5}$, and
+%   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
+%\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%\end{enumerate}
+%}
+%Or diagrammatically, 
+%  \[\begin{array}{clclc}
+%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%  \rotatebox[origin=c]{90}{$\approx$} 
+%  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%  s_{2} & 
+%  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%  \end{array}\]
 \end{lemma}
@@
 	\]
+
 	Let us prove left to right first by induction on 
@@
 
-	The other direction is similar.
+	Now let us prove right to left by induction on 
+	$\judgeDreduceTrans{s_2}{\sOOhalt{o}}$.
+	\begin{itemize}
+		\item If $s_2$ takes zero step to the halting state, it must be halting.
+		By Lemma~\ref{thm:SD-bisim}, $s_2$ is halting as well, so we are done.
+		\item If $\judgeDreduce{s_2}{s_4}$ and 
+		$\judgeDreduceTrans{s_4}{\sOOhalt{o}}$,
+		by Lemma~\ref{thm:SD-bisim}, there exist $s_3,s_5$ such that
+		\[
+			\judgeSreduceTrans{C}{s_1}{s_3}
+			\;\text{and}\;
+			\judgeDreduceTrans{s_4}{s_5}
+			\;\text{and}\;
+			s_3 \approx s_5
+		\]
+		From $\judgeDreduceTrans{s_4}{\sOOhalt{o}}$ and 
+		$\judgeDreduceTrans{s_4}{s_5}$ we know 
+		$\judgeDreduceTrans{s_5}{\sOOhalt{o}}$ because our machine is 
+		deterministic. Now we can apply our induction hypothesis.
+	\end{itemize}
 %  Proving that the left-hand side implies the right-hand side is

### 2019-10-25 paper.tex

@@
 
-In this section, we review lazy cast calculi
-(Section~\ref{sec:cast-calculi}) and coercions 
-(Section~\ref{sec:coercion-calculus}).
+In this section, we fist review lazy cast calculi
+(Section~\ref{sec:cast-calculi}), where we present an abstract machine that is 
+employed in our framework (Section~\ref{sec:framework}). Then we review 
+coercions and their normal forms (Section~\ref{sec:coercion-calculus}), which 
+motivates and inspires the design of hypercoercions 
+(Section~\ref{sec:hypercoercion-definition}).
 
@@
 constructors and blame. The function converting values to 
-observations ($observe(v) = o$) is defined in the natural way.
+observations ($observe(v) = o$) is defined in the obvious way.
 %Let $s$ range over machine states. A state is either looking at an 
@@
   \]
-  \caption{Syntax of coercions and normal forms}
+  \caption{Syntax of coercions and normal forms {\`a} la \citet{siek2012interpretations}.}
   \label{fig:normal-coercion}
@@
 \figref{fig:HC-D} defines the functions $id$, $seq$, and $cast$ that
-construct \lazyD{} hypercoercions, towards satisifying the Cast abstract data 
+construct \lazyD{} hypercoercions, towards satisfying the Cast abstract data 
 type defined in Section~\ref{sec:framework}.
@@
 type of the first coercion does not match the source type of the second. 
-Then we write composition of hypercoercions as $c_1
+Then we write the composition of hypercoercions as $c_1
 \fatsemi^\ell c_2$.  When both $c_1$ and $c_2$ are $\hyperCoercionI$,
@@
 composing shallowly inconsistent hypercoercions. The last two cases
-compose $m_1$ and $m_2$ with the auxilliary function $m \fatsemi^\ell
+compose $m_1$ and $m_2$ with the auxiliary function $m \fatsemi^\ell
 m$, which assumes its inputs have the same top constructor. The
@@
 target type of $c_1$ matches the source type of $c_2$.  The definition
-of composition for UD is particularly straightfoward. The first two
+of composition for UD is particularly straightforward. The first two
 lines say that $\hyperCoercionI$ acts as the identity on both the left
@@
 %
-Coercions involving non-base types, such as functions types,
-may be arbitrarily large, so in those cases the hypercoercion
+Coercions involving non-base types, such as function types,
+may be arbitrarily large, so in those cases, the hypercoercion
 representation can be a pointer to a heap-allocated structure.  Here
@@
 
-\item If the middle is of base type, then the remaining 62 bits are
+\item If the middle is of base types, then the remaining 62 bits are
   used to represent the head (25 bits), middle (11 bits), and tail (26
@@
 We conjecture that all cast representations defined in the literature
-are instances of this ADT.
+are instances of this ADT. The framework is available at the following URL:
+\[\text{\urlLazyDProof}\]
 
@@
 instance $C$ of the Cast ADT, if $C$ satisfies a more refined abstract
-data type for Lazy D casts, then \effCEK{C} is equivelent to
+data type for Lazy D casts, then \effCEK{C} is equivalent to
 \ineffCEKD{}, that is,
@@
 constructor for all casted values.  In \effCEK{C}, however, we do not
-have this generic value constructor, instead we push casts into the ordinary 
-values. Thus non-casted values in \ineffCEK\ corresponds to values in 
+have this generic value constructor, instead, we push casts into the ordinary 
+values. Thus non-casted values in \ineffCEK\ correspond to values in 
 \effCEK{C} where casts are identities. For instance, $(\vOOcons{v_1}{v_2})$ 
@@
 \effCEK{C} to construct casts so we call them \textit{cast
-  constructors}. The forth and last operator enables \effCEK{C} to
+  constructors}. The fourth and last operator enables \effCEK{C} to
 apply casts to values.
@@
 
-Next we define the \emph{Lazy D Cast ADT}, which capture the further
+Next, we define the \emph{Lazy D Cast ADT}, which captures the further
 requirements that are needed for the theorem that establishes
 equivalence to \ineffCEKD{}. Property (1) below states that $id(T)$
-acts like the identity function. Property (2) states that $seq(c,c)$
-acts like a sequence of casts. Properties (3) through (11) state that
-$cast(T_1,l,T_2)$ act like the Lazy D $applyCast$ for \ineffCEK\
+acts as the identity function. Property (2) states that $seq(c,c)$
+acts as a sequence of casts. Properties (3) through (11) state that
+$cast(T_1,l,T_2)$ acts like the Lazy D $applyCast$ for \ineffCEK\
 (Fig.~\ref{fig:applyCast-D-C}).
@@
 
-\figref{fig:machine-cekcc} defines \effCEK{C}, a space-efficient CEK
-machine parameterized over Cast ADT ($C$).  The key differences between 
-\effCEK{C} and \ineffCEK\ are the places where casts can accumulate at runtime, 
-that is, values and continuations. We discuss above the difference in values
-(Definition~\ref{def:values-effCEK}).
+%<<<<<<< HEAD
+\effCEK{C} is a space-efficient CEK machine parameterized over Cast ADT ($C$).  
+The key differences between \effCEK{C} and \ineffCEK\ are the places where 
+casts can accumulate at runtime, that is, values and continuations. We discuss 
+above the difference in values (Definition~\ref{def:values-effCEK}).
 
@@
 \label{def:values-effCEK}
+%=======
+%\begin{figure}
+%%  Syntax
+%>>>>>>> bd39888b0287dbef61e981bd0e79bc8822fc85ce
   \[
@@
 
-The transition relation $\judgeSreduce{C}{s}{s}$ relies on functions provided 
+\figref{fig:machine-cekcc} defines the transition relation 
+$\judgeSreduce{C}{s}{s}$. They rely on functions provided 
 by $C$ to work with casts.
@@
 operand $v_2$, extends the continuation with the codomain cast $c_2$, and 
-evaluate the function body.
+evaluates the function body.
 %
@@
 %%
-To case split a variant, the machine first look at the variant value. If the 
+To case split a variant, the machine first looks at the variant value. If the 
 variant is a left injection, the machine composes the cast in the left 
@@
 %
-If functions are related, we can apply the same cast on both side.
+If functions are related, we can apply the same cast on both sides.
 %
@@
   \inference{
-    v_1 \approx v_2 : P
-  }{
-    \hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
+    v_1 \approx v_2 : I
+  }{
+    \hcvOOinj{I}{v_1} \approx \vOOcast{v_2}{\cOOcast{I}{l}{\TOOdyn}}
     : \TOOdyn
@@
 \begin{proof}
-  Part (1) follow from the definition of $s \approx s$.
+  Part (1) follows from the definition of $s \approx s$.
   Part (2) and (3) are more interesting. 
@@
 
-Other cases are similar. Of course we need the lemma about $applyCast$ 
+Other cases are similar. Of course, we need the lemma about $applyCast$ 
 (\ref{thm:lem-apply-cast-SD}) when cast applications happen in both machines. 
-And in case spliting, we employ $cast(T,l,T)=id(T)$ to relate the continuation 
+And in case splitting, we employ $cast(T,l,T)=id(T)$ to relate the continuation 
 functions.
@@
   Suppose $C$ is an instance of the Cast ADT
-  and the \lazyD{} ADT, $C$ is a monoid,
+  and the \lazyD{} ADT, $C$ is a monoid
   and $cast(T,l,T)=id(T)$.
@@
 % 
-  Or diagrammatically, 
-  \[\begin{array}{clc}
-  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_3\\
-  \rotatebox[origin=c]{90}{$\approx$} 
-  & & \rotatebox[origin=c]{90}{$\approx$} \\
-  s_{2} & 
-  \longrightarrow_{\text{\ineffCEKD}} & s_4 \\
-  \end{array}\]
+%  Or diagrammatically, 
+%  \[\begin{array}{clc}
+%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_3\\
+%  \rotatebox[origin=c]{90}{$\approx$} 
+%  & & \rotatebox[origin=c]{90}{$\approx$} \\
+%  s_{2} & 
+%  \longrightarrow_{\text{\ineffCEKD}} & s_4 \\
+%  \end{array}\]
 \end{lemma}
@@
 \begin{proof}
-  Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
+  Without lose of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
   $\judgeSreduce{C_2}{e}{o}$.\\
@@
 \begin{proof}
-  Immedialy from 
+  Immediately from
   Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
@@
 
-In this section we prove \lazyD\ hypercoercion is 
-correct. First we define $applyCast(v,c)$ to make it an instance of Cast ADT, 
+In this section, we prove \lazyD\ hypercoercions are 
+correct. First, we define $applyCast(v,c)$ to make it an instance of Cast ADT, 
 then prove that it is also Lazy D, and finally apply 
@@
 apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
-that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise the result 
+that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
 is the failure.
@@
 shallow-consistency to compare middles and values ($v \smile m$) in the 
-natural way.
+obvious way.
 
@@
 
-In this paper we presented a new cast representation, hypercoercions,
+In this paper, we presented a new cast representation, hypercoercions,
 in two flavors, Lazy D and Lazy UD. Hypercoercions have a structurally
@@
 The framework includes abstract data types for cast representations
-(Cast ADT and Lazy D Cast ADT), a parameterized abstract machine
+(Cast ADT and its refinement Lazy D Cast ADT), a parameterized abstract machine
 \effCEK{C}, and a theorem which states that \effCEK{C} is equivalent
@@
 %
-The Lazy D Cast ADT refines the Cast ADT. We conjecture that Lazy D
-threesomes, and Lazy D coercions in normal form are instances of the
+%The Lazy D Cast ADT refines the Cast ADT. 
+%
+We conjecture that Lazy D
+threesomes and Lazy D coercions in normal form are instances of the
 Lazy D Cast ADT.

### 2019-10-25 paper.tex
check
added reason to first bisim rule

@@
 % names
-\newcommand{\ineffCEK}{$\mathcal{X}$}
-\newcommand{\ineffCEKD}{$\mathcal{D}$}
-\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
+\newcommand{\ineffCEK}{\ensuremath{\mathcal{X}}}
+\newcommand{\ineffCEKD}{\ensuremath{\mathcal{D}}}
+\newcommand{\ineffCEKUD}{\ensuremath{\mathcal{UD}}}
 \newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
@@
 \newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
-\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
+\newcommand{\effCEK}[1]{\ensuremath{\mathcal{S}(#1)}}
 \newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}
@@
 
-Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.  It is
-the smallest congruence relation that also includes the pairs induced
-by the rules in Fig.~\ref{fig:bisim-SC-D}.
+Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation
+$s_1 \approx s_2$, where $s_1 \in \effCEK{C}$ and $s_2 \in \ineffCEKD{}$.
+It is the smallest congruence relation that also includes the
+pairs induced by the rules in Fig.~\ref{fig:bisim-SC-D}.
 %
@@
 If $k \approx \kappa : T$, adding an identity cast on top of $k$ gives a 
-related continuation.
+related continuation. This handles the way in which
+\effCEK{C} uses $wrap$ to add identity coercions around continuations
+whereas \ineffCEKD{} does not.
 %
@@
 \begin{figure}
-  $\text{\effCEK{C}} \approx \text{\ineffCEKD}$
+%  $\text{\effCEK{C}} \approx \text{\ineffCEKD}$
 % \[\dots\]
-
+  \fbox{$s \approx s$}
+  % Because the grammar for states of the two machines are not identical,
+  % I think it is worthwhile to write out these rules explicitly. -Jeremy
+  \begin{gather*}
+    \inference{dom(\mathcal{E}_1) = dom(\mathcal{E}_2) \\
+               \forall x {:} T \in dom(\mathcal{E}_1),\,
+                   \mathcal{E}_1(x) \approx \mathcal{E}_2(x) : T\\
+               \kappa_1 \approx \kappa_2 : T}
+              {\langle e, \mathcal{E}_1, \kappa_1 \rangle \approx
+              \langle e, \mathcal{E}_2, \kappa_2 \rangle}
+    %% \quad
+    %% \inference{v_1 \approx v_2 : T \quad \kappa_1 \approx \kappa_2 : T}
+    %%           {\langle v_1, \kappa_1 \rangle  \approx
+    %%           \langle v_2, \kappa_2 \rangle}
+    \quad
+    \inference{}
+              {\sOOhalt{o} \approx \sOOhalt{o}}
+  \end{gather*}
   \fbox{$\kappa \approx \kappa : T$}

### 2019-10-25 paper.tex
fixing typo: fist -> first

@@
 
-In this section, we fist review lazy cast calculi
+In this section, we first review lazy cast calculi
 (Section~\ref{sec:cast-calculi}), where we present an abstract machine that is 
@@
 If $k \approx \kappa : T$, adding an identity cast on top of $k$ gives a 
-related continuation. This handles the way in which
-\effCEK{C} uses $wrap$ to add identity coercions around continuations
-whereas \ineffCEKD{} does not.
+related continuation.
 %
@@
   \fbox{$s \approx s$}
-  % Because the grammar for states of the two machines are not identical,
-  % I think it is worthwhile to write out these rules explicitly. -Jeremy
+  % The following rules for s \approx s are technically not needed,
+  % but I think it's kind
+  % to the reader to include them. -Jeremy
   \begin{gather*}
@@
               \langle e, \mathcal{E}_2, \kappa_2 \rangle}
-    %% \quad
-    %% \inference{v_1 \approx v_2 : T \quad \kappa_1 \approx \kappa_2 : T}
-    %%           {\langle v_1, \kappa_1 \rangle  \approx
-    %%           \langle v_2, \kappa_2 \rangle}
+    \quad
+    \inference{v_1 \approx v_2 : T \quad \kappa_1 \approx \kappa_2 : T}
+              {\langle v_1, \kappa_1 \rangle  \approx
+              \langle v_2, \kappa_2 \rangle}
     \quad

### 2019-10-25 paper.tex
typo: subject verb agreement
adding some description

@@
 \newcommand{\vOOcast}[2]{#1\langle#2\rangle}
-\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
+%\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
+% Jeremy prefers the following
+\newcommand{\vOOfun}[3]{\langle \lambda  #2. #3, #1 \rangle}
 \newcommand{\vOOtt}[0]{\mathtt{unit}}
@@
 %\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
-\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
+%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
+% Jeremy prefers the following version:
+\newcommand{\hcvOOfun}[5]{\langle \lambda #3.\, #4 , #1 , #5, #2 \rangle}
 \newcommand{\hcvOOtt}[0]{\mathtt{unit}}
@@
 
-The syntax and static semantics is the same for the \lazyD{} and
-\lazyUD{} cast calculi and is reviewed in \figref{fig:blame-static}.
+The syntax and static semantics are the same for the \lazyD{} and
+\lazyUD{} cast calculi. They are reviewed in \figref{fig:blame-static}.
 As usual, the important features are the cast expressions,
@@
 
-  Reduction \fbox{$\judgeCreduce{s}{s}$}
+  Transition \fbox{$\judgeCreduce{s}{s}$}
   \[
@@
 
-  Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
+  Transition \fbox{$\judgeSreduce{C}{s}{s}$}
   \[
@@
 related continuation. This handles the way in which
-\effCEK{C} uses $wrap$ to add identity coercions around continuations
+\effCEK{C} uses $wrap$ to push identity coercions onto continuations
 whereas \ineffCEKD{} does not.
+%
+We remark that this bisimulation relation is unusual in that it uses
+some ADT operations in its definition, such as $id$, $cast$, and
+$seq$, which is necessary because \effCEK{C} and the bisimulation
+is parameterized over the Cast ADT.
 %
@@
 %
-If $\kOOcast{c}{k_1} \approx \kappa_2 : T$, extending them with 
-the same cast gives related continuations.
-%
-If two values of type $P$ are related, injecting them to $\TOOdyn$ gives 
-related values.
+If $\kOOcast{c}{k_1} \approx \kappa_2 : T$, extending the right-hand
+side with a cast $T_1 \Rightarrow^l T_2$ and sequencing
+$cast(T_1,l,T_2)$ with $c$ on the left-hand side, produces related
+continuations. This takes care of the difference between
+the transition rules for $e \langle T_1 \Rightarrow^l T_2$
+on the two machines.
+%
+If two values of type $I$ are related, injecting them to $\TOOdyn$
+gives related values.
 %
@@
 %
-To relate to a naked function in \ineffCEKD, the function in \effCEK{C} 
-must use identities as its casts.
-%
-If functions are related, we can apply the same cast on both sides.
-%
-Rules for products and sums are similar.
+To relate to a closure in \ineffCEKD, the closure in \effCEK{C} must
+have identities as its casts.
+%
+If a closure on the left is related to a value, we can apply
+equivalent casts on both sides to obtain related values.
+%
+The rules for products and sums are similar.
 
@@
   \\ \\
-   \inference{}{
-    \hcvOOtt \approx \vOOtt : \POOunit
-   }
-   \quad
+   %% This one is an obvious congruence rule. -Jeremy
+   %% \inference{}{
+   %%  \hcvOOtt \approx \vOOtt : \POOunit
+   %% }
+   %% \quad
   \inference{}{

### 2019-10-25 paper.tex
some edits

@@
 on the two machines.
-%
-If two values of type $I$ are related, injecting them to $\TOOdyn$
-gives related values.
-%
-% The following is part of being a congruence. -JS
-%Unit values are of course related. 
-%
-To relate to a closure in \ineffCEKD, the closure in \effCEK{C} must
-have identities as its casts.
-%
-If a closure on the left is related to a value, we can apply
-equivalent casts on both sides to obtain related values.
-%
-The rules for products and sums are similar.
 
@@
     \inference{}
-              {\sOOhalt{o} \approx \sOOhalt{o}}
+              {\sOOhalt{o} \approx \sOOhalt{o}} \\
   \end{gather*} 
@@
   }
-  \\ \\
+  \\[1ex]
    %% This one is an obvious congruence rule. -Jeremy
@@
   }
-  \\ \\
+  \\[1ex]
   \inference{
@@
   }
-\\ \\
+\\[1ex]
 \inference{
-\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
-c_1' = seq(cast(T_3,l,T_1),c_1) \\
-c_2' = seq(c_2,cast(T_2,l,T_4))
-}{
+\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2}}{
 \hcvOOfun{c_1'}{\mathcal{E}}{x}{e}{c_2'}
@@
 }
-\\ \\
+\begin{array}{l}
+c_1' = seq(cast(T_3,l,T_1),c_1) \\
+c_2' = seq(c_2,cast(T_2,l,T_4))
+\end{array}
+\\[1ex]
   \inference{
@@
   }
-\\ \\
+\\[1ex]
   \inference{
-    \hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOprod{T_1}{T_2} \\
-    c_1' = seq(c_1,cast(T_1,l,T_3)) \\
-    c_2' = seq(c_2,cast(T_2,l,T_4))
+    \hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOprod{T_1}{T_2}
   }{
@@
   }
-\\ \\
+  \begin{array}{l}
+    c_1' = seq(c_1,cast(T_1,l,T_3)) \\
+    c_2' = seq(c_2,cast(T_2,l,T_4))
+  \end{array}
+\\[1ex]
   \inference{
@@
   }
-  \\
+  \\[1ex]
   \inference{
@@
 
-%\todo[inline]{Give the motivation for the following lemma. Where
-%  does it get used? As in, which case of which other lemma or theorem? -JS
-%\\---\\
-%Partially fixed. Will say in which cases after finishing the bisim proof. -KC}
-
-We use the following lemma in our bisimulation proof when cast applications 
-happen.
+The bisimulation relation for values is designed to make
+Lemma~\ref{thm:lem-apply-cast-SD} true, that is, if $v_1 \approx v_2$,
+then
+  \[
+  applyCast_{\text{\effCEK{C}}}(v_1,cast(T_1,l,T_2)) 
+  \approx 
+  applyCast_{\text{\ineffCEKD}}(v_2,\cOOcast{T_1}{l}{T_2})
+  \]
+So if two values of type $I$ are related, injecting them to $\TOOdyn$
+gives related values.
+%
+% The following is part of being a congruence. -JS
+%Unit values are of course related. 
+%
+To relate to a closure in \ineffCEKD, the closure in \effCEK{C} must
+have identities as its casts.
+%
+If a closure on the left is related to a value, we can apply
+equivalent casts on both sides to obtain related values.
+%
+The rules for products and sums are similar.
+%
+Lemma~\ref{thm:lem-apply-cast-SD} is used in our bisimulation proof to
+handle the transitions that apply casts to values.
 
@@
   \]
-  To put it another way, our goal is to proving 
+  To put it another way, our goal is to prove that 
   one reduction step in \effCEK{C} corresponds to
@@
   By looking at the definition of $v \approx v$, we know
-  \[ c_{11} = seq(seq(id(T_1),cast(T_1,l,T_3)) \dots) \]
-  \[ c_{12} = seq(seq(id(T_2),cast(T_2,l,T_4)) \dots) \] 
-  \[ v_2 = \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
+  \begin{align*}
+   c_{11} &= seq(seq(id(T_1),cast(T_1,l,T_3)) \dots) \\
+   c_{12} &= seq(seq(id(T_2),cast(T_2,l,T_4)) \dots) \\
+   v_2 &= \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
     \cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
-  \]
-  Thus we have the following reduction in \effCEK{C}. The equation 
-  reasoning employs the premise that $C$ is a monoid.
+  \end{align*}
+  Thus we have the following reduction in \effCEK{C}. Then we employ
+  equational reasoning that relies on the premise that $C$ is a
+  monoid.
   \[
@@
 
-And we have the following reduction in \ineffCEKD, where the last state is 
-related to the above \effCEK{C} state.
-
+We have the following corresponding reduction in \ineffCEKD, where the
+last state is related to the above \effCEK{C} state.
 \[
@@
 
-Other cases are similar. Of course, we need the lemma about $applyCast$ 
-(\ref{thm:lem-apply-cast-SD}) when cast applications happen in both machines. 
-And in case splitting, we employ $cast(T,l,T)=id(T)$ to relate the continuation 
-functions.
+Other cases are similar. Of course, we need the lemma about
+$applyCast$ (Lemma~\ref{thm:lem-apply-cast-SD}) when cast applications
+happen in both machines.  And in case splitting, we employ
+$cast(T,l,T)=id(T)$ to relate the continuation functions.
 \end{proof}

### 2019-10-27 paper.tex
Fill out author information and run spell-check.
Fixes in figure 1
Add environments to figure 2.
reuse environment definition in PL&LC
edits in section 2

@@
 %% For double-blind review submission, w/o CCS and ACM Reference (max
+
 %%submission space)
@@
 \newcommand{\secref}[1]{Section~\ref{#1}}
+\newcommand{\stxinrule}[3]{\text{#2} & #1 & \in & #3\\}
 \newcommand{\stxrule}[3]{\text{#2} & #1 & ::= & #3\\}
@@
 \author{Andre Kuhlenschmidt}
-\email{first2.last2@inst2a.com}         %% \email is recommended
+\email{akuhlens@iu.edu}         %% \email is recommended
 \affiliation{
-  \position{Position2b}
-  \department{Department2b}             %% \department is recommended
-  \institution{Institution2b}           %% \institution is required
-  \streetaddress{Street3b Address2b}
-  \city{City2b}
-  \state{State2b}
-  \postcode{Post-Code2b}
-  \country{Country2b}                   %% \country is recommended
-}
-\email{first2.last2@inst2b.org}         %% \email is recommended
+  %\position{Position2b}
+  \department{Computer Science Department}             %% \department is recommended
+  \institution{Indiana University}           %% \institution is required
+  %\streetaddress{Street3b Address2b}
+  %\city{City2b}
+  %\state{State2b}
+  %\postcode{Post-Code2b}
+  \country{United States}                   %% \country is recommended
+}
 
@@
   \begin{array}{lrcl}
-  \stxrule{T}{Types}{
+  \stxrule{T, S}{Types}{
     \star \mid{}
@@
   \inference{}{
-    \iota \sim \iota
+    \POOunit \sim \POOunit
   } \quad
@@
 %% transition rules starting from$Eval$states are standard.
-To apply a casted function, the machine first casts $v_1$, the
-operand, then applies the cast operand to $v_2$, the underlying
-function, and finally cast the return value.
+To apply a casted function, the machine first casts $v_1$, the operand, then
+applies $v_2$ (the underlying function) to the casted operand, and finally cast
+the return value.
 %
@@
   \begin{array}{lrcl}
+  \stxrule{\mathcal{E}}{Environments}{
+  	\text{a partial function}\;\{\langle x , v \rangle , \dots \}
+%  	\text{partial functions that map  variables to values}
+  }
   \stxrule{v}{Values}{
@@
   \inference{}{
-    \iota \smile \iota
+    \POOunit \smile \POOunit
   } \quad
@@
 
-  \caption{\textit{cast} and its auxilliary functions for Lazy UD.}
+  \caption{\textit{cast} and its auxiliary functions for Lazy UD.}
   \label{fig:HC-UD-cast}

### 2019-10-27 paper.tex
more edits section 2

@@
 %% transition rules starting from$Eval$states are standard.
-To apply a casted function, the machine first casts $v_1$, the operand, then
-applies $v_2$ (the underlying function) to the casted operand, and finally cast
-the return value.
+To apply a casted function, the machine first casts $v_1$ (the operand), then
+applies $v_2$ (the underlying function) to the casted operand, and then finally
+casts the return value.
 %
@@
 respect to \lazyD{} is in the definition of the $\mathit{applyCast}$
-function, in which a cast whose source or target is the unknown type
+function, in which a cast whose source or target is the dynamic type
 $\star$ is always split into two casts that go through an injectable
-type, that is, a type in which all sub-components are the unknown
+type, that is, a type in which all sub-components are the dynamic
 type, such as $\star \to \star$.

### 2019-10-27 paper.tex
Edits to section 3

@@
 In this section, we review the
-coercions~\citep{henglein1994dynamic,herman2010space} and the normal
-form of \citet{siek2012interpretations} to motivate the design of
-hypercoercions.  We omit sum types and product types in this section
-because \citet{siek2012interpretations} did not discuss them. We
-assume a basic familiarity with coercions and direct readers who are
-not familiar with them to \citet{siek2012interpretations} and
+coercions~\citep{henglein1994dynamic,herman2010space} and the normal form of
+\citet{siek2012interpretations} to motivate the design of hypercoercions.  We
+omit sum types and product types in this section because
+\citet{siek2012interpretations} did not discuss them. We assume a basic
+familiarity with coercions, and suggest that readers unfamiliar with coercions
+to familiarize themselves with \citet{siek2012interpretations} and
 \citet{siek2015blame}.
@@
 $I$ to type $\TOOdyn$. An injectable type is simply a type that can be
-cast directly to (injection) and from (projection) $\TOOdyn$. The
+cast directly to and from $\TOOdyn$. The
 definition of injectable types depends on the blame strategy. With \lazyD,
 all pre-types are injectable. With \lazyUD, only
-$\POOfun{\TOOdyn}{\TOOdyn}$ is injectable.
+$\POOfun{\TOOdyn}{\TOOdyn}$ and $\POOunit$ are injectable.
 %
@@
 
-\subsection{\lazyD{} hypercoercions}
+\subsection{\lazyD{} Hypercoercions}
 \label{sec:ld-hc}
@@
 
-\figref{fig:HC-D} defines the functions $id$, $seq$, and $cast$ that
-construct \lazyD{} hypercoercions, towards satisfying the Cast abstract data 
-type defined in Section~\ref{sec:framework}.
-\figref{fig:HC-D} also defines some auxiliary functions.
+\figref{fig:HC-D} defines the functions $id$, $seq$, and $cast$ that construct
+\lazyD{} hypercoercions. We use these functions to satisfy the Cast abstract
+data type defined in Section~\ref{sec:framework}. \figref{fig:HC-D} also defines
+some auxiliary functions.
 
@@
 
-\subsection{\lazyUD{} hypercoercions}
+\subsection{\lazyUD{} Hypercoercions}
 \label{sec:lud-hc}
@@
 $\mathit{castToDyn}$, $\mathit{castFromDyn}$, $\mathit{castToInj}$,
-and $\mathit{castFromInj}$, is to ensure that all of the are
+and $\mathit{castFromInj}$, is to ensure that each of them is
 structurally recursive, which makes them straightforward to define in
@@
   \end{itemize}
-  In the event that a program requires too many blame labels, then one
+  The bits for blame labels represent an index into a table of blame information.
+  In the event that a program requires too many blame labels, then the implementation
   can fallback to using the heap-allocated structure for more
@@
   \end{description}
-  We denote by $c : T_1 \Longrightarrow T_2$ to mean $c$ is in $Cast \; T_1 \; T_2$
+  We use the syntax $c : T_1 \Longrightarrow T_2$ to mean $c$ is in the set $Cast \; T_1 \; T_2$
   and we say ``$c$ is from $T_1$ to $T_2$''.

### 2019-10-27 paper.tex
add article to Cast ADT
Normalizing title case in section 4

@@
 
-\subsection{A Space-efficient CEK machine}
+\subsection{A Space-efficient CEK Machine}
 \label{sec:framework:cek}
@@
 %<<<<<<< HEAD
-\effCEK{C} is a space-efficient CEK machine parameterized over Cast ADT ($C$).  
+\effCEK{C} is a space-efficient CEK machine parameterized over the Cast ADT ($C$).  
 The key differences between \effCEK{C} and \ineffCEK\ are the places where 
@@
 
-\subsection{\effCEK{C} is equivalent to \ineffCEKD{}, provided $C$ is an instance of the Lazy D ADT}
+\subsection{\effCEK{C} Is Equivalent to \ineffCEKD{}, Provided $C$ Is an Instance of the Lazy D ADT}
 \label{secc:framework:monoid-correct}

### 2019-10-27 paper.tex
make paragraph flow more better

@@
 Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
-\ineffCEKD. The operators $id$ and $seq$ are the empty list and list appending 
-respectively. And $applyCast$ applies steps from left to right. Steps are 
-confined by its type rule such that its source and target are different. This 
-restriction is necessary to show $cast(T,l,T) = id(T)$.
+\ineffCEKD. The function $applyCast$ applies steps from left to right. Steps are 
+restricted by its typing rule such that its source and target are different. This 
+restriction is necessary to show $cast(T,l,T) = id(T)$. With this representation
+of casts, the operators $id$ and $seq$ are the empty list of steps and list
+append on casts respectively.
 

### 2019-10-27 paper.tex
Fixing grammar issues.
change eval

@@
 \newcommand{\effCEK}[1]{\ensuremath{\mathcal{S}(#1)}}
-\newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}
+\newcommand{\evalEqv}[2]{
+	\ensuremath{
+		eval_{\text{#1}}(e) = o
+		\;\text{if and only if}\;
+		eval_{\text{#2}}(e) = o}
+}
 \newcommand{\continue}[2]{cont(#2,#1)}
@@
   (11).
-  Part (2) is true because list is known to be a monoid.
+  Part (2) is true because lists are known to be a monoid with respect to append.
   Part (3) follows immediately from the definition of $cast(T,l,T)$
@@
   \label{lem:L-correct}
+  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
   \[
@@
   \[
-  \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
+  \evalEqv{\effCEK{C}}{\ineffCEKD}
+%  \judgeSeval{C}{e}{o}
+%  \;\text{if and only if}\;
+%  \judgeDeval{e}{o}
   \]
@@
 	Immediately from 
-	\evalEqv{\effCEK{C}}{\effCEK{L}} (Lemma~\ref{thm:surely-lazyD-eqv})
+	Equivalence of \lazyD{} Cast ADTs (Lemma~\ref{thm:surely-lazyD-eqv})
+%	\evalEqv{\effCEK{C}}{\effCEK{L}} (Lemma~\ref{thm:surely-lazyD-eqv})
 	and
-	\evalEqv{\effCEK{L}}{\ineffCEKD} (Lemma~\ref{lem:L-correct})
+	$L$ is Correct wrt. \ineffCEKD{} (Lemma~\ref{lem:L-correct})
+%	\evalEqv{\effCEK{L}}{\ineffCEKD} (Lemma~\ref{lem:L-correct})
 \end{proof}
@@
 that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
-is the failure.
+is the failure. The functions
 $ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
@@
 shallow-consistency to compare middles and values ($v \smile m$) in the 
-obvious way.
+obvious way. Likewise, $applyTail(v, t)$ interprets the tail to the appropriate
+cast of $v$.
 

### 2019-10-27 paper.tex
define env for S(C)
Further explain results the applyCast function.

--- 2019-10-27 paper.tex
@@
 \figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions.
-Applying the identity cast for the 
-dynamic type succeeds immediately. Otherwise, we firstly 
-apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
-that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
-is the failure.
-$ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
-In the definition of $applyMiddle(v,\ell,m)$, we generalize 
-shallow-consistency to compare middles and values ($v \smile m$) in the 
-obvious way.
+Applying the identity cast for the dynamic type succeeds immediately. If the
+value is injected and the cast is not the identity cast, then $applyCast$
+projects the value and relies on $applyMiddle$ to ensure that value is shallow
+consistent with target type of the head. Regardless of whether or not the value
+is projected, $applyCast$ applies the middle, then apply the tail if the middle
+succeeds. We denote by $r \; >>= \; f$ to mean that if $r$ is $\rOOsucc{v}$, the
+result is $f(v)$, otherwise, the result is the failure. In the definition of
+$applyMiddle(v,\ell,m)$, we generalize shallow-consistency to compare middles
+and values ($v \smile m$) in the obvious way. When a value is shallowly
+inconsistent from the middle, it is the result of projecting a value that was
+shallowly inconsistent with the expected type of the projection in the head. Thus, a
+blame label $l$ must have been pass in as $\ell$ and is to blame. Finally if a
+failure in $applyMiddle$ has not occurred then $applyTail(v, t)$ interprets the
+tail, $t$, to the appropriate cast of the value $v$.
 
@@
 %% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
+% \appendix
+% \section{Appendix}
+
+% Text of appendix \ldots
 

### 2019-10-27 paper.tex
missing comma
minor edits

@@
 }
+\stxrule{\mathcal{E}}{Environments}{
+	\text{a partial function}\;\{\langle x , v \rangle , \dots \}
+}
+
   \end{array}
@@
 
-Cast results ($r$) are the same as for \ineffCEK. 
+Cast results ($r$) and environments ($\mathcal{E}$) are the same as for 
+\ineffCEK. 
 Value typing ($\judgeType{v}{T}$) is defined in the obvious way.
@@
 
-%<<<<<<< HEAD
 \effCEK{C} is a space-efficient CEK machine parameterized over the Cast ADT ($C$).  
 The key differences between \effCEK{C} and \ineffCEK\ are the places where 
-casts can accumulate at runtime, that is, values and continuations. We discuss 
-above the difference in values (Definition~\ref{def:values-effCEK}).
+casts can accumulate at runtime, that is, values and continuations.
+The differences regarding values was discussed 
+above (Definition~\ref{def:values-effCEK}).
+We define contiuations below, with $\kappa$ ranging over continuations
+and $k$ ranging over pre-continuations.
+%
+Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
+constructor for casts.
+%
+A continuation is now a pre-continuation prefixed with a cast.
 
@@
 \label{def:values-effCEK}
-%=======
-%\begin{figure}
-%%  Syntax
-%>>>>>>> bd39888b0287dbef61e981bd0e79bc8822fc85ce
   \[
   \begin{array}{lrcl}
-% \stxrule{r}{cast results}{
-%   \rOOsucc{v} \mid
-%   \rOOfail{l}
-% }
-% \stxrule{s}{states}{
-%   \sOOinspect{e}{\mathcal{E}}{\kappa} \mid{}
-%   \sOOreturn{v}{\kappa} \mid{}
-%   \sOOhalt{o}
-% }
   \stxrule{\kappa}{Continuation}{
@@
 
-Let $\kappa$ range over continuations and let $k$ range over
-pre-continuations.
-%
-Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
-constructor for casts.
-%
-A continuation is now a pre-continuation prefixed with a cast.
-%
 Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
@@
 %
-The relation is mutually defined on continuations, written $\kappa
+One nice aspect of using abstract machines for this proof is that
+the expressions in the machine are simply related by syntactic equality.
+%
+The bisimulation relation is mutually defined on continuations, written $\kappa
 \approx \kappa : T$, where $T$ is their source type, and values, written $v 
@@
 continuations. This takes care of the difference between
-the transition rules for $e \langle T_1 \Rightarrow^l T_2$
+the transition rules for $e \langle T_1 \Rightarrow^l T_2 \rangle$
 on the two machines.
@@
 
-%Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
-%introduce one more definition. $s_1 \approx^{*} s_2$ means we will get $s_1 
-%\approx s_2$ after more transition steps in \ineffCEKD.
-%
-%\begin{definition}[$s \approx^{*} s$]
-%Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
-%if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
-%that
-%\[
-%\judgeDreduceTrans{s_2}{s_2'}
-%\;\text{and}\;
-%s_1 \approx s_2'
-%\]
-%\end{definition}
-%
-%%\todo[inline]{Explain that this is an unusual formulation of a weak
-%%  bisimulation.  We promise it will all be OK regarding how it is used
-%%  in the correctness proof for S(C). -JS}
-%
-%The lemma below formulate the weak bisimulation between \effCEK{C} and 
-%\ineffCEKD. It is unusual because we use $s \approx s$ in premise while $s 
-%\approx^{*} s$ in conclusion. As we will show in the correctness proof for 
-%\effCEK{C}, however, this formulation is fine for our purpose.
-
-\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
+We now come to the main lemma, the weak bisimulation between
+\effCEK{C} and \ineffCEKD{}.
+
+\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}]
   \label{thm:SD-bisim}
@@
   Suppose $C$ is an instance of the Cast ADT
-  and the \lazyD{} ADT, $C$ is a monoid
+  and the \lazyD{} ADT, $C$ is a monoid,
   and $cast(T,l,T)=id(T)$.
@@
 \begin{proof}
-  Without lose of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
+  Without loss of generality, assume $\judgeSreduce{C_1}{e}{o}$ and prove 
   $\judgeSreduce{C_2}{e}{o}$.\\
@@
 restriction is necessary to show $cast(T,l,T) = id(T)$. With this representation
-of casts, the operators $id$ and $seq$ are the empty list of steps and list
-append on casts respectively.
+of casts, the operator $id$ produces an empty list of steps
+and $seq$ appends two lists of steps.
 
@@
   \funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
-  \funrule{applyMiddle(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
+  \funrule{applyMiddle(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2},\ell,\POOfun{c_3}{c_4})}{
     \rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\mathcal{E}}{x}{e}{(c_2 
@@
 \effCEK{C}, and a theorem which states that \effCEK{C} is equivalent
-to $D$ when $C$ is a Lazy D Cast ADT.
+to $\ineffCEKD{}$ when $C$ is a Lazy D Cast ADT.
 %

### 2019-10-27 paper.tex
remove anonymous, line break in title

@@
 %%submission space)
-\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 %% For double-blind review submission, w/ CCS and ACM Reference
@@
 %% Title information
-\title{Hypercoercions and a Framework for Equivalence of Cast Calculi}
+\title{Hypercoercions and a Framework for \\ Equivalence of Cast Calculi}
 

### 2019-12-02 paper.tex
prove theorems in Agda
fix typos

@@
 \highlight{\text{where}\;
+\kappa\;\text{is waiting for a value of type}\;T
+}
+\\&&
+\highlight{\text{and}\;
 	v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
@@
 \sOOreturn{v}{\kOOmt}}{
-\sOOhalt{observe(v}}{}
+\sOOhalt{observe(v)}}{}
   \end{array}
@@
   c &\fatsemi& \hyperCoercionI{} &=& c\\
-  \hyperCoercionI{} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
-       \hyperCoercionC{p_2}{m_2}{i_2} \\
-  \hyperCoercionC{p_1}{m_1}{\epsilon} &\fatsemi& \hyperCoercionC{\epsilon}{m_2}{i_2} &=&
-       \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} \\
-  \hyperCoercionC{p_1}{m_1}{!} &\fatsemi& \hyperCoercionC{?^l}{m_2}{i_2} &=&
+  \hyperCoercionI{} &\fatsemi& \hyperCoercionC{h_2}{m_2}{t_2} &=&
+       \hyperCoercionC{h_2}{m_2}{t_2} \\
+  \hyperCoercionC{h_1}{m_1}{\epsilon} &\fatsemi& 
+  \hyperCoercionC{\epsilon}{m_2}{t_2} &=&
+       \hyperCoercionC{h_1}{m_1 \fatsemi m_2}{t_2} \\
+  \hyperCoercionC{h_1}{m_1}{!} &\fatsemi& \hyperCoercionC{?^l}{m_2}{t_2} &=&
   \begin{cases}
-    \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} & \text{if } m_1 \smile m_2 \\
-    \hyperCoercionC{p_1}{m_1}{\bot^l} & \text{otherwise}
+    \hyperCoercionC{h_1}{m_1 \fatsemi m_2}{t_2} & \text{if } m_1 \smile m_2 \\
+    \hyperCoercionC{h_1}{m_1}{\bot^l} & \text{otherwise}
   \end{cases} \\
-  \hyperCoercionC{p_1}{m_1}{\bot^l} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
-     \hyperCoercionC{p_1}{m_1}{\bot^l}
+  \hyperCoercionC{h_1}{m_1}{\bot^l} &\fatsemi& \hyperCoercionC{h_2}{m_2}{t_2} 
+  &=&
+     \hyperCoercionC{h_1}{m_1}{\bot^l}
   \end{array}
@@
 presentations of this function do not use auxiliary functions, as we
-do here. The reason that we introduction the auxiliary functions
+do here. The reason that we introduce the auxiliary functions
 $\mathit{castToDyn}$, $\mathit{castFromDyn}$, $\mathit{castToInj}$,
@@
 \begin{proof}
-  Part (1) follows from the definition of $s \approx s$.
-  Part (2) and (3) are more interesting. 
+  Part (3) follows from the definition of $s \approx s$.
+  Part (1) and (2) are more interesting. 
   By the definition of $s \approx s$, it is straightforward to prove 
   $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
-  So we can prove two parts together by showing that 
-  \[
-  \text{if}\; s_{1} \approx s_{2}
-  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
-  \;\text{and}\;\judgeDreduce{s_2}{s_4}
-  \;\text{then}\; s_3 \approx^{*} s_4.
+  So we can prove two parts together by showing that if $s_{1} \approx s_{2}$
+  and $\judgeDreduce{s_2}{s_4}$ then
+  \[
+%  \text{if}\; 
+%  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
+%  \;\text{and}\;\judgeDreduce{s_2}{s_4}
+  \;\text{there exists}\; s'
+  \;\text{such that}\; \judgeDreduceTrans{s_4}{s'}
+  \;\text{and}\; s_3 \approx s'.
   \]
@@
 
-\subsubsection{\effCEK{C_1} and \effCEK{C_2} are equivalence if $C_1$ and $C_2$ are Lazy D}
+\subsubsection{\effCEK{C_1} and \effCEK{C_2} are equivalent if $C_1$ and $C_2$ 
+are Lazy D}
 
@@
   Immediately from
-  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
+  Correctness of \effCEK{C} (Corollary~\ref{thm:SD-equiv}) and 
   Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).

### 2019-12-02 paper.tex
fix typos

@@
 restrict the casts in casted values. If the cast is between pre-types, source 
-and target types must have the same type constructor at the top ($P_1 \approx 
+and target types must have the same type constructor at the top ($P_1 \smile 
 P_2$). If the cast is from a pre-type to the dynamic type, the pre-type must be 
@@
 
-We then apply this framework to \lazyD{} hypercoercions
+We then apply this framework to \lazyD{} hypercoercions $H$
 (Section~\ref{sec:hypercoercion-correctness}), where we show that $H$
@@
 \begin{definition}[Continuations for the \effCEK{C} machine] 
-\label{def:values-effCEK}
+\label{def:conts-effCEK}
   \[

### 2019-12-26 paper.tex
fix more typos
revised, following suggestions from the WGT reviewers

@@
 %\newtheorem{definition}{Definition}
+
+\newcommand{\mbind}{\ensuremath{\underline{\gg}}}
 
@@
 dynamic typing and static typing, notably gradual typing
-\citep{siek2006gradual}, hybrid typing \citep{flanagan2006hybrid},
+\citep{siek2006gradual}, hybrid typing \citep{knowles2010hybrid},
 migratory typing \citep{Tobin-Hochstadt:2006fk}, and multi-language
@@
 representations, with various strengths and weaknesses
-\citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}.
+\citep{Siek:2015:BCT:2737924.2737968,Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}.
 The current state of the art includes
@@
 \begin{itemize}
-\item threesomes \citep{siek2010threesomes,garcia2013calculating},
-\item supercoercions \citep{garcia2013calculating}, and
+\item threesomes 
+\citep{Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603},
+\item supercoercions \citep{Garcia:2013:CTB:2500365.2500603}, and
 \item coercions in normal form
-  \citep{siek2012interpretations,siek2015blame}.
+  \citep{siek2012interpretations,Siek:2015:BCT:2737924.2737968}.
 \end{itemize}
@@
 safe cast compared to UD~\citep{siek2009exploring}, which is why D was
-chosen in Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
+chosen in the Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
 interested in UD because it plays a
@@
 \citep{wadler2009well}.  The UD hypercoercions were inspired by the
-supercoercions of \citet{garcia2013calculating} (hence the name) and
+supercoercions of \citet{Garcia:2013:CTB:2500365.2500603} (hence the name) and
 the D hypercoercions were inspired by the normal forms of
@@
     \eOOinl{T}{T}{e} \mid
-    \eOOinl{T}{T}{e} \mid
+    \eOOinr{T}{T}{e} \mid
     \eOOcase{e}{e}{e} \mid
@@
 $\eOOcast{e}{T_1}{l}{T_2}$, which are responsible for runtime type
-checking, and blame expressions, $\eOOblame{l}$, that raise errors.
-The syntax and static semantics is the same that of
+checking, and blame expressions, $\eOOblame{l}$, that raise errors. Polarities 
+of blame labels is not treated but are straightforward to incorporate. 
+The syntax and static semantics is the same as that of
 \citet{siek2009exploring} except for a few minor exceptions:
@@
           \POOprod{T_3}{T_4}}}
-    }{\mathtt{fst} \; \kappa}
+    }{\kOOcar{\kappa}}
   }{
@@
           \POOprod{T_3}{T_4}}}
-    }{\mathtt{snd} \; \kappa}
+    }{\kOOcdr{\kappa}}
   }{
@@
 \sOOreturn{v_3}{
-  \kOOcaseIII{\vOOinl{v}}{v_2}{\kappa}
+  \kOOcaseIII{(\vOOinl{v})}{v_2}{\kappa}
 }
@@
   \sOOreturn{v_3}{
-    \kOOcaseIII{\vOOinr{v}}{v_2}{\kappa}
+    \kOOcaseIII{(\vOOinr{v})}{v_2}{\kappa}
   }
@@
 \highlight{\text{where}\;
-\kappa\;\text{is waiting for a value of type}\;T
+	\kappa:T
+%\kappa\;\text{is waiting for a value of type}\;T
 }
@@
 \highlight{\text{and}\;
-	v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
+v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
 \\&&
 \highlight{\text{and}\;
-v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
+v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
 }
@@
 to familiarize themselves with \citet{siek2012interpretations} and
-\citet{siek2015blame}.
+\citet{Siek:2015:BCT:2737924.2737968}.
 
@@
       \; \text{and} \;
-      \forall l. t \neq \bot^{l}
+      \forall l. t_1 \neq \bot^{l}
     }
@@
   \; \text{and} \;
-  \forall l. t \neq \bot^{l}
+  \forall l. t_1 \neq \bot^{l}
 }
@@
     then $applyCast(v,seq(c_1,c_2)) = 
-    applyCast(v,c_1) >>= \lambda v'.applyCast(v',c_2)$\\
+    applyCast(v,c_1) \mbind{} \lambda v'.applyCast(v',c_2)$\\
     where 
@@
     \begin{array}{rcl}
-      \rOOsucc{v} >>= f & = & f(v) \\
-      \rOOfail{l} >>= f & = & \rOOfail{l}
+      \rOOsucc{v} \mbind{} f & = & f(v) \\
+      \rOOfail{l} \mbind{} f & = & \rOOfail{l}
     \end{array}
@@
     = 
-    \rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\mathcal{E}}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$
+    \rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\mathcal{E}}{x}{e}{seq(c_2,cast(T_2,l,T_4))})}$
   \item If $(\hcvOOcons{v_1}{c_1}{v_2}{c_2}) : \POOprod{T_1}{T_2}$,
@@
   \redruleS{
-    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
+    \sOOinspect{\eOOinr{T_1}{T_2}{e}}{\mathcal{E}}{\kappa}
   }{
@@
   Apply continuation
-  \fbox{$\continue{k}{v} = s$}
+  \fbox{$\continue{v}{k} = s$}
   \[
@@
 }{
-  \sOOreturn{v_1}{ext(c_1,k)}
+  \sOOreturn{v_1}{ext(c_1,\kappa)}
 }{}
@@
 }{
-  \sOOreturn{v_2}{ext(c_2,k)}
+  \sOOreturn{v_2}{ext(c_2,\kappa)}
 }{}
@@
   \inference{
-    \mathcal{E}_1 \approx \mathcal{E}_2 &
-    dom(\mathcal{E}_1) = dom(\mathcal{E}_2) = \Gamma \\
   	\Gamma , x : T_1 \vdash e : T_2
+  	\\
+  	\forall{} x \in dom(\Gamma).\;
+  		\mathcal{E}_1(x) \approx \mathcal{E}_2(x) : \Gamma(x)
   }{
@@
 }{
-  applyStep(v,s) >>= \lambda v. applyCast(v,c)
+  applyStep(v,s) \mbind{} \lambda v. applyCast(v,c)
 }{}
@@
 is projected, $applyCast$ applies the middle, then apply the tail if the middle
-succeeds. We denote by $r \; >>= \; f$ to mean that if $r$ is $\rOOsucc{v}$, the
+succeeds. We denote by $r \; \mbind{} \; f$ to mean that if $r$ is 
+$\rOOsucc{v}$, the
 result is $f(v)$, otherwise, the result is the failure. In the definition of
@@
   \funrule{applyCast(\hcvOOinj{P}{v},\hyperCoercionC{?^l}{m}{t})}{
-    applyMiddle(v,l,m) \; >>= \; \lambda v. applyTail(t,v)
+    applyMiddle(v,l,m) \; \mbind{} \; \lambda v. applyTail(t,v)
   }{}
   \funrule{applyCast(v,\hyperCoercionC{\epsilon}{m}{t})}{
-    applyMiddle(v,\epsilon,m) \; >>= \; \lambda v. applyTail(t,v)
+    applyMiddle(v,\epsilon,m) \; \mbind{} \; \lambda v. applyTail(t,v)
   }{}

### 2019-12-29 paper.tex
replace observation with observable to follow the convention in Jeremy 2012

@@
 
-\newcommand{\mbind}{\ensuremath{\underline{\gg}}}
+\newcommand{\mbind}{\ensuremath{\;\underline{\gg}\;}}
 
@@
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
-machine halts with an observation ($o$). Observations include all value 
+machine halts with an observable ($o$). Observables include all value 
 constructors and blame. The function converting values to 
-observations ($observe(v) = o$) is defined in the obvious way.
-%Let $s$ range over machine states. A state is either looking at an 
-%expression to decide what to do next, returning a value to a continuation, or 
-%halting with an observation.
+observables ($observe(v) = o$) is defined in the obvious way.
 
@@
   }
-  \stxrule{o}{Observations}{
+  \stxrule{o}{Observables}{
     \oOOinj \mid
@@
 
-%% Three observations on this definition leads to hypercoercion: 
+%% Three observables on this definition leads to hypercoercion: 
 %% \begin{enumerate}
@@
 hypercoercions.  The design of hypercoercions is motivated by the
-observation that a normal coercion has at most three
+observable that a normal coercion has at most three
 parts. Hypercoercions make this structure explicit: a hypercoercion $c$ is
@@
   \label{thm:surely-lazyD-eqv}
-  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
-  \[
-  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
-  \]
+  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT. If 
+  $\judgetype{\emptyset}{e}{T}$ and $o : T$ then
+  \[
+  \evalEqv{\effCEK{C_1}}{\effCEK{C_2}}
+  \]
+%  \[
+%  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
+%  \]
 \end{proposition}
 \begin{proof}
-  Without loss of generality, assume $\judgeSreduce{C_1}{e}{o}$ and prove 
-  $\judgeSreduce{C_2}{e}{o}$.\\
+  Without loss of generality, assume $\judgeSeval{C_1}{e}{o}$ and prove 
+  $\judgeSeval{C_2}{e}{o}$.\\
   By the definition of $eval_{\mathcal{S}(C)}$, we know 
 \[
-\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
+\judgeSreduceTrans{C_1}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
 \]
@@
 \]
-  that is, $\judgeSreduce{C_2}{e}{o}$
+  that is, $\judgeSeval{C_2}{e}{o}$
 \end{proof}
@@
   Suppose $C$ is a \lazyD{} Cast ADT.  If
-  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
+  $\judgetype{\emptyset}{e}{T}$ and $o : T$ then
   \[
   \evalEqv{\effCEK{C}}{\ineffCEKD}
-%  \judgeSeval{C}{e}{o}
-%  \;\text{if and only if}\;
-%  \judgeDeval{e}{o}
   \]

### 2019-12-29 paper.tex
review according to most reviews

@@
 \newcommand{\cOOcast}[3]{#1 \Rightarrow^{#2} #3}
-\newcommand{\oOOinj}{\mathtt{dyn}}
+\newcommand{\oOOdyn}{\mathtt{dyn}}
 \newcommand{\oOOsole}{\mathtt{unit}}
@@
 tracking strategies from the literature: D and
-UD~\citep{siek2009exploring}. We are interested in the D blame
+UD~\citep{siek2009exploring}. With the D strategy, only \textbf{d}own casts 
+(casts from $\TOOdyn$ to some other types) are subject to blame. With the UD 
+strategy, however, some \textbf{u}p casts are also blamable.
+We are interested in the D blame
 tracking strategy because it comes with a more straightforward notion of
@@
 machine halts with an observable ($o$). Observables include all value 
-constructors and blame. The function converting values to 
-observables ($observe(v) = o$) is defined in the obvious way.
+constructors, blame, and $\oOOdyn$, as in \citet{siek2012interpretations}. 
+The function converting values to observables ($observe(v) = o$) is defined in 
+the obvious way.
 
@@
   \stxrule{o}{Observables}{
-    \oOOinj \mid
+    \oOOdyn \mid
     \oOOsole \mid
@@
 hypercoercions.  The design of hypercoercions is motivated by the
-observable that a normal coercion has at most three
+observation that a normal coercion has at most three
 parts. Hypercoercions make this structure explicit: a hypercoercion $c$ is

### 2019-12-29 paper.tex
sync

@@
 \item hypercoercions, a new cast representation, which
-  has a structurally recursive composition and a more compact memory
-  representation.
+  has a structurally recursive composition and a memory
+  representation more compact than space-efficient coercions.
 \item a framework in Agda for proving the correctness of \lazyD{} cast

### 2020-01-03 paper.tex
rewrote weak-bisim-between-S(C)-and-D and Correctness-of-S(C)

--- 2019-12-29 paper.tex
@@
 %\newtheorem{definition}{Definition}
+
+\newcommand{\longdownmapsto}{\rotatebox[origin=c]{-90}{$\scriptstyle\longmapsto$}\mkern2mu}
 
@@
 \newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
+\newcommand{\judgeSreducePlus}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{+} #3}
 \newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
@@
 Corresponding to (1) and (2), the machine state is either in an evaluating
-$\sOOinspect{e}{\mathcal{E}}{\kappa}$ or continuing $\sOOreturn{v}{\kappa}$ configuration, 
+$\sOOinspect{e}{\mathcal{E}}{\kappa}$ or continuing $\sOOreturn{v}{\kappa}$ 
+configuration, 
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
-machine halts with an observable ($o$). Observables include all value 
+machine halts with an observation ($o$). Observations include all value 
 constructors and blame. The function converting values to 
-observables ($observe(v) = o$) is defined in the obvious way.
+observations ($observe(v) = o$) is defined in the obvious way.
+%Let $s$ range over machine states. A state is either looking at an 
+%expression to decide what to do next, returning a value to a continuation, or 
+%halting with an observation.
 
@@
   }
-  \stxrule{o}{Observables}{
+  \stxrule{o}{Observations}{
     \oOOinj \mid
@@
   \\
-  \sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
+  \sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
 \end{cases}}
@@
 of \citet{siek2009exploring}.
+
+\begin{proposition}[\ineffCEKD{} is deterministic]
+	If $\judgeDreduce{s_1}{s_2}$ and $\judgeDreduce{s_1}{s_3}$ then $s_2 = s_3$.
+\end{proposition}
 
@@
 
+\begin{proposition}[\ineffCEKUD{} is deterministic]
+	If $\judgeDreduce{s_1}{s_2}$ and $\judgeUDreduce{s_1}{s_3}$ then $s_2 = 
+	s_3$.
+\end{proposition}
+
 \subsection{Coercions and Normal Forms} 
@@
 
-%% Three observables on this definition leads to hypercoercion: 
+%% Three observations on this definition leads to hypercoercion: 
 %% \begin{enumerate}
@@
 \begin{definition}[Lazy D Cast ADT]
-  \label{def:surely-lazyd}
+  \label{def:Lazy-D-Cast-ADT}
   A  Cast is a Lazy D Cast if:
@@
   \funrule{wrap(k)}{\kOOcast{id(T_1)}{k}}{
-    \sidecond{k : T_1 \Longrightarrow T_2}}
+  	\text{where } k : T_1 \Longrightarrow T_2}
   \end{array}
@@
   \\
-  \sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
+  \sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
   \end{cases}
@@
 evaluation ($\judgeSeval{C}{e}{o}$) are the same as for \ineffCEK.
+
+\begin{proposition}[\effCEK{C} is deterministic]
+	\label{prp:SC-deterministic}
+	If $\judgeSreduce{C}{s_1}{s_2}$ and $\judgeSreduce{C}{s_1}{s_3}$ 
+	then $s_2 = s_3$.
+\end{proposition}
 
@@
 \begin{definition}[Monoid]
+	\label{def:monoid}
   A Cast ADT is a monoid if 
@@
 % \[\dots\]
+
+\fbox{$\Gamma \vdash \mathcal{E} \approx \mathcal{E}$}
+\begin{gather*}
+\inference{
+}{
+	\emptyset \vdash \emptyset \approx \emptyset
+}
+\quad
+\inference{
+	\Gamma \vdash \mathcal{E}_1 \approx \mathcal{E}_2 \\
+	v_1 \approx v_2 : T
+}{
+	\Gamma , x : T \vdash 
+		\mathcal{E}_1 [ x := v_1 ] \approx \mathcal{E}_2 [ x := v_2 ]
+}
+\end{gather*}
+
   \fbox{$s \approx s$}
@@
   \begin{gather*}
-    \inference{dom(\mathcal{E}_1) = dom(\mathcal{E}_2) \\
-               \forall x {:} T \in dom(\mathcal{E}_1),\,
-                   \mathcal{E}_1(x) \approx \mathcal{E}_2(x) : T\\
-               \kappa_1 \approx \kappa_2 : T}
-              {\langle e, \mathcal{E}_1, \kappa_1 \rangle \approx
-              \langle e, \mathcal{E}_2, \kappa_2 \rangle}
-    %% \quad
-    %% \inference{v_1 \approx v_2 : T \quad \kappa_1 \approx \kappa_2 : T}
-    %%           {\langle v_1, \kappa_1 \rangle  \approx
-    %%           \langle v_2, \kappa_2 \rangle}
+    \inference{
+    	\judgetype{\Gamma}{e}{T} \\
+    	\Gamma \vdash \mathcal{E}_1 \approx \mathcal{E}_2 \\
+   		\kappa_1 \approx \kappa_2 : T
+   	}{
+   		\langle e, \mathcal{E}_1, \kappa_1 \rangle 
+   		\approx
+		\langle e, \mathcal{E}_2, \kappa_2 \rangle
+	}
+%    \quad
+%    \inference{v_1 \approx v_2 : T \quad \kappa_1 \approx \kappa_2 : T}
+%               {\langle v_1, \kappa_1 \rangle  \approx
+%               \langle v_2, \kappa_2 \rangle}
     \quad
@@
   	\\
-  	\forall{} x \in dom(\Gamma).\;
-  		\mathcal{E}_1(x) \approx \mathcal{E}_2(x) : \Gamma(x)
+  	\Gamma \vdash \mathcal{E}_1 \approx \mathcal{E}_2
   }{
@@
 The bisimulation relation for values is designed to make
-Lemma~\ref{thm:lem-apply-cast-SD} true, that is, if $v_1 \approx v_2$,
+Lemma~\ref{lem:lem-apply-cast-preserve-bisim} true, that is, if $v_1 \approx 
+v_2$,
 then
@@
 %
-Lemma~\ref{thm:lem-apply-cast-SD} is used in our bisimulation proof to
+Lemma~\ref{lem:lem-apply-cast-preserve-bisim} is used in our bisimulation proof 
+to
 handle the transitions that apply casts to values.
@@
 \begin{lemma}[$applyCast$ Preserves Bisimulation]
-  \label{thm:lem-apply-cast-SD}
+  \label{lem:lem-apply-cast-preserve-bisim}
   Assume $C$ implements Lazy D Cast ADT,
@@
 \begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}]
-  \label{thm:SD-bisim}
-  Assume $C$ implements Lazy D Cast ADT
+	\label{lem:weak-bisim-SC-D}
+	If $C$ implements Lazy D Cast ADT
 	and $C$ is a monoid
-  and $cast(T,l,T)=id(T)$,
-  $s_{1} \in \text{\effCEK{C}}$,
-  $s_{2} \in \text{\ineffCEKD}$,
-  $s_{1} \approx s_{2}$,
+	and $cast(T,l,T)=id(T)$
+	and $s_{1} \approx s_{2}$
+	then either
 \begin{enumerate}
-	\item If $\judgeSreduce{C}{s_1}{s_3}$ then
-	$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
-	\item If $\judgeDreduce{s_2}{s_4}$ then
-	$\judgeSreduceTrans{C}{s_1}{s_3}$,
-	$\judgeDreduceTrans{s_4}{s_5}$, and
-	$s_3 \approx s_5$ for some $s_3$ and $s_5$.
-	\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+	\item $s_1 = \sOOhalt{o}$ and $s_2 = \sOOhalt{o}$ for some $o$, or
+	\item $\judgeSreducePlus{C}{s_1}{s_3}$ 
+		and $\judgeDreducePlus{s_2}{s_4}$
+		and $s_3 \approx s_4$ for some $s_3$ and $s_4$
 \end{enumerate}
+\end{lemma}
+\begin{proof}
+	We proceed by case analysis on $s_1 \approx s_2$. 
+	\begin{description}
+		\item[Case $\inference{}{\sOOhalt{o} \approx \sOOhalt{o}}$]
+		This is case (1).\\ \\
+		\item[Case $\inference{
+			\judgetype{\Gamma}{e}{T} \\
+			\Gamma \vdash \mathcal{E} \approx \mathcal{E}' \\
+			\kappa \approx \kappa' : T
+		}{
+			\langle e, \mathcal{E}, \kappa \rangle 
+			\approx
+			\langle e, \mathcal{E}', \kappa' \rangle
+		}$]
+		This is case (2). By case analysis on $e$.\\ \\
+		\item[Case $\inference{v \approx v' : T\\ \kappa \approx 
+		\kappa' : T}{\sOOreturn{v}{\kappa} \approx 
+		\sOOreturn{v'}{\kappa'}}$] This is case (2). In this case we have the 
+		following reduction in \effCEK{C}.
+\[\begin{array}{rll}
+\sOOreturn{v}{\kappa} &=& \sOOreturn{v}{\kOOcast{c}{k}}\\
+& \longmapsto_{\effCEK{C}} & \begin{cases}
+\continue{k}{v_1} & \sidecond{applyCast(v,c) = \rOOsucc{v_1}} 
+\\
+\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = 			
+	\rOOfail{l}}
+\end{cases}
+\end{array}\]
+
+	We proceed by induction on 
+		$\kOOcast{c}{k} \approx \kappa' : T$. \\
+		\begin{description}
+		\item[Subcase $\inference{
+			k \approx \kappa' : T
+		}{
+			\kOOcast{id(T)}{k} \approx \kappa'
+		}$] 
+		In this case, from the property (1) of Lazy D Cast ADT 
+		(Definition~\ref{def:Lazy-D-Cast-ADT})
+		\[applyCast(v,c) = applyCast(v,id(T)) = \rOOsucc{v}\]
+		Thus,
+		\[
+		\sOOreturn{v}{\kappa} = \sOOreturn{v}{\kOOcast{id(T)}{k}}
+		\longmapsto_{\effCEK{C}} \continue{k}{v}
+		\]
+		We will show shortly that if $v \approx v' : T$ and 
+		$k \approx \kappa' : T$ then there exists an $s'$ such that
+		$\continue{k}{v} \approx s'$ and
+		$\sOOreturn{v'}{\kappa'} \longmapsto_{\ineffCEKD} s'$.
+		\\
+		\item[Subcase $\inference{
+			\kOOcast{c_1}{k_1} \approx \kappa_1' : T_2
+		}{
+			\kOOcast{seq(cast(T_1,l,T_2),c_1)}{k_1} \approx 
+			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_1'}
+		}$]
+In this case, from the property~(2) of Lazy D Cast ADT 
+(Definition~\ref{def:Lazy-D-Cast-ADT})
+\[
+\begin{array}{rcl}
+applyCast(v,c) 
+	&=& applyCast(v,seq(cast(T_1,l,T_2),c_1)) \\
+	&=& applyCast(v,cast(T_1,l,T_2)) \mbind{} \lambda v. applyCast(v,c_1)
+\end{array}
+\]
+In the \ineffCEKD{} machine, we have the following reduction,
+\[
+\sOOreturn{v'}{k'} 
+=
+\sOOreturn{v'}{\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_1'}} 
+\longmapsto_{\ineffCEKD} 
+\begin{cases}
+	\sOOreturn{v_1'}{\kappa_1'} 
+		& \sidecond{applyCast(v',\cOOcast{T_1}{l}{T_2}) = \rOOsucc{v_1'}}
+	\\
+	\sOOhalt{(\oOOblame{l})} 
+		& \sidecond{applyCast(v',\cOOcast{T_1}{l}{T_2}) = \rOOfail{l}}
+\end{cases}
+\]
+
+By Lemma~\ref{lem:lem-apply-cast-preserve-bisim}, 
+$applyCast(v,cast(T_1,l,T_2)) \approx applyCast(v',\cOOcast{T_1}{l}{T_2})$.
+When both cast applications fail, both machines transition to halting states 
+with the same blame label.
+When both cast applications succeed, we apply the induction hypothesis.
+\end{description}
+\end{description}
+
+Now we prove the missing part: if $v \approx v' : T$ and 
+$k \approx \kappa' : T$ then there exists an $s'$ such that
+$\continue{k}{v} \approx s'$ and $\sOOreturn{v'}{\kappa'} 
+\longmapsto_{\ineffCEKD} s'$. We proceed by case analysis on $k \approx \kappa' 
+: T$.
+
+Many cases are trivial. The interesting cases are eliminations 
+(e.g. function applications, pair projections). Due to space limitation, 
+we only illustrate the general idea with function applications:
+\[\inference{
+	v_1 \approx v_1' : \POOfun{T_1}{T_2} \\
+	\kappa_1 \approx \kappa_1' : T_2
+}{
+	\kOOappII{v_1}{\kappa_1} \approx \kOOappII{v_1'}{\kappa_1'}
+}\]
+
+We proceed by induction on the $v_1 \approx v_1' : \POOfun{T_1}{T_2}$.
+
+\begin{description}
+	\item[Case $\inference{
+		\Gamma , x : T_1 \vdash e : T_2
+		\\
+		\Gamma \vdash \mathcal{E} \approx \mathcal{E}'
+	}{
+		\hcvOOfun{id(T_1)}{\mathcal{E}}{x}{e}{id(T_2)}
+		\approx
+		\vOOfun{\mathcal{E}'}{x}{e}
+		: \POOfun{T_1}{T_2}
+	}$]
+\[
+\begin{array}{rcl}
+\continue{k}{v}
+	&=
+	&\continue{\kOOappII{\hcvOOfun{id(T_1)}{\mathcal{E}}{x}{e}{id(T_2)}}{\kappa_1}}{v}
+	\\
+	&=
+	&\sOOinspect{e}{\mathcal{E}[x:=v]}{ext(id(T_2),\kappa_1)}
+	\\
+	&=
+	&\sOOinspect{e}{\mathcal{E}[x:=v]}{\kappa_1}
+\end{array}
+\]
+The first step is substitution of variables. The second step is by the property 
+(1) of Definition~\ref{def:Lazy-D-Cast-ADT}. And the third and final step is by 
+the property (1) of Definition~\ref{def:monoid}.
+\[
+\begin{array}{rll}
+\sOOreturn{v'}{\kappa'} 
+	&=
+	&\sOOreturn{v'}{\kOOappII{\vOOfun{\mathcal{E}'}{x}{e}}{\kappa_1'}}\\
+	&\longmapsto_{\ineffCEKD}
+	&\sOOinspect{e}{\mathcal{E}'[x:=v']}{\kappa_1'}
+\end{array}
+\]
+\item[Case 
+$\inference{
+	\hcvOOfun{c_3}{\mathcal{E}}{x}{e}{c_4} \approx v_2' : \POOfun{T_1}{T_2}
+}{
+	\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}
+		\approx
+	\vOOcast{v_2'}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
+		: \POOfun{T_3}{T_4}
+}
+\begin{array}{l}
+	c_1 = seq(cast(T_3,l,T_1),c_3) \\
+	c_2 = seq(c_4,cast(T_2,l,T_4))
+\end{array}$] 
+\[
+\begin{array}{rcl}
+\continue{k}{v}
+&=
+&\continue{\kOOappII{\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}}{\kappa_1}}{v}
+\\
+&=
+&\begin{cases}
+\sOOinspect{e}{\mathcal{E}[x:=v_1]}{ext(c_2,\kappa)}  &
+\sidecond{applyCast(v,c_1) = \rOOsucc{v_1}}
+\\
+\sOOhalt{l} &
+\sidecond{applyCast(v,c_1) = \rOOfail{l}}
+\end{cases}
+\end{array}
+\]
+
+By property (3) of Monoid (Definition~\ref{def:monoid}), we have
+\[
+ext(c_2,\kappa) = ext(c_4,ext(cast(T_2,l,T_4),\kappa))
+\]
+By property (2) of Lazy D Cast ADT (Definition~\ref{def:Lazy-D-Cast-ADT}), 
+we have
+\[
+applyCast(v,c_1) = applyCast(cast(T_3,l,T_1), v) \mbind{} \lambda v. 
+applyCast(c_3,v)
+\]
+In the \ineffCEKD{} side, we have the following reduction
+\[
+\begin{array}{rll}
+\sOOreturn{v'}{\kappa'} 
+&=
+&\sOOreturn{v'}{\kOOappII{\vOOcast{v_2'}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}}{\kappa_1'}}\\
+&\longmapsto_{\ineffCEKD}
+&\sOOreturn{v'}{\kOOcast{\cOOcast{T_3}{l}{T_1}}{\kOOappII{v_2'}{\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa_1'}}}}\\
+&\longmapsto_{\ineffCEKD}
+&\begin{cases}
+	\sOOreturn{v_3'}{{\kOOappII{v_2'}{\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa_1'}}}}
+		& \sidecond{applyCast(v',\cOOcast{T_3}{l}{T_1}) = \rOOsucc{v_3'}}\\
+	\sOOhalt{(\oOOblame{l})} 
+		& \sidecond{applyCast(v',\cOOcast{T_3}{l}{T_1}) = \rOOfail{l}}
+\end{cases}
+\end{array}
+\]
+By Lemma~\ref{lem:lem-apply-cast-preserve-bisim}, 
+$applyCast(v,cast(T_3,l,T_1)) \approx applyCast(v',\cOOcast{T_3}{l}{T_1})$.  
+When both cast applications fail, both machines transition to halting states 
+with the same blame label.
+When both cast applications succeed, we apply the induction hypothesis.
+\end{description}
+
+\end{proof}
+%
+%\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}]
+%  \label{thm:SD-bisim}
+%  Assume $C$ implements Lazy D Cast ADT
+%  and $C$ is a monoid
+%  and $cast(T,l,T)=id(T)$,
+%  $s_{1} \in \text{\effCEK{C}}$,
+%  $s_{2} \in \text{\ineffCEKD}$,
+%  $s_{1} \approx s_{2}$,
 %\begin{enumerate}
-%  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
-%%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
-%  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
-%    then $\judgeDreduce{s_2}{s_4}$ 
-%    and  $s_3 \approx^{*} s_4$
-%    for some $s_4$
-%  \item If $\judgeDreduce{s_2}{s_4}$
-%    then $\judgeSreduce{C}{s_1}{s_3}$ 
-%    and  $s_3 \approx^{*} s_4$
-%    for some $s_3$
-%\end{enumerate}
-%{\color{red}
-%  Jeremy's attempt to reformulate in a more standard way that
-%  remains equivalent:
-%\begin{enumerate}
-%\item If $\judgeSreduce{C}{s_1}{s_3}$ then
-%  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
-%\item If $\judgeDreduce{s_2}{s_4}$ then
-%  $\judgeSreduce{C}{s_1}{s_3}$,
+%	\item If $\judgeSreduce{C}{s_1}{s_3}$ then
+%	$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
+%	\item If $\judgeDreduce{s_2}{s_4}$ then
+%	$\judgeSreduceTrans{C}{s_1}{s_3}$,
 %	$\judgeDreduceTrans{s_4}{s_5}$, and
 %	$s_3 \approx s_5$ for some $s_3$ and $s_5$.
-%\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%	\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
 %\end{enumerate}
+%%\begin{enumerate}
+%%  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%%%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
+%%  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
+%%    then $\judgeDreduce{s_2}{s_4}$ 
+%%    and  $s_3 \approx^{*} s_4$
+%%    for some $s_4$
+%%  \item If $\judgeDreduce{s_2}{s_4}$
+%%    then $\judgeSreduce{C}{s_1}{s_3}$ 
+%%    and  $s_3 \approx^{*} s_4$
+%%    for some $s_3$
+%%\end{enumerate}
+%%{\color{red}
+%%  Jeremy's attempt to reformulate in a more standard way that
+%%  remains equivalent:
+%%\begin{enumerate}
+%%\item If $\judgeSreduce{C}{s_1}{s_3}$ then
+%%  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
+%%\item If $\judgeDreduce{s_2}{s_4}$ then
+%%  $\judgeSreduce{C}{s_1}{s_3}$,
+%%  $\judgeDreduceTrans{s_4}{s_5}$, and
+%%   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
+%%\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
+%%\end{enumerate}
+%%}
+%%Or diagrammatically, 
+%%  \[\begin{array}{clclc}
+%%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
+%%  \rotatebox[origin=c]{90}{$\approx$} 
+%%  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
+%%  s_{2} & 
+%%  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
+%%  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
+%%  \end{array}\]
+%\end{lemma}
+%\begin{proof}
+%  Part (3) follows from the definition of $s \approx s$.
+%  Part (1) and (2) are more interesting. 
+%  By the definition of $s \approx s$, it is straightforward to prove 
+%  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
+%  So we can prove two parts together by showing that if $s_{1} \approx s_{2}$
+%  and $\judgeDreduce{s_2}{s_4}$ then
+%  \[
+%%  \text{if}\; 
+%%  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
+%%  \;\text{and}\;\judgeDreduce{s_2}{s_4}
+%  \;\text{there exists}\; s'
+%  \;\text{such that}\; \judgeDreduceTrans{s_4}{s'}
+%  \;\text{and}\; s_3 \approx s'.
+%  \]
+%  To put it another way, our goal is to prove that 
+%  one reduction step in \effCEK{C} corresponds to
+%  one or more steps in \ineffCEKD.  
+%  Although there are many cases, the general idea is the same.
+%  Consider
+%  \[
+%  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
+%    wrap(\kOOcar{\kappa})
+%  }
+%  \approx
+%  \sOOreturn{v_2}{\kOOcar{\kappa}}
+%  \]
+%
+%  By looking at the definition of $v \approx v$, we know
+%  \begin{align*}
+%   c_{11} &= seq(seq(id(T_1),cast(T_1,l,T_3)) \dots) \\
+%   c_{12} &= seq(seq(id(T_2),cast(T_2,l,T_4)) \dots) \\
+%   v_2 &= \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
+%    \cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
+%  \end{align*}
+%  Thus we have the following reduction in \effCEK{C}. Then we employ
+%  equational reasoning that relies on the premise that $C$ is a
+%  monoid.
+%  \[
+%  \begin{array}{ll}
+%&
+%\sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{wrap(\kOOcar{\kappa})}
+%\\
+%\longmapsto_\text{\effCEK{C}} &
+%\sOOreturn{v_{11}}{ext(c_{11},\kappa)}
+%\\
+%= &
+%\sOOreturn{v_{11}}{ext(seq(seq(id(T_1),cast(T_1,l,T_3))\dots),\kappa)}
+%\\
+%= &
+%\sOOreturn{v_{11}}{
+%	ext(id(T_1),ext(cast(T_1,l,T_3),ext(\dots,\kappa)))
 %}
-%Or diagrammatically, 
-%  \[\begin{array}{clclc}
-%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
-%  \rotatebox[origin=c]{90}{$\approx$} 
-%  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
-%  s_{2} & 
-%  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
-%  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
-%  \end{array}\]
-\end{lemma}
-\begin{proof}
-  Part (3) follows from the definition of $s \approx s$.
-  Part (1) and (2) are more interesting. 
-  By the definition of $s \approx s$, it is straightforward to prove 
-  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
-  So we can prove two parts together by showing that if $s_{1} \approx s_{2}$
-  and $\judgeDreduce{s_2}{s_4}$ then
-  \[
-%  \text{if}\; 
-%  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
-%  \;\text{and}\;\judgeDreduce{s_2}{s_4}
-  \;\text{there exists}\; s'
-  \;\text{such that}\; \judgeDreduceTrans{s_4}{s'}
-  \;\text{and}\; s_3 \approx s'.
-  \]
-  To put it another way, our goal is to prove that 
-  one reduction step in \effCEK{C} corresponds to
-  one or more steps in \ineffCEKD.  
-  Although there are many cases, the general idea is the same.
-  Consider
-  \[
-  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
-    wrap(\kOOcar{\kappa})
-  }
-  \approx
-  \sOOreturn{v_2}{\kOOcar{\kappa}}
-  \]
-
-  By looking at the definition of $v \approx v$, we know
-  \begin{align*}
-   c_{11} &= seq(seq(id(T_1),cast(T_1,l,T_3)) \dots) \\
-   c_{12} &= seq(seq(id(T_2),cast(T_2,l,T_4)) \dots) \\
-   v_2 &= \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{
-    \cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
-  \end{align*}
-  Thus we have the following reduction in \effCEK{C}. Then we employ
-  equational reasoning that relies on the premise that $C$ is a
-  monoid.
-  \[
-  \begin{array}{ll}
-&
-\sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{wrap(\kOOcar{\kappa})}
-\\
-\longmapsto_\text{\effCEK{C}} &
-\sOOreturn{v_{11}}{ext(c_{11},\kappa)}
-\\
-= &
-\sOOreturn{v_{11}}{ext(seq(seq(id(T_1),cast(T_1,l,T_3))\dots),\kappa)}
-\\
-= &
-\sOOreturn{v_{11}}{
-	ext(id(T_1),ext(cast(T_1,l,T_3),ext(\dots,\kappa)))
-}
-\\
-= &
-\sOOreturn{v_{11}}{ext(cast(T_1,l,T_3),ext(\dots,\kappa)}
-  \end{array}
-  \]
-
-We have the following corresponding reduction in \ineffCEKD, where the
-last state is related to the above \effCEK{C} state.
-\[
-\begin{array}{ll}
-& \sOOreturn{
-  \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{   
-  \cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
-}{\kOOcar{\kappa}}
-\\
-\longmapsto_{\mathcal{D}}^{*} &
-\sOOreturn{(\vOOcons{v_{21}}{v_{22}})}{
-  \kOOcar{
-  \kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
-}}
-\\
-\longmapsto_{\mathcal{D}} &
-\sOOreturn{v_{21}}{
-  \kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
-}
-\end{array}
-\]
-
-Other cases are similar. Of course, we need the lemma about
-$applyCast$ (Lemma~\ref{thm:lem-apply-cast-SD}) when cast applications
-happen in both machines.  And in case splitting, we employ
-$cast(T,l,T)=id(T)$ to relate the continuation functions.
-\end{proof}
+%\\
+%= &
+%\sOOreturn{v_{11}}{ext(cast(T_1,l,T_3),ext(\dots,\kappa)}
+%  \end{array}
+%  \]
+% 
+%We have the following corresponding reduction in \ineffCEKD, where the
+%last state is related to the above \effCEK{C} state.
+%\[
+%\begin{array}{ll}
+%& \sOOreturn{
+%  \vOOcast{(\vOOcons{v_{21}}{v_{22}})}{   
+%  \cOOcast{\POOprod{T_1}{T_2}}{l_1}{\POOprod{T_3}{T_4}}} \dots
+%}{\kOOcar{\kappa}}
+%\\
+%\longmapsto_{\mathcal{D}}^{*} &
+%\sOOreturn{(\vOOcons{v_{21}}{v_{22}})}{
+%  \kOOcar{
+%  \kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
+%}}
+%\\
+%\longmapsto_{\mathcal{D}} &
+%\sOOreturn{v_{21}}{
+%  \kOOcast{\cOOcast{T_1}{l}{T_3}}{\dots\kappa}
+%}
+%\end{array}
+%\]
+%
+%Other cases are similar. Of course, we need the lemma about
+%$applyCast$ (Lemma~\ref{lem:lem-apply-cast-preserve-bisim}) when cast 
+%applications
+%happen in both machines.  And in case splitting, we employ
+%$cast(T,l,T)=id(T)$ to relate the continuation functions.
+%\end{proof}
 
@@
 	\;\text{if and only if}\;
-	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{\kOOmt}}{
+	\judgeDreduceTrans{\sOOinspect{e}{\emptyset}{\kOOmt}}{
 		\sOOhalt{o}
@@
 	\]
-	So we can generalize our goal, and prove that if $s_1 \approx s_2$
+	So we can generalize our goal, and prove that if $s_1 \approx s_1'$
 	\[
@@
 	\;\text{if and only if}\;
-	\judgeSreduceTrans{C}{s_2}{\sOOhalt{o}}
-	\]
-
-	Let us prove left to right first by induction on 
+	\judgeDreduceTrans{s_1'}{\sOOhalt{o}}
+	\]
+
+	Let us prove left to right first. We proceed by induction on 
 	$\judgeSreduceTrans{C}{s_1}{\sOOhalt{o}}$.
@@
 		\item 
-		If $s_1$ takes zero step to the halting state, it must be halting.
-		By Lemma~\ref{thm:SD-bisim}, $s_2$ is halting as well, so we are done.
+		$s_1 = \sOOhalt{o}$ implies $s_1' = \sOOhalt{o}$ by 
+		Lemma~\ref{lem:weak-bisim-SC-D}.
 		\item 
-		If $\judgeSreduce{C}{s_1}{s_3}$ and 
-		$\judgeSreduceTrans{C}{s_3}{\sOOhalt{o}}$,
-		by Lemma~\ref{thm:SD-bisim}, there exists a $s_4$ such that 
-		$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$. So we can apply 
-		our induction hypothesis.
+		If $\judgeSreduce{C}{s_1}{s}$ and 
+		$\judgeSreduceTrans{C}{s}{\sOOhalt{o}}$ for some $s$,
+		by Lemma~\ref{lem:weak-bisim-SC-D}, there exists $s_2$ and $s_2'$ such 
+		that $\judgeSreducePlus{C}{s_1}{s_2}$ and 
+		$\judgeDreducePlus{s_1'}{s_2'}$ 
+		and $s_2 \approx s_2'$. The transition $\judgeSreducePlus{C}{s_1}{s_2}$ 
+		must be a prefix of $\judgeSreducePlus{C}{s_1}{\sOOhalt{o}}$ because 
+		\effCEK{C} is deterministic (Proposition~\ref{prp:SC-deterministic}) 
+		and halting states are stuck. 
+		So we can apply our induction hypothesis on $s_2 \approx s_2'$
 	\end{itemize}
-
-	Now let us prove right to left by induction on 
-	$\judgeDreduceTrans{s_2}{\sOOhalt{o}}$.
-	\begin{itemize}
-		\item If $s_2$ takes zero step to the halting state, it must be halting.
-		By Lemma~\ref{thm:SD-bisim}, $s_2$ is halting as well, so we are done.
-		\item If $\judgeDreduce{s_2}{s_4}$ and 
-		$\judgeDreduceTrans{s_4}{\sOOhalt{o}}$,
-		by Lemma~\ref{thm:SD-bisim}, there exist $s_3,s_5$ such that
-		\[
-			\judgeSreduceTrans{C}{s_1}{s_3}
-			\;\text{and}\;
-			\judgeDreduceTrans{s_4}{s_5}
-			\;\text{and}\;
-			s_3 \approx s_5
-		\]
-		From $\judgeDreduceTrans{s_4}{\sOOhalt{o}}$ and 
-		$\judgeDreduceTrans{s_4}{s_5}$ we know 
-		$\judgeDreduceTrans{s_5}{\sOOhalt{o}}$ because our machine is 
-		deterministic. Now we can apply our induction hypothesis.
-	\end{itemize}
+	The other direction is similar.
 %  Proving that the left-hand side implies the right-hand side is
@@
   \label{thm:surely-lazyD-eqv}
-  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT. If 
-  $\judgetype{\emptyset}{e}{T}$ and $o : T$ then
-  \[
-  \evalEqv{\effCEK{C_1}}{\effCEK{C_2}}
-  \]
-%  \[
-%  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
-%  \]
+  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
+  \[
+  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
+  \]
 \end{proposition}
 \begin{proof}
-  Without loss of generality, assume $\judgeSeval{C_1}{e}{o}$ and prove 
-  $\judgeSeval{C_2}{e}{o}$.\\
+  Without loss of generality, assume $\judgeSreduce{C_1}{e}{o}$ and prove 
+  $\judgeSreduce{C_2}{e}{o}$.\\
   By the definition of $eval_{\mathcal{S}(C)}$, we know 
 \[
-\judgeSreduceTrans{C_1}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
+\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
 \]
@@
 \]
-  that is, $\judgeSeval{C_2}{e}{o}$
+  that is, $\judgeSreduce{C_2}{e}{o}$
 \end{proof}
@@
   Suppose $C$ is a \lazyD{} Cast ADT.  If
-  $\judgetype{\emptyset}{e}{T}$ and $o : T$ then
+  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
   \[
   \evalEqv{\effCEK{C}}{\ineffCEKD}
+%  \judgeSeval{C}{e}{o}
+%  \;\text{if and only if}\;
+%  \judgeDeval{e}{o}
   \]

### 2020-01-04 paper.tex
add corollary: reformulated weak bisim S(C) D

@@
 
+\begin{corollary}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}, 
+reformulated]
+  Assume $C$ implements Lazy D Cast ADT
+  and $C$ is a monoid
+  and $cast(T,l,T)=id(T)$,
+  $s_1 \approx s_1'$,
+\begin{enumerate}
+	\item If $\judgeSreduce{C}{s_1}{s}$ for some $s$, then
+	$\judgeSreduceTrans{C}{s}{s_2}$, and
+	$\judgeDreducePlus{s_1'}{s_2'}$,
+	$s_2 \approx s_2'$ for some $s_2$ and $s_2'$.
+	\item If $\judgeDreduce{s_1'}{s'}$ for some $s'$, then
+	$\judgeDreduceTrans{s'}{s_2'}$, and
+	$\judgeSreducePlus{C}{s_1}{s_2}$,
+	$s_2 \approx s_2'$ for some $s_2$ and $s_2'$.
+	\item $s_1 = \sOOhalt{o}$ if and only if  $s_1' = \sOOhalt{o}$
+\end{enumerate}
+\end{corollary}
+\begin{proof}
+	By applying Lemma~\ref{lem:weak-bisim-SC-D} on $s_1 \approx s_1'$ and case 
+	analysis.
+\end{proof}
+
 \begin{corollary}[Correctness of \effCEK{C}]

### 2020-01-05 paper.tex
fixed fig 5
fixed statement about common-case coercions

--- 2019-12-29 paper.tex
@@
   \begin{array}{rclr}
-    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& v \\
+    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& \rOOsucc{v} \\
     \mathit{applyCast}(v, \cOOcast{P}{l}{\star}) &=&
-        v \langle \cOOcast{P}{l}{I} \rangle
-          \langle \cOOcast{I}{l}{\star} \rangle
+        \rOOsucc{v \langle \cOOcast{P}{l}{I} \rangle
+                   \langle \cOOcast{I}{l}{\star} \rangle}
         & \text{if } I \sim P, I \neq P \\  
     \mathit{applyCast}(v, \cOOcast{\star}{l}{P}) &=&          
-        v \langle \cOOcast{\star}{l}{I} \rangle
-          \langle \cOOcast{I}{l}{P} \rangle
+        \rOOsucc{v \langle \cOOcast{\star}{l}{I} \rangle
+                   \langle \cOOcast{I}{l}{P} \rangle}
         & \text{if } I \sim P, I \neq P \\  
-  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& v \\
+  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& \rOOsucc{v} \\
   \mathit{applyCast}(v \langle \cOOcast{I_1}{l}{\star} \rangle , \cOOcast{\star}{l}{I_2}) &=& \rOOfail{l} & \text{if } I_1 \neq I_2 \\
   \mathit{applyCast}(v, \cOOcast{P_1}{l}{P_2}) &=&
-     v \langle \cOOcast{P_1}{l}{P_2} \rangle & \text{if } P_1 \smile P_2
+           \rOOsucc{v \langle \cOOcast{P_1}{l}{P_2} \rangle}
+          & \text{if } P_1 \smile P_2
   \end{array}
@@
 Hypercoercions enable a bit-level representation that is particularly
-compact for the most common-case coercions. The most frequent
-coercions are injections and projections to base types (here
-$\POOunit$ is the only base type, but in a real language the base
-types would include integers, Booleans, etc.) and identity coercions.
-Values of base types are often stored in CPU registers, so it would be
-nice for coercions on base types to also fit in registers, that is, in
-64 bits, so that applying a coercion to a value would not require
-access to main memory, which is an order of magnitude slower than
-accessing registers on a modern CPU.
-%
-Coercions involving non-base types, such as function types,
-may be arbitrarily large, so in those cases, the hypercoercion
-representation can be a pointer to a heap-allocated structure.  Here
-is a sketch for the bit-level representation for hypercoercions.
+compact for identity coercions and coercions that project from base
+types or inject to base types.  (Here $\POOunit$ is the only base
+type, but in a real language the base types would include integers,
+Booleans, etc.)  We conjecture that such coercions occur more
+frequently than the more complex coercions (e.g. between function
+types), especially because such coercions appear in the leaves of
+complex coercions.
+
+Futhermore, values of base types are often stored in CPU registers, so
+it would be nice for coercions on base types to also fit in registers,
+that is, in 64 bits, so that applying a coercion to a value of base
+type would not require access to main memory, which is an order of
+magnitude slower than accessing registers on a modern CPU.
+%
+Coercions involving non-base types, such as function types, may be
+arbitrarily deep, so in those cases, the hypercoercion representation
+has to be a pointer to a heap-allocated structure.
+
+Here is a sketch for the bit-level representation for hypercoercions.
 

### 2020-01-06 paper.tex

--- 2020-01-04 paper.tex
@@
 \newcommand{\longdownmapsto}{\rotatebox[origin=c]{-90}{$\scriptstyle\longmapsto$}\mkern2mu}
-
 \newcommand{\mbind}{\ensuremath{\;\underline{\gg}\;}}
@@
 respectively. Additionally, there is the $\sOOhalt{o}$ configuration, where the 
-machine halts with an observation ($o$). Observations include all value 
-constructors and blame. The function converting values to 
-observations ($observe(v) = o$) is defined in the obvious way.
-%Let $s$ range over machine states. A state is either looking at an 
-%expression to decide what to do next, returning a value to a continuation, or 
-%halting with an observation.
+machine halts with an observable ($o$). Observables include all value 
+constructors, blame, and $\oOOdyn$, as in \citet{siek2012interpretations}. 
+The function converting values to observables ($observe(v) = o$) is defined in 
+the obvious way.
 
@@
   }
-  \stxrule{o}{Observations}{
-    \oOOinj \mid
+  \stxrule{o}{Observables}{
+    \oOOdyn \mid
     \oOOsole \mid

### 2020-01-06 paper.tex
related work

@@
 \begin{theorem}[\lazyD{} Hypercoercion Respect \ineffCEKD]
-  If $\judgetype{\emptyset}{e}{T}$ and $o : T$
+  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
   \[
@@
 \end{proof}
+
+\section{Related Work} \label{sec:related-work}
+
+\newcommand{\lambdaX}[1]{\ensuremath{\lambda\mathtt{#1}}}
+\newcommand{\lambdaB}{\lambdaX{B}}
+\newcommand{\lambdaS}{\lambdaX{S}}
+
+This section provides a comparison to the work of 
+\citet{Siek:2015:BCT:2737924.2737968}. Their blame calculus 
+(\lambdaB) is 
+similar to our cast calculus (Fig.~\ref{fig:blame-static}). Their \lambdaB\
+has base types and primitive operators, while ours has unit, sum, and product.
+
+They define a translation from \lambdaB\ space-efficient coercion calculus 
+\lambdaS, which has a space-efficient dynamic semantics, and show a 
+bisimulation between \lambdaB\ and \lambdaS. Our work executes the 
+source language with a space-efficient abstract machine, thus has no 
+\lambdaS-like intermediate language.
+
+A strength of their separation of compilation/translation and execution is that 
+they prove the translation is fully abstract and exploit this theorem to prove 
+other interesting theorems (Section 5 of \citet{Siek:2015:BCT:2737924.2737968}).
+
+An advantage of our work is that \effCEK{C} and its related theorems are 
+parameterized over Lazy D Cast ADT. Their work, on the contrary, is specific to 
+their space-efficient coercions.
 

### 2020-01-16 paper.tex
change header

--- 2020-01-06 paper.tex
@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max
-
-%%submission space)
-\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max 
-%%submission space)
-%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-%\documentclass[acmsmall]{acmart}\settopmatter{}
-
-%% Journal information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2020}
-\acmMonth{1}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
+\documentclass[acmsmall,screen]{acmart}\settopmatter{printacmref=true}
+\acmConference[WGT20]{ACM SIGPLAN Workshop on Gradual Typing}{January 25,
+	2020}{New Orleans}
+\acmBooktitle{Informal Proceedings of the first ACM SIGPLAN Workshop on
+	Gradual Typing (WGT20)}
+\acmDOI{}
+\acmPrice{}
 \setcopyright{none}
+%
+%%% For double-blind review submission, w/o CCS and ACM Reference (max 
+%
+%%%submission space)
+%\documentclass[acmsmall]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+%%% For double-blind review submission, w/ CCS and ACM Reference
+%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
+%%% For single-blind review submission, w/o CCS and ACM Reference (max 
+%%%submission space)
+%%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+%%% For single-blind review submission, w/ CCS and ACM Reference
+%%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
+%%% For final camera-ready submission, w/ required CCS and ACM Reference
+%%\documentclass[acmsmall]{acmart}\settopmatter{}
+%
+%
+%%% Journal information
+%%% Supplied to authors by publisher for camera-ready submission;
+%%% use defaults for review submission.
+%\acmJournal{PACMPL}
+%\acmVolume{1}
+%\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
+%\acmArticle{1}
+%\acmYear{2020}
+%\acmMonth{1}
+%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
+%\startPage{1}
+%
+%%% Copyright information
+%%% Supplied to authors (based on authors' rights management selection;
+%%% see authors.acm.org) by publisher for camera-ready submission;
+%%% use 'none' for review submission.
+%\setcopyright{none}
 %\setcopyright{acmcopyright}

### 2020-01-24 Slides/tex/slides.tex
finalize

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{beamer}
\usepackage{natbib}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
% this default might be overridden by plain title style
\newcommand\makebeamertitle{\frame{\maketitle}}%
% (ERT) argument for the TOC
%\AtBeginDocument{%
%  \let\origtableofcontents=\tableofcontents
%  
%\def\tableofcontents{\@ifnextchar[{\origtableofcontents}{\gobbletableofcontents}}
%  \def\gobbletableofcontents#1{\origtableofcontents}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\usetheme{Warsaw}
% or ...

%\setbeamercovered{transparent}
% or whatever (possibly just delete it)

\makeatother

\usepackage{babel}
\begin{document}

\title{Hypercoercions and a Framework for Equivalence of Cast Calculi}

\author{Kuang-Chen Lu\inst{1} \and Jeremy G. Siek\inst{1}\and Andre Kuhlenschmidt\inst{1}}

\institute{\inst{1}Department of Computer Science\\
Indiana University Bloomington}

\date[WGT 2003]{Workshop on Gradual Typing, 2020}

\makebeamertitle

\pgfdeclareimage[height=0.5cm]{institution-logo}{institution-logo.jpg}
\logo{\pgfuseimage{institution-logo}}

%\AtBeginSubsection[]{%
%  \frame<beamer>{ 
%    \frametitle{Outline}   
%    \tableofcontents[currentsection,currentsubsection] 
%  }
%}

%\beamerdefaultoverlayspecification{<+->}
\begin{frame}{Outline}

\tableofcontents{}

\end{frame}

\section{Hypercoercions}

\subsection{The Space-Efficiency Problem}
\begin{frame}{An Example Program}

\framesubtitle{}

\includegraphics[scale=0.3]{resources/even-odd}
\end{frame}
%
\begin{frame}{The Space-Efficiency Problem}
\begin{itemize}
\item Casts might accumulate on continuations (call stacks)
\item Casts might accumulate in values as proxies
\end{itemize}
\end{frame}
%

\subsection{Existing Solutions}
\begin{frame}{Solutions: Space-Efficient Cast Representations}

\begin{itemize}
\item Coercions in normal forms \cite{herman2010space,siek2012interpretations,Siek:2015:BCT:2737924.2737968}
\item Threesomes \cite{Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603}
\item Supercoercions \cite{Garcia:2013:CTB:2500365.2500603}
\end{itemize}
\end{frame}
%
\begin{frame}{Criteria for ``Good'' Cast Representations }

\begin{figure}
\begin{minipage}[t]{0.45\textwidth}%
\includegraphics[scale=0.25]{resources/thinking-face}%
\end{minipage}\hfill{}%
\begin{minipage}[t]{0.45\textwidth}%
\includegraphics[scale=0.5]{resources/all-proof-assistants}%
\end{minipage}
\end{figure}
\end{frame}
%
\begin{frame}{Threesomes are Difficult to Understand}

\begin{figure}
\noindent\begin{minipage}[t][1\totalheight][c]{1\columnwidth}%
\begin{wrapfigure}{I}{0.5\columnwidth}%
\includegraphics[scale=0.7]{resources/Philip_Wadler}\end{wrapfigure}%
\textit{``\ldots{} while preparing a lecture on threesomes a few years
after the paper was published, he required several hours to puzzle
out the meaning of his own notation, $\bot^{mGp}$''\cite{Siek:2015:BCT:2737924.2737968}}%
\end{minipage}
\end{figure}
\end{frame}
%
\begin{frame}{Coercions in Normal Form are Difficult to Mechanize}

\begin{figure}
\includegraphics[scale=0.3]{resources/composition-of-coercions-in-normal-form}

v.s.

\textasciitilde 100 Lines of Agda Code
\end{figure}
\end{frame}
%

\subsection{Our Solution: Hypercoercions}
\begin{frame}{Our Solution: Hypercoercions}

\begin{figure}
\includegraphics[scale=0.4]{resources/hypercoercions-syntax}

Composition of hypercoercions is morally a structural recursion!
\end{figure}
\end{frame}

\section{Equivalence of Cast Calculi}

\subsection{Cast Representations Should be Proved Correct}
\begin{frame}{What do We Mean by a Cast Representation is Correct?}

\[
\text{eval}_{X}(e)=o\text{ if and only if }\text{eval}_{\text{D}}(e)=o
\]

\[
\text{eval}_{X}(e)=o\text{ if and only if }\text{eval}_{\text{UD}}(e)=o
\]
\end{frame}
%

\subsection{Our Solution: CastADT + Parameterized Dynamics}
\begin{frame}{Our Solution: Every Lazy D CastADT is Correct}
\begin{theorem}
Suppose that $C$ is a Lazy D Cast ADT. If $e:T$ and $o:T$ then
\[
\text{eval}_{S(C)}(e)=o\text{ if and only if }\text{eval}_{\text{D}}(e)=o
\]
\end{theorem}

\end{frame}
%
\begin{frame}{How does $S(C)$ work?}
\begin{itemize}
\item Every continuation has exactly one cast frame at the top.
\item Every non-constant value has exactly one proxy.
\end{itemize}
\end{frame}
%
\begin{frame}{What is a Cast ADT?}

\begin{table}
\begin{tabular}{rl}
$\text{id}(T)=c$ & identity cast\tabularnewline
$\text{seq(c,c)}=c$ & cast composition\tabularnewline
$\text{cast}(T,l,T)=c$ & translate casts in source language\tabularnewline
$\text{applyCast}(v,c)=r$ & cast application\tabularnewline
\end{tabular}
\end{table}
\end{frame}
%
\begin{frame}{What is a Lazy D Cast ADT?}
\begin{itemize}
\item $\text{applyCast}(\text{id}(T),v)=\text{succ}(v)$
\item $\text{applyCast}(\text{seq}(c,d),v)=\text{applyCast}(c,v)\underline{\gg}\lambda u.\text{applyCast}(d,u)$
\item $\text{applyCast}(\text{cast}(S,l,T),v)$ respects the Lazy D blame
strategy.
\end{itemize}
\end{frame}

\section*{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item We presented Lazy D and Lazy UD \alert{hypercoercions}.
\item We proved that every \alert{Lazy D Cast ADT} is correct.
\end{itemize}
\medskip{}

\begin{itemize}
\item Outlook
\begin{itemize}
\item Define a Lazy UD Cast ADT and prove a similar theorem.
\item Prove existing cast representations are Lazy D/UD Cast ADT
\end{itemize}
\end{itemize}
\end{frame}
%
\begin{frame}{References}

\bibliographystyle{plain}
\bibliography{/home/lukc/hypercoercion-and-framework-wgt2020/bibfile}
\end{frame}

\end{document}
